### 2024-01-01 main.tex
Add files via upload

\documentclass[12pt]{article}
\usepackage[right=0.7in,left=0.7in,top=1in,bottom=1in]{geometry}
\usepackage{hyperref}
\hypersetup{colorlinks, citecolor=blue, filecolor=blue, linkcolor=blue, urlcolor=blue}
\usepackage{graphicx}
\usepackage{url}
\usepackage[round]{natbib}
\usepackage{amsmath,amsthm} 
\usepackage{engord}
\usepackage{float}
\usepackage{subfig}
\usepackage{pdflscape}
\usepackage{booktabs}
\usepackage{pgfplots}
\pgfplotsset{compat=1.14}
\pgfplotsset{every axis label/.append style={font=\tiny}}
\usepackage[labelsep=period]{caption} %% This switches "Table 1: Title" to "Table 1. Title"

\usepackage{amssymb} %% Necessary, just for the \checkmark command  in tables.
\usepackage{multirow} %% Necessary if we are doing tables in LaTeX

\usepackage{xr}

\usepackage{setspace}
\onehalfspacing

\usepackage{sectsty}
\sectionfont{\large}
\subsectionfont{\normalsize}
\subsubsectionfont{\normalsize}

\newcommand{\specialcell}[2][c]{\begin{tabular}[#1]{@{}l@{}}#2\end{tabular}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{ \vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{
We are grateful for various people from various university, and several conferences for useful feedback. 
}}

\author{Version Zero \thanks{University of Michigan. \href{mailto:zxuyuan@umich.edu}{zxuyuan@umich.edu}} \and Jan 2024\thanks{Feel Free to modify} }
%\author{Author One \thanks{TK University and NBER.
%\href{mailto:TK@TK.edu}{TK@TK.edu}} \and Author Two\thanks{TK University and
%NBER.  \href{mailto:TK@TK.edu}{TK@TK.edu}} \and Author Three\thanks{TK
%University. \href{mailto:TK@TK.edu}{TK@TK.edu}}}

\date{ \vspace*{0.5cm} Jan 2024\\
\textbf{Preliminary and Incomplete.}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\bgroup
\let\footnoterule\relax

\begin{singlespace}
\maketitle

\begin{abstract}
    \noindent This is the main result of the baseline regression and dynamic analysis. You can read the Model and Results section to get more details. Moreover, the Discussion and Conclusion section are the most important part, because this is what we should discuss to make the paper better.
  \end{abstract}
\end{singlespace}
\thispagestyle{empty}

\clearpage
\egroup
\setcounter{page}{1}

%% Temporary tool to track how this paper is structured. Feel free to comment in or out. 
% \tableofcontents
% \bigskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%\section{Introduction\label{sec:introduction}}

\noindent

The remainder of the paper proceeds as follows. Section \ref{sec:model} describes the model. We then present our
empirical results in Section \ref{sec:results}. Finally, Section \ref{sec:discussion} provides the discussion and Section \ref{sec:conclusion} concludes.

\section{Introduction \label{sec:introduction}}

Brief introduction and summary of papers.

\section{Background \label{sec:background}}

Brief background.

\section{Data \label{sec:data}}

This section describes the data and statistical summary. Should consist of graph and one big table.

\section{Model \label{sec:model}}

This is the main result that we have currently done.

The dependent variable is \emph{the natural logarithm of lianjia's income}, \emph{the natural logarithm of lianjia's transaction price} and \emph{the natural logarithm of negotiation period} and in order to quantify the effect of lianjia, we propose three sets of explanatory variables. First, we construct a density based index (DBI) to capture the effect of lianjia's effect and continuous expansion effect. It is defined as the  Second, we construct a proxy variable to capture the effect of the continuous DBI effect. Third, we construct a set of variables to capture the effect of lianjia's entry and continuous expansion.

There are three sets of explanatory variables, including the density-based index (DBI), entry and its continuous effects, and proxy variables capturing the continuous effects of the DBI. First, the DBI is defined as the number of lianjia's stores in a given region as a percentage of the total number of stores in that region. The index is a direct measure of the market power of lianjia in that region. Second, the entry effect of lianjia and its continuous effect are defined as a set of dummy variables consisting of the time of lianjia's entry into that particular market and the corresponding pre- and post-periods. Since we only have seven years in our panel data, we construct seven periods as: $Pre_3 Pre_2, Pre_1, Entry, Post_1, Post_2, Post_3$, while in our regression model, we drop $Pre_1$ in the model and use it as the reference group. The proxy variable is defined as the product of lianjia's market entry and its continuous effects and the DBI, which captures lianjia's local market power. We do not combine all indicators in a single regression because they may interact with each other, making our estimation and interpolation difficult.

We first construct the multi-way clustering with fixed effect model to estimate DBI on the dependent variables. The model is as follows:

\begin{equation}
  Y_{it} = \beta_0 + \beta_1 density_{it} + \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}.
\end{equation}

where $Y_{it}$ is the three main dependent variables, including $\log(income), \log(price)$, and $\log(period)$, $density_{it}$ is the DBI, $\bf{X}_{it}$ is a set of control variables, including brokerage\_control L\_hedonic\_control, transaction\_control and region\_control, while $\tau_{it}$ is the time dummy variable interacting with the fixed effect of the business area, $\mu_i$ is the individual fixed effect and $\epsilon_{it}$ is the error term. The standard errors are clustered at the individual level.

When it comes to the estimation of the entry effect and its continuous effect, we use the following model:

\begin{equation}
  \begin{aligned}
    Y_{it} & = \beta_0 + \beta_1 Pre_3 + \beta_2 Pre_2 + \beta_3 Entry \\
    & + \beta_4 Post_1 + \beta_5 Post_2 + \beta_6 Post_3  + \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}.
  \end{aligned}
\end{equation}

where $Pre$ is the pre-period of lianjia's entry, $Entry$ is the entry period, and $Post$ is the post-period of lianjia's entry. All other model settings are the same as the previous model.

Finally, we construct a proxy variable to capture the continuous effect of the DBI. The model is as follows:

\begin{equation}
  \begin{aligned}
    Y_{it} & = \beta_0 + \beta_1 proxy\_entry + \beta_2 proxy\_pos\_1 \\
    & + \beta_3 proxy\_pos\_2 + \beta_4 proxy\_pos\_3 + \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}.
  \end{aligned}
\end{equation}

where $proxy\_entry$ is the product of the entry effect and the DBI, and $proxy\_pos\_i$ is the product of the post-period effect and the DBI. All other model settings are the same as the previous model. The results are shown in Appendix Table \ref{tab:Baseline} and Appendix Table \ref{tab:Dynamic}.

However, our estimates may not be asymptotically efficient due to the endogeneity of DBI and serial correlation issues. First, DBI is endogenous because the entry of lianjia is endogenous. This is due to the fact that lianjia will choose better locations with higher potential revenues in order to maximize profits. Second, the model suffers from serial correlation because our sample is during the boom period of China's real estate market, and as the number of transactions in the real estate market increases, so do the revenues and prices in the brokerage industry. In addition, lianjia tend to be concentrated in popular areas, which makes for greater growth and thus confounds our estimates. To solve this problem, we use a dynamic panel model for estimation. Dynamic panel models can capture the dynamics of the process by using the lagged dependent variable as a regression variable. This helps in understanding how the past values of the variables affect their current values.

To estimate the dynamic panel model, we use the Arellano-Bond (1991) GMM estimator, which is a two-step estimator. The first step is to use the lagged dependent variable as an instrument for the current dependent variable, and the second step is to use the lagged residuals as an instrument for the current dependent variable. In this paper, we do not use system GMM estimator because the system GMM must assume that the lagged explanatory variables are independent of factors that do not vary over time in the region, and this clearly cannot hold in the present setting. The model is as follows: [\textbf{this should be a line that describes what measures that we use to construct the model}]

\begin{equation}
  \begin{aligned}
    \Delta Y_{it} & = \rho \Delta Y_{it-1} + \beta_1 \Delta Measure_{it} + \bf{\alpha} \Delta \bf{X}_{it} + \Delta \tau_{it} + \Delta \epsilon_{it}.
  \end{aligned}
\end{equation}

where $\Delta Y_{it}$ is the first difference of the dependent variable, $\Delta Measure_{it}$ is the first difference of the our three measurement methods, $\Delta \bf{X}_{it}$ is the first difference of the control variables, $\Delta \tau_{it}$ is the first difference of the time dummy variable interacting with the fixed effect of the business area, and $\Delta \epsilon_{it}$ is the first difference of the error term. The standard errors are clustered at the individual level. The results are shown in Appendix Table \ref{tab:GMM}.

\section{Results \label{sec:results}}

\subsection{Main Results \label{sec:mainresults}}

For Table \ref{tab:Baseline}, the result reveals a significant correlation between the lianjia's local market power and lianjia's income in this given community. However, we discovered no substantial influence of lianjia's local market power on the housing prices or transaction periods in the same community. This could be interpreted to mean that whilst Lianjia's local market power could induce an increase in income, it does not necessarily grant them any significant pricing power nor expedite the transaction period. Therefore, we may deduce that the augmentation of Lianjia's income is primarily driven by an increase in the number of transactions, presumably due to more property listings by Lianjia within the community. This suggests that although lianjia can control more market share in the local market, it does not necessarily mean that it can have monopoly power in this given region. This is partially because the price of the house is determined by the market, and there are also some potential other brokerages that can enter the market. However, lianjia's local market power can still have a significant influence on the income because they can list more housings and have more transactions in the local market.

To further test the results, we first check if lianjia's entry effect and continuous effect is significant. For column 1, 3, and 5 of the Table \ref{tab:Dynamic}, the result reveals that before the lianjia's entry, the natural logarithm of income, housing price and transaction period are not significant. After the entry, we see that after lianjia's entry into this local market, lianjia can immediately increase their income and keep making significantly more income comparing with previous periods. Besides, we see that the entry do not significantly increase the housing price immediately but significantly increase housing price one year after but later on turning back to the normal pricing. Lastly, the lianjia's entry do not significantly lowers the transaction periods. This is consistent with our previous results that lianjia's entry can significantly increase the income but not the housing price and transaction periods in equilibrium.

Lastly, we use the third measurement to test after the lianjia's entry, the continuous effect of lianjia's local power of the local market. For column 2, 4, and 6 of the Table \ref{tab:Dynamic}, the result reveals that the continuous effect of lianjia's local power of the local market is significant for the income, housing price and transaction periods. This result indicates that in different period, the lianjia's local market power can have different influence on the market.

To deal with the endogeneity problem, I propose to use the GMM method to estimate the model. [\textbf{this should be a line that describes the method we construct the GMM model}]

The results in Table \ref{tab:GMM} show that the statistical significance of DBI is robust but our OLS model tends to underestimate the result. Furthermore, we can see that in different period, the lianjia's local market power can make lianjia gain significant more income in the long run but not in the short run after adjusting the serial correlation problems. Besides, lianjia's local market power can also significantly lower the housing prices in this community as well as significantly lower the transaction periods in the long run. This result means that our previous fixed effect model may not be asymptotically efficient and we shall use the GMM method to estimate the model.

Here, is the most important, we should carry out our causal inference and validate our GMM result! We should work on this right now! This is what we should discuss January 2.

\subsection{Robustness Check \label{sec:robustness}}

This section is pretty easy to construct, we can do various tricks. Moreover, we can select different regions with high and low night time lights to find out the different influence factors of lianjia. We just leave it here.

\section{Discussion \label{sec:discussion}}

Pool or separate is also a key issue that we need to take into consideration. Here are some potential ways that we can make the paper better. This exogenous shock can make sure our specification is correct, and we can discuss the following methods.

\begin{enumerate}
  \item Think about the RD design. There may be potential sharp discontinuties in the geosystem. We shall think about it geographically.
  \item Think about the DID design. Because we have multiple cities and multiple years, we can select some cities, which have policies in these years, and treat them as the treatment group and other cities as the control group.
  \item Think about potential IV. This is pretty hard -\_-.
\end{enumerate}

\section{Conclusion\label{sec:conclusion}}

Overall, this is the current results. Just finish the baseline regression and some dynamic analysis.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\begin{singlespace}
%\bibliographystyle{plainnat}
%\bibliographystyle{chicago}
\bibliographystyle{aer}
\bibliography{our-cites.bib}
\end{singlespace}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% These commands start the appendix and change the Table & Figure numbering
\newpage
\appendix
\setcounter{table}{0}
\renewcommand{\tablename}{Appendix Table}
\renewcommand{\figurename}{Appendix Figure}
\renewcommand{\thetable}{A\arabic{table}}
\setcounter{figure}{0}
\renewcommand{\thefigure}{A\arabic{figure}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Appendix Tables and Figures}
% \input{tab_tex/other-regressions.tex}

  \begin{table}[H]
    \begin{center}
    \caption{Baseline Regression Results}
    \label{tab:Baseline}   
    \input{../result_tables/baseline.tex} 
  \end{center}
  \end{table}

% \input{tab_tex/summary_stats.tex}

% \ref{tab:summary_statistics}

  \begin{table}[H]
    \begin{center}
      \begin{scriptsize}
    \caption{Dynamic Regression Results}
    \label{tab:Dynamic}
    \input{../result_tables/dynamic.tex}

\end{scriptsize}
\end{center}
  \end{table}

\begin{table}[H]
  \begin{center}
    \begin{scriptsize}
    \caption{GMM Regression Results}
    \label{tab:GMM}
    \input{../result_tables/gmm.tex}
    \end{scriptsize}
  \end{center}
\end{table}

\end{document}

\newpage 
\section{Appendix One \label{sec:appendix:first}}
\renewcommand{\thetable}{B\arabic{table}}
\setcounter{table}{0}
\renewcommand{\thefigure}{B\arabic{figure}}
\setcounter{figure}{0}

% \input{fig_tex/fig_another_figure.tex}

\newpage
\section{Appendix Two
\label{sec:appendix:two}}
\renewcommand{\thetable}{C\arabic{table}}
\setcounter{table}{0}
\renewcommand{\thefigure}{C\arabic{figure}}
\setcounter{figure}{0}

### 2024-01-03 nearest_community_cpp.cpp
Add files via upload

@@ -1,0 +1,48 @@
+#include <pybind11/pybind11.h>
+#include <pybind11/stl.h>
+#include <vector>
+#include <cmath> // Include the cmath library for math operations
+
+namespace py = pybind11;
+
+// Function to calculate Euclidean distance between two points
+double calculate_distance(const std::vector<double> &point1, const std::vector<double> &point2) {
+    double sum = 0.0;
+    for (size_t i = 0; i < point1.size(); ++i) {
+        double diff = point1[i] - point2[i];
+        sum += diff * diff;
+    }
+    return std::sqrt(sum);
+}
+
+std::vector<std::vector<int>> find_nearest_communities(const std::vector<std::vector<double>> &store_locations, const std::vector<std::vector<double>> &community_locations, int num_nearest_communities) {
+    std::vector<std::vector<int>> nearest_community_indices;
+
+    for (const auto &store_location : store_locations) {
+        std::vector<int> nearest_indices;
+        for (size_t i = 0; i < num_nearest_communities; ++i) {
+            double min_distance = std::numeric_limits<double>::max(); // Initialize with a large value
+            int nearest_index = -1;
+            for (size_t j = 0; j < community_locations.size(); ++j) {
+                // Calculate the distance between the store and community
+                double distance = calculate_distance(store_location, community_locations[j]);
+                if (distance < min_distance) {
+                    min_distance = distance;
+                    nearest_index = static_cast<int>(j);
+                }
+            }
+            if (nearest_index != -1) {
+                nearest_indices.push_back(nearest_index);
+            }
+        }
+        nearest_community_indices.push_back(nearest_indices);
+    }
+
+    return nearest_community_indices;
+}
+
+PYBIND11_MODULE(nearest_community_cpp, m) {
+    m.doc() = "Nearest Community Calculation";
+    m.def("find_nearest_communities", &find_nearest_communities, "Find nearest communities");
+}
+

### 2024-01-03 nearest_community_cpp.cpp
Add files via upload

@@ -2,43 +2,66 @@
 #include <pybind11/stl.h>
 #include <vector>
 #include <cmath> // Include the cmath library for math operations
+#include <limits> // Include the limits library for numeric_limits
 
 namespace py = pybind11;
 
-// Function to calculate Euclidean distance between two points
+// Function to calculate geographical distance between two points (km)
 double calculate_distance(const std::vector<double> &point1, const std::vector<double> &point2) {
-    double sum = 0.0;
-    for (size_t i = 0; i < point1.size(); ++i) {
-        double diff = point1[i] - point2[i];
-        sum += diff * diff;
-    }
-    return std::sqrt(sum);
+    const double earth_radius_km = 6371.0; // Earth's radius in kilometers
+
+    // Convert latitude and longitude from degrees to radians
+    double lat1_rad = point1[1] * M_PI / 180.0;
+    double lon1_rad = point1[0] * M_PI / 180.0;
+    double lat2_rad = point2[1] * M_PI / 180.0;
+    double lon2_rad = point2[0] * M_PI / 180.0;
+
+    // Haversine formula
+    double dlon = lon2_rad - lon1_rad;
+    double dlat = lat2_rad - lat1_rad;
+    double a = std::sin(dlat/2) * std::sin(dlat/2) + std::cos(lat1_rad) * std::cos(lat2_rad) * std::sin(dlon/2) * std::sin(dlon/2);
+    double c = 2 * std::atan2(std::sqrt(a), std::sqrt(1-a));
+    double distance_km = earth_radius_km * c;
+
+    return distance_km;
 }
 
-std::vector<std::vector<int>> find_nearest_communities(const std::vector<std::vector<double>> &store_locations, const std::vector<std::vector<double>> &community_locations, int num_nearest_communities) {
+py::tuple find_nearest_communities(const std::vector<std::vector<double>> &store_locations, const std::vector<std::vector<double>> &community_locations, int num_nearest_communities) {
     std::vector<std::vector<int>> nearest_community_indices;
+    std::vector<std::vector<double>> nearest_community_distances;
 
     for (const auto &store_location : store_locations) {
         std::vector<int> nearest_indices;
-        for (size_t i = 0; i < num_nearest_communities; ++i) {
-            double min_distance = std::numeric_limits<double>::max(); // Initialize with a large value
+        std::vector<double> nearest_distances;
+        std::vector<bool> is_community_selected(community_locations.size(), false);
+
[…]

### 2024-01-03 nearest_stores.cpp
Add files via upload

@@ -1,0 +1,56 @@
+#include <pybind11/pybind11.h>
+#include <pybind11/stl.h>
+#include <vector>
+#include <cmath>
+#include <limits>
+#include <queue>
+
+namespace py = pybind11;
+
+// Function to calculate geographical distance between two points (km)
+double calculate_distance(const std::vector<double> &point1, const std::vector<double> &point2) {
+    const double earth_radius_km = 6371.0; // Earth's radius in kilometers
+
+    // Convert latitude and longitude from degrees to radians
+    double lat1_rad = point1[1] * M_PI / 180.0;
+    double lon1_rad = point1[0] * M_PI / 180.0;
+    double lat2_rad = point2[1] * M_PI / 180.0;
+    double lon2_rad = point2[0] * M_PI / 180.0;
+
+    // Haversine formula
+    double dlon = lon2_rad - lon1_rad;
+    double dlat = lat2_rad - lat1_rad;
+    double a = std::sin(dlat/2) * std::sin(dlat/2) + std::cos(lat1_rad) * std::cos(lat2_rad) * std::sin(dlon/2) * std::sin(dlon/2);
+    double c = 2 * std::atan2(std::sqrt(a), std::sqrt(1-a));
+    double distance_km = earth_radius_km * c;
+
+    return distance_km;
+}
+
+py::tuple find_nearest_stores_to_communities(const std::vector<std::vector<double>> &store_locations, const std::vector<std::vector<double>> &community_locations, int num_nearest_stores) {
+    std::vector<std::vector<int>> nearest_store_indices(community_locations.size());
+    std::vector<std::vector<double>> nearest_store_distances(community_locations.size());
+
+    for (size_t i = 0; i < community_locations.size(); ++i) {
+        // Using a min heap to store the nearest stores
+        std::priority_queue<std::pair<double, int>, std::vector<std::pair<double, int>>, std::greater<std::pair<double, int>>> min_heap;
+
+        for (size_t j = 0; j < store_locations.size(); ++j) {
+            double distance = calculate_distance(community_locations[i], store_locations[j]);
+            min_heap.emplace(distance, j);
+        }
+
+        for (int k = 0; k < num_nearest_stores && !min_heap.empty(); ++k) {
+            nearest_store_indices[i].push_back(min_heap.top().second);
+            nearest_store_distances[i].push_back(min_heap.top().first);
+            min_heap.pop();
+        }
+    }
+
[…]

### 2024-01-04 analysis/RD design analysis.Rmd
Add files via upload

---
title: "RD design analysis"
author: "Xuyuan Zhang"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
geometry: "left=1.5cm,right=1.5cm,top=1cm,bottom=1.5cm"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(tidy=TRUE)
knitr::opts_chunk$set(fig.height=4)
knitr::opts_chunk$set(fig.width=7)
knitr::opts_chunk$set(warning=FALSE)
options(encoding = "UTF-8")
set.seed(123)
```

## structure

1. we first report the figure and export the figure to the folder named figures in directory
2. we then report the main result of the regressions
3. lastly, we report the placebo test and the robustness check

```{r}
# these are the packages that we need to import
library(haven)
library(ggplot2)
library(dplyr)
library(rdrobust)
library(plm)
library(pander) # this is for table showing
library(latex2exp) # this is to export it
```

```{r}
# need to place data on the base directory
data <- read_dta("../template.dta")
panel_data <- pdata.frame(data, index = c("id", "year"))
panel_data$L_jiadian <- lag(panel_data$jiadian, 1)
panel_data$L_kind <- lag(panel_data$kind, 1)
panel_data$L_hotel <- lag(panel_data$hotel, 1)
panel_data$L_shop_mall <- lag(panel_data$shop_mall, 1)
panel_data$L_museum <- lag(panel_data$museum, 1)
panel_data$L_old <- lag(panel_data$old, 1)
panel_data$L_ktv <- lag(panel_data$ktv, 1)
panel_data$L_mid <- lag(panel_data$mid, 1)
panel_data$L_prim <- lag(panel_data$prim, 1)
panel_data$L_west_food <- lag(panel_data$west_food, 1)
panel_data$L_super <- lag(panel_data$super, 1)
panel_data$L_sub <- lag(panel_data$sub, 1)
panel_data$L_park <- lag(panel_data$park, 1)
```

we use these control variables

```{r}
control_variables <- c(
  "jiadian", "kind", "hotel", "shop_mall", "museum", "old", "ktv", "mid", "prim", "west_food", "super", "sub", "park", 
  "area", "bedroom", "toilet", "house_age", "floor_level", "green_ratio", "total_building", "total_floor_number", "living_room", "elevator_ratio", "kitchen", "floor_ratio", "total_resident",
  "L_jiadian", "L_kind", "L_hotel", "L_shop_mall", "L_museum", "L_old", "L_ktv", "L_mid", "L_prim", "L_west_food", "L_super", "L_sub", "L_park",
  "pm25", "pop", "light",
  "non_online_effect", "ln_negotiation_period", "ln_watch_time", "ln_nego_changes",
  "density", "lianjia_5", "other_5", "ln_lead", "ln_watch_people"
)
```

```{r}
rdplot(y = filtered_data$ln_income, 
       x = filtered_data$density, 
       c = 0.2, p =1,  nbins = 20, 
       title = "RD-plot",
       x.label = "nearest distance to lianjia's stores",
       y.label = "lianjia's income in the community")
```

note that the figure only shows points that are within the bandwidth, the whole points are shown in Appendix of the paper.
```{r}
h = 0.151
cutoff = 0.5
running_var = panel_data$nearest_store_distances

filtered_data <- panel_data[abs(running_var - cutoff) <= h, ]

rdplot(y = filtered_data$ln_income, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, p = 1, nbins = 20, 
       title = "RD-plot",
       x.label = "nearest distance to lianjia's stores",
       y.label = "lianjia's income in the community")
```

```{r}
result <- rdrobust(y = panel_data$ln_income, x = panel_data$density, 
                   c = 0.2, covs = panel_data[, control_variables],
                   p = 1) # first using default clustering
```

```{r}
pander(cbind(result$coef, result$pv))
```

```{r}
result
```

### 2024-01-05 analysis/RD design analysis.Rmd
Rename RD design analysis.Rmd to analysis/RD design analysis.Rmd

@@
   "area", "bedroom", "toilet", "house_age", "floor_level", "green_ratio", "total_building", "total_floor_number", "living_room", "elevator_ratio", "kitchen", "floor_ratio", "total_resident",
-  "L_jiadian", "L_kind", "L_hotel", "L_shop_mall", "L_museum", "L_old", "L_ktv", "L_mid", "L_prim", "L_west_food", "L_super", "L_sub", "L_park",
   "pm25", "pop", "light",
-  "non_online_effect", "ln_negotiation_period", "ln_watch_time", "ln_nego_changes",
-  "density", "lianjia_5", "other_5", "ln_lead", "ln_watch_people"
+  "non_online_effect", "ln_negotiation_period", "ln_watch_time", "ln_nego_changes", "ln_lead", "ln_watch_people"
 )
@@
 ```{r}
-rdplot(y = filtered_data$ln_income, 
-       x = filtered_data$density, 
-       c = 0.2, p =1,  nbins = 20, 
-       title = "RD-plot",
-       x.label = "nearest distance to lianjia's stores",
-       y.label = "lianjia's income in the community")
-```
-
-note that the figure only shows points that are within the bandwidth, the whole points are shown in Appendix of the paper.
-```{r}
-h = 0.151
-cutoff = 0.5
-running_var = panel_data$nearest_store_distances
-
-filtered_data <- panel_data[abs(running_var - cutoff) <= h, ]
-
-rdplot(y = filtered_data$ln_income, 
-       x = filtered_data$nearest_store_distances, 
-       c = cutoff, p = 1, nbins = 20, 
-       title = "RD-plot",
-       x.label = "nearest distance to lianjia's stores",
-       y.label = "lianjia's income in the community")
+result <- rdrobust(y = panel_data$ln_income, x = panel_data$nearest_store_distances, 
+                   c = 0.41, covs = panel_data[, control_variables],
+                   p = 1) # first using default clustering
 ```
@@
 ```{r}
-result <- rdrobust(y = panel_data$ln_income, x = panel_data$density, 
-                   c = 0.2, covs = panel_data[, control_variables],
+result
+```
+
+```{r}
+pander(cbind(result$coef, result$pv))
+```
+
+```{r}
+result <- rdrobust(y = panel_data$ln_income, x = panel_data$nearest_store_distances, 
+                   c = 0.41,
                    p = 1) # first using default clustering
+```
+
+```{r}
+result
 ```
@@
 ```
+
+note that the figure only shows points that are within the bandwidth, the whole points are shown in Appendix of the paper.
+
+```{r}
+h = 0.095
+cutoff = 0.41
+running_var = panel_data$nearest_store_distances
+
+filtered_data <- panel_data[abs(running_var - cutoff) <= h, ]
+
+par(mfrow=c(3,1))
+rdplot(y = filtered_data$ln_income, 
+       x = filtered_data$nearest_store_distances, 
+       c = cutoff, nbins = 40, p = 1,
+       title = "RD-plot",
+       x.label = "nearest distance to lianjia's stores",
+       y.label = "lianjia's income in the community")
+
+rdplot(y = filtered_data$ln_income, 
+       x = filtered_data$nearest_store_distances, 
+       c = cutoff, nbins = 40, p = 2,
+       title = "RD-plot",
+       x.label = "nearest distance to lianjia's stores",
+       y.label = "lianjia's income in the community")
+
+rdplot(y = filtered_data$ln_income, 
+       x = filtered_data$nearest_store_distances, 
+       c = cutoff, nbins = 40, p = 3,
+       title = "RD-plot",
+       x.label = "nearest distance to lianjia's stores",
+       y.label = "lianjia's income in the community")
+```
+
+checkings:
+
+1.
+Donut Hole: Exclude observations close to the cutoff and estimate the effect with the remaining data.
+If the discontinuity persists despite the absence of data around the cutoff, this provides evidence against a model misspecification.
+2.
+Mccrary (2008) test: Conduct a McCrary density test to check if there is a discontinuity in the density of the running variable at the cutoff.
+A significant discontinuity may suggest manipulation or sorting around the cutoff.
+3.
+Placebo test: If you have pre-treatment covariates, you can test whether these covariates also jump at the cutoff.
+If they do, this might suggest manipulation or a violation of the RD design assumptions.
+If they don’t, it strengthens the case for a true treatment effect.
+
+```{r}
+cutoff
+donut_width <- 0.011
+panel_data_donut <- panel_data[!(panel_data$nearest_store_distances >= (cutoff - donut_width) & 
+                                 panel_data$nearest_store_distances <= (cutoff + donut_width)),]
+result_donut <- rdrobust(y = panel_data_donut$ln_income, 
+                         x = panel_data_donut$nearest_store_distances, 
+                         c = cutoff,
+                        p = 1, h = 0.066, b = 0.135)
+pander(cbind(result_donut$coef, result_donut$pv))
+print(result_donut)
+```
+
+```{r}
+donut_width <- 0.015
+panel_data_donut <- panel_data[!(panel_data$nearest_store_distances >= (cutoff - donut_width) & 
+                                 panel_data$nearest_store_distances <= (cutoff + donut_width)),]
+result_donut <- rdrobust(y = panel_data_donut$ln_income, 
+                         x = panel_data_donut$nearest_store_distances, 
+                         c = cutoff,  covs = panel_data_donut[, control_variables],
+                        p = 1, h = 0.095, b = 0.185)
+pander(cbind(result_donut$coef, result_donut$pv))
+print(result_donut)
+```
+
+```{r}
+
+library(rdd)
+
+# Give it the running variable and the cutpoint
+# it will automatically produce a plot and select the number of bins and the bandwidth
+# The output will be the p-value for the presence of a discontinuity
+DCdensity(panel_data$nearest_store_distances, cutpoint = 0.41, bw = 0.066, verbose = TRUE, plot = FALSE)
+```
+
+```{r}
+library(rdd)
+
+# Give it the running variable and the cutpoint
+# it will automatically produce a plot and select the number of bins and the bandwidth
+# The output will be the p-value for the presence of a discontinuity
+DCdensity(panel_data$nearest_store_distances, cutpoint = 0.41, bw = 0.095, verbose = TRUE, plot = FALSE)
+```
+
+Conducting placebo test
+
+```{r}
+# using the same bandwidth
+unrelated_result <- rdrobust(y = panel_data$ln_negotiation_period, 
+                             x = panel_data$nearest_store_distances, c = 0.41, h = 0.066, b = 0.135)
+print("Placebo test with unrelated outcome:")
+print(unrelated_result)
+pander(cbind(unrelated_result$coef, unrelated_result$pv))
+```

### 2024-01-05 analysis/RD design analysis.Rmd
Add files via upload

@@
 )
+testing_variables <- c("ln_negotiation_period", "ln_watch_time", "ln_nego_changes", "ln_lead", "ln_watch_people", "ln_end_price")
 ```
@@
 
-Conducting placebo test
+Conducting placebo test. We shall using the same validation bandwidth and bias correction bandwidth. The results are good overall
 
 ```{r}
-# using the same bandwidth
-unrelated_result <- rdrobust(y = panel_data$ln_negotiation_period, 
-                             x = panel_data$nearest_store_distances, c = 0.41, h = 0.066, b = 0.135)
-print("Placebo test with unrelated outcome:")
-print(unrelated_result)
-pander(cbind(unrelated_result$coef, unrelated_result$pv))
+for (validation in testing_variables) {
+  rd_result <- rdrobust(y = panel_data[[validation]], x = panel_data$nearest_store_distances
+                        , c = 0.41, h = 0.066, b = 0.135)
+  cat("Covariate:", validation, "\n")
+  print(summary(rd_result))
+  cat("\n\n")
+
+}
 ```

### 2024-01-08 classifying brokerages/find_stores_within.cpp
Add files via upload

@@ -1,0 +1,54 @@
+#include <pybind11/pybind11.h>
+#include <pybind11/stl.h>
+#include <vector>
+#include <cmath>
+#include <limits>
+#include <queue>
+
+namespace py = pybind11;
+
+// Function to calculate geographical distance between two points (km)
+double calculate_distance(const std::vector<double> &point1, const std::vector<double> &point2) {
+    const double earth_radius_km = 6371.0; // Earth's radius in kilometers
+
+    // Convert latitude and longitude from degrees to radians
+    double lat1_rad = point1[1] * M_PI / 180.0;
+    double lon1_rad = point1[0] * M_PI / 180.0;
+    double lat2_rad = point2[1] * M_PI / 180.0;
+    double lon2_rad = point2[0] * M_PI / 180.0;
+
+    // Haversine formula
+    double dlon = lon2_rad - lon1_rad;
+    double dlat = lat2_rad - lat1_rad;
+    double a = std::sin(dlat/2) * std::sin(dlat/2) + std::cos(lat1_rad) * std::cos(lat2_rad) * std::sin(dlon/2) * std::sin(dlon/2);
+    double c = 2 * std::atan2(std::sqrt(a), std::sqrt(1-a));
+    double distance_km = earth_radius_km * c;
+
+    return distance_km;
+}
+
+// this function calculates the number of stores within a given distance and records the corresponding labels to be further use.
+
+py::tuple find_stores_within(const std::vector<std::vector<double>> &store_locations, 
+                             const std::vector<std::vector<double>> &community_locations, 
+                             const std::vector<int> &labels, 
+                             double within_distance) {
+
+    std::vector<std::vector<int>> nearest_store_labels(community_locations.size());
+
+    for (size_t i = 0; i < community_locations.size(); ++i) {
+        for (size_t j = 0; j < store_locations.size(); ++j) {
+            double distance = calculate_distance(community_locations[i], store_locations[j]);
+            if (distance <= within_distance) {
+                nearest_store_labels[i].push_back(labels[j]);
+            }
+        }
+    }
+
+    return py::make_tuple(nearest_store_labels);
+}
+
+PYBIND11_MODULE(find_stores_within, m) {
+    m.doc() = "Find the stores within a given distance";
+    m.def("find_stores_within", &find_stores_within, "Find the stores within a given distance");
+}

### 2024-01-08 classifying brokerages/hhi_calculator.cpp

@@ -1,0 +1,44 @@
+#include <pybind11/pybind11.h>
+#include <pybind11/stl.h>
+#include <map>
+#include <vector>
+
+namespace py = pybind11;
+
+std::vector<double> calculate_HHI(const std::vector<std::vector<int>>& data) {
+
+    std::vector<double> HHI_indices;
+    for (const auto& row : data) {
+        std::map<int, int> frequency;
+        int totalMarketShare = 0;
+        int independentCount = 0; // total number of independent real estate brokerages in given segment
+        double HHI = 0;
+
+        for(int num: row){
+            if(num != -1){
+                frequency[num]++;
+                totalMarketShare += 1;
+            }
+            else{
+                independentCount++;
+                totalMarketShare += 1;
+            }
+        }
+
+        for(const auto& [key, count]: frequency){
+            double sharePercentage = static_cast<double>(count) / totalMarketShare;
+            HHI += sharePercentage * sharePercentage;
+        }
+
+        HHI += static_cast<double>(independentCount) / totalMarketShare / totalMarketShare;
+        HHI_indices.push_back(HHI);
+    }
+
+    return HHI_indices;
+}
+
+PYBIND11_MODULE(hhi_calculator, m) {
+    m.doc() = "Pybind11 example plugin"; // Optional module docstring
+
+    m.def("calculate_HHI", &calculate_HHI, "A function which calculates the HHI");
+}

### 2024-03-02 cleaning/calculate_nearby_points.cpp
Add files via upload

@@ -1,0 +1,46 @@
+#include <pybind11/pybind11.h>
+#include <pybind11/stl.h>
+#include <vector>
+#include <cmath>
+
+namespace py = pybind11;
+
+double calculate_distance(const std::vector<double> &point1, const std::vector<double> &point2) {
+    const double earth_radius_km = 6371.0;
+    const double deg_to_rad = M_PI / 180.0;
+
+    double lat1_rad = point1[1] * deg_to_rad;
+    double lon1_rad = point1[0] * deg_to_rad;
+    double lat2_rad = point2[1] * deg_to_rad;
+    double lon2_rad = point2[0] * deg_to_rad;
+
+    double dlon = lon2_rad - lon1_rad;
+    double dlat = lat2_rad - lat1_rad;
+    double a = std::sin(dlat/2) * std::sin(dlat/2) + std::cos(lat1_rad) * std::cos(lat2_rad) * std::sin(dlon/2) * std::sin(dlon/2);
+    double c = 2 * std::atan2(std::sqrt(a), std::sqrt(1-a));
+    double distance_km = earth_radius_km * c;
+
+    return distance_km * 1000; // Convert to meters
+}
+
+std::vector<int> calculate_counts(const std::vector<std::vector<double>> &array1, 
+                                         const std::vector<std::vector<double>> &array2, 
+                                         double within_distance_meters) {
+    std::vector<int> counts(array1.size(), 0);
+
+    for (size_t i = 0; i < array1.size(); ++i) {
+        for (size_t j = 0; j < array2.size(); ++j) {
+            if (calculate_distance(array1[i], array2[j]) <= within_distance_meters) {
+                counts[i]++;
+            }
+        }
+    }
+
+    return counts;
+}
+
+PYBIND11_MODULE(calculate_nearby_points, m) {
+    m.doc() = "Calculate number of points within a given distance";
+    m.def("calculate_counts", &calculate_counts, 
+          "Calculates for each point in array1 the count of points in array2 within a specified distance in meters.");
+}

### 2024-05-04 result_tables/summary_statistics.tex
Add files via upload

\begin{tabular}{p{5cm}lllll}
\toprule
Name & Mean without lianjia & SD without lianjia & Mean with lianjia & SD with lianjia & Difference \\
\midrule
The time it takes before a deal is made. & 13.59 & 14.56 & 17.09 & 17.50 & -3.501 (-49.823***) \\
price\_concession & -0.0367 & 0.0318 & -0.0351 & 0.0294 & -0.00200 (-12.088***) \\
percentage of lianjia to all brokerages & 0 & 0 & 0.206 & 0.166 & -0.206 (-384.429***) \\
number of brokerages within 410 meters, which is the cutoff of RD & 5.362 & 6.871 & 12.66 & 8.410 & -7.300 (-217.614***) \\
The number of people watching a listing. & 17.61 & 29.11 & 20.29 & 29.40 & -2.682 (-21.214***) \\
The final agreed price. & 260.5 & 254.9 & 351.9 & 292.1 & -91.48 (-76.662***) \\
without online platformization influence & 0.195 & 0.396 & 0.233 & 0.423 & -0.0380 (-21.384***) \\
The number of times a listing is watched. & 1121 & 1827 & 1233 & 1969 & -112.4 (-13.636***) \\
The number of times a negotiation was held. & 4.769 & 7.686 & 5.683 & 10.78 & -0.914 (-22.178***) \\
The period over which negotiations took place. & 150.5 & 187.5 & 166.6 & 239.1 & -16.06 (-17.075***) \\
Referring to electronic shops. & 1.489 & 3.566 & 1.942 & 4.365 & -0.453 (-26.004***) \\
Referring to proximity to kindergartens & 8.665 & 6.229 & 11.76 & 6.081 & -3.097 (-116.630***) \\
Referring to proximity to hotels & 3.211 & 5.287 & 5.428 & 6.315 & -2.217 (-87.264***) \\
Referring to shopping mall. & 4.554 & 7.539 & 6.698 & 8.489 & -2.144 (-61.405***) \\
Distance to the nearest museum. & 0.617 & 1.533 & 1.023 & 1.869 & -0.406 (-54.395***) \\
Referring to old care systems. & 0.894 & 1.628 & 1.339 & 1.950 & -0.446 (-56.870***) \\
Referring to KTV and some entertainment venues. & 5.179 & 7.853 & 7.305 & 7.759 & -2.126 (-63.096***) \\
Referring to middle schools. & 2.059 & 2.329 & 3.368 & 2.853 & -1.309 (-115.077***) \\
Referring to primary schools. & 2.812 & 2.846 & 4.343 & 3.205 & -1.531 (-116.172***) \\
Referring to the availability of western food nearby. & 3.880 & 7.709 & 7.317 & 10.02 & -3.437 (-87.756***) \\
Referring to proximity to supermarkets (measured by number within given distance & 3.155 & 3.374 & 4.499 & 3.686 & -1.344 (-87.586***) \\
Referring to proximity to subway stations. & 0.683 & 0.945 & 1.111 & 1.099 & -0.429 (-96.038***) \\
Referring to parks. & 3.422 & 4.575 & 4.569 & 3.944 & -1.147 (-62.708***) \\
The area of a property. & 90.82 & 48.57 & 84.97 & 39.15 & 5.845 (31.050***) \\
The number of bedrooms in a property. & 2.338 & 0.816 & 2.202 & 0.730 & 0.136 (40.958***) \\
The number of toilets in a property. & 1.306 & 0.579 & 1.246 & 0.455 & 0.0600 (26.915***) \\
The age of the house. & 18.08 & 11.68 & 20.73 & 11.77 & -2.651 (-52.316***) \\
The level on which a particular room or apartment is, within a building. & 1.854 & 0.975 & 1.933 & 0.931 & -0.0790 (-19.324***) \\
The ratio of the green space to the total plot area. & 0.309 & 0.237 & 0.300 & 0.107 & 0.00900 (12.288***) \\
The total number of buildings in an area. & 26.88 & 56.66 & 20.51 & 50.54 & 6.371 (27.653***) \\
The number of floors in a building. & 12.75 & 8.454 & 12.97 & 8.485 & -0.221 (-6.035***) \\
The number of living rooms in a property. & 1.445 & 0.504 & 1.341 & 0.492 & 0.104 (48.345***) \\
The ratio of elevators to the total number of floors. & 0.453 & 0.413 & 0.408 & 0.279 & 0.0450 (30.475***) \\
The number of kitchens in a property. & 0.983 & 0.150 & 0.983 & 0.125 & 0 (-0.459) \\
The ratio of the floor area to the total plot area. & 4.942 & 329.1 & 2.702 & 9.385 & 2.240 (2.367**) \\
The total number of residents in an area. & 995.8 & 1079 & 901.8 & 956.5 & 93.97 (21.484***) \\
Air quality measure. & 44.08 & 13.29 & 45.74 & 13.89 & -1.664 (-28.266***) \\
Population density. & 15506 & 16336 & 24634 & 18866 & -9100 (-118.769***) \\
Night time lights. & 32.62 & 13.59 & 38.41 & 11.92 & -5.782 (-105.485***) \\
\bottomrule
\end{tabular}

### 2024-05-04 manuscript/main.tex
Add files via upload

\documentclass[12pt]{article}
\usepackage[right=0.7in,left=0.7in,top=1in,bottom=1in]{geometry}
\usepackage{hyperref}
\hypersetup{colorlinks, citecolor=blue, filecolor=blue, linkcolor=blue, urlcolor=blue}
\usepackage{graphicx}
\usepackage{url}
\usepackage[round]{natbib}
\usepackage{amsmath,amsthm}
\usepackage{engord}
\usepackage{float}
\usepackage{subfig}
\usepackage{pdflscape}
\usepackage{booktabs}
\usepackage{pgfplots}
\usepackage{subfig}
\pgfplotsset{compat=1.14}
\usepackage{longtable}
\pgfplotsset{every axis label/.append style={font=\tiny}}
\usepackage[labelsep=period]{caption} %% This switches "Table 1: Title" to "Table 1. Title"
\usepackage{authblk}
\usepackage{amssymb} %% Necessary, just for the \checkmark command  in tables.
\usepackage{multirow} %% Necessary if we are doing tables in LaTeX

\usepackage{xr}

\usepackage{setspace}
\doublespacing

\usepackage{sectsty}
\sectionfont{\large}
\subsectionfont{\normalsize}
\subsubsectionfont{\normalsize}

\newcommand{\specialcell}[2][c]{\begin{tabular}[#1]{@{}l@{}}#2\end{tabular}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{ \vspace*{-2.5cm} \hspace*{-0.5cm}Evaluating the Impact of Offline Store Clusters in the Age of Platforms: Evidence from China's Metropolitan Real Estate Market \footnote{
The preliminary version was entitled "Property brokerage, Partial monopoly and Housing market" and was presented at The 1st Summer Meeting in Urban Economics, China. We are grateful for the comments and suggestions made at the meeting. The code to replicate the paper can be accessed at \href{https://github.com/sergiozxy/RealEstateBrokerage}{https://github.com/sergiozxy/RealEstateBrokerage} The authors gratefully acknowledge financial support from the Fundamental Research Funds for the Central Universities of Sichuan University (2019hhf-08; SKSYL201812; 2018jj-01) and National Natural Science Foundation of China (71773081). We gratefully thank for Hanying Liu from Sichuan University and Chongyu Wang from Florida State University for insightful feedback.
}}

\date{ \vspace*{0.5cm} (Research In Progress)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\author[1]{Guoying Deng}
\author[2]{Xuyuan Zhang \thanks{Email Address: \href{mailto:zxuyuan@umich.edu}{zxuyuan@umich.edu}}}
\affil[1]{Sichuan University}
\affil[2]{University of Michigan, Ann Arbor}

\bgroup
\let\footnoterule\relax

\begin{singlespace}
\maketitle

% Police brutality, law enforcement, and crime: Evidence from Chicago
\begin{abstract}
    \noindent This study examines the impact of offline store expansion by Lianjia, China's leading real estate brokerage, in the context of online platform development. By analyzing micro-level transactions of second homes in ten major Chinese cities from 2016 to 2022, the study explores how the strategic clustering of offline stores enhances Lianjia's influence in local communities and facilitates the creation of an extensive franchise network. This study first conducts a regression discontinuity (RD) design to quantify the optimal influence radius of these stores on housing transactions. By incorporating the optimal influence radius, this study examines the exogenous shock of Lianjia's market entry to identify a significant increase in transaction revenues. However, this effect is diminished during Covid-19 periods. In addition, the paper examines the impact of Lianjia's ACN strategy on its platformization efforts and concludes that the effect is not only from the larger client base brought by the platform, but also from the information control by sharing information within the platform. This study provides valuable insights into the synergy between offline store expansion and online platform development, highlighting their importance in the evolving real estate brokerage market.
  \end{abstract}

  \textbf{Keyword}: Marketing Strategy, Housing Markets, Digital Platforms

  \textbf{JEL} Classification Codes: D4, L1, L8, R3
\end{singlespace}
\thispagestyle{empty}

\clearpage
\egroup
\setcounter{page}{1}

%% Temporary tool to track how this paper is structured. Feel free to comment in or out. 
% \tableofcontents
% \bigskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%\section{Introduction\label{sec:introduction}}

\section{Introduction \label{sec:introduction}}

\noindent

In the real estate market, transaction costs are a critical factor for both buyers and sellers. Minimizing these costs has made the selection of competent real estate agencies a significant priority for both parties. Especially in the context of China's burgeoning real estate market, brokerage firms are assuming an increasingly important role in facilitating the communication channel between buyers and sellers \citep{glaeser_real_2017}. In addition, technological advancements coupled with the proliferation of dominant platforms have created a trend toward greater monopolization within the real estate brokerage industry, rather than fostering a competitive environment. Therefore, it is imperative to analytically examine the expansion strategies of Chinese real estate agencies, especially in the context of escalating platform-based monopolization.

Lianjia is the largest real estate brokerage in China that has platformed real estate transactions by establishing the Beke platform. They can expand rapidly by the expansion of offline stores on a large scale while sharing resources by leveraging the advantages of their platform. Beke has also established an original Agent Cooperate Network (ACN) that integrates and shares the content of its multiple subsidiaries to realize multiple revenue models at the same time.\footnote{The ACN model breaks down the entire process of transaction into parts, each of which is handled by a single person or store, including seller-side: finding sellers, maintaining the listing of the house, commissioning and communicating, and buyer-side: Finding clients, matching homes and clients, facilitating transactions, and providing financial services assistance.} Through the ACN model, Lianjia transforms the internal competition within the system into the overall competitiveness of the system, improving the reputation and influence of the entire brand and gaining a more favorable position in the marketplace. For example, according to the data of AutoNavi Map and CREIS data: In 2020, the number of real estate agent stores in the main urban area of Chengdu City that accessed Beke Housing's platform accounted for about 20\%, but the market share reached 73.98\%.

The reason why Lianjia does not have such a high proportion of offline stores in the market but has an absolute dominant position in metropolis can be explained by the mechanism of China's second-hand real estate market. In the China's real estate market, brokerages still operate on a bilateral agency model, where sellers need to choose the agency that can help them sell their home in the fastest time and for the highest price possible for the transaction. However, due to the asymmetric information characteristics of the real estate market, sellers must find a way to inform buyers and match buyers. In a fully competitive market, sellers would be indifferent in choosing real estate agents.  Nevertheless, as the market trends towards increased monopolization, sellers encounter a dichotomous choice: opt for a larger brokerage firm, which, albeit commanding higher fees, possesses the capacity to expedite housing transactions, or engage with a smaller brokerage, which presents a contrasting scenario of lower fees yet potentially less efficient transaction facilitation.

While it is possible for sellers to adopt a multi-homing strategy, this approach is suboptimal for several reasons. First, the exclusivity of contracts between sellers and agents precludes the adoption of a multi-homing strategy. Second, although sellers can list their houses with multiple brokerages, smaller brokerages often lack a broad enough target client base, which is not very helpful in selling the homes. Third, connecting with multiple brokers simultaneously can make each brokers feel that they are in a difficult position to compete for that house, which reduces their incentive to be proactive in their efforts. Finally, while the variance in service costs between agencies is acknowledged, these costs are trivial compared to the value of the property and are more related to the risk associated with holding a financial asset. Consequently, risk-averse individuals are inclined to choose an agency that provides a guaranteed level of service. Due to the mechanism of online promotion and offline transaction in the real estate brokerage industry, the nature of the brokerage's services in the offline stores is of high value for its influence on the client side. This is the principle behind Lianjia's choice to open stores in the neighborhoods of each target community. By opening a wide range of stores around the communities, the brokerage attracts sellers to list their houses, and attracts buyers in the market through its extensive platform sources, thus obtaining a higher number of transaction and income from the transaction.

In this paper, we empirically test this hypothesis that when brokerages are able to expand their offline stores' coverage in the communities, the brokerages can earn higher income in this community, and we decompose the channels into two parts. On the one hand, is that when brokers have better control over listing information by opening additional offline stores, they are more likely to attract more sellers to choose them, which will then benefited by the online platform effect to extract more buyers and more likely to complete a transaction. On the other hand, when offline stores are closer to the communities, they are more likely to make a house tour to help the buyers to get more information on the house, and therefore, be more likely to complete a transaction. During the Covid-19 pandemic period, the Chinese government restricts the number, and in this period, we find that the number of houses tour is not significantly affected by the number of offline stores, but the listing information significantly decreases because the brokerages are difficult to interact with the sellers and then failure to maintain the information advantage during this period.

Apart from directly measuring the dynamic effect of Lianjia's offline stores to transaction, we use Lianjia's entry into the local segmented market as an exogenous shock to test the effect of entry on transaction characteristics. The results indicate that when Lianjia enters the market, revenues increase significantly, but this is not due to the larger clinic-based, but due to the greater information control brought by the newly opened store. Moreover, during pandemic periods, we find that all effects are diminished, meaning that during pandemic periods, both the client-based effect and the housing information are diminished. Simultaneously, our study also examines the impact of Lianjia's ACN strategy on the real estate market, focusing on its effect on offline store operations. Through this exogenous shock, we find that post-2018, the ACN significantly boosts revenue and alters consumer behaviors, especially in terms of price concessions and house tours. Also, contrary to the previous effect, the effects are diminished during pandemic periods. The findings highlight the resilience of physical stores during a global epidemic and underscore the necessity for a synergistic evolution of online and offline strategies.

The remainder of the paper proceeds as follows. Section \ref{sec:literature_review} reviews the literature that is related to our research. Section \ref{sec:data} describes the data and summarizes the statistical evidence. Section \ref{sec:mechanism_design} presents the main result of our finding. Finally, Section \ref{sec:conclusion} concludes.

\section{Literature Review} \label{sec:literature_review}

\citet{Rosen_hedonic} proposed a hedonic pricing model and explained the price is determined by internal and external factors affecting it. But the hedonic pricing model suffers under conditions of market asymmetry and information inequality. The seminal work on the impact of asymmetric information in markets is \citep{Akerlof_1970}, which demonstrated that markets for used cars tend to be dominated by low-quality goods, or 'lemons,' leading to market inefficiencies.  Furthermore, \citet{grossman_impossibility_1980} further argued that information effective market assumption is hard to hold in reality. Therefore,

In terms of real estate market, several literature has shown that several factors can influence the market pricing and strategies. The \citep{550a6ccf-cde2-3dd1-979f-1a8db2b8ceb9} documents that apart from price competition in the market, there is a lot of market inefficiency that stems from non-price competition, which suggests that as the degree of competition in the market increases, the market becomes progressively less efficient, indicating that the entry dividend begins to fall and aggregate social welfare begins to decline. Moreover, \citet{hendel_relative_2009} analyzes two types of listings in the second-hand housing market and finds that For-Sale-By-Owner type of platforms are less effective in terms of time and probability of sale, while operating better compared to listing homes for sale as a broker. In addition, \citet{bailey_economic_2018} uses data from the social media site Facebook to show that social interactions can influence people's economic decisions. Their results show that people who have friends who are geographically distant in real life and who have a hunch that house prices are about to rise are more likely to buy a house than rent one. Other relevant areas of research include \citep{NIEUWERBURGH_information, salz_intermediation_2022}.

With respect to the behavior of real estate brokerages, the research conducted by \citep{AGARWAL2019715} substantiates that these entities, acting as intermediaries in market transactions, possess superior knowledge of market dynamics. This informational superiority enables the intermediaries to use their bargaining power to secure discounts in the market. Similarly, \citet{HAN2015813} articulates that brokerages operating in unidirectional and bidirectional markets exhibit different levels of bargaining leverage, leading to different motivational drivers. This mechanism is in line with other research, which shows that properties with lower commission rates have a 5\% less likelihood of being sold and takes 12\% longer to sell \citep{10.1257/app.20160214}.

Regarding the impact of online platforms on the real estate sector, research by \citep{ZUMPANO2003134} suggests that while the length of time buyers spend searching for properties remains unchanged, the scope of their search expands to include a greater number of online listings. \citet{ZHANG2021101104} show that the introduction of online platforms is associated with reductions in existing home prices and increased sales volumes, effects that are influenced by new home prices and household size. However, a comprehensive analysis of the influence of the physical stores of online platforms on the real estate market is still lacking in the literature.

Finally, the impact of real estate intermediaries on the market can be decomposed into several aspects. Using a model based on the assumption of a perfectly competitive market in which an influx of brokers competitively enters the market, \citet{williams_agency_1998} shows that the presence of brokers in the market equilibrium exceeds the optimal number of allocations, thereby causing a reduction in social welfare. Moreover, the results show that neither brokers nor sellers are motivated to deviate from the equilibrium price structure, which coincides with the reservation price set by sellers. Complementary research in another study shows that a significant influx of brokers into the market is correlated with a decrease, rather than an increase, in house prices, along with a gradual decrease in transaction cycles within the market \citep{https://doi.org/10.1002/jae.2891}. Furthermore, the work of \citep{qu_identifying_2021-1} highlights the moderating role of broker commissions on the dissemination of market information during transactions. Their findings suggest that the use of a broker can significantly mitigate the concessions that sellers are forced to make in the transaction process, thereby enhancing their ability to complete a home sale more efficiently.

% 由于房地产中介行业线上推广线下成交的机制，中介机构在线下门店中的服务性质对于其在客源方的影响具有很高的价值。链家通常选择在每个目标小区的周边开店便是该原理。链家通过在小区周边大范围开店，从而吸引卖方选择该机构进行挂牌，而又通过其广泛的平台客源来吸引市场中的买方从而获得更多的成交数量与成交收入。由于房地产中介行业线上推广线下成交的机制，中介机构在线下门店中的服务性质对于其在客源方的影响具有很高的价值。链家通常选择在每个目标小区的周边开店便是该原理。链家通过在小区周边大范围开店，从而吸引卖方选择该机构进行挂牌，而又通过其广泛的平台客源来吸引市场中的买方从而获得更多的成交数量与成交收入。

% \section{Theoretical Model}

% There should be a model like: Police brutality, law enforcement, and crime: Evidence from Chicago

\section{Data and Descriptive Evidence \label{sec:data}}

\subsection{Data Collection and Processing}

This study focuses on the housing markets in ten major cities in China, namely Beijing, Shanghai, Chongqing, Tianjin, Shenzhen, Guangzhou, Chengdu, Hangzhou, Wuhan and Nanjing. These cities are not only central to China's economic development, but also reflect the broader trends and characteristics of the country's real estate dynamics. Spanning from 2016 to 2022, the research period encapsulates a pivotal era in China's real estate sector. During the first phase of the study, from 2016 to 2019, the housing markets in these cities experienced a remarkable boom. This period was characterized by significant growth in property prices, supported by robust economic expansion and increased demand in these urban centers. However, the final phase of our study, from 2020 to 2022, paints a contrasting picture. During this period, China's overall economic growth rate has been slower significantly, which has also reflected in a slowdown in the real estate markets of these major cities. In addition, the Chinese government has implemented strict rules in Covid-19 protection, so the real estate agents in these major cities are significantly affected.

The second hand housing transaction data was collected form \href{https://bj.lianjia.com/}{lianjia.com} for ten cities ranging from 2016 to 2022. Initially, we filtered out transaction records exhibiting unusually high prices, identifying them as outliers that could skew the analysis. This was followed by the removal of records with missing values to maintain the integrity of our dataset. Furthermore, we removed all the records that are . We finally have a data with length 1,716,579 second-hand house.\footnote{Due to government restrictions, four of these cities did not list the transaction price for each transaction during the study period.} Since most of lianjia's offline stores are centered around communities, and most of our information is accurate at the community level, and to make our panel compatible, we decided to aggregate the information at the community level. By taking the average of all transaction information, we constructed the panel data with seven years.

To gather more information, we first extracted the POI data from the AutoNavi map using the web-scrawling Python program.\footnote{AutoNavi, a leading mapping application in China with a huge user base of more than 700 million, stands out for its detailed and accurate POI data and precise public transportation information. These features underscore AutoNavi's formidable lead in the digital mapping sector, highlighting its ability to provide unparalleled navigation accuracy and comprehensive urban mobility solutions. Our extracted AutoNavi map contains more than 1 million POIs for each city in each year.} We then classified the extracted POIs into different categories, the specifics of which are discussed in detail in Table \ref{tab:statistical}. This categorization was crucial for understanding the urban infrastructure and amenities available in the vicinity of the analyzed properties. We prioritized POIs within a 500-meter radius-a distance typically covered within a ten-minute walk, consistent with urban planning standards for accessible urban design. This radius was specifically chosen to reflect the immediate urban environment that influences residential desirability and value, as the majority of these POIs provide recreational services. Furthermore, some geo-informational data was also integrated into our research data, which consists of the annual gdp obtained from \citep{zhao_forecasting_2017}, nighttime lights data, obtained from \citep{elvidge_annual_2021} and air pollution data from \citep{doi:10.1021/acs.est.1c05309}. By merging these data with our research panel, we finally get the data.

To We divide our data to those with lianjia and those without lianjia and to check whether lianjia's offline stores have influential effect on the transaction effect in the community. We can see that for income, house tour number and the are all significantly different in those communities with or without lianjia. Furthermore, we find that the those with lianjia have a

\begin{table}[htb!]
    \centering
    \begin{tiny}
    \caption{Statistical Summary}
    \input{../result_tables/summary_statistics.tex}
    \label{tab:statistical}
    \end{tiny}
\end{table}

\subsection{Influential Radius} \label{subsec:Influential_Radius}

The effectiveness of an offline intermediary's influence on its immediate communities is inherently constrained by geographic limitations, with its influence decreasing in proportion to the increase in spatial distance. Moreover, since the offline stores of lianjia are directly operated by the lianjia, strategic considerations regarding the optimal distance between stores are an integral part of their location planning to mitigate the risks associated with over-concentration of stores that could lead to competitive overlap and service homogenization. Consequently, it is imperative to determine an optimal radius threshold and subsequently assess the diversity of agencies operating within this demarcated zone.

To determine the optimal radius of influence, this research employs a regression discontinuity design (RDD) method to examine the influential radius of offline real estate brokerages. The dependent variable in this analysis is the transaction revenue generated by Lianjia within a given community, while the independent variable is the community's proximity to the nearest Lianjia's store. Given that stores are predominantly located within commercial districts-typically encompassing several streets no more than two kilometers in diameter-it is assumed that a requisite number of stores within each district is essential to sustain revenue generation in that community. Building on this premise, the study further investigates the existence of an optimal influence radius within shopping districts, defined as the distance radius within which the presence of a Lianjia optimally increases transaction revenues. At the same time, the study also examines the hypothesis that beyond this optimal radius, the impact on transaction revenues diminishes as a result of the strategic store layout decisions implemented by Lianjia.

\begin{figure}[ht]
    \centering
    \subfloat[RD plot with first order polynomial]{\includegraphics[width=0.5\textwidth]{../figures/RD_Plot_1st_Order.pdf}\label{fig:RD_Plot_1st_Order}}
    \hfill % Adds horizontal space between figures
    \subfloat[RD plot with second order polynomial]{\includegraphics[width=0.5\textwidth]{../figures/RD_Plot_2nd_Order.pdf}\label{fig:RD_Plot_2nd_Order}}
    \hfill % Adds horizontal space between figures
    \subfloat[RD plot with third order polynomial]{\includegraphics[width=0.5\textwidth]{../figures/RD_Plot_3rd_Order.pdf}\label{fig:RD_Plot_3rd_Order}}
    \caption{RD design}
    \label{fig:RD_design}
\end{figure}

From Figure \ref{fig:RD_design} we can see that there is indeed discontinuity in 410 meters of communities to the nearest Lianjia's store. The observed decline in the Lianjia's influence is marked and suggests a pronounced reduction in its impact on the system overall within our study sample. This phenomenon can be attributed to the implementation of the Lianjia's proximity to customers policy, which is evidenced at the data level.

To make the robust check we conducted Donut Hole test by excluding observations close to the cutoff and estimating the effect with the remaining data. The result shows that the discontinuity still exists and this provides evidence against a model misspecification. Furthermore, we carry out the density test by \citep{MCCRARY2008698}. The result shows that the p-value is greater than 0.1, which suggests the result is not due to manipulation of polygons. Finally, we carry out placebo tests which are reported in Appendix, which strengthens the case for a true treatment effect.

\subsection{Stylized Fact}

The dependent variable is \emph{the natural logarithm of lianjia's income}, \emph{the price concession} and \emph{the natural logarithm of home tours} and in order to quantify the effect of lianjia, we first starts with a stylized fact, and try to catch the num. Firstly, we construct a density based index (DBI) to capture the effect of Lianjia's effect and continuous expansion effect. Based on the influential radius test result, it is defined as:

\begin{equation*}
  density_{it} = \frac{lianjia_{it}}{total_{it}},
\end{equation*}

where $lianjia_{it}$ is the number of Lianjia within 410 meters and $total_{it}$ is the total number of brokerages within 410 meters radius. The adoption of this index is based on the understanding that directly using the number of Lianjia's offline stores within a certain radius may suffer from the reverse causality problem. This is primarily because Lianjia, similar to other real estate brokerages, strategically locates its offline stores in locations that have high desirability and consequently high transaction volumes. To mitigate this confounding variable, we propose the use of a comparative metric: the ratio of Lianjia offline stores to the total number of real estate brokerages in the same area. This methodological refinement aims to neutralize the bias introduced by Lianjia's preferred location strategy. Given the lack of barriers to entry in the market, this ratio provides a more nuanced indicator of Lianjia's influence than an absolute number, and this is also in line with the spatial competition model \citep{hotelling_stability_1929, daspremont_hotellings_1979}.

To capture the individual fixed effect and other time-invariant unobservable influential factors, a multi-way fixed effect model is proposed. The model is specified as follows:

\begin{equation}
  Y_{it} = \beta_0 + \beta_1 density_{it} + \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}, \label{eq:multi-way-fe}
\end{equation}

where $Y_{it}$ is the three main dependent variables, including $\log(\text{income})$, price concession, and $\log(\text{number of house tours})$, $density_{it}$ is the DBI, $\bf{X}_{it}$ is a set of control variables, including brokerage\_control L\_hedonic\_control, transaction\_control and region\_control, while $\tau_{it}$ is the time dummy variable interacting with the fixed effect of the business area, $\mu_i$ is the individual fixed effect and $\epsilon_{it}$ is the error term. The standard errors are clustered at the each community level. The results are shown in Table \ref{tab:stylized_fact}.

\begin{table}[htb!]
    \centering
    \begin{scriptsize}
    \input{../result_tables/stylized_fact}
    \caption{The DBI influence to the lianjia's transaction}

    Note: we omit all the control variables in the regression model, and detailed descriptions can be seen from Table \ref{tab:statistical}
    \label{tab:stylized_fact}
    \end{scriptsize}
\end{table}

The results show that the share of Linajia's offline stores in total brokerage plays a significant role in the real estate market, especially in terms of revenue and lead time, but not in terms of price concessions. Specifically, a 1\% increase in a Lianjia's DBI within an area correlates with a 7\% increase in income, as indicated in the log(income) column. Furthermore, this increased DBI also leads to a 4\% increase in the number of home tours in the log(lead times) column, underscoring the Lianjia's increased visibility and potential for customer engagement. In contrast, the analysis shows no significant effect of DBI on price concessions. This finding suggests that while a larger market share increases revenues and the number of house tours, it does not exert pressure to reduce prices through concessions. The broader implications point to the strategic advantage of density or market share in driving business performance metrics, except for pricing strategies, which appear to be unaffected by changes in market share.

Within the temporal scope of our investigation, the dataset encapsulates two distinct epochs: a phase characterized by surging housing prices and the subsequent period marked by the COVID-19 pandemic. These intervals were further complicated by regulatory measures enacted by the Chinese government, significantly altering the operational dynamics and influence of brokerages within the housing market. Acknowledging these temporal shifts necessitates a nuanced analysis of the brokerage effect across different stages of the study period to ensure the robustness of our findings. To address this, we adopt a dynamic analytical approach, dissecting the period into annual segments. This granularity is achieved by constructing seven unique variables, each representing the interaction between brokerage density and the respective $density_{it} * year_{it}$. Our methodology employs a multi-way fixed effects model, as detailed in Equation \eqref{eq:dynamic}, which facilitates a comprehensive examination of temporal variations in the brokerage's market impact.

In the construction of our regression model, we deliberately omit the first period to avoid multicollinearity problem, treating it as a baseline for comparison. This strategic choice allows us to refine our proxy variable—the product of Lianjia's Dealership Balance Index (DBI) and annual dummies—as a more precise measure of Lianjia's local market power. Besides, to control for potential self correlation problem, we also included lagged one period dependent variables in the model.  Other settings are the same with the previous model \eqref{eq:multi-way-fe} and the result is reported in Table \ref{tab:Dynamic}:

\begin{equation}
    Y_{it} = \beta_0 + \rho Y_{it-1} + \sum_{i=2}^7 density_{it} * year_{it} + \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}. \label{eq:dynamic}
\end{equation}

\begin{table}[H]
  \begin{center}
    \begin{scriptsize}
    \caption{Dynamic Regression Results}
    \label{tab:Dynamic}
    \input{../result_tables/dynamic.tex}

    Note: we omit all the control variables in the regression model, and detailed descriptions can be seen from Table \ref{tab:statistical}
    \end{scriptsize}
  \end{center}
\end{table}

The result highlights the dynamic impact of density, encapsulated by Lianjia's DBI, on transaction revenue, home visits, and price concessions over time, especially in response to external factors such as digital transformation and the COVID-19 pandemic. Initially, Lianjia's impact on transaction revenue showed a significant positive trend, peaking in 2018, due to its digital transformation efforts, including the integration of other platform stores into its shared network.  However, the momentum slowed in 2020 and 2021, with the impact becoming significantly negative. This period coincided with the outbreak of the COVID-19 pandemic, which severely disrupted Lianjia's revenue streams and business activities due to widespread restrictions, underscoring the vulnerability of real estate transactions to macroeconomic shocks. In terms of home tours, Lianjia's impact remained robustly positive through 2019. This suggests that a strong market presence correlates with increased buyer attention, which translates into more home tours. However, pandemic-related restrictions dampened this effect in later years, highlighting the challenges posed by external constraints on physical real estate activity. For price concessions, we find that the Lianjia's DBI is significantly negatively correlated with the price concessions during pandemic periods. This is due to the fact that most transactions slow down during these periods and people are more likely to wait longer to find a buyer, which would result in fewer price concessions.

% we can not say that it is a martingale process because the housing market is assymetric information and martingale process is a fair game.

\section{Mechanism Design} \label{sec:mechanism_design}

\subsection{Does Lianjia's Entry influence the segmented market?}

In the preceding section, our research has been directed toward evaluating the dynamic effect of Lianjia's offline stores operation. However, there is an imperative to conduct a more detailed analysis of the impact of Lianjia's entry on regional transaction properties. The core of this necessary analysis derives from the premise that the entry of a Lianjia represents an exogenous shock within the respective local segmented market, thus providing a unique opportunity to study the effect of offline expansion on local real estate market. To facilitate such an analysis, we have constructed a series of dummy variables associated with the presence of the Lianjia within the marketplace, delineated as $pre_2$, $pre_1$ (before entry), $entry$, $post_1$, $post_2$, and $post_3$ (successive post-entry intervals), which encapsulate the respective temporal epochs relative to the Lianjia's entry. These binary indicators serve as central regressors within a structured econometric model with $pre_1$ as the control group, described in Equation \eqref{eq:entry_effect}:

\begin{equation}
    Y_{it} = \rho Y_{it-1} + \beta_0 +  pre_2 + entry + \sum_{i=1}^3 post_i + \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}.   \label{eq:entry_effect}
\end{equation}

$pre_2, entry, post_i$ are correspondingly periods dummy variables and other settings are the same with Equation \eqref{eq:dynamic}. The results are reported in Table \ref{tab:entry_effect}.

\begin{table}[htb!]
  \begin{center}
    \begin{scriptsize}
    \caption{Entry Effect}
    \label{tab:entry_effect}
    \input{../result_tables/entry_effect.tex}

    Note: we omit all the control variables in the regression model, and detailed descriptions can be seen from Table \ref{tab:statistical}
    \end{scriptsize}
  \end{center}
\end{table}

The result presented in the table \ref{tab:entry_effect} examines the effect of a Lianjia's entry into an area on various outcomes. Prior to the Lianjia's entry ($pre_2$), there is no statistically significant effect on any of the three outcomes, suggesting that anticipation of the Lianjia's entry does not affect these metrics. In addition, there is a significant 4\% increase in revenue after the Lianjia's entry ($entry$), suggesting a substantial increase in Lianjia sales. However, the effect on price concessions and number of showings remains statistically insignificant, suggesting that Lianjia's entry does not lead to significant changes in pricing strategies or the number of showings brought to the area.

In the post-entry periods ($post_1$, $post_2$, and $post_3$), the results vary. The first period after entry ($post_1$) shows no significant changes in any of the results. However, after two post-entry periods ($post_2$ and $post_3$), there are significant negative effects on both revenue and number of home visits. These declines suggest a decline in the performance and engagement of the Lianjia, possibly due to the impact of an epidemic that led to a decrease in revenue and showing

In summary, the entry of a Lianjia into an area significantly boosts its sales initially, without altering its pricing strategies or viewer engagement significantly. However, the positive impact is short-lived, turning negative in subsequent periods, likely exacerbated by external factors like an epidemic.

\subsection{Is Lianjia's ACN strategy profitable?}

In addition to the entry effect of Lianjia, there is another exogenous shock during our study period. During our study period, Lianjia came up with the ACN strategy. ACN means to subdivide the whole process of buying and selling a house into different parts, and each part is taken charge of by a person or a store. For this purpose, Lianjia first absorbed some of its competitors in the previous market into its platform network and started to cooperate with them. In addition to this, Lianjia also opened up the form of franchises and gradually started platform integration. To empirically measure the effect of platformization to the offline stores' operations, we first counted the number of all non-Lianjia stores on the Lianjia's Beke platform within a radius of 410 meters, which allowed us to generate a dummy variable $Treatment_{it}$ to represent whether or not there are any other affiliate stores within the platform in this neighborhood. To dynamically capture the varying effects, we generate $Treatmetn_{it} * year$ by producting the year dummy variable with the $Treatment_{it}$ and include them in our regression model. Since the ACN network was officially established at the end of 2018, we can generate a dummy variable equal to 1 if the year is greater than 2018. We then consider the following regression model:

\begin{equation}
    Y_{it}  = \beta_0 + \sum_{i=-2}^3 Treatment_{it} * year + \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}. \label{eq:acn_assessment}
\end{equation}

We treat the 2016's sample as the base year, and other settings are consistent with previous table \ref{tab:Dynamic}. The result is reported in Figure \ref{fig:dynamic_effect}

\begin{figure}[ht]
    \centering
    \subfloat[Effect to income]{\includegraphics[width=0.5\textwidth]{../figures/did_1.pdf}\label{fig:did_income}}
    \hfill % Adds horizontal space between figures
    \subfloat[Effect to price concession]{\includegraphics[width=0.5\textwidth]{../figures/did_2.pdf}\label{fig:did_price_concession}}
    \hfill % Adds horizontal space between figures
    \subfloat[Effect to number of house tours]{\includegraphics[width=0.5\textwidth]{../figures/did_3.pdf}\label{fig:did_lead_times}}
    \caption{Estimation of ACN Platformization Effect}
    \label{fig:dynamic_effect}
\end{figure}

The empirical findings elucidate that prior to the establishment of the ACN, there is an absence of discernible effects attributable to anticipation. Subsequent results for the fiscal year 2018 reveal that the ACN exerts a considerable influence on revenue generation, yet it manifests no significant impact on the metrics of price concessions and the number of house tours. This phenomenon indicates that the efficacy of the ACN model does not derive from an augmentation in client base through absorption but rather through the synthesis and integration of comprehensive data on the supply side. Post-2018 observations indicate the maturation of the platformization process, evidencing its expanding influence from the supply to the demand sector. Notably, a marked negative effect on price concessions is observed, underscoring the ACN's significant role in influencing consumer decision-making processes.

However, the years 2021 and 2022 witnessed a mitigated advantage of these factors due to the global epidemic, underscoring an imperative insight; despite the foundational establishment of online platformization, the inherent benefits of physical storefronts remain irreplaceable. This realization requires a re-evaluation of economic models, advocating a harmonious co-evolution of online and offline market paradigms. This strategic integration aims to leverage the unique strengths of each model to foster a more resilient and adaptive economic ecosystem.

\section{Conclusion and Discussion} \label{sec:conclusion}

The study of Lianjia's strategic expansion into China's real estate brokerage industry, particularly through the implementation of the ACN and the proliferation of offline branches, underscores a transformative impact on market dynamics and transaction efficiency. Our empirical research shows that Lianjia's approach, which seamlessly integrates online platforms with an extensive offline presence, significantly enhances revenue generation and influences consumer behavior, particularly through improved price concessions and increased home viewing. The study highlights the critical role of offline store information and community proximity in increasing transaction revenue and achieving market dominance, even in the face of increasing monopolization trends. Despite the adverse effects of the COVID-19 pandemic, which temporarily diluted the benefits of both customer base expansion and information dissemination, the resilience of physical stores emerges prominently. This resilience, coupled with the strategic leverage of online platforms, underscores the importance of a synergistic online-offline model in overcoming market challenges and maintaining competitive advantage. The findings argue for a nuanced understanding of platform-based monopolization in real estate, suggesting that the successful integration of digital and physical domains can significantly enhance service delivery, market penetration, and overall system competitiveness, paving the way for a more adaptive and robust market system in the face of evolving challenges.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\begin{singlespace}
%\bibliographystyle{plainnat}
%\bibliographystyle{chicago}
\bibliographystyle{aer}
\bibliography{our-cites.bib}
\end{singlespace}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% These commands start the appendix and change the Table & Figure numbering
\newpage
\appendix
\setcounter{table}{0}
\renewcommand{\tablename}{Appendix Table}
\renewcommand{\figurename}{Appendix Figure}
\renewcommand{\thetable}{A\arabic{table}}
\setcounter{figure}{0}
\renewcommand{\thefigure}{A\arabic{figure}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Appendix Tables and Figures}
% \input{tab_tex/other-regressions.tex}

\end{document}

\subsection{Robustness Check} \label{subsec:robustness_check}

\begin{table}[H]
  \begin{center}
    \begin{scriptsize}
    \caption{Robustness Check Using HHI Index}
    \label{tab:sylized_fact}
    \input{../result_tables/robust_hhi.tex}

    \end{scriptsize}
  \end{center}
\end{table}

\begin{table}[H]
  \begin{center}
    \begin{scriptsize}
    \caption{Robustness Check}
    \label{tab:sylized_fact}
    \input{../result_tables/robust_mature.tex}

    \end{scriptsize}
  \end{center}
\end{table}

\newpage 
\section{Appendix One \label{sec:appendix:first}}
\renewcommand{\thetable}{B\arabic{table}}
\setcounter{table}{0}
\renewcommand{\thefigure}{B\arabic{figure}}
\setcounter{figure}{0}

% \input{fig_tex/fig_another_figure.tex}

\newpage
\section{Appendix Two
\label{sec:appendix:two}}
\renewcommand{\thetable}{C\arabic{table}}
\setcounter{table}{0}
\renewcommand{\thefigure}{C\arabic{figure}}
\setcounter{figure}{0}

When it comes to the estimation of the entry effect and its continuous effect, we use the following model:

\begin{equation}
  \begin{aligned}
    Y_{it} & = \beta_0 + \beta_1 Pre_3 + \beta_2 Pre_2 + \beta_3 Entry \\
    & + \beta_4 Post_1 + \beta_5 Post_2 + \beta_6 Post_3  + \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}.
  \end{aligned}
\end{equation}

where $Pre$ is the pre-period of lianjia's entry, $Entry$ is the entry period, and $Post$ is the post-period of lianjia's entry. All other model settings are the same as the previous model.

Finally, we construct a proxy variable to capture the continuous effect of the DBI. The model is as follows:

\begin{equation}
  \begin{aligned}
    Y_{it} & = \beta_0 + \beta_1 proxy\_entry + \beta_2 proxy\_pos\_1 \\
    & + \beta_3 proxy\_pos\_2 + \beta_4 proxy\_pos\_3 + \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}.
  \end{aligned}
\end{equation}

where $proxy\_entry$ is the product of the entry effect and the DBI, and $proxy\_pos\_i$ is the product of the post-period effect and the DBI. All other model settings are the same as the previous model. The results are shown in Appendix Table \ref{tab:Baseline} and Appendix Table \ref{tab:Dynamic}.

However, our estimates may not be asymptotically efficient due to the endogeneity of DBI and serial correlation issues. First, DBI is endogenous because the entry of lianjia is endogenous. This is due to the fact that lianjia will choose better locations with higher potential revenues in order to maximize profits. Second, the model suffers from serial correlation because our sample is during the boom period of China's real estate market, and as the number of transactions in the real estate market increases, so do the revenues and prices in the brokerage industry. In addition, lianjia tend to be concentrated in popular areas, which makes for greater growth and thus confounds our estimates. To solve this problem, we use a dynamic panel model for estimation. Dynamic panel models can capture the dynamics of the process by using the lagged dependent variable as a regression variable. This helps in understanding how the past values of the variables affect their current values.

To estimate the dynamic panel model, we use the Arellano-Bond (1991) GMM estimator, which is a two-step estimator. The first step is to use the lagged dependent variable as an instrument for the current dependent variable, and the second step is to use the lagged residuals as an instrument for the current dependent variable. In this paper, we do not use system GMM estimator because the system GMM must assume that the lagged explanatory variables are independent of factors that do not vary over time in the region, and this clearly cannot hold in the present setting. The model is as follows: [\textbf{this should be a line that describes what measures that we use to construct the model}]

\begin{equation}
  \begin{aligned}
    \Delta Y_{it} & = \rho \Delta Y_{it-1} + \beta_1 \Delta Measure_{it} + \bf{\alpha} \Delta \bf{X}_{it} + \Delta \tau_{it} + \Delta \epsilon_{it}.
  \end{aligned}
\end{equation}

where $\Delta Y_{it}$ is the first difference of the dependent variable, $\Delta Measure_{it}$ is the first difference of the our three measurement methods, $\Delta \bf{X}_{it}$ is the first difference of the control variables, $\Delta \tau_{it}$ is the first difference of the time dummy variable interacting with the fixed effect of the business area, and $\Delta \epsilon_{it}$ is the first difference of the error term. The standard errors are clustered at the individual level. The results are shown in Appendix Table \ref{tab:GMM}.

For Table \ref{tab:Baseline}, the result reveals a significant correlation between the lianjia's local market power and lianjia's income in this given community. However, we discovered no substantial influence of lianjia's local market power on the housing prices or transaction periods in the same community. This could be interpreted to mean that whilst Lianjia's local market power could induce an increase in income, it does not necessarily grant them any significant pricing power nor expedite the transaction period. Therefore, we may deduce that the augmentation of Lianjia's income is primarily driven by an increase in the number of transactions, presumably due to more property listings by Lianjia within the community. This suggests that although lianjia can control more market share in the local market, it does not necessarily mean that it can have monopoly power in this given region. This is partially because the price of the house is determined by the market, and there are also some potential other brokerages that can enter the market. However, lianjia's local market power can still have a significant influence on the income because they can list more housings and have more transactions in the local market.

To further test the results, we first check if lianjia's entry effect and continuous effect is significant. For column 1, 3, and 5 of the Table \ref{tab:Dynamic}, the result reveals that before the lianjia's entry, the natural logarithm of income, housing price and transaction period are not significant. After the entry, we see that after lianjia's entry into this local market, lianjia can immediately increase their income and keep making significantly more income comparing with previous periods. Besides, we see that the entry do not significantly increase the housing price immediately but significantly increase housing price one year after but later on turning back to the normal pricing. Lastly, the lianjia's entry do not significantly lowers the transaction periods. This is consistent with our previous results that lianjia's entry can significantly increase the income but not the housing price and transaction periods in equilibrium.

Lastly, we use the third measurement to test after the lianjia's entry, the continuous effect of lianjia's local power of the local market. For column 2, 4, and 6 of the Table \ref{tab:Dynamic}, the result reveals that the continuous effect of lianjia's local power of the local market is significant for the income, housing price and transaction periods. This result indicates that in different period, the lianjia's local market power can have different influence on the market.

### 2024-05-04 analysis/RD design for density.Rmd
Add files via upload

--- 2024-01-05 analysis/RD design analysis.Rmd
@@
 ```{r}
-result <- rdrobust(y = panel_data$ln_income, x = panel_data$nearest_store_distances, 
-                   c = 0.41, covs = panel_data[, control_variables],
+result <- rdrobust(y = panel_data$ln_income, x = panel_data$density, 
+                   c = 0.2,
                    p = 1) # first using default clustering
@@
 ```{r}
-result <- rdrobust(y = panel_data$ln_income, x = panel_data$nearest_store_distances, 
+result <- rdrobust(y = panel_data$ln_income, x = panel_data$density, 
                    c = 0.41,
@@
 h = 0.095
-cutoff = 0.41
-running_var = panel_data$nearest_store_distances
+cutoff = 0.5
+running_var = panel_data$density
 
@@
 rdplot(y = filtered_data$ln_income, 
-       x = filtered_data$nearest_store_distances, 
+       x = filtered_data$density, 
        c = cutoff, nbins = 40, p = 1,
@@
 rdplot(y = filtered_data$ln_income, 
-       x = filtered_data$nearest_store_distances, 
+       x = filtered_data$density, 
        c = cutoff, nbins = 40, p = 2,
@@
 rdplot(y = filtered_data$ln_income, 
-       x = filtered_data$nearest_store_distances, 
+       x = filtered_data$density, 
        c = cutoff, nbins = 40, p = 3,

### 2024-05-05 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	new file:   plotting/same_distribution.ipynb

@@
 
-\date{ \vspace*{0.5cm} (Research In Progress)}
+\date{ \vspace*{0.5cm} \today}
 
@@
     \noindent This study examines the impact of offline store expansion by Lianjia, China's leading real estate brokerage, in the context of online platform development.
-By analyzing micro-level transactions of second homes in ten major Chinese cities from 2016 to 2022, the study explores how the strategic clustering of offline stores enhances Lianjia's influence in local communities and facilitates the creation of an extensive franchise network.
+By analyzing micro-level transactions of second-hand houses in ten major Chinese cities from 2016 to 2022, the study explores how the strategic clustering of offline stores enhances Lianjia's influence in local communities and facilitates the creation of an extensive franchise network.
 This study first conducts a regression discontinuity (RD) design to quantify the optimal influence radius of these stores on housing transactions.
@@
 
-In the real estate market, transaction costs are a critical factor for both buyers and sellers.
+In the real estate market, transaction cost is a critical factor for both buyers and sellers.
 Minimizing these costs has made the selection of competent real estate agencies a significant priority for both parties.
@@
 Furthermore, \citet{grossman_impossibility_1980} further argued that information effective market assumption is hard to hold in reality.
-Therefore,
+Therefore, the real estate market, which is characterized by information asymmetry, is particularly vulnerable to the adverse selection problem.
+In this context, the role of real estate brokerages is crucial, as they act as intermediaries between buyers and sellers, providing valuable information and facilitating transactions.
 
@@
 
-% \section{Theoretical Model}
+\section{Theoretical Model}
+
+To characterize the real estate brokerage market, we can assume that there are two types of brokerages in the market, where the type $1$ denote the large real estate brokerage that is incorporating the online platform and the offline stores strategies, and the type $2$ denote the small real estate brokerage that only have the offline stores and they should compete with the type $1$ stores and type $2$ stores in the market.
+
+We can assume that there are $N$ number of communities in the market, and each market has $\kappa_i, i \in \{1, \ldots, N\}$ number of houses listed.
+The houses listed follows a AR(1) model specified by:
+
+\begin{equation}
+  \kappa_{i, t} = \rho_{i} \kappa_{i-1, t} + \epsilon_{i, t}, \label{eq:ar1}
+\end{equation}
+
+where $\rho_i$ is the parameter and $\varepsilon_{i, t} \sim \mathcal{N}(0, \sigma_{i, t}^2)$.
+We can assume that the price of the house is determined by the hedonic pricing model, and without loss of generality, the price follows a standard uniform distribution, $P_i \sim Uniform[0, 1]$.
+
+The number of two types of brokerages are characterized by $B_{1, i}$ and $B_{2, i}$, respectively.
+The brokerages have the same positive cost function denoted as $C(\cdot)$ where $\frac{\partial C(\cdot)}{\partial B_{1, t}} > 0$ and $\frac{\partial C^2(\cdot)}{\partial B_{1, t}^2} > 0$.
+The intuition is that because of the marginal cost of the platform is $0$, when considering the cost of opening additional stores in the market, the brokerage does not incur that cost into consideration and therefore, the cost function is equal for both types of stores.
+Moreover, the marginal cost of opening additional stores is increasing, which is consistent with the real estate brokerage market.
+
+There are $L$ number of customers that arrive in the market at random poission rate $\lambda$ and for current issue, we can first assume that the customers are indifferent when selecting the brokerages and we can release this assumption later to make the customers have private preference towards each type of brokerages.
+The probability of selecting the brokerage $i$ is given by:
+
+\begin{equation}
+  p_i = \frac{B_{i, t}}{B_{1, t} + B_{2, t}}. \label{eq:prob}
+\end{equation}
+
+The profit of the brokerage in the community is given by $\pi_1(p_1, p_2) = $
+
+give me a mathematical economics model characterizing the partial equilibrium of real estate broekrage and the competitive market where there are two types of brokerages denoted 1 if the brokerage is the large brokerage that it can communicate with other stores in different regions of the same type 1 brokerage, and denote 2 if it is small brokerage that it can not communicate with the other brokerages in the market
+
+In the later, we can also assume that people have private information or preference towards different brokerages so that there will be another proposition demonstrated about the model.
+
+We can examine the following two effects:
+
+\begin{itemize}
+  \item The real estate brokerage's network effect where the brokerages are more likely to form a edge between each other (this is demonstrated in the ACN's brokerage network model)
+  \item The partial effect of the network effect is not characterized by the price level changes or the brokerage fee increase.
+  \item The network effect should be demonstrated by the increase in the number of transactions and the number of the stores within given radius comparing with the total number of houses in this market.
+\end{itemize}
 
@@
 Initially, we filtered out transaction records exhibiting unusually high prices, identifying them as outliers that could skew the analysis.
-This was followed by the removal of records with missing values to maintain the integrity of our dataset.
-Furthermore, we removed all the records that are .
-We finally have a data with length 1,716,579 second-hand house.\footnote{Due to government restrictions, four of these cities did not list the transaction price for each transaction during the study period.} Since most of lianjia's offline stores are centered around communities, and most of our information is accurate at the community level, and to make our panel compatible, we decided to aggregate the information at the community level.
+We then removed records with missing values to maintain the integrity of our dataset.
+We also removed any records that were listed duplicated.
+We finally have a data with length 1,716,579 second-hand house.\footnote{Due to government restrictions, four of these cities did not list the transaction price for each transaction during the study period.} Since most of the offline stores in lianjia are community-based, and most of the information is accurate at the community level, we decided to aggregate the information at the community level to make our panel compatible.
 By taking the average of all transaction information, we constructed the panel data with seven years.
 
-To gather more information, we first extracted the POI data from the AutoNavi map using the web-scrawling Python program.\footnote{AutoNavi, a leading mapping application in China with a huge user base of more than 700 million, stands out for its detailed and accurate POI data and precise public transportation information.
+To gather other characteristics information, we first extracted the POI data from the AutoNavi map using the web-scrawling Python program.\footnote{AutoNavi, a leading mapping application in China with a huge user base of more than 700 million, stands out for its detailed and accurate POI data and precise public transportation information.
 These features underscore AutoNavi's formidable lead in the digital mapping sector, highlighting its ability to provide unparalleled navigation accuracy and comprehensive urban mobility solutions.
@@
 
-To We divide our data to those with lianjia and those without lianjia and to check whether lianjia's offline stores have influential effect on the transaction effect in the community.
+To check the robustness of the data, we divide our data to those with lianjia and those without lianjia and to check whether lianjia's offline stores have influential effect on the transaction effect in the community.
 We can see that for income, house tour number and the are all significantly different in those communities with or without lianjia.
-Furthermore, we find that the those with lianjia have a
+Furthermore, we find that the other brokerages are also have the same tendency that they typically
+
+This figure is shown in Figure \ref{fig:same_distribution}
 

### 2024-05-05 manuscript/main.tex
new file:   figures/scatter_plot_with_two_brokerages.pdf 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	modified:   plotting/same_distribution.ipynb
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

@@
 To characterize the real estate brokerage market, we can assume that there are two types of brokerages in the market, where the type $1$ denote the large real estate brokerage that is incorporating the online platform and the offline stores strategies, and the type $2$ denote the small real estate brokerage that only have the offline stores and they should compete with the type $1$ stores and type $2$ stores in the market.
+Each type of brokerage follows a standard percentage charge by $r_j$ and they can not manipulate the percentage charge in each submarket.
 
-We can assume that there are $N$ number of communities in the market, and each market has $\kappa_i, i \in \{1, \ldots, N\}$ number of houses listed.
-The houses listed follows a AR(1) model specified by:
+We can assume that there are $M$ number of communities in the market, and each market has $\kappa_i, i \in \{1, \ldots, M\}$ number of houses listed which depends on the previous listing number and we can formulate it as a AR(1) model specified by:
 
@@
 \begin{equation}
-  p_i = \frac{B_{i, t}}{B_{1, t} + B_{2, t}}. \label{eq:prob}
+  p_i = \frac{B_{i, t} \times N^e(B_{1, i})}{B_{1, t} \times N^e(B_{1, i}) + B_{2, t}}. \label{eq:prob}
 \end{equation}
 
-The profit of the brokerage in the community is given by $\pi_1(p_1, p_2) = $
+where $N^e(B_{1, i})$ is a function representing the network effects, and is modeled as $N^e(B_{1, i}) = 1 + \alpha \log(1 + B_{1, i})$ where $\alpha$ is a parameter that quantifies the strength of network effects and the logarithmic form captures diminishing returns to scale as the number of brokerages increases.
+The revenue for each brokerage type $j$ in community $i$ is proportional to the number of houses they sell, which depends on the number of customers they attract:
+
+\begin{equation}
+  R_{i, j, t} = r_j \cdot P_i \cdot N_{i, j, t}
+\end{equation}
+
+where $N_{i, j, t}$ is the number of customers selecting type $j$ brokerage in community $i$ at time period $t$, estimated by:
+
+\begin{equation}
+  N_{i, j, t} = \lambda_i p_{i, j, t}
+\end{equation}
+
+and $\lambda_i$ is the appropriate part of $\lambda$ that arrives in community $i$.
 
 give me a mathematical economics model characterizing the partial equilibrium of real estate broekrage and the competitive market where there are two types of brokerages denoted 1 if the brokerage is the large brokerage that it can communicate with other stores in different regions of the same type 1 brokerage, and denote 2 if it is small brokerage that it can not communicate with the other brokerages in the market
+
+The first proposition is that the charging fee should be higher comparing with type $2$ brokerage.
+
+The second proposition is that the number of stores in high popular regions should be higher in the number of stores and they are more likely to form a network effect.
+
+The third proposition is the introduction of the platform should increase the number of transactions and the number of stores in the market.
+
+The fourth proposition is that the entry of the large brokerage can increase the transaction number and the number of stores in the market.
 
@@
 We can see that for income, house tour number and the are all significantly different in those communities with or without lianjia.
-Furthermore, we find that the other brokerages are also have the same tendency that they typically
-
-This figure is shown in Figure \ref{fig:same_distribution}
+Furthermore, we find that the other brokerages are also have the same tendency that they typically open stores with the same strategy as lianjia, which is consistent with our Theoretical Model's Proposition [xxxxx].
+This figure is shown in Figure \ref{fig:same_distribution}.
 
@@
 \end{table}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.7\textwidth]{../figures/scatter_plot_with_two_brokerages.pdf}
+    \caption{Tendency between two types of brokerages}
+    \label{fig:same_distribution}
+\end{figure}
 

### 2024-05-06 manuscript/main.tex
modified:   manuscript/main.tex

@@
 
+\section{Data and Descriptive Evidence \label{sec:data}}
+
+\subsection{Data Collection and Processing}
+
+This study focuses on the housing markets in ten major cities in China, namely Beijing, Shanghai, Chongqing, Tianjin, Shenzhen, Guangzhou, Chengdu, Hangzhou, Wuhan and Nanjing.
+These cities are not only central to China's economic development, but also reflect the broader trends and characteristics of the country's real estate dynamics.
+Spanning from 2016 to 2022, the research period encapsulates a pivotal era in China's real estate sector.
+During the first phase of the study, from 2016 to 2019, the housing markets in these cities experienced a remarkable boom.
+This period was characterized by significant growth in property prices, supported by robust economic expansion and increased demand in these urban centers.
+However, the final phase of our study, from 2020 to 2022, paints a contrasting picture.
+During this period, China's overall economic growth rate has been slower significantly, which has also reflected in a slowdown in the real estate markets of these major cities.
+In addition, the Chinese government has implemented strict rules in Covid-19 protection, so the real estate agents in these major cities are significantly affected.
+
+The second hand housing transaction data was collected form \href{https://bj.lianjia.com/}{lianjia.com} for ten cities ranging from 2016 to 2022.
+Initially, we filtered out transaction records exhibiting unusually high prices, identifying them as outliers that could skew the analysis.
+We then removed records with missing values to maintain the integrity of our dataset.
+We also removed any records that were listed duplicated.
+We finally have a data with length 1,716,579 second-hand house.\footnote{Due to government restrictions, four of these cities did not list the transaction price for each transaction during the study period.} Since most of the offline stores in lianjia are community-based, and most of the information is accurate at the community level, we decided to aggregate the information at the community level to make our panel compatible.
+By taking the average of all transaction information, we constructed the panel data with seven years.
+
+To gather other characteristics information, we first extracted the POI data from the AutoNavi map using the web-scrawling Python program.\footnote{AutoNavi, a leading mapping application in China with a huge user base of more than 700 million, stands out for its detailed and accurate POI data and precise public transportation information.
+These features underscore AutoNavi's formidable lead in the digital mapping sector, highlighting its ability to provide unparalleled navigation accuracy and comprehensive urban mobility solutions.
+Our extracted AutoNavi map contains more than 1 million POIs for each city in each year.} We then classified the extracted POIs into different categories, the specifics of which are discussed in detail in Table \ref{tab:statistical}.
+This categorization was crucial for understanding the urban infrastructure and amenities available in the vicinity of the analyzed properties.
+We prioritized POIs within a 500-meter radius-a distance typically covered within a ten-minute walk, consistent with urban planning standards for accessible urban design.
+This radius was specifically chosen to reflect the immediate urban environment that influences residential desirability and value, as the majority of these POIs provide recreational services.
+Furthermore, some geo-informational data was also integrated into our research data, which consists of the annual gdp obtained from \citep{zhao_forecasting_2017}, nighttime lights data, obtained from \citep{elvidge_annual_2021} and air pollution data from \citep{doi:10.1021/acs.est.1c05309}.
+By merging these data with our research panel, we finally get the data.
+
+\subsection{Influential Radius} \label{subsec:Influential_Radius}
+
+The effectiveness of an offline intermediary's influence on its immediate communities is inherently constrained by geographic limitations, with its influence decreasing in proportion to the increase in spatial distance.
+Moreover, since the offline stores of lianjia are directly operated by the company, strategic considerations regarding the optimal distance between stores are an integral part of their location planning to mitigate the risks associated with over-concentration of stores that could lead to competitive overlap and service homogenization.
+Consequently, it is imperative to determine an optimal radius threshold and subsequently assess the diversity of agencies operating within this demarcated zone.
+
+To determine the optimal radius of influence, this research employs a regression discontinuity design (RDD) method to examine the influential radius of offline real estate brokerages.
+The dependent variable in this analysis is the transaction revenue generated by Lianjia within a given community, while the independent variable is the community's proximity to the nearest Lianjia's store.
+Given that stores are predominantly located within commercial districts-typically encompassing several streets no more than two kilometers in diameter-it is assumed that a requisite number of stores within each district is essential to sustain revenue generation in that community.
+In addition, since the Lianjia's company adopts a 5-minute walking distance (approximately 400 meters) radius policy, which means that no matter how far away customers live, they should be accessible within a 5-minute walk to the nearest Lianjia's store.
+Building on this premise, the study further investigates the existence of an optimal influence radius within shopping districts, defined as the distance radius within which the presence of a Lianjia optimally increases transaction revenues.
+At the same time, the study also examines the hypothesis that beyond this optimal radius, the impact on transaction revenues diminishes as a result of the strategic store layout decisions implemented by Lianjia.
+
+\begin{figure}[ht]
+    \centering
+    \subfloat[RD plot with first order polynomial]{\includegraphics[width=0.5\textwidth]{../figures/RD_Plot_1st_Order.pdf}\label{fig:RD_Plot_1st_Order}}
+    \hfill % Adds horizontal space between figures
+    \subfloat[RD plot with second order polynomial]{\includegraphics[width=0.5\textwidth]{../figures/RD_Plot_2nd_Order.pdf}\label{fig:RD_Plot_2nd_Order}}
+    \hfill % Adds horizontal space between figures
+    \subfloat[RD plot with third order polynomial]{\includegraphics[width=0.5\textwidth]{../figures/RD_Plot_3rd_Order.pdf}\label{fig:RD_Plot_3rd_Order}}
+    \caption{RD design}
+    \label{fig:RD_design}
+\end{figure}
+
+From Figure \ref{fig:RD_design} we can see that there is indeed discontinuity in 410 meters of communities to the nearest Lianjia's store, which is pretty close to the lianjia's 5-minute walk distance policy.
+The observed decline in the Lianjia's influence is marked and suggests a pronounced reduction in its impact on the system overall within our study sample.
+This phenomenon can be attributed to the implementation of the Lianjia's proximity to customers policy, which is evidenced at the data level.
+
+To make the robust check we conducted Donut Hole test by excluding observations close to the cutoff and estimating the effect with the remaining data.
+The results are shown in Appendix and the result shows that the discontinuity still exists and this provides evidence against a model misspecification.
+Furthermore, we carry out the density test by \citep{MCCRARY2008698}.
+The result shows that the p-value is greater than 0.1, which suggests the result is not due to manipulation of polygons.
+Finally, we carry out placebo tests which are reported in Appendix, which strengthens the case for a true treatment effect.
+
+\subsection{Statistical Summary}
+
+After constructing our optimal radius, we recalcualte the number of lianjia and other brokerages' stores within this radius.
+To check the robustness of the data, we divide our data to those with lianjia and those without lianjia and to check whether lianjia's offline stores have influential effect on the transaction effect in the community.
+We can see that for income, house tour number and the are all significantly different in those communities with or without lianjia.
+Furthermore, we find that the other brokerages are also have the same tendency that they typically open stores with the same strategy as lianjia, which is consistent with our Theoretical Model's Proposition [xxxxx].
+This figure is shown in Figure \ref{fig:same_distribu`tion}.
+`'
+\begin{table}[htb!]
+    \centering
+    \begin{tiny}
+    \caption{Statistical Summary}
+    \input{../result_tables/summary_statistics.tex}
+    \label{tab:statistical}
+    \end{tiny}
+\end{table}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.7\textwidth]{../figures/scatter_plot_with_two_brokerages.pdf}
+    \caption{Tendency between two types of brokerages}
+    \label{fig:same_distribution}
+\end{figure}
+
 \section{Theoretical Model}
@@
 % There should be a model like: Police brutality, law enforcement, and crime: Evidence from Chicago
-
-\section{Data and Descriptive Evidence \label{sec:data}}
-
-\subsection{Data Collection and Processing}
-
-This study focuses on the housing markets in ten major cities in China, namely Beijing, Shanghai, Chongqing, Tianjin, Shenzhen, Guangzhou, Chengdu, Hangzhou, Wuhan and Nanjing.
-These cities are not only central to China's economic development, but also reflect the broader trends and characteristics of the country's real estate dynamics.
-Spanning from 2016 to 2022, the research period encapsulates a pivotal era in China's real estate sector.
-During the first phase of the study, from 2016 to 2019, the housing markets in these cities experienced a remarkable boom.
-This period was characterized by significant growth in property prices, supported by robust economic expansion and increased demand in these urban centers.
-However, the final phase of our study, from 2020 to 2022, paints a contrasting picture.
-During this period, China's overall economic growth rate has been slower significantly, which has also reflected in a slowdown in the real estate markets of these major cities.
-In addition, the Chinese government has implemented strict rules in Covid-19 protection, so the real estate agents in these major cities are significantly affected.
-
-The second hand housing transaction data was collected form \href{https://bj.lianjia.com/}{lianjia.com} for ten cities ranging from 2016 to 2022.
-Initially, we filtered out transaction records exhibiting unusually high prices, identifying them as outliers that could skew the analysis.
-We then removed records with missing values to maintain the integrity of our dataset.
-We also removed any records that were listed duplicated.
-We finally have a data with length 1,716,579 second-hand house.\footnote{Due to government restrictions, four of these cities did not list the transaction price for each transaction during the study period.} Since most of the offline stores in lianjia are community-based, and most of the information is accurate at the community level, we decided to aggregate the information at the community level to make our panel compatible.
-By taking the average of all transaction information, we constructed the panel data with seven years.
-
-To gather other characteristics information, we first extracted the POI data from the AutoNavi map using the web-scrawling Python program.\footnote{AutoNavi, a leading mapping application in China with a huge user base of more than 700 million, stands out for its detailed and accurate POI data and precise public transportation information.
-These features underscore AutoNavi's formidable lead in the digital mapping sector, highlighting its ability to provide unparalleled navigation accuracy and comprehensive urban mobility solutions.
-Our extracted AutoNavi map contains more than 1 million POIs for each city in each year.} We then classified the extracted POIs into different categories, the specifics of which are discussed in detail in Table \ref{tab:statistical}.
-This categorization was crucial for understanding the urban infrastructure and amenities available in the vicinity of the analyzed properties.
-We prioritized POIs within a 500-meter radius-a distance typically covered within a ten-minute walk, consistent with urban planning standards for accessible urban design.
-This radius was specifically chosen to reflect the immediate urban environment that influences residential desirability and value, as the majority of these POIs provide recreational services.
-Furthermore, some geo-informational data was also integrated into our research data, which consists of the annual gdp obtained from \citep{zhao_forecasting_2017}, nighttime lights data, obtained from \citep{elvidge_annual_2021} and air pollution data from \citep{doi:10.1021/acs.est.1c05309}.
-By merging these data with our research panel, we finally get the data.
-
-To check the robustness of the data, we divide our data to those with lianjia and those without lianjia and to check whether lianjia's offline stores have influential effect on the transaction effect in the community.
-We can see that for income, house tour number and the are all significantly different in those communities with or without lianjia.
-Furthermore, we find that the other brokerages are also have the same tendency that they typically open stores with the same strategy as lianjia, which is consistent with our Theoretical Model's Proposition [xxxxx].
-This figure is shown in Figure \ref{fig:same_distribution}.
-
-\begin{table}[htb!]
-    \centering
-    \begin{tiny}
-    \caption{Statistical Summary}
-    \input{../result_tables/summary_statistics.tex}
-    \label{tab:statistical}
-    \end{tiny}
-\end{table}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.7\textwidth]{../figures/scatter_plot_with_two_brokerages.pdf}
-    \caption{Tendency between two types of brokerages}
-    \label{fig:same_distribution}
-\end{figure}
-
-\subsection{Influential Radius} \label{subsec:Influential_Radius}
-
-The effectiveness of an offline intermediary's influence on its immediate communities is inherently constrained by geographic limitations, with its influence decreasing in proportion to the increase in spatial distance.
-Moreover, since the offline stores of lianjia are directly operated by the lianjia, strategic considerations regarding the optimal distance between stores are an integral part of their location planning to mitigate the risks associated with over-concentration of stores that could lead to competitive overlap and service homogenization.
-Consequently, it is imperative to determine an optimal radius threshold and subsequently assess the diversity of agencies operating within this demarcated zone.
-
-To determine the optimal radius of influence, this research employs a regression discontinuity design (RDD) method to examine the influential radius of offline real estate brokerages.
-The dependent variable in this analysis is the transaction revenue generated by Lianjia within a given community, while the independent variable is the community's proximity to the nearest Lianjia's store.
-Given that stores are predominantly located within commercial districts-typically encompassing several streets no more than two kilometers in diameter-it is assumed that a requisite number of stores within each district is essential to sustain revenue generation in that community.
-Building on this premise, the study further investigates the existence of an optimal influence radius within shopping districts, defined as the distance radius within which the presence of a Lianjia optimally increases transaction revenues.
-At the same time, the study also examines the hypothesis that beyond this optimal radius, the impact on transaction revenues diminishes as a result of the strategic store layout decisions implemented by Lianjia.
-
-\begin{figure}[ht]
-    \centering
-    \subfloat[RD plot with first order polynomial]{\includegraphics[width=0.5\textwidth]{../figures/RD_Plot_1st_Order.pdf}\label{fig:RD_Plot_1st_Order}}
-    \hfill % Adds horizontal space between figures
-    \subfloat[RD plot with second order polynomial]{\includegraphics[width=0.5\textwidth]{../figures/RD_Plot_2nd_Order.pdf}\label{fig:RD_Plot_2nd_Order}}
-    \hfill % Adds horizontal space between figures
-    \subfloat[RD plot with third order polynomial]{\includegraphics[width=0.5\textwidth]{../figures/RD_Plot_3rd_Order.pdf}\label{fig:RD_Plot_3rd_Order}}
-    \caption{RD design}
-    \label{fig:RD_design}
-\end{figure}
-
-From Figure \ref{fig:RD_design} we can see that there is indeed discontinuity in 410 meters of communities to the nearest Lianjia's store.
-The observed decline in the Lianjia's influence is marked and suggests a pronounced reduction in its impact on the system overall within our study sample.
-This phenomenon can be attributed to the implementation of the Lianjia's proximity to customers policy, which is evidenced at the data level.
-
-To make the robust check we conducted Donut Hole test by excluding observations close to the cutoff and estimating the effect with the remaining data.
-The result shows that the discontinuity still exists and this provides evidence against a model misspecification.
-Furthermore, we carry out the density test by \citep{MCCRARY2008698}.
-The result shows that the p-value is greater than 0.1, which suggests the result is not due to manipulation of polygons.
-Finally, we carry out placebo tests which are reported in Appendix, which strengthens the case for a true treatment effect.
 

### 2024-05-06 manuscript/main.tex
modified:   manuscript/main.tex 	modified:   manuscript/our-cites.bib

@@
 Section \ref{sec:data} describes the data and summarizes the statistical evidence.
+Section \ref{sec:theoretical_model} presents a theoretical model that incoporate the analysis.
 Section \ref{sec:mechanism_design} presents the main result of our finding.
@@
 Their results show that people who have friends who are geographically distant in real life and who have a hunch that house prices are about to rise are more likely to buy a house than rent one.
-Other relevant areas of research include \citep{NIEUWERBURGH_information, salz_intermediation_2022}.
+Other relevant areas of research include \citep{SIRMANS1991207, NIEUWERBURGH_information, salz_intermediation_2022}.
 
@@
 
-\subsection{Statistical Summary}
+\subsection{Statistical Summary} \label{subsec:Statistical_Summary}
 
@@
 We can see that for income, house tour number and the are all significantly different in those communities with or without lianjia.
-Furthermore, we find that the other brokerages are also have the same tendency that they typically open stores with the same strategy as lianjia, which is consistent with our Theoretical Model's Proposition [xxxxx].
-This figure is shown in Figure \ref{fig:same_distribu`tion}.
-`'
+In addition, we find that the other brokerages also have the same tendency that they typically open stores with the same strategy as Lianjia, which suggests that Lianjia does not have the market power to exclude competent companies from entering the market, and it also suggests that the market is not monopolized by Lianjia.
+We plot the relationship between the number of other brokerages's stores and the number of lianjia's stores and the figure is shown in Figure \ref{fig:same_distribution}.
+
 \begin{table}[htb!]
@@
     \label{fig:same_distribution}
+    Note: the x-axis is the number of lianjia's stores and the y-axis is the number of other brokerages' stores. The fit is a cubic polynomial fit.
 \end{figure}
 
-\section{Theoretical Model}
-
-To characterize the real estate brokerage market, we can assume that there are two types of brokerages in the market, where the type $1$ denote the large real estate brokerage that is incorporating the online platform and the offline stores strategies, and the type $2$ denote the small real estate brokerage that only have the offline stores and they should compete with the type $1$ stores and type $2$ stores in the market.
-Each type of brokerage follows a standard percentage charge by $r_j$ and they can not manipulate the percentage charge in each submarket.
-
-We can assume that there are $M$ number of communities in the market, and each market has $\kappa_i, i \in \{1, \ldots, M\}$ number of houses listed which depends on the previous listing number and we can formulate it as a AR(1) model specified by:
-
-\begin{equation}
-  \kappa_{i, t} = \rho_{i} \kappa_{i-1, t} + \epsilon_{i, t}, \label{eq:ar1}
-\end{equation}
-
-where $\rho_i$ is the parameter and $\varepsilon_{i, t} \sim \mathcal{N}(0, \sigma_{i, t}^2)$.
-We can assume that the price of the house is determined by the hedonic pricing model, and without loss of generality, the price follows a standard uniform distribution, $P_i \sim Uniform[0, 1]$.
-
-The number of two types of brokerages are characterized by $B_{1, i}$ and $B_{2, i}$, respectively.
-The brokerages have the same positive cost function denoted as $C(\cdot)$ where $\frac{\partial C(\cdot)}{\partial B_{1, t}} > 0$ and $\frac{\partial C^2(\cdot)}{\partial B_{1, t}^2} > 0$.
-The intuition is that because of the marginal cost of the platform is $0$, when considering the cost of opening additional stores in the market, the brokerage does not incur that cost into consideration and therefore, the cost function is equal for both types of stores.
-Moreover, the marginal cost of opening additional stores is increasing, which is consistent with the real estate brokerage market.
-
-There are $L$ number of customers that arrive in the market at random poission rate $\lambda$ and for current issue, we can first assume that the customers are indifferent when selecting the brokerages and we can release this assumption later to make the customers have private preference towards each type of brokerages.
-The probability of selecting the brokerage $i$ is given by:
-
-\begin{equation}
-  p_i = \frac{B_{i, t} \times N^e(B_{1, i})}{B_{1, t} \times N^e(B_{1, i}) + B_{2, t}}. \label{eq:prob}
-\end{equation}
-
-where $N^e(B_{1, i})$ is a function representing the network effects, and is modeled as $N^e(B_{1, i}) = 1 + \alpha \log(1 + B_{1, i})$ where $\alpha$ is a parameter that quantifies the strength of network effects and the logarithmic form captures diminishing returns to scale as the number of brokerages increases.
-The revenue for each brokerage type $j$ in community $i$ is proportional to the number of houses they sell, which depends on the number of customers they attract:
-
-\begin{equation}
-  R_{i, j, t} = r_j \cdot P_i \cdot N_{i, j, t}
-\end{equation}
-
-where $N_{i, j, t}$ is the number of customers selecting type $j$ brokerage in community $i$ at time period $t$, estimated by:
-
-\begin{equation}
-  N_{i, j, t} = \lambda_i p_{i, j, t}
-\end{equation}
-
-and $\lambda_i$ is the appropriate part of $\lambda$ that arrives in community $i$.
-
-give me a mathematical economics model characterizing the partial equilibrium of real estate broekrage and the competitive market where there are two types of brokerages denoted 1 if the brokerage is the large brokerage that it can communicate with other stores in different regions of the same type 1 brokerage, and denote 2 if it is small brokerage that it can not communicate with the other brokerages in the market
-
-The first proposition is that the charging fee should be higher comparing with type $2$ brokerage.
-
-The second proposition is that the number of stores in high popular regions should be higher in the number of stores and they are more likely to form a network effect.
-
-The third proposition is the introduction of the platform should increase the number of transactions and the number of stores in the market.
-
-The fourth proposition is that the entry of the large brokerage can increase the transaction number and the number of stores in the market.
-
-In the later, we can also assume that people have private information or preference towards different brokerages so that there will be another proposition demonstrated about the model.
-
-We can examine the following two effects:
-
-\begin{itemize}
-  \item The real estate brokerage's network effect where the brokerages are more likely to form a edge between each other (this is demonstrated in the ACN's brokerage network model)
-  \item The partial effect of the network effect is not characterized by the price level changes or the brokerage fee increase.
-  \item The network effect should be demonstrated by the increase in the number of transactions and the number of the stores within given radius comparing with the total number of houses in this market.
-\end{itemize}
-
-% There should be a model like: Police brutality, law enforcement, and crime: Evidence from Chicago
-
-\subsection{Stylized Fact}
+\subsection{Stylized Fact} \label{subsec:stylized_fact}
 
@@
 
+\section{Theoretical Model} \label{sec:theoretical_model}
+
+\textbf{Should revise the model to make the model can incoporate the network effect and the platform's entry effect so that we can study that the entry of the platform can be helpful to make xxx.}
+
+To characterize the real estate brokerage market, we can assume that there are two types of brokerages in the market, where the type $1$ denote the large real estate brokerage that is incorporating the online platform and the offline stores strategies, and the type $2$ denote the small real estate brokerage that only have the offline stores and they should compete with the type $1$ stores and type $2$ stores in the market.
+Each type of brokerage follows a standard percentage charge by $r_j$ and they can not manipulate the percentage charge in each submarket.
+
+We can assume that there are $M$ number of communities in the market, and each market has $\kappa_i, i \in \{1, \ldots, M\}$ number of houses listed which depends on the previous listing number and we can formulate it as a AR(1) model specified by:
+
+\begin{equation}
+  \kappa_{i, t} = \rho_{i} \kappa_{i-1, t} + \epsilon_{i, t}, \label{eq:ar1}
+\end{equation}
+
+where $\rho_i$ is the parameter and $\varepsilon_{i, t} \sim \mathcal{N}(0, \sigma_{i, t}^2)$.
+We can assume that the price of the house is determined by the hedonic pricing model, and without loss of generality, the price follows a standard uniform distribution, $P_i \sim Uniform[0, 1]$.
+
+The number of two types of brokerages are characterized by $B_{1, i}$ and $B_{2, i}$, respectively.
+The brokerages have the same positive cost function denoted as $C(\cdot)$ where $\frac{\partial C(\cdot)}{\partial B_{1, t}} > 0$ and $\frac{\partial C^2(\cdot)}{\partial B_{1, t}^2} > 0$.
+The intuition is that because of the marginal cost of the platform is $0$, when considering the cost of opening additional stores in the market, the brokerage does not incur that cost into consideration and therefore, the cost function is equal for both types of stores.
+Moreover, the marginal cost of opening additional stores is increasing, which is consistent with the real estate brokerage market.
+
+There are $L$ number of customers that arrive in the market at random poission rate $\lambda$ and for current issue, we can first assume that the customers are indifferent when selecting the brokerages and we can release this assumption later to make the customers have private preference towards each type of brokerages.
+The probability of selecting the brokerage $i$ is given by:
+
+\begin{equation}
+  p_i = \frac{B_{i, t} \times N^e(B_{1, i})}{B_{1, t} \times N^e(B_{1, i}) + B_{2, t}}. \label{eq:prob}
+\end{equation}
+
+where $N^e(B_{1, i})$ is a function representing the network effects, and is modeled as $N^e(B_{1, i}) = 1 + \alpha \log(1 + B_{1, i})$ where $\alpha$ is a parameter that quantifies the strength of network effects and the logarithmic form captures diminishing returns to scale as the number of brokerages increases.
+The revenue for each brokerage type $j$ in community $i$ is proportional to the number of houses they sell, which depends on the number of customers they attract:
+
+\begin{equation}
+  R_{i, j, t} = r_j \cdot P_i \cdot N_{i, j, t}
+\end{equation}
+
+where $N_{i, j, t}$ is the number of customers selecting type $j$ brokerage in community $i$ at time period $t$, estimated by:
+
+\begin{equation}
+  N_{i, j, t} = \lambda_i p_{i, j, t}
+\end{equation}
+
+and $\lambda_i$ is the appropriate part of $\lambda$ that arrives in community $i$.
+
+give me a mathematical economics model characterizing the partial equilibrium of real estate broekrage and the competitive market where there are two types of brokerages denoted 1 if the brokerage is the large brokerage that it can communicate with other stores in different regions of the same type 1 brokerage, and denote 2 if it is small brokerage that it can not communicate with the other brokerages in the market
+
+The first proposition is that the charging fee should be higher comparing with type $2$ brokerage.
+
+The second proposition is that the number of stores in high popular regions should be higher in the number of stores and they are more likely to form a network effect.
+
+The third proposition is the introduction of the platform should increase the number of transactions and the number of stores in the market.
+
+The fourth proposition is that the entry of the large brokerage can increase the transaction number and the number of stores in the market.
+
+The fifth proposition should be the fact that when there is negative shock to the customers, the number of transactions and the number of stores should decrease and the number of brokerage fee should decrease in the long run (which can be modeled using graph or simulation).
+
+The sixth proposition should be the fact that before the increase of the
+
+In the later, we can also assume that people have private information or preference towards different brokerages so that there will be another proposition demonstrated about the model.
+
+We can examine the following two effects:
+
+\begin{itemize}
+  \item The real estate brokerage's network effect where the brokerages are more likely to form a edge between each other (this is demonstrated in the ACN's brokerage network model)
+  \item The partial effect of the network effect is not characterized by the price level changes or the brokerage fee increase.
+  \item The network effect should be demonstrated by the increase in the number of transactions and the number of the stores within given radius comparing with the total number of houses in this market.
+\end{itemize}
+
+% There should be a model like: Police brutality, law enforcement, and crime: Evidence from Chicago
+
 \section{Mechanism Design} \label{sec:mechanism_design}
 
-\subsection{Does Lianjia's Entry influence the segmented market?}
+\subsection{Does Lianjia's Entry influence the segmented market?} \label{subsec:entry_effect}
 
@@
 
-\subsection{Is Lianjia's ACN strategy profitable?}
+\subsection{Is Lianjia's ACN strategy profitable?} \label{subsec:acn_strategy}
 

### 2024-05-06 manuscript/main.tex
Add files via upload

@@
 
+\emph{This should be based on the brokerages' network}
+
 \textbf{Should revise the model to make the model can incoporate the network effect and the platform's entry effect so that we can study that the entry of the platform can be helpful to make xxx.}
 
+This follows from \citep{Armstrong2006}.
+
+Our model is in line with the real world setting that the sellers are hard to know about which platform can bring how many buyers to the market but the buyers can search all the information available online to decide which house they can assess.
+
 To characterize the real estate brokerage market, we can assume that there are two types of brokerages in the market, where the type $1$ denote the large real estate brokerage that is incorporating the online platform and the offline stores strategies, and the type $2$ denote the small real estate brokerage that only have the offline stores and they should compete with the type $1$ stores and type $2$ stores in the market.
-Each type of brokerage follows a standard percentage charge by $r_j$ and they can not manipulate the percentage charge in each submarket.
+Each type of brokerage follows a standard percentage charge by $r_j, j \in \{1, 2\}$ and they can not manipulate the percentage charge in each submarket.
 
@@
 
-There are $L$ number of customers that arrive in the market at random poission rate $\lambda$ and for current issue, we can first assume that the customers are indifferent when selecting the brokerages and we can release this assumption later to make the customers have private preference towards each type of brokerages.
+There are $L$ number of customers and we can first assume that the customers are indifferent when selecting the brokerages and we can release this assumption later to make the customers have private preference towards each type of brokerages.
 The probability of selecting the brokerage $i$ is given by:
@@
 
-The result presented in the table \ref{tab:entry_effect} examines the effect of a Lianjia's entry into an area on various outcomes.
+The result presented in the table \ref{tab:entry_effect} examines the effect of Lianjia's offline stores' entry into an area on various outcomes.
 Prior to the Lianjia's entry ($pre_2$), there is no statistically significant effect on any of the three outcomes, suggesting that anticipation of the Lianjia's entry does not affect these metrics.
@@
 
-We treat the 2016's sample as the base year, and other settings are consistent with previous table \ref{tab:Dynamic}. The result is reported in Figure \ref{fig:dynamic_effect}
+We treat the year 2016 as the base year, and other settings are consistent with previous table \ref{tab:Dynamic}. The result is reported in Figure \ref{fig:dynamic_effect}
 

### 2024-05-07 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.bbl 	modified:   manuscript/main.blg 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex
update

@@
 
-\citet{Rosen_hedonic} proposed a hedonic pricing model and explained the price is determined by internal and external factors affecting it.
-But the hedonic pricing model suffers under conditions of market asymmetry and information inequality.
-The seminal work on the impact of asymmetric information in markets is \citep{Akerlof_1970}, which demonstrated that markets for used cars tend to be dominated by low-quality goods, or 'lemons,' leading to market inefficiencies.
+\citet{Rosen_hedonic} proposed a hedonic pricing model and decomposed the price by internal and external factors affecting it.
+However, the hedonic pricing model suffers from market asymmetry and information inequality.
+The seminal work on the impact of asymmetric information in markets is \citep{Akerlof_1970}, which demonstrated that markets for used cars tend to be dominated by low-quality goods, or 'lemons', leading to market inefficiencies.
  Furthermore, \citet{grossman_impossibility_1980} further argued that information effective market assumption is hard to hold in reality.
@@
 
-In terms of real estate market, several literature has shown that several factors can influence the market pricing and strategies.
+In terms of the real estate market, previous literature has shown that several factors can influence market pricing and strategies.
 The \citep{550a6ccf-cde2-3dd1-979f-1a8db2b8ceb9} documents that apart from price competition in the market, there is a lot of market inefficiency that stems from non-price competition, which suggests that as the degree of competition in the market increases, the market becomes progressively less efficient, indicating that the entry dividend begins to fall and aggregate social welfare begins to decline.
-Moreover, \citet{hendel_relative_2009} analyzes two types of listings in the second-hand housing market and finds that For-Sale-By-Owner type of platforms are less effective in terms of time and probability of sale, while operating better compared to listing homes for sale as a broker.
+Moreover, \citet{hendel_relative_2009} analyzes two types of listings in the second-hand housing market and finds that For-Sale-By-Owner type of platforms are less effective in terms of time and probability of sale while operating better compared to listing homes for sale as a broker.
 In addition, \citet{bailey_economic_2018} uses data from the social media site Facebook to show that social interactions can influence people's economic decisions.
@@
 
-\subsection{Data Collection and Processing}
+\subsection{Data Collection and Processing} \label{subsec:data_collection}
 
@@
 The effectiveness of an offline intermediary's influence on its immediate communities is inherently constrained by geographic limitations, with its influence decreasing in proportion to the increase in spatial distance.
-Moreover, since the offline stores of lianjia are directly operated by the company, strategic considerations regarding the optimal distance between stores are an integral part of their location planning to mitigate the risks associated with over-concentration of stores that could lead to competitive overlap and service homogenization.
+Moreover, since the offline stores of Lianjia are directly operated by the company, strategic considerations regarding the optimal distance between stores are an integral part of their location planning to mitigate the risks associated with over-concentration of stores that could lead to competitive overlap and service homogenization.
 Consequently, it is imperative to determine an optimal radius threshold and subsequently assess the diversity of agencies operating within this demarcated zone.
@@
 To determine the optimal radius of influence, this research employs a regression discontinuity design (RDD) method to examine the influential radius of offline real estate brokerages.
-The dependent variable in this analysis is the transaction revenue generated by Lianjia within a given community, while the independent variable is the community's proximity to the nearest Lianjia's store.
-Given that stores are predominantly located within commercial districts-typically encompassing several streets no more than two kilometers in diameter-it is assumed that a requisite number of stores within each district is essential to sustain revenue generation in that community.
-In addition, since the Lianjia's company adopts a 5-minute walking distance (approximately 400 meters) radius policy, which means that no matter how far away customers live, they should be accessible within a 5-minute walk to the nearest Lianjia's store.
+The dependent variable in this analysis is the transaction revenue generated by Lianjia within a given community, while the independent variable is the community's proximity to the nearest Lianjia store.
+Given that stores are predominantly located within commercial districts, which typically encompass several streets no more than two kilometers in diameter, it is assumed that a requisite number of stores within each district is essential to sustain revenue generation in that community.
+In addition, Lianjia adopts a 5-minute walking distance (approximately 400 meters) radius policy, which means that no matter how far away customers live, they should be accessible within a 5-minute walk to the nearest Lianjia store.
 Building on this premise, the study further investigates the existence of an optimal influence radius within shopping districts, defined as the distance radius within which the presence of a Lianjia optimally increases transaction revenues.
@@
 \section{Theoretical Model} \label{sec:theoretical_model}
-
-\emph{This should be based on the brokerages' network}
 

### 2024-05-08 plotting/plot_distribution.R
new file:   plotting/plot_distribution.R

@@ -1,0 +1,29 @@
+library(ggplot2)
+library(ggmap)
+library(RColorBrewer) # for color selection
+
+# you need to set working directory to the directory that you store the data
+setwd('/home/xuyuan/Desktop/2024 summer/real estate paper/oritignal cleaning/RealEstateBrokerage/plotting')
+
+# Read the input spatial-temporal data
+data <- read.csv('../dataframe_to_map.csv')
+
+# the code book is listed here:
+codebook <- dictionary(c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10), c('Beijing', 'Chengdu', 'Chongqing', 'Guangzhou', 'Hangzhou', 'Nanjing', 'Shanghai', 'Shenzhen', 'Tianjin', 'Wuhan'))
+city_dict <- c(
+  Beijing = "北京市",
+  Chengdu = "成都市",
+  Chongqing = "重庆市",
+  Guangzhou = "广州市",
+  Hangzhou = "杭州市",
+  Nanjing = "南京市",
+  Shanghai = "上海市",
+  Shenzhen = "深圳市",
+  Tianjin = "天津市",
+  Wuhan = "武汉市"
+)
+# the we can correspondingly extract the brokerage data from the corresponding file
+# we only need the year 2022 data.
+data1 <- read_csv('../classifying brokerages/lianjia_beke/')
+
+# now after all these readings we can deal with the 

### 2024-05-08 plotting/plot_distribution.R
new file:   "figures/distribution_of_hp_and_broker/\344\270\212\346\265\267\345\270\202.pdf" 	new file:   "figures/distribution_of_hp_and_broker/\345\214\227\344\272\254\345\270\202.pdf" 	new file:   "figures/distribution_of_hp_and_broker/\345\215\227\344\272\254\345\270\202.pdf" 	new file:   "figures/distribution_of_hp_and_broker/\345\244\251\346\264\245\345\270\202.pdf" 	new file:   "figures/distribution_of_hp_and_broker/\345\271\277\345\267\236\345\270\202.pdf" 	new file:   "figures/distribution_of_hp_and_broker/\346\210\220\351\203\275\345\270\202.pdf" 	new file:   "figures/distribution_of

@@ -1,29 +1,0 @@
-library(ggplot2)
-library(ggmap)
-library(RColorBrewer) # for color selection
-
-# you need to set working directory to the directory that you store the data
-setwd('/home/xuyuan/Desktop/2024 summer/real estate paper/oritignal cleaning/RealEstateBrokerage/plotting')
-
-# Read the input spatial-temporal data
-data <- read.csv('../dataframe_to_map.csv')
-
-# the code book is listed here:
-codebook <- dictionary(c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10), c('Beijing', 'Chengdu', 'Chongqing', 'Guangzhou', 'Hangzhou', 'Nanjing', 'Shanghai', 'Shenzhen', 'Tianjin', 'Wuhan'))
-city_dict <- c(
-  Beijing = "北京市",
-  Chengdu = "成都市",
-  Chongqing = "重庆市",
-  Guangzhou = "广州市",
-  Hangzhou = "杭州市",
-  Nanjing = "南京市",
-  Shanghai = "上海市",
-  Shenzhen = "深圳市",
-  Tianjin = "天津市",
-  Wuhan = "武汉市"
-)
-# the we can correspondingly extract the brokerage data from the corresponding file
-# we only need the year 2022 data.
-data1 <- read_csv('../classifying brokerages/lianjia_beke/')
-
-# now after all these readings we can deal with the 

### 2024-05-08 plotting/plot_distribution.R
new file:   plotting/plot_distribution.R

@@ -1,0 +1,125 @@
+library(ggplot2)
+library(ggmap)
+library(RColorBrewer) # for color selection
+library(aspace)
+library(sf)
+library(glue)
+library(viridis)
+library(stringr)
+# you should register with google API
+register_google(key = "your key")
+# you need to set working directory to the directory that you store the data
+setwd('/home/xuyuan/Desktop/2024 summer/real estate paper/oritignal cleaning/RealEstateBrokerage/plotting') # change this directory that contains the data
+
+# Read the input spatiotemporal data
+data <- read.csv('../dataframe_to_map.csv')
+
+# the code book is listed here:
+codebook <- setNames(c('Beijing', 'Chengdu', 'Chongqing', 'Guangzhou', 'Hangzhou', 'Nanjing', 'Shanghai', 'Shenzhen', 'Tianjin', 'Wuhan'), c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10))
+
+# Dictionary mapping English city names to Chinese city names
+city_dict <- c(
+  Beijing = "北京市",
+  Chengdu = "成都市",
+  Chongqing = "重庆市",
+  Guangzhou = "广州市",
+  Hangzhou = "杭州市",
+  Nanjing = "南京市",
+  Shanghai = "上海市",
+  Shenzhen = "深圳市",
+  Tianjin = "天津市",
+  Wuhan = "武汉市"
+)
+
+if (file.exists('../figures/distribution_of_hp_and_broker')){
+    pass
+} else {
+    dir.create(file.path('../figures/distribution_of_hp_and_broker'))
+}
+
+for (i in 1 : 10){
+  # the we can correspondingly extract the brokerage data from the corresponding file
+  # we only need the year 2022 data.
+  temp_data <- data[data$city_id == i, ]
+  # extract the temperary city name
+  temp_data$city_name <- codebook[as.character(temp_data$city_id)]
+  # store the english name of the city
+  english_name <- temp_data[1, "city_name"]
+  temp_data$city_name_chinese <- city_dict[temp_data$city_name]
+  # and correspondingly chinese name
+  file_name <- temp_data[1, "city_name_chinese"]
+  files <- glue('../classifying brokerages/lianjia_beke/{file_name}22.csv')
+  data1 <- read.csv(files)
+  temp_data$geometry <- st_as_sfc(temp_data$geometry)
+  # Convert the data frame to an sf object
[…]

### 2024-05-08 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.bbl 	modified:   manuscript/main.blg 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

@@
 \author[2]{Xuyuan Zhang \thanks{Email Address: \href{mailto:zxuyuan@umich.edu}{zxuyuan@umich.edu}}}
-\affil[1]{Sichuan University}
-\affil[2]{University of Michigan, Ann Arbor}
+\affil[1]{School of Economics, Sichuan University, China}
+\affil[2]{Department of Economics, University of Michigan, United States}
 
@@
 
-Our model is in line with the real world setting that the sellers are hard to know about which platform can bring how many buyers to the market but the buyers can search all the information available online to decide which house they can assess.
+Our model is in line with the real world setting that the sellers are hard to predict which platform can bring how many buyers to their house but the buyers can search all the information available online to decide which house they are interersted in.
 
@@
 
-We can assume that there are $M$ number of communities in the market, and each market has $\kappa_i, i \in \{1, \ldots, M\}$ number of houses listed which depends on the previous listing number and we can formulate it as a AR(1) model specified by:
+We can assume that there are $M$ number of communities in the market, and each market has $\kappa_i, i \in \{1, \ldots, M\}$ number of houses listed.
+Assume that the sellers are indifferent among the brokerages and therefore, their chossing is only dependent on the proportion of stores in the market.
+We can denote the number of two types of brokerages by $B_{1, i}$ and $B_{2, i}$, respectively and therefore, the number of houses listed in the brokerage $j$ is $\kappa_{i} \times \frac{B_{i, i}}{B_{i, 1} + B_{i, 2}}$.
 
-\begin{equation}
-  \kappa_{i, t} = \rho_{i} \kappa_{i-1, t} + \epsilon_{i, t}, \label{eq:ar1}
-\end{equation}
+We can assume that the price of the house is determined by the hedonic pricing model from various confounding factors that are determined by the community and unique characteristics of the housing, and without loss of generality, the price follows a standard uniform distribution, $P_i \sim Uniform[0, 1]$.
 
-where $\rho_i$ is the parameter and $\varepsilon_{i, t} \sim \mathcal{N}(0, \sigma_{i, t}^2)$.
-We can assume that the price of the house is determined by the hedonic pricing model, and without loss of generality, the price follows a standard uniform distribution, $P_i \sim Uniform[0, 1]$.
-
-The number of two types of brokerages are characterized by $B_{1, i}$ and $B_{2, i}$, respectively.
-The brokerages have the same positive cost function denoted as $C(\cdot)$ where $\frac{\partial C(\cdot)}{\partial B_{1, t}} > 0$ and $\frac{\partial C^2(\cdot)}{\partial B_{1, t}^2} > 0$.
+The brokerages have the same positive cost function denoted as $C(\cdot)$ where $\frac{\partial C(\cdot)}{\partial B_{j}} > 0$ and $\frac{\partial C^2(\cdot)}{\partial B_{j}^2} > 0$ where $j \in \{1, 2\}$.
 The intuition is that because of the marginal cost of the platform is $0$, when considering the cost of opening additional stores in the market, the brokerage does not incur that cost into consideration and therefore, the cost function is equal for both types of stores.
 Moreover, the marginal cost of opening additional stores is increasing, which is consistent with the real estate brokerage market.
+
+We can inherent from the previous literature that there are broad searchers and narrow searchers in the market, \citep{10.1257/aer.20141772}.
 

### 2024-05-09 figures/distribution_of_hp_and_broker.tex
new file:   figures/distribution_of_hp_and_broker.tex 	renamed:    "figures/distribution_of_hp_and_broker/\345\214\227\344\272\254\345\270\202.pdf" -> figures/distribution_of_hp_and_broker/Beijing.pdf 	renamed:    "figures/distribution_of_hp_and_broker/\346\210\220\351\203\275\345\270\202.pdf" -> figures/distribution_of_hp_and_broker/Chengdu.pdf 	renamed:    "figures/distribution_of_hp_and_broker/\351\207\215\345\272\206\345\270\202.pdf" -> figures/distribution_of_hp_and_broker/Chongqing.pdf 	renamed:    "figures/distribution_of_hp_and_broker/\345\271\277\345\267\236\345\270\202.pdf" -> figure

\begin{figure}[h!]
 \begin{scriptsize}   \centering
    \begin{minipage}{0.328\textwidth}
        \includegraphics[width=\linewidth]{../figures/distribution_of_hp_and_broker/Beijing.pdf}
    \end{minipage}
    \hfill
    \begin{minipage}{0.328\textwidth}
        \includegraphics[width=\linewidth]{../figures/distribution_of_hp_and_broker/Chengdu.pdf}
    \end{minipage}
    \begin{minipage}{0.328\textwidth}
        \includegraphics[width=\linewidth]{../figures/distribution_of_hp_and_broker/Chongqing.pdf}
    \end{minipage}

    \begin{minipage}{0.328\textwidth}
        \includegraphics[width=\linewidth]{../figures/distribution_of_hp_and_broker/Guangzhou.pdf}
    \end{minipage}
    \hfill
    \begin{minipage}{0.328\textwidth}
        \includegraphics[width=\linewidth]{../figures/distribution_of_hp_and_broker/Hangzhou.pdf}
    \end{minipage}
    \begin{minipage}{0.328\textwidth}
        \includegraphics[width=\linewidth]{../figures/distribution_of_hp_and_broker/Nanjing.pdf}
    \end{minipage}

    \begin{minipage}{0.328\textwidth}
        \includegraphics[width=\linewidth]{../figures/distribution_of_hp_and_broker/Shanghai.pdf}
    \end{minipage}
    \hfill
    \begin{minipage}{0.328\textwidth}
        \includegraphics[width=\linewidth]{../figures/distribution_of_hp_and_broker/Shenzhen.pdf}
    \end{minipage}
    \begin{minipage}{0.328\textwidth}
        \includegraphics[width=\linewidth]{../figures/distribution_of_hp_and_broker/Tianjin.pdf}
    \end{minipage}

    \begin{minipage}{0.328\textwidth}
        \includegraphics[width=\linewidth]{../figures/distribution_of_hp_and_broker/Wuhan.pdf}
    \end{minipage}
    \hfill

\caption{The distribution of housing prices and brokers in different cities.}

Note: The heat map represents the distribution of housing prices and the standard ellipse represents the distribution of brokers, which is calculated by the mean and standard deviation of the latitude and longitude of brokers. The larger the ellipse, the more sparse the brokerages' distribution is. The Base Map is from Google Map.\end{scriptsize} \end{figure}

### 2024-05-09 plotting/plot_distribution.R

@@ -91,7 +91,7 @@ for (i in 1 : 10){
     ) +
     guides(fill = guide_legend(override.aes= list(alpha = 1)))
   # g.base
-  name_figure <- glue('../figures/distribution_of_hp_and_broker/{file_name}.pdf')
+  name_figure <- glue('../figures/distribution_of_hp_and_broker/{english_name}.pdf')
   name_list_0 <- unique(points_with_admin$name.y)
   g.ellipse.spr <- g.base
   # now we plot for the standard ellipse

### 2024-05-09 manuscript/main.tex
new file:   figures/distribution_of_hp_and_broker.tex 	renamed:    "figures/distribution_of_hp_and_broker/\345\214\227\344\272\254\345\270\202.pdf" -> figures/distribution_of_hp_and_broker/Beijing.pdf 	renamed:    "figures/distribution_of_hp_and_broker/\346\210\220\351\203\275\345\270\202.pdf" -> figures/distribution_of_hp_and_broker/Chengdu.pdf 	renamed:    "figures/distribution_of_hp_and_broker/\351\207\215\345\272\206\345\270\202.pdf" -> figures/distribution_of_hp_and_broker/Chongqing.pdf 	renamed:    "figures/distribution_of_hp_and_broker/\345\271\277\345\267\236\345\270\202.pdf" -> figure

@@
 
-\textbf{Should revise the model to make the model can incoporate the network effect and the platform's entry effect so that we can study that the entry of the platform can be helpful to make xxx.}
-
-This follows from \citep{Armstrong2006}.
-
-Our model is in line with the real world setting that the sellers are hard to predict which platform can bring how many buyers to their house but the buyers can search all the information available online to decide which house they are interersted in.
+Our model accurately reflects the real-world scenario in which sellers face uncertainty regarding the number of buyers each platform might attract, whereas buyers have the advantage of accessing comprehensive online information to make informed decisions about potential house purchases.
+This model also encapsulates the dynamics of a two-sided market, characterized by the mutual attraction between buyers and sellers.
+However, due to asymmetric information, sellers are unable to determine which brokerage will attract the most buyers, creating a gap in their market strategy effectiveness.
 
@@
 We can denote the number of two types of brokerages by $B_{1, i}$ and $B_{2, i}$, respectively and therefore, the number of houses listed in the brokerage $j$ is $\kappa_{i} \times \frac{B_{i, i}}{B_{i, 1} + B_{i, 2}}$.
-
-We can assume that the price of the house is determined by the hedonic pricing model from various confounding factors that are determined by the community and unique characteristics of the housing, and without loss of generality, the price follows a standard uniform distribution, $P_i \sim Uniform[0, 1]$.
+We can assume that the price of the house is determined by the hedonic pricing model from various confounding factors that are determined by the community and unique characteristics of the housing, and we can denote it as $P_i$.
 
@@
 We can inherent from the previous literature that there are broad searchers and narrow searchers in the market, \citep{10.1257/aer.20141772}.
+Specifically, we can assume that there are $L^N_i$ narrow searches that are only searching for the community $i$ and $L^B_i$ broad searchers that are searching for all the communities in the market.
 
-There are $L$ number of customers and we can first assume that the customers are indifferent when selecting the brokerages and we can release this assumption later to make the customers have private preference towards each type of brokerages.
-The probability of selecting the brokerage $i$ is given by:
+We can first consider the naive searchers in the market, where the naive searchers in the market are attracted to the platform by the number of houses listed in the brokerage, and the probability of selecting the brokerage $j$ is given by
+
+\begin{equation}
+  N_i = L^N_i \times \frac{B_{i, j}}{B_{i, 1} + B_{i, 2}}. \label{eq:naive_prob}
+\end{equation}
+
+However, the broad searchers in the market are attracted to the platform by the
+
+and we can release this assumption later to make the customers have private preference towards each type of brokerages. The probability of selecting the brokerage $i$ is given by:
+
+This follows from \citep{Armstrong2006}.
 
@@
 
-% \section{Appendix Tables and Figures}
+\section{Appendix Tables and Figures}
 % \input{tab_tex/other-regressions.tex}
+
+\input{../figures/distribution_of_hp_and_broker.tex}
 

### 2024-05-09 result_tables/summary_statistics.tex
Add files via upload

@@
 percentage of lianjia to all brokerages & 0 & 0 & 0.206 & 0.166 & -0.206 (-384.429***) \\
-number of brokerages within 410 meters, which is the cutoff of RD & 5.362 & 6.871 & 12.66 & 8.410 & -7.300 (-217.614***) \\
+number of other brokerages within 410 meters, which is the cutoff of RD & 5.362 & 6.871 & 12.66 & 8.410 & -7.300 (-217.614***) \\
 The number of people watching a listing. & 17.61 & 29.11 & 20.29 & 29.40 & -2.682 (-21.214***) \\

### 2024-05-10 manuscript/main.tex
modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	modified:   result_tables/dynamic.tex 	modified:   result_tables/entry_effect.tex 	modified:   result_tables/formulate_the_tables.ipynb 	modified:   result_tables/robust_hhi.tex 	modified:   result_tables/robust_mature.tex 	modified:   result_tables/stylized_fact.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:

@@
 The code to replicate the paper can be accessed at \href{https://github.com/sergiozxy/RealEstateBrokerage}{https://github.com/sergiozxy/RealEstateBrokerage} The authors gratefully acknowledge financial support from the Fundamental Research Funds for the Central Universities of Sichuan University (2019hhf-08; SKSYL201812; 2018jj-01) and National Natural Science Foundation of China (71773081).
-We gratefully thank for Hanying Liu from Sichuan University and Chongyu Wang from Florida State University for insightful feedback.
+% We gratefully thank for Hanying Liu from Sichuan University and Chongyu Wang from Florida State University for insightful feedback.
 }}
@@
 Assume that the sellers are indifferent among the brokerages and therefore, their chossing is only dependent on the proportion of stores in the market.
-We can denote the number of two types of brokerages by $B_{1, i}$ and $B_{2, i}$, respectively and therefore, the number of houses listed in the brokerage $j$ is $\kappa_{i} \times \frac{B_{i, i}}{B_{i, 1} + B_{i, 2}}$.
+We can denote the number of two types of brokerages by $\mathcal{B}_{1, i}$ and $B_{2, i}$, respectively and therefore, the number of houses listed in the brokerage $j$ is $\kappa_{i} \times \frac{\mathcal{B}_{i, i}}{\mathcal{B}_{i, 1} + \mathcal{B}_{i, 2}}$.
 We can assume that the price of the house is determined by the hedonic pricing model from various confounding factors that are determined by the community and unique characteristics of the housing, and we can denote it as $P_i$.
+% we may assume the number of houses in each community follows a normal distribution to make the model can have some probability distribution.
 
-The brokerages have the same positive cost function denoted as $C(\cdot)$ where $\frac{\partial C(\cdot)}{\partial B_{j}} > 0$ and $\frac{\partial C^2(\cdot)}{\partial B_{j}^2} > 0$ where $j \in \{1, 2\}$.
+The brokerages have the same positive cost function denoted as $C(\cdot)$ where $\frac{\partial C(\cdot)}{\partial \mathcal{B}_{j}} > 0$ and $\frac{\partial C^2(\cdot)}{\partial \mathcal{B}_{j}^2} > 0$ where $j \in \{1, 2\}$.
 The intuition is that because of the marginal cost of the platform is $0$, when considering the cost of opening additional stores in the market, the brokerage does not incur that cost into consideration and therefore, the cost function is equal for both types of stores.
@@
 We can inherent from the previous literature that there are broad searchers and narrow searchers in the market, \citep{10.1257/aer.20141772}.
-Specifically, we can assume that there are $L^N_i$ narrow searches that are only searching for the community $i$ and $L^B_i$ broad searchers that are searching for all the communities in the market.
+Specifically, we can assume that there are $L^N_i$ narrow searches that are only searching for the community $i$ and let $L^B$ denote the set of broad searchers, defined as those individuals who consider a $\beta$ proportion of all available houses within their expansive search criteria.
+When $\beta = 1$ it means that they are searching for all the available houses in the whole city and $\beta < 1$ indicates a limited scope, possibly due to preferences or capacity constraints.
+Correspondingly, $L^B_i$ represents the subset of broad searchers within community $i$.
 
-We can first consider the naive searchers in the market, where the naive searchers in the market are attracted to the platform by the number of houses listed in the brokerage, and the probability of selecting the brokerage $j$ is given by
+We can first consider the naive searchers in the market, where the naive searchers in the market are attracted to the platform by the number of houses listed in the brokerage, and the probability of selecting the brokerage $j$ is given by the proportion of number of houses listed in the brokerage $j$ and the total number of houses listed in the community $i$:
 
 \begin{equation}
-  N_i = L^N_i \times \frac{B_{i, j}}{B_{i, 1} + B_{i, 2}}. \label{eq:naive_prob}
+  N_{i, j} = L^N_i \times \frac{\mathcal{B}_{i, j}}{\mathcal{B}_{i, 1} + \mathcal{B}_{i, 2}}. \label{eq:naive_prob}
 \end{equation}
 
-However, the broad searchers in the market are attracted to the platform by the
+However, the broad searchers in the market are attracted to the platform by the networking because they are searching for all the communities in the market,
+
+\begin{equation}
+  B_i = L^B_i \times \alpha_j \frac{\mathcal{B}_{i, j}}{\sum_{i^\prime \neq i} (\mathcal{B}_{i^\prime, 1} + \mathcal{B}_{i^\prime, 2})} \label{eq:broad_prob}
+\end{equation}
 

### 2024-05-11 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.bbl 	modified:   manuscript/main.blg 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	modified:   manuscript/our-cites.bib

@@
 
-\citet{Rosen_hedonic} proposed a hedonic pricing model and decomposed the price by internal and external factors affecting it.
+The literature on the real estate market, particularly the role of real estate brokerages, is extensive and informative, starting with the foundational work of \citet{Rosen_hedonic} who introduced the hedonic pricing model.
+This model breaks down property prices by analyzing internal and external factors.
+However, it's worth noting that this model does not adequately account for market asymmetries and information disparities, leading to potential inaccuracies in pricing.
+A fundamental study by \citep{Akerlof_1970} highlights the significant impact of asymmetric information on market dynamics, using the market for used cars as an example.
+Here, the prevalence of low-quality goods, known as 'lemons', often leads to market inefficiencies, a problem that is mirrored in the real estate sector.
+The challenge of asymmetric information in real markets was further emphasized by \citet{grossman_impossibility_1980}, who questioned the feasibility of the effective market assumption, particularly under conditions of information disparity.
+
+Subsequent studies have expanded on these foundational theories, exploring dynamics specific to real estate pricing and strategic behavior.
+\citet{550a6ccf-cde2-3dd1-979f-1a8db2b8ceb9} documents that apart from price competition in the market, there is a lot of market inefficiency that stems from non-price competition, which suggests that as the degree of competition in the market increases, the market becomes progressively less efficient, indicating that the entry dividend begins to fall and aggregate social welfare begins to decline.
+Moreover, \citet{hendel_relative_2009} analyzes two types of listings in the second-hand housing market and finds that For-Sale-By-Owner type of platforms are less effective in terms of time and probability of sale while operating better compared to listing homes for sale as a broker.
+In addition, \citet{bailey_economic_2018} uses data from the social media site Facebook to show that social interactions can influence people's economic decisions.
+Their results show that people who have friends who are geographically distant in real life and who have a hunch that house prices are about to rise are more likely to buy a house than rent one.
+Other relevant areas of research include \citep{SIRMANS1991207, NIEUWERBURGH_information, salz_intermediation_2022}.
+
+The strategic behavior of real estate brokerages has been documented to leverage informational advantages.
+\citet{AGARWAL2019715} confirms that brokerages, as market intermediaries, possess nuanced knowledge of market conditions, enabling them to negotiate discounts effectively.
+Furthermore, \citet{HAN2015813} discusses the varying bargaining power of brokerages across unidirectional and bidirectional markets, influencing their operational strategies.
+This is corroborated by evidence suggesting that properties listed with lower commission rates not only sell less frequently but also take longer to sell \citep{10.1257/app.20160214}.
+The advent of online platforms has significantly altered the landscape of real estate transactions.
+\citet{ZUMPANO2003134} notes that while the duration of property searches has not changed markedly, the scope of searches has broadened to encompass more online listings.
+Moreover, \citet{ZHANG2021101104} associates the rise of online platforms with a reduction in existing home prices and an increase in sales volumes, a dynamic influenced by factors such as new home prices and household demographics.
+However, a detailed analysis of the impact of the presence of these platforms on market performance of offline stores remains scant.
+
+Finally, the overall market influence of real estate intermediaries is multi-faceted.
+Utilizing a model predicated on perfect competition, \citet{williams_agency_1998} illustrates that an excessive entry of brokers into the market can surpass the optimal allocation, reducing social welfare.
+This is further evidenced by studies indicating that a surge in broker numbers can depress house prices and shorten transaction cycles \citep{https://doi.org/10.1002/jae.2891}.
+Additionally, \citet{qu_identifying_2021-1} highlights how broker commissions play a moderating role in disseminating information during transactions, thereby facilitating more efficient home sales.
+Other related literature includes \citep{doi:10.1080/10527001.2021.2016340, doi:10.1080/10835547.1996.12090852}.
+
+% With respect to the behavior of real estate brokerages, the research conducted by \citep{AGARWAL2019715} substantiates that these entities, acting as intermediaries in market transactions, possess superior knowledge of market dynamics.
+This informational superiority enables the intermediaries to use their bargaining power to secure discounts in the market.
+Similarly, \citet{HAN2015813} articulates that brokerages operating in unidirectional and bidirectional markets exhibit different levels of bargaining leverage, leading to different motivational drivers.
+This mechanism is in line with other research, which shows that properties with lower commission rates have a 5\% less likelihood of being sold and takes 12\% longer to sell \citep{10.1257/app.20160214}.
+
+% Regarding the impact of online platforms on the real estate sector, research by \citep{ZUMPANO2003134} suggests that while the length of time buyers spend searching for properties remains unchanged, the scope of their search expands to include a greater number of online listings.
+\citet{ZHANG2021101104} show that the introduction of online platforms is associated with reductions in existing home prices and increased sales volumes, effects that are influenced by new home prices and household size.
+However, a comprehensive analysis of the influence of the physical stores of online platforms on the real estate market is still lacking in the literature.
+
+% Finally, the impact of real estate intermediaries on the market can be decomposed into several aspects.
+Using a model based on the assumption of a perfectly competitive market in which an influx of brokers competitively enters the market, \citet{williams_agency_1998} shows that the presence of brokers in the market equilibrium exceeds the optimal number of allocations, thereby causing a reduction in social welfare.
+Moreover, the results show that neither brokers nor sellers are motivated to deviate from the equilibrium price structure, which coincides with the reservation price set by sellers.
+Complementary research in another study shows that a significant influx of brokers into the market is correlated with a decrease, rather than an increase, in house prices, along with a gradual decrease in transaction cycles within the market \citep{https://doi.org/10.1002/jae.2891}.
+Furthermore, the work of \citep{qu_identifying_2021-1} highlights the moderating role of broker commissions on the dissemination of market information during transactions.
+Their findings suggest that the use of a broker can significantly mitigate the concessions that sellers are forced to make in the transaction process, thereby enhancing their ability to complete a home sale more efficiently.
+
+% Many literature has been conducted to study the real estate market, and the impact of real estate brokerages on the market, beginning with \citet{Rosen_hedonic}, which proposed a hedonic pricing model and decomposed the price by internal and external factors affecting it.
 However, the hedonic pricing model suffers from market asymmetry and information inequality.
@@
 In this context, the role of real estate brokerages is crucial, as they act as intermediaries between buyers and sellers, providing valuable information and facilitating transactions.
-
-In terms of the real estate market, previous literature has shown that several factors can influence market pricing and strategies.
-The \citep{550a6ccf-cde2-3dd1-979f-1a8db2b8ceb9} documents that apart from price competition in the market, there is a lot of market inefficiency that stems from non-price competition, which suggests that as the degree of competition in the market increases, the market becomes progressively less efficient, indicating that the entry dividend begins to fall and aggregate social welfare begins to decline.
-Moreover, \citet{hendel_relative_2009} analyzes two types of listings in the second-hand housing market and finds that For-Sale-By-Owner type of platforms are less effective in terms of time and probability of sale while operating better compared to listing homes for sale as a broker.
-In addition, \citet{bailey_economic_2018} uses data from the social media site Facebook to show that social interactions can influence people's economic decisions.
-Their results show that people who have friends who are geographically distant in real life and who have a hunch that house prices are about to rise are more likely to buy a house than rent one.
-Other relevant areas of research include \citep{SIRMANS1991207, NIEUWERBURGH_information, salz_intermediation_2022}.
-
-With respect to the behavior of real estate brokerages, the research conducted by \citep{AGARWAL2019715} substantiates that these entities, acting as intermediaries in market transactions, possess superior knowledge of market dynamics.
-This informational superiority enables the intermediaries to use their bargaining power to secure discounts in the market.
-Similarly, \citet{HAN2015813} articulates that brokerages operating in unidirectional and bidirectional markets exhibit different levels of bargaining leverage, leading to different motivational drivers.
-This mechanism is in line with other research, which shows that properties with lower commission rates have a 5\% less likelihood of being sold and takes 12\% longer to sell \citep{10.1257/app.20160214}.
-
-Regarding the impact of online platforms on the real estate sector, research by \citep{ZUMPANO2003134} suggests that while the length of time buyers spend searching for properties remains unchanged, the scope of their search expands to include a greater number of online listings.
-\citet{ZHANG2021101104} show that the introduction of online platforms is associated with reductions in existing home prices and increased sales volumes, effects that are influenced by new home prices and household size.
-However, a comprehensive analysis of the influence of the physical stores of online platforms on the real estate market is still lacking in the literature.
-
-Finally, the impact of real estate intermediaries on the market can be decomposed into several aspects.
-Using a model based on the assumption of a perfectly competitive market in which an influx of brokers competitively enters the market, \citet{williams_agency_1998} shows that the presence of brokers in the market equilibrium exceeds the optimal number of allocations, thereby causing a reduction in social welfare.
-Moreover, the results show that neither brokers nor sellers are motivated to deviate from the equilibrium price structure, which coincides with the reservation price set by sellers.
-Complementary research in another study shows that a significant influx of brokers into the market is correlated with a decrease, rather than an increase, in house prices, along with a gradual decrease in transaction cycles within the market \citep{https://doi.org/10.1002/jae.2891}.
-Furthermore, the work of \citep{qu_identifying_2021-1} highlights the moderating role of broker commissions on the dissemination of market information during transactions.
-Their findings suggest that the use of a broker can significantly mitigate the concessions that sellers are forced to make in the transaction process, thereby enhancing their ability to complete a home sale more efficiently.
 
@@
 % we can not say that it is a martingale process because the housing market is assymetric information and martingale process is a fair game.
-
 \section{Theoretical Model} \label{sec:theoretical_model}
@@
 The intuition is that because of the marginal cost of the platform is $0$, when considering the cost of opening additional stores in the market, the brokerage does not incur that cost into consideration and therefore, the cost function is equal for both types of stores.
-Moreover, the marginal cost of opening additional stores is increasing, which is consistent with the real estate brokerage market.
+Moreover, the marginal cost of opening additional stores is increasing, which is consistent with the real estate brokerage market because the more stores the brokerage opens, the administrative cost will increase.
 

### 2024-05-11 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

@@
 \usepackage{xr}
+
+\newtheorem{assumption}{Assumption}
+\newtheorem{definition}{Definition}
+\newtheorem{proposition}{Proposition}
+\newtheorem{corollary}{Corollary}
+\newtheorem{lemma}{Lemma}
+\newtheorem{remark}{Remark}
+\newtheorem{example}{Example}
+\newtheorem{theorem}{Theorem}
 
@@
 
-The result highlights the dynamic impact of density, encapsulated by Lianjia's DBI, on transaction revenue, home visits, and price concessions over time, especially in response to external factors such as digital transformation and the COVID-19 pandemic.
+The result highlights the dynamic impact of density, encapsulated by Lianjia's DBI, on transaction revenue, house tours, and price concessions over time, especially in response to external factors such as digital transformation and the COVID-19 pandemic.
 Initially, Lianjia's impact on transaction revenue showed a significant positive trend, peaking in 2018, due to its digital transformation efforts, including the integration of other platform stores into its shared network.
@@
 
+% we can make the number of stores to $n$ instead of $2$ to make the model more general.
+
+ % we may assume the number of houses in each community follows a normal distribution to make the model can have some probability distribution.
+
 Our model accurately reflects the real-world scenario in which sellers face uncertainty regarding the number of buyers each platform might attract, whereas buyers have the advantage of accessing comprehensive online information to make informed decisions about potential house purchases.
@@
 To characterize the real estate brokerage market, we can assume that there are two types of brokerages in the market, where the type $1$ denote the large real estate brokerage that is incorporating the online platform and the offline stores strategies, and the type $2$ denote the small real estate brokerage that only have the offline stores and they should compete with the type $1$ stores and type $2$ stores in the market.
-Each type of brokerage follows a standard percentage charge by $r_j, j \in \{1, 2\}$ and they can not manipulate the percentage charge in each submarket.
+Each type of brokerage follows a standard percentage charge by $r_j$ where $j \in \{1, 2\}$ and they can not manipulate the percentage charge in each submarket.
 
@@
 We can assume that the price of the house is determined by the hedonic pricing model from various confounding factors that are determined by the community and unique characteristics of the housing, and we can denote it as $P_i$.
-% we may assume the number of houses in each community follows a normal distribution to make the model can have some probability distribution.
 
@@
 When $\beta = 1$ it means that they are searching for all the available houses in the whole city and $\beta < 1$ indicates a limited scope, possibly due to preferences or capacity constraints.
-Correspondingly, $L^B_i$ represents the subset of broad searchers within community $i$.
+Correspondingly, $L^B_i$ represents the subset of broad searchers within community $i$, and the expected number is given by $L^B_i = L^B \times \beta$.
 
-We can first consider the naive searchers in the market, where the naive searchers in the market are attracted to the platform by the number of houses listed in the brokerage, and the probability of selecting the brokerage $j$ is given by the proportion of number of houses listed in the brokerage $j$ and the total number of houses listed in the community $i$:
+We can first focus on the naive searchers in the real estate market.
+These individuals are typically drawn to platforms based on the breadth of listings available.
+Specifically, the probability that a naive searcher will choose brokerage $j$ can be characterized by the principle of the two-sided market.
+This decision is influenced by the ratio of the number of houses listed by brokerage $j$ to the total number of houses listed within community $i$.
+This model aligns with the framework proposed by \citep{Armstrong2006}, where market attractiveness is proportional to the available inventory a brokerage offers relative to the community aggregate:
 
@@
 \begin{equation}
-  B_i = L^B_i \times \alpha_j \frac{\mathcal{B}_{i, j}}{\sum_{i^\prime \neq i} (\mathcal{B}_{i^\prime, 1} + \mathcal{B}_{i^\prime, 2})} \label{eq:broad_prob}
+  B_i = L^B_i \times \alpha_j \times \frac{\mathcal{B}_{i, j}}{\mathcal{B}_{i, 1} + \mathcal{B}_{i, 2}} \label{eq:broad_prob}
 \end{equation}
 
-and we can release this assumption later to make the customers have private preference towards each type of brokerages. The probability of selecting the brokerage $i$ is given by:
-
-This follows from \citep{Armstrong2006}.
+and we can release this assumption later to make the customers have private preference towards each type of brokerage and the brokerages can not observe this pattern.
+Combinning \eqref{eq:naive_prob} and \eqref{eq:broad_prob}, we can get the total number of customers in the community $i$ and the brokerage $j$ is:
 
 \begin{equation}
-  p_i = \frac{B_{i, t} \times N^e(B_{1, i})}{B_{1, t} \times N^e(B_{1, i}) + B_{2, t}}. \label{eq:prob}
+  L_{i, j} = N_{i, j} + B_{i, j} = (L^N_i + L_B \times \beta \times \alpha_j) \times \frac{\mathcal{B}_{i, j}}{\mathcal{B}_{i, 1} + \mathcal{B}_{i, 2}}
+   \label{eq:total_prob}
 \end{equation}
 
-where $N^e(B_{1, i})$ is a function representing the network effects, and is modeled as $N^e(B_{1, i}) = 1 + \alpha \log(1 + B_{1, i})$ where $\alpha$ is a parameter that quantifies the strength of network effects and the logarithmic form captures diminishing returns to scale as the number of brokerages increases.
+We can assume there is an exogenous probability of getting the transaction complete by $\tau_{i, j}$ and the revenue for each brokerage $j$ in community $i$ can be calculated by considering the total number of transactions completed, which is the product of the number of customers handled by the brokerage and the probability of transaction completion.
+
+\begin{equation}
+  R_{i, j} = \tau_{i, j} \times L_{i, j} \times P_i \times r_j \label{eq:revenue}
+\end{equation}
+
+and the correspondingly, the total profit for the brokerage $j$ in the community $i$ is:
+
+\begin{equation}
+  \Pi_{i, j} = R_{i, j} - C(\mathcal{B}_{i, j}) \label{eq:profit}
+\end{equation}
+
+\begin{assumption}
+
+\end{assumption}
+
+% where $N^e(B_{1, i})$ is a function representing the network effects, and is modeled as $N^e(B_{1, i}) = 1 + \alpha \log(1 + B_{1, i})$ where $\alpha$ is a parameter that quantifies the strength of network effects and the logarithmic form captures diminishing returns to scale as the number of brokerages increases.
 The revenue for each brokerage type $j$ in community $i$ is proportional to the number of houses they sell, which depends on the number of customers they attract:
 
-\begin{equation}
-  R_{i, j, t} = r_j \cdot P_i \cdot N_{i, j, t}
-\end{equation}
+% where $N_{i, j, t}$ is the number of customers selecting type $j$ brokerage in community $i$ at time period $t$, estimated by:
 
-where $N_{i, j, t}$ is the number of customers selecting type $j$ brokerage in community $i$ at time period $t$, estimated by:
+% \begin{equation}
+%  N_{i, j, t} = \lambda_i p_{i, j, t}
+%\end{equation}
 
-\begin{equation}
-  N_{i, j, t} = \lambda_i p_{i, j, t}
-\end{equation}
+%and $\lambda_i$ is the appropriate part of $\lambda$ that arrives in community $i$.
 
-and $\lambda_i$ is the appropriate part of $\lambda$ that arrives in community $i$.
+%give me a mathematical economics model characterizing the partial equilibrium of real estate broekrage and the competitive market where there are two types of brokerages denoted 1 if the brokerage is the large brokerage that it can communicate with other stores in different regions of the same type 1 brokerage, and denote 2 if it is small brokerage that it can not communicate with the other brokerages in the market
 
-give me a mathematical economics model characterizing the partial equilibrium of real estate broekrage and the competitive market where there are two types of brokerages denoted 1 if the brokerage is the large brokerage that it can communicate with other stores in different regions of the same type 1 brokerage, and denote 2 if it is small brokerage that it can not communicate with the other brokerages in the market
+% The first proposition is that the charging fee should be higher comparing with type $2$ brokerage.
 
-The first proposition is that the charging fee should be higher comparing with type $2$ brokerage.
+% The second proposition is that the number of stores in high popular regions should be higher in the number of stores and they are more likely to form a network effect.
 
-The second proposition is that the number of stores in high popular regions should be higher in the number of stores and they are more likely to form a network effect.
+% The third proposition is the introduction of the platform should increase the number of transactions and the number of stores in the market.
 
-The third proposition is the introduction of the platform should increase the number of transactions and the number of stores in the market.
+% The fourth proposition is that the entry of the large brokerage can increase the transaction number and the number of stores in the market.
 
-The fourth proposition is that the entry of the large brokerage can increase the transaction number and the number of stores in the market.
+% The fifth proposition should be the fact that when there is negative shock to the customers, the number of transactions and the number of stores should decrease and the number of brokerage fee should decrease in the long run (which can be modeled using graph or simulation).
 
-The fifth proposition should be the fact that when there is negative shock to the customers, the number of transactions and the number of stores should decrease and the number of brokerage fee should decrease in the long run (which can be modeled using graph or simulation).
-
-The sixth proposition should be the fact that before the increase of the
-
-In the later, we can also assume that people have private information or preference towards different brokerages so that there will be another proposition demonstrated about the model.
+% The sixth proposition should be the fact that before the increase of the
 
@@
 The first period after entry ($post_1$) shows no significant changes in any of the results.
-However, after two post-entry periods ($post_2$ and $post_3$), there are significant negative effects on both revenue and number of home visits.
+However, after two post-entry periods ($post_2$ and $post_3$), there are significant negative effects on both revenue and number of house tours.
 These declines suggest a decline in the performance and engagement of the Lianjia, possibly due to the impact of an epidemic that led to a decrease in revenue and showing

### 2024-05-15 manuscript/main.tex
modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.blg 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

@@
 
-The dependent variable is \emph{the natural logarithm of lianjia's income}, \emph{the price concession} and \emph{the natural logarithm of home tours} and in order to quantify the effect of lianjia, we first starts with a stylized fact, and try to catch the num.
-Firstly, we construct a density based index (DBI) to capture the effect of Lianjia's effect and continuous expansion effect.
-Based on the influential radius test result, it is defined as:
+In our analysis, we focus on several dependent variables: \emph{the natural logarithm of lianjia's income}, \emph{the price concession} and \emph{the natural logarithm of home tours}.
+To quantify Lianjia's impact, we begin by establishing a key stylized fact, which we develop a Density-Based Index (DBI) index to capture the Lianjia's offline stores' influential ratio.
+The index is to measure the effects of Lianjia's operations and its continuous expansion.
+The definition of this index is informed by the results of an influential radius test, which helps us capture the spatial extent of Lianjia's influence on local real estate markets.
+This approach allows for a more nuanced understanding of how Lianjia's presence affects key market variables.
+The DBI is calculated as follows:
 
@@
 
-where $lianjia_{it}$ is the number of Lianjia within 410 meters and $total_{it}$ is the total number of brokerages within 410 meters radius.
-The adoption of this index is based on the understanding that directly using the number of Lianjia's offline stores within a certain radius may suffer from the reverse causality problem.
-This is primarily because Lianjia, similar to other real estate brokerages, strategically locates its offline stores in locations that have high desirability and consequently high transaction volumes.
-To mitigate this confounding variable, we propose the use of a comparative metric: the ratio of Lianjia offline stores to the total number of real estate brokerages in the same area.
-This methodological refinement aims to neutralize the bias introduced by Lianjia's preferred location strategy.
-Given the lack of barriers to entry in the market, this ratio provides a more nuanced indicator of Lianjia's influence than an absolute number, and this is also in line with the spatial competition model \citep{hotelling_stability_1929, daspremont_hotellings_1979}.
+where $lianjia_{it}$ represents the number of Lianjia's stores within a 410-meter radius and $total_{it}$ denotes the total number of real estate brokerages' stores within the same radius.
+The choice of this index is grounded in an effort to address potential reverse causality issues.
+Specifically, Lianjia and other brokerages often strategically place their stores in highly desirable locations, which typically also results high transaction volumes.
+This could potentially will caused our estimation biased if we were to simply count the number of Lianjia's stores.
+To control for this issue, we employ a comparative metric: the ratio of Lianjia brokerages to the total number of real estate brokerages within the radius.
+This ratio helps mitigate the bias that may arise from the strategic location choices of Lianjia, offering a clearer measure of its market influence relative to competitors.
+This approach aligns with the principles of spatial competition theory, as articulated in \citep{hotelling_stability_1929, daspremont_hotellings_1979} in competition model.
+Such a comparative metric not only provides a more accurate reflection of Lianjia's market penetration but also adheres to economic modeling standards by accounting for competitive dynamics in the sector.
 
@@
 
+In spired by the finding of the stylized fact, we propose a theoretical model to explain the mechanism behind the empirical results.
 Our model accurately reflects the real-world scenario in which sellers face uncertainty regarding the number of buyers each platform might attract, whereas buyers have the advantage of accessing comprehensive online information to make informed decisions about potential house purchases.
@@
 \end{equation}
-
-\begin{assumption}
-
-\end{assumption}
 

### 2024-05-15 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	deleted:    manuscript/main.aux 	deleted:    manuscript/main.blg 	modified:   manuscript/main.fdb_latexmk 	deleted:    manuscript/main.fls 	deleted:    manuscript/main.log 	deleted:    manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz

@@
 
-To characterize the real estate brokerage market, we can assume that there are two types of brokerages in the market, where the type $1$ denote the large real estate brokerage that is incorporating the online platform and the offline stores strategies, and the type $2$ denote the small real estate brokerage that only have the offline stores and they should compete with the type $1$ stores and type $2$ stores in the market.
-Each type of brokerage follows a standard percentage charge by $r_j$ where $j \in \{1, 2\}$ and they can not manipulate the percentage charge in each submarket.
+To characterize the real estate brokerage market, we can assume that there are $\mathcal{N}$ types of brokerages in the market, where the type $1$ denote the large real estate brokerage that is incorporating the online platform and the offline stores strategies, and the type $2$ to type $\mathcal{N}$ denote the small real estate brokerage that only have the offline stores and they should compete with the type $1$ stores and type $2, \ldots, \mathcal{N}$ stores in the market.
+Each type of brokerage follows a standard percentage charge by $r_j$ where $j \in \{1, 2, \ldots, \mathcal{N}\}$ and they can not manipulate the percentage charge in each submarket.
 
@@
 
-The brokerages have the same positive cost function denoted as $C(\cdot)$ where $\frac{\partial C(\cdot)}{\partial \mathcal{B}_{j}} > 0$ and $\frac{\partial C^2(\cdot)}{\partial \mathcal{B}_{j}^2} > 0$ where $j \in \{1, 2\}$.
+The brokerages have the same positive cost function denoted as $C(\cdot)$ where $\frac{\partial C(\cdot)}{\partial \mathcal{B}_{j}} > 0$ and $\frac{\partial C^2(\cdot)}{\partial \mathcal{B}_{j}^2} > 0$ where $j \in \{1, 2, \ldots, \mathcal{N}\}$.
 The intuition is that because of the marginal cost of the platform is $0$, when considering the cost of opening additional stores in the market, the brokerage does not incur that cost into consideration and therefore, the cost function is equal for both types of stores.
@@
 \begin{equation}
-  N_{i, j} = L^N_i \times \frac{\mathcal{B}_{i, j}}{\mathcal{B}_{i, 1} + \mathcal{B}_{i, 2}}. \label{eq:naive_prob}
+  N_{i, j} = L^N_i \times \frac{\mathcal{B}_{i, j}}{\sum_{j^\prime=1}^{\mathcal{N}}\mathcal{B}_{i, j^\prime}}. \label{eq:naive_prob}
 \end{equation}
 
-However, the broad searchers in the market are attracted to the platform by the networking because they are searching for all the communities in the market,
+However, the broad searchers in the market are attracted to the platform by the networking because they are searching for all the communities in the market, and buyers have different preferences for brokerages based on their online presence, reputation and other factors, with private information $\theta_{b, j}$ representing the buyer's preference for brokerage $j$.
 
 \begin{equation}
-  B_i = L^B_i \times \alpha_j \times \frac{\mathcal{B}_{i, j}}{\mathcal{B}_{i, 1} + \mathcal{B}_{i, 2}} \label{eq:broad_prob}
+  B_i = L^B_i \times \alpha_j \times \frac{\mathcal{B}_{i, j} \times \theta_{b, j}}{\sum_{j^\prime=1}^{\mathcal{N}}\mathcal{B}_{i, j^\prime} \times \theta_{b, j^\prime}} \label{eq:broad_prob}
 \end{equation}
@@
 \begin{equation}
-  L_{i, j} = N_{i, j} + B_{i, j} = (L^N_i + L_B \times \beta \times \alpha_j) \times \frac{\mathcal{B}_{i, j}}{\mathcal{B}_{i, 1} + \mathcal{B}_{i, 2}}
+  L_{i, j} = N_{i, j} + B_{i, j} = (L^N_i + L_B \times \beta \times \alpha_j) \times \frac{\mathcal{B}_{i, j} \times \theta_{b, j}}{\sum_{j^\prime=1}^{\mathcal{N}}\mathcal{B}_{i, j^\prime} \times \theta_{b, j^\prime}}
    \label{eq:total_prob}
@@
 
-We can assume there is an exogenous probability of getting the transaction complete by $\tau_{i, j}$ and the revenue for each brokerage $j$ in community $i$ can be calculated by considering the total number of transactions completed, which is the product of the number of customers handled by the brokerage and the probability of transaction completion.
+We can assume the probability of a successful match between buyers and sellers, which increases with the number of participants on the platform, as $\tau_{i, j} = f(\frac{\mathcal{B}_{i, j}}{\sum_{j^\prime=1}^{\mathcal{N}}\mathcal{B}_{i, j^\prime}})$ and the revenue for each brokerage $j$ in community $i$ can be calculated by considering the total number of transactions completed, which is the product of the number of customers handled by the brokerage and the probability of transaction completion.
 
@@
 \end{equation}
+
+% here is my question using rigorous mathematical model and mathematical framework to:
+
+% now formulate the assumption that other store's brokerage are homogenous and the brokerage $1$'s network effect is greater than other bokerage.
+
+% now give me the first proposition that in equilibrium, the number of brokerage $1$'s share in the market is greater than the number of brokerage $1$'s proportion of number of stores.
+Besides, the brokerage $1$'s optimal choice of broekrage charge is greater than other brokerage
+
+\begin{assumption}[homogenous brokerage]
+  The brokerage $1$'s network effect is greater than other brokerages in the market and assume that the small brokerages (Type $2$ to $\mathcal{N}$) are homogenous and they have the same network effect in the market, i.e., $\alpha_2 = \ldots = \alpha_{\mathcal{N}} = \alpha_s$, where $\alpha_s$ is the network effect for small brokerages.
+We have $\alpah_1 > \alpha_s$.
+\end{assumption}
+
+\begin{proposition}[brokerage $1$'s optimal choice]
+  In equilibrium, the market share of Brokerage 1 (Type 1) is greater than its proportion of the number of stores, and the optimal brokerage fee charged by Brokerage 1 is higher than that charged by other brokerages.
+\end{proposition}
+
+\begin{proof}
+  The total number of customers for Brokerage 1 in community $i$ is given by $L_{i, 1}$ and the total number of stores is $L_{i}$:
+
+  \begin{equation}
+    \text{Market Share}_{i, 1} = \frac{L_{i, 1}}{L_i}
+  \end{equation}
+
+  Since $\alpha_1 > \alpha_s$ and assuming $\theta_{b, 1} \geq \theta_{b, j}$ and Brokerage 1 will attract a higher proportion of broad searchers $L^B$, resulting in a larger market share.
+Thus, in equilibrium, the market share of Brokerage 1 is greater than its proportion of the number of stores.
+
+  To maximize the profit, brokerage $1$ will change $r_1$ such that: $\frac{\partial \Pi_{i, 1}}{\partial r_1} = \frac{\partial R_{i, 1}}{\partial r_1} - \frac{\partial C(\mathcal{B}_{i, 1})}{\partial r_{1}} = 0$.
+Since $\tau_{i, 1}$ and $L_{i, 1}$ are higher for brokerage $1$ due to the stronger network effect, the optimal $r_1$ will be higher compared to the fees charged by other brokerages, $r_j$ for $j \neq 1$.
+\end{proof}
+
+In the following proposition, we will derive the total surplus of the model.
+
+Now we derive the cosumer surplus, which is:
+
+% now consider the two-period entry model now consider the case of the first period there is an equilibrium with all other broekrages but in the next period there is an entry of the first brokerage then derive the new equilibrium of the market and conduct the wellfare analysis in this case
+
+\begin{proposition}[two-period entry model]
+
+\end{proposition}
 

### 2024-05-18 manuscript/main.tex
modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	deleted:    working-version-March-27-2024.pdf

@@
 \noindent
+
+\textbf{Finish Theoretical Model by May 20th, Finish the Online Appendix, Empirical Finding by May 25th, and Finish the Discussion and Conclusion by May 30th.}
 
@@
 
+ % I think this model does not evaculate the meaningful information from the paper, and the paper does not have anything interesting to say in this model.
+
 In spired by the finding of the stylized fact, we propose a theoretical model to explain the mechanism behind the empirical results.
@@
 We can denote the number of two types of brokerages by $\mathcal{B}_{1, i}$ and $B_{2, i}$, respectively and therefore, the number of houses listed in the brokerage $j$ is $\kappa_{i} \times \frac{\mathcal{B}_{i, i}}{\mathcal{B}_{i, 1} + \mathcal{B}_{i, 2}}$.
-We can assume that the price of the house is determined by the hedonic pricing model from various confounding factors that are determined by the community and unique characteristics of the housing, and we can denote it as $P_i$.
+We can assume that the price of the house is determined by the hedonic pricing model from various confounding factors that are determined by the community and unique characteristics of the housing, and we can denote it as $P_i$ that can be ranked and distributed over the range $[\underline{P}_i, \overline{P}_i]$.
+Sellers have a reservation price $\tilde{P}_i$ over the house they sell.
 
@@
 Correspondingly, $L^B_i$ represents the subset of broad searchers within community $i$, and the expected number is given by $L^B_i = L^B \times \beta$.
+We can denote the buyers' utility of owning the house by $U_{i, j}$
 
@@
 
-% here is my question using rigorous mathematical model and mathematical framework to:
-
-% now formulate the assumption that other store's brokerage are homogenous and the brokerage $1$'s network effect is greater than other bokerage.
-
-% now give me the first proposition that in equilibrium, the number of brokerage $1$'s share in the market is greater than the number of brokerage $1$'s proportion of number of stores.
-Besides, the brokerage $1$'s optimal choice of broekrage charge is greater than other brokerage
+The consumer surplus is then: $CS = \sum_{i=1}^M \sum_{j=1}^{\mathcal{N}} \int_0^{L_{i, j}} (U_{i, j} - P_i) dx$.
 
@@
 
-Now we derive the cosumer surplus, which is:
+This model is not good right now because there is no better way to conduct welfare analysis.
 

### 2024-06-06 manuscript/main.tex
modified:   analysis/final_analysis.do 	new file:   analysis/quantile-regression.R 	modified:   manuscript/main.tex

@@
 
+\textbf{Now I think about how to do this, the first task is to write completely the model and estimation of the offline and platform's effect with offline is the brokerage's offline store's entry and the onlien is the platofmrization strategy.}
+
 \section{Introduction \label{sec:introduction}}
@@
 \noindent
-
-\textbf{Finish Theoretical Model by May 20th, Finish the Online Appendix, Empirical Finding by May 25th, and Finish the Discussion and Conclusion by May 30th.}
 
@@
 
+From Table \ref{tab:statistical} we can see that the in our metro areas, the neighborhoods with lianjia within the influential radius tends to have higher number of sales, and the final transaction price is also \textyen 910,000 higher than those neighborhoods without lianjia.
+Moreover, the number of other stores within the influential distance is also signnificantly more than 7.3, which also aligns with our previous intuition that the market is not monopolized by Lianjia.
+This significance difference suggests that if we treat our sample as a cross sectional data and estimate the result with static model without considering the individual fixed effect, we may get a biased result.
+Besides, our model may suffer from endogeneity issue, since the number of lianjia's stores may be endogenous to the transaction price and the number of stores.
+
 \begin{table}[htb!]
@@
 This is due to the fact that most transactions slow down during these periods and people are more likely to wait longer to find a buyer, which would result in fewer price concessions.
-
-% we can not say that it is a martingale process because the housing market is assymetric information and martingale process is a fair game.
-\section{Theoretical Model} \label{sec:theoretical_model}
-
-% we can make the number of stores to $n$ instead of $2$ to make the model more general.
-
- % we may assume the number of houses in each community follows a normal distribution to make the model can have some probability distribution.
-
- % I think this model does not evaculate the meaningful information from the paper, and the paper does not have anything interesting to say in this model.
-
-In spired by the finding of the stylized fact, we propose a theoretical model to explain the mechanism behind the empirical results.
-Our model accurately reflects the real-world scenario in which sellers face uncertainty regarding the number of buyers each platform might attract, whereas buyers have the advantage of accessing comprehensive online information to make informed decisions about potential house purchases.
-This model also encapsulates the dynamics of a two-sided market, characterized by the mutual attraction between buyers and sellers.
-However, due to asymmetric information, sellers are unable to determine which brokerage will attract the most buyers, creating a gap in their market strategy effectiveness.
-
-To characterize the real estate brokerage market, we can assume that there are $\mathcal{N}$ types of brokerages in the market, where the type $1$ denote the large real estate brokerage that is incorporating the online platform and the offline stores strategies, and the type $2$ to type $\mathcal{N}$ denote the small real estate brokerage that only have the offline stores and they should compete with the type $1$ stores and type $2, \ldots, \mathcal{N}$ stores in the market.
-Each type of brokerage follows a standard percentage charge by $r_j$ where $j \in \{1, 2, \ldots, \mathcal{N}\}$ and they can not manipulate the percentage charge in each submarket.
-
-We can assume that there are $M$ number of communities in the market, and each market has $\kappa_i, i \in \{1, \ldots, M\}$ number of houses listed.
-Assume that the sellers are indifferent among the brokerages and therefore, their chossing is only dependent on the proportion of stores in the market.
-We can denote the number of two types of brokerages by $\mathcal{B}_{1, i}$ and $B_{2, i}$, respectively and therefore, the number of houses listed in the brokerage $j$ is $\kappa_{i} \times \frac{\mathcal{B}_{i, i}}{\mathcal{B}_{i, 1} + \mathcal{B}_{i, 2}}$.
-We can assume that the price of the house is determined by the hedonic pricing model from various confounding factors that are determined by the community and unique characteristics of the housing, and we can denote it as $P_i$ that can be ranked and distributed over the range $[\underline{P}_i, \overline{P}_i]$.
-Sellers have a reservation price $\tilde{P}_i$ over the house they sell.
-
-The brokerages have the same positive cost function denoted as $C(\cdot)$ where $\frac{\partial C(\cdot)}{\partial \mathcal{B}_{j}} > 0$ and $\frac{\partial C^2(\cdot)}{\partial \mathcal{B}_{j}^2} > 0$ where $j \in \{1, 2, \ldots, \mathcal{N}\}$.
-The intuition is that because of the marginal cost of the platform is $0$, when considering the cost of opening additional stores in the market, the brokerage does not incur that cost into consideration and therefore, the cost function is equal for both types of stores.
-Moreover, the marginal cost of opening additional stores is increasing, which is consistent with the real estate brokerage market because the more stores the brokerage opens, the administrative cost will increase.
-
-We can inherent from the previous literature that there are broad searchers and narrow searchers in the market, \citep{10.1257/aer.20141772}.
-Specifically, we can assume that there are $L^N_i$ narrow searches that are only searching for the community $i$ and let $L^B$ denote the set of broad searchers, defined as those individuals who consider a $\beta$ proportion of all available houses within their expansive search criteria.
-When $\beta = 1$ it means that they are searching for all the available houses in the whole city and $\beta < 1$ indicates a limited scope, possibly due to preferences or capacity constraints.
-Correspondingly, $L^B_i$ represents the subset of broad searchers within community $i$, and the expected number is given by $L^B_i = L^B \times \beta$.
-We can denote the buyers' utility of owning the house by $U_{i, j}$
-
-We can first focus on the naive searchers in the real estate market.
-These individuals are typically drawn to platforms based on the breadth of listings available.
-Specifically, the probability that a naive searcher will choose brokerage $j$ can be characterized by the principle of the two-sided market.
-This decision is influenced by the ratio of the number of houses listed by brokerage $j$ to the total number of houses listed within community $i$.
-This model aligns with the framework proposed by \citep{Armstrong2006}, where market attractiveness is proportional to the available inventory a brokerage offers relative to the community aggregate:
-
-\begin{equation}
-  N_{i, j} = L^N_i \times \frac{\mathcal{B}_{i, j}}{\sum_{j^\prime=1}^{\mathcal{N}}\mathcal{B}_{i, j^\prime}}. \label{eq:naive_prob}
-\end{equation}
-
-However, the broad searchers in the market are attracted to the platform by the networking because they are searching for all the communities in the market, and buyers have different preferences for brokerages based on their online presence, reputation and other factors, with private information $\theta_{b, j}$ representing the buyer's preference for brokerage $j$.
-
-\begin{equation}
-  B_i = L^B_i \times \alpha_j \times \frac{\mathcal{B}_{i, j} \times \theta_{b, j}}{\sum_{j^\prime=1}^{\mathcal{N}}\mathcal{B}_{i, j^\prime} \times \theta_{b, j^\prime}} \label{eq:broad_prob}
-\end{equation}
-
-and we can release this assumption later to make the customers have private preference towards each type of brokerage and the brokerages can not observe this pattern.
-Combinning \eqref{eq:naive_prob} and \eqref{eq:broad_prob}, we can get the total number of customers in the community $i$ and the brokerage $j$ is:
-
-\begin{equation}
-  L_{i, j} = N_{i, j} + B_{i, j} = (L^N_i + L_B \times \beta \times \alpha_j) \times \frac{\mathcal{B}_{i, j} \times \theta_{b, j}}{\sum_{j^\prime=1}^{\mathcal{N}}\mathcal{B}_{i, j^\prime} \times \theta_{b, j^\prime}}
-   \label{eq:total_prob}
-\end{equation}
-
-We can assume the probability of a successful match between buyers and sellers, which increases with the number of participants on the platform, as $\tau_{i, j} = f(\frac{\mathcal{B}_{i, j}}{\sum_{j^\prime=1}^{\mathcal{N}}\mathcal{B}_{i, j^\prime}})$ and the revenue for each brokerage $j$ in community $i$ can be calculated by considering the total number of transactions completed, which is the product of the number of customers handled by the brokerage and the probability of transaction completion.
-
-\begin{equation}
-  R_{i, j} = \tau_{i, j} \times L_{i, j} \times P_i \times r_j \label{eq:revenue}
-\end{equation}
-
-and the correspondingly, the total profit for the brokerage $j$ in the community $i$ is:
-
-\begin{equation}
-  \Pi_{i, j} = R_{i, j} - C(\mathcal{B}_{i, j}) \label{eq:profit}
-\end{equation}
-
-The consumer surplus is then: $CS = \sum_{i=1}^M \sum_{j=1}^{\mathcal{N}} \int_0^{L_{i, j}} (U_{i, j} - P_i) dx$.
-
-\begin{assumption}[homogenous brokerage]
-  The brokerage $1$'s network effect is greater than other brokerages in the market and assume that the small brokerages (Type $2$ to $\mathcal{N}$) are homogenous and they have the same network effect in the market, i.e., $\alpha_2 = \ldots = \alpha_{\mathcal{N}} = \alpha_s$, where $\alpha_s$ is the network effect for small brokerages.
-We have $\alpah_1 > \alpha_s$.
-\end{assumption}
-
-\begin{proposition}[brokerage $1$'s optimal choice]
-  In equilibrium, the market share of Brokerage 1 (Type 1) is greater than its proportion of the number of stores, and the optimal brokerage fee charged by Brokerage 1 is higher than that charged by other brokerages.
-\end{proposition}
-
-\begin{proof}
-  The total number of customers for Brokerage 1 in community $i$ is given by $L_{i, 1}$ and the total number of stores is $L_{i}$:
-
-  \begin{equation}
-    \text{Market Share}_{i, 1} = \frac{L_{i, 1}}{L_i}
-  \end{equation}
-
-  Since $\alpha_1 > \alpha_s$ and assuming $\theta_{b, 1} \geq \theta_{b, j}$ and Brokerage 1 will attract a higher proportion of broad searchers $L^B$, resulting in a larger market share.
-Thus, in equilibrium, the market share of Brokerage 1 is greater than its proportion of the number of stores.
-
-  To maximize the profit, brokerage $1$ will change $r_1$ such that: $\frac{\partial \Pi_{i, 1}}{\partial r_1} = \frac{\partial R_{i, 1}}{\partial r_1} - \frac{\partial C(\mathcal{B}_{i, 1})}{\partial r_{1}} = 0$.
-Since $\tau_{i, 1}$ and $L_{i, 1}$ are higher for brokerage $1$ due to the stronger network effect, the optimal $r_1$ will be higher compared to the fees charged by other brokerages, $r_j$ for $j \neq 1$.
-\end{proof}
-
-In the following proposition, we will derive the total surplus of the model.
-
-This model is not good right now because there is no better way to conduct welfare analysis.
-
-% now consider the two-period entry model now consider the case of the first period there is an equilibrium with all other broekrages but in the next period there is an entry of the first brokerage then derive the new equilibrium of the market and conduct the wellfare analysis in this case
-
-\begin{proposition}[two-period entry model]
-
-\end{proposition}
-
-% where $N^e(B_{1, i})$ is a function representing the network effects, and is modeled as $N^e(B_{1, i}) = 1 + \alpha \log(1 + B_{1, i})$ where $\alpha$ is a parameter that quantifies the strength of network effects and the logarithmic form captures diminishing returns to scale as the number of brokerages increases.
-The revenue for each brokerage type $j$ in community $i$ is proportional to the number of houses they sell, which depends on the number of customers they attract:
-
-% where $N_{i, j, t}$ is the number of customers selecting type $j$ brokerage in community $i$ at time period $t$, estimated by:
-
-% \begin{equation}
-%  N_{i, j, t} = \lambda_i p_{i, j, t}
-%\end{equation}
-
-%and $\lambda_i$ is the appropriate part of $\lambda$ that arrives in community $i$.
-
-%give me a mathematical economics model characterizing the partial equilibrium of real estate broekrage and the competitive market where there are two types of brokerages denoted 1 if the brokerage is the large brokerage that it can communicate with other stores in different regions of the same type 1 brokerage, and denote 2 if it is small brokerage that it can not communicate with the other brokerages in the market
-
-% The first proposition is that the charging fee should be higher comparing with type $2$ brokerage.
-
-% The second proposition is that the number of stores in high popular regions should be higher in the number of stores and they are more likely to form a network effect.
-
-% The third proposition is the introduction of the platform should increase the number of transactions and the number of stores in the market.
-
-% The fourth proposition is that the entry of the large brokerage can increase the transaction number and the number of stores in the market.
-
-% The fifth proposition should be the fact that when there is negative shock to the customers, the number of transactions and the number of stores should decrease and the number of brokerage fee should decrease in the long run (which can be modeled using graph or simulation).
-
-% The sixth proposition should be the fact that before the increase of the
-
-We can examine the following two effects:
-
-\begin{itemize}
-  \item The real estate brokerage's network effect where the brokerages are more likely to form a edge between each other (this is demonstrated in the ACN's brokerage network model)
-  \item The partial effect of the network effect is not characterized by the price level changes or the brokerage fee increase.
-  \item The network effect should be demonstrated by the increase in the number of transactions and the number of the stores within given radius comparing with the total number of houses in this market.
-\end{itemize}
 
@@
 This result indicates that in different period, the lianjia's local market power can have different influence on the market.
+
+% we can not say that it is a martingale process because the housing market is assymetric information and martingale process is a fair game.
+\section{Theoretical Model} \label{sec:theoretical_model}
+
+% we can make the number of stores to $n$ instead of $2$ to make the model more general.
+
+ % we may assume the number of houses in each community follows a normal distribution to make the model can have some probability distribution.
+
+ % I think this model does not evaculate the meaningful information from the paper, and the paper does not have anything interesting to say in this model.
+
+We can try to decompose the
+
+In spired by the finding of the stylized fact, we propose a theoretical model to explain the mechanism behind the empirical results.
+Our model accurately reflects the real-world scenario in which sellers face uncertainty regarding the number of buyers each platform might attract, whereas buyers have the advantage of accessing comprehensive online information to make informed decisions about potential house purchases.
+This model also encapsulates the dynamics of a two-sided market, characterized by the mutual attraction between buyers and sellers.
+However, due to asymmetric information, sellers are unable to determine which brokerage will attract the most buyers, creating a gap in their market strategy effectiveness.
+
+To characterize the real estate brokerage market, we can assume that there are $\mathcal{N}$ types of brokerages in the market, where the type $1$ denote the large real estate brokerage that is incorporating the online platform and the offline stores strategies, and the type $2$ to type $\mathcal{N}$ denote the small real estate brokerage that only have the offline stores and they should compete with the type $1$ stores and type $2, \ldots, \mathcal{N}$ stores in the market.
+Each type of brokerage follows a standard percentage charge by $r_j$ where $j \in \{1, 2, \ldots, \mathcal{N}\}$ and they can not manipulate the percentage charge in each submarket.
+
+We can assume that there are $M$ number of communities in the market, and each market has $\kappa_i, i \in \{1, \ldots, M\}$ number of houses listed.
+Assume that the sellers are indifferent among the brokerages and therefore, their chossing is only dependent on the proportion of stores in the market.
+We can denote the number of two types of brokerages by $\mathcal{B}_{1, i}$ and $B_{2, i}$, respectively and therefore, the number of houses listed in the brokerage $j$ is $\kappa_{i} \times \frac{\mathcal{B}_{i, i}}{\mathcal{B}_{i, 1} + \mathcal{B}_{i, 2}}$.
+We can assume that the price of the house is determined by the hedonic pricing model from various confounding factors that are determined by the community and unique characteristics of the housing, and we can denote it as $P_i$ that can be ranked and distributed over the range $[\underline{P}_i, \overline{P}_i]$.
+Sellers have a reservation price $\tilde{P}_i$ over the house they sell.
+
+The brokerages have the same positive cost function denoted as $C(\cdot)$ where $\frac{\partial C(\cdot)}{\partial \mathcal{B}_{j}} > 0$ and $\frac{\partial C^2(\cdot)}{\partial \mathcal{B}_{j}^2} > 0$ where $j \in \{1, 2, \ldots, \mathcal{N}\}$.
+The intuition is that because of the marginal cost of the platform is $0$, when considering the cost of opening additional stores in the market, the brokerage does not incur that cost into consideration and therefore, the cost function is equal for both types of stores.
+Moreover, the marginal cost of opening additional stores is increasing, which is consistent with the real estate brokerage market because the more stores the brokerage opens, the administrative cost will increase.
+
+We can inherent from the previous literature that there are broad searchers and narrow searchers in the market, \citep{10.1257/aer.20141772}.
+Specifically, we can assume that there are $L^N_i$ narrow searches that are only searching for the community $i$ and let $L^B$ denote the set of broad searchers, defined as those individuals who consider a $\beta$ proportion of all available houses within their expansive search criteria.
+When $\beta = 1$ it means that they are searching for all the available houses in the whole city and $\beta < 1$ indicates a limited scope, possibly due to preferences or capacity constraints.
+Correspondingly, $L^B_i$ represents the subset of broad searchers within community $i$, and the expected number is given by $L^B_i = L^B \times \beta$.
+We can denote the buyers' utility of owning the house by $U_{i, j}$
+
+We can first focus on the naive searchers in the real estate market.
+These individuals are typically drawn to platforms based on the breadth of listings available.
+Specifically, the probability that a naive searcher will choose brokerage $j$ can be characterized by the principle of the two-sided market.
+This decision is influenced by the ratio of the number of houses listed by brokerage $j$ to the total number of houses listed within community $i$.
+This model aligns with the framework proposed by \citep{Armstrong2006}, where market attractiveness is proportional to the available inventory a brokerage offers relative to the community aggregate:
+
+\begin{equation}
+  N_{i, j} = L^N_i \times \frac{\mathcal{B}_{i, j}}{\sum_{j^\prime=1}^{\mathcal{N}}\mathcal{B}_{i, j^\prime}}. \label{eq:naive_prob}
+\end{equation}
+
+However, the broad searchers in the market are attracted to the platform by the networking because they are searching for all the communities in the market, and buyers have different preferences for brokerages based on their online presence, reputation and other factors, with private information $\theta_{b, j}$ representing the buyer's preference for brokerage $j$.
+
+\begin{equation}
+  B_i = L^B_i \times \alpha_j \times \frac{\mathcal{B}_{i, j} \times \theta_{b, j}}{\sum_{j^\prime=1}^{\mathcal{N}}\mathcal{B}_{i, j^\prime} \times \theta_{b, j^\prime}} \label{eq:broad_prob}
+\end{equation}
+
+and we can release this assumption later to make the customers have private preference towards each type of brokerage and the brokerages can not observe this pattern.
+Combinning \eqref{eq:naive_prob} and \eqref{eq:broad_prob}, we can get the total number of customers in the community $i$ and the brokerage $j$ is:
+
+\begin{equation}
+  L_{i, j} = N_{i, j} + B_{i, j} = (L^N_i + L_B \times \beta \times \alpha_j) \times \frac{\mathcal{B}_{i, j} \times \theta_{b, j}}{\sum_{j^\prime=1}^{\mathcal{N}}\mathcal{B}_{i, j^\prime} \times \theta_{b, j^\prime}}
+   \label{eq:total_prob}
+\end{equation}
+
+We can assume the probability of a successful match between buyers and sellers, which increases with the number of participants on the platform, as $\tau_{i, j} = f(\frac{\mathcal{B}_{i, j}}{\sum_{j^\prime=1}^{\mathcal{N}}\mathcal{B}_{i, j^\prime}})$ and the revenue for each brokerage $j$ in community $i$ can be calculated by considering the total number of transactions completed, which is the product of the number of customers handled by the brokerage and the probability of transaction completion.
+
+\begin{equation}
+  R_{i, j} = \tau_{i, j} \times L_{i, j} \times P_i \times r_j \label{eq:revenue}
+\end{equation}
+
+and the correspondingly, the total profit for the brokerage $j$ in the community $i$ is:
+
+\begin{equation}
+  \Pi_{i, j} = R_{i, j} - C(\mathcal{B}_{i, j}) \label{eq:profit}
+\end{equation}
+
+The consumer surplus is then: $CS = \sum_{i=1}^M \sum_{j=1}^{\mathcal{N}} \int_0^{L_{i, j}} (U_{i, j} - P_i) dx$.
+
+% \begin{assumption}[homogenous brokerage]
+%  The brokerage $1$'s network effect is greater than other brokerages in the market and assume that the small brokerages (Type $2$ to $\mathcal{N}$) are homogenous and they have the same network effect in the market, i.e., $\alpha_2 = \ldots = \alpha_{\mathcal{N}} = \alpha_s$, where $\alpha_s$ is the network effect for small brokerages.
+We have $\alpah_1 > \alpha_s$.
+% \end{assumption}
+
+\begin{proposition}[brokerage $1$'s optimal choice]
+  In equilibrium, the market share of Brokerage 1 (Type 1) is greater than its proportion of the number of stores, and the optimal brokerage fee charged by Brokerage 1 is higher than that charged by other brokerages.
+\end{proposition}
+
+\begin{proof}
+  The total number of customers for Brokerage 1 in community $i$ is given by $L_{i, 1}$ and the total number of stores is $L_{i}$:
+
+  \begin{equation}
+    \text{Market Share}_{i, 1} = \frac{L_{i, 1}}{L_i}
+  \end{equation}
+
+  Since $\alpha_1 > \alpha_s$ and assuming $\theta_{b, 1} \geq \theta_{b, j}$ and Brokerage 1 will attract a higher proportion of broad searchers $L^B$, resulting in a larger market share.
+Thus, in equilibrium, the market share of Brokerage 1 is greater than its proportion of the number of stores.
+
+  To maximize the profit, brokerage $1$ will change $r_1$ such that: $\frac{\partial \Pi_{i, 1}}{\partial r_1} = \frac{\partial R_{i, 1}}{\partial r_1} - \frac{\partial C(\mathcal{B}_{i, 1})}{\partial r_{1}} = 0$.
+Since $\tau_{i, 1}$ and $L_{i, 1}$ are higher for brokerage $1$ due to the stronger network effect, the optimal $r_1$ will be higher compared to the fees charged by other brokerages, $r_j$ for $j \neq 1$.
+\end{proof}
+
+In the following proposition, we will derive the total surplus of the model.
+
+This model is not good right now because there is no better way to conduct welfare analysis.
+
+% now consider the two-period entry model now consider the case of the first period there is an equilibrium with all other broekrages but in the next period there is an entry of the first brokerage then derive the new equilibrium of the market and conduct the wellfare analysis in this case
+
+\begin{proposition}[two-period entry model]
+
+\end{proposition}
+
+% where $N^e(B_{1, i})$ is a function representing the network effects, and is modeled as $N^e(B_{1, i}) = 1 + \alpha \log(1 + B_{1, i})$ where $\alpha$ is a parameter that quantifies the strength of network effects and the logarithmic form captures diminishing returns to scale as the number of brokerages increases.
+The revenue for each brokerage type $j$ in community $i$ is proportional to the number of houses they sell, which depends on the number of customers they attract:
+
+% where $N_{i, j, t}$ is the number of customers selecting type $j$ brokerage in community $i$ at time period $t$, estimated by:
+
+% \begin{equation}
+%  N_{i, j, t} = \lambda_i p_{i, j, t}
+%\end{equation}
+
+%and $\lambda_i$ is the appropriate part of $\lambda$ that arrives in community $i$.
+
+%give me a mathematical economics model characterizing the partial equilibrium of real estate broekrage and the competitive market where there are two types of brokerages denoted 1 if the brokerage is the large brokerage that it can communicate with other stores in different regions of the same type 1 brokerage, and denote 2 if it is small brokerage that it can not communicate with the other brokerages in the market
+
+% The first proposition is that the charging fee should be higher comparing with type $2$ brokerage.
+
+% The second proposition is that the number of stores in high popular regions should be higher in the number of stores and they are more likely to form a network effect.
+
+% The third proposition is the introduction of the platform should increase the number of transactions and the number of stores in the market.
+
+% The fourth proposition is that the entry of the large brokerage can increase the transaction number and the number of stores in the market.
+
+% The fifth proposition should be the fact that when there is negative shock to the customers, the number of transactions and the number of stores should decrease and the number of brokerage fee should decrease in the long run (which can be modeled using graph or simulation).
+
+% The sixth proposition should be the fact that before the increase of the
+
+We can examine the following two effects:
+
+\begin{itemize}
+  \item The real estate brokerage's network effect where the brokerages are more likely to form a edge between each other (this is demonstrated in the ACN's brokerage network model)
+  \item The partial effect of the network effect is not characterized by the price level changes or the brokerage fee increase.
+  \item The network effect should be demonstrated by the increase in the number of transactions and the number of the stores within given radius comparing with the total number of houses in this market.
+\end{itemize}

### 2024-06-06 analysis/quantile-regression.R

@@ -1,0 +1,37 @@
+library(quantreg)
+library(lfe)
+library(haven)
+getwd()
+
+setwd('E:/umich/RealEstateBrokerage-main')
+data <- read_dta("for-analysis.dta")
+
+# define a set of control variables
+
+hedonic_control <- c("jiadian", "kind", "hotel", "shop_mall", "museum", "old", "ktv", "mid", "prim", "west_food", "super", "sub", "park")
+transaction_control <- c("area", "bedroom", "toilet", "house_age", "floor_level", "green_ratio", "total_building", "total_floor_number", "living_room", "elevator_ratio", "kitchen", "floor_ratio", "total_resident")
+region_control <- c("pm25", "pop", "light")
+brokerage_control <- c("non_online_effect", "ln_nego_changes", "ln_negotiation_period")
+lag_hedonic_control <- paste0(hedonic_control, "_hedonic_lag")
+
+dependent_variable <- c("yearx2_density", "yearx3_density", "yearx4_density", "yearx5_density", "yearx6_density", "yearx7_density", "broker_410", "ln_end_price", "ln_watch_people", "ln_watch_time")
+control_variables <- c(brokerage_control, lag_hedonic_control, transaction_control, region_control)
+
+all_vars <- c("ln_income", dependent_variable, control_variables, "year", "bs_code", "id")
+data_subset <- data[complete.cases(data[all_vars]), ]
+# regression on the dependent variables to generate the residual
+model_felm <- felm(as.formula(paste("ln_income ~", paste(dependent_variable, collapse = " + "), "+", paste(control_variables, collapse = " + "), "| year + bs_code + id")), data = data_subset)
+data_subset$resid <- residuals(model_felm)
+
+# save the residual and conduct the quantile model
+key_vars <- c("yearx2_density", "yearx3_density", "yearx4_density", "yearx5_density", "yearx6_density", "yearx7_density")
+quantile_results <- list()
+
+for (var in key_vars) {
+    formula <- as.formula(paste(var, "~ avg_watch_time"))
+    quantile_model <- rq(formula, data = data_subset, tau = seq(0.1, 0.9, by = 0.1))
+    quantile_results[[var]] <- summary(quantile_model)
+}
+
+
+quantile_results

### 2024-06-07 result_tables/summary_statistics.tex
modified:   analysis/final_analysis.do 	modified:   figures/did_1.pdf 	modified:   figures/did_2.pdf 	modified:   figures/did_3.pdf 	deleted:    manuscript/main.aux 	deleted:    manuscript/main.blg 	modified:   manuscript/main.fdb_latexmk 	deleted:    manuscript/main.fls 	deleted:    manuscript/main.log 	deleted:    manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	modified:   result_tables/difference_in_difference.tex 	modified:   result_tables/dynamic.tex 	modified:   result_tables/entry_effect.tex 	new file:   resu

--- 2024-05-04 result_tables/summary_statistics.tex
@@
-\begin{tabular}{p{5cm}lllll}
+\begin{tabular}{llllll}
 \toprule
@@
 The time it takes before a deal is made. & 13.59 & 14.56 & 17.09 & 17.50 & -3.501 (-49.823***) \\
-price\_concession & -0.0367 & 0.0318 & -0.0351 & 0.0294 & -0.00200 (-12.088***) \\
+price_concession & -0.0367 & 0.0318 & -0.0351 & 0.0294 & -0.00200 (-12.088***) \\
 percentage of lianjia to all brokerages & 0 & 0 & 0.206 & 0.166 & -0.206 (-384.429***) \\

### 2024-06-08 manuscript/main.tex
modified:   analysis/final_analysis.do 	modified:   figures/did_1.pdf 	modified:   figures/did_2.pdf 	modified:   figures/did_3.pdf 	deleted:    manuscript/main.aux 	deleted:    manuscript/main.blg 	modified:   manuscript/main.fdb_latexmk 	deleted:    manuscript/main.fls 	deleted:    manuscript/main.log 	deleted:    manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	modified:   result_tables/difference_in_difference.tex 	modified:   result_tables/dynamic.tex 	modified:   result_tables/entry_effect.tex 	new file:   resu

@@
 
-\title{ \vspace*{-2.5cm} \hspace*{-0.5cm}Evaluating the Impact of Offline Store Clusters in the Age of Platforms: Evidence from China's Metropolitan Real Estate Market \footnote{
+\title{ \vspace*{-2.5cm} \hspace*{-0.5cm}Evaluating the Impact of Offline Store Clusters under the Consolidation: Evidence from China's Metropolitan Real Estate Market \footnote{
 The preliminary version was entitled "Property brokerage, Partial monopoly and Housing market" and was presented at The 1st Summer Meeting in Urban Economics, China.
@@
 
-\textbf{Now I think about how to do this, the first task is to write completely the model and estimation of the offline and platform's effect with offline is the brokerage's offline store's entry and the onlien is the platofmrization strategy.}
-
 \section{Introduction \label{sec:introduction}}
@@
 \noindent
+
+% Brokerage consolidation refers to the process by which a larger real estate brokerage firm integrates multiple smaller brokerage firms into a single, unified platform.
 

### 2024-06-08 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.blg 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

@@
 
-\title{ \vspace*{-2.5cm} \hspace*{-0.5cm}Evaluating the Impact of Offline Store Clusters under the Consolidation: Evidence from China's Metropolitan Real Estate Market \footnote{
+\title{ \vspace*{-2.5cm} \hspace*{-0.5cm}Offline Store Expansion and Platform Consolidation: Evidence from major cities in China \footnote{
 The preliminary version was entitled "Property brokerage, Partial monopoly and Housing market" and was presented at The 1st Summer Meeting in Urban Economics, China.
@@
 \begin{abstract}
-    \noindent This study examines the impact of offline store expansion by Lianjia, China's leading real estate brokerage, in the context of online platform development.
-By analyzing micro-level transactions of second-hand houses in ten major Chinese cities from 2016 to 2022, the study explores how the strategic clustering of offline stores enhances Lianjia's influence in local communities and facilitates the creation of an extensive franchise network.
-This study first conducts a regression discontinuity (RD) design to quantify the optimal influence radius of these stores on housing transactions.
-By incorporating the optimal influence radius, this study examines the exogenous shock of Lianjia's market entry to identify a significant increase in transaction revenues.
-However, this effect is diminished during Covid-19 periods.
-In addition, the paper examines the impact of Lianjia's ACN strategy on its platformization efforts and concludes that the effect is not only from the larger client base brought by the platform, but also from the information control by sharing information within the platform.
-This study provides valuable insights into the synergy between offline store expansion and online platform development, highlighting their importance in the evolving real estate brokerage market.
+    \noindent This study examines the impact of offline store expansion by Lianjia, China's leading real estate brokerage, within the framework of platform consolidation.
+By analyzing micro-level transactions of second-hand houses in ten major Chinese cities from 2016 to 2022, the research investigates how the transaction patterns of traditional brokerages, characterized by strategic clustering of offline stores, transition towards online consolidation, thereby facilitating the development of an extensive franchise network.
+Utilizing a regression discontinuity (RD) design, the study quantifies the optimal influence radius of these stores on housing transactions.
+Incorporating this optimal influence radius, the study further investigates the exogenous shock of Lianjia's market entry, identifying a significant increase in transaction revenues before the Covid-19.
+However, this effect is attenuated during the Covid-19 period due to remote work and other restrictive policies implemented by the Chinese government.
+Additionally, the paper explores the impact of Lianjia's Agent Cooperation Network (ACN) strategy on its platform consolidation effect, concluding that this strategy enhances Lianjia's revenue generation and facilitates transactions.
+This study provides valuable insights into the synergy between offline store expansion and online platform development, highlighting future trajectories in the evolving real estate brokerage market.
   \end{abstract}
@@
 
-% Brokerage consolidation refers to the process by which a larger real estate brokerage firm integrates multiple smaller brokerage firms into a single, unified platform.
-
 In the real estate market, transaction cost is a critical factor for both buyers and sellers.
 Minimizing these costs has made the selection of competent real estate agencies a significant priority for both parties.
+Real estate brokers not only help in reducing transaction costs but also provide essential market information, negotiation support, and legal assistance, thereby ensuring smoother and more efficient transactions.
 Especially in the context of China's burgeoning real estate market, brokerage firms are assuming an increasingly important role in facilitating the communication channel between buyers and sellers \citep{glaeser_real_2017}.
-In addition, technological advancements coupled with the proliferation of dominant platforms have created a trend toward greater monopolization within the real estate brokerage industry, rather than fostering a competitive environment.
-Therefore, it is imperative to analytically examine the expansion strategies of Chinese real estate agencies, especially in the context of escalating platform-based monopolization.
+Their expertise and local market knowledge have become indispensable in navigating the complex real estate landscape.
 
-Lianjia is the largest real estate brokerage in China that has platformed real estate transactions by establishing the Beke platform.
-They can expand rapidly by the expansion of offline stores on a large scale while sharing resources by leveraging the advantages of their platform.
-Beke has also established an original Agent Cooperate Network (ACN) that integrates and shares the content of its multiple subsidiaries to realize multiple revenue models at the same time.\footnote{The ACN model breaks down the entire process of transaction into parts, each of which is handled by a single person or store, including seller-side: finding sellers, maintaining the listing of the house, commissioning and communicating, and buyer-side: Finding clients, matching homes and clients, facilitating transactions, and providing financial services assistance.} Through the ACN model, Lianjia transforms the internal competition within the system into the overall competitiveness of the system, improving the reputation and influence of the entire brand and gaining a more favorable position in the marketplace.
-For example, according to the data of AutoNavi Map and CREIS data: In 2020, the number of real estate agent stores in the main urban area of Chengdu City that accessed Beke Housing's platform accounted for about 20\%, but the market share reached 73.98\%.
+The Chinese real estate brokerage market has long been characterized by intense competition among offline stores, with multiple brokerages establishing a presence within the same community to vie for clients.
+However, the advent of online platforms has dramatically reshaped the dynamics of real estate transactions.
+Brokerage consolidation, a process where larger firms absorb smaller ones into a unified platform, is emerging as a transformative trend, redefining how properties are bought and sold across China.
 
-The reason why Lianjia does not have such a high proportion of offline stores in the market but has an absolute dominant position in metropolis can be explained by the mechanism of China's second-hand real estate market.
-In the China's real estate market, brokerages still operate on a bilateral agency model, where sellers need to choose the agency that can help them sell their home in the fastest time and for the highest price possible for the transaction.
-However, due to the asymmetric information characteristics of the real estate market, sellers must find a way to inform buyers and match buyers.
-In a fully competitive market, sellers would be indifferent in choosing real estate agents.
-Nevertheless, as the market trends towards increased monopolization, sellers encounter a dichotomous choice: opt for a larger brokerage firm, which, albeit commanding higher fees, possesses the capacity to expedite housing transactions, or engage with a smaller brokerage, which presents a contrasting scenario of lower fees yet potentially less efficient transaction facilitation.
+Lianjia, the largest real estate brokerage in China, has revolutionized real estate transactions through the establishment of the Beke platform.
+This platform enables rapid expansion by integrating offline stores on a large scale while leveraging the advantages of resource sharing.
+However, prior to 2018, the platform Beke primarily focused on facilitating listings from Lianjia's offline stores and aimed to attract buyers from the market.
+However, in 2018, Beke established a new strategy named Agent Cooperate Network (ACN), which integrates and shares the content across its multiple subsidiaries to realize multiple revenue models simultaneously.\footnote{The ACN model disaggregates the transaction process into specialized tasks handled by individual agents or stores.
+These tasks include seller-side activities such as sourcing sellers, maintaining property listings, commission negotiations, and buyer-side activities like client acquisition, property-client matching, transaction facilitation, and financial services assistance.}
 
-While it is possible for sellers to adopt a multi-homing strategy, this approach is suboptimal for several reasons.
-First, the exclusivity of contracts between sellers and agents precludes the adoption of a multi-homing strategy.
-Second, although sellers can list their houses with multiple brokerages, smaller brokerages often lack a broad enough target client base, which is not very helpful in selling the homes.
-Third, connecting with multiple brokers simultaneously can make each brokers feel that they are in a difficult position to compete for that house, which reduces their incentive to be proactive in their efforts.
-Finally, while the variance in service costs between agencies is acknowledged, these costs are trivial compared to the value of the property and are more related to the risk associated with holding a financial asset.
-Consequently, risk-averse individuals are inclined to choose an agency that provides a guaranteed level of service.
-Due to the mechanism of online promotion and offline transaction in the real estate brokerage industry, the nature of the brokerage's services in the offline stores is of high value for its influence on the client side.
-This is the principle behind Lianjia's choice to open stores in the neighborhoods of each target community.
-By opening a wide range of stores around the communities, the brokerage attracts sellers to list their houses, and attracts buyers in the market through its extensive platform sources, thus obtaining a higher number of transaction and income from the transaction.
+Through the ACN model, Lianjia transforms internal competition within the system into overall system competitiveness, thereby enhancing the brand's reputation and market influence.
+More importantly, this strategic allows Lianjia to cooperate with other previously competitors by consolidating resources and forms a consolidation.
+For instance, data from AutoNavi Map and CREIS indicate that in 2020, although only about 20\% of real estate agent stores in the main urban area of Chengdu City are Lianjia's offline stores, these stores achieved a market share of 73.98\%.
+This remarkable market penetration underscores the efficacy of Beke's integrated platform and ACN model in dominating the real estate brokerage landscape.
+The Table \ref{tab:precise_proportion_contraction} shows the comparision of the market share of Lianjia and the share of the number of stores in the market.
 
-In this paper, we empirically test this hypothesis that when brokerages are able to expand their offline stores' coverage in the communities, the brokerages can earn higher income in this community, and we decompose the channels into two parts.
+What's more, in the China's real estate market, brokerages still operate on a bilateral agency model, where sellers need to choose the agency that can help them sell their home in the fastest time and for the highest price possible for the transaction.
+However, due to the asymmetric information inherent in the real estate market, sellers face challenges in effectively informing and matching with potential buyers.
+n a perfectly competitive market, sellers would be indifferent in their choice of real estate agents.
+Nonetheless, as the market trends toward increased monopolization, sellers confront a dichotomous decision: engage a larger brokerage firm, which, despite higher fees, offers the potential for expedited transactions, or opt for a smaller brokerage with lower fees but potentially less efficient transaction facilitation.
+
+While sellers may consider a multi-homing strategy—listing their property with multiple brokerages—this approach is suboptimal for several reasons.
+Firstly, the exclusivity of contracts between sellers and agents often precludes the adoption of a multi-homing strategy.
+Secondly, although sellers can list their properties with multiple brokerages, smaller agencies frequently lack a sufficiently broad client base, limiting their effectiveness in selling homes.Thirdly, engaging multiple brokers simultaneously can lead to reduced incentives among agents, as they perceive competition for the same property, diminishing their proactive efforts.
+Finally, while service cost variations between agencies are acknowledged, these costs are minor compared to the property's value and are more closely related to the risks associated with holding a financial asset.
+Consequently, risk-averse sellers are inclined to choose an agency that provides a guaranteed level of service.
+
+Given the dual nature of online promotion and offline transactions in the real estate brokerage industry, the quality of offline services is crucial for influencing client decisions.
+This principle underpins Lianjia's strategy of establishing numerous stores within targeted communities.
+By opening a wide range of stores in various neighborhoods and adopting a downstream consolidation model through platform design, the brokerage effectively attracts sellers to list their properties and buyers through its extensive platform resources.
+This strategy not only enhances transaction volume but also increases income derived from these transactions.
+
+In this paper, we empirically estimate the offline stores' , the brokerages can earn higher income in this community, and we decompose the channels into two parts.
 On the one hand, is that when brokers have better control over listing information by opening additional offline stores, they are more likely to attract more sellers to choose them, which will then benefited by the online platform effect to extract more buyers and more likely to complete a transaction.

### 2024-06-08 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

@@
 
-In this paper, we empirically estimate the offline stores' , the brokerages can earn higher income in this community, and we decompose the channels into two parts.
-On the one hand, is that when brokers have better control over listing information by opening additional offline stores, they are more likely to attract more sellers to choose them, which will then benefited by the online platform effect to extract more buyers and more likely to complete a transaction.
-On the other hand, when offline stores are closer to the communities, they are more likely to make a house tour to help the buyers to get more information on the house, and therefore, be more likely to complete a transaction.
-During the Covid-19 pandemic period, the Chinese government restricts the number, and in this period, we find that the number of houses tour is not significantly affected by the number of offline stores, but the listing information significantly decreases because the brokerages are difficult to interact with the sellers and then failure to maintain the information advantage during this period.
+In this paper, we empirically estimate the effects of offline store clustering and online platform consolidation in China's second-hand real estate market.
+Utilizing micro-level transaction data, we construct our research sample by aggregating information at the neighborhood level.
+We employ a regression discontinuity (RD) design to identify the optimal influential radius of offline stores on neighborhood transactions, finding that this radius corresponds to a brokerage's five-minute walk service distance.
+Subsequently, we apply a difference-in-difference (DID) estimation method to evaluate the exogenous impact of Lianjia's market entry on local segments.
+This exogenous effect captures the clustering impact of offline real estate brokerage stores.
+Our results indicate that Lianjia's offline stores significantly enhance transaction revenues, although this effect diminishes during and after the COVID-19 period.
 
-Apart from directly measuring the dynamic effect of Lianjia's offline stores to transaction, we use Lianjia's entry into the local segmented market as an exogenous shock to test the effect of entry on transaction characteristics.
-The results indicate that when Lianjia enters the market, revenues increase significantly, but this is not due to the larger clinic-based, but due to the greater information control brought by the newly opened store.
-Moreover, during pandemic periods, we find that all effects are diminished, meaning that during pandemic periods, both the client-based effect and the housing information are diminished.
-Simultaneously, our study also examines the impact of Lianjia's ACN strategy on the real estate market, focusing on its effect on offline store operations.
-Through this exogenous shock, we find that post-2018, the ACN significantly boosts revenue and alters consumer behaviors, especially in terms of price concessions and house tours.
-Also, contrary to the previous effect, the effects are diminished during pandemic periods.
-The findings highlight the resilience of physical stores during a global epidemic and underscore the necessity for a synergistic evolution of online and offline strategies.
+To assess the consolidation effect of the online platform, we treat the year Lianjia implemented the Agent Cooperate Network (ACN) strategy as an exogenous shock to the market.
+Our findings reveal that this strategy substantially boosts revenues and alters consumer behaviors, particularly in the number of house tours facilitated by the brokerage.
+These results underscore the necessity for a synergistic evolution of online and offline strategies in the real estate brokerage market.
+Furthermore, they indicate that the online consolidation effect is becoming increasingly significant relative to the offline clustering effect.
+
+Our research has several implications.
+Firstly, it indicates that with the advent of new technologies, the online consolidation effect is becoming increasingly important for real estate companies.
+This shift underscores the need for firms to enhance their digital strategies to remain competitive.
+Secondly, our findings have broader significance for other industries where online consolidation can potentially replace traditional offline clustering.
+For example, in the retail sector, online marketplaces such as Alibaba in China have significantly outpaced physical stores by consolidating various vendors into a single, accessible platform.
+
+By examining these dynamics, our research contributes to a deeper understanding of the evolving landscape of real estate brokerage in China.
+It provides valuable insights for policymakers and industry stakeholders aiming to enhance market efficiency and competitiveness.
+As the online consolidation effect continues to grow, our findings highlight the importance of adapting to this trend and evolving strategies accordingly.
+Specifically, transitioning from a bilateral brokerage model to a model where buyer and seller agencies are separated could be crucial for sustaining a competitive advantage in the real estate brokerage market.
+This strategic shift entails leveraging online platforms to integrate services and enhance transaction efficiency, thereby benefiting both consumers and firms.
+By disentangling the roles of buyer and seller agents, the market can reduce conflicts of interest, increase transparency, and improve overall market efficiency.
+This alignment with economic principles of specialization and efficiency further underscores the potential for significant gains in consumer welfare and firm profitability.
 
@@
 Section \ref{sec:literature_review} reviews the literature that is related to our research.
-Section \ref{sec:data} describes the data and summarizes the statistical evidence.
-Section \ref{sec:theoretical_model} presents a theoretical model that incoporate the analysis.
+Section \ref{sec:data} describes the study background and the data source.
+Section \ref{sec:statistical} describes the statistical summary and other relevant information.
 Section \ref{sec:mechanism_design} presents the main result of our finding.

### 2024-06-09 manuscript/main.tex
modified:   analysis/final_analysis.do 	modified:   manuscript/main.aux 	modified:   manuscript/main.bbl 	modified:   manuscript/main.blg 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	modified:   manuscript/our-cites.bib 	modified:   result_tables/entry_effect_hetero.tex 	modified:   result_tables/formulate_the_tables.ipynb 	modified:   result_tables/heter_platform_did.tex 	modified:   result_tab

@@
 Section \ref{sec:literature_review} reviews the literature that is related to our research.
-Section \ref{sec:data} describes the study background and the data source.
-Section \ref{sec:statistical} describes the statistical summary and other relevant information.
+Section \ref{sec:data} describes the study background and statistical summary.
 Section \ref{sec:mechanism_design} presents the main result of our finding.
-Finally, Section \ref{sec:conclusion} concludes.
+Finally, Section \ref{sec:conclusion} contains the discussion and concludes.
 
@@
 
-Finally, the overall market influence of real estate intermediaries is multi-faceted.
-Utilizing a model predicated on perfect competition, \citet{williams_agency_1998} illustrates that an excessive entry of brokers into the market can surpass the optimal allocation, reducing social welfare.
-This is further evidenced by studies indicating that a surge in broker numbers can depress house prices and shorten transaction cycles \citep{https://doi.org/10.1002/jae.2891}.
-Additionally, \citet{qu_identifying_2021-1} highlights how broker commissions play a moderating role in disseminating information during transactions, thereby facilitating more efficient home sales.
+Moreover, the overall market influence of real estate intermediaries is multifaceted.
+Utilizing a model predicated on perfect competition, \citet{williams_agency_1998} illustrates that excessive entry of brokers into the market can surpass the optimal allocation, thereby reducing social welfare.
+This is corroborated by studies indicating that an increase in the number of brokers can depress house prices and shorten transaction cycles \citep{https://doi.org/10.1002/jae.2891}.
+Additionally, \citet{qu_identifying_2021-1} highlights the moderating role of broker commissions in disseminating information during transactions, facilitating more efficient home sales.
 Other related literature includes \citep{doi:10.1080/10527001.2021.2016340, doi:10.1080/10835547.1996.12090852}.
+
+Finally, the concept of the platform as a "two-sided market" or kind of intermediates that connects the buyer side and seller side digitally, \citep{10.1162/154247603322493212, Langley_Leyshon_2017}.
+Despite the significant attention given to online platforms, there is a lack of systematic analysis on the impact of offline stores of online platforms on market performance or on real estate brokerage.
+Therefore, this paper aims to fill this gap by examining the influence of offline stores associated with online platforms on the real estate market.
 
@@
 
+In the Appendix Table \ref{tab:} we also report the results of the robustness check of the dynamic model. The results show that the dynamic model
+
 % There should be a model like: Police brutality, law enforcement, and crime: Evidence from Chicago
@@
 
+To check the robustness of the entry effect, we also conduct the
+
+\begin{table}
+  \begin{center}
+    \begin{scriptsize}
+      \caption{Robustness Check of Entry Effect}
+      \label{tab:entry_effect_robustness}
+      \input{../result_tables/entry_effect_hetero.tex}
+
+    Note: we omit all the control variables in the regression model, and detailed descriptions can be seen from Table \ref{tab:statistical}.
+    \end{scriptsize}
+  \end{center}
+\end{table}
+
 \subsection{Is Lianjia's ACN strategy profitable?} \label{subsec:acn_strategy}
@@
 
+\begin{table}
+  \begin{center}
+    \begin{scriptsize}
+      \caption{Robustness Check of Online Consolidation Effect}
+      \label{tab:heter_platform_did}
+      \input{../result_tables/heter_platform_did.tex}
+
+    Note: we omit all the control variables in the regression model, and detailed descriptions can be seen from Table \ref{tab:statistical}.
+    \end{scriptsize}
+  \end{center}
+\end{table}
+
 \section{Conclusion and Discussion} \label{sec:conclusion}
@@
 \input{../figures/distribution_of_hp_and_broker.tex}
+
+\begin{table}[H]
+  \begin{center}
+    \begin{scriptsize}
+    \caption{Robustness Check By HHI Index}
+    \label{tab:sylized_fact_hetero_hhi}
+    \input{../result_tables/robust_hhi.tex}
+
+    \end{scriptsize}
+  \end{center}
+\end{table}
+
+\begin{table}[H]
+  \begin{center}
+    \begin{scriptsize}
+    \caption{Robustness Check By Market Maturity Index}
+    \label{tab:sylized_fact_hetero_mature}
+    \input{../result_tables/robust_mature.tex}
+
+    \end{scriptsize}
+  \end{center}
+\end{table}
 

### 2024-06-09 analysis/RD design analysis.Rmd
modified:   analysis/RD design analysis.Rmd 	new file:   analysis/RD-design-analysis.log 	new file:   analysis/RD-design-analysis.tex 	new file:   analysis/RD_Plot_1st_Order.pdf 	new file:   analysis/RD_Plot_2nd_Order.pdf 	new file:   analysis/RD_Plot_3rd_Order.pdf 	new file:   analysis/donut_robust.tex 	new file:   archive/RD design archived.Rmd 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	new

@@
 library(haven)
+library(rdd)
 library(ggplot2)
@@
 library(plm)
+library(xtable)
 library(pander) # this is for table showing
 library(latex2exp) # this is to export it
+setwd("E:/umich/RealEstateBrokerage-main")
+# need to place data on the base directory
+data <- read_dta("template.dta")
+working_directory <-"E:/umich/RealEstateBrokerage"
 ```
@@
 ```{r}
-# need to place data on the base directory
-data <- read_dta("../template.dta")
 panel_data <- pdata.frame(data, index = c("id", "year"))
@@
 ```{r}
-result <- rdrobust(y = panel_data$ln_income, x = panel_data$nearest_store_distances, 
-                   c = 0.41, covs = panel_data[, control_variables],
-                   p = 1) # first using default clustering
-```
-
-```{r}
-result
-```
-
-```{r}
-pander(cbind(result$coef, result$pv))
-```
-
-```{r}
-result <- rdrobust(y = panel_data$ln_income, x = panel_data$nearest_store_distances, 
-                   c = 0.41,
-                   p = 1) # first using default clustering
-```
-
-```{r}
-result
-```
-
-```{r}
-pander(cbind(result$coef, result$pv))
-```
-
-```{r}
-result
-```
-
-note that the figure only shows points that are within the bandwidth, the whole points are shown in Appendix of the paper.
-
-```{r}
-h = 0.095
+h = 0.066
 cutoff = 0.41
@@
 
-par(mfrow=c(3,1))
+# Export the first RD plot to its own PDF file
+pdf("RD_Plot_1st_Order.pdf", width = 8, height = 4) # Adjust the width and height as needed
 rdplot(y = filtered_data$ln_income, 
@@
        c = cutoff, nbins = 40, p = 1,
-       title = "RD-plot",
-       x.label = "nearest distance to lianjia's stores",
-       y.label = "lianjia's income in the community")
+       title = "RD-plot 1st order polynomial",
+       x.label = "Nearest distance to Lianjia's stores",
+       y.label = "Log of income in the community")
+dev.off() # Close the PDF device
 
+# Export the second RD plot to its own PDF file
+pdf("RD_Plot_2nd_Order.pdf", width = 8, height = 4) # Adjust the width and height as needed
 rdplot(y = filtered_data$ln_income, 
@@
        c = cutoff, nbins = 40, p = 2,
-       title = "RD-plot",
-       x.label = "nearest distance to lianjia's stores",
-       y.label = "lianjia's income in the community")
+       title = "RD-plot 2nd order polynomial",
+       x.label = "Nearest distance to Lianjia's stores",
+       y.label = "Log of income in the community")
+dev.off() # Close the PDF device
 
+# Export the third RD plot to its own PDF file
+pdf("RD_Plot_3rd_Order.pdf", width = 8, height = 4) # Adjust the width and height as needed
 rdplot(y = filtered_data$ln_income, 
@@
        c = cutoff, nbins = 40, p = 3,
-       title = "RD-plot",
-       x.label = "nearest distance to lianjia's stores",
-       y.label = "lianjia's income in the community")
+       title = "RD-plot 3rd order polynomial",
+       x.label = "Nearest distance to Lianjia's stores",
+       y.label = "Log of income in the community")
+dev.off() # Close the PDF device
 ```
 
-checkings:
+```{r}
+bw_methods <- c("mserd", "cerrd")
+kernel_list <- c("uniform", "triangular")
+results_list <- list()
+counter <- 1
+for (bw_method in bw_methods) {
+    for (kernel_in in kernel_list){
+        result <- rdrobust(y = panel_data$ln_income, x = panel_data$nearest_store_distances, 
+                     c = 0.41,
+                     p = 1, 
+                     bwselect = bw_method, kernel = kernel_in)
+
+        effective_obs <- sum(result$N_h)
+
+        results_list[[counter]] <- data.frame(
+        Method = bw_method,
+        Kernel = kernel_in,
+        Estimate = format(result$coef[1], digits = 3, scientific = FALSE),
+        SE = format(result$se[1], digits = 3, scientific = FALSE),
+        Z = format(result$z[1], digits = 3, scientific = FALSE),
+        PValue = format(result$pv[1], digits = 3, scientific = FALSE),
+        Bandwidth = format(result$bws[1], digits = 3, scientific = FALSE),
+        EffectiveObs = effective_obs
+    )
+        counter <- counter + 1
+    }
+}
+results <- do.call(rbind, results_list)
+latex_code <- print(xtable(results, 
+                           caption = "RD Estimates with Different Bandwidth Selection Methods and Kernels", 
+                           label = "tab:rd_bandwidth_kernel_results"), 
+                    include.rownames = FALSE, 
+                    type = "latex",
+                    print.results = FALSE)
+write(latex_code, file = paste(working_directory , "result_tables/rdd_result_summary.tex", sep='/'))
+print(results)
+```
+
+# checkings:
 
@@
 If they don’t, it strengthens the case for a true treatment effect.
+
+## Donut Hole Test
 
@@
 ```{r}
-donut_width <- 0.015
+perform_rd_analysis <- function(cutoff, donut_width, h, b) {
+  # select the data that we need
   panel_data_donut <- panel_data[!(panel_data$nearest_store_distances >= (cutoff - donut_width) & 
                                    panel_data$nearest_store_distances <= (cutoff + donut_width)),]
+  # run the rdrobust result
+  result_donut <- rdrobust(y = panel_data_donut$ln_income, 
+                           x = panel_data_donut$nearest_store_distances, 
+                           c = cutoff,
+                           p = 1, h = h, b = b)
+  # return the coefficient and the p value
+  conventional <- c("Conventional", result_donut$coef[1, 1], result_donut$se[1, 1], result_donut$pv[1, 1])
+  bias_corrected <- c("Bias-Corrected", result_donut$coef[2, 1], result_donut$se[2, 1], result_donut$pv[2, 1])
+  robust <- c("Robust", 
+              format(result_donut$coef[3, 1], digits = 3, scientific = FALSE), 
+              format(result_donut$se[3, 1], digits = 3, scientific = FALSE), 
+              format(result_donut$pv[3, 1], digits = 3, scientific = FALSE))
+
+  # combine the results
+  result_table <- rbind(conventional, bias_corrected, robust)
+  colnames(result_table) <- c("Method", "Coef", "SE", "p-value")
+  return(result_table)
+}
+
+cutoff = 0.41
+donut_widths <- c(0.01, 0.0125, 0.015, 0.0175, 0.02, 0.0225, 0.025)
+results <- list()
+
+for (donut in donut_widths) {
+  result <- perform_rd_analysis(cutoff, donut, 0.066, 0.135)
+  results[[paste0("donut_", donut)]] <- result
+}
+
+```
+
+```{r}
+perform_rd_analysis <- function(cutoff, donut_width, h, b) {
+  # select the data that we need
+  panel_data_donut <- panel_data[!(panel_data$nearest_store_distances >= (cutoff - donut_width) & 
+                                   panel_data$nearest_store_distances <= (cutoff + donut_width)),]
+  # run the rdrobust result
   result_donut <- rdrobust(y = panel_data_donut$ln_income, 
@@
                            c = cutoff, covs = panel_data_donut[, control_variables],
-                        p = 1, h = 0.095, b = 0.185)
-pander(cbind(result_donut$coef, result_donut$pv))
-print(result_donut)
+                           p = 1, h = h, b = b)
+  # return the coefficient and the p value
+  conventional <- c("Conventional", result_donut$coef[1, 1], result_donut$se[1, 1], result_donut$pv[1, 1])
+  bias_corrected <- c("Bias-Corrected", result_donut$coef[2, 1], result_donut$se[2, 1], result_donut$pv[2, 1])
+  robust <- c("Robust", 
+              format(result_donut$coef[3, 1], digits = 3, scientific = FALSE), 
+              format(result_donut$se[3, 1], digits = 3, scientific = FALSE), 
+              format(result_donut$pv[3, 1], digits = 3, scientific = FALSE))
+
+  # combine the results
+  result_table <- rbind(conventional, bias_corrected, robust)
+  colnames(result_table) <- c("Method", "Coef", "SE", "p-value")
+  return(result_table)
+}
+
+cutoff = 0.41
+donut_widths <- c(0.01, 0.0125, 0.015, 0.0175, 0.02, 0.0225, 0.025)
+results_with_control <- list()
+
+for (donut in donut_widths) {
+  result <- perform_rd_analysis(cutoff, donut, 0.066, 0.135)
+  results_with_control[[paste0("donut_", donut)]] <- result
+}
 ```
@@
 ```{r}
+# with controls
+combined_results_with_control <- do.call(rbind, lapply(names(results_with_control), function(donut) {
+  result <- results_with_control[[donut]]
+  robust_result <- result[result[, "Method"] == "Robust", ]
+  data.frame(Donut_Width = donut, Method = robust_result[1], Coef = robust_result[2], SE = robust_result[3], p_value = robust_result[4])
+}))
+colnames(combined_results_with_control) <- c("Donut Width", "Method", "Coef", "SE", "p-value")
 
-library(rdd)
+# without controls
+combined_results <- do.call(rbind, lapply(names(results), function(donut) {
+  result <- results[[donut]]
+  robust_result <- result[result[, "Method"] == "Robust", ]
+  data.frame(Donut_Width = donut, Method = robust_result[1], Coef = robust_result[2], SE = robust_result[3], p_value = robust_result[4])
+}))
+colnames(combined_results) <- c("Donut Width", "Method", "Coef", "SE", "p-value")
 
+merged_results <- merge(combined_results_with_control, combined_results, by = c("Donut Width", "Method"))
+merged_results_df <- as.data.frame(merged_results)
+
+colnames(merged_results_df) <- c("Donut Width", "Method", "Coef", "SE", "p-value", "Coef", "SE", "p-value")
+
+# print as a latex table
+latex_code <- print(xtable(merged_results_df, 
+                           caption = "RD Analysis Donut RD Results with and without Controls", 
+                           label = "tab:rd_robust_results"), 
+                    include.rownames = FALSE, 
+                    type = "latex",
+                    print.results = FALSE)
+
+latex_code <- gsub("\\\\begin\\{tabular\\}\\{llllllll\\}\n  \\\\hline\n", 
+                   "\\\\begin{tabular}{llllllll}\n  \\\\hline\n &  & \\\\multicolumn{3}{c}{Without Control} & \\\\multicolumn{3}{c}{With Control} \\\\\\\\\n", 
+                   latex_code)
+
+latex_code <- gsub("\\\\end\\{tabular\\}", "\\\\end{tabular}\nNote that the cutoff is 0.41, the main bandwidth is 0.066 and the bias bandwidth is 0.135.", latex_code)
+
+write(latex_code, file = paste(working_directory , "result_tables/donut_robust.tex", sep='/'))
+```
+
+## McCrary Sorting Test
+
+```{r}
 # Give it the running variable and the cutpoint
@@
 # The output will be the p-value for the presence of a discontinuity
+DCdensity(filtered_data$nearest_store_distances, cutpoint = 0.41, bw = 0.066, verbose = TRUE, plot = FALSE)
 DCdensity(panel_data$nearest_store_distances, cutpoint = 0.41, bw = 0.066, verbose = TRUE, plot = FALSE)
@@
 
-```{r}
-library(rdd)
-
-# Give it the running variable and the cutpoint
-# it will automatically produce a plot and select the number of bins and the bandwidth
-# The output will be the p-value for the presence of a discontinuity
-DCdensity(panel_data$nearest_store_distances, cutpoint = 0.41, bw = 0.095, verbose = TRUE, plot = FALSE)
-```
+## PlaceBo Test
 
@@
 ```{r}
+testing_variables <- c("pop", "light", "price_concession", "ln_end_price", "ln_nego_changes", "ln_watch_time", "green_ratio", "bedroom", "ln_watch_people", "living_room", "ln_negotiation_period", "museum", "kind", "mid", "sub", "house_age", "total_building")
+
+results_list <- list()
+
+counter <- 1
+
 for (validation in testing_variables) {
-  rd_result <- rdrobust(y = panel_data[[validation]], x = panel_data$nearest_store_distances
-                        , c = 0.41, h = 0.066, b = 0.135)
-  cat("Covariate:", validation, "\n")
-  print(summary(rd_result))
-  cat("\n\n")
+  rd_result <- rdrobust(y = panel_data[[validation]], x = panel_data$nearest_store_distances,
+                        c = 0.41, h = 0.066, b = 0.135,
+                        bwselect = "mserd", kernel = "triangular")
 
+  # 提取有效观测值数量并相加
+  effective_obs <- sum(rd_result$N_h)
+
+  # 提取结果并存储到列表中
+  results_list[[counter]] <- data.frame(
+    Covariate = validation,
+    Estimate = format(rd_result$coef[1], digits = 3, scientific = FALSE),
+    SE = format(rd_result$se[1], digits = 3, scientific = FALSE),
+    Z = format(rd_result$z[1], digits = 3, scientific = FALSE),
+    PValue = format(rd_result$pv[1], digits = 3, scientific = FALSE),
+    Bandwidth = format(rd_result$bws[1], digits = 3, scientific = FALSE),
+    EffectiveObs = effective_obs
+  )
+  counter <- counter + 1
 }
+
+results <- do.call(rbind, results_list)
+
+latex_code <- print(xtable(results, 
+                           caption = "Placebo Test Results for Different Covariates", 
+                           label = "tab:placebo_test_results"), 
+                    include.rownames = FALSE, 
+                    type = "latex",
+                    print.results = FALSE)
+write(latex_code, file = paste(working_directory , "result_tables/rdd_placebo_test.tex", sep='/'))
+print(results)
+
 ```
+
+## Cutoff Point movement
+
+The movement of the cutoff point should make the estimation non-significant
+
+```{r}
+cutoffs_width <- c(0.15, 0.2, 0.25, 0.30, 0.35, 0.50, 0.65, 0.7)
+
+results_list <- list()
+counter <- 1
+for (cutoff in cutoffs_width) {
+  # rd_result <- rdrobust(y = panel_data$ln_income, x = panel_data$nearest_store_distances, c = cutoff, h = 0.066, b = 0.135, bwselect = "mserd", kernel = "triangular")
+  rd_result <- rdrobust(y = panel_data$ln_income, x = panel_data$nearest_store_distances,
+                        c = cutoff)
+
+  # 提取有效观测值数量并相加
+  effective_obs <- sum(rd_result$N_h)
+  # 提取结果并存储到列表中
+  results_list[[counter]] <- data.frame(
+    Cutoff = cutoff,
+    Estimate = format(rd_result$coef[1], digits = 3, scientific = FALSE),
+    SE = format(rd_result$se[1], digits = 3, scientific = FALSE),
+    Z = format(rd_result$z[1], digits = 3, scientific = FALSE),
+    PValue = format(rd_result$pv[1], digits = 3, scientific = FALSE),
+    Bandwidth = format(rd_result$bws[1], digits = 3, scientific = FALSE),
+    EffectiveObs = effective_obs
+  )
+  counter <- counter + 1
+}
+results <- do.call(rbind, results_list)
+
+latex_code <- print(xtable(results, 
+                           caption = "Placebo Test Results for Different Cutoff Point", 
+                           label = "tab:movement_cutoff"), 
+                    include.rownames = FALSE, 
+                    type = "latex",
+                    print.results = FALSE)
+write(latex_code, file = paste(working_directory , "result_tables/movement_cutoff.tex", sep='/'))
+print(results)
+```

### 2024-06-09 analysis/RD-design-analysis.tex
modified:   analysis/RD design analysis.Rmd 	new file:   analysis/RD-design-analysis.log 	new file:   analysis/RD-design-analysis.tex 	new file:   analysis/RD_Plot_1st_Order.pdf 	new file:   analysis/RD_Plot_2nd_Order.pdf 	new file:   analysis/RD_Plot_3rd_Order.pdf 	new file:   analysis/donut_robust.tex 	new file:   archive/RD design archived.Rmd 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	new

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[left=1.5cm,right=1.5cm,top=1cm,bottom=1.5cm]{geometry}
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={RD design analysis},
  pdfauthor={Xuyuan Zhang},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{RD design analysis}
\author{Xuyuan Zhang}
\date{09 六月, 2024}

\begin{document}
\maketitle

\hypertarget{structure}{%
\subsection{structure}\label{structure}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  we first report the figure and export the figure to the folder named
  figures in directory
\item
  we then report the main result of the regressions
\item
  lastly, we report the placebo test and the robustness check
\end{enumerate}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# these are the packages that we need to import}
\FunctionTok{library}\NormalTok{(haven)}
\FunctionTok{library}\NormalTok{(rdd)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 载入需要的程辑包：sandwich
\end{verbatim}

\begin{verbatim}
## 载入需要的程辑包：lmtest
\end{verbatim}

\begin{verbatim}
## 载入需要的程辑包：zoo
\end{verbatim}

\begin{verbatim}
## 
## 载入程辑包：'zoo'
\end{verbatim}

\begin{verbatim}
## The following objects are masked from 'package:base':
## 
##     as.Date, as.Date.numeric
\end{verbatim}

\begin{verbatim}
## 载入需要的程辑包：AER
\end{verbatim}

\begin{verbatim}
## 载入需要的程辑包：car
\end{verbatim}

\begin{verbatim}
## 载入需要的程辑包：carData
\end{verbatim}

\begin{verbatim}
## 载入需要的程辑包：survival
\end{verbatim}

\begin{verbatim}
## 载入需要的程辑包：Formula
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(ggplot2)}
\FunctionTok{library}\NormalTok{(dplyr)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## 载入程辑包：'dplyr'
\end{verbatim}

\begin{verbatim}
## The following object is masked from 'package:car':
## 
##     recode
\end{verbatim}

\begin{verbatim}
## The following objects are masked from 'package:stats':
## 
##     filter, lag
\end{verbatim}

\begin{verbatim}
## The following objects are masked from 'package:base':
## 
##     intersect, setdiff, setequal, union
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(rdrobust)}
\FunctionTok{library}\NormalTok{(plm)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## 载入程辑包：'plm'
\end{verbatim}

\begin{verbatim}
## The following objects are masked from 'package:dplyr':
## 
##     between, lag, lead
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(xtable)}
\FunctionTok{library}\NormalTok{(pander)  }\CommentTok{\# this is for table showing}
\FunctionTok{library}\NormalTok{(latex2exp)  }\CommentTok{\# this is to export it}
\FunctionTok{setwd}\NormalTok{(}\StringTok{"E:/umich/RealEstateBrokerage{-}main"}\NormalTok{)}
\CommentTok{\# need to place data on the base directory}
\NormalTok{data }\OtherTok{\textless{}{-}} \FunctionTok{read\_dta}\NormalTok{(}\StringTok{"template.dta"}\NormalTok{)}
\NormalTok{working\_directory }\OtherTok{\textless{}{-}} \StringTok{"E:/umich/RealEstateBrokerage"}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{panel\_data }\OtherTok{\textless{}{-}} \FunctionTok{pdata.frame}\NormalTok{(data, }\AttributeTok{index =} \FunctionTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{, }\StringTok{"year"}\NormalTok{))}
\NormalTok{panel\_data}\SpecialCharTok{$}\NormalTok{L\_jiadian }\OtherTok{\textless{}{-}} \FunctionTok{lag}\NormalTok{(panel\_data}\SpecialCharTok{$}\NormalTok{jiadian, }\DecValTok{1}\NormalTok{)}
\NormalTok{panel\_data}\SpecialCharTok{$}\NormalTok{L\_kind }\OtherTok{\textless{}{-}} \FunctionTok{lag}\NormalTok{(panel\_data}\SpecialCharTok{$}\NormalTok{kind, }\DecValTok{1}\NormalTok{)}
\NormalTok{panel\_data}\SpecialCharTok{$}\NormalTok{L\_hotel }\OtherTok{\textless{}{-}} \FunctionTok{lag}\NormalTok{(panel\_data}\SpecialCharTok{$}\NormalTok{hotel, }\DecValTok{1}\NormalTok{)}
\NormalTok{panel\_data}\SpecialCharTok{$}\NormalTok{L\_shop\_mall }\OtherTok{\textless{}{-}} \FunctionTok{lag}\NormalTok{(panel\_data}\SpecialCharTok{$}\NormalTok{shop\_mall, }\DecValTok{1}\NormalTok{)}
\NormalTok{panel\_data}\SpecialCharTok{$}\NormalTok{L\_museum }\OtherTok{\textless{}{-}} \FunctionTok{lag}\NormalTok{(panel\_data}\SpecialCharTok{$}\NormalTok{museum, }\DecValTok{1}\NormalTok{)}
\NormalTok{panel\_data}\SpecialCharTok{$}\NormalTok{L\_old }\OtherTok{\textless{}{-}} \FunctionTok{lag}\NormalTok{(panel\_data}\SpecialCharTok{$}\NormalTok{old, }\DecValTok{1}\NormalTok{)}
\NormalTok{panel\_data}\SpecialCharTok{$}\NormalTok{L\_ktv }\OtherTok{\textless{}{-}} \FunctionTok{lag}\NormalTok{(panel\_data}\SpecialCharTok{$}\NormalTok{ktv, }\DecValTok{1}\NormalTok{)}
\NormalTok{panel\_data}\SpecialCharTok{$}\NormalTok{L\_mid }\OtherTok{\textless{}{-}} \FunctionTok{lag}\NormalTok{(panel\_data}\SpecialCharTok{$}\NormalTok{mid, }\DecValTok{1}\NormalTok{)}
\NormalTok{panel\_data}\SpecialCharTok{$}\NormalTok{L\_prim }\OtherTok{\textless{}{-}} \FunctionTok{lag}\NormalTok{(panel\_data}\SpecialCharTok{$}\NormalTok{prim, }\DecValTok{1}\NormalTok{)}
\NormalTok{panel\_data}\SpecialCharTok{$}\NormalTok{L\_west\_food }\OtherTok{\textless{}{-}} \FunctionTok{lag}\NormalTok{(panel\_data}\SpecialCharTok{$}\NormalTok{west\_food, }\DecValTok{1}\NormalTok{)}
\NormalTok{panel\_data}\SpecialCharTok{$}\NormalTok{L\_super }\OtherTok{\textless{}{-}} \FunctionTok{lag}\NormalTok{(panel\_data}\SpecialCharTok{$}\NormalTok{super, }\DecValTok{1}\NormalTok{)}
\NormalTok{panel\_data}\SpecialCharTok{$}\NormalTok{L\_sub }\OtherTok{\textless{}{-}} \FunctionTok{lag}\NormalTok{(panel\_data}\SpecialCharTok{$}\NormalTok{sub, }\DecValTok{1}\NormalTok{)}
\NormalTok{panel\_data}\SpecialCharTok{$}\NormalTok{L\_park }\OtherTok{\textless{}{-}} \FunctionTok{lag}\NormalTok{(panel\_data}\SpecialCharTok{$}\NormalTok{park, }\DecValTok{1}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

we use these control variables

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{control\_variables }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"jiadian"}\NormalTok{, }\StringTok{"kind"}\NormalTok{, }\StringTok{"hotel"}\NormalTok{, }\StringTok{"shop\_mall"}\NormalTok{, }\StringTok{"museum"}\NormalTok{, }\StringTok{"old"}\NormalTok{,}
    \StringTok{"ktv"}\NormalTok{, }\StringTok{"mid"}\NormalTok{, }\StringTok{"prim"}\NormalTok{, }\StringTok{"west\_food"}\NormalTok{, }\StringTok{"super"}\NormalTok{, }\StringTok{"sub"}\NormalTok{, }\StringTok{"park"}\NormalTok{, }\StringTok{"area"}\NormalTok{, }\StringTok{"bedroom"}\NormalTok{,}
    \StringTok{"toilet"}\NormalTok{, }\StringTok{"house\_age"}\NormalTok{, }\StringTok{"floor\_level"}\NormalTok{, }\StringTok{"green\_ratio"}\NormalTok{, }\StringTok{"total\_building"}\NormalTok{, }\StringTok{"total\_floor\_number"}\NormalTok{,}
    \StringTok{"living\_room"}\NormalTok{, }\StringTok{"elevator\_ratio"}\NormalTok{, }\StringTok{"kitchen"}\NormalTok{, }\StringTok{"floor\_ratio"}\NormalTok{, }\StringTok{"total\_resident"}\NormalTok{,}
    \StringTok{"pm25"}\NormalTok{, }\StringTok{"pop"}\NormalTok{, }\StringTok{"light"}\NormalTok{, }\StringTok{"non\_online\_effect"}\NormalTok{, }\StringTok{"ln\_negotiation\_period"}\NormalTok{, }\StringTok{"ln\_watch\_time"}\NormalTok{,}
    \StringTok{"ln\_nego\_changes"}\NormalTok{, }\StringTok{"ln\_lead"}\NormalTok{, }\StringTok{"ln\_watch\_people"}\NormalTok{)}
\NormalTok{testing\_variables }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"ln\_negotiation\_period"}\NormalTok{, }\StringTok{"ln\_watch\_time"}\NormalTok{, }\StringTok{"ln\_nego\_changes"}\NormalTok{,}
    \StringTok{"ln\_lead"}\NormalTok{, }\StringTok{"ln\_watch\_people"}\NormalTok{, }\StringTok{"ln\_end\_price"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{h }\OtherTok{=} \FloatTok{0.066}
\NormalTok{cutoff }\OtherTok{=} \FloatTok{0.41}
\NormalTok{running\_var }\OtherTok{=}\NormalTok{ panel\_data}\SpecialCharTok{$}\NormalTok{nearest\_store\_distances}

\NormalTok{filtered\_data }\OtherTok{\textless{}{-}}\NormalTok{ panel\_data[}\FunctionTok{abs}\NormalTok{(running\_var }\SpecialCharTok{{-}}\NormalTok{ cutoff) }\SpecialCharTok{\textless{}=}\NormalTok{ h, ]}

\CommentTok{\# Export the first RD plot to its own PDF file}
\FunctionTok{pdf}\NormalTok{(}\StringTok{"RD\_Plot\_1st\_Order.pdf"}\NormalTok{, }\AttributeTok{width =} \DecValTok{8}\NormalTok{, }\AttributeTok{height =} \DecValTok{4}\NormalTok{)  }\CommentTok{\# Adjust the width and height as needed}
\FunctionTok{rdplot}\NormalTok{(}\AttributeTok{y =}\NormalTok{ filtered\_data}\SpecialCharTok{$}\NormalTok{ln\_income, }\AttributeTok{x =}\NormalTok{ filtered\_data}\SpecialCharTok{$}\NormalTok{nearest\_store\_distances, }\AttributeTok{c =}\NormalTok{ cutoff,}
    \AttributeTok{nbins =} \DecValTok{40}\NormalTok{, }\AttributeTok{p =} \DecValTok{1}\NormalTok{, }\AttributeTok{title =} \StringTok{"RD{-}plot 1st order polynomial"}\NormalTok{, }\AttributeTok{x.label =} \StringTok{"Nearest distance to Lianjia\textquotesingle{}s stores"}\NormalTok{,}
    \AttributeTok{y.label =} \StringTok{"Log of income in the community"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## [1] "Mass points detected in the running variable."
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{dev.off}\NormalTok{()  }\CommentTok{\# Close the PDF device}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## pdf 
##   2
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Export the second RD plot to its own PDF file}
\FunctionTok{pdf}\NormalTok{(}\StringTok{"RD\_Plot\_2nd\_Order.pdf"}\NormalTok{, }\AttributeTok{width =} \DecValTok{8}\NormalTok{, }\AttributeTok{height =} \DecValTok{4}\NormalTok{)  }\CommentTok{\# Adjust the width and height as needed}
\FunctionTok{rdplot}\NormalTok{(}\AttributeTok{y =}\NormalTok{ filtered\_data}\SpecialCharTok{$}\NormalTok{ln\_income, }\AttributeTok{x =}\NormalTok{ filtered\_data}\SpecialCharTok{$}\NormalTok{nearest\_store\_distances, }\AttributeTok{c =}\NormalTok{ cutoff,}
    \AttributeTok{nbins =} \DecValTok{40}\NormalTok{, }\AttributeTok{p =} \DecValTok{2}\NormalTok{, }\AttributeTok{title =} \StringTok{"RD{-}plot 2nd order polynomial"}\NormalTok{, }\AttributeTok{x.label =} \StringTok{"Nearest distance to Lianjia\textquotesingle{}s stores"}\NormalTok{,}
    \AttributeTok{y.label =} \StringTok{"Log of income in the community"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## [1] "Mass points detected in the running variable."
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{dev.off}\NormalTok{()  }\CommentTok{\# Close the PDF device}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## pdf 
##   2
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Export the third RD plot to its own PDF file}
\FunctionTok{pdf}\NormalTok{(}\StringTok{"RD\_Plot\_3rd\_Order.pdf"}\NormalTok{, }\AttributeTok{width =} \DecValTok{8}\NormalTok{, }\AttributeTok{height =} \DecValTok{4}\NormalTok{)  }\CommentTok{\# Adjust the width and height as needed}
\FunctionTok{rdplot}\NormalTok{(}\AttributeTok{y =}\NormalTok{ filtered\_data}\SpecialCharTok{$}\NormalTok{ln\_income, }\AttributeTok{x =}\NormalTok{ filtered\_data}\SpecialCharTok{$}\NormalTok{nearest\_store\_distances, }\AttributeTok{c =}\NormalTok{ cutoff,}
    \AttributeTok{nbins =} \DecValTok{40}\NormalTok{, }\AttributeTok{p =} \DecValTok{3}\NormalTok{, }\AttributeTok{title =} \StringTok{"RD{-}plot 3rd order polynomial"}\NormalTok{, }\AttributeTok{x.label =} \StringTok{"Nearest distance to Lianjia\textquotesingle{}s stores"}\NormalTok{,}
    \AttributeTok{y.label =} \StringTok{"Log of income in the community"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## [1] "Mass points detected in the running variable."
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{dev.off}\NormalTok{()  }\CommentTok{\# Close the PDF device}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## pdf 
##   2
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{bw\_methods }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"mserd"}\NormalTok{, }\StringTok{"cerrd"}\NormalTok{)}
\NormalTok{kernel\_list }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"uniform"}\NormalTok{, }\StringTok{"triangular"}\NormalTok{)}
\NormalTok{results\_list }\OtherTok{\textless{}{-}} \FunctionTok{list}\NormalTok{()}
\NormalTok{counter }\OtherTok{\textless{}{-}} \DecValTok{1}
\ControlFlowTok{for}\NormalTok{ (bw\_method }\ControlFlowTok{in}\NormalTok{ bw\_methods) \{}
    \ControlFlowTok{for}\NormalTok{ (kernel\_in }\ControlFlowTok{in}\NormalTok{ kernel\_list) \{}
\NormalTok{        result }\OtherTok{\textless{}{-}} \FunctionTok{rdrobust}\NormalTok{(}\AttributeTok{y =}\NormalTok{ panel\_data}\SpecialCharTok{$}\NormalTok{ln\_income, }\AttributeTok{x =}\NormalTok{ panel\_data}\SpecialCharTok{$}\NormalTok{nearest\_store\_distances,}
            \AttributeTok{c =} \FloatTok{0.41}\NormalTok{, }\AttributeTok{p =} \DecValTok{1}\NormalTok{, }\AttributeTok{bwselect =}\NormalTok{ bw\_method, }\AttributeTok{kernel =}\NormalTok{ kernel\_in)}

\NormalTok{        effective\_obs }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(result}\SpecialCharTok{$}\NormalTok{N\_h)}

\NormalTok{        results\_list[[counter]] }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(}\AttributeTok{Method =}\NormalTok{ bw\_method, }\AttributeTok{Kernel =}\NormalTok{ kernel\_in,}
            \AttributeTok{Estimate =} \FunctionTok{format}\NormalTok{(result}\SpecialCharTok{$}\NormalTok{coef[}\DecValTok{1}\NormalTok{], }\AttributeTok{digits =} \DecValTok{3}\NormalTok{, }\AttributeTok{scientific =} \ConstantTok{FALSE}\NormalTok{), }\AttributeTok{SE =} \FunctionTok{format}\NormalTok{(result}\SpecialCharTok{$}\NormalTok{se[}\DecValTok{1}\NormalTok{],}
                \AttributeTok{digits =} \DecValTok{3}\NormalTok{, }\AttributeTok{scientific =} \ConstantTok{FALSE}\NormalTok{), }\AttributeTok{Z =} \FunctionTok{format}\NormalTok{(result}\SpecialCharTok{$}\NormalTok{z[}\DecValTok{1}\NormalTok{], }\AttributeTok{digits =} \DecValTok{3}\NormalTok{,}
                \AttributeTok{scientific =} \ConstantTok{FALSE}\NormalTok{), }\AttributeTok{PValue =} \FunctionTok{format}\NormalTok{(result}\SpecialCharTok{$}\NormalTok{pv[}\DecValTok{1}\NormalTok{], }\AttributeTok{digits =} \DecValTok{3}\NormalTok{, }\AttributeTok{scientific =} \ConstantTok{FALSE}\NormalTok{),}
            \AttributeTok{Bandwidth =} \FunctionTok{format}\NormalTok{(result}\SpecialCharTok{$}\NormalTok{bws[}\DecValTok{1}\NormalTok{], }\AttributeTok{digits =} \DecValTok{3}\NormalTok{, }\AttributeTok{scientific =} \ConstantTok{FALSE}\NormalTok{), }\AttributeTok{EffectiveObs =}\NormalTok{ effective\_obs)}
\NormalTok{        counter }\OtherTok{\textless{}{-}}\NormalTok{ counter }\SpecialCharTok{+} \DecValTok{1}
\NormalTok{    \}}
\NormalTok{\}}
\NormalTok{results }\OtherTok{\textless{}{-}} \FunctionTok{do.call}\NormalTok{(rbind, results\_list)}
\NormalTok{latex\_code }\OtherTok{\textless{}{-}} \FunctionTok{print}\NormalTok{(}\FunctionTok{xtable}\NormalTok{(results, }\AttributeTok{caption =} \StringTok{"RD Estimates with Different Bandwidth Selection Methods and Kernels"}\NormalTok{,}
    \AttributeTok{label =} \StringTok{"tab:rd\_bandwidth\_kernel\_results"}\NormalTok{), }\AttributeTok{include.rownames =} \ConstantTok{FALSE}\NormalTok{, }\AttributeTok{type =} \StringTok{"latex"}\NormalTok{,}
    \AttributeTok{print.results =} \ConstantTok{FALSE}\NormalTok{)}
\FunctionTok{write}\NormalTok{(latex\_code, }\AttributeTok{file =} \FunctionTok{paste}\NormalTok{(working\_directory, }\StringTok{"result\_tables/rdd\_result\_summary.tex"}\NormalTok{,}
    \AttributeTok{sep =} \StringTok{"/"}\NormalTok{))}
\FunctionTok{print}\NormalTok{(results)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##   Method     Kernel Estimate     SE     Z PValue Bandwidth EffectiveObs
## 1  mserd    uniform  -0.0584 0.0263 -2.22 0.0263    0.0773        37645
## 2  mserd triangular  -0.0697 0.0314 -2.22 0.0267     0.066        32020
## 3  cerrd    uniform  -0.0874 0.0361 -2.42 0.0156    0.0418        19988
## 4  cerrd triangular  -0.0663 0.0434 -1.53  0.126    0.0357        17191
\end{verbatim}

\hypertarget{checkings}{%
\section{checkings:}\label{checkings}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Donut Hole: Exclude observations close to the cutoff and estimate the
  effect with the remaining data. If the discontinuity persists despite
  the absence of data around the cutoff, this provides evidence against
  a model misspecification.
\item
  Mccrary (2008) test: Conduct a McCrary density test to check if there
  is a discontinuity in the density of the running variable at the
  cutoff. A significant discontinuity may suggest manipulation or
  sorting around the cutoff.
\item
  Placebo test: If you have pre-treatment covariates, you can test
  whether these covariates also jump at the cutoff. If they do, this
  might suggest manipulation or a violation of the RD design
  assumptions. If they don't, it strengthens the case for a true
  treatment effect.
\end{enumerate}

\hypertarget{donut-hole-test}{%
\subsection{Donut Hole Test}\label{donut-hole-test}}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{cutoff}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## [1] 0.41
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{donut\_width }\OtherTok{\textless{}{-}} \FloatTok{0.011}
\NormalTok{panel\_data\_donut }\OtherTok{\textless{}{-}}\NormalTok{ panel\_data[}\SpecialCharTok{!}\NormalTok{(panel\_data}\SpecialCharTok{$}\NormalTok{nearest\_store\_distances }\SpecialCharTok{\textgreater{}=}\NormalTok{ (cutoff }\SpecialCharTok{{-}}
\NormalTok{    donut\_width) }\SpecialCharTok{\&}\NormalTok{ panel\_data}\SpecialCharTok{$}\NormalTok{nearest\_store\_distances }\SpecialCharTok{\textless{}=}\NormalTok{ (cutoff }\SpecialCharTok{+}\NormalTok{ donut\_width)),}
\NormalTok{    ]}
\NormalTok{result\_donut }\OtherTok{\textless{}{-}} \FunctionTok{rdrobust}\NormalTok{(}\AttributeTok{y =}\NormalTok{ panel\_data\_donut}\SpecialCharTok{$}\NormalTok{ln\_income, }\AttributeTok{x =}\NormalTok{ panel\_data\_donut}\SpecialCharTok{$}\NormalTok{nearest\_store\_distances,}
    \AttributeTok{c =}\NormalTok{ cutoff, }\AttributeTok{p =} \DecValTok{1}\NormalTok{, }\AttributeTok{h =} \FloatTok{0.066}\NormalTok{, }\AttributeTok{b =} \FloatTok{0.135}\NormalTok{)}
\FunctionTok{pander}\NormalTok{(}\FunctionTok{cbind}\NormalTok{(result\_donut}\SpecialCharTok{$}\NormalTok{coef, result\_donut}\SpecialCharTok{$}\NormalTok{pv))}
\end{Highlighting}
\end{Shaded}

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2917}}
  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1528}}
  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1528}}@{}}
\toprule()
\begin{minipage}[b]{\linewidth}\centering
~
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Coeff
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
P\textgreater\textbar z\textbar{}
\end{minipage} \\
\midrule()
\endhead
\textbf{Conventional} & -0.03879 & 0.3898 \\
\textbf{Bias-Corrected} & -0.06374 & 0.1577 \\
\textbf{Robust} & -0.06374 & 0.2383 \\
\bottomrule()
\end{longtable}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{print}\NormalTok{(result\_donut)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Call: rdrobust
## 
## Number of Obs.               212028
## BW type                      Manual
## Kernel                   Triangular
## VCE method                       NN
## 
## Number of Obs.               118399        93629
## Eff. Number of Obs.           14893        11945
## Order est. (p)                    1            1
## Order bias  (q)                   2            2
## BW est. (h)                   0.066        0.066
## BW bias (b)                   0.135        0.135
## rho (h/b)                     0.489        0.489
## Unique Obs.                  118399        93629
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{perform\_rd\_analysis }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(cutoff, donut\_width, h, b) \{}
    \CommentTok{\# select the data that we need}
\NormalTok{    panel\_data\_donut }\OtherTok{\textless{}{-}}\NormalTok{ panel\_data[}\SpecialCharTok{!}\NormalTok{(panel\_data}\SpecialCharTok{$}\NormalTok{nearest\_store\_distances }\SpecialCharTok{\textgreater{}=}\NormalTok{ (cutoff }\SpecialCharTok{{-}}
\NormalTok{        donut\_width) }\SpecialCharTok{\&}\NormalTok{ panel\_data}\SpecialCharTok{$}\NormalTok{nearest\_store\_distances }\SpecialCharTok{\textless{}=}\NormalTok{ (cutoff }\SpecialCharTok{+}\NormalTok{ donut\_width)),}
\NormalTok{        ]}
    \CommentTok{\# run the rdrobust result}
\NormalTok{    result\_donut }\OtherTok{\textless{}{-}} \FunctionTok{rdrobust}\NormalTok{(}\AttributeTok{y =}\NormalTok{ panel\_data\_donut}\SpecialCharTok{$}\NormalTok{ln\_income, }\AttributeTok{x =}\NormalTok{ panel\_data\_donut}\SpecialCharTok{$}\NormalTok{nearest\_store\_distances,}
        \AttributeTok{c =}\NormalTok{ cutoff, }\AttributeTok{p =} \DecValTok{1}\NormalTok{, }\AttributeTok{h =}\NormalTok{ h, }\AttributeTok{b =}\NormalTok{ b)}
    \CommentTok{\# return the coefficient and the p value}
\NormalTok{    conventional }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"Conventional"}\NormalTok{, result\_donut}\SpecialCharTok{$}\NormalTok{coef[}\DecValTok{1}\NormalTok{, }\DecValTok{1}\NormalTok{], result\_donut}\SpecialCharTok{$}\NormalTok{se[}\DecValTok{1}\NormalTok{,}
        \DecValTok{1}\NormalTok{], result\_donut}\SpecialCharTok{$}\NormalTok{pv[}\DecValTok{1}\NormalTok{, }\DecValTok{1}\NormalTok{])}
\NormalTok{    bias\_corrected }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"Bias{-}Corrected"}\NormalTok{, result\_donut}\SpecialCharTok{$}\NormalTok{coef[}\DecValTok{2}\NormalTok{, }\DecValTok{1}\NormalTok{], result\_donut}\SpecialCharTok{$}\NormalTok{se[}\DecValTok{2}\NormalTok{,}
        \DecValTok{1}\NormalTok{], result\_donut}\SpecialCharTok{$}\NormalTok{pv[}\DecValTok{2}\NormalTok{, }\DecValTok{1}\NormalTok{])}
\NormalTok{    robust }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"Robust"}\NormalTok{, result\_donut}\SpecialCharTok{$}\NormalTok{coef[}\DecValTok{3}\NormalTok{, }\DecValTok{1}\NormalTok{], result\_donut}\SpecialCharTok{$}\NormalTok{se[}\DecValTok{3}\NormalTok{, }\DecValTok{1}\NormalTok{], result\_donut}\SpecialCharTok{$}\NormalTok{pv[}\DecValTok{3}\NormalTok{,}
        \DecValTok{1}\NormalTok{])}

    \CommentTok{\# combine the results}
\NormalTok{    result\_table }\OtherTok{\textless{}{-}} \FunctionTok{rbind}\NormalTok{(conventional, bias\_corrected, robust)}
    \FunctionTok{colnames}\NormalTok{(result\_table) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"Method"}\NormalTok{, }\StringTok{"Coef"}\NormalTok{, }\StringTok{"SE"}\NormalTok{, }\StringTok{"p{-}value"}\NormalTok{)}
    \FunctionTok{return}\NormalTok{(result\_table)}
\NormalTok{\}}

\NormalTok{cutoff }\OtherTok{=} \FloatTok{0.41}
\NormalTok{donut\_widths }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\FloatTok{0.01}\NormalTok{, }\FloatTok{0.0125}\NormalTok{, }\FloatTok{0.015}\NormalTok{, }\FloatTok{0.0175}\NormalTok{, }\FloatTok{0.02}\NormalTok{, }\FloatTok{0.0225}\NormalTok{, }\FloatTok{0.025}\NormalTok{)}
\NormalTok{results }\OtherTok{\textless{}{-}} \FunctionTok{list}\NormalTok{()}

\ControlFlowTok{for}\NormalTok{ (donut }\ControlFlowTok{in}\NormalTok{ donut\_widths) \{}
\NormalTok{    result }\OtherTok{\textless{}{-}} \FunctionTok{perform\_rd\_analysis}\NormalTok{(cutoff, donut, }\FloatTok{0.066}\NormalTok{, }\FloatTok{0.135}\NormalTok{)}
\NormalTok{    results[[}\FunctionTok{paste0}\NormalTok{(}\StringTok{"donut\_"}\NormalTok{, donut)]] }\OtherTok{\textless{}{-}}\NormalTok{ result}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{perform\_rd\_analysis }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(cutoff, donut\_width, h, b) \{}
    \CommentTok{\# select the data that we need}
\NormalTok{    panel\_data\_donut }\OtherTok{\textless{}{-}}\NormalTok{ panel\_data[}\SpecialCharTok{!}\NormalTok{(panel\_data}\SpecialCharTok{$}\NormalTok{nearest\_store\_distances }\SpecialCharTok{\textgreater{}=}\NormalTok{ (cutoff }\SpecialCharTok{{-}}
\NormalTok{        donut\_width) }\SpecialCharTok{\&}\NormalTok{ panel\_data}\SpecialCharTok{$}\NormalTok{nearest\_store\_distances }\SpecialCharTok{\textless{}=}\NormalTok{ (cutoff }\SpecialCharTok{+}\NormalTok{ donut\_width)),}
\NormalTok{        ]}
    \CommentTok{\# run the rdrobust result}
\NormalTok{    result\_donut }\OtherTok{\textless{}{-}} \FunctionTok{rdrobust}\NormalTok{(}\AttributeTok{y =}\NormalTok{ panel\_data\_donut}\SpecialCharTok{$}\NormalTok{ln\_income, }\AttributeTok{x =}\NormalTok{ panel\_data\_donut}\SpecialCharTok{$}\NormalTok{nearest\_store\_distances,}
        \AttributeTok{c =}\NormalTok{ cutoff, }\AttributeTok{covs =}\NormalTok{ panel\_data\_donut[, control\_variables], }\AttributeTok{p =} \DecValTok{1}\NormalTok{, }\AttributeTok{h =}\NormalTok{ h, }\AttributeTok{b =}\NormalTok{ b)}
    \CommentTok{\# return the coefficient and the p value}
\NormalTok{    conventional }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"Conventional"}\NormalTok{, result\_donut}\SpecialCharTok{$}\NormalTok{coef[}\DecValTok{1}\NormalTok{, }\DecValTok{1}\NormalTok{], result\_donut}\SpecialCharTok{$}\NormalTok{se[}\DecValTok{1}\NormalTok{,}
        \DecValTok{1}\NormalTok{], result\_donut}\SpecialCharTok{$}\NormalTok{pv[}\DecValTok{1}\NormalTok{, }\DecValTok{1}\NormalTok{])}
\NormalTok{    bias\_corrected }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"Bias{-}Corrected"}\NormalTok{, result\_donut}\SpecialCharTok{$}\NormalTok{coef[}\DecValTok{2}\NormalTok{, }\DecValTok{1}\NormalTok{], result\_donut}\SpecialCharTok{$}\NormalTok{se[}\DecValTok{2}\NormalTok{,}
        \DecValTok{1}\NormalTok{], result\_donut}\SpecialCharTok{$}\NormalTok{pv[}\DecValTok{2}\NormalTok{, }\DecValTok{1}\NormalTok{])}
\NormalTok{    robust }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"Robust"}\NormalTok{, result\_donut}\SpecialCharTok{$}\NormalTok{coef[}\DecValTok{3}\NormalTok{, }\DecValTok{1}\NormalTok{], result\_donut}\SpecialCharTok{$}\NormalTok{se[}\DecValTok{3}\NormalTok{, }\DecValTok{1}\NormalTok{], result\_donut}\SpecialCharTok{$}\NormalTok{pv[}\DecValTok{3}\NormalTok{,}
        \DecValTok{1}\NormalTok{])}

    \CommentTok{\# combine the results}
\NormalTok{    result\_table }\OtherTok{\textless{}{-}} \FunctionTok{rbind}\NormalTok{(conventional, bias\_corrected, robust)}
    \FunctionTok{colnames}\NormalTok{(result\_table) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"Method"}\NormalTok{, }\StringTok{"Coef"}\NormalTok{, }\StringTok{"SE"}\NormalTok{, }\StringTok{"p{-}value"}\NormalTok{)}
    \FunctionTok{return}\NormalTok{(result\_table)}
\NormalTok{\}}

\NormalTok{cutoff }\OtherTok{=} \FloatTok{0.41}
\NormalTok{donut\_widths }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\FloatTok{0.01}\NormalTok{, }\FloatTok{0.0125}\NormalTok{, }\FloatTok{0.015}\NormalTok{, }\FloatTok{0.0175}\NormalTok{, }\FloatTok{0.02}\NormalTok{, }\FloatTok{0.0225}\NormalTok{, }\FloatTok{0.025}\NormalTok{)}
\NormalTok{results\_with\_control }\OtherTok{\textless{}{-}} \FunctionTok{list}\NormalTok{()}

\ControlFlowTok{for}\NormalTok{ (donut }\ControlFlowTok{in}\NormalTok{ donut\_widths) \{}
\NormalTok{    result }\OtherTok{\textless{}{-}} \FunctionTok{perform\_rd\_analysis}\NormalTok{(cutoff, donut, }\FloatTok{0.066}\NormalTok{, }\FloatTok{0.135}\NormalTok{)}
\NormalTok{    results\_with\_control[[}\FunctionTok{paste0}\NormalTok{(}\StringTok{"donut\_"}\NormalTok{, donut)]] }\OtherTok{\textless{}{-}}\NormalTok{ result}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# with controls}
\NormalTok{combined\_results\_with\_control }\OtherTok{\textless{}{-}} \FunctionTok{do.call}\NormalTok{(rbind, }\FunctionTok{lapply}\NormalTok{(}\FunctionTok{names}\NormalTok{(results\_with\_control),}
    \ControlFlowTok{function}\NormalTok{(donut) \{}
\NormalTok{        result }\OtherTok{\textless{}{-}}\NormalTok{ results\_with\_control[[donut]]}
\NormalTok{        robust\_result }\OtherTok{\textless{}{-}}\NormalTok{ result[result[, }\StringTok{"Method"}\NormalTok{] }\SpecialCharTok{==} \StringTok{"Robust"}\NormalTok{, ]}
        \FunctionTok{data.frame}\NormalTok{(}\AttributeTok{Donut\_Width =}\NormalTok{ donut, }\AttributeTok{Method =}\NormalTok{ robust\_result[}\DecValTok{1}\NormalTok{], }\AttributeTok{Coef =}\NormalTok{ robust\_result[}\DecValTok{2}\NormalTok{],}
            \AttributeTok{SE =}\NormalTok{ robust\_result[}\DecValTok{3}\NormalTok{], }\AttributeTok{p\_value =}\NormalTok{ robust\_result[}\DecValTok{4}\NormalTok{])}
\NormalTok{    \}))}
\FunctionTok{colnames}\NormalTok{(combined\_results\_with\_control) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"Donut Width"}\NormalTok{, }\StringTok{"Method"}\NormalTok{, }\StringTok{"Coef"}\NormalTok{, }\StringTok{"SE"}\NormalTok{,}
    \StringTok{"p{-}value"}\NormalTok{)}

\CommentTok{\# without controls}
\NormalTok{combined\_results }\OtherTok{\textless{}{-}} \FunctionTok{do.call}\NormalTok{(rbind, }\FunctionTok{lapply}\NormalTok{(}\FunctionTok{names}\NormalTok{(results), }\ControlFlowTok{function}\NormalTok{(donut) \{}
\NormalTok{    result }\OtherTok{\textless{}{-}}\NormalTok{ results[[donut]]}
\NormalTok{    robust\_result }\OtherTok{\textless{}{-}}\NormalTok{ result[result[, }\StringTok{"Method"}\NormalTok{] }\SpecialCharTok{==} \StringTok{"Robust"}\NormalTok{, ]}
    \FunctionTok{data.frame}\NormalTok{(}\AttributeTok{Donut\_Width =}\NormalTok{ donut, }\AttributeTok{Method =}\NormalTok{ robust\_result[}\DecValTok{1}\NormalTok{], }\AttributeTok{Coef =}\NormalTok{ robust\_result[}\DecValTok{2}\NormalTok{],}
        \AttributeTok{SE =}\NormalTok{ robust\_result[}\DecValTok{3}\NormalTok{], }\AttributeTok{p\_value =}\NormalTok{ robust\_result[}\DecValTok{4}\NormalTok{])}
\NormalTok{\}))}
\FunctionTok{colnames}\NormalTok{(combined\_results) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"Donut Width"}\NormalTok{, }\StringTok{"Method"}\NormalTok{, }\StringTok{"Coef"}\NormalTok{, }\StringTok{"SE"}\NormalTok{, }\StringTok{"p{-}value"}\NormalTok{)}

\NormalTok{merged\_results }\OtherTok{\textless{}{-}} \FunctionTok{merge}\NormalTok{(combined\_results\_with\_control, combined\_results, }\AttributeTok{by =} \FunctionTok{c}\NormalTok{(}\StringTok{"Donut Width"}\NormalTok{,}
    \StringTok{"Method"}\NormalTok{))}
\NormalTok{merged\_results\_df }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(merged\_results)}

\FunctionTok{colnames}\NormalTok{(merged\_results\_df) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"Donut Width"}\NormalTok{, }\StringTok{"Method"}\NormalTok{, }\StringTok{"Coef"}\NormalTok{, }\StringTok{"SE"}\NormalTok{, }\StringTok{"p{-}value"}\NormalTok{,}
    \StringTok{"Coef"}\NormalTok{, }\StringTok{"SE"}\NormalTok{, }\StringTok{"p{-}value"}\NormalTok{)}

\CommentTok{\# print as a latex table}
\NormalTok{latex\_code }\OtherTok{\textless{}{-}} \FunctionTok{print}\NormalTok{(}\FunctionTok{xtable}\NormalTok{(merged\_results\_df, }\AttributeTok{caption =} \StringTok{"RD Analysis Donut RD Results with and without Controls"}\NormalTok{,}
    \AttributeTok{label =} \StringTok{"tab:rd\_robust\_results"}\NormalTok{), }\AttributeTok{include.rownames =} \ConstantTok{FALSE}\NormalTok{, }\AttributeTok{type =} \StringTok{"latex"}\NormalTok{, }\AttributeTok{print.results =} \ConstantTok{FALSE}\NormalTok{)}

\NormalTok{latex\_code }\OtherTok{\textless{}{-}} \FunctionTok{gsub}\NormalTok{(}\StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}\textbackslash{}\textbackslash{}}\StringTok{begin}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{\{tabular}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{\}}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{\{llllllll}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{\}}\SpecialCharTok{\textbackslash{}n}\StringTok{  }\SpecialCharTok{\textbackslash{}\textbackslash{}\textbackslash{}\textbackslash{}}\StringTok{hline}\SpecialCharTok{\textbackslash{}n}\StringTok{"}\NormalTok{, }\StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}\textbackslash{}\textbackslash{}}\StringTok{begin\{tabular\}\{llllllll\}}\SpecialCharTok{\textbackslash{}n}\StringTok{  }\SpecialCharTok{\textbackslash{}\textbackslash{}\textbackslash{}\textbackslash{}}\StringTok{hline}\SpecialCharTok{\textbackslash{}n}\StringTok{ \&  \& }\SpecialCharTok{\textbackslash{}\textbackslash{}\textbackslash{}\textbackslash{}}\StringTok{multicolumn\{3\}\{c\}\{Without Control\} \& }\SpecialCharTok{\textbackslash{}\textbackslash{}\textbackslash{}\textbackslash{}}\StringTok{multicolumn\{3\}\{c\}\{With Control\} }\SpecialCharTok{\textbackslash{}\textbackslash{}\textbackslash{}\textbackslash{}\textbackslash{}\textbackslash{}\textbackslash{}\textbackslash{}\textbackslash{}n}\StringTok{"}\NormalTok{,}
\NormalTok{    latex\_code)}

\NormalTok{latex\_code }\OtherTok{\textless{}{-}} \FunctionTok{gsub}\NormalTok{(}\StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}\textbackslash{}\textbackslash{}}\StringTok{end}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{\{tabular}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{\}"}\NormalTok{, }\StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}\textbackslash{}\textbackslash{}}\StringTok{end\{tabular\}}\SpecialCharTok{\textbackslash{}n}\StringTok{Note that the cutoff is 0.41, the main bandwidth is 0.066 and the bias bandwidth is 0.135."}\NormalTok{,}
\NormalTok{    latex\_code)}

\FunctionTok{write}\NormalTok{(latex\_code, }\AttributeTok{file =} \FunctionTok{paste}\NormalTok{(working\_directory, }\StringTok{"result\_tables/donut\_robust.tex"}\NormalTok{,}
    \AttributeTok{sep =} \StringTok{"/"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\hypertarget{mccrary-sorting-test}{%
\subsection{McCrary Sorting Test}\label{mccrary-sorting-test}}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Give it the running variable and the cutpoint it will automatically produce a}
\CommentTok{\# plot and select the number of bins and the bandwidth The output will be the}
\CommentTok{\# p{-}value for the presence of a discontinuity}
\FunctionTok{DCdensity}\NormalTok{(filtered\_data}\SpecialCharTok{$}\NormalTok{nearest\_store\_distances, }\AttributeTok{cutpoint =} \FloatTok{0.41}\NormalTok{, }\AttributeTok{bw =} \FloatTok{0.066}\NormalTok{, }\AttributeTok{verbose =} \ConstantTok{TRUE}\NormalTok{,}
    \AttributeTok{plot =} \ConstantTok{FALSE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Using calculated bin size:  0.000 
## Log difference in heights is  -0.026  with SE  0.025 
##   this gives a z-stat of  -1.070 
##   and a p value of  0.284
\end{verbatim}

\begin{verbatim}
## [1] 0.2844948
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{DCdensity}\NormalTok{(panel\_data}\SpecialCharTok{$}\NormalTok{nearest\_store\_distances, }\AttributeTok{cutpoint =} \FloatTok{0.41}\NormalTok{, }\AttributeTok{bw =} \FloatTok{0.066}\NormalTok{, }\AttributeTok{verbose =} \ConstantTok{TRUE}\NormalTok{,}
    \AttributeTok{plot =} \ConstantTok{FALSE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Using calculated bin size:  0.016 
## Log difference in heights is  -0.041  with SE  0.025 
##   this gives a z-stat of  -1.641 
##   and a p value of  0.101
\end{verbatim}

\begin{verbatim}
## [1] 0.1007234
\end{verbatim}

\hypertarget{placebo-test}{%
\subsection{PlaceBo Test}\label{placebo-test}}

Conducting placebo test. We shall using the same validation bandwidth
and bias correction bandwidth. The results are good overall

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{testing\_variables }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"pop"}\NormalTok{, }\StringTok{"light"}\NormalTok{, }\StringTok{"price\_concession"}\NormalTok{, }\StringTok{"ln\_end\_price"}\NormalTok{, }\StringTok{"ln\_nego\_changes"}\NormalTok{,}
    \StringTok{"ln\_watch\_time"}\NormalTok{, }\StringTok{"green\_ratio"}\NormalTok{, }\StringTok{"bedroom"}\NormalTok{, }\StringTok{"ln\_watch\_people"}\NormalTok{, }\StringTok{"living\_room"}\NormalTok{,}
    \StringTok{"ln\_negotiation\_period"}\NormalTok{, }\StringTok{"hhi"}\NormalTok{, }\StringTok{"super"}\NormalTok{, }\StringTok{"museum"}\NormalTok{, }\StringTok{"kind"}\NormalTok{, }\StringTok{"mid"}\NormalTok{, }\StringTok{"sub"}\NormalTok{, }\StringTok{"house\_age"}\NormalTok{,}
    \StringTok{"total\_building"}\NormalTok{)}

\NormalTok{results\_list }\OtherTok{\textless{}{-}} \FunctionTok{list}\NormalTok{()}

\NormalTok{counter }\OtherTok{\textless{}{-}} \DecValTok{1}

\ControlFlowTok{for}\NormalTok{ (validation }\ControlFlowTok{in}\NormalTok{ testing\_variables) \{}
\NormalTok{    rd\_result }\OtherTok{\textless{}{-}} \FunctionTok{rdrobust}\NormalTok{(}\AttributeTok{y =}\NormalTok{ panel\_data[[validation]], }\AttributeTok{x =}\NormalTok{ panel\_data}\SpecialCharTok{$}\NormalTok{nearest\_store\_distances,}
        \AttributeTok{c =} \FloatTok{0.41}\NormalTok{, }\AttributeTok{h =} \FloatTok{0.066}\NormalTok{, }\AttributeTok{b =} \FloatTok{0.135}\NormalTok{, }\AttributeTok{bwselect =} \StringTok{"mserd"}\NormalTok{, }\AttributeTok{kernel =} \StringTok{"triangular"}\NormalTok{)}

    \CommentTok{\# 提取有效观测值数量并相加}
\NormalTok{    effective\_obs }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(rd\_result}\SpecialCharTok{$}\NormalTok{N\_h)}

    \CommentTok{\# 提取结果并存储到列表中}
\NormalTok{    results\_list[[counter]] }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(}\AttributeTok{Covariate =}\NormalTok{ validation, }\AttributeTok{Estimate =} \FunctionTok{format}\NormalTok{(rd\_result}\SpecialCharTok{$}\NormalTok{coef[}\DecValTok{1}\NormalTok{],}
        \AttributeTok{digits =} \DecValTok{3}\NormalTok{, }\AttributeTok{scientific =} \ConstantTok{FALSE}\NormalTok{), }\AttributeTok{SE =} \FunctionTok{format}\NormalTok{(rd\_result}\SpecialCharTok{$}\NormalTok{se[}\DecValTok{1}\NormalTok{], }\AttributeTok{digits =} \DecValTok{3}\NormalTok{,}
        \AttributeTok{scientific =} \ConstantTok{FALSE}\NormalTok{), }\AttributeTok{Z =} \FunctionTok{format}\NormalTok{(rd\_result}\SpecialCharTok{$}\NormalTok{z[}\DecValTok{1}\NormalTok{], }\AttributeTok{digits =} \DecValTok{3}\NormalTok{, }\AttributeTok{scientific =} \ConstantTok{FALSE}\NormalTok{),}
        \AttributeTok{PValue =} \FunctionTok{format}\NormalTok{(rd\_result}\SpecialCharTok{$}\NormalTok{pv[}\DecValTok{1}\NormalTok{], }\AttributeTok{digits =} \DecValTok{3}\NormalTok{, }\AttributeTok{scientific =} \ConstantTok{FALSE}\NormalTok{), }\AttributeTok{Bandwidth =} \FunctionTok{format}\NormalTok{(rd\_result}\SpecialCharTok{$}\NormalTok{bws[}\DecValTok{1}\NormalTok{],}
            \AttributeTok{digits =} \DecValTok{3}\NormalTok{, }\AttributeTok{scientific =} \ConstantTok{FALSE}\NormalTok{), }\AttributeTok{EffectiveObs =}\NormalTok{ effective\_obs)}
\NormalTok{    counter }\OtherTok{\textless{}{-}}\NormalTok{ counter }\SpecialCharTok{+} \DecValTok{1}
\NormalTok{\}}

\NormalTok{results }\OtherTok{\textless{}{-}} \FunctionTok{do.call}\NormalTok{(rbind, results\_list)}

\NormalTok{latex\_code }\OtherTok{\textless{}{-}} \FunctionTok{print}\NormalTok{(}\FunctionTok{xtable}\NormalTok{(results, }\AttributeTok{caption =} \StringTok{"Placebo Test Results for Different Covariates"}\NormalTok{,}
    \AttributeTok{label =} \StringTok{"tab:placebo\_test\_results"}\NormalTok{), }\AttributeTok{include.rownames =} \ConstantTok{FALSE}\NormalTok{, }\AttributeTok{type =} \StringTok{"latex"}\NormalTok{,}
    \AttributeTok{print.results =} \ConstantTok{FALSE}\NormalTok{)}
\FunctionTok{write}\NormalTok{(latex\_code, }\AttributeTok{file =} \FunctionTok{paste}\NormalTok{(working\_directory, }\StringTok{"result\_tables/rdd\_placebo\_test.tex"}\NormalTok{,}
    \AttributeTok{sep =} \StringTok{"/"}\NormalTok{))}
\FunctionTok{print}\NormalTok{(results)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##                Covariate  Estimate       SE       Z             PValue
## 1                    pop     -73.6      396  -0.186              0.852
## 2                  light    -0.203     0.26  -0.779              0.436
## 3       price_concession -0.000379 0.000739  -0.513              0.608
## 4           ln_end_price   -0.0234   0.0167   -1.41               0.16
## 5        ln_nego_changes -0.000518   0.0222 -0.0233              0.981
## 6          ln_watch_time    0.0726   0.0682    1.06              0.288
## 7            green_ratio  -0.00161  0.00231  -0.696              0.487
## 8                bedroom  -0.00858   0.0176  -0.487              0.626
## 9        ln_watch_people    0.0542   0.0357    1.52              0.129
## 10           living_room  0.000998   0.0113  0.0881               0.93
## 11 ln_negotiation_period  -0.00648   0.0266  -0.243              0.808
## 12                   hhi    0.0444  0.00578    7.68 0.0000000000000156
## 13                 super    -0.298   0.0823   -3.62           0.000292
## 14                museum   -0.0544   0.0416   -1.31              0.191
## 15                  kind   0.00667    0.136  0.0491              0.961
## 16                   mid    0.0124   0.0608   0.204              0.838
## 17                   sub     0.046   0.0244    1.89              0.059
## 18             house_age     0.209    0.275    0.76              0.447
## 19        total_building    -0.275    0.829  -0.332               0.74
##    Bandwidth EffectiveObs
## 1      0.066        32010
## 2      0.066        32010
## 3      0.066        31437
## 4      0.066        32010
## 5      0.066        32010
## 6      0.066        32010
## 7      0.066        32010
## 8      0.066        32010
## 9      0.066        32010
## 10     0.066        32010
## 11     0.066        32010
## 12     0.066        32010
## 13     0.066        32010
## 14     0.066        32010
## 15     0.066        32010
## 16     0.066        32010
## 17     0.066        32010
## 18     0.066        32010
## 19     0.066        32010
\end{verbatim}

\hypertarget{cutoff-point-movement}{%
\subsection{Cutoff Point movement}\label{cutoff-point-movement}}

The movement of the cutoff point should make the estimation
non-significant

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{cutoffs\_width }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\FloatTok{0.15}\NormalTok{, }\FloatTok{0.2}\NormalTok{, }\FloatTok{0.25}\NormalTok{, }\FloatTok{0.3}\NormalTok{, }\FloatTok{0.35}\NormalTok{, }\FloatTok{0.5}\NormalTok{, }\FloatTok{0.65}\NormalTok{, }\FloatTok{0.7}\NormalTok{)}

\NormalTok{results\_list }\OtherTok{\textless{}{-}} \FunctionTok{list}\NormalTok{()}
\NormalTok{counter }\OtherTok{\textless{}{-}} \DecValTok{1}
\ControlFlowTok{for}\NormalTok{ (cutoff }\ControlFlowTok{in}\NormalTok{ cutoffs\_width) \{}
    \CommentTok{\# rd\_result \textless{}{-} rdrobust(y = panel\_data$ln\_income, x =}
    \CommentTok{\# panel\_data$nearest\_store\_distances, c = cutoff, h = 0.066, b = 0.135,}
    \CommentTok{\# bwselect = \textquotesingle{}mserd\textquotesingle{}, kernel = \textquotesingle{}triangular\textquotesingle{})}
\NormalTok{    rd\_result }\OtherTok{\textless{}{-}} \FunctionTok{rdrobust}\NormalTok{(}\AttributeTok{y =}\NormalTok{ panel\_data}\SpecialCharTok{$}\NormalTok{ln\_income, }\AttributeTok{x =}\NormalTok{ panel\_data}\SpecialCharTok{$}\NormalTok{nearest\_store\_distances,}
        \AttributeTok{c =}\NormalTok{ cutoff)}

    \CommentTok{\# 提取有效观测值数量并相加}
\NormalTok{    effective\_obs }\OtherTok{\textless{}{-}} \FunctionTok{sum}\NormalTok{(rd\_result}\SpecialCharTok{$}\NormalTok{N\_h)}
    \CommentTok{\# 提取结果并存储到列表中}
\NormalTok{    results\_list[[counter]] }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(}\AttributeTok{Cutoff =}\NormalTok{ cutoff, }\AttributeTok{Estimate =} \FunctionTok{format}\NormalTok{(rd\_result}\SpecialCharTok{$}\NormalTok{coef[}\DecValTok{1}\NormalTok{],}
        \AttributeTok{digits =} \DecValTok{3}\NormalTok{, }\AttributeTok{scientific =} \ConstantTok{FALSE}\NormalTok{), }\AttributeTok{SE =} \FunctionTok{format}\NormalTok{(rd\_result}\SpecialCharTok{$}\NormalTok{se[}\DecValTok{1}\NormalTok{], }\AttributeTok{digits =} \DecValTok{3}\NormalTok{,}
        \AttributeTok{scientific =} \ConstantTok{FALSE}\NormalTok{), }\AttributeTok{Z =} \FunctionTok{format}\NormalTok{(rd\_result}\SpecialCharTok{$}\NormalTok{z[}\DecValTok{1}\NormalTok{], }\AttributeTok{digits =} \DecValTok{3}\NormalTok{, }\AttributeTok{scientific =} \ConstantTok{FALSE}\NormalTok{),}
        \AttributeTok{PValue =} \FunctionTok{format}\NormalTok{(rd\_result}\SpecialCharTok{$}\NormalTok{pv[}\DecValTok{1}\NormalTok{], }\AttributeTok{digits =} \DecValTok{3}\NormalTok{, }\AttributeTok{scientific =} \ConstantTok{FALSE}\NormalTok{), }\AttributeTok{Bandwidth =} \FunctionTok{format}\NormalTok{(rd\_result}\SpecialCharTok{$}\NormalTok{bws[}\DecValTok{1}\NormalTok{],}
            \AttributeTok{digits =} \DecValTok{3}\NormalTok{, }\AttributeTok{scientific =} \ConstantTok{FALSE}\NormalTok{), }\AttributeTok{EffectiveObs =}\NormalTok{ effective\_obs)}
\NormalTok{    counter }\OtherTok{\textless{}{-}}\NormalTok{ counter }\SpecialCharTok{+} \DecValTok{1}
\NormalTok{\}}
\NormalTok{results }\OtherTok{\textless{}{-}} \FunctionTok{do.call}\NormalTok{(rbind, results\_list)}

\NormalTok{latex\_code }\OtherTok{\textless{}{-}} \FunctionTok{print}\NormalTok{(}\FunctionTok{xtable}\NormalTok{(results, }\AttributeTok{caption =} \StringTok{"Placebo Test Results for Different Cutoff Point"}\NormalTok{,}
    \AttributeTok{label =} \StringTok{"tab:movement\_cutoff"}\NormalTok{), }\AttributeTok{include.rownames =} \ConstantTok{FALSE}\NormalTok{, }\AttributeTok{type =} \StringTok{"latex"}\NormalTok{, }\AttributeTok{print.results =} \ConstantTok{FALSE}\NormalTok{)}
\FunctionTok{write}\NormalTok{(latex\_code, }\AttributeTok{file =} \FunctionTok{paste}\NormalTok{(working\_directory, }\StringTok{"result\_tables/movement\_cutoff.tex"}\NormalTok{,}
    \AttributeTok{sep =} \StringTok{"/"}\NormalTok{))}
\FunctionTok{print}\NormalTok{(results)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##   Cutoff Estimate     SE      Z PValue Bandwidth EffectiveObs
## 1   0.15   0.0331  0.032   1.03  0.301    0.0427        31371
## 2   0.20   0.0424 0.0318   1.33  0.183    0.0418        31560
## 3   0.25   0.0153 0.0229  0.668  0.504    0.0809        56751
## 4   0.30  -0.0233 0.0219  -1.06  0.289    0.0996        64315
## 5   0.35   -0.025 0.0199  -1.26  0.209     0.134        76718
## 6   0.50  -0.0102 0.0267 -0.383  0.702     0.113        41909
## 7   0.65   0.0588 0.0372   1.58  0.113       0.1        21900
## 8   0.70  -0.0311 0.0316 -0.984  0.325     0.154        29610
\end{verbatim}

\end{document}

### 2024-06-09 archive/RD design archived.Rmd
modified:   analysis/RD design analysis.Rmd 	new file:   analysis/RD-design-analysis.log 	new file:   analysis/RD-design-analysis.tex 	new file:   analysis/RD_Plot_1st_Order.pdf 	new file:   analysis/RD_Plot_2nd_Order.pdf 	new file:   analysis/RD_Plot_3rd_Order.pdf 	new file:   analysis/donut_robust.tex 	new file:   archive/RD design archived.Rmd 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	new

--- 2024-01-05 analysis/RD design analysis.Rmd
@@
 library(latex2exp) # this is to export it
+setwd("E:/umich/RealEstateBrokerage-main")
+# need to place data on the base directory
+data <- read_dta("template.dta")
 ```
@@
 ```{r}
-result
-```
+h = 0.066
+cutoff = 0.41
+running_var = panel_data$nearest_store_distances
 
-```{r}
-pander(cbind(result$coef, result$pv))
-```
+filtered_data <- panel_data[abs(running_var - cutoff) <= h, ]
 
-```{r}
-result <- rdrobust(y = panel_data$ln_income, x = panel_data$nearest_store_distances, 
-                   c = 0.41,
-                   p = 1) # first using default clustering
+# Export the first RD plot to its own PDF file
+pdf("RD_Plot_1st_Order.pdf", width = 8, height = 4) # Adjust the width and height as needed
+rdplot(y = filtered_data$ln_income, 
+       x = filtered_data$nearest_store_distances, 
+       c = cutoff, nbins = 40, p = 1,
+       title = "RD-plot 1st order polynomial",
+       x.label = "Nearest distance to Lianjia's stores",
+       y.label = "Log of income in the community")
+dev.off() # Close the PDF device
+
+# Export the second RD plot to its own PDF file
+pdf("RD_Plot_2nd_Order.pdf", width = 8, height = 4) # Adjust the width and height as needed
+rdplot(y = filtered_data$ln_income, 
+       x = filtered_data$nearest_store_distances, 
+       c = cutoff, nbins = 40, p = 2,
+       title = "RD-plot 2nd order polynomial",
+       x.label = "Nearest distance to Lianjia's stores",
+       y.label = "Log of income in the community")
+dev.off() # Close the PDF device
+
+# Export the third RD plot to its own PDF file
+pdf("RD_Plot_3rd_Order.pdf", width = 8, height = 4) # Adjust the width and height as needed
+rdplot(y = filtered_data$ln_income, 
+       x = filtered_data$nearest_store_distances, 
+       c = cutoff, nbins = 40, p = 3,
+       title = "RD-plot 3rd order polynomial",
+       x.label = "Nearest distance to Lianjia's stores",
+       y.label = "Log of income in the community")
+dev.off() # Close the PDF device
+
 ```
@@
 ```{r}
-result
+result <- rdrobust(y = panel_data$pop, x = panel_data$nearest_store_distances, 
+                   c = 0.41,
+                   p = 1) # first using default clustering
+result2 <- rdrobust(y = panel_data$light, x = panel_data$nearest_store_distances, 
+                   c = 0.41,
+                   p = 1)
+result3 <- rdrobust(y = panel_data$ln_end_price, x = panel_data$nearest_store_distances, 
+                   c = 0.41,
+                   p = 1)
+```
+
+```{r}
+pander(cbind(result$coef, result$pv))
+pander(cbind(result2$coef, result2$pv))
+pander(cbind(result3$coef, result3$pv))
 ```
@@
 ```{r}
-h = 0.095
+h = 0.124
 cutoff = 0.41
@@
 par(mfrow=c(3,1))
-rdplot(y = filtered_data$ln_income, 
+rdplot(y = filtered_data$ln_lead, 
        x = filtered_data$nearest_store_distances, 
@@
 
-rdplot(y = filtered_data$ln_income, 
+rdplot(y = filtered_data$ln_lead, 
        x = filtered_data$nearest_store_distances, 
@@
 
-rdplot(y = filtered_data$ln_income, 
+rdplot(y = filtered_data$ln_lead, 
+       x = filtered_data$nearest_store_distances, 
+       c = cutoff, nbins = 40, p = 3,
+       title = "RD-plot",
+       x.label = "nearest distance to lianjia's stores",
+       y.label = "lianjia's income in the community")
+```
+
+```{r}
+h = 0.158
+cutoff = 0.41
+running_var = panel_data$nearest_store_distances
+
+filtered_data <- panel_data[abs(running_var - cutoff) <= h, ]
+
+par(mfrow=c(3,1))
+rdplot(y = filtered_data$price_concession, 
+       x = filtered_data$nearest_store_distances, 
+       c = cutoff, nbins = 40, p = 1,
+       title = "RD-plot",
+       x.label = "nearest distance to lianjia's stores",
+       y.label = "lianjia's income in the community")
+
+rdplot(y = filtered_data$price_concession, 
+       x = filtered_data$nearest_store_distances, 
+       c = cutoff, nbins = 40, p = 2,
+       title = "RD-plot",
+       x.label = "nearest distance to lianjia's stores",
+       y.label = "lianjia's income in the community")
+
+rdplot(y = filtered_data$price_concession, 
        x = filtered_data$nearest_store_distances, 
@@
 ```
+
+```{r}
+results <- data.frame(
+  Cutpoint = numeric(),
+  Bandwidth = numeric(),
+  LogDiff = numeric(),
+  SE = numeric(),
+  ZStat = numeric(),
+  PValue = numeric()
+)
+
+h = 0.066
+cutoff = 0.41
+running_var = panel_data$nearest_store_distances
+
+filtered_data <- panel_data[abs(running_var - cutoff) <= h, ]
+
+# 定义切点和带宽的向量
+cutpoints <- c(0.41)
+bandwidths <- c(0.60, 0.063, 0.066, 0.069, 0.72)
+
+results_list <- list()
+
+# 循环遍历切点和带宽
+counter <- 1
+for (cutpoint in cutpoints) {
+  for (bw in bandwidths) {
+    # 运行 McCrary Sorting Test 并捕获输出
+    capture_output <- capture.output(result <- DCdensity(filtered_data$nearest_store_distances, cutpoint = cutpoint, bw = bw, verbose = TRUE, plot = FALSE))
+
+    # 提取结果
+    log_diff <- as.numeric(sub(".*Log difference in heights is\\s+([-+]?\\d*\\.\\d+).*", "\\1", capture_output[grep("Log difference in heights is", capture_output)]))
+    se <- as.numeric(sub(".*with SE\\s+([-+]?\\d*\\.\\d+).*", "\\1", capture_output[grep("with SE", capture_output)]))
+    z_stat <- as.numeric(sub(".*this gives a z-stat of\\s+([-+]?\\d*\\.\\d+).*", "\\1", capture_output[grep("this gives a z-stat of", capture_output)]))
+    p_value <- as.numeric(sub(".*and a p value of\\s+([-+]?\\d*\\.\\d+).*", "\\1", capture_output[grep("and a p value of", capture_output)]))
+
+    # 将结果存储到列表中
+    results_list[[counter]] <- data.frame(
+      Cutpoint = cutpoint,
+      Bandwidth = bw,
+      LogDiff = log_diff,
+      SE = se,
+      ZStat = z_stat,
+      PValue = p_value
+    )
+    counter <- counter + 1
+  }
+}
+
+# 将结果列表转换为数据框
+results <- do.call(rbind, results_list)
+
+# 打印结果数据框
+print(results)
+```

### 2024-06-09 manuscript/main.tex
modified:   analysis/RD design analysis.Rmd 	new file:   analysis/RD-design-analysis.log 	new file:   analysis/RD-design-analysis.tex 	new file:   analysis/RD_Plot_1st_Order.pdf 	new file:   analysis/RD_Plot_2nd_Order.pdf 	new file:   analysis/RD_Plot_3rd_Order.pdf 	new file:   analysis/donut_robust.tex 	new file:   archive/RD design archived.Rmd 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	new

@@
 
-The second hand housing transaction data was collected form \href{https://bj.lianjia.com/}{lianjia.com} for ten cities ranging from 2016 to 2022.
+The second hand housing transaction data was collected form \href{https://www.ke.com/city/}{beke.com} for ten cities ranging from 2016 to 2022.
 Initially, we filtered out transaction records exhibiting unusually high prices, identifying them as outliers that could skew the analysis.
@@
 
+\input{../result_tables/rdd_result_summary.tex}
+
 From Figure \ref{fig:RD_design} we can see that there is indeed discontinuity in 410 meters of communities to the nearest Lianjia's store, which is pretty close to the lianjia's 5-minute walk distance policy.
@@
 This phenomenon can be attributed to the implementation of the Lianjia's proximity to customers policy, which is evidenced at the data level.
+Table \ref{tab:rd_bandwidth_kernel_results} considers different kernel and bandwidth choices, and the results are consistent with the 410 meters radius.
+The only non-significance is the CER-optimal bandwidth selector with triangular kernel, which is because the selected bandwidth is too small to capture the discontinuity.
+The results are robust to different bandwidth and kernel choices, which suggests that the 410 meters is the optimal radius for Lianjia's offline stores.
 
@@
 Furthermore, we carry out the density test by \citep{MCCRARY2008698}.
-The result shows that the p-value is greater than 0.1, which suggests the result is not due to manipulation of polygons.
-Finally, we carry out placebo tests which are reported in Appendix, which strengthens the case for a true treatment effect.
+The result shows that the p-value is greater than 0.1 (p value equals 0.101), which suggests the result is not due to manipulation of polygons.
+Finally, we carry out placebo tests which are reported in Appendix, which shows that our result is robust.
+Specifically, Table \ref{tab:placebo_test_results} shows that the discontinuity does not exist in the placebo test, which suggests that our result is not due to the manipulation of the data.
+Table \ref{tab:movement_cutoff} shows that other cutoffs do not have the same effect as the 410 meters cutoff, which suggests that the 410 meters is the optimal radius for Lianjia's offline stores.
 
@@
 \input{../figures/distribution_of_hp_and_broker.tex}
+
+\input{../result_tables/donut_robust.tex}
+
+\input{../result_tables/rdd_placebo_test.tex}
+
+\input{../result_tables/movement_cutoff.tex}
 

### 2024-06-10 manuscript/main.tex
modified:   manuscript/main.tex

@@
 
-In the Appendix Table \ref{tab:} we also report the results of the robustness check of the dynamic model. The results show that the dynamic model
+In the Appendix Table \ref{tab:sylized_fact_hetero_hhi} we also report the results of the robustness check of the dynamic model.
+The results show that the dynamic model Table \ref{tab:sylized_fact_hetero_mature}
 

### 2024-06-10 manuscript/main.tex
renamed:    analysis/working on district level.do -> archive/working on district level.do 	modified:   manuscript/main.aux 	modified:   manuscript/main.blg 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

@@
 
-To gather other characteristics information, we first extracted the POI data from the AutoNavi map using the web-scrawling Python program.\footnote{AutoNavi, a leading mapping application in China with a huge user base of more than 700 million, stands out for its detailed and accurate POI data and precise public transportation information.
-These features underscore AutoNavi's formidable lead in the digital mapping sector, highlighting its ability to provide unparalleled navigation accuracy and comprehensive urban mobility solutions.
-Our extracted AutoNavi map contains more than 1 million POIs for each city in each year.} We then classified the extracted POIs into different categories, the specifics of which are discussed in detail in Table \ref{tab:statistical}.
-This categorization was crucial for understanding the urban infrastructure and amenities available in the vicinity of the analyzed properties.
-We prioritized POIs within a 500-meter radius-a distance typically covered within a ten-minute walk, consistent with urban planning standards for accessible urban design.
-This radius was specifically chosen to reflect the immediate urban environment that influences residential desirability and value, as the majority of these POIs provide recreational services.
-Furthermore, some geo-informational data was also integrated into our research data, which consists of the annual gdp obtained from \citep{zhao_forecasting_2017}, nighttime lights data, obtained from \citep{elvidge_annual_2021} and air pollution data from \citep{doi:10.1021/acs.est.1c05309}.
-By merging these data with our research panel, we finally get the data.
+To gather additional characteristic information, we first extracted Point of Interest (POI) data from the AutoNavi map using a web-scraping Python program.\footnote{AutoNavi, a leading mapping application in China with a user base exceeding 700 million, is renowned for its detailed and accurate POI data as well as precise public transportation information.
+These features underscore AutoNavi's leadership in the digital mapping sector, highlighting its ability to provide unparalleled navigation accuracy and comprehensive urban mobility solutions.
+Our extracted AutoNavi dataset includes over one million POIs per city annually.} The extracted POIs were then classified into various categories, as detailed in Table \ref{tab
+}. This classification is crucial for understanding the urban infrastructure and amenities available in the vicinity of the analyzed properties.
+
+We matched each type of POI to the neighborhood-level data within a 500-meter radius, a distance typically covered by walking and consistent with urban planning standards for accessible urban design.
+This radius was also specifically selected to reflect the immediate urban environment influencing residential desirability and property values, as the majority of these POIs provide recreational services.
+Additionally, we integrated geo-informational data into our research, including annual GDP data from \citet{zhao_forecasting_2017}, nighttime lights data from \citet{elvidge_annual_2021}, and air pollution data from \citet{doi:10.1021/acs.est.1c05309}.
+We generated the centroid of the neighborhood-level data's polygon and then extracted the value from the geo-informational data.
+By merging these data sources with our research panel, we constructed a comprehensive research sample.
 
@@
 
-In the Appendix Table \ref{tab:sylized_fact_hetero_hhi} we also report the results of the robustness check of the dynamic model.
+To check the robustness of the result, we calculate the HHI index for each segmented market which is defined as $HHI = \sum_{i=1}^N (s_i)^2$ where $s_i$ is the market share of firm $i$ expressed as a percentage.
+Then we estimate the model by separating the samples to those with high HHI and low HHI where HHI is greater than 2000 and less than 2000.
+The results are shown in Table \ref{tab:sylized_fact_hetero_hhi}.
+The result indicates that
+
+Moreover, to check the heterogeneity issue, we also classifies the we also report the results of the robustness check of the dynamic model.
 The results show that the dynamic model Table \ref{tab:sylized_fact_hetero_mature}

### 2024-06-11 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

@@
 
-To check the robustness of the result, we calculate the HHI index for each segmented market which is defined as $HHI = \sum_{i=1}^N (s_i)^2$ where $s_i$ is the market share of firm $i$ expressed as a percentage.
-Then we estimate the model by separating the samples to those with high HHI and low HHI where HHI is greater than 2000 and less than 2000.
-The results are shown in Table \ref{tab:sylized_fact_hetero_hhi}.
-The result indicates that
-
-Moreover, to check the heterogeneity issue, we also classifies the we also report the results of the robustness check of the dynamic model.
-The results show that the dynamic model Table \ref{tab:sylized_fact_hetero_mature}
+To verify the robustness of our results, we calculated the Herfindahl-Hirschman Index (HHI) for each segmented market, defined as $HHI = \sum_{i=1}^N (s_i)^2$ where $s_i$ is the market share of firm $i$ expressed as a percentage.
+We then estimated the model by dividing the sample into high HHI (greater than 2000) and low HHI (less than 2000) groups.
+The results, shown in Table \ref{tab:sylized_fact_hetero_hhi}, indicate that Lianjia's offline stores have a more substantial impact on transaction properties in more competitive markets compared to more monopolized ones.
+This effect arises from two main factors: first, Lianjia's market power is insufficient to exclude other competitors from entering the market, and second, the area may not be attractive to other competitors, resulting in a larger market share for Lianjia.
+Furthermore, to address the heterogeneity issue, we introduced a dummy variable equal to one if the market already had Lianjia presence before 2016 and estimated the model by separating the sample based on this criterion.
+The results, presented in Table \ref{tab:sylized_fact_hetero_mature}, demonstrate that the years 2017, 2018, and 2019 have a significant positive impact on Lianjia's revenue in this segmented market.
+Another interesting phenomenon observed is that the number of house tours is significant for the years 2018 and 2019 in the lower maturity group, whereas in the higher maturity group, the number of house tours becomes significant in 2020.
+These findings indicate that in less mature markets, the entry of Lianjia drives increased profitability and enhances the attractiveness of its offline store strategy.
+Moreover, this suggests that Lianjia's market entry and subsequent strategies are more immediately impactful in less mature markets.
 
@@
 To facilitate such an analysis, we have constructed a series of dummy variables associated with the presence of the Lianjia within the marketplace, delineated as $pre_2$, $pre_1$ (before entry), $entry$, $post_1$, $post_2$, and $post_3$ (successive post-entry intervals), which encapsulate the respective temporal epochs relative to the Lianjia's entry.
+To eliminate the effect of the well constructed effect, we drop all the variables that have Lianjia's offline stores before the year 2016 to better estimate the effect of Lianjia's entry on the market.
 These binary indicators serve as central regressors within a structured econometric model with $pre_1$ as the control group, described in Equation \eqref{eq:entry_effect}:
@@
 
-In the post-entry periods ($post_1$, $post_2$, and $post_3$), the results vary.
-The first period after entry ($post_1$) shows no significant changes in any of the results.
-However, after two post-entry periods ($post_2$ and $post_3$), there are significant negative effects on both revenue and number of house tours.
-These declines suggest a decline in the performance and engagement of the Lianjia, possibly due to the impact of an epidemic that led to a decrease in revenue and showing
+In the post-entry periods ($post_1$, $post_2$, and $post_3$), the results exhibit notable variations.
+The first period after entry ($post_1$) shows no significant changes in any of the metrics analyzed.
+However, in the subsequent post-entry periods ($post_2$ and $post_3$), there are significant negative effects on both revenue and the number of house tours.
+These declines suggest a deterioration in Lianjia's performance and customer engagement, likely attributable to the impact of the epidemic, which led to a decrease in overall revenue.
+Interestingly, Lianjia's entry does not have a significant effect on price concessions but does show a negative impact on the number of house tours during the epidemic periods.
+This negative effect is also attributed to the epidemic, which reduced the frequency of house tours due to heightened health concerns and mobility restrictions.
 
@@
 
-To check the robustness of the entry effect, we also conduct the
+To verify the robustness of the entry effect, we classified the sample into low and high Herfindahl-Hirschman Index (HHI) groups.
+The results, presented in Table \ref{tab:entry_effect_robustness}, indicate that the entry effect is more pronounced in the high HHI group, with an impact of 6.8\%, and this effect persists into the subsequent period, increasing to 7.8\%.
+However, following the epidemic, the effect becomes significantly negative in the low HHI group, suggesting that the entry effect is more adversely affected by epidemic policies in less concentrated markets.
+Conversely, the effect remains non-significant in the high HHI group.
+Additionally, Lianjia's entry does not significantly influence price concessions in either group, nor does it significantly affect the number of house tours.
+However, post-epidemic, the number of house tours shows a significantly negative effect in the low HHI group, indicating a more substantial decline in customer engagement in less concentrated markets.
 
@@
 
-We treat the year 2016 as the base year, and other settings are consistent with previous table \ref{tab:Dynamic}. The result is reported in Figure \ref{fig:dynamic_effect}
+We treat the year 2016 as the base year, and other settings are consistent with previous table \ref{tab:Dynamic}. The result is reported in Figure \ref{fig:dynamic_effect}.
 
@@
 This strategic integration aims to leverage the unique strengths of each model to foster a more resilient and adaptive economic ecosystem.
+
+To check the robustness of the result, we also calculated the average number of watching times in the beke's website during the sample periods and estimated the model separately (need to further refine and reformulate).
 
@@
 
+\clearpage
+
 \begin{table}[H]
@@
 \end{table}
+
+\clearpage
 

### 2024-06-14 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.blg 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

@@
 
-\subsection{Is Lianjia's ACN strategy profitable?} \label{subsec:acn_strategy}
+\subsection{Estimate Lianjia's platform consolidation effect} \label{subsec:acn_strategy}
 
-In addition to the entry effect of Lianjia, there is another exogenous shock during our study period.
-During our study period, Lianjia came up with the ACN strategy.
+To empirically estimate the effect of Lianjia's platform strategy, we consider a unique exogenous shock that occurred during our study period.
+During our study period, Lianjia implemented the ACN strategy.
 ACN means to subdivide the whole process of buying and selling a house into different parts, and each part is taken charge of by a person or a store.
-For this purpose, Lianjia first absorbed some of its competitors in the previous market into its platform network and started to cooperate with them.
+For this purpose, Lianjia first
+
+Lianjia first absorbed some of its competitors in the previous market into its platform network and started to cooperate with them.
 In addition to this, Lianjia also opened up the form of franchises and gradually started platform integration.

### 2024-06-18 manuscript/main.tex
modified:   analysis/final_analysis.do 	new file:   analysis/individual.do 	modified:   archive/final_analysis.do 	renamed:    cleaning/clean district 8_13.do -> cleaning/clean district.do 	new file:   cleaning/clean individual.do 	new file:   cleaning/merged_back_to_the_individual.ipynb 	modified:   manuscript/main.tex

@@
 
-In the preceding section, our research has been directed toward evaluating the dynamic effect of Lianjia's offline stores operation.
-However, there is an imperative to conduct a more detailed analysis of the impact of Lianjia's entry on regional transaction properties.
-The core of this necessary analysis derives from the premise that the entry of a Lianjia represents an exogenous shock within the respective local segmented market, thus providing a unique opportunity to study the effect of offline expansion on local real estate market.
+In the preceding section, our research concentrated on evaluating the dynamic impact of Lianjia's offline store operations.
+Nevertheless, the presence of a self-selection bias in this dynamic entry factor necessitates the application of causal inference methods to more accurately estimate the effect of Lianjia's offline stores.
+Consequently, we adopted the Difference-in-Difference (DiD) estimation technique.
+The foundation of this analysis is predicated on the assumption that the entry of a Lianjia store constitutes an exogenous shock within the local segmented market, thereby providing a unique natural experiment to examine the effects of offline expansion on the local real estate market.
+Although Lianjia's entry is not a randomized event, the DiD estimation method remains robust in estimating the entry effect by comparing variations in outcome variables before and after Lianjia's entry in the segmented market.
+
 To facilitate such an analysis, we have constructed a series of dummy variables associated with the presence of the Lianjia within the marketplace, delineated as $pre_2$, $pre_1$ (before entry), $entry$, $post_1$, $post_2$, and $post_3$ (successive post-entry intervals), which encapsulate the respective temporal epochs relative to the Lianjia's entry.

### 2024-06-19 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

@@
 We also removed any records that were listed duplicated.
-We finally have a data with length 1,716,579 second-hand house.\footnote{Due to government restrictions, four of these cities did not list the transaction price for each transaction during the study period.} Since most of the offline stores in lianjia are community-based, and most of the information is accurate at the community level, we decided to aggregate the information at the community level to make our panel compatible.
-By taking the average of all transaction information, we constructed the panel data with seven years.
+We finally have a data with length 1,778,647 second-hand houses.\footnote{Due to government restrictions, four of these cities did not list the transaction price for each transaction during the study period.} After cleaning the data, we constructed two research samples: one at the individual transaction level and the other at the neighborhood level.
+The individual transaction sample contains detailed information on each transaction, including the transaction price, transaction date, price concessions, and the number of house tours.
+The neighborhood-level sample aggregates transaction data at the community level, encompassing variables such as the average transaction price and the average number of house tours.
+Additionally, we calculated the annual number of house transactions to capture Lianjia's transaction activity within each neighborhood.
+This data structure enables a comprehensive analysis of the impact of offline stores on housing transactions across both individual and neighborhood dimensions.
 
-To gather additional characteristic information, we first extracted Point of Interest (POI) data from the AutoNavi map using a web-scraping Python program.\footnote{AutoNavi, a leading mapping application in China with a user base exceeding 700 million, is renowned for its detailed and accurate POI data as well as precise public transportation information.
+To gather additional characteristic information, Point of Interest (POI) data was extracted from the AutoNavi map using a web-scraping Python program.\footnote{AutoNavi, a leading mapping application in China with a user base exceeding 700 million, is renowned for its detailed and accurate POI data as well as precise public transportation information.
 These features underscore AutoNavi's leadership in the digital mapping sector, highlighting its ability to provide unparalleled navigation accuracy and comprehensive urban mobility solutions.
-Our extracted AutoNavi dataset includes over one million POIs per city annually.} The extracted POIs were then classified into various categories, as detailed in Table \ref{tab
-}. This classification is crucial for understanding the urban infrastructure and amenities available in the vicinity of the analyzed properties.
+Our extracted AutoNavi dataset includes over one million POIs per city annually.} The extracted POIs were then classified into various categories, as detailed in Table \ref{tab:statistical} and it primarily represents living facilities, entertainment venues, restaurants, hospitals, and other public amenities.
+This classification is crucial for understanding the urban infrastructure and amenities available in the vicinity of the analyzed properties.
 
-We matched each type of POI to the neighborhood-level data within a 500-meter radius, a distance typically covered by walking and consistent with urban planning standards for accessible urban design.
-This radius was also specifically selected to reflect the immediate urban environment influencing residential desirability and property values, as the majority of these POIs provide recreational services.
-Additionally, we integrated geo-informational data into our research, including annual GDP data from \citet{zhao_forecasting_2017}, nighttime lights data from \citet{elvidge_annual_2021}, and air pollution data from \citet{doi:10.1021/acs.est.1c05309}.
-We generated the centroid of the neighborhood-level data's polygon and then extracted the value from the geo-informational data.
-By merging these data sources with our research panel, we constructed a comprehensive research sample.
+Each type of POI was matched to our data within a 500-meter radius, a distance typically covered by walking and consistent with urban planning standards for accessible urban design.
+This radius reflects the immediate urban environment influencing residential desirability and property values, as most of these POIs provide recreational services.
+Additionally, geo-informational data, including annual GDP data from \citet{zhao_forecasting_2017}, nighttime lights data from \citet{elvidge_annual_2021}, and air pollution data from \citet{doi:10.1021/acs.est.1c05309}, was integrated into our research.
+The centroid of the neighborhood-level data's polygon was generated, and values from the geo-informational data were extracted.
+By merging these data sources with our research panel, a comprehensive research sample was constructed.
 
@@
 
-To determine the optimal radius of influence, this research employs a regression discontinuity design (RDD) method to examine the influential radius of offline real estate brokerages.
+To determine the optimal radius of influence, this research employs a regression discontinuity design (RDD) method on the neighborhood level transaction data to examine the influential radius of offline real estate brokerages.
 The dependent variable in this analysis is the transaction revenue generated by Lianjia within a given community, while the independent variable is the community's proximity to the nearest Lianjia store.
@@
 
-In our analysis, we focus on several dependent variables: \emph{the natural logarithm of lianjia's income}, \emph{the price concession} and \emph{the natural logarithm of home tours}.
+In our analysis, we focus on several dependent variables: \emph{the natural logarithm of lianjia's income}, \emph{the natural logarithm of home tours}, \emph{the natural logarithm of transaction period} and \emph{the price concession}.
 To quantify Lianjia's impact, we begin by establishing a key stylized fact, which we develop a Density-Based Index (DBI) index to capture the Lianjia's offline stores' influential ratio.
@@
 
+In column 1 and 2, we estimated the model using the neighborhood-level data and in column 3 and 4, we estiamted the model using the individual-level data, respectively.
 The results show that the share of Linajia's offline stores in total brokerage plays a significant role in the real estate market, especially in terms of revenue and lead time, but not in terms of price concessions.
@@
     \subfloat[Effect to income]{\includegraphics[width=0.5\textwidth]{../figures/did_1.pdf}\label{fig:did_income}}
+    \subfloat[Effect to number of house tours]{\includegraphics[width=0.5\textwidth]{../figures/did_2.pdf}\label{fig:did_lead_times}}
     \hfill % Adds horizontal space between figures
-    \subfloat[Effect to price concession]{\includegraphics[width=0.5\textwidth]{../figures/did_2.pdf}\label{fig:did_price_concession}}
-    \hfill % Adds horizontal space between figures
-    \subfloat[Effect to number of house tours]{\includegraphics[width=0.5\textwidth]{../figures/did_3.pdf}\label{fig:did_lead_times}}
+    \subfloat[Effect to transaction period]{\includegraphics[width=0.5\textwidth]{../figures/did_3.pdf}\label{fig:negotiation_period}}
+    \subfloat[Effect to price concession]{\includegraphics[width=0.5\textwidth]{../figures/did_4.pdf}\label{fig:did_price_concession}}
     \caption{Estimation of ACN Platformization Effect}

### 2024-06-20 manuscript/main.tex
modified:   analysis/individual.do 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	modified:   result_tables/difference_in_difference.tex 	modified:   result_tables/dynamic.tex 	modified:   result_tables/entry_effect.tex 	modified:   result_tables/entry_effect_hetero.tex 	modified:   result_tables/formulate_the_tables.ipynb 	modified:   result_tables/heter_platform_did.tex 	modified:   result_table

@@
 \usepackage{url}
+\usepackage{adjustbox}
 \usepackage[round]{natbib}
@@
 In column 1 and 2, we estimated the model using the neighborhood-level data and in column 3 and 4, we estiamted the model using the individual-level data, respectively.
-The results show that the share of Linajia's offline stores in total brokerage plays a significant role in the real estate market, especially in terms of revenue and lead time, but not in terms of price concessions.
-Specifically, a 1\% increase in a Lianjia's DBI within an area correlates with a 7\% increase in income, as indicated in the log(income) column.
-Furthermore, this increased DBI also leads to a 4\% increase in the number of home tours in the log(lead times) column, underscoring the Lianjia's increased visibility and potential for customer engagement.
-In contrast, the analysis shows no significant effect of DBI on price concessions.
-This finding suggests that while a larger market share increases revenues and the number of house tours, it does not exert pressure to reduce prices through concessions.
+The results show that the share of Linajia's offline stores in total brokerage plays a significant role in the real estate market, especially in terms of revenue and lead time, but not in terms of price concession and transaction period.
+Specifically, a 1\% increase in a Lianjia's DBI within an area correlates with a 7\% increase in income, as indicated in column 1.
+Furthermore, this increased DBI also leads to a 4\% increase in the number of home tours in the column 2, underscoring the Lianjia's increased visibility and potential for customer engagement.
+In contrast, the analysis shows no significant effect of DBI on price concessions and transaction time.
+This finding suggests that while a larger market share increases revenues and the number of house tours, it may not be beneficial for mathcing the buyers and sellers.
 The broader implications point to the strategic advantage of density or market share in driving business performance metrics, except for pricing strategies, which appear to be unaffected by changes in market share.
@@
 ACN means to subdivide the whole process of buying and selling a house into different parts, and each part is taken charge of by a person or a store.
-For this purpose, Lianjia first
-
-Lianjia first absorbed some of its competitors in the previous market into its platform network and started to cooperate with them.
+For this purpose, Lianjia can cooperate with other competitors in the market and integrate their resources to provide a better service to the customers.
+This strategy is a significant change in Lianjia's business model, and it is expected to have a significant impact on the market.
 In addition to this, Lianjia also opened up the form of franchises and gradually started platform integration.
@@
 
-The empirical findings elucidate that prior to the establishment of the ACN, there is an absence of discernible effects attributable to anticipation.
+The empirical findings elucidate that prior toz the establishment of the ACN, there is an absence of discernible effects attributable to anticipation.
 Subsequent results for the fiscal year 2018 reveal that the ACN exerts a considerable influence on revenue generation, yet it manifests no significant impact on the metrics of price concessions and the number of house tours.

### 2024-06-21 manuscript/main.tex
modified:   analysis/final_analysis.do 	modified:   analysis/individual.do 	modified:   cleaning/clean individual.do 	modified:   cleaning/merged_back_to_the_individual.ipynb 	modified:   manuscript/main.tex 	modified:   result_tables/entry_effect_hetero.tex 	modified:   result_tables/formulate_the_tables.ipynb

@@
 Consequently, we adopted the Difference-in-Difference (DiD) estimation technique.
-The foundation of this analysis is predicated on the assumption that the entry of a Lianjia store constitutes an exogenous shock within the local segmented market, thereby providing a unique natural experiment to examine the effects of offline expansion on the local real estate market.
-Although Lianjia's entry is not a randomized event, the DiD estimation method remains robust in estimating the entry effect by comparing variations in outcome variables before and after Lianjia's entry in the segmented market.
+The foundation of this analysis is predicated on the assumption that the entry of a Lianjia store constitutes an exogenous shock within the local segmented market, thereby providing an unique natural experiment to examine the effects of offline expansion on the local real estate market.
+Although Lianjia's entry is not a randomized event, the DiD estimation method remains unbiased in estimating the entry effect by comparing variations in outcome variables before and after Lianjia's entry in the segmented market.
 
@@
 The result presented in the table \ref{tab:entry_effect} examines the effect of Lianjia's offline stores' entry into an area on various outcomes.
-Prior to the Lianjia's entry ($pre_2$), there is no statistically significant effect on any of the three outcomes, suggesting that anticipation of the Lianjia's entry does not affect these metrics.
+Prior to the Lianjia's entry ($pre_2$), there is no statistically significant effect on Lianjia's transaction properties, suggesting that anticipation of the Lianjia's entry does not affect these metrics.
 In addition, there is a significant 4\% increase in revenue after the Lianjia's entry ($entry$), suggesting a substantial increase in Lianjia sales.
@@
 
-To empirically estimate the effect of Lianjia's platform strategy, we consider a unique exogenous shock that occurred during our study period.
+To empirically estimate the effect of Lianjia's platform strategy, we consider an exogenous shock that occurred during our study period.
 During our study period, Lianjia implemented the ACN strategy.

### 2024-06-22 manuscript/main.tex
modified:   analysis/final_analysis.do 	new file:   figures/plotting_parallel_trend.do 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	modified:   result_tables/dynamic.tex 	modified:   result_tables/entry_effect.tex 	modified:   result_tables/entry_effect_hetero.tex 	modified:   result_tables/formulate_the_tables.ipynb 	modified:   result_tables/heter_platform_did.tex 	modified:   result_tables/robust_hhi.tex 	modified:   result_

@@
 \begin{equation}
-    Y_{it} = \rho Y_{it-1} + \beta_0 +  pre_2 + entry + \sum_{i=1}^3 post_i + \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}.   \label{eq:entry_effect}
+    Y_{it} = \beta_0 +  pre_2 + entry + \sum_{i=1}^3 post_i + \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}.   \label{eq:entry_effect}
 \end{equation}
@@
 
-The result presented in the table \ref{tab:entry_effect} examines the effect of Lianjia's offline stores' entry into an area on various outcomes.
-Prior to the Lianjia's entry ($pre_2$), there is no statistically significant effect on Lianjia's transaction properties, suggesting that anticipation of the Lianjia's entry does not affect these metrics.
-In addition, there is a significant 4\% increase in revenue after the Lianjia's entry ($entry$), suggesting a substantial increase in Lianjia sales.
-However, the effect on price concessions and number of showings remains statistically insignificant, suggesting that Lianjia's entry does not lead to significant changes in pricing strategies or the number of showings brought to the area.
+The results presented in the table \ref{tab:entry_effect} analyze the impact of Lianjia's offline stores entering segmented markets.
+Prior to Lianjia's entry ($pre_2$), there is no statistically significant effect on Lianjia's transaction properties, indicating that anticipation of Lianjia's entry does not influence these metrics.
+Post-entry ($entry$), there is a significant 9.1\% increase in revenue, suggesting a substantial boost in Lianjia's sales.
+However, this effect decreases to 4.7\% in the subsequent period ($post_1$) and continues to diminish in the following periods ($post_2$ and $post_3$), indicating a gradual decline in Lianjia's performance after the initial entry period.
+Similarly, the number of house tours exhibits a significant 2.3\% increase during the entry period, followed by a 3.\% increase in the first post-entry period.
+Nonetheless, this effect lessens in $post_2$, though it remains significant in $post_3$.
+This trend is attributed to the impact of the COVID-19 pandemic in 2020, which significantly affected the real estate market and brokerage's operation mode.
 
-In the post-entry periods ($post_1$, $post_2$, and $post_3$), the results exhibit notable variations.
-The first period after entry ($post_1$) shows no significant changes in any of the metrics analyzed.
-However, in the subsequent post-entry periods ($post_2$ and $post_3$), there are significant negative effects on both revenue and the number of house tours.
-These declines suggest a deterioration in Lianjia's performance and customer engagement, likely attributable to the impact of the epidemic, which led to a decrease in overall revenue.
-Interestingly, Lianjia's entry does not have a significant effect on price concessions but does show a negative impact on the number of house tours during the epidemic periods.
-This negative effect is also attributed to the epidemic, which reduced the frequency of house tours due to heightened health concerns and mobility restrictions.
+In terms of the transaction period, the offline store's influence is always not significant, which suggests that the offline store's entry does not help to match the buyers and sellers in searching the houses, which is in line with the intuition that when platform is more mature, people's searching behavior is more likely to be online.
+Lastly, regarding price concessions, the entry of Lianjia's offline stores exhibits a 4.5\% positive effect.
+This suggests that the presence of offline stores may facilitate an increase in price concessions.
+This effect can be attributed to the enhanced efficiency in matching buyers with suitable properties, thereby encouraging sellers to be more amenable to price negotiations.
+Additionally, offline stores possess better control over neighborhood information, which aids in effectively marketing properties to potential buyers, thereby capturing additional surplus.
 
-In summary, the entry of a Lianjia into an area significantly boosts its sales initially, without altering its pricing strategies or viewer engagement significantly.
-However, the positive impact is short-lived, turning negative in subsequent periods, likely exacerbated by external factors like an epidemic.
+In summary, the entry of Lianjia into a segmented market initially results in a significant increase in revenue and facilitates a higher number of house tours, which, in turn, leads to greater price concessions.
+However, this positive impact is transient, diminishing over time due to increased market competition and external factors such as the COVID-19 pandemic.
+This suggests that while Lianjia's entry provides a short-term boost to its market performance, the sustainability of this effect is challenged by both competitive dynamics and unforeseen external shocks.
 
 To verify the robustness of the entry effect, we classified the sample into low and high Herfindahl-Hirschman Index (HHI) groups.
-The results, presented in Table \ref{tab:entry_effect_robustness}, indicate that the entry effect is more pronounced in the high HHI group, with an impact of 6.8\%, and this effect persists into the subsequent period, increasing to 7.8\%.
-However, following the epidemic, the effect becomes significantly negative in the low HHI group, suggesting that the entry effect is more adversely affected by epidemic policies in less concentrated markets.
-Conversely, the effect remains non-significant in the high HHI group.
-Additionally, Lianjia's entry does not significantly influence price concessions in either group, nor does it significantly affect the number of house tours.
-However, post-epidemic, the number of house tours shows a significantly negative effect in the low HHI group, indicating a more substantial decline in customer engagement in less concentrated markets.
+The results, presented in Table \ref{tab:entry_effect_robustness}, indicate that the income effect for Lianjia remains consistent across both groups.
+Specifically, income increases by 9.2\% during the entry period, with the effect decreasing to 5.1\% in the subsequent period for the higher HHI group, and increasing by 9.6\% during the entry period and decreasing to 4.7\% for the lower HHI group.
+However, a significant difference emerges in the number of house tours.
+The entry of Lianjia increases the number of house tours by 2.9\% for the higher HHI group and by 4.4\% for the lower HHI group.
+In the subsequent period, the effect diminishes for the lower HHI group, indicating that the entry of new competitors mitigates Lianjia's entry effect.
+Conversely, the entry effect remains significant for the higher HHI group.
+This analysis underscores the varying impacts of market concentration on Lianjia's market performance post-entry.
+
+Furthermore, in columns 5 and 6, the entry of Lianjia's offline stores significantly shortens the transaction period for the higher HHI group.
+This suggests that offline stores enhance market efficiency by better matching buyers and sellers.
+Conversely, this effect is not significant in the lower HHI group, indicating that the benefits of offline stores diminish in more competitive markets.
+Regarding price concessions, the entry of Lianjia's offline stores does not have a significant effect in the lower HHI group initially.
+However, by the $post_3$ period, the effect becomes significant and positive.
+This delayed impact may be attributed to the offline stores gradually improving market transparency and information dissemination, which eventually leads to better price concessions.
+For the higher HHI group, the entry of Lianjia's offline stores consistently has a significant effect on price concessions.
+This reinforces the notion that in less competitive markets, offline stores play a crucial role in facilitating better matches between buyers and sellers and improving overall market efficiency.
+In the Appendix we also conducted the robustness check by classifying the group by matured market and less matured market.
+[ THERE IS ALSO A GRAPH OF PARALLEL TREND NEED TO BE ADDED HERE.
+]
 
@@
 
-To empirically estimate the effect of Lianjia's platform strategy, we consider an exogenous shock that occurred during our study period.
-During our study period, Lianjia implemented the ACN strategy.
-ACN means to subdivide the whole process of buying and selling a house into different parts, and each part is taken charge of by a person or a store.
-For this purpose, Lianjia can cooperate with other competitors in the market and integrate their resources to provide a better service to the customers.
+To empirically estimate the effect of Lianjia's platform strategy, we consider an exogenous shock that occurred during our study period: Lianjia's implementation of a downstream consolidation strategy.
+This strategy involves the integration of offline stores with online platforms, leveraging the advantages of Lianjia's Agent Cooperation Network (ACN) strategy.
+The ACN strategy subdivides the entire process of buying and selling a house into distinct parts, with each part managed by a specific agent or store.
+By sharing transaction dividends among multiple stores, Lianjia fosters cooperation with other market competitors and integrates their resources to enhance service quality for customers.
+This approach is designed to improve efficiency and customer satisfaction by combining online and offline resources, thus providing a comprehensive and streamlined service experience.
+
 This strategy is a significant change in Lianjia's business model, and it is expected to have a significant impact on the market.
@@
 \begin{equation}
-    Y_{it}  = \beta_0 + \sum_{i=-2}^3 Treatment_{it} * year + \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}. \label{eq:acn_assessment}
+    Y_{it}  = \beta_0 + \sum_{i=1}^5 Treatment_{it} * year + \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}. \label{eq:acn_assessment}
 \end{equation}
 
-We treat the year 2016 as the base year, and other settings are consistent with previous table \ref{tab:Dynamic}. The result is reported in Figure \ref{fig:dynamic_effect}.
+By focusing on 2017 as the baseline, we can empirically estimate the outcomes with greater precision and reliability, ensuring that our analysis accurately reflects the impact of Lianjia's strategy without the confounding effects of prior periods.
+Other settings are consistent with previous table \ref{tab:Dynamic} and the result is reported in Figure \ref{fig:dynamic_effect}.
 
@@
 
-The empirical findings elucidate that prior toz the establishment of the ACN, there is an absence of discernible effects attributable to anticipation.
-Subsequent results for the fiscal year 2018 reveal that the ACN exerts a considerable influence on revenue generation, yet it manifests no significant impact on the metrics of price concessions and the number of house tours.
-This phenomenon indicates that the efficacy of the ACN model does not derive from an augmentation in client base through absorption but rather through the synthesis and integration of comprehensive data on the supply side.
-Post-2018 observations indicate the maturation of the platformization process, evidencing its expanding influence from the supply to the demand sector.
-Notably, a marked negative effect on price concessions is observed, underscoring the ACN's significant role in influencing consumer decision-making processes.
+The empirical findings indicate that during the first year of consolidation, Lianjia's transaction revenue did not show a statistically significant difference from zero.
+However, from 2019 to 2021, the transaction revenue demonstrated a significant positive increase, ranging from 4.9\% to 2.6\%.
+Additionally, the consolidation of the platform had a significantly positive impact on the number of house tours, which increased by 3.9\% to 6.4\% from 2018 to 2022, with this trend continuing upward throughout the sample period.
+Furthermore, when comparing the effect of platform consolidation with the entry effect of offline stores, the data clearly show that the platformization effect is substantially more pronounced.
+This suggests that the platformization strategy is markedly more effective than the offline store entry strategy in generating revenue and attracting buyers in the market.
+These results underscore the superior efficacy of platform consolidation in enhancing market performance and provide compelling evidence for the strategic advantage of platformization over traditional offline expansion.
 
-However, the years 2021 and 2022 witnessed a mitigated advantage of these factors due to the global epidemic, underscoring an imperative insight; despite the foundational establishment of online platformization, the inherent benefits of physical storefronts remain irreplaceable.
-This realization requires a re-evaluation of economic models, advocating a harmonious co-evolution of online and offline market paradigms.
-This strategic integration aims to leverage the unique strengths of each model to foster a more resilient and adaptive economic ecosystem.
+However, in terms of the transaction period, the platformization strategy does not exhibit a significant effect, indicating that platformization does not assist brokerages in facilitating better matching and negotiation between sellers and buyers.
+A similar pattern is observed in price concessions, suggesting that the platformization strategy does not contribute to reducing price concessions.
+While the platformization strategy is less effective in influencing individuals' decision-making processes compared to offline store entry, it proves more effective in increasing revenue and the number of house tours.
+This discrepancy highlights that the platformization strategy excels in attracting customers and generating revenue, but falls short in aiding the matching and negotiation process.
+These findings align with the intuition that platformization is more likely to draw customers and boost revenue, yet it is less effective in assisting buyers and sellers in reaching agreements.
 
-To check the robustness of the result, we also calculated the average number of watching times in the beke's website during the sample periods and estimated the model separately (need to further refine and reformulate).
+To further investigate the impact of market concentration on the effectiveness of the platformization strategy, we classified the samples into high and low Herfindahl-Hirschman Index (HHI) groups and estimated the model separately for each group.
+The high HHI group, representing markets with higher concentration, revealed that the platformization strategy does not confer significant benefits for Lianjia's operations.
+Conversely, in the low HHI group, indicative of less competitive markets, the platformization strategy significantly increases revenue.
+This suggests that the platformization strategy is more effective in less competitive markets, enhancing Lianjia's competitiveness.
+In terms of the number of house tours, the effect of platformization is consistent across both high and low HHI groups.
+This consistency aligns with the intuition that consumer preferences for different types of brokerages are similar, and individuals are equally likely to search for houses online regardless of the brokerage's market share.
+Moreover, our analysis in columns 5 to 8 shows that the platformization strategy does not have a significant effect on the transaction period or price concessions.
+This finding suggests that the platformization strategy does not facilitate better matching between buyers and sellers or improve the negotiation process.
+This aligns with the intuition that while the platformization strategy can attract more customers and generate revenue, it does not inherently improve the efficiency of matching buyers and sellers or negotiating terms because most of the transactions are still offline based.
 

### 2024-06-22 manuscript/main.tex
update the latest result

@@
 
+In the online Appendix \ref{tab:platform_consolidation_hetero_mature}, we present the heterogeneous effects of Lianjia's operations in both mature and immature markets.
+Figure \ref{fig:treatment_consolidation} illustrates the distribution of income across the treatment and control groups.
+Prior to the intervention, the two groups exhibit parallel trends, indicating no significant differences.
+The treatment effect becomes significant only after the first period, aligning with our empirical findings.
+
 \section{Conclusion and Discussion} \label{sec:conclusion}
@@
     \caption{Robustness Check By HHI Index}
-    \label{tab:sylized_fact_hetero_hhi}
+    \label{tab:dynamic_hhi}
     \input{../result_tables/robust_hhi.tex}
@@
     \caption{Robustness Check By Market Maturity Index}
-    \label{tab:sylized_fact_hetero_mature}
+    \label{tab:platform_consolidation_hetero_mature}
     \input{../result_tables/robust_mature.tex}
@@
 \end{table}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.7\textwidth]{../figures/average_income_by_treatment_platform.pdf}
+    \caption{Treatment Effect of platform consolidation}
+    \label{fig:treatment_consolidation}
+    Note: the x-axis is year and the y-axis is the average income of Lianjia in each year. The graph uses the neighborhood-level data.
+\end{figure}
 

### 2024-06-22 manuscript/main.tex
update teh result

@@
 However, prior to 2018, the platform Beke primarily focused on facilitating listings from Lianjia's offline stores and aimed to attract buyers from the market.
-However, in 2018, Beke established a new strategy named Agent Cooperate Network (ACN), which integrates and shares the content across its multiple subsidiaries to realize multiple revenue models simultaneously.\footnote{The ACN model disaggregates the transaction process into specialized tasks handled by individual agents or stores.
-These tasks include seller-side activities such as sourcing sellers, maintaining property listings, commission negotiations, and buyer-side activities like client acquisition, property-client matching, transaction facilitation, and financial services assistance.}
+However, in 2014, Beke established a new strategy named Agent Cooperate Network (ACN), which integrates and shares the content across its multiple subsidiaries to realize multiple revenue models simultaneously.\footnote{The ACN model disaggregates the transaction process into specialized tasks handled by individual agents or stores.
+These tasks include seller-side activities such as sourcing sellers, maintaining property listings, commission negotiations, and buyer-side activities like client acquisition, property-client matching, transaction facilitation, and financial services assistance.} Moreover, in 2018, Lianjia decided to enhance its Agent Cooperation Network (ACN) strategy by incorporating smaller brokerages into its network and launching franchise stores under the brand name Deyou, along with other smaller formats.
+This strategic move aimed to increase network effects and further consolidate the platform, thereby enhancing market power and operational efficiency.
 
-Through the ACN model, Lianjia transforms internal competition within the system into overall system competitiveness, thereby enhancing the brand's reputation and market influence.
-More importantly, this strategic allows Lianjia to cooperate with other previously competitors by consolidating resources and forms a consolidation.
+Through the success of the platform consolidation, Lianjia transforms internal competition within the system into overall system competitiveness, thereby enhancing the brand's reputation and market influence.
+More importantly, this strategic allows Lianjia to cooperate with other previously competitors by consolidating resources.
 For instance, data from AutoNavi Map and CREIS indicate that in 2020, although only about 20\% of real estate agent stores in the main urban area of Chengdu City are Lianjia's offline stores, these stores achieved a market share of 73.98\%.
@@
 
-While sellers may consider a multi-homing strategy—listing their property with multiple brokerages—this approach is suboptimal for several reasons.
-Firstly, the exclusivity of contracts between sellers and agents often precludes the adoption of a multi-homing strategy.
-Secondly, although sellers can list their properties with multiple brokerages, smaller agencies frequently lack a sufficiently broad client base, limiting their effectiveness in selling homes.Thirdly, engaging multiple brokers simultaneously can lead to reduced incentives among agents, as they perceive competition for the same property, diminishing their proactive efforts.
+While sellers might consider a co-listing strategy—listing their property with multiple brokerages—this approach is suboptimal for several reasons within China's real estate market.
+Despite previous literature, such as \citep{RePEc:kap:jrefec:v:67:y:2023:i:3:d:10.1007_s11146-021-09858-w}, indicating that the co-listing can be beneficial for clients under multiple-listing service.
+Specifically in China's real estate market, firstly, the exclusivity of contracts between sellers and agents often precludes the adoption of a co-listing strategy.
+Secondly, although sellers can list their properties with multiple brokerages, smaller agencies frequently lack a sufficiently broad client base, limiting their effectiveness in selling homes.
+Thirdly, engaging multiple brokers simultaneously can lead to reduced incentives among agents, as they perceive competition for the same property, diminishing their proactive efforts.
 Finally, while service cost variations between agencies are acknowledged, these costs are minor compared to the property's value and are more closely related to the risks associated with holding a financial asset.
@@
 
-To assess the consolidation effect of the online platform, we treat the year Lianjia implemented the Agent Cooperate Network (ACN) strategy as an exogenous shock to the market.
+To assess the consolidation effect of the online platform, we treat the year Lianjia implemented the platform consolidation strategy as an exogenous shock to the market.
+The platform consolidation strategy is majorly based on the Agent Cooperation Network (ACN) framework of Lianjia, where Lianjia can divide the process of transaction to multiple agents.
 Our findings reveal that this strategy substantially boosts revenues and alters consumer behaviors, particularly in the number of house tours facilitated by the brokerage.

### 2024-06-23 manuscript/main.tex
modified:   analysis/final_analysis.do 	modified:   analysis/individual.do 	modified:   cleaning/clean district.do 	modified:   manuscript/main.aux 	modified:   manuscript/main.bbl 	modified:   manuscript/main.blg 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	new file:   manuscript/main.pdf 	deleted:    manuscript/main.synctex(busy) 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	new file:   result_tables/code_book_table.tex 	modified:   result_tables/formulate_the_tables.ipynb 	new file:   result_tables/st

@@
 The Table \ref{tab:precise_proportion_contraction} shows the comparision of the market share of Lianjia and the share of the number of stores in the market.
+[NEED TO ADD A FIGURE OR TABLE]
 
@@
 These features underscore AutoNavi's leadership in the digital mapping sector, highlighting its ability to provide unparalleled navigation accuracy and comprehensive urban mobility solutions.
-Our extracted AutoNavi dataset includes over one million POIs per city annually.} The extracted POIs were then classified into various categories, as detailed in Table \ref{tab:statistical} and it primarily represents living facilities, entertainment venues, restaurants, hospitals, and other public amenities.
+Our extracted AutoNavi dataset includes over one million POIs per city annually.} The extracted POIs were then classified into various categories, as detailed in Table \ref{tab:statistical_district} and Table \ref{tab:statistical_individual} and it primarily represents living facilities, entertainment venues, restaurants, hospitals, and other public amenities.
 This classification is crucial for understanding the urban infrastructure and amenities available in the vicinity of the analyzed properties.
@@
 
-From Table \ref{tab:statistical} we can see that the in our metro areas, the neighborhoods with lianjia within the influential radius tends to have higher number of sales, and the final transaction price is also \textyen 910,000 higher than those neighborhoods without lianjia.
+From Table \ref{tab:statistical_district} we can see that the in our metro areas, the neighborhoods with lianjia within the influential radius tends to have higher number of sales, and the final transaction price is also \textyen 910,000 higher than those neighborhoods without lianjia.
 Moreover, the number of other stores within the influential distance is also signnificantly more than 7.3, which also aligns with our previous intuition that the market is not monopolized by Lianjia.
@@
     \begin{tiny}
-    \caption{Statistical Summary}
-    \input{../result_tables/summary_statistics.tex}
-    \label{tab:statistical}
+    \caption{Statistical Summary for the Neighborhoods-Data with Lianjia and without Lianjia}
+    \input{../result_tables/summary_statistics_district.tex}
+    \label{tab:statistical_district}
+
+    Note that the code book of the variables can be seen in the Appendix \ref{tab:codebook}
+    \end{tiny}
+\end{table}
+
+\begin{table}[htb!]
+  \centering
+  \begin{tiny}
+  \caption{Statistical Summary for the Individual-Data with Lianjia and without Lianjia}
+  \input{../result_tables/summary_statistics_indi.tex}
+  \label{tab:statistical_individual}
+
+  Note that the code book of the variables can be seen in the Appendix \ref{tab:codebook}
   \end{tiny}  
@@
 
-    Note: we omit all the control variables in the regression model, and detailed descriptions can be seen from Table \ref{tab:statistical}
+    Note: we omit all the control variables in the regression model, and detailed descriptions can be seen from Table \ref{tab:statistical_district} and Table \ref{tab:statistical_individual}.
     \label{tab:stylized_fact}
@@
 
-    Note: we omit all the control variables in the regression model, and detailed descriptions can be seen from Table \ref{tab:statistical}
+    Note: we omit all the control variables in the regression model, and detailed descriptions can be seen from Table \ref{tab:statistical_district} and Table \ref{tab:statistical_individual}.
     \end{scriptsize}
@@
 
-    Note: we omit all the control variables in the regression model, and detailed descriptions can be seen from Table \ref{tab:statistical}.
+    Note: we omit all the control variables in the regression model, and detailed descriptions can be seen from Table \ref{tab:statistical_district} and Table \ref{tab:statistical_individual}.
     \end{scriptsize}
@@
 \end{figure}
+
+\begin{table}[H]
+  \begin{center}
+    \begin{scriptsize}
+    \caption{Codebook}
+    \label{tab:codebook}
+    \input{../result_tables/code_book_table.tex}
+
+    \end{scriptsize}
+  \end{center}
+\end{table}
 

### 2024-06-23 result_tables/code_book_table.tex
modified:   analysis/final_analysis.do 	modified:   analysis/individual.do 	modified:   cleaning/clean district.do 	modified:   manuscript/main.aux 	modified:   manuscript/main.bbl 	modified:   manuscript/main.blg 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	new file:   manuscript/main.pdf 	deleted:    manuscript/main.synctex(busy) 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	new file:   result_tables/code_book_table.tex 	modified:   result_tables/formulate_the_tables.ipynb 	new file:   result_tables/st

\begin{tabular}{lll}
\toprule
Name & Label & Dimension \\
\midrule
income & The income lianjia in this given district/housing. & $10^5 \times$ \textyen \\
lead\_times & The time it takes before a deal is made. & counts \\
price\_concession & price changes (ending price - starting price) / starting price & \% \\
density & percentage of lianjia to all brokerages & \% / 100 \\
broker\_410 & number of other brokerages within 410 meters, which is the cutoff of RD & counts \\
watching\_people & The number of people watching this listing. & counts \\
end\_price & The final agreed price. & \textyen \\
non\_online\_effect & without online platformization influence & bool indicator \\
watched\_times & The number of times a listing is watched. & counts \\
nego\_times & The number of times a negotiation was held. & counts \\
nego\_period & The period over which negotiations took place. & days \\
jiadian & Referring to electronic shops. & counts \\
kind & Referring to proximity to kindergartens & counts \\
hotel & Referring to proximity to hotels & counts \\
shop\_mall & Referring to shopping mall. & counts \\
museum & Distance to the nearest museum. & counts \\
old & Referring to old care systems. & counts \\
ktv & Referring to KTV and some entertainment venues. & counts \\
mid & Referring to middle schools. & counts \\
prim & Referring to primary schools. & counts \\
west\_food & Referring to the availability of western food nearby. & counts \\
super & Referring to proximity to supermarkets (measured by number within given distance & counts \\
sub & Referring to proximity to subway stations. & counts \\
park & Referring to parks. & counts \\
area & The area of a property. & $m^2$ \\
bedroom & The number of bedrooms in a property. & counts \\
toilet & The number of toilets in a property. & counts \\
house\_age & The age of the house. & years \\
floor\_level & The level on which a particular room or apartment is, within a building. & categories \\
green\_ratio & The ratio of the green space to the total plot area. & \% / 100 \\
total\_building & The total number of buildings in an area. & counts \\
total\_floor\_number & The number of floors in a building. & counts \\
living\_room & The number of living rooms in a property. & counts \\
elevator\_ratio & The ratio of elevators to the total number of floors. & \% / 100 \\
kitchen & The number of kitchens in a property. & counts \\
floor\_ratio & The ratio of the floor area to the total plot area. & fraction \\
total\_resident & The total number of residents in an area. & counts \\
pm25 & Air quality measure. & mass/volume \\
pop & Population density. & people/$km^2$ \\
light & Night time lights. & lux \\
\bottomrule
\end{tabular}

### 2024-06-23 manuscript/main.tex
new file:   figures/distribution_of_ten_cities.pdf 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	new file:   plotting/plotting_distribution_of_offline_stores_in_different_cities.R

@@
     \noindent This study examines the impact of offline store expansion by Lianjia, China's leading real estate brokerage, within the framework of platform consolidation.
-By analyzing micro-level transactions of second-hand houses in ten major Chinese cities from 2016 to 2022, the research investigates how the transaction patterns of traditional brokerages, characterized by strategic clustering of offline stores, transition towards online consolidation, thereby facilitating the development of an extensive franchise network.
-Utilizing a regression discontinuity (RD) design, the study quantifies the optimal influence radius of these stores on housing transactions.
-Incorporating this optimal influence radius, the study further investigates the exogenous shock of Lianjia's market entry, identifying a significant increase in transaction revenues before the Covid-19.
-However, this effect is attenuated during the Covid-19 period due to remote work and other restrictive policies implemented by the Chinese government.
-Additionally, the paper explores the impact of Lianjia's Agent Cooperation Network (ACN) strategy on its platform consolidation effect, concluding that this strategy enhances Lianjia's revenue generation and facilitates transactions.
-This study provides valuable insights into the synergy between offline store expansion and online platform development, highlighting future trajectories in the evolving real estate brokerage market.
+By analyzing micro-level transactions of second-hand houses in ten major Chinese cities from 2016 to 2022, the research investigates how the transaction patterns of traditional brokerages, characterized by the strategic clustering of offline stores, transition towards online consolidation, thereby facilitating the development of an extensive franchise network.
+Utilizing a regression discontinuity (RD) design, the study quantifies the optimal influence radius of offline stores on housing transactions.
+Incorporating this optimal influence radius, the study further empirically estimates the effects of real estate brokerage's offline store expansion and online platform consolidation on transaction properties.
+This analysis leverages the exogenous shock of Lianjia's market entry, identifying a significant increase in transaction revenues before the COVID-19 pandemic.
+However, this effect diminishes during the pandemic due to remote work and restrictive policies implemented by the Chinese government.
+The study also examines the online platform consolidation effect by analyzing the period in 2018 when Lianjia revised and improved its Agent Cooperation Network (ACN).
+
+    \textbf{The results indicate that this strategy significantly boosts revenues and also suggest that the offline store's effect is majorly focused on people's transaction behaviors but the online platform's effect can be more insightful to provide a more efficient transaction process.
+} % this need to be revised.
+
+    This study provides valuable insights into the synergy between offline store expansion and online platform development, elucidating future trajectories in the evolving real estate brokerage market and analogous sectors.
   \end{abstract}
 
-  \textbf{Keyword}: Marketing Strategy, Housing Markets, Digital Platforms
+  \textbf{Keyword}: Marketing Strategy, Digital Platforms, Platform Consolidation, Real Estate Brokerage
 
@@
 
-In the real estate market, transaction cost is a critical factor for both buyers and sellers.
-Minimizing these costs has made the selection of competent real estate agencies a significant priority for both parties.
-Real estate brokers not only help in reducing transaction costs but also provide essential market information, negotiation support, and legal assistance, thereby ensuring smoother and more efficient transactions.
-Especially in the context of China's burgeoning real estate market, brokerage firms are assuming an increasingly important role in facilitating the communication channel between buyers and sellers \citep{glaeser_real_2017}.
-Their expertise and local market knowledge have become indispensable in navigating the complex real estate landscape.
+Understanding housing markets is crucial due to their significant impact on household finance, as housing is typically the largest component of a household's portfolio.
+The illiquidity of housing creates a strong link between housing and labor markets, and transaction costs are critical for buyers and sellers in the real estate market.
+Real estate brokers play a vital role in reducing these costs, providing essential market information, negotiation support, and legal assistance to ensure smoother and more efficient transactions.
+With the improvement of China's legal system in the real estate market, the brokerage market is expanding and becoming more prosperous.
+Especially in the context of China's burgeoning real estate market, brokerage firms are assuming an increasingly important role in facilitating the communications between buyers and sellers \citep{glaeser_real_2017}.
+Given the heterogeneous and "thin" nature of real estate goods \citep{HAN2015813}, the expertise and local market knowledge of real estate brokers have become indispensable in navigating the complex real estate landscape.
 
@@
 Brokerage consolidation, a process where larger firms absorb smaller ones into a unified platform, is emerging as a transformative trend, redefining how properties are bought and sold across China.
-
 Lianjia, the largest real estate brokerage in China, has revolutionized real estate transactions through the establishment of the Beke platform.
@@
 More importantly, this strategic allows Lianjia to cooperate with other previously competitors by consolidating resources.
-For instance, data from AutoNavi Map and CREIS indicate that in 2020, although only about 20\% of real estate agent stores in the main urban area of Chengdu City are Lianjia's offline stores, these stores achieved a market share of 73.98\%.
+According to the IPO prospectus by Beke, the market share of Lianjia is around 20.8\% in year 2020 in China's second hand housing market and the number of stores share in the whole China is less than 5\% according to the AutoNavi map and moreover, in large cities like Chengdu, Beijing and Shanghai, the second hand housing share of Lianjia is even larger to
+
 This remarkable market penetration underscores the efficacy of Beke's integrated platform and ACN model in dominating the real estate brokerage landscape.
-The Table \ref{tab:precise_proportion_contraction} shows the comparision of the market share of Lianjia and the share of the number of stores in the market.
+The Figure \ref{fig:precise_proportion_contraction} shows the comparision of the market share of Lianjia and the share of the number of stores in the market.
 [NEED TO ADD A FIGURE OR TABLE]
@@
 Furthermore, they indicate that the online consolidation effect is becoming increasingly significant relative to the offline clustering effect.
+
+% Accodring to 招股书，链家在2021的成交是cross store占比76\%
 
@@
 
+The Chinese real estate market witnessed a significnat drop at 2022 and the labor market is fierece in recently and therefore, the people are pretty hard to get on jobs.
+
 The study of Lianjia's strategic expansion into China's real estate brokerage industry, particularly through the implementation of the ACN and the proliferation of offline branches, underscores a transformative impact on market dynamics and transaction efficiency.
@@
 \section{Appendix Tables and Figures}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.7\textwidth]{../figures/distribution_of_ten_cities.pdf}
+  \caption{Distribution of Ten Cities's Brokerages Store Shares}
+  \label{fig:distribution_store_shares}
+  Note: the x-axis is city's name and the y-axis is the offline brokerage's stores share in the city. The data source is from AutoNavi Map.
+\end{figure}
+
 % \input{tab_tex/other-regressions.tex}

### 2024-06-23 plotting/plotting_distribution_of_offline_stores_in_different_cities.R

@@ -1,0 +1,135 @@
+library(ggplot2)
+library(sf)
+library(dplyr)
+library(RColorBrewer)
+library(ggthemes)
+library(scico)
+# https://bookdown.org/nicohahn/making_maps_with_r5/docs/ggplot2.html
+# https://upgo.lab.mcgill.ca/2019/12/13/making-beautiful-maps/
+
+setwd('E:/umich/RealEstateBrokerage-main/ChinaAdminDivisonSHP/3. City')
+
+base_shp <- "city.shp"
+base_map <- st_read(base_shp)
+
+names(base_map)[names(base_map) == 'ct_name'] <- 'name'
+base_map <- base_map %>%
+    mutate(name = recode(name, 
+                         "北京城区" = "北京市",
+                         "天津城区" = "天津市",
+                         "上海城区" = "上海市",
+                         "重庆城区" = "重庆市",
+                         "重庆郊县" = "重庆市")) # we do not care about whether the major cities and the other parts
+
+sansha_data <- base_map %>%
+    filter(name == "三沙市")
+base_map <- base_map %>%
+    filter(name != "三沙市")
+
+# ggplot() +
+#     geom_sf(data = base_map) +
+#     theme_minimal() +
+#     ggtitle("Base Map")
+
+# this is a sample for the data and then we will generate the rest of the data to the result
+
+file_path <- 'C:/Users/Xuyuan/Desktop/macro part/20总结_final.csv'
+data <- read.csv(file_path)
+
+# in order to better show the result, we should drop samples that have too short data
+merged_data$store_share <- merged_data$lianjia / merged_data$all
+
+selected_cities <- c("天津市", "北京市", "上海市", "南京市", "成都市", "武汉市", "杭州市", "重庆市", "广州市", "深圳市")
+english_names <- c("Tianjin", "Beijing", "Shanghai", "Nanjing", "Chengdu", "Wuhan", "Hangzhou", "Chongqing", "Guangzhou", "Shenzhen")
+
+city_mapping <- setNames(english_names, selected_cities)
+
+filtered_data <- merged_data %>%
+    filter(name %in% selected_cities) %>%
+    mutate(city = city_mapping[name]) %>% # Replace Chinese names with English names
+    arrange(desc(store_share)) %>% # Sort by store_share from high to low
+    distinct(city, .keep_all = TRUE) # Remove duplicates based on the city name
+
[…]

### 2024-06-24 manuscript/main.tex
new file:   figures/distribution_of_cities_share.pdf 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	new file:   plotting/distribution_of_ten_cities.R 	modified:   plotting/plotting_distribution_of_offline_stores_in_different_cities.R 	modified:   thinking.md

@@
 More importantly, this strategic allows Lianjia to cooperate with other previously competitors by consolidating resources.
-According to the IPO prospectus by Beke, the market share of Lianjia is around 20.8\% in year 2020 in China's second hand housing market and the number of stores share in the whole China is less than 5\% according to the AutoNavi map and moreover, in large cities like Chengdu, Beijing and Shanghai, the second hand housing share of Lianjia is even larger to
+According to Beke's IPO prospectus, Lianjia held approximately a 20.8\% market share in China's second-hand housing market in 2020.
+However, data from AutoNavi Map indicates that Lianjia's share of stores nationwide was less than 5\%.
+Notably, in major cities such as Beijing and Shanghai, Lianjia's market share exceeded 45\% and 30\%, respectively, based on data from the local Housing and Urban-Rural Development Committees.
+Despite this, Lianjia's offline store share in these cities was less than 25\% in Beijing and 10\% in Shanghai, highlighting a significant discrepancy between market presence and physical store distribution.
+This remarkable market penetration underscores the efficacy of Beke's integrated platform and ACN model in dominating the real estate brokerage landscape.
+The Figure \ref{fig:precise_proportion_contraction} illustrates the distribution of Lianjia's offline stores across China.
+The data reveals a significant concentration of these stores in first-tier cities, indicating a pronounced regional disparity.
+Lianjia's offline store presence is notably uneven, with a high density in major urban centers and sparse distribution in other regions, reflecting strategic market positioning and possibly underlying economic and demographic factors influencing store locations.
 
-This remarkable market penetration underscores the efficacy of Beke's integrated platform and ACN model in dominating the real estate brokerage landscape.
-The Figure \ref{fig:precise_proportion_contraction} shows the comparision of the market share of Lianjia and the share of the number of stores in the market.
-[NEED TO ADD A FIGURE OR TABLE]
+ % https://36kr.com/p/2450037897386121#:~:text=%E6%A0%B9%E6%8D%AE%E5%8C%97%E4%BA%AC%E4%BD%8F%E5%BB%BA%E5%A7%94%E6%95%B0%E6%8D%AE,%E6%80%BB%E7%AD%BE%E7%BA%A6%E5%A5%97%E6%95%B0%E7%9A%8439%25%E3%80%82
+
+% https://36kr.com/p/2268329112035080
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.7\textwidth]{../figures/distribution_of_cities_share.pdf}
+  \caption{Distribution of Lianjia's stores' percentage across China}
+  \label{fig:precise_proportion_contraction}
+  Note: This plot displays the percentage of Lianjia's offline stores in each city relative to the total number of brokerages in that city, based on data from AutoNavi Map.
+Gray areas indicate invalid information, while white areas denote cities without any Lianjia stores.
+Additionally, Sansha city is featured in the bottom right corner of the graph.
+\end{figure}
 

### 2024-06-24 plotting/distribution_of_ten_cities.R

@@ -1,0 +1,33 @@
+library(ggplot2)
+library(sf)
+library(dplyr)
+library(RColorBrewer)
+library(ggthemes)
+library(scico)
+
+file_path <- 'C:/Users/Xuyuan/Desktop/macro part/20总结_final.csv'
+data <- read.csv(file_path)
+
+# in order to better show the result, we should drop samples that have too short data
+data$store_share <- data$lianjia / data$all
+
+selected_cities <- c("天津市", "北京市", "上海市", "南京市", "成都市", "武汉市", "杭州市", "重庆市", "广州市", "深圳市")
+english_names <- c("Tianjin", "Beijing", "Shanghai", "Nanjing", "Chengdu", "Wuhan", "Hangzhou", "Chongqing", "Guangzhou", "Shenzhen")
+
+city_mapping <- setNames(english_names, selected_cities)
+
+filtered_data <- data %>%
+    filter(name %in% selected_cities) %>%
+    mutate(city = city_mapping[name]) %>% # Replace Chinese names with English names
+    arrange(desc(store_share)) %>% # Sort by store_share from high to low
+    distinct(city, .keep_all = TRUE) # Remove duplicates based on the city name
+
+ten_cities_distribution <- ggplot(filtered_data, aes(x = reorder(city, -store_share), y = store_share)) +
+    geom_bar(stat = "identity", fill = "skyblue", color = "black", alpha = 0.7) +
+    labs(x = "City",
+         y = "Store Share") +
+    theme_minimal() +
+    theme(plot.title = element_text(hjust = 0.5)) +
+    theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+ggsave(file = "distribution_of_ten_cities.pdf", plot = ten_cities_distribution, dpi = 300)

### 2024-06-24 plotting/plotting_distribution_of_offline_stores_in_different_cities.R

@@ -4,6 +4,10 @@ library(dplyr)
 library(RColorBrewer)
 library(ggthemes)
 library(scico)
+library(viridis)
+library(cowplot)
+library(ggspatial)
+library(grid)
 # https://bookdown.org/nicohahn/making_maps_with_r5/docs/ggplot2.html
 # https://upgo.lab.mcgill.ca/2019/12/13/making-beautiful-maps/
 
@@ -18,18 +22,12 @@ base_map <- base_map %>%
                          "北京城区" = "北京市",
                          "天津城区" = "天津市",
                          "上海城区" = "上海市",
-                         "重庆城区" = "重庆市",
-                         "重庆郊县" = "重庆市")) # we do not care about whether the major cities and the other parts
+                         "重庆城区" = "重庆市")) # we do not care about whether the major cities and the other parts
 
 sansha_data <- base_map %>%
     filter(name == "三沙市")
 base_map <- base_map %>%
     filter(name != "三沙市")
-
-# ggplot() +
-#     geom_sf(data = base_map) +
-#     theme_minimal() +
-#     ggtitle("Base Map")
 
 # this is a sample for the data and then we will generate the rest of the data to the result
 
@@ -37,50 +35,60 @@ file_path <- 'C:/Users/Xuyuan/Desktop/macro part/20总结_final.csv'
 data <- read.csv(file_path)
 
 # in order to better show the result, we should drop samples that have too short data
-merged_data$store_share <- merged_data$lianjia / merged_data$all
 
 selected_cities <- c("天津市", "北京市", "上海市", "南京市", "成都市", "武汉市", "杭州市", "重庆市", "广州市", "深圳市")
-english_names <- c("Tianjin", "Beijing", "Shanghai", "Nanjing", "Chengdu", "Wuhan", "Hangzhou", "Chongqing", "Guangzhou", "Shenzhen")
-
-city_mapping <- setNames(english_names, selected_cities)
-
-filtered_data <- merged_data %>%
-    filter(name %in% selected_cities) %>%
-    mutate(city = city_mapping[name]) %>% # Replace Chinese names with English names
-    arrange(desc(store_share)) %>% # Sort by store_share from high to low
-    distinct(city, .keep_all = TRUE) # Remove duplicates based on the city name
-
-ten_cities_distribution <- ggplot(filtered_data, aes(x = reorder(city, -store_share), y = store_share)) +
[…]

### 2024-06-24 manuscript/main.tex
update the package

@@
 
-The Chinese real estate brokerage market has long been characterized by intense competition among offline stores, with multiple brokerages establishing a presence within the same community to vie for clients.
-However, the advent of online platforms has dramatically reshaped the dynamics of real estate transactions.
+China's real estate market possesses distinct features characterized by the prominence of offline stores, setting it apart from the markets in other developed countries.
+Compared to the United States, where the Multiple Listing Service (MLS) provides comprehensive and reliable information online, facilitating transactions in a market where houses are typically situated far apart, the role of offline real estate stores is minimized.
+In contrast, China's real estate market is predominantly offline-based, with online listings serving mainly as references.
+Face-to-face interactions remain crucial for transactions.
+Additionally, the Chinese government imposes stringent restrictions on the online listing prices, leading to a reluctance among sellers to list their properties online.
+This regulatory environment allows real estate brokerages to sometimes post misleading prices to attract potential buyers, subsequently offering private information about other properties.
+In Singapore, the real estate market is heavily influenced by government-coordinated prices and evaluation companies' suggested prices.
+Conversely, in China, sellers have more freedom to set arbitrary listing prices.
+It is common practice for Chinese sellers to list their properties at higher prices, anticipating that buyers will negotiate and feel incentivized by securing a perceived better deal.
+
+Even though the Chinese real estate brokerage market has traditionally been characterized by intense competition among offline stores, the advent of online platforms has dramatically reshaped the dynamics of real estate transactions.
 Brokerage consolidation, a process where larger firms absorb smaller ones into a unified platform, is emerging as a transformative trend, redefining how properties are bought and sold across China.
@@
 
+% \subsection{Why Offline Operation is Critical In Real Estate Transaction} \label{subsec:why_offline_is_critical}
+
  % https://36kr.com/p/2450037897386121#:~:text=%E6%A0%B9%E6%8D%AE%E5%8C%97%E4%BA%AC%E4%BD%8F%E5%BB%BA%E5%A7%94%E6%95%B0%E6%8D%AE,%E6%80%BB%E7%AD%BE%E7%BA%A6%E5%A5%97%E6%95%B0%E7%9A%8439%25%E3%80%82
@@
 
-What's more, in the China's real estate market, brokerages still operate on a bilateral agency model, where sellers need to choose the agency that can help them sell their home in the fastest time and for the highest price possible for the transaction.
+Additionally, in the China's real estate market, brokerages still operate on a bilateral agency model, where sellers need to choose the agency that can help them sell their home in the fastest time and for the highest price possible for the transaction.
 However, due to the asymmetric information inherent in the real estate market, sellers face challenges in effectively informing and matching with potential buyers.
-n a perfectly competitive market, sellers would be indifferent in their choice of real estate agents.
+In a perfectly competitive market, sellers would be indifferent in their choice of real estate agents.
 Nonetheless, as the market trends toward increased monopolization, sellers confront a dichotomous decision: engage a larger brokerage firm, which, despite higher fees, offers the potential for expedited transactions, or opt for a smaller brokerage with lower fees but potentially less efficient transaction facilitation.
@@
 To assess the consolidation effect of the online platform, we treat the year Lianjia implemented the platform consolidation strategy as an exogenous shock to the market.
-The platform consolidation strategy is majorly based on the Agent Cooperation Network (ACN) framework of Lianjia, where Lianjia can divide the process of transaction to multiple agents.
+The platform consolidation strategy is majorly based on the Agent Cooperation Network (ACN) framework of Lianjia and attracting various franchise stores to join the network.
 Our findings reveal that this strategy substantially boosts revenues and alters consumer behaviors, particularly in the number of house tours facilitated by the brokerage.
+
+% WE ARE WORKING ON THIS
+
 These results underscore the necessity for a synergistic evolution of online and offline strategies in the real estate brokerage market.
-Furthermore, they indicate that the online consolidation effect is becoming increasingly significant relative to the offline clustering effect.
+Furthermore, we find that the online consolidation effect is and the effect is
+
+Lastly, the network effect has cross stores according to the IPO prospectus, in year 2021, Lianjia is expected to achive approximately 76\% of cross stores transactions.
 
@@
 
+In the China's real estate market the
+
 The Chinese real estate market witnessed a significnat drop at 2022 and the labor market is fierece in recently and therefore, the people are pretty hard to get on jobs.

### 2024-06-25 analysis/counting_number_of_stores.cpp
new file:   analysis/counting_number_of_stores.cpp 	new file:   analysis/network_estimation.ipynb

@@ -1,0 +1,60 @@
+#include <pybind11/pybind11.h>
+#include <pybind11/stl.h>
+#include <vector>
+#include <cmath>
+
+namespace py = pybind11;
+
+// this is the code to calculate the geospatial distance
+double calculate_distance(const std::vector<double> &point1, const std::vector<double> &point2) {
+    const double earth_radius_km = 6371.0;
+    const double deg_to_rad = M_PI / 180.0;
+
+    double lat1_rad = point1[1] * deg_to_rad;
+    double lon1_rad = point1[0] * deg_to_rad;
+    double lat2_rad = point2[1] * deg_to_rad;
+    double lon2_rad = point2[0] * deg_to_rad;
+
+    double dlon = lon2_rad - lon1_rad;
+    double dlat = lat2_rad - lat1_rad;
+    double a = std::sin(dlat / 2) * std::sin(dlat / 2) + std::cos(lat1_rad) * std::cos(lat2_rad) * std::sin(dlon / 2) * std::sin(dlon / 2);
+    double c = 2 * std::atan2(std::sqrt(a), std::sqrt(1 - a));
+    double distance_km = earth_radius_km * c;
+
+    return distance_km * 1000; // Convert to meters
+}
+
+std::vector<int> network_formation(const std::vector<std::vector<double>> &stores, 
+                                         const std::vector<std::vector<double>> &communities, 
+                                         const std::vector<int> &effects,
+                                         double within_distance_meters) {
+
+    // 匹配门店和社区：将每个门店与给定半径内的社区匹配。
+    // 计算边的效应值：构建门店和社区的配对，并将效应值分配给边。
+    // 连接共享社区的门店：将具有共同社区的门店连接起来，并将边的权重设为共享社区效应值的和。
+    // 折扣因子：对于共享邻居的情况，应用折扣因子，以反映共享效应的折减。
+    // 对于具有共同邻居的情况，应用折扣因子。折扣因子可以定义为共享社区效应值之和除以两个门店效应值之和的比值。
+
+    // 所以我们的store与store之间的关联会是0 < x < 1/2，所以我们可以保证A*B*C的时候这个效应会逐步降低
+
+    std::vector<int> counts(communities.size(), 0);
+    std::vector<std::vector<int>> network;
+    std::vector<std::vector<int>> effect;
+    std::vector<std::pair<int, int>> edge;
+
+    for (size_t i = 0; i < communities.size(); ++i) {
+        for (size_t j = 0; j < stores.size(); ++j) {
[…]

### 2024-06-26 manuscript/main.tex
new file:   .vscode/settings.json 	deleted:    analysis/counting_number_of_stores.cpp 	deleted:    analysis/network_estimation.ipynb 	modified:   manuscript/main.aux 	modified:   manuscript/main.blg 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	new file:   network_estimation/network_estimation.ipynb 	new file:   network_estimation/network_formulation.cpp 	new file:   network_estimation/network_fo

@@
 
+\section{Collaborative Spillover Effect} \label{sec:network_effect}
+
+The last section is to estimate the Lianjia's collaborative spillover effect.
+Lianjia decided to change from brokerage's direction operation to a combination of platform.
+By attracting other brokerage's into the network will initially make the brokreage's profit down because attracting other people in the platform meaning the market share would be decreased due to the intense competition.
+However, after the setup of the platform, the market will be more productive and more competitive to occupying a larger share of the whole network.
+This mechanism is more likely to get better control over the listing and people are more willing to list their house on this platform.
+Then accordin to the this would be resulted in a winners-take-all market.
+
+In this case, we need to empirically estimate the spillover effect, and if this spillover effect is significant in this setting then people's reaction
+
+To set up, we first match the brokerages' with the
+
 \section{Conclusion and Discussion} \label{sec:conclusion}

### 2024-06-26 analysis/counting_number_of_stores.cpp

@@ -1,60 +1,0 @@
-#include <pybind11/pybind11.h>
-#include <pybind11/stl.h>
-#include <vector>
-#include <cmath>
-
-namespace py = pybind11;
-
-// this is the code to calculate the geospatial distance
-double calculate_distance(const std::vector<double> &point1, const std::vector<double> &point2) {
-    const double earth_radius_km = 6371.0;
-    const double deg_to_rad = M_PI / 180.0;
-
-    double lat1_rad = point1[1] * deg_to_rad;
-    double lon1_rad = point1[0] * deg_to_rad;
-    double lat2_rad = point2[1] * deg_to_rad;
-    double lon2_rad = point2[0] * deg_to_rad;
-
-    double dlon = lon2_rad - lon1_rad;
-    double dlat = lat2_rad - lat1_rad;
-    double a = std::sin(dlat / 2) * std::sin(dlat / 2) + std::cos(lat1_rad) * std::cos(lat2_rad) * std::sin(dlon / 2) * std::sin(dlon / 2);
-    double c = 2 * std::atan2(std::sqrt(a), std::sqrt(1 - a));
-    double distance_km = earth_radius_km * c;
-
-    return distance_km * 1000; // Convert to meters
-}
-
-std::vector<int> network_formation(const std::vector<std::vector<double>> &stores, 
-                                         const std::vector<std::vector<double>> &communities, 
-                                         const std::vector<int> &effects,
-                                         double within_distance_meters) {
-
-    // 匹配门店和社区：将每个门店与给定半径内的社区匹配。
-    // 计算边的效应值：构建门店和社区的配对，并将效应值分配给边。
-    // 连接共享社区的门店：将具有共同社区的门店连接起来，并将边的权重设为共享社区效应值的和。
-    // 折扣因子：对于共享邻居的情况，应用折扣因子，以反映共享效应的折减。
-    // 对于具有共同邻居的情况，应用折扣因子。折扣因子可以定义为共享社区效应值之和除以两个门店效应值之和的比值。
-
-    // 所以我们的store与store之间的关联会是0 < x < 1/2，所以我们可以保证A*B*C的时候这个效应会逐步降低
-
-    std::vector<int> counts(communities.size(), 0);
-    std::vector<std::vector<int>> network;
-    std::vector<std::vector<int>> effect;
-    std::vector<std::pair<int, int>> edge;
-
-    for (size_t i = 0; i < communities.size(); ++i) {
-        for (size_t j = 0; j < stores.size(); ++j) {
[…]

### 2024-06-26 network_estimation/network_formulation.cpp

@@ -1,0 +1,88 @@
+#include <pybind11/pybind11.h>
+#include <pybind11/stl.h>
+#include <vector>
+#include <cmath>
+
+namespace py = pybind11;
+
+// this is the code to calculate the geospatial distance
+double calculate_distance(const std::vector<double> &point1, const std::vector<double> &point2) {
+    const double earth_radius_km = 6371.0;
+    const double deg_to_rad = M_PI / 180.0;
+
+    double lat1_rad = point1[1] * deg_to_rad;
+    double lon1_rad = point1[0] * deg_to_rad;
+    double lat2_rad = point2[1] * deg_to_rad;
+    double lon2_rad = point2[0] * deg_to_rad;
+
+    double dlon = lon2_rad - lon1_rad;
+    double dlat = lat2_rad - lat1_rad;
+    double a = std::sin(dlat / 2) * std::sin(dlat / 2) + std::cos(lat1_rad) * std::cos(lat2_rad) * std::sin(dlon / 2) * std::sin(dlon / 2);
+    double c = 2 * std::atan2(std::sqrt(a), std::sqrt(1 - a));
+    double distance_km = earth_radius_km * c;
+
+    return distance_km * 1000; // Convert to meters
+}
+
+
+std::pair<std::vector<std::vector<int>>, std::vector<std::tuple<int, int, double>>> network_formation(
+    // 匹配门店和社区：将每个门店与给定半径内的社区匹配。
+    // 计算边的效应值：构建门店和社区的配对，并将效应值分配给边。
+    // 连接共享社区的门店：将具有共同社区的门店连接起来，并将边的权重设为共享社区效应值的和。
+    // 折扣因子：对于共享邻居的情况，应用折扣因子，以反映共享效应的折减。
+    // 对于具有共同邻居的情况，应用折扣因子。折扣因子可以定义为共享社区效应值之和除以两个门店效应值之和的比值。
+
+    // 所以我们的store与store之间的关联会是0 < x < 1/2，所以我们可以保证A*B*C的时候这个效应会逐步降低
+    const std::vector<std::vector<double>> &stores, 
+    const std::vector<std::vector<double>> &communities, 
+    const std::vector<int> &effects,
+    double within_distance_meters) {
+
+    std::vector<std::vector<int>> network(stores.size());
+    std::vector<std::tuple<int, int, double>> edges;
+
+    // Match stores with communities within the given radius
+    for (size_t i = 0; i < communities.size(); ++i) {
+        for (size_t j = 0; j < stores.size(); ++j) {
[…]

### 2024-06-26 network_estimation/network_formulation.cpp
modified:   manuscript/main.aux 	modified:   manuscript/main.bbl 	modified:   manuscript/main.blg 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	modified:   manuscript/our-cites.bib 	modified:   network_estimation/network_estimation.ipynb 	modified:   network_estimation/network_formulation.cpp 	modified:   network_estimation/network_formulation.so

@@ -25,7 +25,7 @@ double calculate_distance(const std::vector<double> &point1, const std::vector<d
 }
 
 
-std::pair<std::vector<std::vector<int>>, std::vector<std::tuple<int, int, double>>> network_formation(
+std::pair<std::vector<std::vector<std::pair<int, double>>>, std::vector<std::tuple<int, int, double>>> network_formation(
     // 匹配门店和社区：将每个门店与给定半径内的社区匹配。
     // 计算边的效应值：构建门店和社区的配对，并将效应值分配给边。
     // 连接共享社区的门店：将具有共同社区的门店连接起来，并将边的权重设为共享社区效应值的和。
@@ -38,14 +38,14 @@ std::pair<std::vector<std::vector<int>>, std::vector<std::tuple<int, int, double
     const std::vector<int> &effects,
     double within_distance_meters) {
 
-    std::vector<std::vector<int>> network(stores.size());
+    std::vector<std::vector<std::pair<int, double>>> network(stores.size());
     std::vector<std::tuple<int, int, double>> edges;
 
     // Match stores with communities within the given radius
     for (size_t i = 0; i < communities.size(); ++i) {
         for (size_t j = 0; j < stores.size(); ++j) {
             if (calculate_distance(communities[i], stores[j]) <= within_distance_meters) {
-                network[j].push_back(i);
+                network[j].emplace_back(i, effects[i]);
             }
         }
     }
@@ -56,20 +56,19 @@ std::pair<std::vector<std::vector<int>>, std::vector<std::tuple<int, int, double
         for (size_t j = i + 1; j < stores.size(); ++j) {
             // iterate over all adjacent stores and find the shared communities
             double shared_effect = 0;
-            for (int community : network[i]) {
-                if (std::find(network[j].begin(), network[j].end(), community) != network[j].end()) {
-                    // if the community is shared between the two stores
-                    shared_effect += effects[community];
+            for (const auto &community : network[i]) {
+                if (std::find_if(network[j].begin(), network[j].end(), [&](const std::pair<int, double> &c) { return c.first == community.first; }) != network[j].end()) {
+                    shared_effect += community.second;
                 }
             }
             if (shared_effect > 0) {
                 double total_effect_i = 0;
-                for (int community : network[i]) {
-                    total_effect_i += effects[community];
+                for (const auto &community : network[i]) {
+                    total_effect_i += community.second;
                 }
                 double total_effect_j = 0;
-                for (int community : network[j]) {
-                    total_effect_j += effects[community];
[…]

### 2024-06-26 archive/some archived words.tex
update the bibtex

--- 2024-06-24 manuscript/main.tex
@@
-\documentclass[12pt]{article}
-\usepackage[right=0.7in,left=0.7in,top=1in,bottom=1in]{geometry}
-\usepackage{hyperref}
-\hypersetup{colorlinks, citecolor=blue, filecolor=blue, linkcolor=blue, urlcolor=blue}
-\usepackage{graphicx}
-\usepackage{url}
-\usepackage{adjustbox}
-\usepackage[round]{natbib}
-\usepackage{amsmath,amsthm}
-\usepackage{engord}
-\usepackage{float}
-\usepackage{subfig}
-\usepackage{pdflscape}
-\usepackage{booktabs}
-\usepackage{pgfplots}
-\usepackage{subfig}
-\pgfplotsset{compat=1.14}
-\usepackage{longtable}
-\pgfplotsset{every axis label/.append style={font=\tiny}}
-\usepackage[labelsep=period]{caption} %% This switches "Table 1: Title" to "Table 1. Title"
-\usepackage{authblk}
-\usepackage{amssymb} %% Necessary, just for the \checkmark command  in tables.
-\usepackage{multirow} %% Necessary if we are doing tables in LaTeX
-
-\usepackage{xr}
-
-\newtheorem{assumption}{Assumption}
-\newtheorem{definition}{Definition}
-\newtheorem{proposition}{Proposition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{lemma}{Lemma}
-\newtheorem{remark}{Remark}
-\newtheorem{example}{Example}
-\newtheorem{theorem}{Theorem}
-
-\usepackage{setspace}
-\doublespacing
-
-\usepackage{sectsty}
-\sectionfont{\large}
-\subsectionfont{\normalsize}
-\subsubsectionfont{\normalsize}
-
-\newcommand{\specialcell}[2][c]{\begin{tabular}[#1]{@{}l@{}}#2\end{tabular}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\title{ \vspace*{-2.5cm} \hspace*{-0.5cm}Offline Store Expansion and Platform Consolidation: Evidence from major cities in China \footnote{
-The preliminary version was entitled "Property brokerage, Partial monopoly and Housing market" and was presented at The 1st Summer Meeting in Urban Economics, China.
-We are grateful for the comments and suggestions made at the meeting.
-The code to replicate the paper can be accessed at \href{https://github.com/sergiozxy/RealEstateBrokerage}{https://github.com/sergiozxy/RealEstateBrokerage} The authors gratefully acknowledge financial support from the Fundamental Research Funds for the Central Universities of Sichuan University (2019hhf-08; SKSYL201812; 2018jj-01) and National Natural Science Foundation of China (71773081).
-% We gratefully thank for Hanying Liu from Sichuan University and Chongyu Wang from Florida State University for insightful feedback.
-}}
-
-\date{ \vspace*{0.5cm} \today}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{document}
-
-\author[1]{Guoying Deng}
-\author[2]{Xuyuan Zhang \thanks{Email Address: \href{mailto:zxuyuan@umich.edu}{zxuyuan@umich.edu}}}
-\affil[1]{School of Economics, Sichuan University, China}
-\affil[2]{Department of Economics, University of Michigan, United States}
-
-\bgroup
-\let\footnoterule\relax
-
-\begin{singlespace}
-\maketitle
-
-% Police brutality, law enforcement, and crime: Evidence from Chicago
-\begin{abstract}
-    \noindent This study examines the impact of offline store expansion by Lianjia, China's leading real estate brokerage, within the framework of platform consolidation.
-By analyzing micro-level transactions of second-hand houses in ten major Chinese cities from 2016 to 2022, the research investigates how the transaction patterns of traditional brokerages, characterized by the strategic clustering of offline stores, transition towards online consolidation, thereby facilitating the development of an extensive franchise network.
-Utilizing a regression discontinuity (RD) design, the study quantifies the optimal influence radius of offline stores on housing transactions.
-Incorporating this optimal influence radius, the study further empirically estimates the effects of real estate brokerage's offline store expansion and online platform consolidation on transaction properties.
-This analysis leverages the exogenous shock of Lianjia's market entry, identifying a significant increase in transaction revenues before the COVID-19 pandemic.
-However, this effect diminishes during the pandemic due to remote work and restrictive policies implemented by the Chinese government.
-The study also examines the online platform consolidation effect by analyzing the period in 2018 when Lianjia revised and improved its Agent Cooperation Network (ACN).
-
-    \textbf{The results indicate that this strategy significantly boosts revenues and also suggest that the offline store's effect is majorly focused on people's transaction behaviors but the online platform's effect can be more insightful to provide a more efficient transaction process.
-} % this need to be revised.
-
-    This study provides valuable insights into the synergy between offline store expansion and online platform development, elucidating future trajectories in the evolving real estate brokerage market and analogous sectors.
-  \end{abstract}
-
-  \textbf{Keyword}: Marketing Strategy, Digital Platforms, Platform Consolidation, Real Estate Brokerage
-
-  \textbf{JEL} Classification Codes: D4, L1, L8, R3
-\end{singlespace}
-\thispagestyle{empty}
-
-\clearpage
-\egroup
-\setcounter{page}{1}
-
-%% Temporary tool to track how this paper is structured. Feel free to comment in or out. 
-% \tableofcontents
-% \bigskip
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%\section{Introduction\label{sec:introduction}}
-
-\section{Introduction \label{sec:introduction}}
-
-\noindent
-
-Understanding housing markets is crucial due to their significant impact on household finance, as housing is typically the largest component of a household's portfolio.
-The illiquidity of housing creates a strong link between housing and labor markets, and transaction costs are critical for buyers and sellers in the real estate market.
-Real estate brokers play a vital role in reducing these costs, providing essential market information, negotiation support, and legal assistance to ensure smoother and more efficient transactions.
-With the improvement of China's legal system in the real estate market, the brokerage market is expanding and becoming more prosperous.
-Especially in the context of China's burgeoning real estate market, brokerage firms are assuming an increasingly important role in facilitating the communications between buyers and sellers \citep{glaeser_real_2017}.
-Given the heterogeneous and "thin" nature of real estate goods \citep{HAN2015813}, the expertise and local market knowledge of real estate brokers have become indispensable in navigating the complex real estate landscape.
-
-The Chinese real estate brokerage market has long been characterized by intense competition among offline stores, with multiple brokerages establishing a presence within the same community to vie for clients.
-However, the advent of online platforms has dramatically reshaped the dynamics of real estate transactions.
-Brokerage consolidation, a process where larger firms absorb smaller ones into a unified platform, is emerging as a transformative trend, redefining how properties are bought and sold across China.
-Lianjia, the largest real estate brokerage in China, has revolutionized real estate transactions through the establishment of the Beke platform.
-This platform enables rapid expansion by integrating offline stores on a large scale while leveraging the advantages of resource sharing.
-However, prior to 2018, the platform Beke primarily focused on facilitating listings from Lianjia's offline stores and aimed to attract buyers from the market.
-However, in 2014, Beke established a new strategy named Agent Cooperate Network (ACN), which integrates and shares the content across its multiple subsidiaries to realize multiple revenue models simultaneously.\footnote{The ACN model disaggregates the transaction process into specialized tasks handled by individual agents or stores.
-These tasks include seller-side activities such as sourcing sellers, maintaining property listings, commission negotiations, and buyer-side activities like client acquisition, property-client matching, transaction facilitation, and financial services assistance.} Moreover, in 2018, Lianjia decided to enhance its Agent Cooperation Network (ACN) strategy by incorporating smaller brokerages into its network and launching franchise stores under the brand name Deyou, along with other smaller formats.
-This strategic move aimed to increase network effects and further consolidate the platform, thereby enhancing market power and operational efficiency.
-
-Through the success of the platform consolidation, Lianjia transforms internal competition within the system into overall system competitiveness, thereby enhancing the brand's reputation and market influence.
-More importantly, this strategic allows Lianjia to cooperate with other previously competitors by consolidating resources.
-According to Beke's IPO prospectus, Lianjia held approximately a 20.8\% market share in China's second-hand housing market in 2020.
-However, data from AutoNavi Map indicates that Lianjia's share of stores nationwide was less than 5\%.
-Notably, in major cities such as Beijing and Shanghai, Lianjia's market share exceeded 45\% and 30\%, respectively, based on data from the local Housing and Urban-Rural Development Committees.
-Despite this, Lianjia's offline store share in these cities was less than 25\% in Beijing and 10\% in Shanghai, highlighting a significant discrepancy between market presence and physical store distribution.
-This remarkable market penetration underscores the efficacy of Beke's integrated platform and ACN model in dominating the real estate brokerage landscape.
-The Figure \ref{fig:precise_proportion_contraction} illustrates the distribution of Lianjia's offline stores across China.
-The data reveals a significant concentration of these stores in first-tier cities, indicating a pronounced regional disparity.
-Lianjia's offline store presence is notably uneven, with a high density in major urban centers and sparse distribution in other regions, reflecting strategic market positioning and possibly underlying economic and demographic factors influencing store locations.
-
- % https://36kr.com/p/2450037897386121#:~:text=%E6%A0%B9%E6%8D%AE%E5%8C%97%E4%BA%AC%E4%BD%8F%E5%BB%BA%E5%A7%94%E6%95%B0%E6%8D%AE,%E6%80%BB%E7%AD%BE%E7%BA%A6%E5%A5%97%E6%95%B0%E7%9A%8439%25%E3%80%82
-
-% https://36kr.com/p/2268329112035080
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.7\textwidth]{../figures/distribution_of_cities_share.pdf}
-  \caption{Distribution of Lianjia's stores' percentage across China}
-  \label{fig:precise_proportion_contraction}
-  Note: This plot displays the percentage of Lianjia's offline stores in each city relative to the total number of brokerages in that city, based on data from AutoNavi Map.
-Gray areas indicate invalid information, while white areas denote cities without any Lianjia stores.
-Additionally, Sansha city is featured in the bottom right corner of the graph.
-\end{figure}
-
-What's more, in the China's real estate market, brokerages still operate on a bilateral agency model, where sellers need to choose the agency that can help them sell their home in the fastest time and for the highest price possible for the transaction.
-However, due to the asymmetric information inherent in the real estate market, sellers face challenges in effectively informing and matching with potential buyers.
-n a perfectly competitive market, sellers would be indifferent in their choice of real estate agents.
-Nonetheless, as the market trends toward increased monopolization, sellers confront a dichotomous decision: engage a larger brokerage firm, which, despite higher fees, offers the potential for expedited transactions, or opt for a smaller brokerage with lower fees but potentially less efficient transaction facilitation.
-
-While sellers might consider a co-listing strategy—listing their property with multiple brokerages—this approach is suboptimal for several reasons within China's real estate market.
-Despite previous literature, such as \citep{RePEc:kap:jrefec:v:67:y:2023:i:3:d:10.1007_s11146-021-09858-w}, indicating that the co-listing can be beneficial for clients under multiple-listing service.
-Specifically in China's real estate market, firstly, the exclusivity of contracts between sellers and agents often precludes the adoption of a co-listing strategy.
-Secondly, although sellers can list their properties with multiple brokerages, smaller agencies frequently lack a sufficiently broad client base, limiting their effectiveness in selling homes.
-Thirdly, engaging multiple brokers simultaneously can lead to reduced incentives among agents, as they perceive competition for the same property, diminishing their proactive efforts.
-Finally, while service cost variations between agencies are acknowledged, these costs are minor compared to the property's value and are more closely related to the risks associated with holding a financial asset.
-Consequently, risk-averse sellers are inclined to choose an agency that provides a guaranteed level of service.
-
-Given the dual nature of online promotion and offline transactions in the real estate brokerage industry, the quality of offline services is crucial for influencing client decisions.
-This principle underpins Lianjia's strategy of establishing numerous stores within targeted communities.
-By opening a wide range of stores in various neighborhoods and adopting a downstream consolidation model through platform design, the brokerage effectively attracts sellers to list their properties and buyers through its extensive platform resources.
-This strategy not only enhances transaction volume but also increases income derived from these transactions.
-
-In this paper, we empirically estimate the effects of offline store clustering and online platform consolidation in China's second-hand real estate market.
-Utilizing micro-level transaction data, we construct our research sample by aggregating information at the neighborhood level.
-We employ a regression discontinuity (RD) design to identify the optimal influential radius of offline stores on neighborhood transactions, finding that this radius corresponds to a brokerage's five-minute walk service distance.
-Subsequently, we apply a difference-in-difference (DID) estimation method to evaluate the exogenous impact of Lianjia's market entry on local segments.
-This exogenous effect captures the clustering impact of offline real estate brokerage stores.
-Our results indicate that Lianjia's offline stores significantly enhance transaction revenues, although this effect diminishes during and after the COVID-19 period.
-
-To assess the consolidation effect of the online platform, we treat the year Lianjia implemented the platform consolidation strategy as an exogenous shock to the market.
-The platform consolidation strategy is majorly based on the Agent Cooperation Network (ACN) framework of Lianjia, where Lianjia can divide the process of transaction to multiple agents.
-Our findings reveal that this strategy substantially boosts revenues and alters consumer behaviors, particularly in the number of house tours facilitated by the brokerage.
-These results underscore the necessity for a synergistic evolution of online and offline strategies in the real estate brokerage market.
-Furthermore, they indicate that the online consolidation effect is becoming increasingly significant relative to the offline clustering effect.
-
-% Accodring to 招股书，链家在2021的成交是cross store占比76\%
-
-Our research has several implications.
-Firstly, it indicates that with the advent of new technologies, the online consolidation effect is becoming increasingly important for real estate companies.
-This shift underscores the need for firms to enhance their digital strategies to remain competitive.
-Secondly, our findings have broader significance for other industries where online consolidation can potentially replace traditional offline clustering.
-For example, in the retail sector, online marketplaces such as Alibaba in China have significantly outpaced physical stores by consolidating various vendors into a single, accessible platform.
-
-By examining these dynamics, our research contributes to a deeper understanding of the evolving landscape of real estate brokerage in China.
-It provides valuable insights for policymakers and industry stakeholders aiming to enhance market efficiency and competitiveness.
-As the online consolidation effect continues to grow, our findings highlight the importance of adapting to this trend and evolving strategies accordingly.
-Specifically, transitioning from a bilateral brokerage model to a model where buyer and seller agencies are separated could be crucial for sustaining a competitive advantage in the real estate brokerage market.
-This strategic shift entails leveraging online platforms to integrate services and enhance transaction efficiency, thereby benefiting both consumers and firms.
-By disentangling the roles of buyer and seller agents, the market can reduce conflicts of interest, increase transparency, and improve overall market efficiency.
-This alignment with economic principles of specialization and efficiency further underscores the potential for significant gains in consumer welfare and firm profitability.
-
-The remainder of the paper proceeds as follows.
-Section \ref{sec:literature_review} reviews the literature that is related to our research.
-Section \ref{sec:data} describes the study background and statistical summary.
-Section \ref{sec:mechanism_design} presents the main result of our finding.
-Finally, Section \ref{sec:conclusion} contains the discussion and concludes.
-
-\section{Literature Review} \label{sec:literature_review}
-
-The literature on the real estate market, particularly the role of real estate brokerages, is extensive and informative, starting with the foundational work of \citet{Rosen_hedonic} who introduced the hedonic pricing model.
-This model breaks down property prices by analyzing internal and external factors.
-However, it's worth noting that this model does not adequately account for market asymmetries and information disparities, leading to potential inaccuracies in pricing.
-A fundamental study by \citep{Akerlof_1970} highlights the significant impact of asymmetric information on market dynamics, using the market for used cars as an example.
-Here, the prevalence of low-quality goods, known as 'lemons', often leads to market inefficiencies, a problem that is mirrored in the real estate sector.
-The challenge of asymmetric information in real markets was further emphasized by \citet{grossman_impossibility_1980}, who questioned the feasibility of the effective market assumption, particularly under conditions of information disparity.
-
-Subsequent studies have expanded on these foundational theories, exploring dynamics specific to real estate pricing and strategic behavior.
-\citet{550a6ccf-cde2-3dd1-979f-1a8db2b8ceb9} documents that apart from price competition in the market, there is a lot of market inefficiency that stems from non-price competition, which suggests that as the degree of competition in the market increases, the market becomes progressively less efficient, indicating that the entry dividend begins to fall and aggregate social welfare begins to decline.
-Moreover, \citet{hendel_relative_2009} analyzes two types of listings in the second-hand housing market and finds that For-Sale-By-Owner type of platforms are less effective in terms of time and probability of sale while operating better compared to listing homes for sale as a broker.
-In addition, \citet{bailey_economic_2018} uses data from the social media site Facebook to show that social interactions can influence people's economic decisions.
-Their results show that people who have friends who are geographically distant in real life and who have a hunch that house prices are about to rise are more likely to buy a house than rent one.
-Other relevant areas of research include \citep{SIRMANS1991207, NIEUWERBURGH_information, salz_intermediation_2022}.
-
-The strategic behavior of real estate brokerages has been documented to leverage informational advantages.
-\citet{AGARWAL2019715} confirms that brokerages, as market intermediaries, possess nuanced knowledge of market conditions, enabling them to negotiate discounts effectively.
-Furthermore, \citet{HAN2015813} discusses the varying bargaining power of brokerages across unidirectional and bidirectional markets, influencing their operational strategies.
-This is corroborated by evidence suggesting that properties listed with lower commission rates not only sell less frequently but also take longer to sell \citep{10.1257/app.20160214}.
-The advent of online platforms has significantly altered the landscape of real estate transactions.
-\citet{ZUMPANO2003134} notes that while the duration of property searches has not changed markedly, the scope of searches has broadened to encompass more online listings.
-Moreover, \citet{ZHANG2021101104} associates the rise of online platforms with a reduction in existing home prices and an increase in sales volumes, a dynamic influenced by factors such as new home prices and household demographics.
-However, a detailed analysis of the impact of the presence of these platforms on market performance of offline stores remains scant.
-
-Moreover, the overall market influence of real estate intermediaries is multifaceted.
-Utilizing a model predicated on perfect competition, \citet{williams_agency_1998} illustrates that excessive entry of brokers into the market can surpass the optimal allocation, thereby reducing social welfare.
-This is corroborated by studies indicating that an increase in the number of brokers can depress house prices and shorten transaction cycles \citep{https://doi.org/10.1002/jae.2891}.
-Additionally, \citet{qu_identifying_2021-1} highlights the moderating role of broker commissions in disseminating information during transactions, facilitating more efficient home sales.
-Other related literature includes \citep{doi:10.1080/10527001.2021.2016340, doi:10.1080/10835547.1996.12090852}.
-
-Finally, the concept of the platform as a "two-sided market" or kind of intermediates that connects the buyer side and seller side digitally, \citep{10.1162/154247603322493212, Langley_Leyshon_2017}.
-Despite the significant attention given to online platforms, there is a lack of systematic analysis on the impact of offline stores of online platforms on market performance or on real estate brokerage.
-Therefore, this paper aims to fill this gap by examining the influence of offline stores associated with online platforms on the real estate market.
-
-% With respect to the behavior of real estate brokerages, the research conducted by \citep{AGARWAL2019715} substantiates that these entities, acting as intermediaries in market transactions, possess superior knowledge of market dynamics.
-This informational superiority enables the intermediaries to use their bargaining power to secure discounts in the market.
-Similarly, \citet{HAN2015813} articulates that brokerages operating in unidirectional and bidirectional markets exhibit different levels of bargaining leverage, leading to different motivational drivers.
-This mechanism is in line with other research, which shows that properties with lower commission rates have a 5\% less likelihood of being sold and takes 12\% longer to sell \citep{10.1257/app.20160214}.
-
-% Regarding the impact of online platforms on the real estate sector, research by \citep{ZUMPANO2003134} suggests that while the length of time buyers spend searching for properties remains unchanged, the scope of their search expands to include a greater number of online listings.
-\citet{ZHANG2021101104} show that the introduction of online platforms is associated with reductions in existing home prices and increased sales volumes, effects that are influenced by new home prices and household size.
-However, a comprehensive analysis of the influence of the physical stores of online platforms on the real estate market is still lacking in the literature.
-
-% Finally, the impact of real estate intermediaries on the market can be decomposed into several aspects.
-Using a model based on the assumption of a perfectly competitive market in which an influx of brokers competitively enters the market, \citet{williams_agency_1998} shows that the presence of brokers in the market equilibrium exceeds the optimal number of allocations, thereby causing a reduction in social welfare.
-Moreover, the results show that neither brokers nor sellers are motivated to deviate from the equilibrium price structure, which coincides with the reservation price set by sellers.
-Complementary research in another study shows that a significant influx of brokers into the market is correlated with a decrease, rather than an increase, in house prices, along with a gradual decrease in transaction cycles within the market \citep{https://doi.org/10.1002/jae.2891}.
-Furthermore, the work of \citep{qu_identifying_2021-1} highlights the moderating role of broker commissions on the dissemination of market information during transactions.
-Their findings suggest that the use of a broker can significantly mitigate the concessions that sellers are forced to make in the transaction process, thereby enhancing their ability to complete a home sale more efficiently.
-
-% Many literature has been conducted to study the real estate market, and the impact of real estate brokerages on the market, beginning with \citet{Rosen_hedonic}, which proposed a hedonic pricing model and decomposed the price by internal and external factors affecting it.
-However, the hedonic pricing model suffers from market asymmetry and information inequality.
-The seminal work on the impact of asymmetric information in markets is \citep{Akerlof_1970}, which demonstrated that markets for used cars tend to be dominated by low-quality goods, or 'lemons', leading to market inefficiencies.
-Furthermore, \citet{grossman_impossibility_1980} further argued that information effective market assumption is hard to hold in reality.
-Therefore, the real estate market, which is characterized by information asymmetry, is particularly vulnerable to the adverse selection problem.
-In this context, the role of real estate brokerages is crucial, as they act as intermediaries between buyers and sellers, providing valuable information and facilitating transactions.
-
-% 由于房地产中介行业线上推广线下成交的机制，中介机构在线下门店中的服务性质对于其在客源方的影响具有很高的价值。链家通常选择在每个目标小区的周边开店便是该原理。链家通过在小区周边大范围开店，从而吸引卖方选择该机构进行挂牌，而又通过其广泛的平台客源来吸引市场中的买方从而获得更多的成交数量与成交收入。由于房地产中介行业线上推广线下成交的机制，中介机构在线下门店中的服务性质对于其在客源方的影响具有很高的价值。链家通常选择在每个目标小区的周边开店便是该原理。链家通过在小区周边大范围开店，从而吸引卖方选择该机构进行挂牌，而又通过其广泛的平台客源来吸引市场中的买方从而获得更多的成交数量与成交收入。
-
-\section{Data and Descriptive Evidence \label{sec:data}}
-
-\subsection{Data Collection and Processing} \label{subsec:data_collection}
-
-This study focuses on the housing markets in ten major cities in China, namely Beijing, Shanghai, Chongqing, Tianjin, Shenzhen, Guangzhou, Chengdu, Hangzhou, Wuhan and Nanjing.
-These cities are not only central to China's economic development, but also reflect the broader trends and characteristics of the country's real estate dynamics.
-Spanning from 2016 to 2022, the research period encapsulates a pivotal era in China's real estate sector.
-During the first phase of the study, from 2016 to 2019, the housing markets in these cities experienced a remarkable boom.
-This period was characterized by significant growth in property prices, supported by robust economic expansion and increased demand in these urban centers.
-However, the final phase of our study, from 2020 to 2022, paints a contrasting picture.
-During this period, China's overall economic growth rate has been slower significantly, which has also reflected in a slowdown in the real estate markets of these major cities.
-In addition, the Chinese government has implemented strict rules in Covid-19 protection, so the real estate agents in these major cities are significantly affected.
-
-The second hand housing transaction data was collected form \href{https://www.ke.com/city/}{beke.com} for ten cities ranging from 2016 to 2022.
-Initially, we filtered out transaction records exhibiting unusually high prices, identifying them as outliers that could skew the analysis.
-We then removed records with missing values to maintain the integrity of our dataset.
-We also removed any records that were listed duplicated.
-We finally have a data with length 1,778,647 second-hand houses.\footnote{Due to government restrictions, four of these cities did not list the transaction price for each transaction during the study period.} After cleaning the data, we constructed two research samples: one at the individual transaction level and the other at the neighborhood level.
-The individual transaction sample contains detailed information on each transaction, including the transaction price, transaction date, price concessions, and the number of house tours.
-The neighborhood-level sample aggregates transaction data at the community level, encompassing variables such as the average transaction price and the average number of house tours.
-Additionally, we calculated the annual number of house transactions to capture Lianjia's transaction activity within each neighborhood.
-This data structure enables a comprehensive analysis of the impact of offline stores on housing transactions across both individual and neighborhood dimensions.
-
-To gather additional characteristic information, Point of Interest (POI) data was extracted from the AutoNavi map using a web-scraping Python program.\footnote{AutoNavi, a leading mapping application in China with a user base exceeding 700 million, is renowned for its detailed and accurate POI data as well as precise public transportation information.
-These features underscore AutoNavi's leadership in the digital mapping sector, highlighting its ability to provide unparalleled navigation accuracy and comprehensive urban mobility solutions.
-Our extracted AutoNavi dataset includes over one million POIs per city annually.} The extracted POIs were then classified into various categories, as detailed in Table \ref{tab:statistical_district} and Table \ref{tab:statistical_individual} and it primarily represents living facilities, entertainment venues, restaurants, hospitals, and other public amenities.
-This classification is crucial for understanding the urban infrastructure and amenities available in the vicinity of the analyzed properties.
-
-Each type of POI was matched to our data within a 500-meter radius, a distance typically covered by walking and consistent with urban planning standards for accessible urban design.
-This radius reflects the immediate urban environment influencing residential desirability and property values, as most of these POIs provide recreational services.
-Additionally, geo-informational data, including annual GDP data from \citet{zhao_forecasting_2017}, nighttime lights data from \citet{elvidge_annual_2021}, and air pollution data from \citet{doi:10.1021/acs.est.1c05309}, was integrated into our research.
-The centroid of the neighborhood-level data's polygon was generated, and values from the geo-informational data were extracted.
-By merging these data sources with our research panel, a comprehensive research sample was constructed.
-
-\subsection{Influential Radius} \label{subsec:Influential_Radius}
-
-The effectiveness of an offline intermediary's influence on its immediate communities is inherently constrained by geographic limitations, with its influence decreasing in proportion to the increase in spatial distance.
-Moreover, since the offline stores of Lianjia are directly operated by the company, strategic considerations regarding the optimal distance between stores are an integral part of their location planning to mitigate the risks associated with over-concentration of stores that could lead to competitive overlap and service homogenization.
-Consequently, it is imperative to determine an optimal radius threshold and subsequently assess the diversity of agencies operating within this demarcated zone.
-
-To determine the optimal radius of influence, this research employs a regression discontinuity design (RDD) method on the neighborhood level transaction data to examine the influential radius of offline real estate brokerages.
-The dependent variable in this analysis is the transaction revenue generated by Lianjia within a given community, while the independent variable is the community's proximity to the nearest Lianjia store.
-Given that stores are predominantly located within commercial districts, which typically encompass several streets no more than two kilometers in diameter, it is assumed that a requisite number of stores within each district is essential to sustain revenue generation in that community.
-In addition, Lianjia adopts a 5-minute walking distance (approximately 400 meters) radius policy, which means that no matter how far away customers live, they should be accessible within a 5-minute walk to the nearest Lianjia store.
-Building on this premise, the study further investigates the existence of an optimal influence radius within shopping districts, defined as the distance radius within which the presence of a Lianjia optimally increases transaction revenues.
-At the same time, the study also examines the hypothesis that beyond this optimal radius, the impact on transaction revenues diminishes as a result of the strategic store layout decisions implemented by Lianjia.
-
-\begin{figure}[ht]
-    \centering
-    \subfloat[RD plot with first order polynomial]{\includegraphics[width=0.5\textwidth]{../figures/RD_Plot_1st_Order.pdf}\label{fig:RD_Plot_1st_Order}}
-    \hfill % Adds horizontal space between figures
-    \subfloat[RD plot with second order polynomial]{\includegraphics[width=0.5\textwidth]{../figures/RD_Plot_2nd_Order.pdf}\label{fig:RD_Plot_2nd_Order}}
-    \hfill % Adds horizontal space between figures
-    \subfloat[RD plot with third order polynomial]{\includegraphics[width=0.5\textwidth]{../figures/RD_Plot_3rd_Order.pdf}\label{fig:RD_Plot_3rd_Order}}
-    \caption{RD design}
-    \label{fig:RD_design}
-\end{figure}
-
-\input{../result_tables/rdd_result_summary.tex}
-
-From Figure \ref{fig:RD_design} we can see that there is indeed discontinuity in 410 meters of communities to the nearest Lianjia's store, which is pretty close to the lianjia's 5-minute walk distance policy.
-The observed decline in the Lianjia's influence is marked and suggests a pronounced reduction in its impact on the system overall within our study sample.
-This phenomenon can be attributed to the implementation of the Lianjia's proximity to customers policy, which is evidenced at the data level.
-Table \ref{tab:rd_bandwidth_kernel_results} considers different kernel and bandwidth choices, and the results are consistent with the 410 meters radius.
-The only non-significance is the CER-optimal bandwidth selector with triangular kernel, which is because the selected bandwidth is too small to capture the discontinuity.
-The results are robust to different bandwidth and kernel choices, which suggests that the 410 meters is the optimal radius for Lianjia's offline stores.
-
-To make the robust check we conducted Donut Hole test by excluding observations close to the cutoff and estimating the effect with the remaining data.
-The results are shown in Appendix and the result shows that the discontinuity still exists and this provides evidence against a model misspecification.
-Furthermore, we carry out the density test by \citep{MCCRARY2008698}.
-The result shows that the p-value is greater than 0.1 (p value equals 0.101), which suggests the result is not due to manipulation of polygons.
-Finally, we carry out placebo tests which are reported in Appendix, which shows that our result is robust.
-Specifically, Table \ref{tab:placebo_test_results} shows that the discontinuity does not exist in the placebo test, which suggests that our result is not due to the manipulation of the data.
-Table \ref{tab:movement_cutoff} shows that other cutoffs do not have the same effect as the 410 meters cutoff, which suggests that the 410 meters is the optimal radius for Lianjia's offline stores.
-
-\subsection{Statistical Summary} \label{subsec:Statistical_Summary}
-
-After constructing our optimal radius, we recalcualte the number of lianjia and other brokerages' stores within this radius.
-To check the robustness of the data, we divide our data to those with lianjia and those without lianjia and to check whether lianjia's offline stores have influential effect on the transaction effect in the community.
-We can see that for income, house tour number and the are all significantly different in those communities with or without lianjia.
-In addition, we find that the other brokerages also have the same tendency that they typically open stores with the same strategy as Lianjia, which suggests that Lianjia does not have the market power to exclude competent companies from entering the market, and it also suggests that the market is not monopolized by Lianjia.
-We plot the relationship between the number of other brokerages's stores and the number of lianjia's stores and the figure is shown in Figure \ref{fig:same_distribution}.
-
-From Table \ref{tab:statistical_district} we can see that the in our metro areas, the neighborhoods with lianjia within the influential radius tends to have higher number of sales, and the final transaction price is also \textyen 910,000 higher than those neighborhoods without lianjia.
-Moreover, the number of other stores within the influential distance is also signnificantly more than 7.3, which also aligns with our previous intuition that the market is not monopolized by Lianjia.
-This significance difference suggests that if we treat our sample as a cross sectional data and estimate the result with static model without considering the individual fixed effect, we may get a biased result.
-Besides, our model may suffer from endogeneity issue, since the number of lianjia's stores may be endogenous to the transaction price and the number of stores.
-
-\begin{table}[htb!]
-    \centering
-    \begin{tiny}
-    \caption{Statistical Summary for the Neighborhoods-Data with Lianjia and without Lianjia}
-    \input{../result_tables/summary_statistics_district.tex}
-    \label{tab:statistical_district}
-
-    Note that the code book of the variables can be seen in the Appendix \ref{tab:codebook}
-    \end{tiny}
-\end{table}
-
-\begin{table}[htb!]
-  \centering
-  \begin{tiny}
-  \caption{Statistical Summary for the Individual-Data with Lianjia and without Lianjia}
-  \input{../result_tables/summary_statistics_indi.tex}
-  \label{tab:statistical_individual}
-
-  Note that the code book of the variables can be seen in the Appendix \ref{tab:codebook}
-  \end{tiny}  
-\end{table}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.7\textwidth]{../figures/scatter_plot_with_two_brokerages.pdf}
-    \caption{Tendency between two types of brokerages}
-    \label{fig:same_distribution}
-    Note: the x-axis is the number of lianjia's stores and the y-axis is the number of other brokerages' stores. The fit is a cubic polynomial fit.
-\end{figure}
-
-\subsection{Stylized Fact} \label{subsec:stylized_fact}
-
-In our analysis, we focus on several dependent variables: \emph{the natural logarithm of lianjia's income}, \emph{the natural logarithm of home tours}, \emph{the natural logarithm of transaction period} and \emph{the price concession}.
-To quantify Lianjia's impact, we begin by establishing a key stylized fact, which we develop a Density-Based Index (DBI) index to capture the Lianjia's offline stores' influential ratio.
-The index is to measure the effects of Lianjia's operations and its continuous expansion.
-The definition of this index is informed by the results of an influential radius test, which helps us capture the spatial extent of Lianjia's influence on local real estate markets.
-This approach allows for a more nuanced understanding of how Lianjia's presence affects key market variables.
-The DBI is calculated as follows:
-
-\begin{equation*}
-  density_{it} = \frac{lianjia_{it}}{total_{it}},
-\end{equation*}
-
-where $lianjia_{it}$ represents the number of Lianjia's stores within a 410-meter radius and $total_{it}$ denotes the total number of real estate brokerages' stores within the same radius.
-The choice of this index is grounded in an effort to address potential reverse causality issues.
-Specifically, Lianjia and other brokerages often strategically place their stores in highly desirable locations, which typically also results high transaction volumes.
-This could potentially will caused our estimation biased if we were to simply count the number of Lianjia's stores.
-To control for this issue, we employ a comparative metric: the ratio of Lianjia brokerages to the total number of real estate brokerages within the radius.
-This ratio helps mitigate the bias that may arise from the strategic location choices of Lianjia, offering a clearer measure of its market influence relative to competitors.
-This approach aligns with the principles of spatial competition theory, as articulated in \citep{hotelling_stability_1929, daspremont_hotellings_1979} in competition model.
-Such a comparative metric not only provides a more accurate reflection of Lianjia's market penetration but also adheres to economic modeling standards by accounting for competitive dynamics in the sector.
-
-To capture the individual fixed effect and other time-invariant unobservable influential factors, a multi-way fixed effect model is proposed. The model is specified as follows:
-
-\begin{equation}
-  Y_{it} = \beta_0 + \beta_1 density_{it} + \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}, \label{eq:multi-way-fe}
-\end{equation}
-
-where $Y_{it}$ is the three main dependent variables, including $\log(\text{income})$, price concession, and $\log(\text{number of house tours})$, $density_{it}$ is the DBI, $\bf{X}_{it}$ is a set of control variables, including brokerage\_control L\_hedonic\_control, transaction\_control and region\_control, while $\tau_{it}$ is the time dummy variable interacting with the fixed effect of the business area, $\mu_i$ is the individual fixed effect and $\epsilon_{it}$ is the error term.
-The standard errors are clustered at the each community level.
-The results are shown in Table \ref{tab:stylized_fact}.
-
-\begin{table}[htb!]
-    \centering
-    \begin{scriptsize}
-    \input{../result_tables/stylized_fact}
-    \caption{The DBI influence to the lianjia's transaction}
-
-    Note: we omit all the control variables in the regression model, and detailed descriptions can be seen from Table \ref{tab:statistical_district} and Table \ref{tab:statistical_individual}.
-    \label{tab:stylized_fact}
-    \end{scriptsize}
-\end{table}
-
-In column 1 and 2, we estimated the model using the neighborhood-level data and in column 3 and 4, we estiamted the model using the individual-level data, respectively.
-The results show that the share of Linajia's offline stores in total brokerage plays a significant role in the real estate market, especially in terms of revenue and lead time, but not in terms of price concession and transaction period.
-Specifically, a 1\% increase in a Lianjia's DBI within an area correlates with a 7\% increase in income, as indicated in column 1.
-Furthermore, this increased DBI also leads to a 4\% increase in the number of home tours in the column 2, underscoring the Lianjia's increased visibility and potential for customer engagement.
-In contrast, the analysis shows no significant effect of DBI on price concessions and transaction time.
-This finding suggests that while a larger market share increases revenues and the number of house tours, it may not be beneficial for mathcing the buyers and sellers.
-The broader implications point to the strategic advantage of density or market share in driving business performance metrics, except for pricing strategies, which appear to be unaffected by changes in market share.
-
-Within the temporal scope of our investigation, the dataset encapsulates two distinct epochs: a phase characterized by surging housing prices and the subsequent period marked by the COVID-19 pandemic.
-These intervals were further complicated by regulatory measures enacted by the Chinese government, significantly altering the operational dynamics and influence of brokerages within the housing market.
-Acknowledging these temporal shifts necessitates a nuanced analysis of the brokerage effect across different stages of the study period to ensure the robustness of our findings.
-To address this, we adopt a dynamic analytical approach, dissecting the period into annual segments.
-This granularity is achieved by constructing seven unique variables, each representing the interaction between brokerage density and the respective $density_{it} * year_{it}$.
-Our methodology employs a multi-way fixed effects model, as detailed in Equation \eqref{eq:dynamic}, which facilitates a comprehensive examination of temporal variations in the brokerage's market impact.
-
-In the construction of our regression model, we deliberately omit the first period to avoid multicollinearity problem, treating it as a baseline for comparison.
-This strategic choice allows us to refine our proxy variable—the product of Lianjia's Dealership Balance Index (DBI) and annual dummies—as a more precise measure of Lianjia's local market power.
-Besides, to control for potential self correlation problem, we also included lagged one period dependent variables in the model.
-Other settings are the same with the previous model \eqref{eq:multi-way-fe} and the result is reported in Table \ref{tab:Dynamic}:
-
-\begin{equation}
-    Y_{it} = \beta_0 + \rho Y_{it-1} + \sum_{i=2}^7 density_{it} * year_{it} + \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}. \label{eq:dynamic}
-\end{equation}
-
-\begin{table}[H]
-  \begin{center}
-    \begin{scriptsize}
-    \caption{Dynamic Regression Results}
-    \label{tab:Dynamic}
-    \input{../result_tables/dynamic.tex}
-
-    Note: we omit all the control variables in the regression model, and detailed descriptions can be seen from Table \ref{tab:statistical_district} and Table \ref{tab:statistical_individual}.
-    \end{scriptsize}
-  \end{center}
-\end{table}
-
-The result highlights the dynamic impact of density, encapsulated by Lianjia's DBI, on transaction revenue, house tours, and price concessions over time, especially in response to external factors such as digital transformation and the COVID-19 pandemic.
-Initially, Lianjia's impact on transaction revenue showed a significant positive trend, peaking in 2018, due to its digital transformation efforts, including the integration of other platform stores into its shared network.
-However, the momentum slowed in 2020 and 2021, with the impact becoming significantly negative.
-This period coincided with the outbreak of the COVID-19 pandemic, which severely disrupted Lianjia's revenue streams and business activities due to widespread restrictions, underscoring the vulnerability of real estate transactions to macroeconomic shocks.
-In terms of home tours, Lianjia's impact remained robustly positive through 2019.
-This suggests that a strong market presence correlates with increased buyer attention, which translates into more home tours.
-However, pandemic-related restrictions dampened this effect in later years, highlighting the challenges posed by external constraints on physical real estate activity.
-For price concessions, we find that the Lianjia's DBI is significantly negatively correlated with the price concessions during pandemic periods.
-This is due to the fact that most transactions slow down during these periods and people are more likely to wait longer to find a buyer, which would result in fewer price concessions.
-
-To verify the robustness of our results, we calculated the Herfindahl-Hirschman Index (HHI) for each segmented market, defined as $HHI = \sum_{i=1}^N (s_i)^2$ where $s_i$ is the market share of firm $i$ expressed as a percentage.
-We then estimated the model by dividing the sample into high HHI (greater than 2000) and low HHI (less than 2000) groups.
-The results, shown in Table \ref{tab:sylized_fact_hetero_hhi}, indicate that Lianjia's offline stores have a more substantial impact on transaction properties in more competitive markets compared to more monopolized ones.
-This effect arises from two main factors: first, Lianjia's market power is insufficient to exclude other competitors from entering the market, and second, the area may not be attractive to other competitors, resulting in a larger market share for Lianjia.
-Furthermore, to address the heterogeneity issue, we introduced a dummy variable equal to one if the market already had Lianjia presence before 2016 and estimated the model by separating the sample based on this criterion.
-The results, presented in Table \ref{tab:sylized_fact_hetero_mature}, demonstrate that the years 2017, 2018, and 2019 have a significant positive impact on Lianjia's revenue in this segmented market.
-Another interesting phenomenon observed is that the number of house tours is significant for the years 2018 and 2019 in the lower maturity group, whereas in the higher maturity group, the number of house tours becomes significant in 2020.
-These findings indicate that in less mature markets, the entry of Lianjia drives increased profitability and enhances the attractiveness of its offline store strategy.
-Moreover, this suggests that Lianjia's market entry and subsequent strategies are more immediately impactful in less mature markets.
-
-% There should be a model like: Police brutality, law enforcement, and crime: Evidence from Chicago
-
-\section{Mechanism Design} \label{sec:mechanism_design}
-
-\subsection{Does Lianjia's Entry influence the segmented market?} \label{subsec:entry_effect}
-
-In the preceding section, our research concentrated on evaluating the dynamic impact of Lianjia's offline store operations.
-Nevertheless, the presence of a self-selection bias in this dynamic entry factor necessitates the application of causal inference methods to more accurately estimate the effect of Lianjia's offline stores.
-Consequently, we adopted the Difference-in-Difference (DiD) estimation technique.
-The foundation of this analysis is predicated on the assumption that the entry of a Lianjia store constitutes an exogenous shock within the local segmented market, thereby providing an unique natural experiment to examine the effects of offline expansion on the local real estate market.
-Although Lianjia's entry is not a randomized event, the DiD estimation method remains unbiased in estimating the entry effect by comparing variations in outcome variables before and after Lianjia's entry in the segmented market.
-
-To facilitate such an analysis, we have constructed a series of dummy variables associated with the presence of the Lianjia within the marketplace, delineated as $pre_2$, $pre_1$ (before entry), $entry$, $post_1$, $post_2$, and $post_3$ (successive post-entry intervals), which encapsulate the respective temporal epochs relative to the Lianjia's entry.
-To eliminate the effect of the well constructed effect, we drop all the variables that have Lianjia's offline stores before the year 2016 to better estimate the effect of Lianjia's entry on the market.
-These binary indicators serve as central regressors within a structured econometric model with $pre_1$ as the control group, described in Equation \eqref{eq:entry_effect}:
-
-\begin{equation}
-    Y_{it} = \beta_0 +  pre_2 + entry + \sum_{i=1}^3 post_i + \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}.   \label{eq:entry_effect}
-\end{equation}
-
-$pre_2, entry, post_i$ are correspondingly periods dummy variables and other settings are the same with Equation \eqref{eq:dynamic}. The results are reported in Table \ref{tab:entry_effect}.
-
-\begin{table}[htb!]
-  \begin{center}
-    \begin{scriptsize}
-    \caption{Entry Effect}
-    \label{tab:entry_effect}
-    \input{../result_tables/entry_effect.tex}
-
-    Note: we omit all the control variables in the regression model, and detailed descriptions can be seen from Table \ref{tab:statistical_district} and Table \ref{tab:statistical_individual}.
-    \end{scriptsize}
-  \end{center}
-\end{table}
-
-The results presented in the table \ref{tab:entry_effect} analyze the impact of Lianjia's offline stores entering segmented markets.
-Prior to Lianjia's entry ($pre_2$), there is no statistically significant effect on Lianjia's transaction properties, indicating that anticipation of Lianjia's entry does not influence these metrics.
-Post-entry ($entry$), there is a significant 9.1\% increase in revenue, suggesting a substantial boost in Lianjia's sales.
-However, this effect decreases to 4.7\% in the subsequent period ($post_1$) and continues to diminish in the following periods ($post_2$ and $post_3$), indicating a gradual decline in Lianjia's performance after the initial entry period.
-Similarly, the number of house tours exhibits a significant 2.3\% increase during the entry period, followed by a 3.\% increase in the first post-entry period.
-Nonetheless, this effect lessens in $post_2$, though it remains significant in $post_3$.
-This trend is attributed to the impact of the COVID-19 pandemic in 2020, which significantly affected the real estate market and brokerage's operation mode.
-
-In terms of the transaction period, the offline store's influence is always not significant, which suggests that the offline store's entry does not help to match the buyers and sellers in searching the houses, which is in line with the intuition that when platform is more mature, people's searching behavior is more likely to be online.
-Lastly, regarding price concessions, the entry of Lianjia's offline stores exhibits a 4.5\% positive effect.
-This suggests that the presence of offline stores may facilitate an increase in price concessions.
-This effect can be attributed to the enhanced efficiency in matching buyers with suitable properties, thereby encouraging sellers to be more amenable to price negotiations.
-Additionally, offline stores possess better control over neighborhood information, which aids in effectively marketing properties to potential buyers, thereby capturing additional surplus.
-
-In summary, the entry of Lianjia into a segmented market initially results in a significant increase in revenue and facilitates a higher number of house tours, which, in turn, leads to greater price concessions.
-However, this positive impact is transient, diminishing over time due to increased market competition and external factors such as the COVID-19 pandemic.
-This suggests that while Lianjia's entry provides a short-term boost to its market performance, the sustainability of this effect is challenged by both competitive dynamics and unforeseen external shocks.
-
-To verify the robustness of the entry effect, we classified the sample into low and high Herfindahl-Hirschman Index (HHI) groups.
-The results, presented in Table \ref{tab:entry_effect_robustness}, indicate that the income effect for Lianjia remains consistent across both groups.
-Specifically, income increases by 9.2\% during the entry period, with the effect decreasing to 5.1\% in the subsequent period for the higher HHI group, and increasing by 9.6\% during the entry period and decreasing to 4.7\% for the lower HHI group.
-However, a significant difference emerges in the number of house tours.
-The entry of Lianjia increases the number of house tours by 2.9\% for the higher HHI group and by 4.4\% for the lower HHI group.
-In the subsequent period, the effect diminishes for the lower HHI group, indicating that the entry of new competitors mitigates Lianjia's entry effect.
-Conversely, the entry effect remains significant for the higher HHI group.
-This analysis underscores the varying impacts of market concentration on Lianjia's market performance post-entry.
-
-Furthermore, in columns 5 and 6, the entry of Lianjia's offline stores significantly shortens the transaction period for the higher HHI group.
-This suggests that offline stores enhance market efficiency by better matching buyers and sellers.
-Conversely, this effect is not significant in the lower HHI group, indicating that the benefits of offline stores diminish in more competitive markets.
-Regarding price concessions, the entry of Lianjia's offline stores does not have a significant effect in the lower HHI group initially.
-However, by the $post_3$ period, the effect becomes significant and positive.
-This delayed impact may be attributed to the offline stores gradually improving market transparency and information dissemination, which eventually leads to better price concessions.
-For the higher HHI group, the entry of Lianjia's offline stores consistently has a significant effect on price concessions.
-This reinforces the notion that in less competitive markets, offline stores play a crucial role in facilitating better matches between buyers and sellers and improving overall market efficiency.
-In the Appendix we also conducted the robustness check by classifying the group by matured market and less matured market.
-[ THERE IS ALSO A GRAPH OF PARALLEL TREND NEED TO BE ADDED HERE.
-]
-
-\begin{table}
-  \begin{center}
-    \begin{scriptsize}
-      \caption{Robustness Check of Entry Effect}
-      \label{tab:entry_effect_robustness}
-      \input{../result_tables/entry_effect_hetero.tex}
-
-    Note: we omit all the control variables in the regression model, and detailed descriptions can be seen from Table \ref{tab:statistical_district} and Table \ref{tab:statistical_individual}.
-    \end{scriptsize}
-  \end{center}
-\end{table}
-
-\subsection{Estimate Lianjia's platform consolidation effect} \label{subsec:acn_strategy}
-
-To empirically estimate the effect of Lianjia's platform strategy, we consider an exogenous shock that occurred during our study period: Lianjia's implementation of a downstream consolidation strategy.
-This strategy involves the integration of offline stores with online platforms, leveraging the advantages of Lianjia's Agent Cooperation Network (ACN) strategy.
-The ACN strategy subdivides the entire process of buying and selling a house into distinct parts, with each part managed by a specific agent or store.
-By sharing transaction dividends among multiple stores, Lianjia fosters cooperation with other market competitors and integrates their resources to enhance service quality for customers.
-This approach is designed to improve efficiency and customer satisfaction by combining online and offline resources, thus providing a comprehensive and streamlined service experience.
-
-This strategy is a significant change in Lianjia's business model, and it is expected to have a significant impact on the market.
-In addition to this, Lianjia also opened up the form of franchises and gradually started platform integration.
-To empirically measure the effect of platformization to the offline stores' operations, we first counted the number of all non-Lianjia stores on the Lianjia's Beke platform within a radius of 410 meters, which allowed us to generate a dummy variable $Treatment_{it}$ to represent whether or not there are any other affiliate stores within the platform in this neighborhood.
-To dynamically capture the varying effects, we generate $Treatmetn_{it} * year$ by producting the year dummy variable with the $Treatment_{it}$ and include them in our regression model.
-Since the ACN network was officially established at the end of 2018, we can generate a dummy variable equal to 1 if the year is greater than 2018.
-We then consider the following regression model:
-
-\begin{equation}
-    Y_{it}  = \beta_0 + \sum_{i=1}^5 Treatment_{it} * year + \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}. \label{eq:acn_assessment}
-\end{equation}
-
-By focusing on 2017 as the baseline, we can empirically estimate the outcomes with greater precision and reliability, ensuring that our analysis accurately reflects the impact of Lianjia's strategy without the confounding effects of prior periods.
-Other settings are consistent with previous table \ref{tab:Dynamic} and the result is reported in Figure \ref{fig:dynamic_effect}.
-
-\begin{figure}[ht]
-    \centering
-    \subfloat[Effect to income]{\includegraphics[width=0.5\textwidth]{../figures/did_1.pdf}\label{fig:did_income}}
-    \subfloat[Effect to number of house tours]{\includegraphics[width=0.5\textwidth]{../figures/did_2.pdf}\label{fig:did_lead_times}}
-    \hfill % Adds horizontal space between figures
-    \subfloat[Effect to transaction period]{\includegraphics[width=0.5\textwidth]{../figures/did_3.pdf}\label{fig:negotiation_period}}
-    \subfloat[Effect to price concession]{\includegraphics[width=0.5\textwidth]{../figures/did_4.pdf}\label{fig:did_price_concession}}
-    \caption{Estimation of ACN Platformization Effect}
-    \label{fig:dynamic_effect}
-\end{figure}
-
-The empirical findings indicate that during the first year of consolidation, Lianjia's transaction revenue did not show a statistically significant difference from zero.
-However, from 2019 to 2021, the transaction revenue demonstrated a significant positive increase, ranging from 4.9\% to 2.6\%.
-Additionally, the consolidation of the platform had a significantly positive impact on the number of house tours, which increased by 3.9\% to 6.4\% from 2018 to 2022, with this trend continuing upward throughout the sample period.
-Furthermore, when comparing the effect of platform consolidation with the entry effect of offline stores, the data clearly show that the platformization effect is substantially more pronounced.
-This suggests that the platformization strategy is markedly more effective than the offline store entry strategy in generating revenue and attracting buyers in the market.
-These results underscore the superior efficacy of platform consolidation in enhancing market performance and provide compelling evidence for the strategic advantage of platformization over traditional offline expansion.
-
-However, in terms of the transaction period, the platformization strategy does not exhibit a significant effect, indicating that platformization does not assist brokerages in facilitating better matching and negotiation between sellers and buyers.
-A similar pattern is observed in price concessions, suggesting that the platformization strategy does not contribute to reducing price concessions.
-While the platformization strategy is less effective in influencing individuals' decision-making processes compared to offline store entry, it proves more effective in increasing revenue and the number of house tours.
-This discrepancy highlights that the platformization strategy excels in attracting customers and generating revenue, but falls short in aiding the matching and negotiation process.
-These findings align with the intuition that platformization is more likely to draw customers and boost revenue, yet it is less effective in assisting buyers and sellers in reaching agreements.
-
-To further investigate the impact of market concentration on the effectiveness of the platformization strategy, we classified the samples into high and low Herfindahl-Hirschman Index (HHI) groups and estimated the model separately for each group.
-The high HHI group, representing markets with higher concentration, revealed that the platformization strategy does not confer significant benefits for Lianjia's operations.
-Conversely, in the low HHI group, indicative of less competitive markets, the platformization strategy significantly increases revenue.
-This suggests that the platformization strategy is more effective in less competitive markets, enhancing Lianjia's competitiveness.
-In terms of the number of house tours, the effect of platformization is consistent across both high and low HHI groups.
-This consistency aligns with the intuition that consumer preferences for different types of brokerages are similar, and individuals are equally likely to search for houses online regardless of the brokerage's market share.
-Moreover, our analysis in columns 5 to 8 shows that the platformization strategy does not have a significant effect on the transaction period or price concessions.
-This finding suggests that the platformization strategy does not facilitate better matching between buyers and sellers or improve the negotiation process.
-This aligns with the intuition that while the platformization strategy can attract more customers and generate revenue, it does not inherently improve the efficiency of matching buyers and sellers or negotiating terms because most of the transactions are still offline based.
-
-\begin{table}
-  \begin{center}
-    \begin{scriptsize}
-      \caption{Robustness Check of Online Consolidation Effect}
-      \label{tab:heter_platform_did}
-      \input{../result_tables/heter_platform_did.tex}
-
-    Note: we omit all the control variables in the regression model, and detailed descriptions can be seen from Table \ref{tab:statistical_district} and Table \ref{tab:statistical_individual}.
-    \end{scriptsize}
-  \end{center}
-\end{table}
-
-In the online Appendix \ref{tab:platform_consolidation_hetero_mature}, we present the heterogeneous effects of Lianjia's operations in both mature and immature markets.
-Figure \ref{fig:treatment_consolidation} illustrates the distribution of income across the treatment and control groups.
-Prior to the intervention, the two groups exhibit parallel trends, indicating no significant differences.
-The treatment effect becomes significant only after the first period, aligning with our empirical findings.
-
-\section{Conclusion and Discussion} \label{sec:conclusion}
-
-The Chinese real estate market witnessed a significnat drop at 2022 and the labor market is fierece in recently and therefore, the people are pretty hard to get on jobs.
-
-The study of Lianjia's strategic expansion into China's real estate brokerage industry, particularly through the implementation of the ACN and the proliferation of offline branches, underscores a transformative impact on market dynamics and transaction efficiency.
-Our empirical research shows that Lianjia's approach, which seamlessly integrates online platforms with an extensive offline presence, significantly enhances revenue generation and influences consumer behavior, particularly through improved price concessions and increased home viewing.
-The study highlights the critical role of offline store information and community proximity in increasing transaction revenue and achieving market dominance, even in the face of increasing monopolization trends.
-Despite the adverse effects of the COVID-19 pandemic, which temporarily diluted the benefits of both customer base expansion and information dissemination, the resilience of physical stores emerges prominently.
-This resilience, coupled with the strategic leverage of online platforms, underscores the importance of a synergistic online-offline model in overcoming market challenges and maintaining competitive advantage.
-The findings argue for a nuanced understanding of platform-based monopolization in real estate, suggesting that the successful integration of digital and physical domains can significantly enhance service delivery, market penetration, and overall system competitiveness, paving the way for a more adaptive and robust market system in the face of evolving challenges.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\clearpage
-\begin{singlespace}
-%\bibliographystyle{plainnat}
-%\bibliographystyle{chicago}
-\bibliographystyle{aer}
-\bibliography{our-cites.bib}
-\end{singlespace}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%% These commands start the appendix and change the Table & Figure numbering
-\newpage
-\appendix
-\setcounter{table}{0}
-\renewcommand{\tablename}{Appendix Table}
-\renewcommand{\figurename}{Appendix Figure}
-\renewcommand{\thetable}{A\arabic{table}}
-\setcounter{figure}{0}
-\renewcommand{\thefigure}{A\arabic{figure}}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Appendix Tables and Figures}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.7\textwidth]{../figures/distribution_of_ten_cities.pdf}
-  \caption{Distribution of Ten Cities's Brokerages Store Shares}
-  \label{fig:distribution_store_shares}
-  Note: the x-axis is city's name and the y-axis is the offline brokerage's stores share in the city. The data source is from AutoNavi Map.
-\end{figure}
-
-% \input{tab_tex/other-regressions.tex}
-
-\input{../figures/distribution_of_hp_and_broker.tex}
-
-\input{../result_tables/donut_robust.tex}
-
-\input{../result_tables/rdd_placebo_test.tex}
-
-\input{../result_tables/movement_cutoff.tex}
-
-\clearpage
-
-\begin{table}[H]
-  \begin{center}
-    \begin{scriptsize}
-    \caption{Robustness Check By HHI Index}
-    \label{tab:dynamic_hhi}
-    \input{../result_tables/robust_hhi.tex}
-
-    \end{scriptsize}
-  \end{center}
-\end{table}
-
-\clearpage
-
-\begin{table}[H]
-  \begin{center}
-    \begin{scriptsize}
-    \caption{Robustness Check By Market Maturity Index}
-    \label{tab:platform_consolidation_hetero_mature}
-    \input{../result_tables/robust_mature.tex}
-
-    \end{scriptsize}
-  \end{center}
-\end{table}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.7\textwidth]{../figures/average_income_by_treatment_platform.pdf}
-    \caption{Treatment Effect of platform consolidation}
-    \label{fig:treatment_consolidation}
-    Note: the x-axis is year and the y-axis is the average income of Lianjia in each year. The graph uses the neighborhood-level data.
-\end{figure}
-
-\begin{table}[H]
-  \begin{center}
-    \begin{scriptsize}
-    \caption{Codebook}
-    \label{tab:codebook}
-    \input{../result_tables/code_book_table.tex}
-
-    \end{scriptsize}
-  \end{center}
-\end{table}
-
-\end{document}
-
 \subsection{Robustness Check} \label{subsec:robustness_check}

### 2024-06-26 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.bbl 	modified:   manuscript/main.blg 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	modified:   manuscript/our-cites.bib 	modified:   network_estimation/network_estimation.ipynb 	modified:   network_estimation/network_formulation.cpp 	modified:   network_estimation/network_formulation.so
update the bibtex

@@
-\documentclass[12pt]{article}
-\usepackage[right=0.7in,left=0.7in,top=1in,bottom=1in]{geometry}
+\documentclass[11pt]{article}
+\usepackage[right=1in,left=1in,top=1in,bottom=1in]{geometry}
 \usepackage{hyperref}
@@
 
+The result is consistent with the opinion that most platform like uber and lyft that does not have enough network strength and \citep{10.1257/jep.28.2.3}
+
+\citep{WOS:000454186600016}
+
 \section{Collaborative Spillover Effect} \label{sec:network_effect}
@@
 \end{document}
-
-\subsection{Robustness Check} \label{subsec:robustness_check}
-
-\begin{table}[H]
-  \begin{center}
-    \begin{scriptsize}
-    \caption{Robustness Check Using HHI Index}
-    \label{tab:sylized_fact}
-    \input{../result_tables/robust_hhi.tex}
-
-    \end{scriptsize}
-  \end{center}
-\end{table}
-
-\begin{table}[H]
-  \begin{center}
-    \begin{scriptsize}
-    \caption{Robustness Check}
-    \label{tab:sylized_fact}
-    \input{../result_tables/robust_mature.tex}
-
-    \end{scriptsize}
-  \end{center}
-\end{table}
-
-\newpage 
-\section{Appendix One \label{sec:appendix:first}}
-\renewcommand{\thetable}{B\arabic{table}}
-\setcounter{table}{0}
-\renewcommand{\thefigure}{B\arabic{figure}}
-\setcounter{figure}{0}
-
-% \input{fig_tex/fig_another_figure.tex}
-
-\newpage
-\section{Appendix Two
-\label{sec:appendix:two}}
-\renewcommand{\thetable}{C\arabic{table}}
-\setcounter{table}{0}
-\renewcommand{\thefigure}{C\arabic{figure}}
-\setcounter{figure}{0}
-
-When it comes to the estimation of the entry effect and its continuous effect, we use the following model:
-
-\begin{equation}
-  \begin{aligned}
-    Y_{it} & = \beta_0 + \beta_1 Pre_3 + \beta_2 Pre_2 + \beta_3 Entry \\
-    & + \beta_4 Post_1 + \beta_5 Post_2 + \beta_6 Post_3  + \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}.
-  \end{aligned}
-\end{equation}
-
-where $Pre$ is the pre-period of lianjia's entry, $Entry$ is the entry period, and $Post$ is the post-period of lianjia's entry. All other model settings are the same as the previous model.
-
-Finally, we construct a proxy variable to capture the continuous effect of the DBI. The model is as follows:
-
-\begin{equation}
-  \begin{aligned}
-    Y_{it} & = \beta_0 + \beta_1 proxy\_entry + \beta_2 proxy\_pos\_1 \\
-    & + \beta_3 proxy\_pos\_2 + \beta_4 proxy\_pos\_3 + \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}.
-  \end{aligned}
-\end{equation}
-
-where $proxy\_entry$ is the product of the entry effect and the DBI, and $proxy\_pos\_i$ is the product of the post-period effect and the DBI.
-All other model settings are the same as the previous model.
-The results are shown in Appendix Table \ref{tab:Baseline} and Appendix Table \ref{tab:Dynamic}.
-
-However, our estimates may not be asymptotically efficient due to the endogeneity of DBI and serial correlation issues.
-First, DBI is endogenous because the entry of lianjia is endogenous.
-This is due to the fact that lianjia will choose better locations with higher potential revenues in order to maximize profits.
-Second, the model suffers from serial correlation because our sample is during the boom period of China's real estate market, and as the number of transactions in the real estate market increases, so do the revenues and prices in the brokerage industry.
-In addition, lianjia tend to be concentrated in popular areas, which makes for greater growth and thus confounds our estimates.
-To solve this problem, we use a dynamic panel model for estimation.
-Dynamic panel models can capture the dynamics of the process by using the lagged dependent variable as a regression variable.
-This helps in understanding how the past values of the variables affect their current values.
-
-To estimate the dynamic panel model, we use the Arellano-Bond (1991) GMM estimator, which is a two-step estimator.
-The first step is to use the lagged dependent variable as an instrument for the current dependent variable, and the second step is to use the lagged residuals as an instrument for the current dependent variable.
-In this paper, we do not use system GMM estimator because the system GMM must assume that the lagged explanatory variables are independent of factors that do not vary over time in the region, and this clearly cannot hold in the present setting.
-The model is as follows: [\textbf{this should be a line that describes what measures that we use to construct the model}]
-
-\begin{equation}
-  \begin{aligned}
-    \Delta Y_{it} & = \rho \Delta Y_{it-1} + \beta_1 \Delta Measure_{it} + \bf{\alpha} \Delta \bf{X}_{it} + \Delta \tau_{it} + \Delta \epsilon_{it}.
-  \end{aligned}
-\end{equation}
-
-where $\Delta Y_{it}$ is the first difference of the dependent variable, $\Delta Measure_{it}$ is the first difference of the our three measurement methods, $\Delta \bf{X}_{it}$ is the first difference of the control variables, $\Delta \tau_{it}$ is the first difference of the time dummy variable interacting with the fixed effect of the business area, and $\Delta \epsilon_{it}$ is the first difference of the error term.
-The standard errors are clustered at the individual level.
-The results are shown in Appendix Table \ref{tab:GMM}.
-
-For Table \ref{tab:Baseline}, the result reveals a significant correlation between the lianjia's local market power and lianjia's income in this given community.
-However, we discovered no substantial influence of lianjia's local market power on the housing prices or transaction periods in the same community.
-This could be interpreted to mean that whilst Lianjia's local market power could induce an increase in income, it does not necessarily grant them any significant pricing power nor expedite the transaction period.
-Therefore, we may deduce that the augmentation of Lianjia's income is primarily driven by an increase in the number of transactions, presumably due to more property listings by Lianjia within the community.
-This suggests that although lianjia can control more market share in the local market, it does not necessarily mean that it can have monopoly power in this given region.
-This is partially because the price of the house is determined by the market, and there are also some potential other brokerages that can enter the market.
-However, lianjia's local market power can still have a significant influence on the income because they can list more housings and have more transactions in the local market.
-
-To further test the results, we first check if lianjia's entry effect and continuous effect is significant.
-For column 1, 3, and 5 of the Table \ref{tab:Dynamic}, the result reveals that before the lianjia's entry, the natural logarithm of income, housing price and transaction period are not significant.
-After the entry, we see that after lianjia's entry into this local market, lianjia can immediately increase their income and keep making significantly more income comparing with previous periods.
-Besides, we see that the entry do not significantly increase the housing price immediately but significantly increase housing price one year after but later on turning back to the normal pricing.
-Lastly, the lianjia's entry do not significantly lowers the transaction periods.
-This is consistent with our previous results that lianjia's entry can significantly increase the income but not the housing price and transaction periods in equilibrium.
-
-Lastly, we use the third measurement to test after the lianjia's entry, the continuous effect of lianjia's local power of the local market.
-For column 2, 4, and 6 of the Table \ref{tab:Dynamic}, the result reveals that the continuous effect of lianjia's local power of the local market is significant for the income, housing price and transaction periods.
-This result indicates that in different period, the lianjia's local market power can have different influence on the market.
-
-% we can not say that it is a martingale process because the housing market is assymetric information and martingale process is a fair game.
-\section{Theoretical Model} \label{sec:theoretical_model}
-
-% we can make the number of stores to $n$ instead of $2$ to make the model more general.
-
- % we may assume the number of houses in each community follows a normal distribution to make the model can have some probability distribution.
-
- % I think this model does not evaculate the meaningful information from the paper, and the paper does not have anything interesting to say in this model.
-
-We can try to decompose the
-
-In spired by the finding of the stylized fact, we propose a theoretical model to explain the mechanism behind the empirical results.
-Our model accurately reflects the real-world scenario in which sellers face uncertainty regarding the number of buyers each platform might attract, whereas buyers have the advantage of accessing comprehensive online information to make informed decisions about potential house purchases.
-This model also encapsulates the dynamics of a two-sided market, characterized by the mutual attraction between buyers and sellers.
-However, due to asymmetric information, sellers are unable to determine which brokerage will attract the most buyers, creating a gap in their market strategy effectiveness.
-
-To characterize the real estate brokerage market, we can assume that there are $\mathcal{N}$ types of brokerages in the market, where the type $1$ denote the large real estate brokerage that is incorporating the online platform and the offline stores strategies, and the type $2$ to type $\mathcal{N}$ denote the small real estate brokerage that only have the offline stores and they should compete with the type $1$ stores and type $2, \ldots, \mathcal{N}$ stores in the market.
-Each type of brokerage follows a standard percentage charge by $r_j$ where $j \in \{1, 2, \ldots, \mathcal{N}\}$ and they can not manipulate the percentage charge in each submarket.
-
-We can assume that there are $M$ number of communities in the market, and each market has $\kappa_i, i \in \{1, \ldots, M\}$ number of houses listed.
-Assume that the sellers are indifferent among the brokerages and therefore, their chossing is only dependent on the proportion of stores in the market.
-We can denote the number of two types of brokerages by $\mathcal{B}_{1, i}$ and $B_{2, i}$, respectively and therefore, the number of houses listed in the brokerage $j$ is $\kappa_{i} \times \frac{\mathcal{B}_{i, i}}{\mathcal{B}_{i, 1} + \mathcal{B}_{i, 2}}$.
-We can assume that the price of the house is determined by the hedonic pricing model from various confounding factors that are determined by the community and unique characteristics of the housing, and we can denote it as $P_i$ that can be ranked and distributed over the range $[\underline{P}_i, \overline{P}_i]$.
-Sellers have a reservation price $\tilde{P}_i$ over the house they sell.
-
-The brokerages have the same positive cost function denoted as $C(\cdot)$ where $\frac{\partial C(\cdot)}{\partial \mathcal{B}_{j}} > 0$ and $\frac{\partial C^2(\cdot)}{\partial \mathcal{B}_{j}^2} > 0$ where $j \in \{1, 2, \ldots, \mathcal{N}\}$.
-The intuition is that because of the marginal cost of the platform is $0$, when considering the cost of opening additional stores in the market, the brokerage does not incur that cost into consideration and therefore, the cost function is equal for both types of stores.
-Moreover, the marginal cost of opening additional stores is increasing, which is consistent with the real estate brokerage market because the more stores the brokerage opens, the administrative cost will increase.
-
-We can inherent from the previous literature that there are broad searchers and narrow searchers in the market, \citep{10.1257/aer.20141772}.
-Specifically, we can assume that there are $L^N_i$ narrow searches that are only searching for the community $i$ and let $L^B$ denote the set of broad searchers, defined as those individuals who consider a $\beta$ proportion of all available houses within their expansive search criteria.
-When $\beta = 1$ it means that they are searching for all the available houses in the whole city and $\beta < 1$ indicates a limited scope, possibly due to preferences or capacity constraints.
-Correspondingly, $L^B_i$ represents the subset of broad searchers within community $i$, and the expected number is given by $L^B_i = L^B \times \beta$.
-We can denote the buyers' utility of owning the house by $U_{i, j}$
-
-We can first focus on the naive searchers in the real estate market.
-These individuals are typically drawn to platforms based on the breadth of listings available.
-Specifically, the probability that a naive searcher will choose brokerage $j$ can be characterized by the principle of the two-sided market.
-This decision is influenced by the ratio of the number of houses listed by brokerage $j$ to the total number of houses listed within community $i$.
-This model aligns with the framework proposed by \citep{Armstrong2006}, where market attractiveness is proportional to the available inventory a brokerage offers relative to the community aggregate:
-
-\begin{equation}
-  N_{i, j} = L^N_i \times \frac{\mathcal{B}_{i, j}}{\sum_{j^\prime=1}^{\mathcal{N}}\mathcal{B}_{i, j^\prime}}. \label{eq:naive_prob}
-\end{equation}
-
-However, the broad searchers in the market are attracted to the platform by the networking because they are searching for all the communities in the market, and buyers have different preferences for brokerages based on their online presence, reputation and other factors, with private information $\theta_{b, j}$ representing the buyer's preference for brokerage $j$.
-
-\begin{equation}
-  B_i = L^B_i \times \alpha_j \times \frac{\mathcal{B}_{i, j} \times \theta_{b, j}}{\sum_{j^\prime=1}^{\mathcal{N}}\mathcal{B}_{i, j^\prime} \times \theta_{b, j^\prime}} \label{eq:broad_prob}
-\end{equation}
-
-and we can release this assumption later to make the customers have private preference towards each type of brokerage and the brokerages can not observe this pattern.
-Combinning \eqref{eq:naive_prob} and \eqref{eq:broad_prob}, we can get the total number of customers in the community $i$ and the brokerage $j$ is:
-
-\begin{equation}
-  L_{i, j} = N_{i, j} + B_{i, j} = (L^N_i + L_B \times \beta \times \alpha_j) \times \frac{\mathcal{B}_{i, j} \times \theta_{b, j}}{\sum_{j^\prime=1}^{\mathcal{N}}\mathcal{B}_{i, j^\prime} \times \theta_{b, j^\prime}}
-   \label{eq:total_prob}
-\end{equation}
-
-We can assume the probability of a successful match between buyers and sellers, which increases with the number of participants on the platform, as $\tau_{i, j} = f(\frac{\mathcal{B}_{i, j}}{\sum_{j^\prime=1}^{\mathcal{N}}\mathcal{B}_{i, j^\prime}})$ and the revenue for each brokerage $j$ in community $i$ can be calculated by considering the total number of transactions completed, which is the product of the number of customers handled by the brokerage and the probability of transaction completion.
-
-\begin{equation}
-  R_{i, j} = \tau_{i, j} \times L_{i, j} \times P_i \times r_j \label{eq:revenue}
-\end{equation}
-
-and the correspondingly, the total profit for the brokerage $j$ in the community $i$ is:
-
-\begin{equation}
-  \Pi_{i, j} = R_{i, j} - C(\mathcal{B}_{i, j}) \label{eq:profit}
-\end{equation}
-
-The consumer surplus is then: $CS = \sum_{i=1}^M \sum_{j=1}^{\mathcal{N}} \int_0^{L_{i, j}} (U_{i, j} - P_i) dx$.
-
-% \begin{assumption}[homogenous brokerage]
-%  The brokerage $1$'s network effect is greater than other brokerages in the market and assume that the small brokerages (Type $2$ to $\mathcal{N}$) are homogenous and they have the same network effect in the market, i.e., $\alpha_2 = \ldots = \alpha_{\mathcal{N}} = \alpha_s$, where $\alpha_s$ is the network effect for small brokerages.
-We have $\alpah_1 > \alpha_s$.
-% \end{assumption}
-
-\begin{proposition}[brokerage $1$'s optimal choice]
-  In equilibrium, the market share of Brokerage 1 (Type 1) is greater than its proportion of the number of stores, and the optimal brokerage fee charged by Brokerage 1 is higher than that charged by other brokerages.
-\end{proposition}
-
-\begin{proof}
-  The total number of customers for Brokerage 1 in community $i$ is given by $L_{i, 1}$ and the total number of stores is $L_{i}$:
-
-  \begin{equation}
-    \text{Market Share}_{i, 1} = \frac{L_{i, 1}}{L_i}
-  \end{equation}
-
-  Since $\alpha_1 > \alpha_s$ and assuming $\theta_{b, 1} \geq \theta_{b, j}$ and Brokerage 1 will attract a higher proportion of broad searchers $L^B$, resulting in a larger market share.
-Thus, in equilibrium, the market share of Brokerage 1 is greater than its proportion of the number of stores.
-
-  To maximize the profit, brokerage $1$ will change $r_1$ such that: $\frac{\partial \Pi_{i, 1}}{\partial r_1} = \frac{\partial R_{i, 1}}{\partial r_1} - \frac{\partial C(\mathcal{B}_{i, 1})}{\partial r_{1}} = 0$.
-Since $\tau_{i, 1}$ and $L_{i, 1}$ are higher for brokerage $1$ due to the stronger network effect, the optimal $r_1$ will be higher compared to the fees charged by other brokerages, $r_j$ for $j \neq 1$.
-\end{proof}
-
-In the following proposition, we will derive the total surplus of the model.
-
-This model is not good right now because there is no better way to conduct welfare analysis.
-
-% now consider the two-period entry model now consider the case of the first period there is an equilibrium with all other broekrages but in the next period there is an entry of the first brokerage then derive the new equilibrium of the market and conduct the wellfare analysis in this case
-
-\begin{proposition}[two-period entry model]
-
-\end{proposition}
-
-% where $N^e(B_{1, i})$ is a function representing the network effects, and is modeled as $N^e(B_{1, i}) = 1 + \alpha \log(1 + B_{1, i})$ where $\alpha$ is a parameter that quantifies the strength of network effects and the logarithmic form captures diminishing returns to scale as the number of brokerages increases.
-The revenue for each brokerage type $j$ in community $i$ is proportional to the number of houses they sell, which depends on the number of customers they attract:
-
-% where $N_{i, j, t}$ is the number of customers selecting type $j$ brokerage in community $i$ at time period $t$, estimated by:
-
-% \begin{equation}
-%  N_{i, j, t} = \lambda_i p_{i, j, t}
-%\end{equation}
-
-%and $\lambda_i$ is the appropriate part of $\lambda$ that arrives in community $i$.
-
-%give me a mathematical economics model characterizing the partial equilibrium of real estate broekrage and the competitive market where there are two types of brokerages denoted 1 if the brokerage is the large brokerage that it can communicate with other stores in different regions of the same type 1 brokerage, and denote 2 if it is small brokerage that it can not communicate with the other brokerages in the market
-
-% The first proposition is that the charging fee should be higher comparing with type $2$ brokerage.
-
-% The second proposition is that the number of stores in high popular regions should be higher in the number of stores and they are more likely to form a network effect.
-
-% The third proposition is the introduction of the platform should increase the number of transactions and the number of stores in the market.
-
-% The fourth proposition is that the entry of the large brokerage can increase the transaction number and the number of stores in the market.
-
-% The fifth proposition should be the fact that when there is negative shock to the customers, the number of transactions and the number of stores should decrease and the number of brokerage fee should decrease in the long run (which can be modeled using graph or simulation).
-
-% The sixth proposition should be the fact that before the increase of the
-
-We can examine the following two effects:
-
-\begin{itemize}
-  \item The real estate brokerage's network effect where the brokerages are more likely to form a edge between each other (this is demonstrated in the ACN's brokerage network model)
-  \item The partial effect of the network effect is not characterized by the price level changes or the brokerage fee increase.
-  \item The network effect should be demonstrated by the increase in the number of transactions and the number of the stores within given radius comparing with the total number of houses in this market.
-\end{itemize}

### 2024-06-27 manuscript/main.tex

@@
 \usepackage{booktabs}
+\usepackage{endnotes}
 \usepackage{pgfplots}
@@
 This is corroborated by studies indicating that an increase in the number of brokers can depress house prices and shorten transaction cycles \citep{https://doi.org/10.1002/jae.2891}.
-Additionally, \citet{qu_identifying_2021-1} highlights the moderating role of broker commissions in disseminating information during transactions, facilitating more efficient home sales.
+Additionally, \citet{qu_identifying_2021} highlights the moderating role of broker commissions in disseminating information during transactions, facilitating more efficient home sales.
 Other related literature includes \citep{doi:10.1080/10527001.2021.2016340, doi:10.1080/10835547.1996.12090852}.
@@
 %\bibliographystyle{chicago}
-\bibliographystyle{aer}
-\bibliography{our-cites.bib}
+% \bibliographystyle{aer}
+% \bibliography{our-cites.bib}
+
+\begin{thebibliography}{}
+
+  \bibitem[Bailey et al.(2018)]{bailey_economic_2018}
+  Bailey, M., R. Cao, T. Kuchler, and J. Stroebel. 2018. The Economic Effects of Social Networks: Evidence from the Housing Market. \textit{Journal of Political Economy}, 126(6), 2224-2276.
+
+  \bibitem[Rosen(1974)]{Rosen_hedonic}
+  Rosen, S.
+1974.
+Hedonic Prices and Implicit Markets: Product Differentiation in Pure Competition.
+\textit{Journal of Political Economy}, 82(1), 34-55.% Available at \url{http://www.jstor.org/stable/1830899}.
+
+  \bibitem[Chen and Wen(2017)]{chen_great_2017}
+  Chen, K., and Y. Wen. 2017. The Great Housing Boom of China. \textit{American Economic Journal: Macroeconomics}, 9(2), 73-114.
+
+  \bibitem[Farrell and Shapiro(1990)]{farrell_horizontal_1990}
+  Farrell, J., and C. Shapiro. 1990. Horizontal Mergers: An Equilibrium Analysis. \textit{American Economic Review}, 80(1), 107-126.
+
+  \bibitem[Athey and Imbens(2016)]{athey_recursive_2016}
+  Athey, S., and G. Imbens. 2016. Recursive Partitioning for Heterogeneous Causal Effects. \textit{Proceedings of the National Academy of Sciences of the United States of America}, 113(27), 7353-7360.
+
+  \bibitem[d'Aspremont et al.(1979)]{daspremont_hotellings_1979}
+  d'Aspremont, C., J. J. Gabszewicz, and J.-F. Thisse. 1979. On Hotelling’s "Stability in Competition". \textit{Econometrica}, 47(5), 1145-1150.
+
+  \bibitem[Glaeser et al.(2017)]{glaeser_real_2017}
+  Glaeser, E., W. Huang, Y. Ma, and A. Shleifer. 2017. A Real Estate Boom with Chinese Characteristics. \textit{Journal of Economic Perspectives}, 31(1), 93-116.
+
+  \bibitem[Grossman and Stiglitz(1980)]{grossman_impossibility_1980}
+  Grossman, S. J., and J. E. Stiglitz. 1980. On the Impossibility of Informationally Efficient Markets. \textit{American Economic Review}, 70(3), 393-408.
+
+  \bibitem[Handbury(2021)]{handbury_are_2021}
+  Handbury, J. 2021. Are Poor Cities Cheap for Everyone? Non-Homotheticity and the Cost of Living Across U.S. Cities. \textit{Econometrica}, 89(6), 2679-2715.
+
+  \bibitem[Hendel et al.(2009)]{hendel_relative_2009}
+  Hendel, I., A. Nevo, and F. Ortalo-Magné. 2009. The Relative Performance of Real Estate Marketing Platforms: MLS versus FSBOMadison.com. \textit{American Economic Review}, 99(5), 1878-1898.
+
+  \bibitem[Hotelling(1929)]{hotelling_stability_1929}
+  Hotelling, H. 1929. The Stability in Competition. \textit{Economic Journal}, 39, 41-57.
+
+  \bibitem[Hsieh and Moretti(2003)]{hsieh_can_2003}
+  Hsieh, C.-T., and E. Moretti. 2003. Can Free Entry Be Inefficient? Fixed Commissions and Social Waste in the Real Estate Industry. \textit{Journal of Political Economy}, 111(5), 1076-1122.
+
+  \bibitem[Hui and Chan(2014)]{hui_foreign_2014}
+  Hui, E. C. M., and K. K. K. Chan. 2014. Foreign Direct Investment in China's Real Estate Market. \textit{Habitat International}, 43, 231-239.
+
+  \bibitem[Piazzesi et al.(2020)]{piazzesi_segmented_2020}
+  Piazzesi, M., M. Schneider, and J. Stroebel. 2020. Segmented Housing Search. \textit{American Economic Review}, 110(3), 720-759.
+
+  \bibitem[Qu et al.(2021)]{qu_identifying_2021}
+  Qu, W., Y. Huang, and G. Deng. 2021. Identifying the Critical Factors Behind the Second-Hand Housing Price Concession: Empirical Evidence from China. \textit{Habitat International}, 117, 102442.
+
+  \bibitem[Salz(2022)]{salz_intermediation_2022}
+  Salz, T. 2022. Intermediation and Competition in Search Markets: An Empirical Case Study. \textit{Journal of Political Economy}, 130(2), 310-345.
+
+  \bibitem[Williams(1998)]{williams_agency_1998}
+  Williams, J. T. 1998. Agency and Brokerage of Real Assets in Competitive Equilibrium. \textit{Review of Financial Studies}, 11(2), 239-280.
+
+  \bibitem[Wong et al.(2012)]{wong_liquidity_2012}
+  Wong, S. K., C. Y. Yiu, and K. W. Chau. 2012. Liquidity and Information Asymmetry in the Real Estate Market. \textit{The Journal of Real Estate Finance and Economics}, 45(1), 49-62.
+
+  \bibitem[Zhao(2015)]{zhao_rational_2015}
+  Zhao, B. 2015. Rational Housing Bubble. \textit{Economic Theory}, 60(1), 141-201.
+
+  \bibitem[Elvidge et al.(2021)]{elvidge_annual_2021}
+  Elvidge, C.
+D., M.
+Zhizhin, T.
+Ghosh, F.-C.
+Hsu, and J.
+Taneja.
+2021.
+Annual Time Series of Global VIIRS Nighttime Lights Derived from Monthly Averages: 2012 to 2019.
+\textit{Remote Sensing}, 13(5), 922.
+
+  \bibitem[Zhang et al.(2021)]{zhang_online_2021}
+  Zhang, X., Z.
+Lin, Y.
+Zhang, Y.
+Zheng, and J.
+Zhang.
+2021.
+Online Property Brokerage Platform and Prices of Second-Hand Houses: Evidence from Lianjia's Entry.
+\textit{Electronic Commerce Research and Applications}, 50, 101104.
+
+  \bibitem[Wei and Zhang(2011)]{wei_competitive_2011}
+  Wei, S.-J., and X. Zhang. 2011. The Competitive Saving Motive: Evidence from Rising Sex Ratios and Savings Rates in China. \textit{Journal of Political Economy}, 119(3), 511-564.
+
+  \bibitem[Zhao et al.(2017)]{zhao_forecasting_2017}
+  Zhao, N., Y.
+Liu, G.
+Cao, E.
+L.
+Samson, and J.
+Zhang.
+2017.
+Forecasting China’s GDP at the Pixel Level Using Nighttime Lights Time Series and Population Images.
+\textit{GIScience \& Remote Sensing}, 54(3), 407-425.
+
+  \bibitem[Akerlof(1970)]{Akerlof_1970}
+  Akerlof, G. A. 1970. The Market for "Lemons": Quality Uncertainty and the Market Mechanism. \textit{The Quarterly Journal of Economics}, 84(3), 488-500.
+
+  \bibitem[Yang et al.(2021)]{YANG2021102359}
+  Yang, L., K. W. Chau, and Y. Chen. 2021. Impacts of Information Asymmetry and Policy Shock on Rental and Vacancy Dynamics in Retail Property Markets. \textit{Habitat International}, 111, 102359.
+
+  \bibitem[Barwick and Pathak(2015)]{https://doi.org/10.1111/1756-2171.12082}
+  Barwick, P. J., and P. A. Pathak. 2015. The Costs of Free Entry: An Empirical Study of Real Estate Agents in Greater Boston. \textit{The RAND Journal of Economics}, 46(1), 103-145.
+
+  \bibitem[Barwick et al.(2017)]{10.1257/app.20160214}
+  Barwick, P. J., P. A. Pathak, and M. Wong. 2017. Conflicts of Interest and Steering in Residential Brokerage. \textit{American Economic Journal: Applied Economics}, 9(3), 191-222.
+
+  \bibitem[Levitt and Syverson(2008)]{d082a2db-5cce-33f2-87c4-9cb020cc6666}
+  Levitt, S.
+D., and C.
+Syverson.
+2008.
+Market Distortions When Agents Are Better Informed: The Value of Information in Real Estate Transactions.
+\textit{The Review of Economics and Statistics}, 90(4), 599-611.
+
+  \bibitem[Pope et al.(2015)]{POPE201589}
+  Pope, D. G., J. C. Pope, and J. R. Sydnor. 2015. Focal Points and Bargaining in Housing Markets. \textit{Games and Economic Behavior}, 93, 89-107.
+
+  \bibitem[Han and Strange(2015)]{HAN2015813}
+  Han, L., and W. C. Strange. 2015. The Microstructure of Housing Markets: Search, Bargaining, and Brokerage. In \textit{Handbook of Regional and Urban Economics}, Vol. 5, pp. 813-886. Elsevier.
+
+  \bibitem[Genesove and Han(2012)]{GENESOVE201231}
+  Genesove, D., and L. Han. 2012. Search and Matching in the Housing Market. \textit{Journal of Urban Economics}, 72(1), 31-45.
+
+  \bibitem[Han and Hong(2011)]{550a6ccf-cde2-3dd1-979f-1a8db2b8ceb9}
+  Han, L., and S.-H. Hong. 2011. Testing Cost Inefficiency Under Free Entry in the Real Estate Brokerage Industry. \textit{Journal of Business \& Economic Statistics}, 29(4), 564-578.
+
+  \bibitem[Van Nieuwerburgh and Veldkamp(2010)]{NIEUWERBURGH_information}
+  Van Nieuwerburgh, S., and L. Veldkamp. 2010. Information Acquisition and Under-Diversification. \textit{The Review of Economic Studies}, 77(2), 779-805.
+
+  \bibitem[Zhang et al.(2021)]{ZHANG2021101104}
+  Zhang, X., Z.
+Lin, Y.
+Zhang, Y.
+Zheng, and J.
+Zhang.
+2021.
+Online Property Brokerage Platform and Prices of Second-Hand Houses: Evidence from Lianjia’s Entry.
+\textit{Electronic Commerce Research and Applications}, 50, 101104.
+
+  \bibitem[Agarwal et al.(2019)]{AGARWAL2019715}
+  Agarwal, S., J. He, T. F. Sing, and C. Song. 2019. Do Real Estate Agents Have Information Advantages in Housing Markets? \textit{Journal of Financial Economics}, 134(3), 715-735.
+
+  \bibitem[Piazzesi et al.(2020)]{10.1257/aer.20141772}
+  Piazzesi, M., M. Schneider, and J. Stroebel. 2020. Segmented Housing Search. \textit{American Economic Review}, 110(3), 720-759.
+
+  \bibitem[Hong(2022)]{https://doi.org/10.1002/jae.2891}
+  Hong, S.-H. 2022. Real Estate Agents' Influence on Housing Search. \textit{Journal of Applied Econometrics}, 37(3), 563-582.
+
+  \bibitem[Van Donkelaar et al.(2021)]{doi:10.1021/acs.est.1c05309}
+  Van Donkelaar, A., M.
+S.
+Hammer, L.
+Bindle, M.
+Brauer, J.
+R.
+Brook, M.
+J.
+Garay, N.
+C.
+Hsu, O.
+V.
+Kalashnikova, R.
+A.
+Kahn, C.
+Lee, R.
+C.
+Levy, A.
+Lyapustin, A.
+M.
+Sayer, and R.
+V.
+Martin.
+2021.
+Monthly Global Estimates of Fine Particulate Matter and Their Uncertainty.
+\textit{Environmental Science \& Technology}, 55(22), 15287-15300.
+
+  \bibitem[Zumpano et al.(2003)]{ZUMPANO2003134}
+  Zumpano, L. V., K. H. Johnson, and R. I. Anderson. 2003. Internet Use and Real Estate Brokerage Market Intermediation. \textit{Journal of Housing Economics}, 12(2), 134-150.
+
+  \bibitem[McCrary(2008)]{MCCRARY2008698}
+  McCrary, J. 2008. Manipulation of the Running Variable in the Regression Discontinuity Design: A Density Test. \textit{Journal of Econometrics}, 142(2), 698-714.
+
+  \bibitem[Sirmans et al.(1991)]{SIRMANS1991207}
+  Sirmans, C. F., G. K. Turnbull, and J. D. Benjamin. 1991. The Markets for Housing and Real Estate Broker Services. \textit{Journal of Housing Economics}, 1(3), 207-217.
+
+  \bibitem[Armstrong(2006)]{Armstrong2006}
+  Armstrong, M. 2006. Competition in Two-Sided Markets. \textit{The RAND Journal of Economics}, 37(3), 668-691.
+
+  \bibitem[Beck et al.(2022)]{doi:10.1080/10527001.2021.2016340}
+  Beck, J., F. Scott, and A. Yelowitz. 2022. The Impact of Real Estate Agent Specialization and Activity Level on Market Outcomes. \textit{Journal of Housing Research}, 31(2), 163-180.
+
+  \bibitem[Jud et al.(1996)]{doi:10.1080/10835547.1996.12090852}
+  Jud, D., T. Seaks, and D. Winkler. 1996. Time on the Market: The Impact of Residential Brokerage. \textit{Journal of Real Estate Research}, 12(2), 447-458.
+
+  \bibitem[Rochet and Tirole(2003)]{10.1162/154247603322493212}
+  Rochet, J.-C., and J. Tirole. 2003. Platform Competition in Two-Sided Markets. \textit{Journal of the European Economic Association}, 1(4), 990-1029.
+
+  \bibitem[Li and Qi(2022)]{10.1093/cje/beac054}
+  Li, Z., and H. Qi. 2022. Platform Power: Monopolisation and Financialisation in the Era of Big Tech. \textit{Cambridge Journal of Economics}, 46(6), 1289-1314.
+
+  \bibitem[Langley and Leyshon(2017)]{Langley_Leyshon_2017}
+  Langley, P., and A. Leyshon. 2017. Platform Capitalism: The Intermediation and Capitalisation of Digital Economic Circulation. \textit{Finance and Society}, 3(1), 11-31.
+
+  \bibitem[Allen et al.(2023)]{RePEc:kap:jrefec:v:67:y:2023:i:3:d:10.1007_s11146-021-09858-w}
+  Allen, M. T., J. D. Benefield, and R. C. Rutherford. 2023. Co-Listing Strategies: Better Transaction Outcomes? \textit{The Journal of Real Estate Finance and Economics}, 67(3), 517-544.
+
+  \bibitem[Varian(2014)]{10.1257/jep.28.2.3}
+  Varian, H. R. 2014. Big Data: New Tricks for Econometrics. \textit{Journal of Economic Perspectives}, 28(2), 3-28.
+
+  \bibitem[Zhu and Iansiti(2019)]{WOS:000454186600016}
+  Zhu, F., and M. Iansiti. 2019. Why Some Platforms Thrive and Others Don't. \textit{Harvard Business Review}, 97(1), 118-125.
+
+  \end{thebibliography}
 \end{singlespace}

### 2024-06-28 analysis/quantile-regression.R
modified:   analysis/quantile-regression.R 	modified:   network_estimation/network_estimate.ipynb 	modified:   network_estimation/network_estimation.ipynb

@@ -1,10 +1,19 @@
-library(quantreg)
 library(lfe)
 library(haven)
+library(dplyr)
+library(quantreg)
 getwd()
 
 setwd('E:/umich/RealEstateBrokerage-main')
-data <- read_dta("for-analysis.dta")
+data <- read_dta("individual.dta")
+
+
+data <- data %>%
+  mutate(across(matches("^yearx"), ~ . * influence, .names = "influence_{col}"))
+
+# now we are working on the CIC estimation
+pre_policy_data <- data[data$year %in% c(2016, 2017), ]
+post_policy_data <- data[data$year %in% c(2018, 2019, 2020, 2021, 2022), ]
 
 # define a set of control variables
 
@@ -12,10 +21,26 @@ hedonic_control <- c("jiadian", "kind", "hotel", "shop_mall", "museum", "old", "
 transaction_control <- c("area", "bedroom", "toilet", "house_age", "floor_level", "green_ratio", "total_building", "total_floor_number", "living_room", "elevator_ratio", "kitchen", "floor_ratio", "total_resident")
 region_control <- c("pm25", "pop", "light")
 brokerage_control <- c("non_online_effect", "ln_nego_changes", "ln_negotiation_period")
-lag_hedonic_control <- paste0(hedonic_control, "_hedonic_lag")
+control_variables <- c(brokerage_control, hedonic_control, transaction_control, region_control)
+
+quantiles <- c(0.1, 0.25, 0.5, 0.75, 0.9)
+coefficients <- list()
+standard_errors <- list()
+
+# Loop over each quantile
+for (q in quantiles) {
+    # Run quantile regression
+    model <- rq(price_concession ~ policy + influence + policy_influence + control_variables, 
+                data = data, tau = q)
+    
+    # Store the coefficients and standard errors
+    coefficients[[as.character(q)]] <- coef(summary(model))["policy_influence", "Value"]
+    standard_errors[[as.character(q)]] <- coef(summary(model))["policy_influence", "Std. Error"]
+}
+
 
 dependent_variable <- c("yearx2_density", "yearx3_density", "yearx4_density", "yearx5_density", "yearx6_density", "yearx7_density", "broker_410", "ln_end_price", "ln_watch_people", "ln_watch_time")
-control_variables <- c(brokerage_control, lag_hedonic_control, transaction_control, region_control)
+
 
 all_vars <- c("ln_income", dependent_variable, control_variables, "year", "bs_code", "id")
[…]

### 2024-06-28 manuscript/main.tex
modified:   analysis/quantile-regression.R 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	modified:   network_estimation/network_estimate.ipynb 	modified:   network_estimation/network_estimation.ipynb 	new file:   network_estimation/network_structure.ipynb

@@
 
+We decided to use the so called Change-in-Change (CIC) estimator proposed by \citep{https://doi.org/10.1111/j.1468-0262.2006.00668.x}. The CIC model does not assume that the
+
 \section{Conclusion and Discussion} \label{sec:conclusion}
@@
 
+  \bibitem[Athey and Imbens(2006)]{https://doi.org/10.1111/j.1468-0262.2006.00668.x}
+  Athey, S., and G.
+W.
+Imbens.
+2006.
+Identification and Inference in Nonlinear Difference-in-Differences Models.
+\textit{Econometrica}, 74(2), 431-497.% Available at \url{https://onlinelibrary.wiley.com/doi/abs/10.1111/j.1468-0262.2006.00668.x}.
+
   \end{thebibliography}

### 2024-06-28 analysis/quantile-regression.R

@@ -1,3 +1,4 @@
+library(qte)
 library(lfe)
 library(haven)
 library(dplyr)
@@ -5,11 +6,18 @@ library(quantreg)
 getwd()
 
 setwd('E:/umich/RealEstateBrokerage-main')
-data <- read_dta("individual.dta")
+data <- read_dta("template.dta")
 
+# so the main idea is to generate the treatment effect where the treated group 
+# happens when the
 
-data <- data %>%
-  mutate(across(matches("^yearx"), ~ . * influence, .names = "influence_{col}"))
+# our result is not influenced by the COVID because the network effect is consistent in terms of the 
+# because the stores are faced with the short term shock and the operation should be long term that they can not directly close or open new stores
+# so the network effect is consistent in terms of the COVID-19
+# Besides, we can also estimate the model trying to see the parallel trend is satisfied or not in this model
+
+# data <- data %>%
+#   mutate(across(matches("^yearx"), ~ . * influence, .names = "influence_{col}"))
 
 # now we are working on the CIC estimation
 pre_policy_data <- data[data$year %in% c(2016, 2017), ]
@@ -23,36 +31,33 @@ region_control <- c("pm25", "pop", "light")
 brokerage_control <- c("non_online_effect", "ln_nego_changes", "ln_negotiation_period")
 control_variables <- c(brokerage_control, hedonic_control, transaction_control, region_control)
 
-quantiles <- c(0.1, 0.25, 0.5, 0.75, 0.9)
-coefficients <- list()
-standard_errors <- list()
-
-# Loop over each quantile
-for (q in quantiles) {
-    # Run quantile regression
-    model <- rq(price_concession ~ policy + influence + policy_influence + control_variables, 
-                data = data, tau = q)
-    
-    # Store the coefficients and standard errors
-    coefficients[[as.character(q)]] <- coef(summary(model))["policy_influence", "Value"]
-    standard_errors[[as.character(q)]] <- coef(summary(model))["policy_influence", "Std. Error"]
-}
+quantiles <- c(0.05, 0.95, 0.05)
 
 
 dependent_variable <- c("yearx2_density", "yearx3_density", "yearx4_density", "yearx5_density", "yearx6_density", "yearx7_density", "broker_410", "ln_end_price", "ln_watch_people", "ln_watch_time")
 
-
-all_vars <- c("ln_income", dependent_variable, control_variables, "year", "bs_code", "id")
[…]

### 2024-06-30 manuscript/main.tex
update the correct results

@@
 
-\section{Collaborative Spillover Effect} \label{sec:network_effect}
+\section{Extension: Collaborative Spillover Effect} \label{sec:network_effect}
 
@@
 We decided to use the so called Change-in-Change (CIC) estimator proposed by \citep{https://doi.org/10.1111/j.1468-0262.2006.00668.x}. The CIC model does not assume that the
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.7\textwidth]{../figures/network_formation_effect.pdf}
+  \caption{The structure of network formation effect}
+  \label{fig:network_formation_effect_graph}
+
+  Note: The red nodes represent the distribution of Lianjia's offline stores, while the blue nodes indicate the distribution of neighborhoods within the market.
+Dotted edges illustrate the connections between neighborhoods and stores, whereas solid lines depict the interactions between offline stores.
+The size of the red nodes corresponds to the local clustering effect, with larger nodes indicating a more significant local clustering phenomenon.
+\end{figure}
+
+The table shown in the Table \ref{tab:network_clustering_effect} shows the
 

### 2024-07-01 analysis/quantile-regression.R
modified:   analysis/quantile-regression.R

@@ -1,12 +1,58 @@
-library(qte)
+# library(qte) # this is the implementation of CIC model and we do not need it right now
 library(lfe)
 library(haven)
 library(dplyr)
 library(quantreg)
+library(fixest)
+set.seed(130)
 getwd()
 
-setwd('E:/umich/RealEstateBrokerage-main')
+setwd('/home/xuyuan/Desktop/2024 summer/real estate paper/oritignal cleaning/RealEstateBrokerage')
 data <- read_dta("template.dta")
+
+# now here we consider the CIC model where the dependent variable is the influence
+# and the treatment effect is a set of variables indicating whether the online 
+# consolidation spread the influence effect. I have already know that the treatment 
+# effect can make the influence effect heterogenous because treatment effect can 
+# have different heterogenous effect on various level of the influence, 
+# and therefore, we cannot use traditional DID, then we have to use CIC and the 
+# expected result should be a quantiled treatment effect on various level of the 
+# influence. Give me the code in R.
+
+pre_policy_data <- data[data$year %in% c(2016, 2017), ]
+post_policy_data <- data[data$year %in% c(2018, 2019, 2020, 2021, 2022), ]
+
+hedonic_control <- c("jiadian", "kind", "hotel", "shop_mall", "museum", "old", "ktv", "mid", "prim", "west_food", "super", "sub", "park")
+transaction_control <- c("area", "bedroom", "toilet", "house_age", "floor_level", "green_ratio", "total_building", "total_floor_number", "living_room", "elevator_ratio", "kitchen", "floor_ratio", "total_resident")
+region_control <- c("pm25", "pop", "light")
+brokerage_control <- c("non_online_effect", "ln_nego_changes", "ln_negotiation_period")
+other_main_variables <- c("broker_410", "ln_end_price", "ln_watch_people", "ln_watch_time")
+control_variables <- c(other_main_variables, brokerage_control, hedonic_control, transaction_control, region_control)
+control_formula <- paste(control_variables, collapse = " + ")
+dependent_variable <- c("pre1_treatment", "treatment", "post1_treatment", "post2_treatment", "post3_treatment")
+quantiles <- c(0.05, 0.95, 0.05)
+
+data <- data %>%
+  mutate(year_factor = as.factor(year),
+         bs_code_year = interaction(bs_code, year, drop = TRUE),
[…]

### 2024-07-01 archive/quantile-regression.R
update the result

@@ -1,4 +1,11 @@
 # library(qte) # this is the implementation of CIC model and we do not need it right now
+
+# if you are using the caen version's R
+# first install R-tools from https://cran.rstudio.com/bin/windows/Rtools/history.html
+# this CAEN version is 4.0.2 and install it to the zxuyuan
+# install.packages("rlang")
+# install.packages("lifecycle")
+# and then install other packages
 library(lfe)
 library(haven)
 library(dplyr)
@@ -7,7 +14,8 @@ library(fixest)
 set.seed(130)
 getwd()
 
-setwd('/home/xuyuan/Desktop/2024 summer/real estate paper/oritignal cleaning/RealEstateBrokerage')
+setwd('C:/Users/zxuyuan/Downloads')
+# setwd('/home/xuyuan/Desktop/2024 summer/real estate paper/oritignal cleaning/RealEstateBrokerage')
 data <- read_dta("template.dta")
 
 # now here we consider the CIC model where the dependent variable is the influence

### 2024-07-02 analysis/RD design analysis.Rmd
modified:   analysis/RD design analysis.Rmd 	deleted:    analysis/RD_Plot_1st_Order.pdf 	deleted:    analysis/RD_Plot_2nd_Order.pdf 	deleted:    analysis/RD_Plot_3rd_Order.pdf 	modified:   analysis/final_analysis.do 	modified:   analysis/individual.do 	modified:   figures/RD_Plot_1st_Order.pdf 	modified:   figures/RD_Plot_2nd_Order.pdf 	modified:   figures/RD_Plot_3rd_Order.pdf 	new file:   figures/did_1.pdf 	deleted:    figures/did_1.tif 	new file:   figures/did_2.pdf 	deleted:    figures/did_2.tif 	new file:   figures/did_3.pdf 	deleted:    figures/did_3.tif 	new file:   figures/did_4.pdf 	d

@@
 # these are the packages that we need to import
+library(dplyr)
 library(haven)
@@
 ```{r}
+ci_level = 95
 h = 0.066
@@
 running_var = panel_data$nearest_store_distances
-
+running_var <- as.numeric(running_var)
 filtered_data <- panel_data[abs(running_var - cutoff) <= h, ]
@@
        x.label = "Nearest distance to Lianjia's stores",
-       y.label = "Log of income in the community")
+       y.label = "Log of income in the community", col.dots = "blue")
 dev.off() # Close the PDF device
@@
        c = cutoff, nbins = 40, p = 2,
-       title = "RD-plot 2nd order polynomial",
+       title = "RD-plot 1st order polynomial",
        x.label = "Nearest distance to Lianjia's stores",
-       y.label = "Log of income in the community")
+       y.label = "Log of income in the community", col.dots = "blue")
 dev.off() # Close the PDF device

### 2024-07-02 manuscript/main.tex
modified:   analysis/RD design analysis.Rmd 	deleted:    analysis/RD_Plot_1st_Order.pdf 	deleted:    analysis/RD_Plot_2nd_Order.pdf 	deleted:    analysis/RD_Plot_3rd_Order.pdf 	modified:   analysis/final_analysis.do 	modified:   analysis/individual.do 	modified:   figures/RD_Plot_1st_Order.pdf 	modified:   figures/RD_Plot_2nd_Order.pdf 	modified:   figures/RD_Plot_3rd_Order.pdf 	new file:   figures/did_1.pdf 	deleted:    figures/did_1.tif 	new file:   figures/did_2.pdf 	deleted:    figures/did_2.tif 	new file:   figures/did_3.pdf 	deleted:    figures/did_3.tif 	new file:   figures/did_4.pdf 	d

@@
       \label{tab:entry_effect_robustness}
-      \input{../result_tables/entry_effect_hetero.tex}
+      \input{../result_tables/entry_effect_hetero_1.tex}
+
+    Note: we omit all the control variables in the regression model, and detailed descriptions can be seen from Table \ref{tab:statistical_district} and Table \ref{tab:statistical_individual}.
+    \end{scriptsize}
+  \end{center}
+\end{table}
+
+\begin{table}
+  \begin{center}
+    \begin{scriptsize}
+      \caption{Robustness Check of Entry Effect (Continued)}
+      \label{tab:entry_effect_robustness}
+      \input{../result_tables/entry_effect_hetero_2.tex}
 
@@
     \subfloat[Effect to price concession]{\includegraphics[width=0.5\textwidth]{../figures/did_4.pdf}\label{fig:did_price_concession}}
-    \caption{Estimation of ACN Platformization Effect}
+    \caption{Estimation of Platform Consolidation Effect}
     \label{fig:dynamic_effect}
@@
       \label{tab:heter_platform_did}
-      \input{../result_tables/heter_platform_did.tex}
+      \input{../result_tables/heter_platform_did_1.tex}
+
+    Note: we omit all the control variables in the regression model, and detailed descriptions can be seen from Table \ref{tab:statistical_district} and Table \ref{tab:statistical_individual}.
+    \end{scriptsize}
+  \end{center}
+\end{table}
+
+\begin{table}
+  \begin{center}
+    \begin{scriptsize}
+      \caption{Robustness Check of Online Consolidation Effect (Continued)}
+      \label{tab:heter_platform_did}
+      \input{../result_tables/heter_platform_did_2.tex}
 
@@
 
-We decided to use the so called Change-in-Change (CIC) estimator proposed by \citep{https://doi.org/10.1111/j.1468-0262.2006.00668.x}. The CIC model does not assume that the
+We decided to use the so called quantile estimator proposed by \citep{https://doi.org/10.1111/j.1468-0262.2006.00668.x}. The CIC model does not assume that the
 
@@
 
+  \bibitem[Machado and Santos Silva(2019)]{machado_quantiles_2019}
+Machado, J. A. F., and J. M. C. Santos Silva. 2019. Quantiles via Moments. \textit{Journal of Econometrics}, 213(1), 145-173.
+
   \end{thebibliography}
@@
 
-\begin{table}[H]
-  \begin{center}
-    \begin{scriptsize}
-    \caption{Robustness Check By Market Maturity Index}
-    \label{tab:platform_consolidation_hetero_mature}
-    \input{../result_tables/robust_mature.tex}
-
-    \end{scriptsize}
-  \end{center}
-\end{table}
+% \begin{table}[H]
+%   \begin{center}
+%     \begin{scriptsize}
+%     \caption{Robustness Check By Market Maturity Index}
+%     \label{tab:platform_consolidation_hetero_mature}
+%     \input{../result_tables/robust_mature.tex}
+
+%     \end{scriptsize}
+%   \end{center}
+% \end{table}
 

### 2024-07-02 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	modified:   result_tables/entry_effect_hetero_1.tex 	modified:   result_tables/entry_effect_hetero_2.tex 	modified:   result_tables/formulate_the_tables.ipynb 	modified:   result_tables/heter_platform_did_1.tex 	modified:   result_tables/heter_platform_did_2.tex 	modified:   result_tables/quantile_network_formation.tex

@@
 
-The second hand housing transaction data was collected form \href{https://www.ke.com/city/}{beke.com} for ten cities ranging from 2016 to 2022.
-Initially, we filtered out transaction records exhibiting unusually high prices, identifying them as outliers that could skew the analysis.
+The second hand housing transaction data was collected form \href{https://www.ke.com/city/}{beke.com} for ten cities ranging from 2016 to 2022.\footnote{Due to government policy, Lianjia was unable to disclose transaction prices in Beijing, Shenzhen, and Wuhan for the years 2021 and 2022, as well as in Chengdu for 2021.
+Consequently, we have excluded this period of data for these cities from our analysis.} Initially, we filtered out transaction records exhibiting unusually high prices, identifying them as outliers that could skew the analysis.
 We then removed records with missing values to maintain the integrity of our dataset.
@@
 \begin{equation}
-    Y_{it} = \beta_0 +  pre_2 + entry + \sum_{i=1}^3 post_i + \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}.   \label{eq:entry_effect}
+    Y_{it} = \beta_0 +  pre_2 + entry + \sum_{i=1}^3 post_i + \bf{\alpha} \bf{X}_{it} + \tau_{t} + \mu_i + \epsilon_{it}.   \label{eq:entry_effect}
 \end{equation}
@@
 However, this effect decreases to 4.7\% in the subsequent period ($post_1$) and continues to diminish in the following periods ($post_2$ and $post_3$), indicating a gradual decline in Lianjia's performance after the initial entry period.
-Similarly, the number of house tours exhibits a significant 2.3\% increase during the entry period, followed by a 3.\% increase in the first post-entry period.
+Similarly, the number of house tours exhibits a significant 2.3\% increase during the entry period, followed by a 3.1\% increase in the first post-entry period.
 Nonetheless, this effect lessens in $post_2$, though it remains significant in $post_3$.
@@
 To verify the robustness of the entry effect, we classified the sample into low and high Herfindahl-Hirschman Index (HHI) groups.
-The results, presented in Table \ref{tab:entry_effect_robustness}, indicate that the income effect for Lianjia remains consistent across both groups.
-Specifically, income increases by 9.2\% during the entry period, with the effect decreasing to 5.1\% in the subsequent period for the higher HHI group, and increasing by 9.6\% during the entry period and decreasing to 4.7\% for the lower HHI group.
+The results, presented in Table \ref{tab:entry_effect_robustness_1}, indicate that the income effect for Lianjia remains consistent across both groups.
+Specifically, income increases by 7.9\% during the entry period, with the effect decreasing to 5.0\% in the subsequent period for the lower HHI group, which demonstrates the entry can create a very large impact on the compettive market.
+Moreover, the income increases by 6.8\% and 7.8\% during the entry period and decreases to insignificant after the entry period in the moderate and high concentration market.
+This demonstrates that Lianjia's entry can only make companies profitable in less competitive markets, and it can enhance profitability in more competitive markets.
 However, a significant difference emerges in the number of house tours.
-The entry of Lianjia increases the number of house tours by 2.9\% for the higher HHI group and by 4.4\% for the lower HHI group.
-In the subsequent period, the effect diminishes for the lower HHI group, indicating that the entry of new competitors mitigates Lianjia's entry effect.
-Conversely, the entry effect remains significant for the higher HHI group.
+The entry of Lianjia increases the number of house tours by 5.4\% in the second year and 5.9\% in the third year for the low competitive group.
+The entry's effect is also significant, with a 3.9\% increase in the number of house tours in the second year for the high concentration market.
+However, this effect diminishes for the moderately competitive group.
+The result indicates that the results indicate that when facing other competitors in the market, Lianjia is more likely to make greater efforts to attract more sellers.
 This analysis underscores the varying impacts of market concentration on Lianjia's market performance post-entry.
 
-Furthermore, in columns 5 and 6, the entry of Lianjia's offline stores significantly shortens the transaction period for the higher HHI group.
-This suggests that offline stores enhance market efficiency by better matching buyers and sellers.
-Conversely, this effect is not significant in the lower HHI group, indicating that the benefits of offline stores diminish in more competitive markets.
-Regarding price concessions, the entry of Lianjia's offline stores does not have a significant effect in the lower HHI group initially.
-However, by the $post_3$ period, the effect becomes significant and positive.
-This delayed impact may be attributed to the offline stores gradually improving market transparency and information dissemination, which eventually leads to better price concessions.
+Furthermore, in Table \ref{tab:entry_effect_robustness_2}, The entry of Lianjia's offline stores significantly shortens the transaction period for the moderate HHI group by about 5\%.
+Conversely, this effect is not significant in the lower HHI group and higher concentration group.
+This pattern suggests that when the market is highly competitive, Lianjia is not able to shorten the transaction period and in highly concentrated markets, Lianjia is also unable to use its information advantage to shorten the transaction period.
+Regarding price concessions, the entry of Lianjia's offline stores does not have a significant effect in the moderate HHI group initially.
+However, the entry of offline stores have no influence on other groups.
+Overall, the results suggest that the entry of offline stores has a very limited influence on consumers' welfare but can help the brokerage earn more profit.
+Additionally, the entry of Lianjia's offline stores can help the brokerage attract more sellers and, consequently, find more buyers in the market, thereby increasing the brokerage's informational advantage.
+In the Appendix we also conducted the robustness check by classifying the group by matured market and less matured market.
+
+% This delayed impact may be attributed to the offline stores gradually improving market transparency and information dissemination, which eventually leads to better price concessions.
 For the higher HHI group, the entry of Lianjia's offline stores consistently has a significant effect on price concessions.
@@
 In the Appendix we also conducted the robustness check by classifying the group by matured market and less matured market.
-[ THERE IS ALSO A GRAPH OF PARALLEL TREND NEED TO BE ADDED HERE.
-]
 
@@
       \caption{Robustness Check of Entry Effect}
-      \label{tab:entry_effect_robustness}
+      \label{tab:entry_effect_robustness_1}
       \input{../result_tables/entry_effect_hetero_1.tex}
@@
       \caption{Robustness Check of Entry Effect (Continued)}
-      \label{tab:entry_effect_robustness}
+      \label{tab:entry_effect_robustness_2}
       \input{../result_tables/entry_effect_hetero_2.tex}
@@
 
-We decided to use the so called quantile estimator proposed by \citep{https://doi.org/10.1111/j.1468-0262.2006.00668.x}. The CIC model does not assume that the
+We decided to use the so called quantile estimator described in model  proposed by \citep{machado_quantiles_2019}.
+
+\begin{equation}
+  \begin{aligned}
+    Q_y(\xi \mid X) & = \beta_0 + \beta_1(\xi) \text{pre\_treatment}_{it} + \beta_2(\xi) \text{treatment} + \sum_{i=3}^5 \beta_i(\xi) \text{post\_treatment}_{it} \\
+    & + \beta(\xi) \bf{X}_{it} + \mu_i + \tau_t + \varepsilon_{it}
+  \end{aligned}
+\end{equation}
+
+\ref{tab:quantile_estimate_network} shows the quantile estimation of the . We can see that the
 
@@
 
-The table shown in the Table \ref{tab:network_clustering_effect} shows the
+\begin{table}
+  \begin{center}
+    \begin{scriptsize}
+      \caption{Estimated Network Spillover Effect}
+      \label{tab:estiamted_spillover_effect}
+      \input{../result_tables/clustering_indices.tex}
+
+      Note: The indices used are the Average and Global Clustering Coefficients.
+$*$ denotes a low network effect, which ranges from 0.3 to 0.5.
+$**$ indicates a moderate network effect, ranging from 0.5 to 0.75.
+$***$ signifies a large network effect, ranging from 0.75 to 1.
+    \end{scriptsize}
+  \end{center}
+\end{table}
+
+\begin{table}
+  \begin{center}
+    \begin{scriptsize}
+      \caption{Quantile Estimation of the Network Spillover Effect}
+      \label{tab:quantile_estimate_network}
+      \input{../result_tables/quantile_network_formation.tex}
+
+    Note: we omit all the control variables in the regression model, and detailed descriptions can be seen from Table \ref{tab:statistical_district} and Table \ref{tab:statistical_individual}.
+    \end{scriptsize}
+  \end{center}
+\end{table}
 

### 2024-07-02 manuscript/main.tex
modified:   manuscript/main.tex

@@
 \begin{equation}
-    Y_{it} = \beta_0 +  pre_2 + entry + \sum_{i=1}^3 post_i + \bf{\alpha} \bf{X}_{it} + \tau_{t} + \mu_i + \epsilon_{it}.   \label{eq:entry_effect}
+    Y_{it} = \beta_0 +  pre_2 + entry + \sum_{i=1}^3 post_i + \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}.   \label{eq:entry_effect}
 \end{equation}
@@
 In addition to this, Lianjia also opened up the form of franchises and gradually started platform integration.
-To empirically measure the effect of platformization to the offline stores' operations, we first counted the number of all non-Lianjia stores on the Lianjia's Beke platform within a radius of 410 meters, which allowed us to generate a dummy variable $Treatment_{it}$ to represent whether or not there are any other affiliate stores within the platform in this neighborhood.
-To dynamically capture the varying effects, we generate $Treatmetn_{it} * year$ by producting the year dummy variable with the $Treatment_{it}$ and include them in our regression model.
-Since the ACN network was officially established at the end of 2018, we can generate a dummy variable equal to 1 if the year is greater than 2018.
+To empirically measure the effect of platformization on offline store operations, we first counted the number of all non-Lianjia stores on Lianjia's Beke platform within a radius of 410 meters.
+This allowed us to generate a dummy variable, $\text{Treatment}_{it}$, which equals one if the ratio $\frac{\text{Lianjia}}{\text{Beke}} < 0.8$ in this area and the year is 2018 or later.
+This ratio is selected because if Lianjia accounts for more than 80\% of the Beke's offline stores, the strategy's effect is negligible and only effective for Lianjia.
+To dynamically capture the varying effects, we generate a set of dummy variable $\text{post\_j\_treatment}_{it}$, where $j \in \{1, 2, 3\}$ and $\text{pre\_treatment}_{it}$ and include them in our regression model.
 We then consider the following regression model:
@@
 \begin{equation}
-    Y_{it}  = \beta_0 + \sum_{i=1}^5 Treatment_{it} * year + \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}. \label{eq:acn_assessment}
+  \begin{aligned}
+    Y_{it} & = \beta_0 + \beta_1 \text{prev\_treatment}_{it} + \beta_2 \text{\treatment}_{it} + \sum_{j=3}^5 \beta_{i} \text{post\_j\_treatment_{it}}+ \\
+           & \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}. \label{eq:acn_assessment}
+  \end{aligned}
 \end{equation}
 
-By focusing on 2017 as the baseline, we can empirically estimate the outcomes with greater precision and reliability, ensuring that our analysis accurately reflects the impact of Lianjia's strategy without the confounding effects of prior periods.
-Other settings are consistent with previous table \ref{tab:Dynamic} and the result is reported in Figure \ref{fig:dynamic_effect}.
+where our key independent variables are described above. Other settings are consistent with previous table \ref{tab:Dynamic} and the result is reported in Figure \ref{fig:dynamic_effect}.
 
@@
 
-The empirical findings indicate that during the first year of consolidation, Lianjia's transaction revenue did not show a statistically significant difference from zero.
-However, from 2019 to 2021, the transaction revenue demonstrated a significant positive increase, ranging from 4.9\% to 2.6\%.
-Additionally, the consolidation of the platform had a significantly positive impact on the number of house tours, which increased by 3.9\% to 6.4\% from 2018 to 2022, with this trend continuing upward throughout the sample period.
-Furthermore, when comparing the effect of platform consolidation with the entry effect of offline stores, the data clearly show that the platformization effect is substantially more pronounced.
-This suggests that the platformization strategy is markedly more effective than the offline store entry strategy in generating revenue and attracting buyers in the market.
+The empirical findings indicate that in the first year of the consolidation strategy, Lianjia's transaction revenue did not show a statistically significant difference.
+However, after the first year, the transaction revenue demonstrated a significant positive increase, ranging from 3\% to 6\%.
+Additionally, the platform consolidation had a significantly positive impact on the number of house tours, with effects following the same trend as the transaction revenue.
+Furthermore, when comparing the effect of platform consolidation with the entry effect of offline stores, the result indicates that the effect is substantially more pronounced and more continuous.
 These results underscore the superior efficacy of platform consolidation in enhancing market performance and provide compelling evidence for the strategic advantage of platformization over traditional offline expansion.
@@
 However, in terms of the transaction period, the platformization strategy does not exhibit a significant effect, indicating that platformization does not assist brokerages in facilitating better matching and negotiation between sellers and buyers.
-A similar pattern is observed in price concessions, suggesting that the platformization strategy does not contribute to reducing price concessions.
+Moreover, in terms of the platform's consolidation effect on price concessions, we find that the effect is significant after the first period, with a 4.2\% increase in the first year after the treatment and a 7.1\% increase in the second year.
+However, the effect becomes insignificant after the third year.
+Overall, the results show that comparing with the offline store's entry effect, the platform's consolidation strategy can have more pronounced influence not only on effectiveness on trasaction but also on the overall revenue.
+
+revise the paragraph to make it more economics and academic
+( this is today's work )
+
 While the platformization strategy is less effective in influencing individuals' decision-making processes compared to offline store entry, it proves more effective in increasing revenue and the number of house tours.

### 2024-07-02 manuscript/main.tex
modified:   analysis/final_analysis.do 	modified:   analysis/individual.do 	new file:   did_1.pdf 	new file:   did_2.pdf 	new file:   did_3.pdf 	new file:   did_4.pdf 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	modified:   result_tables/difference_in_difference.tex 	modified:   result_tables/dynamic.tex 	modified:   result_tables/entry_effect.tex 	modified:   re

@@
 Utilizing micro-level transaction data, we construct our research sample by aggregating information at the neighborhood level.
-We employ a regression discontinuity (RD) design to identify the optimal influential radius of offline stores on neighborhood transactions, finding that this radius corresponds to a brokerage's five-minute walk service distance.
+We employ a regression discontinuity (RD) design to identify the optimal influential radius of offline stores on neighborhood transactions, finding that this radius corresponds to a brokerage's five-minute walk service distance, which is also documented in similar fields \citep{AZMI2012406}.
 Subsequently, we apply a difference-in-difference (DID) estimation method to evaluate the exogenous impact of Lianjia's market entry on local segments.
@@
 Additionally, we calculated the annual number of house transactions to capture Lianjia's transaction activity within each neighborhood.
+We also calcualted the revenue of each neighborhood for each year by the formula: $\text{annual transaction number} \times \text{average transaction price} \times \text{brokerage fee}$ where $\text{brokerage fee}$ is 2.7\%.
 This data structure enables a comprehensive analysis of the impact of offline stores on housing transactions across both individual and neighborhood dimensions.
@@
 Given that stores are predominantly located within commercial districts, which typically encompass several streets no more than two kilometers in diameter, it is assumed that a requisite number of stores within each district is essential to sustain revenue generation in that community.
-In addition, Lianjia adopts a 5-minute walking distance (approximately 400 meters) radius policy, which means that no matter how far away customers live, they should be accessible within a 5-minute walk to the nearest Lianjia store.
+In addition, Lianjia adopts a pedestrian shed strategy, also known as a 5-minute walking distance (approximately 400 meters) strategy, which means that customers should be accessible within a 5-minute walk to the nearest Lianjia store to reduce the .
 Building on this premise, the study further investigates the existence of an optimal influence radius within shopping districts, defined as the distance radius within which the presence of a Lianjia optimally increases transaction revenues.
@@
 Furthermore, we carry out the density test by \citep{MCCRARY2008698}.
-The result shows that the p-value is greater than 0.1 (p value equals 0.101), which suggests the result is not due to manipulation of polygons.
+The result shows that the p-value is greater than 0.1, which suggests the result is not due to manipulation of polygons.
 Finally, we carry out placebo tests which are reported in Appendix, which shows that our result is robust.
@@
 After constructing our optimal radius, we recalcualte the number of lianjia and other brokerages' stores within this radius.
-To check the robustness of the data, we divide our data to those with lianjia and those without lianjia and to check whether lianjia's offline stores have influential effect on the transaction effect in the community.
-We can see that for income, house tour number and the are all significantly different in those communities with or without lianjia.
+To check the robustness of the data, we divide our data to those with lianjia and those without lianjia and to check whether lianjia's offline stores have influential effect on the transaction effect in the neighborhoods.
+We can see that for transaction numbers, income, number of house tours and price concession are all significantly different in those neighborhoods with or without lianjia.
 In addition, we find that the other brokerages also have the same tendency that they typically open stores with the same strategy as Lianjia, which suggests that Lianjia does not have the market power to exclude competent companies from entering the market, and it also suggests that the market is not monopolized by Lianjia.
@@
 
-In our analysis, we focus on several dependent variables: \emph{the natural logarithm of lianjia's income}, \emph{the natural logarithm of home tours}, \emph{the natural logarithm of transaction period} and \emph{the price concession}.
+In our analysis, we focus on several dependent variables: \emph{the natural logarithm of lianjia's transaction number}, \emph{the natural logarithm of home tours}, \emph{the natural logarithm of transaction period} and \emph{the price concession}.
 To quantify Lianjia's impact, we begin by establishing a key stylized fact, which we develop a Density-Based Index (DBI) index to capture the Lianjia's offline stores' influential ratio.
@@
   \begin{aligned}
-    Y_{it} & = \beta_0 + \beta_1 \text{prev\_treatment}_{it} + \beta_2 \text{\treatment}_{it} + \sum_{j=3}^5 \beta_{i} \text{post\_j\_treatment_{it}}+ \\
+    Y_{it} & = \beta_0 + \beta_1 \text{prev\_treatment}_{it} + \beta_2 \text{treatment}_{it} + \sum_{j=3}^5 \beta_{i} \text{post\_j\_treatment}_{it} + \\
            & \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}. \label{eq:acn_assessment}
@@
 
+\bibitem[Azmi et al.(2012)]{AZMI2012406}
+Azmi, D.
+I., H.
+A.
+Karim, and M.
+Z.
+M.
+Amin.
+2012.
+Comparing the Walking Behaviour between Urban and Rural Residents.
+\textit{Procedia - Social and Behavioral Sciences}, 68(7), 406-416.
+% Available at \url{https://www.sciencedirect.com/science/article/pii/S1877042812057205}.
+
   \end{thebibliography}

### 2024-07-03 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

@@
 This study focuses on the housing markets in ten major cities in China, namely Beijing, Shanghai, Chongqing, Tianjin, Shenzhen, Guangzhou, Chengdu, Hangzhou, Wuhan and Nanjing.
-These cities are not only central to China's economic development, but also reflect the broader trends and characteristics of the country's real estate dynamics.
+These cities are not only pivotal to China's economic development, but also serve as exemplars of the broader trends and characteristics inherent in the China's real estate dynamics.
 Spanning from 2016 to 2022, the research period encapsulates a pivotal era in China's real estate sector.
@@
 We finally have a data with length 1,778,647 second-hand houses.\footnote{Due to government restrictions, four of these cities did not list the transaction price for each transaction during the study period.} After cleaning the data, we constructed two research samples: one at the individual transaction level and the other at the neighborhood level.
-The individual transaction sample contains detailed information on each transaction, including the transaction price, transaction date, price concessions, and the number of house tours.
+The individual transaction sample contains detailed information on each transaction, including the transaction price, transaction date, price concessions, and the transaction period.
 The neighborhood-level sample aggregates transaction data at the community level, encompassing variables such as the average transaction price and the average number of house tours.
 Additionally, we calculated the annual number of house transactions to capture Lianjia's transaction activity within each neighborhood.
-We also calcualted the revenue of each neighborhood for each year by the formula: $\text{annual transaction number} \times \text{average transaction price} \times \text{brokerage fee}$ where $\text{brokerage fee}$ is 2.7\%.
-This data structure enables a comprehensive analysis of the impact of offline stores on housing transactions across both individual and neighborhood dimensions.
+We also calcualted the revenue of each neighborhood for each year by the formula: $\text{annual transaction number} \times \text{average transaction price} \times \text{brokerage fee}$ where the brokerage fee is set at 2.7\% as the majority of houses in our research sample are charged at this uniform rate.
+This data enables us to carry out a comprehensive analysis of the impact of offline stores on housing transactions across both individual and neighborhood dimensions.
 
@@
 Given that stores are predominantly located within commercial districts, which typically encompass several streets no more than two kilometers in diameter, it is assumed that a requisite number of stores within each district is essential to sustain revenue generation in that community.
-In addition, Lianjia adopts a pedestrian shed strategy, also known as a 5-minute walking distance (approximately 400 meters) strategy, which means that customers should be accessible within a 5-minute walk to the nearest Lianjia store to reduce the .
+In addition, Lianjia adopts a pedestrian shed strategy, also known as a 5-minute walking distance (approximately 400 meters) strategy, which means that customers should be accessible within a 5-minute walk to the nearest Lianjia store to reduce the visiting cost.
 Building on this premise, the study further investigates the existence of an optimal influence radius within shopping districts, defined as the distance radius within which the presence of a Lianjia optimally increases transaction revenues.
@@
 
-From Figure \ref{fig:RD_design} we can see that there is indeed discontinuity in 410 meters of communities to the nearest Lianjia's store, which is pretty close to the lianjia's 5-minute walk distance policy.
+From Figure \ref{fig:RD_design} we can see that there is indeed discontinuity in 410 meters of communities to the nearest Lianjia's store, which is pretty close to the lianjia's 5-minute walk distance policy (400 meters).
 The observed decline in the Lianjia's influence is marked and suggests a pronounced reduction in its impact on the system overall within our study sample.
@@
 
-where $Y_{it}$ is the three main dependent variables, including $\log(\text{income})$, price concession, and $\log(\text{number of house tours})$, $density_{it}$ is the DBI, $\bf{X}_{it}$ is a set of control variables, including brokerage\_control L\_hedonic\_control, transaction\_control and region\_control, while $\tau_{it}$ is the time dummy variable interacting with the fixed effect of the business area, $\mu_i$ is the individual fixed effect and $\epsilon_{it}$ is the error term.
-The standard errors are clustered at the each community level.
-The results are shown in Table \ref{tab:stylized_fact}.
+where $Y_{it}$ is the three main dependent variables, including $\log(\text{income})$, price concession, and $\log(\text{number of house tours})$, $density_{it}$ is the DBI, $\bf{X}_{it}$ is a set of control variables, including brokerage\_control L\_hedonic\_control, transaction\_control and region\_control, while $\tau_{it}$ is the time dummy variable interacting with the fixed effect of the business area, $\mu_i$ is the neighborhood fixed effect and $\epsilon_{it}$ is the random error term.
+The standard errors are clustered at the each business area level.\footnote{The business area is defined as a combination of multiple neighborhoods, which Lianjia designates as the primary divisions of the entire region.} The results are shown in Table \ref{tab:stylized_fact}.
 
@@
 In column 1 and 2, we estimated the model using the neighborhood-level data and in column 3 and 4, we estiamted the model using the individual-level data, respectively.
-The results show that the share of Linajia's offline stores in total brokerage plays a significant role in the real estate market, especially in terms of revenue and lead time, but not in terms of price concession and transaction period.
-Specifically, a 1\% increase in a Lianjia's DBI within an area correlates with a 7\% increase in income, as indicated in column 1.
-Furthermore, this increased DBI also leads to a 4\% increase in the number of home tours in the column 2, underscoring the Lianjia's increased visibility and potential for customer engagement.
+The results show that the share of Linajia's offline stores in total brokerage plays a significant role in the real estate market, especially in terms of number and lead time, but not in terms of price concession and transaction period.
+Specifically, a 1\% increase in a Lianjia's DBI within an area correlates with a 7\% increase in number, as indicated in column 1.
+Furthermore, this increased DBI also leads to a 4.2\% increase in the number of home tours in the column 2, underscoring the Lianjia's increased visibility and potential for customer engagement.
 In contrast, the analysis shows no significant effect of DBI on price concessions and transaction time.
-This finding suggests that while a larger market share increases revenues and the number of house tours, it may not be beneficial for mathcing the buyers and sellers.
-The broader implications point to the strategic advantage of density or market share in driving business performance metrics, except for pricing strategies, which appear to be unaffected by changes in market share.
+This finding suggests that while a larger share of offline stores within the segmented market increases the number of sales and the number of house tours, it may not be beneficial for mathcing the buyers and sellers.
+The broader implications point to the strategic advantage of density or market share in driving business performance metrics, except for customers' choices, which appear to be unaffected by changes in market share.
 
@@
 Besides, to control for potential self correlation problem, we also included lagged one period dependent variables in the model.
-Other settings are the same with the previous model \eqref{eq:multi-way-fe} and the result is reported in Table \ref{tab:Dynamic}:
+Other settings are the same with the previous model \eqref{eq:multi-way-fe} and the model is described as \eqref{eq:dynamic} and the results are reported in Table \ref{tab:Dynamic}:
 
@@
 
-The result highlights the dynamic impact of density, encapsulated by Lianjia's DBI, on transaction revenue, house tours, and price concessions over time, especially in response to external factors such as digital transformation and the COVID-19 pandemic.
-Initially, Lianjia's impact on transaction revenue showed a significant positive trend, peaking in 2018, due to its digital transformation efforts, including the integration of other platform stores into its shared network.
-However, the momentum slowed in 2020 and 2021, with the impact becoming significantly negative.
-This period coincided with the outbreak of the COVID-19 pandemic, which severely disrupted Lianjia's revenue streams and business activities due to widespread restrictions, underscoring the vulnerability of real estate transactions to macroeconomic shocks.
-In terms of home tours, Lianjia's impact remained robustly positive through 2019.
-This suggests that a strong market presence correlates with increased buyer attention, which translates into more home tours.
+The result highlights the dynamic impact of offline store's share on maret performance, especially in response to external factors such as the digital transformation and the COVID-19 pandemic.
+Firstly, Lianjia's impact on transaction number showed a significant decreasing trend, but remains significantly positive before the 2020.
+However, the impact of offline stores turned significantly negative in 2020 and 2021, coinciding with the outbreak of the COVID-19 pandemic.
+The widespread restrictions during this period severely disrupted Lianjia's offline transaction procedures and business activities, highlighting the vulnerability of real estate transactions to macroeconomic shocks.
+
+In terms of number of home tours, Lianjia's impact remained positive from 2018 to 2020.
+This period coincides with Lianjia's online platform consolidation period where Lianjia decides to  This suggests that a strong market presence correlates with increased buyer attention, which translates into more home tours.
 However, pandemic-related restrictions dampened this effect in later years, highlighting the challenges posed by external constraints on physical real estate activity.
@@
 Nevertheless, the presence of a self-selection bias in this dynamic entry factor necessitates the application of causal inference methods to more accurately estimate the effect of Lianjia's offline stores.
-Consequently, we adopted the Difference-in-Difference (DiD) estimation technique.
-The foundation of this analysis is predicated on the assumption that the entry of a Lianjia store constitutes an exogenous shock within the local segmented market, thereby providing an unique natural experiment to examine the effects of offline expansion on the local real estate market.
+Consequently, we adopted the Difference-in-Difference (DiD) estimation to estimate the offline's store's entry's influence on the market performance.
+From the market's performance, the Lianjia's offline's store's entry into the segmented market is an exogenous shock to the two-sided customers, where sellers are more likey to be attracted by the brokerage and buyers are also more likely to be attracted by the more listing information in the neighborhood.
 Although Lianjia's entry is not a randomized event, the DiD estimation method remains unbiased in estimating the entry effect by comparing variations in outcome variables before and after Lianjia's entry in the segmented market.
@@
     \centering
-    \subfloat[Effect to income]{\includegraphics[width=0.5\textwidth]{../figures/did_1.pdf}\label{fig:did_income}}
+    \subfloat[Effect to transaction number]{\includegraphics[width=0.5\textwidth]{../figures/did_1.pdf}\label{fig:did_num}}
     \subfloat[Effect to number of house tours]{\includegraphics[width=0.5\textwidth]{../figures/did_2.pdf}\label{fig:did_lead_times}}
@@
 revise the paragraph to make it more economics and academic
-( this is today's work )
 

### 2024-07-03 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

@@
 
-where $Y_{it}$ is the three main dependent variables, including $\log(\text{income})$, price concession, and $\log(\text{number of house tours})$, $density_{it}$ is the DBI, $\bf{X}_{it}$ is a set of control variables, including brokerage\_control L\_hedonic\_control, transaction\_control and region\_control, while $\tau_{it}$ is the time dummy variable interacting with the fixed effect of the business area, $\mu_i$ is the neighborhood fixed effect and $\epsilon_{it}$ is the random error term.
+where $Y_{it}$ is the three main dependent variables, including $\log(\text{number})$, price concession, and $\log(\text{lead times})$, $density_{it}$ is the DBI, $\bf{X}_{it}$ is a set of control variables, including brokerage\_control Lag(hedonic\_control), transaction\_control and region\_control, while $\tau_{it}$ is the time dummy variable interacting with the fixed effect of the business area, $\mu_i$ is the neighborhood fixed effect and $\epsilon_{it}$ is the random error term.
 The standard errors are clustered at the each business area level.\footnote{The business area is defined as a combination of multiple neighborhoods, which Lianjia designates as the primary divisions of the entire region.} The results are shown in Table \ref{tab:stylized_fact}.
@@
     Note: we omit all the control variables in the regression model, and detailed descriptions can be seen from Table \ref{tab:statistical_district} and Table \ref{tab:statistical_individual}.
+In column 1 and 2, we estimated the model using the neighborhood-level data and in column 3 and 4, we estiamted the model using the individual-level data, respectively.
     \label{tab:stylized_fact}
@@
 
-In column 1 and 2, we estimated the model using the neighborhood-level data and in column 3 and 4, we estiamted the model using the individual-level data, respectively.
 The results show that the share of Linajia's offline stores in total brokerage plays a significant role in the real estate market, especially in terms of number and lead time, but not in terms of price concession and transaction period.
@@
 In the construction of our regression model, we deliberately omit the first period to avoid multicollinearity problem, treating it as a baseline for comparison.
-This strategic choice allows us to refine our proxy variable—the product of Lianjia's Dealership Balance Index (DBI) and annual dummies—as a more precise measure of Lianjia's local market power.
+This strategic choice allows us to refine our proxy variable—the product of Lianjia's Dealership Balance Index (DBI) and annual dummies—as a better measure of Lianjia's local market power.
 Besides, to control for potential self correlation problem, we also included lagged one period dependent variables in the model.
@@
 The widespread restrictions during this period severely disrupted Lianjia's offline transaction procedures and business activities, highlighting the vulnerability of real estate transactions to macroeconomic shocks.
-
 In terms of number of home tours, Lianjia's impact remained positive from 2018 to 2020.
-This period coincides with Lianjia's online platform consolidation period where Lianjia decides to  This suggests that a strong market presence correlates with increased buyer attention, which translates into more home tours.
+This period coincides with Lianjia's online platform consolidation period where Lianjia decides to adopt the online platform consolidation strategy, where the offline stores have more incentives to attract more buyers to visit their stores.
+This suggests that a strong market presence correlates with increased buyer attention, which translates into more home tours.
 However, pandemic-related restrictions dampened this effect in later years, highlighting the challenges posed by external constraints on physical real estate activity.
+Regarding the transaction period, the results indicate that Lianjia's DBI initially prolonged the transaction period.
+However, this effect reversed in 2020, albeit not continuously.
+This is likely due to the combined effects of online consolidation and the pandemic, with initial improvements followed by subsequent deterioration.
 For price concessions, we find that the Lianjia's DBI is significantly negatively correlated with the price concessions during pandemic periods.
@@
 
-To verify the robustness of our results, we calculated the Herfindahl-Hirschman Index (HHI) for each segmented market, defined as $HHI = \sum_{i=1}^N (s_i)^2$ where $s_i$ is the market share of firm $i$ expressed as a percentage.
-We then estimated the model by dividing the sample into high HHI (greater than 2000) and low HHI (less than 2000) groups.
-The results, shown in Table \ref{tab:sylized_fact_hetero_hhi}, indicate that Lianjia's offline stores have a more substantial impact on transaction properties in more competitive markets compared to more monopolized ones.
-This effect arises from two main factors: first, Lianjia's market power is insufficient to exclude other competitors from entering the market, and second, the area may not be attractive to other competitors, resulting in a larger market share for Lianjia.
-Furthermore, to address the heterogeneity issue, we introduced a dummy variable equal to one if the market already had Lianjia presence before 2016 and estimated the model by separating the sample based on this criterion.
-The results, presented in Table \ref{tab:sylized_fact_hetero_mature}, demonstrate that the years 2017, 2018, and 2019 have a significant positive impact on Lianjia's revenue in this segmented market.
-Another interesting phenomenon observed is that the number of house tours is significant for the years 2018 and 2019 in the lower maturity group, whereas in the higher maturity group, the number of house tours becomes significant in 2020.
-These findings indicate that in less mature markets, the entry of Lianjia drives increased profitability and enhances the attractiveness of its offline store strategy.
-Moreover, this suggests that Lianjia's market entry and subsequent strategies are more immediately impactful in less mature markets.
-
-% There should be a model like: Police brutality, law enforcement, and crime: Evidence from Chicago
-
 \section{Mechanism Design} \label{sec:mechanism_design}
@@
 In the preceding section, our research concentrated on evaluating the dynamic impact of Lianjia's offline store operations.
-Nevertheless, the presence of a self-selection bias in this dynamic entry factor necessitates the application of causal inference methods to more accurately estimate the effect of Lianjia's offline stores.
+Nevertheless, the presence of a self-selection bias in this dynamic entry factor necessitates the application of causal inference methods to better estimate the effect of Lianjia's offline stores.
 Consequently, we adopted the Difference-in-Difference (DiD) estimation to estimate the offline's store's entry's influence on the market performance.
@@
 To eliminate the effect of the well constructed effect, we drop all the variables that have Lianjia's offline stores before the year 2016 to better estimate the effect of Lianjia's entry on the market.
-These binary indicators serve as central regressors within a structured econometric model with $pre_1$ as the control group, described in Equation \eqref{eq:entry_effect}:
+These dummy variables serve as key independent variables with $pre_1$ as the control group, described in Equation \eqref{eq:entry_effect}:
 
 \begin{equation}
-    Y_{it} = \beta_0 +  pre_2 + entry + \sum_{i=1}^3 post_i + \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}.   \label{eq:entry_effect}
+    Y_{it} = \beta_0 +  \beta_1 pre_2 + \beta_2 entry + \beta_3 post_1 + \beta_4 post_2 + \beta_5 post_3 + \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}.   \label{eq:entry_effect}
 \end{equation}
 
-$pre_2, entry, post_i$ are correspondingly periods dummy variables and other settings are the same with Equation \eqref{eq:dynamic}. The results are reported in Table \ref{tab:entry_effect}.
+$pre_2, entry, post_i$ are correspondingly periods dummy variables and other settings are the same with Equation \eqref{eq:dynamic}.
+To mitigate the risk of missing information, we exclude the lagged variable lag(hedonic\_control) from the model and instead use the contemporaneous variable hedonic\_control.
+All subsequent models will also use hedonic\_control instead of its lag term.
+The results are reported in Table \ref{tab:entry_effect}.
 
@@
 
-To verify the robustness of the entry effect, we classified the sample into low and high Herfindahl-Hirschman Index (HHI) groups.
+To verify the robustness of our results, we calculated the Herfindahl-Hirschman Index (HHI) for each segmented market, defined as $HHI = \sum_{i=1}^N (s_i)^2$ where $s_i$ is the market share of firm $i$ expressed as a percentage.
+Higher HHI values indicate greater market concentration.
+To further validate the entry effect, we classified the sample into three groups based on HHI values: low HHI ($0 \leq HHI \leq 1,000$), moderate HHI ($1,000 \leq HHI \leq 2,500$) and high HHI ($2,500 \leq HHI \leq 10,000$).
+This classification allows us to assess the impact of Lianjia's entry across markets with varying levels of competition and concentration, ensuring that our findings are not driven by specific market conditions.
 The results, presented in Table \ref{tab:entry_effect_robustness_1}, indicate that the income effect for Lianjia remains consistent across both groups.

### 2024-07-03 manuscript/main.tex
modified:   manuscript/main.tex 	deleted:    result_tables/heter_platform_did.tex

@@
 In addition to this, Lianjia also opened up the form of franchises and gradually started platform integration.
-To empirically measure the effect of platformization on offline store operations, we first counted the number of all non-Lianjia stores on Lianjia's Beke platform within a radius of 410 meters.
+To empirically measure the effect of platform consolidation on offline store operations, we first counted the number of all non-Lianjia stores on Lianjia's Beke platform within a radius of 410 meters.
 This allowed us to generate a dummy variable, $\text{Treatment}_{it}$, which equals one if the ratio $\frac{\text{Lianjia}}{\text{Beke}} < 0.8$ in this area and the year is 2018 or later.
-This ratio is selected because if Lianjia accounts for more than 80\% of the Beke's offline stores, the strategy's effect is negligible and only effective for Lianjia.
+This ratio is selected because if Lianjia accounts for more than 80\% of the Beke's offline stores, the strategy's effect is negligible in this segmented market.
 To dynamically capture the varying effects, we generate a set of dummy variable $\text{post\_j\_treatment}_{it}$, where $j \in \{1, 2, 3\}$ and $\text{pre\_treatment}_{it}$ and include them in our regression model.
@@
 
-The empirical findings indicate that in the first year of the consolidation strategy, Lianjia's transaction revenue did not show a statistically significant difference.
-However, after the first year, the transaction revenue demonstrated a significant positive increase, ranging from 3\% to 6\%.
+The empirical findings indicate that in the first year of the consolidation strategy, Lianjia's transaction number did not show a statistically significant difference.
+However, after the first year, the transaction number demonstrated a significant positive increase, ranging from 2.9\% to 6.2\%.
 Additionally, the platform consolidation had a significantly positive impact on the number of house tours, with effects following the same trend as the transaction revenue.
@@
 However, the effect becomes insignificant after the third year.
-Overall, the results show that comparing with the offline store's entry effect, the platform's consolidation strategy can have more pronounced influence not only on effectiveness on trasaction but also on the overall revenue.
-
-revise the paragraph to make it more economics and academic
-
+Overall, the results indicate that, compared to the offline store entry effect, the platform consolidation strategy has a more pronounced influence on both transaction effectiveness and consumer response to housing units.
+This can be attributed to the increased control of information by the brokerage, which enables better alignment with consumer preferences.
+Consequently, the brokerage can provide enhanced services tailored to individual tastes, thereby facilitating transactions more effectively.
+
+% to this line
 While the platformization strategy is less effective in influencing individuals' decision-making processes compared to offline store entry, it proves more effective in increasing revenue and the number of house tours.

### 2024-07-03 manuscript/main.tex
update the progress

@@
 These results underscore the superior efficacy of platform consolidation in enhancing market performance and provide compelling evidence for the strategic advantage of platformization over traditional offline expansion.
-
 However, in terms of the transaction period, the platformization strategy does not exhibit a significant effect, indicating that platformization does not assist brokerages in facilitating better matching and negotiation between sellers and buyers.
@@
 However, the effect becomes insignificant after the third year.
+
 Overall, the results indicate that, compared to the offline store entry effect, the platform consolidation strategy has a more pronounced influence on both transaction effectiveness and consumer response to housing units.
+However, this strategy does not appear to be beneficial for sellers in the market.
+The benefits in terms of transaction period are not significant, and the increasing price concessions suggest that sellers are compelled to adjust listing prices to attract buyers.
+This can be attributed to the brokerage's increased control of information, which follows from attracting more sellers to join the network.
+While this provides a better match for buyers, it deteriorates the benefits for sellers.
+Consequently, the combined forces of better information provision for buyers and the influx of sellers keep the transaction period unchanged for houses that complete transactions, but there are more houses that fail to make a deal.
+It is worth noting that our data does not allow for separate estimation of these effects, which warrants further research.
+These findings align with the intuition that larger network effects are more likely to positively impact market performance but may not bring benefits to sellers.
+
+% Overall, the results indicate that, compared to the offline store entry effect, the platform consolidation strategy has a more pronounced influence on both transaction effectiveness and consumer response to housing units.
 This can be attributed to the increased control of information by the brokerage, which enables better alignment with consumer preferences.
 Consequently, the brokerage can provide enhanced services tailored to individual tastes, thereby facilitating transactions more effectively.
-
-% to this line
-While the platformization strategy is less effective in influencing individuals' decision-making processes compared to offline store entry, it proves more effective in increasing revenue and the number of house tours.
-This discrepancy highlights that the platformization strategy excels in attracting customers and generating revenue, but falls short in aiding the matching and negotiation process.
-These findings align with the intuition that platformization is more likely to draw customers and boost revenue, yet it is less effective in assisting buyers and sellers in reaching agreements.
-
-To further investigate the impact of market concentration on the effectiveness of the platformization strategy, we classified the samples into high and low Herfindahl-Hirschman Index (HHI) groups and estimated the model separately for each group.
-The high HHI group, representing markets with higher concentration, revealed that the platformization strategy does not confer significant benefits for Lianjia's operations.
-Conversely, in the low HHI group, indicative of less competitive markets, the platformization strategy significantly increases revenue.
-This suggests that the platformization strategy is more effective in less competitive markets, enhancing Lianjia's competitiveness.
-In terms of the number of house tours, the effect of platformization is consistent across both high and low HHI groups.
+These findings align with the intuition that the larger the network effect, the more likely it is to positively impact market performance and consumer satisfaction.
+
+To further investigate the impact of market concentration on the effectiveness of the platform consolidation strategy, we also classified the samples into low, moderate and high HHI groups and estimated the model separately for each group.
+The high HHI group, representing markets with higher concentration, revealed that the platform consolidation strategy does not confer significant benefits for Lianjia's operations.
+Conversely, in the low HHI group, indicative of less competitive markets, the platformization strategy significantly increases the transaction number.
+This suggests that the platform consolidation strategy is more effective in less competitive markets, enhancing Lianjia's competitiveness.
+In terms of the number of house tours, the effect of platform consolidation is consistent across both high and low HHI groups.
 This consistency aligns with the intuition that consumer preferences for different types of brokerages are similar, and individuals are equally likely to search for houses online regardless of the brokerage's market share.
@@
 
-In the online Appendix \ref{tab:platform_consolidation_hetero_mature}, we present the heterogeneous effects of Lianjia's operations in both mature and immature markets.
-Figure \ref{fig:treatment_consolidation} illustrates the distribution of income across the treatment and control groups.
+Appendix Figure \ref{fig:treatment_consolidation} illustrates the distribution of income across the treatment and control groups.
 Prior to the intervention, the two groups exhibit parallel trends, indicating no significant differences.
@@
 
-The result is consistent with the opinion that most platform like uber and lyft that does not have enough network strength and \citep{10.1257/jep.28.2.3}
-
-\citep{WOS:000454186600016}
-
-\section{Extension: Collaborative Spillover Effect} \label{sec:network_effect}
-
-The last section is to estimate the Lianjia's collaborative spillover effect.
-Lianjia decided to change from brokerage's direction operation to a combination of platform.
+The result is consistent with the opinion that most platform like uber and lyft that does not have enough network strength and we confirmed that within smaller networks and clustering  \citep{10.1257/jep.28.2.3}
+
+\section{Extension: Network Clustering Effect} \label{sec:network_effect}
+
+Previous literature illustrates that the strength of network effects and network clustering can be crucial for the operation of platforms and long-run competitiveness \citep{WOS:000454186600016}.
+The real estate market is characterized as a thin market, where local clustering patterns are more important in transactions, and people tend to have preferences within a given region.
+Therefore, segmented markets are largely independent of one another.
+In this context, brokerages have been fragmented into local clusters within each segmented market, allowing competitors to enter other segmented markets with relatively low costs.
+However, the entry barriers within markets already dominated by Lianjia are largely dependent on the network effects within these clusters.
+Thus, it is necessary to consider the network structure of Lianjia's offline stores and evaluate the impact of this network structure on neighborhoods within the segmented market.
+
+The last section is to estimate the Lianjia's spillover network effect.
+Following the Lianjia's platform consolidation strategy, Lianjia decided to change from brokerage's direction operation to a combination of platform.
 By attracting other brokerage's into the network will initially make the brokreage's profit down because attracting other people in the platform meaning the market share would be decreased due to the intense competition.
@@
 Then accordin to the this would be resulted in a winners-take-all market.
+
+We proposed a measure for the network clustering effect within the segmented market by treating offline stores and neighborhoods as nodes in a graph.
+Each offline store is connected to a neighborhood if the distance between them is within a five-minute walk, in line with the proposed five-minute walk strategy, and assigning a weight of 1 if the store and neighborhood nodes are connected.
+To document the connections between offline stores, for each year, we calculated the shared neighborhood transaction numbers and divided this by the total transaction numbers for store $i$ and store $j$.
+Mathematically, this can be represented as:
+
+\begin{equation}
+  \text{weight}_{ij} = \frac{(\text{shared transactions between store $i$ and store $j$})^2}{\text{total transaction for store $i$} \times \text{total transaction in store $j$}} \label{eq:weight_between_stores}
+\end{equation}
+
+This weight represents the strength of the connection between the stores. We then calculated the network clustering effect for each neighborhood using the following formula:
+
+\begin{equation}
+  \text{Clustering Effect}_{\text{neighborhood}} =  \label{eq:clustering_effect_for_neighborhood}
+\end{equation}
+
+where $n$ represents the number of stores connected to the neighborhood directly and indirectly, and $m$ represents the number of shared transactions between connected stores.
+This approach allows us to quantify the local clustering effect within the segmented market and assess its impact on neighborhoods.
+
+This connection is in line with the reality in that firstly, cooperation between stores to complete a transaction is very common, and more stores within the segmented market can contributed more to the transaction as more efforts can be jointly made between different agents.
+Secondly, the influence of the netowrk decays from subconnected nodes and this is due to the decreasing benefits by connecting other sub-connecting.
 

### 2024-07-04 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

@@
 \usepackage{pgfplots}
+\usepackage{algorithm}
+\usepackage{algorithmic}
 \usepackage{subfig}
@@
 
-The last section is to estimate the Lianjia's spillover network effect.
-Following the Lianjia's platform consolidation strategy, Lianjia decided to change from brokerage's direction operation to a combination of platform.
-By attracting other brokerage's into the network will initially make the brokreage's profit down because attracting other people in the platform meaning the market share would be decreased due to the intense competition.
-However, after the setup of the platform, the market will be more productive and more competitive to occupying a larger share of the whole network.
-This mechanism is more likely to get better control over the listing and people are more willing to list their house on this platform.
-Then accordin to the this would be resulted in a winners-take-all market.
-
 We proposed a measure for the network clustering effect within the segmented market by treating offline stores and neighborhoods as nodes in a graph.
-Each offline store is connected to a neighborhood if the distance between them is within a five-minute walk, in line with the proposed five-minute walk strategy, and assigning a weight of 1 if the store and neighborhood nodes are connected.
+Each offline store is connected to a neighborhood if the distance between them is within a five-minute walk, in line with the proposed five-minute walk strategy, and assigning a weight of $1$ if the store and neighborhood nodes are connected.
 To document the connections between offline stores, for each year, we calculated the shared neighborhood transaction numbers and divided this by the total transaction numbers for store $i$ and store $j$.
@@
 
-This weight represents the strength of the connection between the stores. We then calculated the network clustering effect for each neighborhood using the following formula:
-
-\begin{equation}
-  \text{Clustering Effect}_{\text{neighborhood}} =  \label{eq:clustering_effect_for_neighborhood}
-\end{equation}
-
-where $n$ represents the number of stores connected to the neighborhood directly and indirectly, and $m$ represents the number of shared transactions between connected stores.
-This approach allows us to quantify the local clustering effect within the segmented market and assess its impact on neighborhoods.
-
-This connection is in line with the reality in that firstly, cooperation between stores to complete a transaction is very common, and more stores within the segmented market can contributed more to the transaction as more efforts can be jointly made between different agents.
-Secondly, the influence of the netowrk decays from subconnected nodes and this is due to the decreasing benefits by connecting other sub-connecting.
-
-In this case, we need to empirically estimate the spillover effect, and if this spillover effect is significant in this setting then people's reaction
-
-To set up, we first match the brokerages' with the
-
-We decided to use the so called quantile estimator described in model  proposed by \citep{machado_quantiles_2019}.
-
-\begin{equation}
-  \begin{aligned}
-    Q_y(\xi \mid X) & = \beta_0 + \beta_1(\xi) \text{pre\_treatment}_{it} + \beta_2(\xi) \text{treatment} + \sum_{i=3}^5 \beta_i(\xi) \text{post\_treatment}_{it} \\
-    & + \beta(\xi) \bf{X}_{it} + \mu_i + \tau_t + \varepsilon_{it}
-  \end{aligned}
-\end{equation}
-
-\ref{tab:quantile_estimate_network} shows the quantile estimation of the . We can see that the
+This weight represents the strength of the connection between the stores, enabling us to construct a network graph for our analysis.
+To visualize this network, we randomly selected 10 points and used a maximum search depth of 10 to plot the graph, as shown in Figure \ref{fig:network_formation_effect_graph}.
+WE constructed the measure indices as local clustering effect and global clustering effect.
+The local clustering effect refers to the degree to which nodes in a network tend to cluster together, forming tight-knit groups.
+In contrast, the global clustering effect shows the overall pattern of clustering across the entire network.
+Detailed indices for each city and each year is reported in Table \ref{tab:local_global_clustering_indices}.
+In this graph, the size of the nodes indicates the significance of the local clustering effect, with larger nodes representing stronger local clustering.
+
+From the graph, we can see that the
 
@@
     \begin{scriptsize}
-      \caption{Estimated Network Spillover Effect}
-      \label{tab:estiamted_spillover_effect}
+      \caption{Average Local Clustering Index and Global Clustering Index}
+      \label{tab:local_global_clustering_indices}
       \input{../result_tables/clustering_indices.tex}
@@
 \end{table}
+
+We then calculated the network clustering effect for each neighborhood using Breadth First Search Algorithm (BFS) described in the Algorithm \ref{alg:clustering_effect}:
+
+\begin{algorithm}[H]
+  \caption{Calculate Clustering Effect for Each Neighborhood}
+  \label{alg:clustering_effect}
+  \begin{algorithmic}[1]
+    \STATE \textbf{Input:} Graph $G = (N, E)$ with neighborhoods and stores, edge weights $w_{ij}$.
+    \STATE \textbf{Output:} Clustering effect for each neighborhood.
+
+    \FOR{each neighborhood $n \in N$}
+      \STATE Initialize the set of directly connected stores $S_n$.
+      \STATE Initialize queue $Q \leftarrow \{(s, w_{ns}) \mid s \in S_n\}$.
+      \STATE Initialize set of visited stores $V \leftarrow \{s \mid s \in S_n\}$.
+      \STATE Initialize $\text{Cluster Effect}_n \leftarrow 0$.
+
+      \WHILE{$Q$ is not empty}
+        \STATE Dequeue $(s, \text{effect}_s) \leftarrow Q.\text{pop}(0)$.
+        \FOR{each neighbor store $s^\prime \in G.\text{neighbors}(s)$}
+          \IF{$s^\prime \notin V$}
+          \STATE Calculate propagated effect $\text{effect}_{s^\prime} \leftarrow \text{effect}_s \times w_{ss^\prime}$.
+                \STATE Enqueue $(s^\prime, \text{effect}_{s^\prime})$ into $Q$.
+                \STATE Add $s^\prime$ to visited set $V$.
+            \ENDIF
+        \ENDFOR
+        \STATE Accumulate $\text{Cluster Effect}_n \leftarrow \text{Cluster Effect}_n + \text{effect}_s$.
+      \ENDWHILE
+    \ENDFOR
+    \STATE \textbf{return} Clustering effects for all neighborhoods.
+  \end{algorithmic}
+\end{algorithm}
+
+% need to refine
+This approach allows us to quantify the local clustering effect within the segmented market and assess its impact on neighborhoods.
+This connection is in line with the reality in that firstly, cooperation between stores to complete a transaction is very common, and more stores within the segmented market can contributed more to the transaction as more efforts can be jointly made between different agents.
+Secondly, the influence of the netowrk decays from subconnected nodes and this is due to the decreasing benefits by connecting other sub-connecting.
+
+Following the Lianjia's platform consolidation strategy, Lianjia decided to consolidate downstream brokerages to form a larger clustering within the segmented market and increase.
+By attracting other brokerage's into the network will initially make the brokreage's profit down because attracting other people in the platform meaning the market share would be decreased due to the intense competition.
+However, after the setup of the platform, the market will be more productive and more competitive to occupying a larger share of the whole network.
+This mechanism is more likely to get better control over the listing and people are more willing to list their house on this platform.
+Then according to the this would be resulted in a winners-take-all market.
+
+In this case, we need to empirically estimate the spillover effect, and if this spillover effect is significant in this setting then people's reaction
+
+To set up, we first match the brokerages' with the
+
+We decided to use the so called quantile estimator described in model  proposed by \citep{machado_quantiles_2019}.
+
+\begin{equation}
+  \begin{aligned}
+    Q_y(\xi \mid X) & = \beta_0 + \beta_1(\xi) \text{pre\_treatment}_{it} + \beta_2(\xi) \text{treatment}_{it} + \sum_{i=3}^5 \beta_i(\xi) \text{post\_treatment}_{it} \\
+    & + \beta(\xi) \bf{X}_{it} + \mu_i + \tau_t + \varepsilon_{it}
+  \end{aligned}
+\end{equation}
+
+\ref{tab:quantile_estimate_network} shows the quantile estimation of the . We can see that the
 
@@
 
+Descriptions of the measures of the clustering coefficient effects:
+
+We also calcualted the the local clustering coefficient for a node $i$, which is a measure of the likelihood that the neighbors of $i$ are also neighbors of each other, and it is calcualted as:
+
+\begin{equation*}
+  C_i = \frac{2e_i}{k_i(k_i - 1)}  
+\end{equation*}
+
+where $e_i$ is the number of edges between the neighbors of node $i$ and $k_i$ is the degree of node $i$.
+The average clustering coefficient is the mean of the local clustering coefficients for all nodes in the network, defined as: $C = \frac{1}{n} \sum_{i=1}^n C_i$ where $n$ is the total number of nodes.
+This index indicates how close the neighbors of a node are to forming a complete graph (clique).
+
+The global clustering coefficient, also known as transitivity, is a measure of the overall tendency of the network to form triangles.
+It is defined as the ratio of the number of closed triplets (triangles) to the number of all triplets (both open and closed) in the network.
+
+\begin{equation*}
+  C_g = \frac{3 \times \text{number of closed triplets}}{\text{number of all triplets}}  
+\end{equation*}
+
+A triplet consists of three nodes connected by either two (open triplet) or three (closed triplet) edges.
+This index indicates the global interconnectedness and the presence of tightly knit groups within the entire network.
+For both indices, higher values indicate a denser network.
+Typically, values between 0.75 and 1 signify a dense network, values between 0.4 and 0.7 indicate a moderately dense network, and values between 0 and 0.3 represent a sparse network.
+
 \end{document}

### 2024-07-04 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

@@
 
-From the graph, we can see that the
+% 从图中，我们可以发现大多数的节点都是相互连接的，但是部分节点是与其他节点互不相连的，这一方面说明了，对于部分局部市场，链家拥有的网络效应并不是很强，也证明了链家的网络更类似于局部的clustering而不是整体相连；另一方面，对于最大的connected component，节点的分布也具有不对称性，可以看到部分门店具有中心作用，其拥有更大的网络可达性，而部分节点虽然与其他节点相连，但是其更多的是处于局部小三角，小聚合，所以其网络效应不大。最后，我们可以发现，对于门店节点所连接的其他neighborhood节点，其分布也不具备对称性，对于高聚合度的门店节点其拥有的neighborhood节点也更为密集，这一方面是因为其具有更高的经济价值，所以其在网络中的地位也更高，所以其拥有的网络效应也更强。最后，综合来看
+
+From the figure, we can observe that most nodes are interconnected, but some nodes are not connected to others.
+This indicates that, in certain local markets, Lianjia's network effect is not very strong, demonstrating that Lianjia's network is more akin to localized clustering rather than being entirely interconnected.
+On the other hand, for the largest connected component, the distribution of nodes is also asymmetric.
+Some stores play a central role, possessing greater network accessibility, while other nodes, although connected to others, are more likely to form small local triangles or clusters, resulting in a smaller network effect.
+Finally, we can observe that the distribution of neighborhood nodes connected to store nodes is also asymmetrical.
+Stores with higher aggregation degrees have denser neighborhood nodes, partly due to their higher economic value, which enhances their status in the network and strengthens their network effect.
+Overall, these observations suggest that while Lianjia's network exhibits significant local clustering, its overall network connectivity varies, with certain stores and neighborhoods playing pivotal roles due to their higher economic significance.
+The stronger network effects observed in high-value areas emphasize the role of economic factors in shaping the structure and influence of the network.
 

### 2024-07-04 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	modified:   network_estimation/network_structure.ipynb 	modified:   result_tables/clustering_indices.tex

@@
 \begin{equation}
-  Y_{it} = \beta_0 + \beta_1 density_{it} + \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}, \label{eq:multi-way-fe}
+  Y_{it} = \beta_0 + \beta_1 density_{it} + \bf{\alpha} \bf{X}_{it} + \eta_{t} \times \text{bs\_code}_i + \mu_i + \epsilon_{it}, \label{eq:multi-way-fe}
 \end{equation}
 
-where $Y_{it}$ is the three main dependent variables, including $\log(\text{number})$, price concession, and $\log(\text{lead times})$, $density_{it}$ is the DBI, $\bf{X}_{it}$ is a set of control variables, including brokerage\_control Lag(hedonic\_control), transaction\_control and region\_control, while $\tau_{it}$ is the time dummy variable interacting with the fixed effect of the business area, $\mu_i$ is the neighborhood fixed effect and $\epsilon_{it}$ is the random error term.
+where $Y_{it}$ is the three main dependent variables, including $\log(\text{number})$, price concession, and $\log(\text{lead times})$, $density_{it}$ is the DBI, $\bf{X}_{it}$ is a set of control variables, including brokerage\_control Lag(hedonic\_control), transaction\_control and region\_control, while $\eta_{t} \times \text{bs\_code}_i$ is the time dummy variable interacting with the fixed effect of the business area, $\mu_i$ is the neighborhood fixed effect and $\epsilon_{it}$ is the random error term.
 The standard errors are clustered at the each business area level.\footnote{The business area is defined as a combination of multiple neighborhoods, which Lianjia designates as the primary divisions of the entire region.} The results are shown in Table \ref{tab:stylized_fact}.
@@
 \begin{equation}
-    Y_{it} = \beta_0 + \rho Y_{it-1} + \sum_{i=2}^7 density_{it} * year_{it} + \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}. \label{eq:dynamic}
+  Y_{it} = \beta_0 + \rho Y_{it-1} + \sum_{i=2}^7 density_{it} * year_{it} + \bf{\alpha} \bf{X}_{it} + \eta_{t} \times \text{bs\_code}_i + \mu_i + \epsilon_{it}. \label{eq:dynamic}
 \end{equation}
@@
 \begin{equation}
-    Y_{it} = \beta_0 +  \beta_1 pre_2 + \beta_2 entry + \beta_3 post_1 + \beta_4 post_2 + \beta_5 post_3 + \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}.   \label{eq:entry_effect}
+  Y_{it} = \beta_0 +  \beta_1 pre_2 + \beta_2 entry + \beta_3 post_1 + \beta_4 post_2 + \beta_5 post_3 + \bf{\alpha} \bf{X}_{it} + \eta_{t} \times \text{bs\_code}_i + \mu_i + \epsilon_{it}.
+\label{eq:entry_effect}
 \end{equation}
@@
     Y_{it} & = \beta_0 + \beta_1 \text{prev\_treatment}_{it} + \beta_2 \text{treatment}_{it} + \sum_{j=3}^5 \beta_{i} \text{post\_j\_treatment}_{it} + \\
-           & \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}. \label{eq:acn_assessment}
+           & \bf{\alpha} \bf{X}_{it} + \eta_{t} \times \text{bs\_code}_i + \mu_i + \epsilon_{it}. \label{eq:acn_assessment}
   \end{aligned}
@@
 
+\subsection{Measure of Network Effect} \label{subsec:measure_network_effect}
+
 Previous literature illustrates that the strength of network effects and network clustering can be crucial for the operation of platforms and long-run competitiveness \citep{WOS:000454186600016}.
@@
 
+From Table \ref{tab:local_global_clustering_indices}, we observe a general increasing trend in the network effects during the study period, with some cities exhibiting more pronounced network effects than others.
+However, it is important to note that no city demonstrates a particularly strong network effect throughout the research period; the network effects remain moderate.
+This suggests that the observed network structure is characterized by local clustering rather than extensive global connectivity, consistent with our graphical observations.
+Moreover, Lianjia's network effects exhibit similar patterns in terms of local clustering indices across different cities.
+However, the overall connectivity, as indicated by the global clustering index, varies significantly among cities.
+For instance, Guangzhou has a global clustering index of 0.56, indicating a very high level of overall connectivity.
+This contrast highlights the heterogeneous nature of network structures across different urban markets.
+
 \begin{figure}
@@
 
-We then calculated the network clustering effect for each neighborhood using Breadth First Search Algorithm (BFS) described in the Algorithm \ref{alg:clustering_effect}:
+To calculate the network effect on the neighborhoods in the graph, we then calculated the network clustering effect for each neighborhood using Breadth First Search Algorithm (BFS) described in the Algorithm \ref{alg:clustering_effect}:
 
@@
 This approach allows us to quantify the local clustering effect within the segmented market and assess its impact on neighborhoods.
-This connection is in line with the reality in that firstly, cooperation between stores to complete a transaction is very common, and more stores within the segmented market can contributed more to the transaction as more efforts can be jointly made between different agents.
-Secondly, the influence of the netowrk decays from subconnected nodes and this is due to the decreasing benefits by connecting other sub-connecting.
-
-Following the Lianjia's platform consolidation strategy, Lianjia decided to consolidate downstream brokerages to form a larger clustering within the segmented market and increase.
-By attracting other brokerage's into the network will initially make the brokreage's profit down because attracting other people in the platform meaning the market share would be decreased due to the intense competition.
-However, after the setup of the platform, the market will be more productive and more competitive to occupying a larger share of the whole network.
-This mechanism is more likely to get better control over the listing and people are more willing to list their house on this platform.
-Then according to the this would be resulted in a winners-take-all market.
-
-In this case, we need to empirically estimate the spillover effect, and if this spillover effect is significant in this setting then people's reaction
-
-To set up, we first match the brokerages' with the
-
-We decided to use the so called quantile estimator described in model  proposed by \citep{machado_quantiles_2019}.
+The average effect of the network is [] and the standard deviation is [].
+This connection is in line with the reality in several ways.
+Firstly, cooperation between stores to complete a transaction is very common, and having more stores within the segmented market can contribute significantly to the transaction process as more efforts can be jointly made by different agents.
+The collaboration between agents enhances the efficiency and effectiveness of the transaction process, leading to potentially quicker sales and better matching between buyers and properties.
+Secondly, the influence of the network decays with distance from subconnected nodes.
+This is due to the diminishing benefits of connecting with more distant nodes, as the value of information decreases with increasing distance.
+Information shared over longer distances may lose relevance or accuracy, thereby reducing its appeal and utility in facilitating transactions.
+Thirdly, we disregard each neighborhood's influence from other neighborhoods.
+This assumption is consistent with the observation that most houses within a neighborhood share similar characteristics, and the transaction effects within one neighborhood do not significantly impact other neighborhoods.
+Lastly, following Lianjia's platform consolidation strategy, the company decided to consolidate downstream brokerages to form larger clusters within the segmented market.
+This strategy primarily focuses on enhancing the connectivity and collaboration among stores within the network.
+To assess the impact of this strategy, we can examine the effects at the neighborhood level, as the increased cooperation among stores is expected to influence local market dynamics.
+By analyzing the neighborhood-level effects, we can better understand how the consolidation of brokerages translates into improved transaction efficiency and enhanced network effects, thereby reflecting the overall success of the platform consolidation strategy.
+
+\subsection{Estimation of Network Consolidation on Network Effect} \label{subsec:platform_network_effect}
+
+To empirically estimate the impact of network consolidation on the network effect, we also consider the influence of Lianjia's platform consolidation strategy on the local network clustering effect for each neighborhood.
+This strategy primarily targets Lianjia's offline stores, and its impact is likely to be heterogeneous across different neighborhoods.
+Specifically, neighborhoods that already had a diverse range of stores within the network before the strategy's implementation are expected to experience a more pronounced effect.
+Conversely, in neighborhoods where the local network effect was initially weak, the strategy's influence is expected to be relatively limited.
+
+In this context, a DID estimator can be employed to evaluate the average treatment effect.
+However, given the dynamic nature of the strategy's implementation across different periods, the traditional DID approach may not fully capture the varying impacts.
+Therefore, we employ a quantile regression estimator, as described in the model proposed by \citep{machado_quantiles_2019}, to better understand the distributional effects of the strategy.
+The quantile regression approach allows us to analyze the impact of the platform consolidation strategy across different points in the distribution of the local network clustering effect.
+This method provides a more nuanced understanding of how the strategy affects neighborhoods differently, capturing both the average treatment effect and the variability in effects across the distribution.
+The model is described as the follows:
 
@@
   \begin{aligned}
-    Q_y(\xi \mid X) & = \beta_0 + \beta_1(\xi) \text{pre\_treatment}_{it} + \beta_2(\xi) \text{treatment}_{it} + \sum_{i=3}^5 \beta_i(\xi) \text{post\_treatment}_{it} \\
-    & + \beta(\xi) \bf{X}_{it} + \mu_i + \tau_t + \varepsilon_{it}
+    Q_y(\tau \mid X) & = \beta_0 + \beta_1(\tau) \text{Pre\_Treatment}_{it} + \beta_2(\tau) \text{Treatment}_{it} + \sum_{j=3}^5 \beta_j(\tau) \text{Post\_j\_Treatment}_{it} \\
+                     & + \alpha(\tau) \bf{X}_{it} + \mu_i + \eta_t + \epsilon{it}
   \end{aligned}
@@
 
-\ref{tab:quantile_estimate_network} shows the quantile estimation of the . We can see that the
+where $Q_y(\xi \mid X)$ represents the $\tau$-th quantile of the dependent variable $y$ given the predictors $X$, where $\tau \in \{5, 10, \ldots, 95\}$.
+$\beta_0$ is the intercept term, $\text{Pre\_Treatment}_{it}$ is a dummy variable indicating the pre-treatment period, $\text{Treatment}_{it}$ is a dummy variable indicating the treatment group in 2018 and $\text{Post\_j\_Treatment}$ is a set of dummy variables indicating the post treatment group interacting with that year.
+$\mu_i$ represents individual fixed effects and $\eta_t$ is the year fixed effect and $\epsilon_{it}$ is the error term.
+To eliminate potential biases arising from nodes that are perpetually isolated from the network, such as neighborhoods with very few listings, we have decided to exclude samples that do not have any connections with other nodes.
+The results are reported in Table \ref{tab:quantile_estimate_network}.
+
+Table \ref{tab:quantile_estimate_network} presents the quantile estimation results of the network clustering effect following the platform consolidation strategy.
+Prior to the treatment, the coefficients are not significant at the 10\% level, indicating no observable effect on the network clustering effect and no observatory changes before the effect.
+In the first period after the platform consolidation strategy's implementation, the influence on the lowest 5\% quantile of the network is not significant at the 10\% level.
+However, there is a significant increase in network clustering, with a coefficient of 0.86, though the magnitude of this effect decreases as the quantile level increases.
+This suggests that the platform consolidation strategy has a more pronounced impact on neighborhoods with initially lower network clustering, facilitating the formation of larger and more connected networks.
+
+The effect of the strategy continues to grow in magnitude in the first period post treatment groups, with coefficients increasing from 1.1 to 1.4 across the quantiles.
+This trend intensifies in the second period, with even greater changes observed in network clustering, indicating an escalating impact over time.
+This pattern is consistent with the intuition that the platform consolidation strategy enhances network effects by forming larger clusters within the segmented market, thereby improving transaction efficiency and market competitiveness.
+In the final period of the study, the trend in magnitude begins to shift.
+The strategy's effect becomes significant for already well-connected groups rather than for those with initially low connectivity.
+This indicates that the consolidation strategy continues to strengthen existing networks, making well-connected neighborhoods even more integrated and efficient.
+
+Overall, the results suggest that the platform consolidation strategy has a significant and dynamic impact on the network clustering effect.
+Initially, it benefits neighborhoods with lower connectivity, helping them to form larger and more efficient clusters.
+Over time, the strategy's influence extends to enhance the clustering of already well-connected neighborhoods, thereby continuously improving the overall network structure and market performance.
+Moreover, from the long-term perspectives, the online consolidation effect is beneficial for Lianjia's competitiveness because the larger the local network effect, the better Lianjia can better can have better contorl in the information.
+Moreover, from a long-term perspective, the online consolidation effect enhances Lianjia's competitiveness, as a stronger local network effect enables Lianjia to exert greater control over information.
 
@@
 
-The Chinese real estate market witnessed a significnat drop at 2022 and the labor market is fierece in recently and therefore, the people are pretty hard to get on jobs.
+The Chinese real estate market witnessed a significant drop at 2022 and the labor market is fierece in recently and therefore, the people are pretty hard to get on jobs.
 

### 2024-07-05 manuscript/main.tex
update teh change

@@
 
-\title{ \vspace*{-2.5cm} \hspace*{-0.5cm}Offline Store Expansion and Platform Consolidation: Evidence from major cities in China \footnote{
+\title{ \vspace*{-2.5cm} \hspace*{-0.5cm}Platform-Mediated Consolidation and Offline Store Expansion: Evidence from Real Estate Brokerages in Major Chinese Cities \footnote{
 The preliminary version was entitled "Property brokerage, Partial monopoly and Housing market" and was presented at The 1st Summer Meeting in Urban Economics, China.
@@
 \begin{abstract}
-    \noindent This study examines the impact of offline store expansion by Lianjia, China's leading real estate brokerage, within the framework of platform consolidation.
-By analyzing micro-level transactions of second-hand houses in ten major Chinese cities from 2016 to 2022, the research investigates how the transaction patterns of traditional brokerages, characterized by the strategic clustering of offline stores, transition towards online consolidation, thereby facilitating the development of an extensive franchise network.
-Utilizing a regression discontinuity (RD) design, the study quantifies the optimal influence radius of offline stores on housing transactions.
-Incorporating this optimal influence radius, the study further empirically estimates the effects of real estate brokerage's offline store expansion and online platform consolidation on transaction properties.
-This analysis leverages the exogenous shock of Lianjia's market entry, identifying a significant increase in transaction revenues before the COVID-19 pandemic.
-However, this effect diminishes during the pandemic due to remote work and restrictive policies implemented by the Chinese government.
-The study also examines the online platform consolidation effect by analyzing the period in 2018 when Lianjia revised and improved its Agent Cooperation Network (ACN).
-
-    \textbf{The results indicate that this strategy significantly boosts revenues and also suggest that the offline store's effect is majorly focused on people's transaction behaviors but the online platform's effect can be more insightful to provide a more efficient transaction process.
-} % this need to be revised.
-
+    \noindent This study examines the impact of offline store expansion by Lianjia, China's leading real estate brokerage, within the framework of platform-mediated consolidation.
+By analyzing micro-level transactions of second-hand houses from Lianjia in ten major Chinese cities from 2016 to 2022, this research investigates how the transaction patterns of traditional brokerages, characterized by the strategic clustering of offline stores, transition towards platform-mediated consolidation, thereby facilitating the development of an extensive franchise network.
+Utilizing a regression discontinuity (RD) design, the study quantifies the optimal influence radius of offline stores (410 meters) on housing transactions.
+Incorporating this optimal influence radius, the study further empirically estimates the effects of real estate brokerage's offline store expansion and platform-based consolidation on transaction properties.
+The results indicate that this strategy significantly boosts revenues and attracts more people to housing tours.
+The results also suggest that neither the platform-based strategy nor offline expansion affects the transaction period, but offline store expansion can indeed reduce the price gap between sellers and buyers.
+Additionally, we proposed a measure of the network effect and found that Lianjia's offline stores show a local clustering pattern with moderate network strength.
+We then analyzed the effect of platform-mediated consolidation on network strength and concluded that the effect is significantly positive.
 This study provides valuable insights into the synergy between offline store expansion and online platform development, elucidating future trajectories in the evolving real estate brokerage market and analogous sectors.
@@
 
-  \textbf{Keyword}: Marketing Strategy, Digital Platforms, Platform Consolidation, Real Estate Brokerage
+  \textbf{Keyword}: Marketing Strategy, Platforms, Platform-Mediated Consolidation, Real Estate Brokerage
 
@@
 
-To determine the optimal radius of influence, this research employs a regression discontinuity design (RDD) method on the neighborhood level transaction data to examine the influential radius of offline real estate brokerages.
+To determine the optimal radius of influence, this research employs a regression discontinuity (RD) design on the neighborhood level transaction data to examine the influential radius of offline real estate brokerages.
 The dependent variable in this analysis is the transaction revenue generated by Lianjia within a given community, while the independent variable is the community's proximity to the nearest Lianjia store.
@@
 The treatment effect becomes significant only after the first period, aligning with our empirical findings.
-
-The result is consistent with the opinion that most platform like uber and lyft that does not have enough network strength and we confirmed that within smaller networks and clustering  \citep{10.1257/jep.28.2.3}
 
@@
 This approach allows us to quantify the local clustering effect within the segmented market and assess its impact on neighborhoods.
-The average effect of the network is [] and the standard deviation is [].
+The average effect of the network is 2.18 and the standard deviation is 2.55.
 This connection is in line with the reality in several ways.
@@
 
-\section{Conclusion and Discussion} \label{sec:conclusion}
-
-In the China's real estate market the
-
-The Chinese real estate market witnessed a significant drop at 2022 and the labor market is fierece in recently and therefore, the people are pretty hard to get on jobs.
+\section{Discussion and Conclusion} \label{sec:conclusion}
+
+This paper has presented that in China's real estate market, brokerages' offline stores play an critical factor in transaction. In our baseline
+
+The result is consistent with the opinion that most platform like uber and lyft that does not have enough network strength and we confirmed that within smaller networks and clustering  \citep{10.1257/jep.28.2.3}
 

### 2024-07-05 analysis/RD design analysis.Rmd
modified:   analysis/RD design analysis.Rmd 	deleted:    analysis/RD-design-analysis.log 	deleted:    analysis/placebo-test/coefficients.dta 	deleted:    analysis/placebo-test/~permute_neighbor.do.stswp 	new file:   plotting/placebo_plot.R

@@
 library(ggplot2)
-library(dplyr)
 library(rdrobust)

### 2024-07-05 plotting/placebo_plot.R

@@ -1,0 +1,45 @@
+library(dplyr)
+library(haven)
+library(ggplot2)
+library(extrafont)
+library(ggthemes)
+
+name_figures <- c(
+    ""
+)
+
+
+loadfonts(device = "win")
+setwd("E:/umich/RealEstateBrokerage/analysis/placebo-test")
+data <- read_dta("lead_entry_effect.dta")
+
+means <- colMeans(data)
+sds <- apply(data, 2, sd)
+
+names_list <- c('pre2', 'pre1', 'entry', 'post1', 'post2', 'post3')
+
+plot_data <- data.frame(
+    Coefficient = factor(names_list, levels = names_list),
+    Mean = means,
+    SD = sds
+)
+
+
+
+result <- ggplot(plot_data, aes(x = Coefficient, y = Mean)) +
+    geom_point(size = 3, color = "darkblue") +
+    geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = 0.2) +
+    theme_classic(base_family = "Times New Roman") +  # Use Arial font
+    labs(y = "Mean Value",
+         x = "Coefficient") +
+    theme_bw() +  # Apply a beautiful theme from ggthemes
+    theme(
+        text = element_text(family = "Times New Roman", size = 14),  # Use Arial font
+        axis.title = element_text(size = 9, face = "bold"),
+        axis.text = element_text(size = 7, face = "bold"),
+        plot.title = element_text(size = 7, hjust = 0.5),
+        legend.title = element_text(size = 5),
+        legend.text = element_text(size = 5)
+    )
+
+ggsave(name_figure, plot = result, dpi = 300)

### 2024-07-06 manuscript/main.tex
new file:   figures/typical_observation.png 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	figures/typical_sample_lianjia

@@
 By analyzing micro-level transactions of second-hand houses from Lianjia in ten major Chinese cities from 2016 to 2022, this research investigates how the transaction patterns of traditional brokerages, characterized by the strategic clustering of offline stores, transition towards platform-mediated consolidation, thereby facilitating the development of an extensive franchise network.
-Utilizing a regression discontinuity (RD) design, the study quantifies the optimal influence radius of offline stores (410 meters) on housing transactions.
+Utilizing a regression discontinuity design (RDD), the study quantifies the optimal influence radius of offline stores (410 meters) on housing transactions.
 Incorporating this optimal influence radius, the study further empirically estimates the effects of real estate brokerage's offline store expansion and platform-based consolidation on transaction properties.
@@
 
-China's real estate market possesses distinct features characterized by the prominence of offline stores, setting it apart from the markets in other developed countries.
+China's real estate listings market possesses distinct features characterized by the prominence of offline stores, setting it apart from the markets in other developed countries.
 Compared to the United States, where the Multiple Listing Service (MLS) provides comprehensive and reliable information online, facilitating transactions in a market where houses are typically situated far apart, the role of offline real estate stores is minimized.
@@
 Lianjia's offline store presence is notably uneven, with a high density in major urban centers and sparse distribution in other regions, reflecting strategic market positioning and possibly underlying economic and demographic factors influencing store locations.
+% \citep{peng_mortgage_2023}
 
@@
 Utilizing micro-level transaction data, we construct our research sample by aggregating information at the neighborhood level.
-We employ a regression discontinuity (RD) design to identify the optimal influential radius of offline stores on neighborhood transactions, finding that this radius corresponds to a brokerage's five-minute walk service distance, which is also documented in similar fields \citep{AZMI2012406}.
+We employ a regression discontinuity design (RDD) to identify the optimal influential radius of offline stores on neighborhood transactions, finding that this radius corresponds to a brokerage's five-minute walk service distance, which is also documented in similar fields \citep{AZMI2012406}.
 Subsequently, we apply a difference-in-difference (DID) estimation method to evaluate the exogenous impact of Lianjia's market entry on local segments.
@@
 
-To assess the consolidation effect of the online platform, we treat the year Lianjia implemented the platform consolidation strategy as an exogenous shock to the market.
+To assess the consolidation effect of the online platform, we treat the year Lianjia implemented the platform based consolidation strategy as an exogenous shock to the market.
 The platform consolidation strategy is majorly based on the Agent Cooperation Network (ACN) framework of Lianjia and attracting various franchise stores to join the network.
 Our findings reveal that this strategy substantially boosts revenues and alters consumer behaviors, particularly in the number of house tours facilitated by the brokerage.
-
-% WE ARE WORKING ON THIS
-
-These results underscore the necessity for a synergistic evolution of online and offline strategies in the real estate brokerage market.
-Furthermore, we find that the online consolidation effect is and the effect is
-
-Lastly, the network effect has cross stores according to the IPO prospectus, in year 2021, Lianjia is expected to achive approximately 76\% of cross stores transactions.
+The number of
+
+To conduct the
+
+\footnote{According to the IPO prospectus, in year 2021, Lianjia is expected to achive approximately 76\% of cross stores transactions.}
 
 % Accodring to 招股书，链家在2021的成交是cross store占比76\%
-
-Our research has several implications.
-Firstly, it indicates that with the advent of new technologies, the online consolidation effect is becoming increasingly important for real estate companies.
-This shift underscores the need for firms to enhance their digital strategies to remain competitive.
-Secondly, our findings have broader significance for other industries where online consolidation can potentially replace traditional offline clustering.
-For example, in the retail sector, online marketplaces such as Alibaba in China have significantly outpaced physical stores by consolidating various vendors into a single, accessible platform.
-
-By examining these dynamics, our research contributes to a deeper understanding of the evolving landscape of real estate brokerage in China.
-It provides valuable insights for policymakers and industry stakeholders aiming to enhance market efficiency and competitiveness.
-As the online consolidation effect continues to grow, our findings highlight the importance of adapting to this trend and evolving strategies accordingly.
-Specifically, transitioning from a bilateral brokerage model to a model where buyer and seller agencies are separated could be crucial for sustaining a competitive advantage in the real estate brokerage market.
-This strategic shift entails leveraging online platforms to integrate services and enhance transaction efficiency, thereby benefiting both consumers and firms.
-By disentangling the roles of buyer and seller agents, the market can reduce conflicts of interest, increase transparency, and improve overall market efficiency.
-This alignment with economic principles of specialization and efficiency further underscores the potential for significant gains in consumer welfare and firm profitability.
 
@@
 Section \ref{sec:mechanism_design} presents the main result of our finding.
+Section \ref{sec:network_effect} presents our measure to the local network effect and analyzes the platform-mediated consolidation on the local network effect.
 Finally, Section \ref{sec:conclusion} contains the discussion and concludes.
@@
 
-To determine the optimal radius of influence, this research employs a regression discontinuity (RD) design on the neighborhood level transaction data to examine the influential radius of offline real estate brokerages.
+To determine the optimal radius of influence, this research employs a RDD on the neighborhood level transaction data to examine the influential radius of offline real estate brokerages.
 The dependent variable in this analysis is the transaction revenue generated by Lianjia within a given community, while the independent variable is the community's proximity to the nearest Lianjia store.
@@
     \centering
-    \subfloat[RD plot with first order polynomial]{\includegraphics[width=0.5\textwidth]{../figures/RD_Plot_1st_Order.pdf}\label{fig:RD_Plot_1st_Order}}
+    \subfloat[RDD plot with first order polynomial]{\includegraphics[width=0.5\textwidth]{../figures/RD_Plot_1st_Order.pdf}\label{fig:RD_Plot_1st_Order}}
     \hfill % Adds horizontal space between figures
-    \subfloat[RD plot with second order polynomial]{\includegraphics[width=0.5\textwidth]{../figures/RD_Plot_2nd_Order.pdf}\label{fig:RD_Plot_2nd_Order}}
+    \subfloat[RDD plot with second order polynomial]{\includegraphics[width=0.5\textwidth]{../figures/RD_Plot_2nd_Order.pdf}\label{fig:RD_Plot_2nd_Order}}
     \hfill % Adds horizontal space between figures
-    \subfloat[RD plot with third order polynomial]{\includegraphics[width=0.5\textwidth]{../figures/RD_Plot_3rd_Order.pdf}\label{fig:RD_Plot_3rd_Order}}
-    \caption{RD design}
+    \subfloat[RDD plot with third order polynomial]{\includegraphics[width=0.5\textwidth]{../figures/RD_Plot_3rd_Order.pdf}\label{fig:RD_Plot_3rd_Order}}
+    \caption{RDD design}
     \label{fig:RD_design}
@@
 where $Y_{it}$ is the three main dependent variables, including $\log(\text{number})$, price concession, and $\log(\text{lead times})$, $density_{it}$ is the DBI, $\bf{X}_{it}$ is a set of control variables, including brokerage\_control Lag(hedonic\_control), transaction\_control and region\_control, while $\eta_{t} \times \text{bs\_code}_i$ is the time dummy variable interacting with the fixed effect of the business area, $\mu_i$ is the neighborhood fixed effect and $\epsilon_{it}$ is the random error term.
-The standard errors are clustered at the each business area level.\footnote{The business area is defined as a combination of multiple neighborhoods, which Lianjia designates as the primary divisions of the entire region.} The results are shown in Table \ref{tab:stylized_fact}.
+The standard errors are clustered at the each business area level.\footnote{The business area is defined as a zone with combination of multiple neighborhoods, which Lianjia designates as the primary divisions of the entire region.
+The Lianjia's definition of a zone is different and typically smaller than a zone defined by the government.} The results are shown in Table \ref{tab:stylized_fact}.
 
@@
 
-The effect of the strategy continues to grow in magnitude in the first period post treatment groups, with coefficients increasing from 1.1 to 1.4 across the quantiles.
+The effect of the strategy continues to grow in magnitude in the first period post treatment groups, with coefficients increasing from 1.1 to 1.4 across the quantiles and this effect is also significantly larger in magnitude when compared to the mean network effect of 2.18.
 This trend intensifies in the second period, with even greater changes observed in network clustering, indicating an escalating impact over time.
@@
 
-This paper has presented that in China's real estate market, brokerages' offline stores play an critical factor in transaction. In our baseline
-
-The result is consistent with the opinion that most platform like uber and lyft that does not have enough network strength and we confirmed that within smaller networks and clustering  \citep{10.1257/jep.28.2.3}
+In this paper, we demonstrated that in China's real estate market, brokerage offline stores play a critical role in transactions.
+Brokerages can adopt offline store expansion strategies to gain significant benefits.
+Specifically, our results indicate that the expansion of Lianjia's stores leads to an increase in the company's market share in the region by 4.8\% to 9.1\% and attracts more clients, as evidenced by an increase in number of house tours by 2.3\% to 3.1\%.
+Additionally, the study reveals that while offline store expansion does not significantly affect the transaction period, it facilitates better communication between buyers and sellers.
+% this is wrong
+
+Secondly, Lianjia's platform-mediated consolidation can also increase its transaction revenue by X% to Y% and boost the number of viewings by X% to Y%.
+However, this effect does not significantly impact communication, thus not affecting the price adjustment range or transaction cycle.
+
+Lastly, we established the presence of localized network effects and found that Lianjia's network effects are primarily characterized by local clustering, with moderate network strength.
+The platform-mediated consolidation helps Lianjia achieve greater localized network effects, which in turn, enhances its long-term influence in the market.
+
+%首先，我们的结果表明链家的门店扩张会导致链家在该地区的说如提高\%到\%，并会导致带看次数也就是吸引客人的数量增加\%到%，此外，研究表明线下门店扩张效应对于成交周期并没有显著影响，但是可以帮助买卖双方扩大信息的沟通，从而减少调价幅度。第二，链家的platform-mediated consolidation同样可以提高链家的成交收入在%到%，并会导致带看次数增加%到%，但是该效应并不会对人们的沟通产生影响，从而影响调价幅度和成交周期。最后，我们建立局部网络效应并且我们发现链家的网络效应主要是局部clustering的并且网络强度是moderate的，链家的platform-mediated consolidation可以帮助链家获得更大的局部网络效应，这将帮助链家在长期获得更大的影响力。
+
+Our research has several implications.
+Firstly, it indicates that with the advent of new technologies, the online consolidation effect is becoming increasingly important for real estate companies.
+This shift underscores the need for firms to enhance their digital strategies to remain competitive.
+Secondly, our findings have broader significance for other industries where online consolidation can potentially replace traditional offline clustering.
+For example, in the retail sector, online marketplaces such as Alibaba in China have significantly outpaced physical stores by consolidating various vendors into a single, accessible platform.
+
+This exercise is also of broad implications The result is consistent with the opinion that most platform like uber and lyft that does not have enough network strength and we confirmed that within smaller networks and clustering  \citep{10.1257/jep.28.2.3}.
+
+By examining these dynamics, our research contributes to a deeper understanding of the evolving landscape of real estate brokerage in China.
+It provides valuable insights for policymakers and industry stakeholders aiming to enhance market efficiency and competitiveness.
+As the online consolidation effect continues to grow, our findings highlight the importance of adapting to this trend and evolving strategies accordingly.
+Specifically, transitioning from a bilateral brokerage model to a model where buyer and seller agencies are separated could be crucial for sustaining a competitive advantage in the real estate brokerage market.
+This strategic shift entails leveraging online platforms to integrate services and enhance transaction efficiency, thereby benefiting both consumers and firms.
+By disentangling the roles of buyer and seller agents, the market can reduce conflicts of interest, increase transparency, and improve overall market efficiency.
+This alignment with economic principles of specialization and efficiency further underscores the potential for significant gains in consumer welfare and firm profitability.
 
@@
 The findings argue for a nuanced understanding of platform-based monopolization in real estate, suggesting that the successful integration of digital and physical domains can significantly enhance service delivery, market penetration, and overall system competitiveness, paving the way for a more adaptive and robust market system in the face of evolving challenges.
+
+% main structure:
+% 1. conclusions
+% 2. why the exercise is important
+% 3. policy implications
+% 4. further research directions
 
@@
 2017.
-Forecasting China’s GDP at the Pixel Level Using Nighttime Lights Time Series and Population Images.
+Forecasting China's GDP at the Pixel Level Using Nighttime Lights Time Series and Population Images.
 \textit{GIScience \& Remote Sensing}, 54(3), 407-425.
@@
 
+\bibitem[Peng(2023)]{peng_mortgage_2023}
+Peng, Y.
+2023.
+Mortgage Credit and Housing Markets.
+\textit{SSRN Electronic Journal}, Working Paper.
+Available at \url{https://ssrn.com/abstract=4537500} or \url{http://dx.doi.org/10.2139/ssrn.4537500}.
   \end{thebibliography}

### 2024-07-06 manuscript/main.tex
new file:   figures/typical_sample_lianjia.pdf 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

@@
 
-\begin{figure}
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.9\textwidth]{../figures/typical_sample_lianjia.pdf}
+  \caption{Sample of Lianjia's Offline Store with High Clustering}
+  \label{fig:typical_sample_lianjia}
+
+  This photo was taken in Chengdu, where Lianjia operates over 1,500 offline stores.
+It is common to see two stores located within a short distance of each other.
+The green store in the photo is one of Lianjia's offline stores.
+As you can see, across the street, there are two Lianjia stores, each managed by different store managers.
+\end{figure}
+
+\begin{figure}[H]
   \centering
@@
 
-\begin{figure}
+\begin{figure}[H]
     \centering

### 2024-07-06 manuscript/main.tex
update the result

@@
 In our analysis, we focus on several dependent variables: \emph{the natural logarithm of lianjia's transaction number}, \emph{the natural logarithm of home tours}, \emph{the natural logarithm of transaction period} and \emph{the price concession}.
+To take the natural logarithm without lossing information, we decided to add one to the number of house tours because some transactions are purely online-based.
+Additionally, we decided to winsorize the sample for the natural logarithms of Lianjia's transaction number, home tours, and transaction period at the 1st and 99th percentiles to mitigate the influence of extreme values.
+The price concession is defined as $|\frac{\text{transaction price} - \text{listing price}}{\text{listing price}}| \times 100\%$.
 To quantify Lianjia's impact, we begin by establishing a key stylized fact, which we develop a Density-Based Index (DBI) index to capture the Lianjia's offline stores' influential ratio.
@@
 Nevertheless, the presence of a self-selection bias in this dynamic entry factor necessitates the application of causal inference methods to better estimate the effect of Lianjia's offline stores.
-Consequently, we adopted the Difference-in-Difference (DiD) estimation to estimate the offline's store's entry's influence on the market performance.
+Consequently, we adopted the Difference-in-Difference (DID) estimation to estimate the offline's store's entry's influence on the market performance.
 From the market's performance, the Lianjia's offline's store's entry into the segmented market is an exogenous shock to the two-sided customers, where sellers are more likey to be attracted by the brokerage and buyers are also more likely to be attracted by the more listing information in the neighborhood.
-Although Lianjia's entry is not a randomized event, the DiD estimation method remains unbiased in estimating the entry effect by comparing variations in outcome variables before and after Lianjia's entry in the segmented market.
+Although Lianjia's entry is not a randomized event, the DiD estimation method remains consistent in estimating the entry effect by comparing variations in outcome variables before and after Lianjia's entry in the segmented market.
 
@@
 The results presented in the table \ref{tab:entry_effect} analyze the impact of Lianjia's offline stores entering segmented markets.
-Prior to Lianjia's entry ($pre_2$), there is no statistically significant effect on Lianjia's transaction properties, indicating that anticipation of Lianjia's entry does not influence these metrics.
-Post-entry ($entry$), there is a significant 9.1\% increase in revenue, suggesting a substantial boost in Lianjia's sales.
+Prior to Lianjia's entry ($pre_2$), there is no statistically significant effect on Lianjia's transaction properties, indicating that there is no anticipation effect for Lianjia's entry.
+In terms of the Lianjia's entry effect ($entry$), there is a significant 9.1\% increase in revenue, suggesting a substantial boost in Lianjia's sales.
 However, this effect decreases to 4.7\% in the subsequent period ($post_1$) and continues to diminish in the following periods ($post_2$ and $post_3$), indicating a gradual decline in Lianjia's performance after the initial entry period.
 Similarly, the number of house tours exhibits a significant 2.3\% increase during the entry period, followed by a 3.1\% increase in the first post-entry period.
-Nonetheless, this effect lessens in $post_2$, though it remains significant in $post_3$.
-This trend is attributed to the impact of the COVID-19 pandemic in 2020, which significantly affected the real estate market and brokerage's operation mode.
-
-In terms of the transaction period, the offline store's influence is always not significant, which suggests that the offline store's entry does not help to match the buyers and sellers in searching the houses, which is in line with the intuition that when platform is more mature, people's searching behavior is more likely to be online.
+Nonetheless, this effect diminishes in the second post-treatment period ($post_2$), though it continues to exhibit statistical significance in the third post-treatment period ($post_3$).
+% This trend is attributed to the impact of the COVID-19 pandemic in 2020, which significantly affected the real estate market and brokerage's operation mode.
+
+Regarding the transaction period, the influence of the offline store is consistently insignificant.
+This finding suggests that the entry of offline stores does not facilitate the matching of buyers and sellers in the housing market.
+This outcome aligns with the intuition that when platform and online information is readily accessible, individuals' search behavior tends to be predominantly online-based.
 Lastly, regarding price concessions, the entry of Lianjia's offline stores exhibits a 4.5\% positive effect.
@@
 
+We conducted a placebo test, as illustrated in Figure \ref{fig:placebo_entry}.
+For this test, we employed a neighborhood sample with randomly generated treatment effects.
+Additionally, to assess the impact of heteorogeniety across years, we generated interactions between year and the dummy random treatment effect to determine the significance of these effects.
+The results indicate that none of the treatment effects are statistically significant, suggesting that our estimates are not influenced by other confounding factors.
 % This delayed impact may be attributed to the offline stores gradually improving market transparency and information dissemination, which eventually leads to better price concessions.
@@
 Furthermore, when comparing the effect of platform consolidation with the entry effect of offline stores, the result indicates that the effect is substantially more pronounced and more continuous.
-These results underscore the superior efficacy of platform consolidation in enhancing market performance and provide compelling evidence for the strategic advantage of platformization over traditional offline expansion.
+These results underscore the superior efficacy of platform consolidation in enhancing market performance and provide compelling evidence for the strategic advantage of consolidation over traditional offline expansion.
 However, in terms of the transaction period, the platformization strategy does not exhibit a significant effect, indicating that platformization does not assist brokerages in facilitating better matching and negotiation between sellers and buyers.
@@
 The treatment effect becomes significant only after the first period, aligning with our empirical findings.
+We conducted a placebo test, as illustrated in Figure \ref{fig:placebo_platform} like our previous estimation of the offline store expansion.
+The test result also shows that there is no other confounding factors affecting our analysis.
 
@@
 
-In this paper, we demonstrated that in China's real estate market, brokerage offline stores play a critical role in transactions.
-Brokerages can adopt offline store expansion strategies to gain significant benefits.
+Our study highlights the transformative impact of Lianjia's strategic expansion in China's real estate brokerage industry through the implementation of the online-mediated consolidation strategy and the massive expansion of offline branches.
+Our empirical research demonstrates that Lianjia's approach, which seamlessly integrates online platforms with an extensive offline presence, significantly enhances revenue generation and influences consumer behavior through improved price concessions and increased number of house tours.
 Specifically, our results indicate that the expansion of Lianjia's stores leads to an increase in the company's market share in the region by 4.8\% to 9.1\% and attracts more clients, as evidenced by an increase in number of house tours by 2.3\% to 3.1\%.
-Additionally, the study reveals that while offline store expansion does not significantly affect the transaction period, it facilitates better communication between buyers and sellers.
-% this is wrong
-
-Secondly, Lianjia's platform-mediated consolidation can also increase its transaction revenue by X% to Y% and boost the number of viewings by X% to Y%.
-However, this effect does not significantly impact communication, thus not affecting the price adjustment range or transaction cycle.
-
+Additionally, the study reveals that while offline store expansion does not significantly affect the transaction period, but it facilitates better communication between buyers and sellers by contributing the price concession in transaction.
+Secondly, Lianjia's platform-mediated consolidation can also increase its transaction revenue by 2.9\% to 6.2\% and boost the number of house tours by 2.9\% to 3.0\%.
+However, this effect does not significantly impact communication, thus not affecting the price concession and transaction period.
 Lastly, we established the presence of localized network effects and found that Lianjia's network effects are primarily characterized by local clustering, with moderate network strength.
 The platform-mediated consolidation helps Lianjia achieve greater localized network effects, which in turn, enhances its long-term influence in the market.
-
-%首先，我们的结果表明链家的门店扩张会导致链家在该地区的说如提高\%到\%，并会导致带看次数也就是吸引客人的数量增加\%到%，此外，研究表明线下门店扩张效应对于成交周期并没有显著影响，但是可以帮助买卖双方扩大信息的沟通，从而减少调价幅度。第二，链家的platform-mediated consolidation同样可以提高链家的成交收入在%到%，并会导致带看次数增加%到%，但是该效应并不会对人们的沟通产生影响，从而影响调价幅度和成交周期。最后，我们建立局部网络效应并且我们发现链家的网络效应主要是局部clustering的并且网络强度是moderate的，链家的platform-mediated consolidation可以帮助链家获得更大的局部网络效应，这将帮助链家在长期获得更大的影响力。
 
@@
 For example, in the retail sector, online marketplaces such as Alibaba in China have significantly outpaced physical stores by consolidating various vendors into a single, accessible platform.
-
-This exercise is also of broad implications The result is consistent with the opinion that most platform like uber and lyft that does not have enough network strength and we confirmed that within smaller networks and clustering  \citep{10.1257/jep.28.2.3}.
+Lastly, this study demonstrates that, under the platform's consolidation effect, offline stores can enhance revenue and improve transaction efficiency.
+These findings can be extended to other similar fields, as discussed by \citep{10.1257/jep.28.2.3}.
 
@@
 
-The study of Lianjia's strategic expansion into China's real estate brokerage industry, particularly through the implementation of the ACN and the proliferation of offline branches, underscores a transformative impact on market dynamics and transaction efficiency.
-Our empirical research shows that Lianjia's approach, which seamlessly integrates online platforms with an extensive offline presence, significantly enhances revenue generation and influences consumer behavior, particularly through improved price concessions and increased home viewing.
-The study highlights the critical role of offline store information and community proximity in increasing transaction revenue and achieving market dominance, even in the face of increasing monopolization trends.
-Despite the adverse effects of the COVID-19 pandemic, which temporarily diluted the benefits of both customer base expansion and information dissemination, the resilience of physical stores emerges prominently.
-This resilience, coupled with the strategic leverage of online platforms, underscores the importance of a synergistic online-offline model in overcoming market challenges and maintaining competitive advantage.
-The findings argue for a nuanced understanding of platform-based monopolization in real estate, suggesting that the successful integration of digital and physical domains can significantly enhance service delivery, market penetration, and overall system competitiveness, paving the way for a more adaptive and robust market system in the face of evolving challenges.
+Future research could explore several potential directions.
+First, investigating the long-term impacts of online and offline integration on market competition and consumer behavior in various real estate markets globally could provide comparative insights.
+Second, examining the role of emerging technologies, such as artificial intelligence and blockchain, in further enhancing the efficiency and transparency of real estate transactions would be valuable.
+Third, assessing the socio-economic implications of platform-based monopolization, particularly in terms of access to affordable housing and regional economic disparities, could offer important policy implications.
+Lastly, exploring the adaptability of the online-offline integration model in other sectors, such as healthcare and education, could extend the applicability of these findings and contribute to a broader understanding of digital transformation across industries.
 

### 2024-07-06 manuscript/main.tex
modified:   analysis/final_analysis.do 	modified:   analysis/individual.do 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

@@
 
-\begin{figure}
+\begin{figure}[H]
   \centering
@@
 
-To assess the consolidation effect of the online platform, we treat the year Lianjia implemented the platform based consolidation strategy as an exogenous shock to the market.
-The platform consolidation strategy is majorly based on the Agent Cooperation Network (ACN) framework of Lianjia and attracting various franchise stores to join the network.
-Our findings reveal that this strategy substantially boosts revenues and alters consumer behaviors, particularly in the number of house tours facilitated by the brokerage.
-The number of
-
-To conduct the
-
-\footnote{According to the IPO prospectus, in year 2021, Lianjia is expected to achive approximately 76\% of cross stores transactions.}
-
-% Accodring to 招股书，链家在2021的成交是cross store占比76\%
-
-The remainder of the paper proceeds as follows.
-Section \ref{sec:literature_review} reviews the literature that is related to our research.
-Section \ref{sec:data} describes the study background and statistical summary.
-Section \ref{sec:mechanism_design} presents the main result of our finding.
-Section \ref{sec:network_effect} presents our measure to the local network effect and analyzes the platform-mediated consolidation on the local network effect.
-Finally, Section \ref{sec:conclusion} contains the discussion and concludes.
+To evaluate the effects of platform-mediated consolidation, we consider the year Lianjia implemented its platform-based consolidation strategy as an exogenous shock to the market.
+This strategy primarily revolves around the ACN framework of Lianjia and the incorporation of various franchise stores into the network.
+Our empirical analysis indicates that this strategy significantly increases revenues and enhances the attraction of buyers and sellers, particularly in the number of house tours facilitated by the brokerage.
+However, our findings suggest that the platform-based consolidation does not effectively reduce the transaction period nor does it promote price concessions.
+This contrasts with the offline expansion strategy, which demonstrates a positive impact on promoting price concessions.
+While the economic impact of the online-based consolidation strategy is not as pronounced as that of the offline expansion strategy, it remains economically significant.
+
+According to Lianjia's IPO prospectus, the company is projected to achieve approximately 76\% of cross-store transactions in 2021.
+This underscores the necessity of analyzing the network effects among Lianjia's offline stores and conducting a detailed examination of these effects.
+To assess Lianjia's network effect, we propose a measure of the local network effect by incorporating neighborhoods and offline stores, given that offline stores predominantly cluster around neighborhoods.
+We employ a Breadth-First Search (BFS) algorithm to construct the network formation and propose a gravity-based measure to evaluate the offline clustered network effect on neighborhoods.
+Additionally, we examine the impact of online-mediated consolidation on the offline stores' network effect on neighborhoods.
+Our findings reveal that Lianjia's offline stores exhibit a moderate network effect characterized by local clustering patterns.\footnote{\ref{fig:typical_sample_lianjia} shows a typical observation in Chengdu that two proximate Lianjia stores closely cooperate to manage property listings.
+In this arrangement, agents have the flexibility to bring customers for house tours.} Furthermore, the platform-mediated consolidation significantly enhances the network effect, indicating that this consolidation strategy effectively strengthens the network effect of Lianjia's offline stores.
+
+The structure of the paper is organized as follows.
+Section \ref{sec:literature_review} provides a comprehensive review of the relevant literature.
+Section \ref{sec:data} outlines the study's background, including a statistical summary and stylized facts.
+Section \ref{sec:mechanism_design} examines the impact of Lianjia's offline store expansion and platform-mediated consolidation on transaction properties..
+Section \ref{sec:network_effect} details the measurement of local network effects and analyzes the influence of platform-mediated consolidation on these effects.
+Finally, Section \ref{sec:conclusion} discusses the findings and offers concluding remarks.
 
@@
 To empirically estimate the effect of Lianjia's platform strategy, we consider an exogenous shock that occurred during our study period: Lianjia's implementation of a downstream consolidation strategy.
-This strategy involves the integration of offline stores with online platforms, leveraging the advantages of Lianjia's Agent Cooperation Network (ACN) strategy.
+This strategy involves the integration of offline stores with online platforms, leveraging the advantages of Lianjia's ACN strategy.
 The ACN strategy subdivides the entire process of buying and selling a house into distinct parts, with each part managed by a specific agent or store.

### 2024-07-07 manuscript/main.tex
update the change

@@
 
+However, how do we measure the network effect and understand its formation?
+What constitutes the formation of the network effect?
 Previous literature illustrates that the strength of network effects and network clustering can be crucial for the operation of platforms and long-run competitiveness \citep{WOS:000454186600016}.
@@
 The average effect of the network is 2.18 and the standard deviation is 2.55.
-This connection is in line with the reality in several ways.
+We detailed describes these indices in Appendix Section \ref{subsec:descriptions_clustering_indices}.\footnote{We also Describes other measures of network indices in Appendix Section \ref{subsec:other_indices_measures}.} This connection is in line with the reality in several ways.
 Firstly, cooperation between stores to complete a transaction is very common, and having more stores within the segmented market can contribute significantly to the transaction process as more efforts can be jointly made by different agents.
@@
     Q_y(\tau \mid X) & = \beta_0 + \beta_1(\tau) \text{Pre\_Treatment}_{it} + \beta_2(\tau) \text{Treatment}_{it} + \sum_{j=3}^5 \beta_j(\tau) \text{Post\_j\_Treatment}_{it} \\
-                     & + \alpha(\tau) \bf{X}_{it} + \mu_i + \eta_t + \epsilon{it}
+                     & + \alpha(\tau) \bf{X}_{it} + \mu_i + \eta_t + \epsilon_{it}
   \end{aligned}
@@
 
+\newpage
+
 \begin{figure}[H]
   \centering
-  \includegraphics[width=0.7\textwidth]{../figures/distribution_of_ten_cities.pdf}
+  \includegraphics[width=0.9\textwidth]{../figures/distribution_of_ten_cities.pdf}
   \caption{Distribution of Ten Cities's Brokerages Store Shares}
@@
 \end{figure}
+
+\newpage
 
@@
 
-Descriptions of the measures of the clustering coefficient effects:
+\newpage
+
+\section{Description of the network effect indices} \label{sec:network_effect_indices}
+
+\subsection{Descriptions of the clustering indices} \label{subsec:descriptions_clustering_indices}
+
+We also provide a descriptions of the measures of the clustering coefficient effects:
 
@@
 
+\subsection{Other Indices Measures} \label{subsec:other_indices_measures}
+
+We also consider other indices that describes the network formation using degree centrality, betweenness centrality, closeness centrality and page rank:
+
+Degree centrality measures the number of direct connections a node has to other nodes in the network. It is defined as:
+
+\begin{equation*}
+  C_D(v) = \frac{d(v)}{n - 1}
+\end{equation*}
+
+where $d(v)$ is the degree of node $v$, and $n$ is the total number of nodes in the network.
+A higher degree centrality indicates that a node has more direct connections and may be considered more influential or important within the network.
+
+Closeness centrality measures how close a node is to all other nodes in the network, based on the shortest paths. It is given by:
+
+\begin{equation*}
+  C_C(v) = \frac{n - 1}{\sum_{u \neq v} d(u, v)}
+\end{equation*}
+
+where $d(u, v)$ is the shortest path distance between nodes $u$ and $v$.
+A higher closeness centrality indicates that a node can reach other nodes more quickly, signifying a more central position within the network.
+
+PageRank is a measure of the importance of nodes in a network, originally developed for ranking web pages. It is calculated using the following iterative formula:
+
+\begin{equation*}
+  PR(v) = \frac{1 - d}{n} + d\sum_{u \in M(v)} \frac{PR(u)}{L(u)}
+\end{equation*}
+
+where $d$ is a damping factor (typically set to $0.85$), $M(v)$ is the set of nodes that link to $v$, $L(u)$ is the number of outbound links from node $u$.
+Nodes with high PageRank scores are considered to have high influence and are often central to the network's structure.
+
+\begin{table}[H]
+  \caption{Other Meausre Indices of the Network Effect}
+  \label{other:measures}
+  \input{../result_tables/other_indices_appendix.tex}
+\end{table}
 \end{document}
+
+% Freeman, L. C. (1977). A set of measures of centrality based on betweenness. Sociometry, 40(1), 35-41.
+% Newman, M. E. J. (2010). Networks: An Introduction. Oxford University Press.
+% Page, L., Brin, S., Motwani, R., & Winograd, T. (1999). The PageRank citation ranking: Bringing order to the web. Stanford InfoLab.

### 2024-07-08 manuscript/main.tex
new file:   analysis/placebo-test/.Rhistory 	new file:   analysis/placebo-test/conces_platform.dta 	new file:   figures/placebo_results/placebo_entry_concession.pdf 	new file:   figures/placebo_results/placebo_entry_lead.pdf 	new file:   figures/placebo_results/placebo_entry_num.pdf 	new file:   figures/placebo_results/placebo_entry_period.pdf 	new file:   figures/placebo_results/placebo_plat_concession.pdf 	new file:   figures/placebo_results/placebo_plat_lead.pdf 	new file:   figures/placebo_results/placebo_plat_num.pdf 	new file:   figures/placebo_results/placebo_plat_period.pdf 	deleted:

@@
 \pgfplotsset{compat=1.14}
-\usepackage{longtable}
+\usepackage{subcaption}
 \pgfplotsset{every axis label/.append style={font=\tiny}}
@@
 
-We conducted a placebo test, as illustrated in Figure \ref{fig:placebo_entry}.
+We conducted a placebo test, as illustrated in Figure \ref{fig:placebo_concession_entry}.
 For this test, we employed a neighborhood sample with randomly generated treatment effects.
@@
       \caption{Robustness Check of Online Consolidation Effect}
-      \label{tab:heter_platform_did}
+      \label{tab:heter_platform_did_1}
       \input{../result_tables/heter_platform_did_1.tex}
@@
       \caption{Robustness Check of Online Consolidation Effect (Continued)}
-      \label{tab:heter_platform_did}
+      \label{tab:heter_platform_did_2}
       \input{../result_tables/heter_platform_did_2.tex}
@@
 The treatment effect becomes significant only after the first period, aligning with our empirical findings.
-We conducted a placebo test, as illustrated in Figure \ref{fig:placebo_platform} like our previous estimation of the offline store expansion.
+We conducted a placebo test, as illustrated in Figure \ref{fig:placebo_concession_plat} like our previous estimation of the offline store expansion.
 The test result also shows that there is no other confounding factors affecting our analysis.
@@
 
+\section{Placebo Test}
+
+\begin{figure}[ht]
+  \centering
+  \subfloat[Placebo Test to transaction number]{\includegraphics[width=0.5\textwidth]{../figures/placebo_results/placebo_entry_num.pdf}\label{fig:placebo_num_entry}}
+  \subfloat[Placebo Test to number of house tours]{\includegraphics[width=0.5\textwidth]{../figures/placebo_results/placebo_entry_lead.pdf}\label{fig:placebo_lead_entry}}
+  \hfill % Adds horizontal space between figures
+  \subfloat[Placebo Test to transaction period]{\includegraphics[width=0.5\textwidth]{../figures/placebo_results/placebo_entry_period.pdf}\label{fig:placebo_period_entry}}
+  \subfloat[Placebo Test to price concession]{\includegraphics[width=0.5\textwidth]{../figures/placebo_results/placebo_entry_concession.pdf}\label{fig:placebo_concession_entry}}
+  \caption{Placebo Test to Entry Effect}
+  \label{fig:placebo_test_entry}
+\end{figure}
+
+\begin{figure}[ht]
+  \centering
+  \subfloat[Placebo Test to transaction number]{\includegraphics[width=0.5\textwidth]{../figures/placebo_results/placebo_plat_num.pdf}\label{fig:placebo_num_plat}}
+  \subfloat[Placebo Test to number of house tours]{\includegraphics[width=0.5\textwidth]{../figures/placebo_results/placebo_plat_lead.pdf}\label{fig:placebo_lead_plat}}
+  \hfill % Adds horizontal space between figures
+  \subfloat[Placebo Test to transaction period]{\includegraphics[width=0.5\textwidth]{../figures/placebo_results/placebo_plat_period.pdf}\label{fig:placebo_period_plat}}
+  \subfloat[Placebo Test to price concession]{\includegraphics[width=0.5\textwidth]{../figures/placebo_results/placebo_plat_concession.pdf}\label{fig:placebo_concession_plat}}
+  \caption{Placebo Test to Platform-Mediated Consolidation Effect}
+  \label{fig:placebo_test_plat}
+\end{figure}
+
 \section{Description of the network effect indices} \label{sec:network_effect_indices}
@@
 Nodes with high PageRank scores are considered to have high influence and are often central to the network's structure.
+
+The results also indicate that the local network effect of Lianjia tends to be sparse and the network is not well-connected.
+The network effect is primarily characterized by local clustering, with moderate network strength.
+
+\end{document}
 
@@
 \end{table}
-\end{document}
 

### 2024-07-08 plotting/placebo_plot.R

@@ -3,43 +3,110 @@ library(haven)
 library(ggplot2)
 library(extrafont)
 library(ggthemes)
+library(showtext)
 
 name_figures <- c(
-    ""
+  "placebo_entry_num.pdf",
+  "placebo_entry_lead.pdf",
+  "placebo_entry_period.pdf",
+  "placebo_entry_concession.pdf"
 )
 
+name_figures2 <- c(
+    "placebo_plat_num.pdf",
+    "placebo_plat_lead.pdf",
+    "placebo_plat_period.pdf",
+    "placebo_plat_concession.pdf"
+)
 
+# This is for Windows System
 loadfonts(device = "win")
+
+# for LINUX system:
+# Enable showtext to automatically use the registered fonts
+showtext_auto()
+
+# Manually add the Times New Roman font
+font_add("Times New Roman", 
+         regular = "/usr/share/fonts/truetype/msttcorefonts/times.ttf",
+         bold = "/usr/share/fonts/truetype/msttcorefonts/timesbd.ttf",
+         italic = "/usr/share/fonts/truetype/msttcorefonts/timesi.ttf",
+         bolditalic = "/usr/share/fonts/truetype/msttcorefonts/timesbi.ttf")
+# Windows System
 setwd("E:/umich/RealEstateBrokerage/analysis/placebo-test")
-data <- read_dta("lead_entry_effect.dta")
+# Linux System
+setwd("/home/xuyuan/Desktop/RealEstateBrokerage/analysis/placebo-test")
 
-means <- colMeans(data)
-sds <- apply(data, 2, sd)
-
-names_list <- c('pre2', 'pre1', 'entry', 'post1', 'post2', 'post3')
-
-plot_data <- data.frame(
-    Coefficient = factor(names_list, levels = names_list),
-    Mean = means,
-    SD = sds
-)
+file_names <- c('num_entry_effect.dta', 'lead_entry_effect.dta', 'period_entry_effect.dta', 'conces_entry_effect.dta')
+file_names2 <- c('num_platform.dta', 'lead_platform.dta', 'period_platform.dta', 'conces_platform.dta')
 
 
 
-result <- ggplot(plot_data, aes(x = Coefficient, y = Mean)) +
-    geom_point(size = 3, color = "darkblue") +
-    geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = 0.2) +
-    theme_classic(base_family = "Times New Roman") +  # Use Arial font
[…]

### 2024-07-08 manuscript/main.tex
new file:   Plotting of Sample Distribution/GpMessages/2616494096400 	new file:   Plotting of Sample Distribution/ImportLog/55c4de46096847c88b832e57b051473d_Import.xml 	new file:   Plotting of Sample Distribution/ImportLog/9cdfaa0a4cd74623bd00534f923a7525_Import.xml 	new file:   Plotting of Sample Distribution/ImportLog/b6386bc1a434430fbca275b5770f744a_Import.xml 	new file:   Plotting of Sample Distribution/Plotting of Sample Distribution.aprx 	new file:   Plotting of Sample Distribution/Plotting of Sample Distribution.atbx 	new file:   Plotting of Sample Distribution/Plotting of Sample Distri

--- 2024-07-07 manuscript/main.tex
@@
 \pgfplotsset{compat=1.14}
-\usepackage{longtable}
 \pgfplotsset{every axis label/.append style={font=\tiny}}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% APPENDIX
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\section{Appendix Tables and Figures}
+\section{Additional Descriptions of Data} \label{sec:appendix_data}
 
@@
 As you can see, across the street, there are two Lianjia stores, each managed by different store managers.
+This phenomenon is very common in large Chinese cities and can be found in many markets, see for example Figure \ref{fig:typical_layout_Beijing}.
 \end{figure}
@@
 \newpage
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.9\textwidth]{../figures/typical_layout_beijing.pdf}
+  \caption{Sample of Lianjia's Offline Stores in Beijing}
+  \label{fig:typical_layout_Beijing}
+
+This figure illustrates the spatial distribution of Lianjia's offline stores in Beijing for the year 2021.
+The data reveals a significant clustering of stores around major residential buildings, demonstrating a high degree of localization within the real estate brokerage market.
+This pattern is indicative of the competitive dynamics and agglomeration economies prevalent in the Chinese real estate sector, where proximity to key infrastructure.
+The data source is from AutoNavi Map.
+\end{figure}
+
+\input{../figures/distribution_of_hp_and_broker.tex}
 
@@
   \label{fig:distribution_store_shares}
+
   Note: the x-axis is city's name and the y-axis is the offline brokerage's stores share in the city. The data source is from AutoNavi Map.
@@
 
-\newpage
-
+\clearpage
+
+\section{Additional RDD Robustness Tests} \label{sec:additional_rdd}
 % \input{tab_tex/other-regressions.tex}
 
-\input{../figures/distribution_of_hp_and_broker.tex}
-
+Table \ref{}
 \input{../result_tables/donut_robust.tex}
@@
 
+\section{Placebo Test}
+
+\begin{figure}[H]
+  \centering
+  \subfloat[Placebo Test to transaction number]{\includegraphics[width=0.45\textwidth]{../figures/placebo_results/placebo_entry_num.pdf}\label{fig:placebo_num_entry}}
+  \subfloat[Placebo Test to number of house tours]{\includegraphics[width=0.45\textwidth]{../figures/placebo_results/placebo_entry_lead.pdf}\label{fig:placebo_lead_entry}}
+  \hfill % Adds horizontal space between figures
+  \subfloat[Placebo Test to transaction period]{\includegraphics[width=0.45\textwidth]{../figures/placebo_results/placebo_entry_period.pdf}\label{fig:placebo_period_entry}}
+  \subfloat[Placebo Test to price concession]{\includegraphics[width=0.45\textwidth]{../figures/placebo_results/placebo_entry_concession.pdf}\label{fig:placebo_concession_entry}}
+  \caption{Placebo Test to Entry Effect}
+  \label{fig:placebo_test_entry}
+
+  Note: The x-axis is the coefficient of the
+
+  the model is described in Equation \eqref{eq:entry_effect}
+  \end{figure}
+
+\begin{figure}[H]
+  \centering
+  \subfloat[Placebo Test to transaction number]{\includegraphics[width=0.45\textwidth]{../figures/placebo_results/placebo_plat_num.pdf}\label{fig:placebo_num_plat}}
+  \subfloat[Placebo Test to number of house tours]{\includegraphics[width=0.45\textwidth]{../figures/placebo_results/placebo_plat_lead.pdf}\label{fig:placebo_lead_plat}}
+  \hfill % Adds horizontal space between figures
+  \subfloat[Placebo Test to transaction period]{\includegraphics[width=0.45\textwidth]{../figures/placebo_results/placebo_plat_period.pdf}\label{fig:placebo_period_plat}}
+  \subfloat[Placebo Test to price concession]{\includegraphics[width=0.45\textwidth]{../figures/placebo_results/placebo_plat_concession.pdf}\label{fig:placebo_concession_plat}}
+  \caption{Placebo Test to Platform-Mediated Consolidation Effect}
+  \label{fig:placebo_test_plat}
+
+  Note: The x-axis is the coefficient of the
+
+  the model is described in Equation \eqref{eq:acn_assessment}
+
+\end{figure}
+
+\newpage
+
 \section{Description of the network effect indices} \label{sec:network_effect_indices}

### 2024-07-08 manuscript/main.tex
modified:   analysis/final_analysis.do 	modified:   analysis/individual.do 	new file:   analysis/robustness_check.do 	deleted:    archive/.archieved.do 	deleted:    archive/RD design archived.Rmd 	deleted:    archive/analysis-2.do 	deleted:    archive/analysis.do 	deleted:    archive/analysis_1km.do 	deleted:    archive/clean_1km.do 	deleted:    archive/final_analysis.do 	deleted:    archive/quantile-regression.R 	deleted:    archive/quickly_filter_good_result.do 	deleted:    archive/some archived words.tex 	deleted:    archive/working on district level original.do 	deleted:    archive/working

@@
 Additionally, \citet{qu_identifying_2021} highlights the moderating role of broker commissions in disseminating information during transactions, facilitating more efficient home sales.
-Other related literature includes \citep{doi:10.1080/10527001.2021.2016340, doi:10.1080/10835547.1996.12090852}.
+Lastly, \citet{AGARWAL2024103668} utilized second-hand real estate transaction data from Beijing to demonstrate that real estate agents may significantly contribute to the formation of Yin-Yang contracts.
+They quantified the magnitude of the resulting tax evasion, attributing it to the learning-by-doing effect and peer influence among agents.
+However, their study lacked a spatial analysis component that would consider the local network effects.
+Other related literature includes \citep{doi:10.1080/10527001.2021.2016340, d082a2db-5cce-33f2-87c4-9cb020cc6666, doi:10.1080/10835547.1996.12090852}.
 
@@
 
+  \bibitem[Agarwal et al.(2024)]{AGARWAL2024103668}
+Agarwal, S., Kuang, W., Wang, L., and Yang, Y. 2024. The role of agents in fraudulent activities: Evidence from the housing market in Beijing. \textit{Journal of Urban Economics}, 142, 103668.
+
   \bibitem[Armstrong(2006)]{Armstrong2006}
@@
 
-\begin{table}[H]
-  \begin{center}
-    \begin{scriptsize}
-    \caption{Robustness Check By HHI Index}
-    \label{tab:dynamic_hhi}
-    \input{../result_tables/robust_hhi.tex}
-
-    \end{scriptsize}
-  \end{center}
-\end{table}
-
 \clearpage

### 2024-07-08 archive/quantile-regression.R

@@ -1,106 +1,0 @@
-# library(qte) # this is the implementation of CIC model and we do not need it right now
-
-# if you are using the caen version's R
-# first install R-tools from https://cran.rstudio.com/bin/windows/Rtools/history.html
-# this CAEN version is 4.0.2 and install it to the zxuyuan
-# install.packages("rlang")
-# install.packages("lifecycle")
-# and then install other packages
-library(lfe)
-library(haven)
-library(dplyr)
-library(quantreg)
-library(fixest)
-set.seed(130)
-getwd()
-
-setwd('C:/Users/zxuyuan/Downloads')
-# setwd('/home/xuyuan/Desktop/2024 summer/real estate paper/oritignal cleaning/RealEstateBrokerage')
-data <- read_dta("template.dta")
-
-# now here we consider the CIC model where the dependent variable is the influence
-# and the treatment effect is a set of variables indicating whether the online 
-# consolidation spread the influence effect. I have already know that the treatment 
-# effect can make the influence effect heterogenous because treatment effect can 
-# have different heterogenous effect on various level of the influence, 
-# and therefore, we cannot use traditional DID, then we have to use CIC and the 
-# expected result should be a quantiled treatment effect on various level of the 
-# influence. Give me the code in R.
-
-pre_policy_data <- data[data$year %in% c(2016, 2017), ]
-post_policy_data <- data[data$year %in% c(2018, 2019, 2020, 2021, 2022), ]
-
-hedonic_control <- c("jiadian", "kind", "hotel", "shop_mall", "museum", "old", "ktv", "mid", "prim", "west_food", "super", "sub", "park")
-transaction_control <- c("area", "bedroom", "toilet", "house_age", "floor_level", "green_ratio", "total_building", "total_floor_number", "living_room", "elevator_ratio", "kitchen", "floor_ratio", "total_resident")
-region_control <- c("pm25", "pop", "light")
-brokerage_control <- c("non_online_effect", "ln_nego_changes", "ln_negotiation_period")
-other_main_variables <- c("broker_410", "ln_end_price", "ln_watch_people", "ln_watch_time")
-control_variables <- c(other_main_variables, brokerage_control, hedonic_control, transaction_control, region_control)
-control_formula <- paste(control_variables, collapse = " + ")
-dependent_variable <- c("pre1_treatment", "treatment", "post1_treatment", "post2_treatment", "post3_treatment")
-quantiles <- c(0.05, 0.95, 0.05)
-
[…]

### 2024-07-08 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

@@
 This is corroborated by evidence suggesting that properties listed with lower commission rates not only sell less frequently but also take longer to sell \citep{10.1257/app.20160214}.
+Additionally, studies have documented that brokerages may adopt discriminatory strategies, steering minorities into neighborhoods with lower economic opportunities and higher exposures to crime and pollution, thereby contributing to persistent social and economic inequalities in the United States \citep{RePEc:ucp:jpolec:doi:10.1086/720140}.
 The advent of online platforms has significantly altered the landscape of real estate transactions.
@@
 Available at \url{https://ssrn.com/abstract=4537500} or \url{http://dx.doi.org/10.2139/ssrn.4537500}.
+
+\bibitem[Christensen and Timmins(2022)]{RePEc:ucp:jpolec:doi:10.1086/720140}
+Christensen, P., and C. Timmins. 2022. Sorting or Steering: The Effects of Housing Discrimination on Neighborhood Choice. \textit{Journal of Political Economy}, 130(8), 2110-2163.
   \end{thebibliography}
@@
 
+\section{Codebook} \label{sec:codebook}
+
+\begin{table}[H]
+  \begin{center}
+    \begin{scriptsize}
+    \caption{Codebook}
+    \label{tab:codebook}
+    \input{../result_tables/code_book_table.tex}
+
+    \end{scriptsize}
+  \end{center}
+\end{table}
+
 \section{Additional Descriptions of Data} \label{sec:appendix_data}
@@
 \clearpage
+
+Section{Additional Robustness Check of Main Results} \label{sec:additional_robustness}
 
@@
 
-\begin{table}[H]
-  \begin{center}
-    \begin{scriptsize}
-    \caption{Codebook}
-    \label{tab:codebook}
-    \input{../result_tables/code_book_table.tex}
-
-    \end{scriptsize}
-  \end{center}
-\end{table}
-
 \newpage
 
-\section{Placebo Test}
+\subsection{Placebo Test} \label{subsec:placebo_test}
 
@@
 
+\subsection{Alternative Methods} \label{subsec:alternative_methods}
+
 % Freeman, L. C. (1977). A set of measures of centrality based on betweenness. Sociometry, 40(1), 35-41.

### 2024-07-08 manuscript/main.tex
update the robustness check

@@
 
+\subsection{Additional Robustness Check for the Offline Expansion Effect} \label{subsec:expansion_effect}
+
+\begin{table}
+  \begin{center}
+    \begin{scriptsize}
+      \caption{Robustness Check of Lianjia's Offline Expansion Effect}
+      \label{tab:robustness_check_additional_1}
+      \input{../result_tables/entry_robust_adding_variables_1.tex}
+
+    Note: we omit all the control variables in the regression model, and detailed descriptions can be seen from Table \ref{tab:statistical_district} and Table \ref{tab:statistical_individual}.
+    \end{scriptsize}
+  \end{center}
+\end{table}
+
+\begin{table}
+  \begin{center}
+    \begin{scriptsize}
+      \caption{Robustness Check of Lianjia's Offline Expansion Effect (Continued)}
+      \label{tab:robustness_check_additional_2}
+      \input{../result_tables/entry_robust_adding_variables_2.tex}
+
+    Note: we omit all the control variables in the regression model, and detailed descriptions can be seen from Table \ref{tab:statistical_district} and Table \ref{tab:statistical_individual}.
+    \end{scriptsize}
+  \end{center}
+\end{table}
+
+\begin{table}
+  \begin{center}
+    \begin{scriptsize}
+      \caption{Robustness Check of Lianjia's Platform-Mediated Consolidation Effect}
+      \label{tab:robustness_check_platform_1}
+      \input{../result_tables/plat_robust_adding_variables_1.tex}
+
+    Note: we omit all the control variables in the regression model, and detailed descriptions can be seen from Table \ref{tab:statistical_district} and Table \ref{tab:statistical_individual}.
+    \end{scriptsize}
+  \end{center}
+\end{table}
+
+\begin{table}
+  \begin{center}
+    \begin{scriptsize}
+      \caption{Robustness Check of Lianjia's Platform-Mediated Consolidation Effect (Continued)}
+      \label{tab:robustness_check_platform_2}
+      \input{../result_tables/plat_robust_adding_variables_2.tex}
+
+    Note: we omit all the control variables in the regression model, and detailed descriptions can be seen from Table \ref{tab:statistical_district} and Table \ref{tab:statistical_individual}.
+    \end{scriptsize}
+  \end{center}
+\end{table}
+
 \clearpage

### 2024-07-09 analysis/RD design analysis.Rmd
modified:   analysis/RD design analysis.Rmd 	deleted:    analysis/RD-design-analysis.tex 	deleted:    analysis/donut_robust.tex 	modified:   figures/RD_Plot_1st_Order.pdf 	new file:   figures/RD_Plot_1st_Order_robust.pdf 	modified:   figures/RD_Plot_2nd_Order.pdf 	new file:   figures/RD_Plot_2nd_Order_robust.pdf 	modified:   figures/RD_Plot_3rd_Order.pdf 	new file:   figures/RD_Plot_3rd_Order_robust.pdf 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscr

--- 2024-06-09 analysis/RD design analysis.Rmd
@@
 working_directory <-"E:/umich/RealEstateBrokerage"
+set.seed(130)
 ```
@@
 ```{r}
-h = 0.066
+ci_level = 95
+h = 0.063
 cutoff = 0.41
 running_var = panel_data$nearest_store_distances
-
+running_var <- as.numeric(running_var)
 filtered_data <- panel_data[abs(running_var - cutoff) <= h, ]
@@
 pdf("RD_Plot_1st_Order.pdf", width = 8, height = 4) # Adjust the width and height as needed
+rdplot(y = filtered_data$income, 
+       x = filtered_data$nearest_store_distances, 
+       c = cutoff, nbins = 40, p = 1,
+       title = "RD-plot 1st order polynomial",
+       x.label = "Nearest distance to Lianjia's stores",
+       y.label = "Log of income in the community", col.dots = "blue", kernel = "triangular")
+dev.off() # Close the PDF device
+
+# Export the second RD plot to its own PDF file
+pdf("RD_Plot_2nd_Order.pdf", width = 8, height = 4) # Adjust the width and height as needed
+rdplot(y = filtered_data$income, 
+       x = filtered_data$nearest_store_distances, 
+       c = cutoff, nbins = 40, p = 2,
+       title = "RD-plot 1st order polynomial",
+       x.label = "Nearest distance to Lianjia's stores",
+       y.label = "Log of income in the community", col.dots = "blue", kernel = "triangular")
+dev.off() # Close the PDF device
+
+# Export the third RD plot to its own PDF file
+pdf("RD_Plot_3rd_Order.pdf", width = 8, height = 4) # Adjust the width and height as needed
+rdplot(y = filtered_data$income, 
+       x = filtered_data$nearest_store_distances, 
+       c = cutoff, nbins = 40, p = 3,
+       title = "RD-plot 3rd order polynomial",
+       x.label = "Nearest distance to Lianjia's stores",
+       y.label = "Log of income in the community", col.dots = "blue", kernel = "triangular")
+dev.off() # Close the PDF device
+```
+
+```{r}
+ci_level = 95
+h = 0.063
+cutoff = 0.41
+running_var = panel_data$nearest_store_distances
+running_var <- as.numeric(running_var)
+filtered_data <- panel_data[abs(running_var - cutoff) <= h, ]
+
+# Export the first RD plot to its own PDF file
+pdf("RD_Plot_1st_Order_robust.pdf", width = 8, height = 4) # Adjust the width and height as needed
 rdplot(y = filtered_data$ln_income, 
@@
        x.label = "Nearest distance to Lianjia's stores",
-       y.label = "Log of income in the community")
+       y.label = "Log of income in the community", col.dots = "blue", kernel = "triangular")
 dev.off() # Close the PDF device
@@
 # Export the second RD plot to its own PDF file
-pdf("RD_Plot_2nd_Order.pdf", width = 8, height = 4) # Adjust the width and height as needed
+pdf("RD_Plot_2nd_Order_robust.pdf", width = 8, height = 4) # Adjust the width and height as needed
 rdplot(y = filtered_data$ln_income, 
@@
        c = cutoff, nbins = 40, p = 2,
-       title = "RD-plot 2nd order polynomial",
+       title = "RD-plot 1st order polynomial",
        x.label = "Nearest distance to Lianjia's stores",
-       y.label = "Log of income in the community")
+       y.label = "Log of income in the community", col.dots = "blue", kernel = "triangular")
 dev.off() # Close the PDF device
@@
 # Export the third RD plot to its own PDF file
-pdf("RD_Plot_3rd_Order.pdf", width = 8, height = 4) # Adjust the width and height as needed
+pdf("RD_Plot_3rd_Order_robust.pdf", width = 8, height = 4) # Adjust the width and height as needed
 rdplot(y = filtered_data$ln_income, 
@@
        x.label = "Nearest distance to Lianjia's stores",
-       y.label = "Log of income in the community")
+       y.label = "Log of income in the community", col.dots = "blue", kernel = "triangular")
 dev.off() # Close the PDF device
+```
+
+```{r}
+bw_methods <- c("mserd", "cerrd")
+kernel_list <- c("uniform", "triangular")
+results_list <- list()
+counter <- 1
+for (bw_method in bw_methods) {
+    for (kernel_in in kernel_list){
+        result <- rdrobust(y = panel_data$income, x = panel_data$nearest_store_distances, 
+                     c = 0.41,
+                     p = 1, 
+                     bwselect = bw_method, kernel = kernel_in)
+
+        effective_obs <- sum(result$N_h)
+
+        results_list[[counter]] <- data.frame(
+        Method = bw_method,
+        Kernel = kernel_in,
+        Estimate = format(result$coef[1], digits = 3, scientific = FALSE),
+        SE = format(result$se[1], digits = 3, scientific = FALSE),
+        Z = format(result$z[1], digits = 3, scientific = FALSE),
+        PValue = format(result$pv[1], digits = 3, scientific = FALSE),
+        Bandwidth = format(result$bws[1], digits = 3, scientific = FALSE),
+        EffectiveObs = effective_obs
+    )
+        counter <- counter + 1
+    }
+}
+results <- do.call(rbind, results_list)
+latex_code <- print(xtable(results, 
+                           caption = "RD Estimates with Different Bandwidth Selection Methods and Kernels", 
+                           label = "tab:rd_bandwidth_kernel_results"), 
+                    include.rownames = FALSE, 
+                    type = "latex",
+                    print.results = FALSE)
+write(latex_code, file = paste(working_directory , "result_tables/rdd_result_summary.tex", sep='/'))
+print(results)
+```
+
+```{r}
+result <- rdrobust(y = panel_data$income, x = panel_data$nearest_store_distances, 
+                     c = 0.41,
+                     p = 1, 
+                     bwselect = "mserd", kernel = "triangular")
+```
+
+```{r}
+print(result)
 ```
@@
 latex_code <- print(xtable(results, 
-                           caption = "RD Estimates with Different Bandwidth Selection Methods and Kernels", 
-                           label = "tab:rd_bandwidth_kernel_results"), 
+                           caption = "RD Estimates with Different Bandwidth Selection Methods and Kernels (robust method with log(income))", 
+                           label = "tab:rd_bandwidth_kernel_results_robust"), 
                     include.rownames = FALSE, 
@@
                     print.results = FALSE)
-write(latex_code, file = paste(working_directory , "result_tables/rdd_result_summary.tex", sep='/'))
+write(latex_code, file = paste(working_directory , "result_tables/rdd_result_summary_robust.tex", sep='/'))
 print(results)
@@
 If they don’t, it strengthens the case for a true treatment effect.
+4. The result should robust to little changes across the bandwidth.
 
@@
 ```{r}
-cutoff
-donut_width <- 0.011
-panel_data_donut <- panel_data[!(panel_data$nearest_store_distances >= (cutoff - donut_width) & 
-                                 panel_data$nearest_store_distances <= (cutoff + donut_width)),]
-result_donut <- rdrobust(y = panel_data_donut$ln_income, 
-                         x = panel_data_donut$nearest_store_distances, 
-                         c = cutoff,
-                        p = 1, h = 0.066, b = 0.135)
-pander(cbind(result_donut$coef, result_donut$pv))
-print(result_donut)
+panel_data <- as.data.frame(panel_data)
+panel_data$nearest_store_distances <- as.numeric(panel_data$nearest_store_distances)
 ```
@@
 ```{r}
+original_model_num <- 30532
+
 perform_rd_analysis <- function(cutoff, donut_width, h, b) {
@@
   # run the rdrobust result
-  result_donut <- rdrobust(y = panel_data_donut$ln_income, 
+  result_donut <- rdrobust(y = panel_data_donut$income, 
                            x = panel_data_donut$nearest_store_distances, 
                            c = cutoff,
-                           p = 1, h = h, b = b)
+                           p = 1, h = h, b = b, kernel = "triangular")
+  effective_obs <- sum(result_donut$N_h)
+  drop_ratio <- (original_model_num - effective_obs) / original_model_num 
+  drop_ratio_percentage <- round(drop_ratio * 100, 2)
   # return the coefficient and the p value
-  conventional <- c("Conventional", result_donut$coef[1, 1], result_donut$se[1, 1], result_donut$pv[1, 1])
-  bias_corrected <- c("Bias-Corrected", result_donut$coef[2, 1], result_donut$se[2, 1], result_donut$pv[2, 1])
+  conventional <- c("Conventional", result_donut$coef[1, 1], result_donut$se[1, 1], result_donut$pv[1, 1], drop_ratio_percentage)
+  bias_corrected <- c("Bias-Corrected", result_donut$coef[2, 1], result_donut$se[2, 1], result_donut$pv[2, 1], drop_ratio_percentage)
   robust <- c("Robust", 
@@
               format(result_donut$se[3, 1], digits = 3, scientific = FALSE), 
-              format(result_donut$pv[3, 1], digits = 3, scientific = FALSE))
-
+              format(result_donut$pv[3, 1], digits = 3, scientific = FALSE), drop_ratio_percentage)
   # combine the results
   result_table <- rbind(conventional, bias_corrected, robust)
-  colnames(result_table) <- c("Method", "Coef", "SE", "p-value")
+  colnames(result_table) <- c("Method", "Coef", "SE", "p-value", "Drop Ratio (%)")
   return(result_table)
@@
 cutoff = 0.41
-donut_widths <- c(0.01, 0.0125, 0.015, 0.0175, 0.02, 0.0225, 0.025)
+donut_widths <- c(0.005, 0.0075, 0.01, 0.0125, 0.015, 0.0175, 0.02)
 results <- list()
@@
 for (donut in donut_widths) {
-  result <- perform_rd_analysis(cutoff, donut, 0.066, 0.135)
+  result <- perform_rd_analysis(cutoff, donut, 0.063, 0.125)
   results[[paste0("donut_", donut)]] <- result
@@
 ```{r}
+results
+```
+
+```{r}
+original_model_num <- 30532
 perform_rd_analysis <- function(cutoff, donut_width, h, b) {
@@
   # run the rdrobust result
-  result_donut <- rdrobust(y = panel_data_donut$ln_income, 
+  result_donut <- rdrobust(y = panel_data_donut$income, 
                            x = panel_data_donut$nearest_store_distances, 
                            c = cutoff, covs = panel_data_donut[, control_variables],
-                           p = 1, h = h, b = b)
+                           p = 1, h = h, b = b, kernel = "triangular")
+  effective_obs <- sum(result_donut$N_h)
+  drop_ratio <- (original_model_num - effective_obs) / original_model_num 
+  drop_ratio_percentage <- round(drop_ratio * 100, 2)
   # return the coefficient and the p value
-  conventional <- c("Conventional", result_donut$coef[1, 1], result_donut$se[1, 1], result_donut$pv[1, 1])
-  bias_corrected <- c("Bias-Corrected", result_donut$coef[2, 1], result_donut$se[2, 1], result_donut$pv[2, 1])
+  conventional <- c("Conventional", result_donut$coef[1, 1], result_donut$se[1, 1], result_donut$pv[1, 1], drop_ratio_percentage)
+  bias_corrected <- c("Bias-Corrected", result_donut$coef[2, 1], result_donut$se[2, 1], result_donut$pv[2, 1], drop_ratio_percentage)
   robust <- c("Robust", 
@@
               format(result_donut$se[3, 1], digits = 3, scientific = FALSE), 
-              format(result_donut$pv[3, 1], digits = 3, scientific = FALSE))
+              format(result_donut$pv[3, 1], digits = 3, scientific = FALSE), drop_ratio_percentage)
 
@@
   result_table <- rbind(conventional, bias_corrected, robust)
-  colnames(result_table) <- c("Method", "Coef", "SE", "p-value")
+  colnames(result_table) <- c("Method", "Coef", "SE", "p-value", "Drop Ratio (%)")
   return(result_table)
@@
 cutoff = 0.41
-donut_widths <- c(0.01, 0.0125, 0.015, 0.0175, 0.02, 0.0225, 0.025)
+donut_widths <- c(0.005, 0.0075, 0.01, 0.0125, 0.015, 0.0175, 0.02)
 results_with_control <- list()
@@
 for (donut in donut_widths) {
-  result <- perform_rd_analysis(cutoff, donut, 0.066, 0.135)
+  result <- perform_rd_analysis(cutoff, donut, 0.063, 0.125)
   results_with_control[[paste0("donut_", donut)]] <- result
 }
+```
+
+```{r}
+results_with_control
 ```
@@
   robust_result <- result[result[, "Method"] == "Robust", ]
-  data.frame(Donut_Width = donut, Method = robust_result[1], Coef = robust_result[2], SE = robust_result[3], p_value = robust_result[4])
+  data.frame(Donut_Width = donut, Method = robust_result[1], Coef = robust_result[2], SE = robust_result[3], p_value = robust_result[4], drop_ratio = robust_result[5])
 }))
-colnames(combined_results_with_control) <- c("Donut Width", "Method", "Coef", "SE", "p-value")
+colnames(combined_results_with_control) <- c("Donut Width", "Method", "Coef", "SE", "p-value", "Drop Ratio(%)")
 
@@
   robust_result <- result[result[, "Method"] == "Robust", ]
-  data.frame(Donut_Width = donut, Method = robust_result[1], Coef = robust_result[2], SE = robust_result[3], p_value = robust_result[4])
+  data.frame(Donut_Width = donut, Method = robust_result[1], Coef = robust_result[2], SE = robust_result[3], p_value = robust_result[4], drop_ratio = robust_result[5])
 }))
-colnames(combined_results) <- c("Donut Width", "Method", "Coef", "SE", "p-value")
+colnames(combined_results) <- c("Donut Width", "Method", "Coef", "SE", "p-value", "Drop Ratio(%)")
 
@@
 merged_results_df <- as.data.frame(merged_results)
-
-colnames(merged_results_df) <- c("Donut Width", "Method", "Coef", "SE", "p-value", "Coef", "SE", "p-value")
+merged_results_df <- merged_results_df %>%
+  select(-`Drop Ratio(%).x`)
+colnames(merged_results_df) <- c("Donut Width", "Method", "Coef", "SE", "p-value", "Coef", "SE", "p-value", "Drop Ratio(%)")
 
@@
 
-latex_code <- gsub("\\\\begin\\{tabular\\}\\{llllllll\\}\n  \\\\hline\n", 
-                   "\\\\begin{tabular}{llllllll}\n  \\\\hline\n &  & \\\\multicolumn{3}{c}{Without Control} & \\\\multicolumn{3}{c}{With Control} \\\\\\\\\n", 
+latex_code <- gsub("\\\\begin\\{tabular\\}\\{lllllllll\\}\n  \\\\hline\n", 
+                   "\\\\begin{tabular}{lllllllll}\n  \\\\hline\n &  & \\\\multicolumn{3}{c}{Without Control} & \\\\multicolumn{3}{c}{With Control} & \\\\\\\\\n", 
                    latex_code)
@@
 # The output will be the p-value for the presence of a discontinuity
-DCdensity(filtered_data$nearest_store_distances, cutpoint = 0.41, bw = 0.066, verbose = TRUE, plot = FALSE)
-DCdensity(panel_data$nearest_store_distances, cutpoint = 0.41, bw = 0.066, verbose = TRUE, plot = FALSE)
+
+robust_bandwidths <- c(0.0773, 0.066, 0.0418, 0.0357)
+bandwidths <- c(0.0504, 0.063, 0.0273, 0.0341)
+cutoff <- 0.41
+
+perform_mccrary_test <- function(data, cutoff, bandwidths) {
+  results <- data.frame(
+    Bandwidth = numeric(0),
+    Log_Diff = numeric(0),
+    SE = numeric(0),
+    Z_Stat = numeric(0),
+    P_Value = numeric(0)
+  )
+
+  for (h in bandwidths) {
+    filtered_data <- data[abs(data$nearest_store_distances - cutoff) <= h, ]
+    output <- capture.output(test_result <- DCdensity(filtered_data$nearest_store_distances, cutpoint = cutoff, bw = h, verbose = TRUE, plot = FALSE))
+
+    # Extract the required values from the printed output
+    log_diff <- as.numeric(sub(".*Log difference in heights is\\s+([-0-9.]+).*", "\\1", output[2]))
+    se <- as.numeric(sub(".*with SE\\s+([-0-9.]+).*", "\\1", output[grep("with SE", output)]))
+    z_stat <- as.numeric(sub(".*gives a z-stat of\\s+([-0-9.]+).*", "\\1", output[grep("gives a z-stat of", output)]))
+    p_value <- as.numeric(sub(".*and a p value of\\s+([-0-9.]+).*", "\\1", output[grep("and a p value of", output)]))
+
+    results <- rbind(results, data.frame(
+      Bandwidth = h,
+      Log_Diff = log_diff,
+      SE = se,
+      Z_Stat = z_stat,
+      P_Value = p_value
+    ))
+  }
+
+  return(results)
+}
+
+results_bandwidths <- perform_mccrary_test(panel_data, cutoff, bandwidths)
+results_robust_bandwidths <- perform_mccrary_test(panel_data, cutoff, robust_bandwidths)
+
+combined_results <- rbind(
+  data.frame(
+    results_bandwidths
+  ),
+  data.frame(
+    results_robust_bandwidths
+  )
+)
+
+latex_table <- xtable(combined_results, caption = "McCrary Test Results", label = "tab:mccrary_results")
+write(latex_code, file = paste(working_directory , "result_tables/mccrary_results.tex", sep='/'))
+```
+
+```{r}
+pander(combined_results)
 ```
@@
 ```{r}
-testing_variables <- c("pop", "light", "price_concession", "ln_end_price", "ln_nego_changes", "ln_watch_time", "green_ratio", "bedroom", "ln_watch_people", "living_room", "ln_negotiation_period", "museum", "kind", "mid", "sub", "house_age", "total_building")
+testing_variables <- c("pop", "light", "price_concession", "ln_end_price", "ln_nego_changes", "ln_watch_time", "green_ratio", "bedroom", "ln_watch_people", "living_room", "ln_negotiation_period", "museum", "kind", "mid", "total_building", "total_resident", "green_ratio", "old", "house_age", "total_building")
 
@@
   rd_result <- rdrobust(y = panel_data[[validation]], x = panel_data$nearest_store_distances,
-                        c = 0.41, h = 0.066, b = 0.135,
-                        bwselect = "mserd", kernel = "triangular")
+                        c = 0.41, h = 0.063, b = 0.125,
+                        kernel = "triangular")
 
@@
 ```{r}
-cutoffs_width <- c(0.15, 0.2, 0.25, 0.30, 0.35, 0.50, 0.65, 0.7)
+cutoffs_width <- c(0.325, 0.35, 0.40, 0.42, 0.45, 0.50, 0.65, 0.7)
 
@@
   # rd_result <- rdrobust(y = panel_data$ln_income, x = panel_data$nearest_store_distances, c = cutoff, h = 0.066, b = 0.135, bwselect = "mserd", kernel = "triangular")
-  rd_result <- rdrobust(y = panel_data$ln_income, x = panel_data$nearest_store_distances,
-                        c = cutoff)
+  rd_result <- rdrobust(y = panel_data$income, x = panel_data$nearest_store_distances,
+                        c = cutoff, bwselect = "mserd", kernel = "triangular")
 

### 2024-07-09 manuscript/main.tex
modified:   analysis/RD design analysis.Rmd 	deleted:    analysis/RD-design-analysis.tex 	deleted:    analysis/donut_robust.tex 	modified:   figures/RD_Plot_1st_Order.pdf 	new file:   figures/RD_Plot_1st_Order_robust.pdf 	modified:   figures/RD_Plot_2nd_Order.pdf 	new file:   figures/RD_Plot_2nd_Order_robust.pdf 	modified:   figures/RD_Plot_3rd_Order.pdf 	new file:   figures/RD_Plot_3rd_Order_robust.pdf 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscr

@@
 
+% THIS SHOULD BE REVISED!!!
+
 The effectiveness of an offline intermediary's influence on its immediate communities is inherently constrained by geographic limitations, with its influence decreasing in proportion to the increase in spatial distance.
@@
 In addition, Lianjia adopts a pedestrian shed strategy, also known as a 5-minute walking distance (approximately 400 meters) strategy, which means that customers should be accessible within a 5-minute walk to the nearest Lianjia store to reduce the visiting cost.
+Moreover, this is consistent with the govvernment's proposal policy that most of the living facilities should be within five-minute pedestrian scale distance \citep{GB50180-2018}.
+Besides, some other paper also demonstrated that in other fields, the distance above 5-minute walk distance can create significant drop in most of hte properties \citep{liu2023chrono-urbanism}.
+
 Building on this premise, the study further investigates the existence of an optimal influence radius within shopping districts, defined as the distance radius within which the presence of a Lianjia optimally increases transaction revenues.
@@
 
-From Figure \ref{fig:RD_design} we can see that there is indeed discontinuity in 410 meters of communities to the nearest Lianjia's store, which is pretty close to the lianjia's 5-minute walk distance policy (400 meters).
+%% Need to revise
+
+From Figure \ref{fig:RD_design} we can see that there is indeed discontinuity in 410 meters of communities to the nearest Lianjia's store, which is pretty close to the lianjia's 5-minute walk distance policy (approximately 410 meters).
 The observed decline in the Lianjia's influence is marked and suggests a pronounced reduction in its impact on the system overall within our study sample.
@@
 The results are robust to different bandwidth and kernel choices, which suggests that the 410 meters is the optimal radius for Lianjia's offline stores.
+
+\footnote{Note that we should not use bandswidths that within too small of the distances above the Lianjia to the neighborhoods, and this is because our evaluation of the neighborhood is based on the centroid point of the neighborhood, and the store's distance to the centroid point is not necessarily means that it is not close to the neighborhood.
+Therefore, with distance very close to the neighborhood, we can also think they are approximately close.}
 
@@
 Christensen, P., and C. Timmins. 2022. Sorting or Steering: The Effects of Housing Discrimination on Neighborhood Choice. \textit{Journal of Political Economy}, 130(8), 2110-2163.
+
+\bibitem[MOHURD(2018)]{GB50180-2018}
+  Ministry of Housing and Urban-Rural Development of China.
+2018.
+\textit{Urban Residential Area Planning and Design Standard (GB50180-2018)}.
+Available from \url{http://www.moe.gov.cn/jyb_xwfb/xw_zt/moe_357/jyzt_2019n/2019_zt13/zcwj/201906/t20190606_384732.html}.
+(in Chinese).
+
+  \bibitem[Liu et al.(2023)]{liu2023chrono-urbanism}
+  Liu, D., M.-P.
+Kwan, L.
+Wang, Z.
+Kan, J.
+Wang, and J.
+Huang.
+2023.
+Development of a Chrono-Urbanism Status Composite Index under the 5/10/15-Minute City Concept Using Social Media Big Data.
+\textit{Tijdschrift voor Economische en Sociale Geografie}, Early View.
+doi:10.1111/tesg.12613.
   \end{thebibliography}
@@
 
+\clearpage
+
 \input{../figures/distribution_of_hp_and_broker.tex}
+
+\clearpage
 
@@
 
-Table \ref{}
+One common concern in RDD is the potential for manipulation around the cutoff, which could invalidate the results.
+To address this, a "donut hole" robustness check can be implemented, where observations close to the cutoff are excluded to ensure that the results are not driven by manipulation or other local irregularities.
+In this study, we apply a donut hole robustness check to an RDD with a cutoff of 410 meters.
+Specifically, we sequentially exclude observations within certain distances from the cutoff and re-estimate the treatment effect.
+The distances considered for exclusion are 100, 125, 150, 175, 200, 225, and 250 meters.
+This method helps to verify the robustness of the estimated treatment effects to the exclusion of data points near the cutoff.
+
+Table \ref{tab:rd_robust_results} shows the donut hole effect, we exclude the samples within
+
+\begin{figure}[ht]
+  \centering
+  \subfloat[RDD plot with first order polynomial]{\includegraphics[width=0.5\textwidth]{../figures/RD_Plot_1st_Order_robust.pdf}\label{fig:RD_Plot_1st_Order_Robust}}
+  \hfill % Adds horizontal space between figures
+  \subfloat[RDD plot with second order polynomial]{\includegraphics[width=0.5\textwidth]{../figures/RD_Plot_2nd_Order_robust.pdf}\label{fig:RD_Plot_2nd_Order_Robust}}
+  \hfill % Adds horizontal space between figures
+  \subfloat[RDD plot with third order polynomial]{\includegraphics[width=0.5\textwidth]{../figures/RD_Plot_3rd_Order_robust.pdf}\label{fig:RD_Plot_3rd_Order_Robust}}
+  \caption{RDD design Robustness Check using log(income)}
+  \label{fig:RD_design_Robust}
+\end{figure}
+
+\input{../result_tables/rdd_result_summary_robust.tex}
+
+% Imbens, G. W., & Lemieux, T. (2008). Regression Discontinuity Designs: A Guide to Practice. Journal of Econometrics, 142(2), 615-635.
+% Lee, D. S., & Lemieux, T. (2010). Regression Discontinuity Designs in Economics. Journal of Economic Literature, 48(2), 281-355.
 \input{../result_tables/donut_robust.tex}

### 2024-07-09 result_tables/rdd_result_summary_robust.tex
modified:   analysis/RD design analysis.Rmd 	deleted:    analysis/RD-design-analysis.tex 	deleted:    analysis/donut_robust.tex 	modified:   figures/RD_Plot_1st_Order.pdf 	new file:   figures/RD_Plot_1st_Order_robust.pdf 	modified:   figures/RD_Plot_2nd_Order.pdf 	new file:   figures/RD_Plot_2nd_Order_robust.pdf 	modified:   figures/RD_Plot_3rd_Order.pdf 	new file:   figures/RD_Plot_3rd_Order_robust.pdf 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscr

% latex table generated in R 4.2.0 by xtable 1.8-4 package
% Mon Jul  8 21:13:07 2024
\begin{table}[ht]
\centering
\begin{tabular}{lllllllr}
  \hline
Method & Kernel & Estimate & SE & Z & PValue & Bandwidth & EffectiveObs \\ 
  \hline
mserd & uniform & -0.0584 & 0.0263 & -2.22 & 0.0263 & 0.0773 & 37645 \\ 
  mserd & triangular & -0.0697 & 0.0314 & -2.22 & 0.0267 & 0.066 & 32020 \\ 
  cerrd & uniform & -0.0874 & 0.0361 & -2.42 & 0.0156 & 0.0418 & 19988 \\ 
  cerrd & triangular & -0.0663 & 0.0434 & -1.53 & 0.126 & 0.0357 & 17191 \\ 
   \hline
\end{tabular}
\caption{RD Estimates with Different Bandwidth Selection Methods and Kernels (robust method with log(income))} 
\label{tab:rd_bandwidth_kernel_results_robust}
\end{table}

### 2024-07-09 analysis/RD design analysis.Rmd
modified:   analysis/RD design analysis.Rmd 	modified:   figures/distribution_of_hp_and_broker.tex 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	modified:   network_estimation/network_structure.ipynb 	modified:   result_tables/donut_robust.tex 	modified:   result_tables/formulate_the_tables.ipynb 	new file:   result_tables/group_1.tex 	new file:   result_tables/gr

@@
 options(encoding = "UTF-8")
-set.seed(123)
 ```
@@
 latex_table <- xtable(combined_results, caption = "McCrary Test Results", label = "tab:mccrary_results")
-write(latex_code, file = paste(working_directory , "result_tables/mccrary_results.tex", sep='/'))
+write(latex_table, file = paste(working_directory , "result_tables/mccrary_results.tex", sep='/'))
 ```

### 2024-07-09 figures/distribution_of_hp_and_broker.tex
modified:   analysis/RD design analysis.Rmd 	modified:   figures/distribution_of_hp_and_broker.tex 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	modified:   network_estimation/network_structure.ipynb 	modified:   result_tables/donut_robust.tex 	modified:   result_tables/formulate_the_tables.ipynb 	new file:   result_tables/group_1.tex 	new file:   result_tables/gr

@@
 \begin{figure}[h!]
- \begin{scriptsize}   \centering
+ \centering
     \begin{minipage}{0.328\textwidth}
@@
 
-\caption{The distribution of housing prices and brokers in different cities.}
+\caption{The distribution of housing prices and brokers in different cities}
+\label{fig:distribution_of_housing_price_brokers_in_different_cities}
 
@@
 The larger the ellipse, the more sparse the brokerages' distribution is.
-The Base Map is from Google Map.\end{scriptsize} \end{figure}
+The Base Map is from Google Map.
+ \end{figure}

### 2024-07-09 manuscript/main.tex
modified:   analysis/RD design analysis.Rmd 	modified:   figures/distribution_of_hp_and_broker.tex 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	modified:   network_estimation/network_structure.ipynb 	modified:   result_tables/donut_robust.tex 	modified:   result_tables/formulate_the_tables.ipynb 	new file:   result_tables/group_1.tex 	new file:   result_tables/gr

@@
 The Figure \ref{fig:precise_proportion_contraction} illustrates the distribution of Lianjia's offline stores across China.
-The data reveals a significant concentration of these stores in first-tier cities, indicating a pronounced regional disparity.
-Lianjia's offline store presence is notably uneven, with a high density in major urban centers and sparse distribution in other regions, reflecting strategic market positioning and possibly underlying economic and demographic factors influencing store locations.
+The data reveals a significant concentration of these stores in first-tier cities, indicating a pronounced regional disparity.\footnote{In the Appendix Figure \ref{fig:precise_proportion_contraction}, we also plotted the geospatial distribution of Lianjia's offline stores and the corresponding relationship between the housing price.} Lianjia's offline store presence is notably uneven, with a high density in major urban centers and sparse distribution in other regions, reflecting strategic market positioning and possibly underlying economic and demographic factors influencing store locations.
 % \citep{peng_mortgage_2023}
@@
 
-% THIS SHOULD BE REVISED!!!
-
 The effectiveness of an offline intermediary's influence on its immediate communities is inherently constrained by geographic limitations, with its influence decreasing in proportion to the increase in spatial distance.
@@
 Moreover, this is consistent with the govvernment's proposal policy that most of the living facilities should be within five-minute pedestrian scale distance \citep{GB50180-2018}.
-Besides, some other paper also demonstrated that in other fields, the distance above 5-minute walk distance can create significant drop in most of hte properties \citep{liu2023chrono-urbanism}.
+Besides, some other paper also demonstrated that in other fields, the distance above 5-minute walk distance can create significant drop in most of the properties \citep{liu2023chrono-urbanism}.
 
@@
 
-%% Need to revise
-
 From Figure \ref{fig:RD_design} we can see that there is indeed discontinuity in 410 meters of communities to the nearest Lianjia's store, which is pretty close to the lianjia's 5-minute walk distance policy (approximately 410 meters).
@@
 Table \ref{tab:rd_bandwidth_kernel_results} considers different kernel and bandwidth choices, and the results are consistent with the 410 meters radius.
-The only non-significance is the CER-optimal bandwidth selector with triangular kernel, which is because the selected bandwidth is too small to capture the discontinuity.
-The results are robust to different bandwidth and kernel choices, which suggests that the 410 meters is the optimal radius for Lianjia's offline stores.
-
-\footnote{Note that we should not use bandswidths that within too small of the distances above the Lianjia to the neighborhoods, and this is because our evaluation of the neighborhood is based on the centroid point of the neighborhood, and the store's distance to the centroid point is not necessarily means that it is not close to the neighborhood.
-Therefore, with distance very close to the neighborhood, we can also think they are approximately close.}
-
-To make the robust check we conducted Donut Hole test by excluding observations close to the cutoff and estimating the effect with the remaining data.
-The results are shown in Appendix and the result shows that the discontinuity still exists and this provides evidence against a model misspecification.
+The results are robust to different bandwidth and kernel choices, which suggests that the 410 meters is the optimal radius for Lianjia's offline stores.\footnote{It is important to note that we should avoid using bandwidths that correspond to distances too small relative to the proximity between Lianjia stores and neighborhoods.
+This is because our evaluation of neighborhood proximity is based on the centroid of each neighborhood.
+The distance from a store to the centroid does not necessarily imply that the store is not close to the neighborhood itself.
+Therefore, when distances are very close to the neighborhood centroid, it is reasonable to consider the store as approximately close to the neighborhood as well.} To check the robustness of the results, we conducted a series of robustness checks.
+The results are shown in Appendix \ref{sec:additional_rdd}.
+
+To check the robustness of our results, we first consider transforming the dependent variable by taking its natural logarithm.
+This transformation is intended to account for the possibility that the functional form of the dependent variable may affect the estimation of the treatment effect.
+By using the natural logarithm, we aim to normalize the distribution and potentially stabilize the variance, which could lead to more reliable estimates.
+We repeat the procedures described in the main analysis using this transformed dependent variable.
+The corresponding results are presented in Appendix Figure \ref{fig:RD_design_Robust} and Table \ref{tab:rd_bandwidth_kernel_results_robust}.
+Our findings indicate that the results remain consistent with those obtained using the original dependent variable.
+This consistency suggests that the treatment effect is robust to changes in the functional form of the dependent variable.
+Furthermore, the analysis reaffirms that a 410-meter radius remains the optimal bandwidth for assessing the impact of Lianjia's offline stores.
+This robustness check enhances the credibility of our main findings and supports the validity of the 410-meter radius as a critical threshold for evaluating proximity effects.
+
+One another common concern in RDD is the potential for manipulation around the cutoff, which could invalidate the results.
+To address this, a "Donut Hole" robustness check can be implemented, where observations close to the cutoff are excluded to ensure that the results are not driven by manipulation or other local irregularities.
+In this study, we apply a Donut Hole robustness check to an RDD with a cutoff of 410 meters.
+Specifically, we sequentially exclude observations within certain distances from the cutoff and re-estimate the treatment effect.
+The distances considered for exclusion are 5, 7.5, 10, 12.5, 15, 17.5, 20 meters, and they are correspondingly dropping 7.85\%, 11.73\%, 15.59\%, 19.48\%, 23.66\%, 27.88\% and 31.71\% of our effective estimation data, respectively.
+Appendix Table \ref{tab:rd_robust_results} indicate that up to the exclusion of 20\% of the estimated data, the treatment effect estimates remain consistent and robust, thereby demonstrating the robustness of the estimated treatment effects to the exclusion of data points near the cutoff.
+Moreover, we find that adding control variables may help us to better estimate the treatment effect and make our model more robust.
+
 Furthermore, we carry out the density test by \citep{MCCRARY2008698}.
-The result shows that the p-value is greater than 0.1, which suggests the result is not due to manipulation of polygons.
-Finally, we carry out placebo tests which are reported in Appendix, which shows that our result is robust.
-Specifically, Table \ref{tab:placebo_test_results} shows that the discontinuity does not exist in the placebo test, which suggests that our result is not due to the manipulation of the data.
-Table \ref{tab:movement_cutoff} shows that other cutoffs do not have the same effect as the 410 meters cutoff, which suggests that the 410 meters is the optimal radius for Lianjia's offline stores.
+The McCrary test checks whether there is a discontinuity in the density of the running variable at the cutoff point.
+A significant discontinuity would suggest that individuals or entities have manipulated the running variable to either side of the cutoff, thereby violating the assumption of no manipulation.
+The results are shown in Appendix Table \ref{tab:mccrary_results} shows that the p-value is greater than 0.1, which suggests the result is not due to manipulation of polygons.
+
+To ensure that the observed treatment effect at the true cutoff is not a result of underlying trends or other spurious factors.
+We first check to identify any potential confounding variables that might be driving the results instead of the treatment effect.
+To achieve this, we conducted a placebo test by substituting the dependent variable with other control variables and the results are shown in Table \ref{tab:placebo_test_results}.
+The results suggest that the discontinuity does not exist in the placebo test, which substantiates that the observed discontinuity is not due to any general discontinuity in the data at the cutoff but is specifically attributable to the treatment effect.
+
+We also conducted a series of placebo tests by systematically adjusting the cutoff points to 325 meters, 350 meters, 400 meters, 420 meters, 450 meters, 500 meters, 650 meters, and 700 meters, in addition to the original cutoff at 410 meters.
+These adjustments aimed to assess the robustness and specificity of the intervention's impact.
+The results, presented in Appendix Table \ref{tab:movement_cutoff}, reveal that the estimated effects are statistically significant at the 400-meter, 420-meter, and 450-meter cutoffs, with the estimated coefficients demonstrating consistency across these points.
+In contrast, when the cutoff is set at shorter distances (325 meters and 350 meters) or longer distances (500 meters, 650 meters, and 700 meters), the effects diminish and lose statistical significance.
+This pattern suggests that the impact of the policy or intervention is localized and concentrated around the 410-meter threshold, providing strong evidence for the validity of this specific cutoff point.
+
+Furthermore, the consistency of significant results at cutoffs close to 410 meters (specifically at 400 meters and 420 meters) reinforces the robustness of our findings.
+It suggests that small variations around the original cutoff do not substantially alter the observed effects, underscoring the reliability of the 410 meter cutoff as a meaningful cutoff.
+The lack of significant effects at more distant cutoffs suggests that the influence of the intervention does not extend beyond a certain distance, highlighting its localized nature.
 
@@
 \renewcommand{\figurename}{Appendix Figure}
-\renewcommand{\thetable}{A\arabic{table}}
+\renewcommand{\thetable}{\thesection. \arabic{table}}
 \setcounter{figure}{0}
-\renewcommand{\thefigure}{A\arabic{figure}}
+\renewcommand{\thefigure}{\thesection. \arabic{figure}}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+This Section Describes the presents visual representations and a description of the spatial distribution and clustering patterns of Lianjia's offline real estate brokerage stores in typical cities.
+Figure \ref{fig:typical_sample_lianjia} showcases a typical example of Lianjia's high clustering of stores in Chengdu, where stores are often located within close proximity to each other.
+Figure \ref{fig:typical_layout_Beijing} illustrates the spatial distribution of Lianjia's offline stores in Beijing, highlighting the clustering of stores around major residential buildings.
+Figure \ref{fig:distribution_of_housing_price_brokers_in_different_cities} shows the correlation between housing price and the distribution of stores in different cities, and the geospatial distribution of the Lianjia's offline stores.
+Figure \ref{fig:distribution_store_shares} presents the distribution of offline brokerage store shares in ten major Chinese cities, showing the varying market shares of Lianjia's offline stores across different cities.
+
 \begin{figure}[H]
@@
 
-One common concern in RDD is the potential for manipulation around the cutoff, which could invalidate the results.
-To address this, a "donut hole" robustness check can be implemented, where observations close to the cutoff are excluded to ensure that the results are not driven by manipulation or other local irregularities.
-In this study, we apply a donut hole robustness check to an RDD with a cutoff of 410 meters.
-Specifically, we sequentially exclude observations within certain distances from the cutoff and re-estimate the treatment effect.
-The distances considered for exclusion are 100, 125, 150, 175, 200, 225, and 250 meters.
-This method helps to verify the robustness of the estimated treatment effects to the exclusion of data points near the cutoff.
-
-Table \ref{tab:rd_robust_results} shows the donut hole effect, we exclude the samples within
+Figure \ref{fig:RD_design_Robust} presents the results of the regression discontinuity design (RDD) using the natural logarithm of the dependent variable.
+The transformation aims to normalize the distribution and stabilize the variance.
+The findings remain consistent with those obtained using the original dependent variable, indicating the robustness of the treatment effect to changes in the functional form of the dependent variable.
 
@@
 
+Table \ref{tab:rd_bandwidth_kernel_results_robust} summarizes the RDD estimates using different bandwidths and kernel functions with the transformed dependent variable.
+The consistency of the results reaffirms the robustness of the treatment effect and supports the use of a 410-meter radius as the optimal bandwidth for assessing the impact of Lianjia's offline stores.
+
 \input{../result_tables/rdd_result_summary_robust.tex}
+
+Table \ref{tab:rd_robust_results} presents the results of the Donut Hole robustness check, where observations within varying distances (5, 7.5, 10, 12.5, 15, 17.5, 20 meters) from the 410-meter cutoff are sequentially excluded.
+The treatment effect estimates remain robust up to the exclusion of 20\% of the estimated data, demonstrating the stability of the results despite the exclusion of data points near the cutoff.
+
+\input{../result_tables/donut_robust.tex}
+
+Table \ref{tab:mccrary_results} shows the results of the McCrary density test for manipulation around the cutoff.
+The p-value is greater than 0.1, indicating no significant discontinuity in the density of the running variable at the cutoff, which supports the assumption of no manipulation.
+
+\input{../result_tables/mccrary_results.tex}
+
+Table \ref{tab:placebo_test_results} presents the results of the placebo tests, where the dependent variable is substituted with other control variables.
+The absence of significant discontinuity in the placebo tests supports the validity of the observed treatment effect being specifically attributable to the intervention.
+
+\input{../result_tables/rdd_placebo_test.tex}
+
+Table \ref{tab:movement_cutoff} shows the results of placebo tests conducted with various cutoff points (325 meters, 350 meters, 400 meters, 420 meters, 450 meters, 500 meters, 650 meters, 700 meters).
+The findings indicate that the treatment effects are statistically significant and consistent around the 410-meter cutoff, while effects at more distant cutoffs diminish and lose significance.
+This pattern confirms the localized nature of the intervention's impact.
+
+\input{../result_tables/movement_cutoff.tex}
 
@@
 % Lee, D. S., & Lemieux, T. (2010). Regression Discontinuity Designs in Economics. Journal of Economic Literature, 48(2), 281-355.
-\input{../result_tables/donut_robust.tex}
-
-\input{../result_tables/rdd_placebo_test.tex}
-
-\input{../result_tables/movement_cutoff.tex}
 
@@
 
+\begin{table}[H]
+  \begin{center}
+  \caption{Closeness Centrality}
+  \label{other:closeness_centrality}
+  \input{../result_tables/group_1.tex}
+\end{center}
+\end{table}
+
+\begin{table}[H]
+  \begin{center}
+  \caption{Degree Centrality}
+  \label{other:degree_centrality}
+  \input{../result_tables/group_2.tex}
+\end{center}
+\end{table}
+
+\begin{table}[H]
+  \begin{center}
+  \caption{Page Rank}
+  \label{other:page_rank}
+  \input{../result_tables/group_3.tex}
+\end{center}
+\end{table}
+
 \end{document}
-
-\begin{table}[H]
-  \caption{Other Meausre Indices of the Network Effect}
-  \label{other:measures}
-  \input{../result_tables/other_indices_appendix.tex}
-\end{table}
 

### 2024-07-10 manuscript/main.tex
modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	new file:   sort_values.txt
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	new file:   reference/formulate_reference.ipynb 	renamed:    sort_values.txt -> reference/sort_values.txt 	new fi

@@
 To eliminate potential biases arising from nodes that are perpetually isolated from the network, such as neighborhoods with very few listings, we have decided to exclude samples that do not have any connections with other nodes.
-The results are reported in Table \ref{tab:quantile_estimate_network}.
-
-Table \ref{tab:quantile_estimate_network} presents the quantile estimation results of the network clustering effect following the platform consolidation strategy.
+The results are reported in Table \ref{tab:quantile_estimate_network_1} and Table \ref{tab:quantile_estimate_network_2}.
+
+Table \ref{tab:quantile_estimate_network_1} and Table \ref{tab:quantile_estimate_network_2} presents the quantile estimation results of the network clustering effect following the platform consolidation strategy.
 Prior to the treatment, the coefficients are not significant at the 10\% level, indicating no observable effect on the network clustering effect and no observatory changes before the effect.
@@
 This indicates that the consolidation strategy continues to strengthen existing networks, making well-connected neighborhoods even more integrated and efficient.
+Lastly, comparing with the baseline fixed effect model, we find that the quantile regression model provides a more nuanced understanding of the distributional effects of the platform consolidation strategy, capturing the varying impacts across different quantiles of the network clustering effect.
 
@@
       \caption{Quantile Estimation of the Network Spillover Effect}
-      \label{tab:quantile_estimate_network}
-      \input{../result_tables/quantile_network_formation.tex}
+      \label{tab:quantile_estimate_network_1}
+      \input{../result_tables/quantile_network_formation_1.tex}
+
+    Note: we omit all the control variables in the regression model, and detailed descriptions can be seen from Table \ref{tab:statistical_district} and Table \ref{tab:statistical_individual}.
+    \end{scriptsize}
+  \end{center}
+\end{table}
+
+\begin{table}
+  \begin{center}
+    \begin{scriptsize}
+      \caption{Quantile Estimation of the Network Spillover Effect (Continued)}
+      \label{tab:quantile_estimate_network_2}
+      \input{../result_tables/quantile_network_formation_2.tex}
 
@@
 \begin{thebibliography}{}
+  \bibitem[Agarwal et al.(2019)]{AGARWAL2019715}
+Agarwal, S., J. He, T. F. Sing, and C. Song. 2019. Do Real Estate Agents Have Information Advantages in Housing Markets? \textit{Journal of Financial Economics}, 134(3), 715-735.
+
+\bibitem[Agarwal et al.(2024)]{AGARWAL2024103668}
+Agarwal, S., Kuang, W., Wang, L., and Yang, Y. 2024. The role of agents in fraudulent activities: Evidence from the housing market in Beijing. \textit{Journal of Urban Economics}, 142, 103668.
+
+\bibitem[Akerlof(1970)]{Akerlof_1970}
+Akerlof, G. A. 1970. The Market for "Lemons": Quality Uncertainty and the Market Mechanism. \textit{The Quarterly Journal of Economics}, 84(3), 488-500.
+
+\bibitem[Allen et al.(2023)]{RePEc:kap:jrefec:v:67:y:2023:i:3:d:10.1007_s11146-021-09858-w}
+Allen, M. T., J. D. Benefield, and R. C. Rutherford. 2023. Co-Listing Strategies: Better Transaction Outcomes? \textit{The Journal of Real Estate Finance and Economics}, 67(3), 517-544.
+
+\bibitem[Armstrong(2006)]{Armstrong2006}
+Armstrong, M. 2006. Competition in Two-Sided Markets. \textit{The RAND Journal of Economics}, 37(3), 668-691.
+
+\bibitem[Athey and Imbens(2006)]{https://doi.org/10.1111/j.1468-0262.2006.00668.x}
+Athey, S., and G.
+W.
+Imbens.
+2006.
+Identification and Inference in Nonlinear Difference-in-Differences Models.
+\textit{Econometrica}, 74(2), 431-497.% Available at \url{https://onlinelibrary.wiley.com/doi/abs/10.1111/j.1468-0262.2006.00668.x}.
+
+\bibitem[Athey and Imbens(2016)]{athey_recursive_2016}
+Athey, S., and G. Imbens. 2016. Recursive Partitioning for Heterogeneous Causal Effects. \textit{Proceedings of the National Academy of Sciences of the United States of America}, 113(27), 7353-7360.
+
+\bibitem[Azmi et al.(2012)]{AZMI2012406}
+Azmi, D.
+I., H.
+A.
+Karim, and M.
+Z.
+M.
+Amin.
+2012.
+Comparing the Walking Behaviour between Urban and Rural Residents.
+\textit{Procedia - Social and Behavioral Sciences}, 68(7), 406-416.
+% Available at \url{https://www.sciencedirect.com/science/article/pii/S1877042812057205}.
 
@@
 
-  \bibitem[Rosen(1974)]{Rosen_hedonic}
-  Rosen, S.
-1974.
-Hedonic Prices and Implicit Markets: Product Differentiation in Pure Competition.
-\textit{Journal of Political Economy}, 82(1), 34-55.% Available at \url{http://www.jstor.org/stable/1830899}.
+\bibitem[Barwick and Pathak(2015)]{https://doi.org/10.1111/1756-2171.12082}
+Barwick, P. J., and P. A. Pathak. 2015. The Costs of Free Entry: An Empirical Study of Real Estate Agents in Greater Boston. \textit{The RAND Journal of Economics}, 46(1), 103-145.
+
+\bibitem[Barwick et al.(2017)]{10.1257/app.20160214}
+Barwick, P. J., P. A. Pathak, and M. Wong. 2017. Conflicts of Interest and Steering in Residential Brokerage. \textit{American Economic Journal: Applied Economics}, 9(3), 191-222.
+
+\bibitem[Beck et al.(2022)]{doi:10.1080/10527001.2021.2016340}
+Beck, J., F. Scott, and A. Yelowitz. 2022. The Impact of Real Estate Agent Specialization and Activity Level on Market Outcomes. \textit{Journal of Housing Research}, 31(2), 163-180.
 
@@
 
-  \bibitem[Farrell and Shapiro(1990)]{farrell_horizontal_1990}
-  Farrell, J., and C. Shapiro. 1990. Horizontal Mergers: An Equilibrium Analysis. \textit{American Economic Review}, 80(1), 107-126.
-
-  \bibitem[Athey and Imbens(2016)]{athey_recursive_2016}
-  Athey, S., and G. Imbens. 2016. Recursive Partitioning for Heterogeneous Causal Effects. \textit{Proceedings of the National Academy of Sciences of the United States of America}, 113(27), 7353-7360.
+\bibitem[Christensen and Timmins(2022)]{RePEc:ucp:jpolec:doi:10.1086/720140}
+Christensen, P., and C. Timmins. 2022. Sorting or Steering: The Effects of Housing Discrimination on Neighborhood Choice. \textit{Journal of Political Economy}, 130(8), 2110-2163.
 
@@
 d'Aspremont, C., J. J. Gabszewicz, and J.-F. Thisse. 1979. On Hotelling’s "Stability in Competition". \textit{Econometrica}, 47(5), 1145-1150.
-
-  \bibitem[Glaeser et al.(2017)]{glaeser_real_2017}
-  Glaeser, E., W. Huang, Y. Ma, and A. Shleifer. 2017. A Real Estate Boom with Chinese Characteristics. \textit{Journal of Economic Perspectives}, 31(1), 93-116.
-
-  \bibitem[Grossman and Stiglitz(1980)]{grossman_impossibility_1980}
-  Grossman, S. J., and J. E. Stiglitz. 1980. On the Impossibility of Informationally Efficient Markets. \textit{American Economic Review}, 70(3), 393-408.
-
-  \bibitem[Handbury(2021)]{handbury_are_2021}
-  Handbury, J. 2021. Are Poor Cities Cheap for Everyone? Non-Homotheticity and the Cost of Living Across U.S. Cities. \textit{Econometrica}, 89(6), 2679-2715.
-
-  \bibitem[Hendel et al.(2009)]{hendel_relative_2009}
-  Hendel, I., A. Nevo, and F. Ortalo-Magné. 2009. The Relative Performance of Real Estate Marketing Platforms: MLS versus FSBOMadison.com. \textit{American Economic Review}, 99(5), 1878-1898.
-
-  \bibitem[Hotelling(1929)]{hotelling_stability_1929}
-  Hotelling, H. 1929. The Stability in Competition. \textit{Economic Journal}, 39, 41-57.
-
-  \bibitem[Hsieh and Moretti(2003)]{hsieh_can_2003}
-  Hsieh, C.-T., and E. Moretti. 2003. Can Free Entry Be Inefficient? Fixed Commissions and Social Waste in the Real Estate Industry. \textit{Journal of Political Economy}, 111(5), 1076-1122.
-
-  \bibitem[Hui and Chan(2014)]{hui_foreign_2014}
-  Hui, E. C. M., and K. K. K. Chan. 2014. Foreign Direct Investment in China's Real Estate Market. \textit{Habitat International}, 43, 231-239.
-
-  \bibitem[Piazzesi et al.(2020)]{piazzesi_segmented_2020}
-  Piazzesi, M., M. Schneider, and J. Stroebel. 2020. Segmented Housing Search. \textit{American Economic Review}, 110(3), 720-759.
-
-  \bibitem[Qu et al.(2021)]{qu_identifying_2021}
-  Qu, W., Y. Huang, and G. Deng. 2021. Identifying the Critical Factors Behind the Second-Hand Housing Price Concession: Empirical Evidence from China. \textit{Habitat International}, 117, 102442.
-
-  \bibitem[Salz(2022)]{salz_intermediation_2022}
-  Salz, T. 2022. Intermediation and Competition in Search Markets: An Empirical Case Study. \textit{Journal of Political Economy}, 130(2), 310-345.
-
-  \bibitem[Williams(1998)]{williams_agency_1998}
-  Williams, J. T. 1998. Agency and Brokerage of Real Assets in Competitive Equilibrium. \textit{Review of Financial Studies}, 11(2), 239-280.
-
-  \bibitem[Wong et al.(2012)]{wong_liquidity_2012}
-  Wong, S. K., C. Y. Yiu, and K. W. Chau. 2012. Liquidity and Information Asymmetry in the Real Estate Market. \textit{The Journal of Real Estate Finance and Economics}, 45(1), 49-62.
-
-  \bibitem[Zhao(2015)]{zhao_rational_2015}
-  Zhao, B. 2015. Rational Housing Bubble. \textit{Economic Theory}, 60(1), 141-201.
 
@@
 
-  \bibitem[Zhang et al.(2021)]{zhang_online_2021}
-  Zhang, X., Z.
-Lin, Y.
-Zhang, Y.
-Zheng, and J.
-Zhang.
-2021.
-Online Property Brokerage Platform and Prices of Second-Hand Houses: Evidence from Lianjia's Entry.
-\textit{Electronic Commerce Research and Applications}, 50, 101104.
-
-  \bibitem[Wei and Zhang(2011)]{wei_competitive_2011}
-  Wei, S.-J., and X. Zhang. 2011. The Competitive Saving Motive: Evidence from Rising Sex Ratios and Savings Rates in China. \textit{Journal of Political Economy}, 119(3), 511-564.
-
-  \bibitem[Zhao et al.(2017)]{zhao_forecasting_2017}
-  Zhao, N., Y.
-Liu, G.
-Cao, E.
-L.
-Samson, and J.
-Zhang.
-2017.
-Forecasting China's GDP at the Pixel Level Using Nighttime Lights Time Series and Population Images.
-\textit{GIScience \& Remote Sensing}, 54(3), 407-425.
-
-  \bibitem[Akerlof(1970)]{Akerlof_1970}
-  Akerlof, G. A. 1970. The Market for "Lemons": Quality Uncertainty and the Market Mechanism. \textit{The Quarterly Journal of Economics}, 84(3), 488-500.
-
-  \bibitem[Yang et al.(2021)]{YANG2021102359}
-  Yang, L., K. W. Chau, and Y. Chen. 2021. Impacts of Information Asymmetry and Policy Shock on Rental and Vacancy Dynamics in Retail Property Markets. \textit{Habitat International}, 111, 102359.
-
-  \bibitem[Barwick and Pathak(2015)]{https://doi.org/10.1111/1756-2171.12082}
-  Barwick, P. J., and P. A. Pathak. 2015. The Costs of Free Entry: An Empirical Study of Real Estate Agents in Greater Boston. \textit{The RAND Journal of Economics}, 46(1), 103-145.
-
-  \bibitem[Barwick et al.(2017)]{10.1257/app.20160214}
-  Barwick, P. J., P. A. Pathak, and M. Wong. 2017. Conflicts of Interest and Steering in Residential Brokerage. \textit{American Economic Journal: Applied Economics}, 9(3), 191-222.
+\bibitem[Farrell and Shapiro(1990)]{farrell_horizontal_1990}
+Farrell, J., and C. Shapiro. 1990. Horizontal Mergers: An Equilibrium Analysis. \textit{American Economic Review}, 80(1), 107-126.
+
+\bibitem[Genesove and Han(2012)]{GENESOVE201231}
+Genesove, D., and L. Han. 2012. Search and Matching in the Housing Market. \textit{Journal of Urban Economics}, 72(1), 31-45.
+
+\bibitem[Glaeser et al.(2017)]{glaeser_real_2017}
+Glaeser, E., W. Huang, Y. Ma, and A. Shleifer. 2017. A Real Estate Boom with Chinese Characteristics. \textit{Journal of Economic Perspectives}, 31(1), 93-116.
+
+\bibitem[Grossman and Stiglitz(1980)]{grossman_impossibility_1980}
+Grossman, S. J., and J. E. Stiglitz. 1980. On the Impossibility of Informationally Efficient Markets. \textit{American Economic Review}, 70(3), 393-408.
+
+\bibitem[Han and Hong(2011)]{550a6ccf-cde2-3dd1-979f-1a8db2b8ceb9}
+Han, L., and S.-H. Hong. 2011. Testing Cost Inefficiency Under Free Entry in the Real Estate Brokerage Industry. \textit{Journal of Business \& Economic Statistics}, 29(4), 564-578.
+
+\bibitem[Han and Strange(2015)]{HAN2015813}
+Han, L., and W. C. Strange. 2015. The Microstructure of Housing Markets: Search, Bargaining, and Brokerage. In \textit{Handbook of Regional and Urban Economics}, Vol. 5, pp. 813-886.
+
+\bibitem[Handbury(2021)]{handbury_are_2021}
+Handbury, J. 2021. Are Poor Cities Cheap for Everyone? Non-Homotheticity and the Cost of Living Across U.S. Cities. \textit{Econometrica}, 89(6), 2679-2715.
+
+\bibitem[Hendel et al.(2009)]{hendel_relative_2009}
+Hendel, I., A. Nevo, and F. Ortalo-Magné. 2009. The Relative Performance of Real Estate Marketing Platforms: MLS versus FSBOMadison.com. \textit{American Economic Review}, 99(5), 1878-1898.
+
+\bibitem[Hong(2022)]{https://doi.org/10.1002/jae.2891}
+Hong, S.-H. 2022. Real Estate Agents' Influence on Housing Search. \textit{Journal of Applied Econometrics}, 37(3), 563-582.
+
+\bibitem[Hotelling(1929)]{hotelling_stability_1929}
+Hotelling, H. 1929. The Stability in Competition. \textit{Economic Journal}, 39, 41-57.
+
+\bibitem[Hsieh and Moretti(2003)]{hsieh_can_2003}
+Hsieh, C.-T., and E. Moretti. 2003. Can Free Entry Be Inefficient? Fixed Commissions and Social Waste in the Real Estate Industry. \textit{Journal of Political Economy}, 111(5), 1076-1122.
+
+\bibitem[Hui and Chan(2014)]{hui_foreign_2014}
+Hui, E. C. M., and K. K. K. Chan. 2014. Foreign Direct Investment in China's Real Estate Market. \textit{Habitat International}, 43, 231-239.
+
+\bibitem[Jud et al.(1996)]{doi:10.1080/10835547.1996.12090852}
+Jud, D., T. Seaks, and D. Winkler. 1996. Time on the Market: The Impact of Residential Brokerage. \textit{Journal of Real Estate Research}, 12(2), 447-458.
+
+\bibitem[Langley and Leyshon(2017)]{Langley_Leyshon_2017}
+Langley, P., and A. Leyshon. 2017. Platform Capitalism: The Intermediation and Capitalisation of Digital Economic Circulation. \textit{Finance and Society}, 3(1), 11-31.
 
@@
 
+\bibitem[Li and Qi(2022)]{10.1093/cje/beac054}
+Li, Z., and H. Qi. 2022. Platform Power: Monopolisation and Financialisation in the Era of Big Tech. \textit{Cambridge Journal of Economics}, 46(6), 1289-1314.
+
+\bibitem[Liu et al.(2023)]{liu2023chrono-urbanism}
+Liu, D., M.-P.
+Kwan, L.
+Wang, Z.
+Kan, J.
+Wang, and J.
+Huang.
+2023.
+Development of a Chrono-Urbanism Status Composite Index under the 5/10/15-Minute City Concept Using Social Media Big Data.
+\textit{Tijdschrift voor Economische en Sociale Geografie}, Early View.
+doi:10.1111/tesg.12613.
+
+\bibitem[Machado and Santos Silva(2019)]{machado_quantiles_2019}
+Machado, J. A. F., and J. M. C. Santos Silva. 2019. Quantiles via Moments. \textit{Journal of Econometrics}, 213(1), 145-173.
+
+\bibitem[McCrary(2008)]{MCCRARY2008698}
+McCrary, J. 2008. Manipulation of the Running Variable in the Regression Discontinuity Design: A Density Test. \textit{Journal of Econometrics}, 142(2), 698-714.
+
+\bibitem[MOHURD(2018)]{GB50180-2018}
+Ministry of Housing and Urban-Rural Development of China.
+2018.
+\textit{Urban Residential Area Planning and Design Standard (GB50180-2018)}.
+Available from \url{http://www.moe.gov.cn/jyb_xwfb/xw_zt/moe_357/jyzt_2019n/2019_zt13/zcwj/201906/t20190606_384732.html}.
+(in Chinese).
+
+\bibitem[Peng(2023)]{peng_mortgage_2023}
+Peng, Y.
+2023.
+Mortgage Credit and Housing Markets.
+\textit{SSRN Electronic Journal}, Working Paper.
+Available at \url{https://ssrn.com/abstract=4537500} or \url{http://dx.doi.org/10.2139/ssrn.4537500}.
+
+\bibitem[Piazzesi et al.(2020)]{10.1257/aer.20141772}
+Piazzesi, M., M. Schneider, and J. Stroebel. 2020. Segmented Housing Search. \textit{American Economic Review}, 110(3), 720-759.
+
+\bibitem[Piazzesi et al.(2020)]{piazzesi_segmented_2020}
+Piazzesi, M., M. Schneider, and J. Stroebel. 2020. Segmented Housing Search. \textit{American Economic Review}, 110(3), 720-759.
+
 \bibitem[Pope et al.(2015)]{POPE201589}
@@
 
-  \bibitem[Han and Strange(2015)]{HAN2015813}
-  Han, L., and W. C. Strange. 2015. The Microstructure of Housing Markets: Search, Bargaining, and Brokerage. In \textit{Handbook of Regional and Urban Economics}, Vol. 5, pp. 813-886. Elsevier.
-
-  \bibitem[Genesove and Han(2012)]{GENESOVE201231}
-  Genesove, D., and L. Han. 2012. Search and Matching in the Housing Market. \textit{Journal of Urban Economics}, 72(1), 31-45.
-
-  \bibitem[Han and Hong(2011)]{550a6ccf-cde2-3dd1-979f-1a8db2b8ceb9}
-  Han, L., and S.-H. Hong. 2011. Testing Cost Inefficiency Under Free Entry in the Real Estate Brokerage Industry. \textit{Journal of Business \& Economic Statistics}, 29(4), 564-578.
-
-  \bibitem[Van Nieuwerburgh and Veldkamp(2010)]{NIEUWERBURGH_information}
-  Van Nieuwerburgh, S., and L. Veldkamp. 2010. Information Acquisition and Under-Diversification. \textit{The Review of Economic Studies}, 77(2), 779-805.
-
-  \bibitem[Zhang et al.(2021)]{ZHANG2021101104}
-  Zhang, X., Z.
-Lin, Y.
-Zhang, Y.
-Zheng, and J.
-Zhang.
-2021.
-Online Property Brokerage Platform and Prices of Second-Hand Houses: Evidence from Lianjia’s Entry.
-\textit{Electronic Commerce Research and Applications}, 50, 101104.
-
-  \bibitem[Agarwal et al.(2019)]{AGARWAL2019715}
-  Agarwal, S., J. He, T. F. Sing, and C. Song. 2019. Do Real Estate Agents Have Information Advantages in Housing Markets? \textit{Journal of Financial Economics}, 134(3), 715-735.
-
-  \bibitem[Piazzesi et al.(2020)]{10.1257/aer.20141772}
-  Piazzesi, M., M. Schneider, and J. Stroebel. 2020. Segmented Housing Search. \textit{American Economic Review}, 110(3), 720-759.
-
-  \bibitem[Hong(2022)]{https://doi.org/10.1002/jae.2891}
-  Hong, S.-H. 2022. Real Estate Agents' Influence on Housing Search. \textit{Journal of Applied Econometrics}, 37(3), 563-582.
+\bibitem[Qu et al.(2021)]{qu_identifying_2021}
+Qu, W., Y. Huang, and G. Deng. 2021. Identifying the Critical Factors Behind the Second-Hand Housing Price Concession: Empirical Evidence from China. \textit{Habitat International}, 117, 102442.
+
+\bibitem[Rochet and Tirole(2003)]{10.1162/154247603322493212}
+Rochet, J.-C., and J. Tirole. 2003. Platform Competition in Two-Sided Markets. \textit{Journal of the European Economic Association}, 1(4), 990-1029.
+
+\bibitem[Rosen(1974)]{Rosen_hedonic}
+Rosen, S.
+1974.
+Hedonic Prices and Implicit Markets: Product Differentiation in Pure Competition.
+\textit{Journal of Political Economy}, 82(1), 34-55.% Available at \url{http://www.jstor.org/stable/1830899}.
+
+\bibitem[Salz(2022)]{salz_intermediation_2022}
+Salz, T. 2022. Intermediation and Competition in Search Markets: An Empirical Case Study. \textit{Journal of Political Economy}, 130(2), 310-345.
+
+\bibitem[Sirmans et al.(1991)]{SIRMANS1991207}
+Sirmans, C. F., G. K. Turnbull, and J. D. Benjamin. 1991. The Markets for Housing and Real Estate Broker Services. \textit{Journal of Housing Economics}, 1(3), 207-217.
 
@@
 
+\bibitem[Van Nieuwerburgh and Veldkamp(2010)]{NIEUWERBURGH_information}
+Van Nieuwerburgh, S., and L. Veldkamp. 2010. Information Acquisition and Under-Diversification. \textit{The Review of Economic Studies}, 77(2), 779-805.
+
+\bibitem[Varian(2014)]{10.1257/jep.28.2.3}
+Varian, H. R. 2014. Big Data: New Tricks for Econometrics. \textit{Journal of Economic Perspectives}, 28(2), 3-28.
+
+\bibitem[Wei and Zhang(2011)]{wei_competitive_2011}
+Wei, S.-J., and X. Zhang. 2011. The Competitive Saving Motive: Evidence from Rising Sex Ratios and Savings Rates in China. \textit{Journal of Political Economy}, 119(3), 511-564.
+
+\bibitem[Williams(1998)]{williams_agency_1998}
+Williams, J. T. 1998. Agency and Brokerage of Real Assets in Competitive Equilibrium. \textit{Review of Financial Studies}, 11(2), 239-280.
+
+\bibitem[Wong et al.(2012)]{wong_liquidity_2012}
+Wong, S. K., C. Y. Yiu, and K. W. Chau. 2012. Liquidity and Information Asymmetry in the Real Estate Market. \textit{The Journal of Real Estate Finance and Economics}, 45(1), 49-62.
+
+\bibitem[Yang et al.(2021)]{YANG2021102359}
+Yang, L., K. W. Chau, and Y. Chen. 2021. Impacts of Information Asymmetry and Policy Shock on Rental and Vacancy Dynamics in Retail Property Markets. \textit{Habitat International}, 111, 102359.
+
+\bibitem[Zhang et al.(2021)]{ZHANG2021101104}
+Zhang, X., Z.
+Lin, Y.
+Zhang, Y.
+Zheng, and J.
+Zhang.
+2021.
+Online Property Brokerage Platform and Prices of Second-Hand Houses: Evidence from Lianjia's Entry.
+\textit{Electronic Commerce Research and Applications}, 50, 101104.
+
+\bibitem[Zhang et al.(2021)]{zhang_online_2021}
+Zhang, X., Z.
+Lin, Y.
+Zhang, Y.
+Zheng, and J.
+Zhang.
+2021.
+Online Property Brokerage Platform and Prices of Second-Hand Houses: Evidence from Lianjia's Entry.
+\textit{Electronic Commerce Research and Applications}, 50, 101104.
+
+\bibitem[Zhao et al.(2017)]{zhao_forecasting_2017}
+Zhao, N., Y.
+Liu, G.
+Cao, E.
+L.
+Samson, and J.
+Zhang.
+2017.
+Forecasting China's GDP at the Pixel Level Using Nighttime Lights Time Series and Population Images.
+\textit{GIScience \& Remote Sensing}, 54(3), 407-425.
+
+\bibitem[Zhao(2015)]{zhao_rational_2015}
+Zhao, B. 2015. Rational Housing Bubble. \textit{Economic Theory}, 60(1), 141-201.
+
+\bibitem[Zhu and Iansiti(2019)]{WOS:000454186600016}
+Zhu, F., and M. Iansiti. 2019. Why Some Platforms Thrive and Others Don't. \textit{Harvard Business Review}, 97(1), 118-125.
+
 \bibitem[Zumpano et al.(2003)]{ZUMPANO2003134}
@@
 
-  \bibitem[McCrary(2008)]{MCCRARY2008698}
-  McCrary, J. 2008. Manipulation of the Running Variable in the Regression Discontinuity Design: A Density Test. \textit{Journal of Econometrics}, 142(2), 698-714.
-
-  \bibitem[Sirmans et al.(1991)]{SIRMANS1991207}
-  Sirmans, C. F., G. K. Turnbull, and J. D. Benjamin. 1991. The Markets for Housing and Real Estate Broker Services. \textit{Journal of Housing Economics}, 1(3), 207-217.
-
-  \bibitem[Agarwal et al.(2024)]{AGARWAL2024103668}
-Agarwal, S., Kuang, W., Wang, L., and Yang, Y. 2024. The role of agents in fraudulent activities: Evidence from the housing market in Beijing. \textit{Journal of Urban Economics}, 142, 103668.
-
-  \bibitem[Armstrong(2006)]{Armstrong2006}
-  Armstrong, M. 2006. Competition in Two-Sided Markets. \textit{The RAND Journal of Economics}, 37(3), 668-691.
-
-  \bibitem[Beck et al.(2022)]{doi:10.1080/10527001.2021.2016340}
-  Beck, J., F. Scott, and A. Yelowitz. 2022. The Impact of Real Estate Agent Specialization and Activity Level on Market Outcomes. \textit{Journal of Housing Research}, 31(2), 163-180.
-
-  \bibitem[Jud et al.(1996)]{doi:10.1080/10835547.1996.12090852}
-  Jud, D., T. Seaks, and D. Winkler. 1996. Time on the Market: The Impact of Residential Brokerage. \textit{Journal of Real Estate Research}, 12(2), 447-458.
-
-  \bibitem[Rochet and Tirole(2003)]{10.1162/154247603322493212}
-  Rochet, J.-C., and J. Tirole. 2003. Platform Competition in Two-Sided Markets. \textit{Journal of the European Economic Association}, 1(4), 990-1029.
-
-  \bibitem[Li and Qi(2022)]{10.1093/cje/beac054}
-  Li, Z., and H. Qi. 2022. Platform Power: Monopolisation and Financialisation in the Era of Big Tech. \textit{Cambridge Journal of Economics}, 46(6), 1289-1314.
-
-  \bibitem[Langley and Leyshon(2017)]{Langley_Leyshon_2017}
-  Langley, P., and A. Leyshon. 2017. Platform Capitalism: The Intermediation and Capitalisation of Digital Economic Circulation. \textit{Finance and Society}, 3(1), 11-31.
-
-  \bibitem[Allen et al.(2023)]{RePEc:kap:jrefec:v:67:y:2023:i:3:d:10.1007_s11146-021-09858-w}
-  Allen, M. T., J. D. Benefield, and R. C. Rutherford. 2023. Co-Listing Strategies: Better Transaction Outcomes? \textit{The Journal of Real Estate Finance and Economics}, 67(3), 517-544.
-
-  \bibitem[Varian(2014)]{10.1257/jep.28.2.3}
-  Varian, H. R. 2014. Big Data: New Tricks for Econometrics. \textit{Journal of Economic Perspectives}, 28(2), 3-28.
-
-  \bibitem[Zhu and Iansiti(2019)]{WOS:000454186600016}
-  Zhu, F., and M. Iansiti. 2019. Why Some Platforms Thrive and Others Don't. \textit{Harvard Business Review}, 97(1), 118-125.
-
-  \bibitem[Athey and Imbens(2006)]{https://doi.org/10.1111/j.1468-0262.2006.00668.x}
-  Athey, S., and G.
-W.
-Imbens.
-2006.
-Identification and Inference in Nonlinear Difference-in-Differences Models.
-\textit{Econometrica}, 74(2), 431-497.% Available at \url{https://onlinelibrary.wiley.com/doi/abs/10.1111/j.1468-0262.2006.00668.x}.
-
-  \bibitem[Machado and Santos Silva(2019)]{machado_quantiles_2019}
-Machado, J. A. F., and J. M. C. Santos Silva. 2019. Quantiles via Moments. \textit{Journal of Econometrics}, 213(1), 145-173.
-
-\bibitem[Azmi et al.(2012)]{AZMI2012406}
-Azmi, D.
-I., H.
-A.
-Karim, and M.
-Z.
-M.
-Amin.
-2012.
-Comparing the Walking Behaviour between Urban and Rural Residents.
-\textit{Procedia - Social and Behavioral Sciences}, 68(7), 406-416.
-% Available at \url{https://www.sciencedirect.com/science/article/pii/S1877042812057205}.
-
-\bibitem[Peng(2023)]{peng_mortgage_2023}
-Peng, Y.
-2023.
-Mortgage Credit and Housing Markets.
-\textit{SSRN Electronic Journal}, Working Paper.
-Available at \url{https://ssrn.com/abstract=4537500} or \url{http://dx.doi.org/10.2139/ssrn.4537500}.
-
-\bibitem[Christensen and Timmins(2022)]{RePEc:ucp:jpolec:doi:10.1086/720140}
-Christensen, P., and C. Timmins. 2022. Sorting or Steering: The Effects of Housing Discrimination on Neighborhood Choice. \textit{Journal of Political Economy}, 130(8), 2110-2163.
-
-\bibitem[MOHURD(2018)]{GB50180-2018}
-  Ministry of Housing and Urban-Rural Development of China.
-2018.
-\textit{Urban Residential Area Planning and Design Standard (GB50180-2018)}.
-Available from \url{http://www.moe.gov.cn/jyb_xwfb/xw_zt/moe_357/jyzt_2019n/2019_zt13/zcwj/201906/t20190606_384732.html}.
-(in Chinese).
-
-  \bibitem[Liu et al.(2023)]{liu2023chrono-urbanism}
-  Liu, D., M.-P.
-Kwan, L.
-Wang, Z.
-Kan, J.
-Wang, and J.
-Huang.
-2023.
-Development of a Chrono-Urbanism Status Composite Index under the 5/10/15-Minute City Concept Using Social Media Big Data.
-\textit{Tijdschrift voor Economische en Sociale Geografie}, Early View.
-doi:10.1111/tesg.12613.
   \end{thebibliography}
@@
 
-% \begin{table}[H]
-%   \begin{center}
-%     \begin{scriptsize}
-%     \caption{Robustness Check By Market Maturity Index}
-%     \label{tab:platform_consolidation_hetero_mature}
-%     \input{../result_tables/robust_mature.tex}
-
-%     \end{scriptsize}
-%   \end{center}
-% \end{table}
-
 \begin{figure}[H]

### 2024-07-10 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	modified:   reference/sort_values.txt

@@
 Utilizing a regression discontinuity design (RDD), the study quantifies the optimal influence radius of offline stores (410 meters) on housing transactions.
-Incorporating this optimal influence radius, the study further empirically estimates the effects of real estate brokerage's offline store expansion and platform-based consolidation on transaction properties.
+Incorporating this optimal influence radius, the study further empirically estimates the effects of real estate brokerage's offline store expansion and platform-mediated consolidation on transaction properties.
 The results indicate that this strategy significantly boosts revenues and attracts more people to housing tours.
-The results also suggest that neither the platform-based strategy nor offline expansion affects the transaction period, but offline store expansion can indeed reduce the price gap between sellers and buyers.
+The results also suggest that neither the platform-mediated strategy nor offline expansion affects the transaction period, but offline store expansion can indeed reduce the price gap between sellers and buyers.
 Additionally, we proposed a measure of the network effect and found that Lianjia's offline stores show a local clustering pattern with moderate network strength.
@@
 
-Understanding housing markets is crucial due to their significant impact on household finance, as housing is typically the largest component of a household's portfolio.
-The illiquidity of housing creates a strong link between housing and labor markets, and transaction costs are critical for buyers and sellers in the real estate market.
-Real estate brokers play a vital role in reducing these costs, providing essential market information, negotiation support, and legal assistance to ensure smoother and more efficient transactions.
+% https://www.zaobao.com.sg/realtime/china/story20231213-1455835#:~:text=%E6%8D%AE%E5%A4%AE%E8%A7%86%E6%96%B0%E9%97%BB%E6%8A%A5%E9%81%93%EF%BC%8C%E4%B8%AD%E5%9B%BD,%E6%96%B0%E5%BB%BA%E5%95%86%E5%93%81%E4%BD%8F%E5%AE%85%E4%BA%A4%E6%98%93%E9%87%8F%E3%80%82
+
+According to the Ministry of Housing and Urban-Rural Development in China, the proportion of second-hand housing transactions rose to 37.1\% in 2023, with this trend showing continuous growth.
+Unlike the primary housing market, where transactions are straightforward, the secondary housing market necessitates sellers having access to buyers, thereby making transaction costs a critical factor for both parties.
+In this context, real estate brokers play a pivotal role in mitigating these costs.
+They provide essential market information, negotiation support, and legal assistance, thereby facilitating smoother and more efficient transactions in the real estate market.
+The involvement of brokers reduces the information asymmetry and transactional frictions that are characteristic of the secondary housing market, thus enhancing market efficiency.
 With the improvement of China's legal system in the real estate market, the brokerage market is expanding and becoming more prosperous.
@@
 
-China's real estate listings market possesses distinct features characterized by the prominence of offline stores, setting it apart from the markets in other developed countries.
+Chinese real estate listings market possesses distinct features characterized by the prominence of offline stores, setting it apart from the markets in other developed countries.
 Compared to the United States, where the Multiple Listing Service (MLS) provides comprehensive and reliable information online, facilitating transactions in a market where houses are typically situated far apart, the role of offline real estate stores is minimized.
-In contrast, China's real estate market is predominantly offline-based, with online listings serving mainly as references.
+In contrast, Chinese real estate market is predominantly offline-based, with online listings serving mainly as references.
 Face-to-face interactions remain crucial for transactions.
@@
 
-Additionally, in the China's real estate market, brokerages still operate on a bilateral agency model, where sellers need to choose the agency that can help them sell their home in the fastest time and for the highest price possible for the transaction.
+Additionally, in the Chinese real estate market, brokerages still operate on a bilateral agency model, where sellers need to choose the agency that can help them sell their home in the fastest time and for the highest price possible for the transaction.
 However, due to the asymmetric information inherent in the real estate market, sellers face challenges in effectively informing and matching with potential buyers.
@@
 
-While sellers might consider a co-listing strategy—listing their property with multiple brokerages—this approach is suboptimal for several reasons within China's real estate market.
+While sellers might consider a co-listing strategy—listing their property with multiple brokerages—this approach is suboptimal for several reasons within Chinese real estate market.
 Despite previous literature, such as \citep{RePEc:kap:jrefec:v:67:y:2023:i:3:d:10.1007_s11146-021-09858-w}, indicating that the co-listing can be beneficial for clients under multiple-listing service.
-Specifically in China's real estate market, firstly, the exclusivity of contracts between sellers and agents often precludes the adoption of a co-listing strategy.
+Specifically in Chinese real estate market, firstly, the exclusivity of contracts between sellers and agents often precludes the adoption of a co-listing strategy.
 Secondly, although sellers can list their properties with multiple brokerages, smaller agencies frequently lack a sufficiently broad client base, limiting their effectiveness in selling homes.
@@
 
-To evaluate the effects of platform-mediated consolidation, we consider the year Lianjia implemented its platform-based consolidation strategy as an exogenous shock to the market.
+To evaluate the effects of platform-mediated consolidation, we consider the year Lianjia implemented its platform-mediated consolidation strategy as an exogenous shock to the market.
 This strategy primarily revolves around the ACN framework of Lianjia and the incorporation of various franchise stores into the network.
 Our empirical analysis indicates that this strategy significantly increases revenues and enhances the attraction of buyers and sellers, particularly in the number of house tours facilitated by the brokerage.
-However, our findings suggest that the platform-based consolidation does not effectively reduce the transaction period nor does it promote price concessions.
+However, our findings suggest that the platform-mediated consolidation does not effectively reduce the transaction period nor does it promote price concessions.
 This contrasts with the offline expansion strategy, which demonstrates a positive impact on promoting price concessions.
@@
 
-The literature on the real estate market, particularly the role of real estate brokerages, is extensive and informative, starting with the foundational work of \citet{Rosen_hedonic} who introduced the hedonic pricing model.
+The literature on the real estate market, particularly the role of real estate brokerages, is extensive and informative, starting with the foundational work of \citep{Rosen_hedonic} who introduced the hedonic pricing model.
 This model breaks down property prices by analyzing internal and external factors.
@@
 
-Finally, the concept of the platform as a "two-sided market" or kind of intermediates that connects the buyer side and seller side digitally, \citep{10.1162/154247603322493212, Langley_Leyshon_2017}.
-Despite the significant attention given to online platforms, there is a lack of systematic analysis on the impact of offline stores of online platforms on market performance or on real estate brokerage.
+Finally, the concept of the platform as a "two-sided market" or kind of intermediates that connects the buyer side and seller side digitally, \citep{10.1162/154247603322493212, Langley_Leyshon_2017, 10.1257/aer.100.4.1642}.
+\citet{https://doi.org/10.1111/j.1756-2171.2006.tb00036.x} characterizes real estate brokerages as a two-sided market.
+In this model, brokerages must effectively communicate and mediate between sellers and buyers, facilitating transactions and ensuring efficient market operations.
+Despite the significant attention given to online platforms and real estate broekerage's two-sided market \citep{10.1257/jep.23.3.125}, there is a lack of systematic analysis on the impact of offline stores of online platforms on market performance or on real estate brokerage.
 Therefore, this paper aims to fill this gap by examining the influence of offline stores associated with online platforms on the real estate market.
 
-% With respect to the behavior of real estate brokerages, the research conducted by \citep{AGARWAL2019715} substantiates that these entities, acting as intermediaries in market transactions, possess superior knowledge of market dynamics.
-This informational superiority enables the intermediaries to use their bargaining power to secure discounts in the market.
-Similarly, \citet{HAN2015813} articulates that brokerages operating in unidirectional and bidirectional markets exhibit different levels of bargaining leverage, leading to different motivational drivers.
-This mechanism is in line with other research, which shows that properties with lower commission rates have a 5\% less likelihood of being sold and takes 12\% longer to sell \citep{10.1257/app.20160214}.
-
-% Regarding the impact of online platforms on the real estate sector, research by \citep{ZUMPANO2003134} suggests that while the length of time buyers spend searching for properties remains unchanged, the scope of their search expands to include a greater number of online listings.
-\citet{ZHANG2021101104} show that the introduction of online platforms is associated with reductions in existing home prices and increased sales volumes, effects that are influenced by new home prices and household size.
-However, a comprehensive analysis of the influence of the physical stores of online platforms on the real estate market is still lacking in the literature.
-
-% Finally, the impact of real estate intermediaries on the market can be decomposed into several aspects.
-Using a model based on the assumption of a perfectly competitive market in which an influx of brokers competitively enters the market, \citet{williams_agency_1998} shows that the presence of brokers in the market equilibrium exceeds the optimal number of allocations, thereby causing a reduction in social welfare.
-Moreover, the results show that neither brokers nor sellers are motivated to deviate from the equilibrium price structure, which coincides with the reservation price set by sellers.
-Complementary research in another study shows that a significant influx of brokers into the market is correlated with a decrease, rather than an increase, in house prices, along with a gradual decrease in transaction cycles within the market \citep{https://doi.org/10.1002/jae.2891}.
-Furthermore, the work of \citep{qu_identifying_2021-1} highlights the moderating role of broker commissions on the dissemination of market information during transactions.
-Their findings suggest that the use of a broker can significantly mitigate the concessions that sellers are forced to make in the transaction process, thereby enhancing their ability to complete a home sale more efficiently.
-
-% Many literature has been conducted to study the real estate market, and the impact of real estate brokerages on the market, beginning with \citet{Rosen_hedonic}, which proposed a hedonic pricing model and decomposed the price by internal and external factors affecting it.
-However, the hedonic pricing model suffers from market asymmetry and information inequality.
-The seminal work on the impact of asymmetric information in markets is \citep{Akerlof_1970}, which demonstrated that markets for used cars tend to be dominated by low-quality goods, or 'lemons', leading to market inefficiencies.
-Furthermore, \citet{grossman_impossibility_1980} further argued that information effective market assumption is hard to hold in reality.
-Therefore, the real estate market, which is characterized by information asymmetry, is particularly vulnerable to the adverse selection problem.
-In this context, the role of real estate brokerages is crucial, as they act as intermediaries between buyers and sellers, providing valuable information and facilitating transactions.
-
-% 由于房地产中介行业线上推广线下成交的机制，中介机构在线下门店中的服务性质对于其在客源方的影响具有很高的价值。链家通常选择在每个目标小区的周边开店便是该原理。链家通过在小区周边大范围开店，从而吸引卖方选择该机构进行挂牌，而又通过其广泛的平台客源来吸引市场中的买方从而获得更多的成交数量与成交收入。由于房地产中介行业线上推广线下成交的机制，中介机构在线下门店中的服务性质对于其在客源方的影响具有很高的价值。链家通常选择在每个目标小区的周边开店便是该原理。链家通过在小区周边大范围开店，从而吸引卖方选择该机构进行挂牌，而又通过其广泛的平台客源来吸引市场中的买方从而获得更多的成交数量与成交收入。
+To our knowledge, this paper represents the pioneering empirical investigation into the effects of offline store expansion and platform-mediated consolidation within the real estate brokerage market.
+Furthermore, it is the first to analyze the local network effects within the specific context of real estate transactions.
+Additionally, this paper systematically examines how informational advantages can enhance brokerage revenue within the framework of local network effects.
+By delving into these dynamics, we aim to contribute to the broader economics literature by providing a nuanced understanding of how offline and online integration influences market behavior and outcomes.
+Our findings offer meaningful insights into the strategic decisions of real estate brokerages, highlighting the significance of network effects and informational advantages in shaping competitive advantage and market performance.
+This research not only fills critical gaps in the literature but also provides a comprehensive framework for future studies to explore the intersection of offline expansion, digital consolidation, and local network effects in various economic contexts.
+By systematically examining these phenomena, we enhance the understanding of how technological and infrastructural developments can drive revenue generation and market consolidation in the real estate industry and beyond.
 
@@
 This study focuses on the housing markets in ten major cities in China, namely Beijing, Shanghai, Chongqing, Tianjin, Shenzhen, Guangzhou, Chengdu, Hangzhou, Wuhan and Nanjing.
-These cities are not only pivotal to China's economic development, but also serve as exemplars of the broader trends and characteristics inherent in the China's real estate dynamics.
-Spanning from 2016 to 2022, the research period encapsulates a pivotal era in China's real estate sector.
+These cities are not only pivotal to China's economic development, but also serve as exemplars of the broader trends and characteristics inherent in the Chinese real estate dynamics.
+Spanning from 2016 to 2022, the research period encapsulates a pivotal era in Chinese real estate sector.
 During the first phase of the study, from 2016 to 2019, the housing markets in these cities experienced a remarkable boom.
@@
 These results underscore the superior efficacy of platform consolidation in enhancing market performance and provide compelling evidence for the strategic advantage of consolidation over traditional offline expansion.
-However, in terms of the transaction period, the platformization strategy does not exhibit a significant effect, indicating that platformization does not assist brokerages in facilitating better matching and negotiation between sellers and buyers.
+However, in terms of the transaction period, the consolidation strategy does not exhibit a significant effect, indicating that consolidation does not assist brokerages in facilitating better matching and negotiation between sellers and buyers.
 Moreover, in terms of the platform's consolidation effect on price concessions, we find that the effect is significant after the first period, with a 4.2\% increase in the first year after the treatment and a 7.1\% increase in the second year.
@@
 The high HHI group, representing markets with higher concentration, revealed that the platform consolidation strategy does not confer significant benefits for Lianjia's operations.
-Conversely, in the low HHI group, indicative of less competitive markets, the platformization strategy significantly increases the transaction number.
+Conversely, in the low HHI group, indicative of less competitive markets, the consolidation strategy significantly increases the transaction number.
 This suggests that the platform consolidation strategy is more effective in less competitive markets, enhancing Lianjia's competitiveness.
@@
 This consistency aligns with the intuition that consumer preferences for different types of brokerages are similar, and individuals are equally likely to search for houses online regardless of the brokerage's market share.
-Moreover, our analysis in columns 5 to 8 shows that the platformization strategy does not have a significant effect on the transaction period or price concessions.
-This finding suggests that the platformization strategy does not facilitate better matching between buyers and sellers or improve the negotiation process.
-This aligns with the intuition that while the platformization strategy can attract more customers and generate revenue, it does not inherently improve the efficiency of matching buyers and sellers or negotiating terms because most of the transactions are still offline based.
+Moreover, our analysis in columns 5 to 8 shows that the consolidation strategy does not have a significant effect on the transaction period or price concessions.
+This finding suggests that the consolidation strategy does not facilitate better matching between buyers and sellers or improve the negotiation process.
+This aligns with the intuition that while the consolidation strategy can attract more customers and generate revenue, it does not inherently improve the efficiency of matching buyers and sellers or negotiating terms because most of the transactions are still offline based.
 
@@
 
-Our study highlights the transformative impact of Lianjia's strategic expansion in China's real estate brokerage industry through the implementation of the online-mediated consolidation strategy and the massive expansion of offline branches.
+Our study highlights the transformative impact of Lianjia's strategic expansion in Chinese real estate brokerage industry through the implementation of the online-mediated consolidation strategy and the massive expansion of offline branches.
 Our empirical research demonstrates that Lianjia's approach, which seamlessly integrates online platforms with an extensive offline presence, significantly enhances revenue generation and influences consumer behavior through improved price concessions and increased number of house tours.
@@
 Second, examining the role of emerging technologies, such as artificial intelligence and blockchain, in further enhancing the efficiency and transparency of real estate transactions would be valuable.
-Third, assessing the socio-economic implications of platform-based monopolization, particularly in terms of access to affordable housing and regional economic disparities, could offer important policy implications.
+Third, assessing the socio-economic implications of platform monopolization, particularly in terms of access to affordable housing and regional economic disparities, could offer important policy implications.
 Lastly, exploring the adaptability of the online-offline integration model in other sectors, such as healthcare and education, could extend the applicability of these findings and contribute to a broader understanding of digital transformation across industries.
@@
 \bibitem[Hui and Chan(2014)]{hui_foreign_2014}
-Hui, E. C. M., and K. K. K. Chan. 2014. Foreign Direct Investment in China's Real Estate Market. \textit{Habitat International}, 43, 231-239.
+Hui, E. C. M., and K. K. K. Chan. 2014. Foreign Direct Investment in Chinese real estate Market. \textit{Habitat International}, 43, 231-239.
 
@@
 
+\bibitem[Rochet and Tirole(2006)]{https://doi.org/10.1111/j.1756-2171.2006.tb00036.x}
+Rochet, J.-C., and J. Tirole. 2006. Two-Sided Markets: A Progress Report. \textit{The RAND Journal of Economics} 37(3): 645-667. % https://doi.org/10.1111/j.1756-2171.2006.tb00036.x.
+
 \bibitem[Rosen(1974)]{Rosen_hedonic}
@@
 \textit{Journal of Political Economy}, 82(1), 34-55.% Available at \url{http://www.jstor.org/stable/1830899}.
+
+\bibitem[Rysman(2009)]{10.1257/jep.23.3.125}
+Rysman, M. 2009. The Economics of Two-Sided Markets. \textit{Journal of Economic Perspectives} 23(3): 125-143. % https://doi.org/10.1257/jep.23.3.125.
 
@@
 
+\bibitem[Weyl(2010)]{10.1257/aer.100.4.1642}
+Weyl, E. G. 2010. A Price Theory of Multi-Sided Platforms. \textit{American Economic Review} 100(4): 1642-1672. % https://doi.org/10.1257/aer.100.4.1642.
+
 \bibitem[Williams(1998)]{williams_agency_1998}
@@
 
-\subsection{Alternative Methods} \label{subsec:alternative_methods}
-
 % Freeman, L. C. (1977). A set of measures of centrality based on betweenness. Sociometry, 40(1), 35-41.

### 2024-07-10 manuscript/main.tex
update the changes

@@
 Additionally, the entry of Lianjia's offline stores can help the brokerage attract more sellers and, consequently, find more buyers in the market, thereby increasing the brokerage's informational advantage.
-In the Appendix we also conducted the robustness check by classifying the group by matured market and less matured market.
+In the Appendix we also conducted the robustness check by classifying the market with low and high nighttime light areas and the results are reported in Appendix Table \ref{tab:robustness_nighttime_light_entry}.
 
@@
 The test result also shows that there is no other confounding factors affecting our analysis.
+In the Appendix Table \ref{tab:robustness_nighttime_light_consolidation}, we also classified the samples to low and high nighttime light areas, and the results show that our results are robust.
 
@@
 
+\begin{table}
+  \begin{center}
+    \begin{scriptsize}
+      \caption{Robustness Check for Offline Expansion Effect Using Nighttime Lights}
+      \label{tab:robustness_nighttime_light_entry}
+      \input{../result_tables/entry_light_robustness.tex}
+
+    Note: we omit all the control variables in the regression model, and detailed descriptions can be seen from Table \ref{tab:statistical_district} and Table \ref{tab:statistical_individual}.
+    \end{scriptsize}
+  \end{center}
+\end{table}
+
+\subsection{Robustness Check by Dividing the Samples to Low and High Nighttime Lights} \label{subsec:nighttime_light_robustness_check}
+
+\begin{table}
+  \begin{center}
+    \begin{scriptsize}
+      \caption{Robustness Check for Platform Consolidation Effect Using Nighttime Lights}
+      \label{tab:robustness_nighttime_light_consolidation}
+      \input{../result_tables/plat_light_robustness.tex}
+
+    Note: we omit all the control variables in the regression model, and detailed descriptions can be seen from Table \ref{tab:statistical_district} and Table \ref{tab:statistical_individual}.
+    \end{scriptsize}
+  \end{center}
+\end{table}
+
 \subsection{Placebo Test} \label{subsec:placebo_test}

### 2024-07-10 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

@@
 
-\section{Mechanism Design} \label{sec:mechanism_design}
+\section{Estimation of Offline Expansion Effect and Online-Mediated Consolidation Effect} \label{sec:mechanism_design}
 
@@
 Additionally, offline stores possess better control over neighborhood information, which aids in effectively marketing properties to potential buyers, thereby capturing additional surplus.
-
-In summary, the entry of Lianjia into a segmented market initially results in a significant increase in revenue and facilitates a higher number of house tours, which, in turn, leads to greater price concessions.
-However, this positive impact is transient, diminishing over time due to increased market competition and external factors such as the COVID-19 pandemic.
-This suggests that while Lianjia's entry provides a short-term boost to its market performance, the sustainability of this effect is challenged by both competitive dynamics and unforeseen external shocks.
 
@@
 Additionally, the entry of Lianjia's offline stores can help the brokerage attract more sellers and, consequently, find more buyers in the market, thereby increasing the brokerage's informational advantage.
+
+To further check the robustness of our results, we conducted another three tests.
+In the Appendix, we conducted the same estimation but without additional control variables and the results are reported in Appendix Table \ref{tab:entry_effect_robustness_1} and Appendix Table \ref{tab:entry_effect_robustness_2}.
+The estiamted results are shown consistent without additional control variabels.
 In the Appendix we also conducted the robustness check by classifying the market with low and high nighttime light areas and the results are reported in Appendix Table \ref{tab:robustness_nighttime_light_entry}.
 
-We conducted a placebo test, as illustrated in Figure \ref{fig:placebo_concession_entry}.
+We also conducted a placebo test, as illustrated in Figure \ref{fig:placebo_concession_entry}.
 For this test, we employed a neighborhood sample with randomly generated treatment effects.
@@
 
-\begin{table}
+\begin{table}[H]
   \begin{center}
@@
 The treatment effect becomes significant only after the first period, aligning with our empirical findings.
+
+Same as the Section \ref{subsec:entry_effect}, we performed the estimation without incorporating additional control variables, as documented in Appendix Table \ref{tab:robustness_check_platform_1} and Appendix Table \ref{tab:robustness_check_platform_2}.
+The findings remain consistent with our initial estimates.
+In the Appendix Table \ref{tab:robustness_nighttime_light_consolidation}, we also categorize the sample into areas with low and high nighttime light.
+The results from this stratification further corroborate the robustness of our original conclusions.
+
 We conducted a placebo test, as illustrated in Figure \ref{fig:placebo_concession_plat} like our previous estimation of the offline store expansion.
 The test result also shows that there is no other confounding factors affecting our analysis.
-In the Appendix Table \ref{tab:robustness_nighttime_light_consolidation}, we also classified the samples to low and high nighttime light areas, and the results show that our results are robust.
 
@@
 
-\clearpage
-
-Section{Additional Robustness Check of Main Results} \label{sec:additional_robustness}
+\newpage
+
+\section{Additional Robustness Check of Main Results} \label{sec:additional_robustness}
 
@@
 
-\begin{table}
+In this section, we report the robustness check of DID model.
+Table \ref{tab:robustness_check_additional_1}, Table \ref{tab:robustness_check_additional_2} display the estimation outcomes without the inclusion of additional control variables.
+By comparing these results with those obtained when controls are included, we observe that the estimates remain consistent across different model specifications.
+This consistency indicates the robustness of our findings, reinforcing the validity of our conclusions.
+
+\begin{table}[H]
   \begin{center}
@@
 
-\begin{table}
+Table \ref{tab:robustness_check_platform_1} and \ref{tab:robustness_check_platform_2} shows the results or our estimation with or without additional control variables, and the results are consistent.
+
+\begin{table}[H]
   \begin{center}
@@
 \clearpage
+
+Figure \ref{fig:treatment_consolidation} shows the statistical summary of the Lianjia's summary with the treatment group and the control grouls.
+We can see that the general trend is similar to the estimation results.
 
@@
 
-\begin{table}
+\subsection{Robustness Check by Dividing the Samples to Low and High Nighttime Lights} \label{subsec:nighttime_light_robustness_check}
+
+Table \ref{tab:robustness_nighttime_light_entry} and Table \ref{tab:robustness_nighttime_light_consolidation} show the additional results of the DID model by classifying the samples to low and high nighttime light areas.
+The results show that there is heterogeneity effect across different areas, but the general estimation results are in line with our main model.
+
+\begin{table}[H]
   \begin{center}
@@
 
-\subsection{Robustness Check by Dividing the Samples to Low and High Nighttime Lights} \label{subsec:nighttime_light_robustness_check}
-
-\begin{table}
+\begin{table}[H]
   \begin{center}
@@
 \subsection{Placebo Test} \label{subsec:placebo_test}
+
+Figure \ref{fig:placebo_test_entry} and Figure \ref{fig:placebo_test_plat} show the results of the placebo test for the entry effect and the platform consolidation effect.
+The results show that the random treatment effect is non-significant at the 10\% level, indicating that the treatment effect is not due to other factors.
 

### 2024-07-10 manuscript/main.tex
modified:   analysis/RD design analysis.Rmd 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	modified:   result_tables/rdd_result_summary.tex

@@
 
-  \textbf{Keyword}: Marketing Strategy, Platforms, Platform-Mediated Consolidation, Real Estate Brokerage
-
-  \textbf{JEL} Classification Codes: D4, L1, L8, R3
+  \textbf{Keyword}: Real estate brokerage, Platform-mediated consolidation, Offline store operation, Franchise network
+
+  \textbf{JEL} Classification Codes: R30, R31, L85, L86
 \end{singlespace}
@@
     \subfloat[RDD plot with third order polynomial]{\includegraphics[width=0.5\textwidth]{../figures/RD_Plot_3rd_Order.pdf}\label{fig:RD_Plot_3rd_Order}}
-    \caption{RDD design}
+    \caption{RDD with Different Polynomial Orders}
     \label{fig:RD_design}
+
+    Note that the running variable is divided into 40 bins, considering only the samples within the specified bandwidth.
+The polynomial order for the RDD analysis ranges from 1 to 3.
+Each plot illustrates the relationship between the community transaction revenue and the nearest distance to Lianjia's stores, with the discontinuity point at the cutoff.
 \end{figure}
@@
 
-    Note that the code book of the variables can be seen in the Appendix \ref{tab:codebook}
+    Note that the code book of the variables can be seen in the Appendix \ref{tab:codebook} and with or without lianjia represent whether there are Lianjia's offline stores within the influential radius.
     \end{tiny}
@@
 
-  Note that the code book of the variables can be seen in the Appendix \ref{tab:codebook}
+  Note that the code book of the variables can be seen in the Appendix \ref{tab:codebook} and with or without lianjia represent whether there are Lianjia's offline stores within the influential radius.
   \end{tiny}  

### 2024-07-17 manuscript/main.tex
Add files via upload

@@
 During this period, China's overall economic growth rate has been slower significantly, which has also reflected in a slowdown in the real estate markets of these major cities.
-In addition, the Chinese government has implemented strict rules in Covid-19 protection, so the real estate agents in these major cities are significantly affected.
+In addition, the Chinese government has implemented strict rules in Covid-19 protection and an unprecedented suite of new policies to prevent house prices from falling, so the real estate agents in these major cities are significantly affected.
 
@@
 
-Each type of POI was matched to our data within a 500-meter radius, a distance typically covered by walking and consistent with urban planning standards for accessible urban design.
+Each type of POI, excluding brokerages offline stores information, was matched to our data within a 500-meter radius, a distance typically covered by walking and consistent with urban planning standards for accessible urban design.
 This radius reflects the immediate urban environment influencing residential desirability and property values, as most of these POIs provide recreational services.
@@
 We plot the relationship between the number of other brokerages's stores and the number of lianjia's stores and the figure is shown in Figure \ref{fig:same_distribution}.
-
-From Table \ref{tab:statistical_district} we can see that the in our metro areas, the neighborhoods with lianjia within the influential radius tends to have higher number of sales, and the final transaction price is also \textyen 910,000 higher than those neighborhoods without lianjia.
+The figure shows that the the number of other brokerages' stores is positively correlated and the general trend tends to be linear, which further suggests that the market is not monopolized by Lianjia.
+
+From Table \ref{tab:statistical_district} we can see that the in our metro areas, the neighborhoods with lianjia within the influential radius tends to have higher number of sales, and the final transaction price is also \textyen 910,000 (approximately 35\%) higher than those neighborhoods without lianjia.
 Moreover, the number of other stores within the influential distance is also signnificantly more than 7.3, which also aligns with our previous intuition that the market is not monopolized by Lianjia.
@@
 This ratio helps mitigate the bias that may arise from the strategic location choices of Lianjia, offering a clearer measure of its market influence relative to competitors.
-This approach aligns with the principles of spatial competition theory, as articulated in \citep{hotelling_stability_1929, daspremont_hotellings_1979} in competition model.
+This approach aligns with the principles of spatial competition theory, as articulated by \citep{hotelling_stability_1929, daspremont_hotellings_1979} in competition model.
 Such a comparative metric not only provides a more accurate reflection of Lianjia's market penetration but also adheres to economic modeling standards by accounting for competitive dynamics in the sector.
@@
 In contrast, the analysis shows no significant effect of DBI on price concessions and transaction time.
-This finding suggests that while a larger share of offline stores within the segmented market increases the number of sales and the number of house tours, it may not be beneficial for mathcing the buyers and sellers.
+This finding suggests that while a larger share of offline stores within the segmented market increases the number of sales and the number of house tours, it may not be beneficial for mathcing the buyers and sellers, as demonstrated by the insignificance of the coefficients of log(transaction period) and price concessions.
 The broader implications point to the strategic advantage of density or market share in driving business performance metrics, except for customers' choices, which appear to be unaffected by changes in market share.

### 2024-07-26 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

@@
 \title{ \vspace*{-2.5cm} \hspace*{-0.5cm}Platform-Mediated Consolidation and Offline Store Expansion: Evidence from Real Estate Brokerages in Major Chinese Cities \footnote{
-The preliminary version was entitled "Property brokerage, Partial monopoly and Housing market" and was presented at The 1st Summer Meeting in Urban Economics, China.
+The preliminary version was presented at The 1st Summer Meeting in Urban Economics, China.
 We are grateful for the comments and suggestions made at the meeting.
@@
 Utilizing a regression discontinuity design (RDD), the study quantifies the optimal influence radius of offline stores (410 meters) on housing transactions.
-Incorporating this optimal influence radius, the study further empirically estimates the effects of real estate brokerage's offline store expansion and platform-mediated consolidation on transaction properties.
+The study empirically estimates the effects of real estate brokerage's offline store expansion and platform-mediated consolidation on transaction properties.
 The results indicate that this strategy significantly boosts revenues and attracts more people to housing tours.
-The results also suggest that neither the platform-mediated strategy nor offline expansion affects the transaction period, but offline store expansion can indeed reduce the price gap between sellers and buyers.
-Additionally, we proposed a measure of the network effect and found that Lianjia's offline stores show a local clustering pattern with moderate network strength.
-We then analyzed the effect of platform-mediated consolidation on network strength and concluded that the effect is significantly positive.
+Additionally, the results suggest that neither the platform-mediated strategy nor offline expansion affects the transaction period, but offline store expansion can reduce the price gap between sellers and buyers.
+Furthermore, the study introduces a measure of network effect, revealing that Lianjia's offline stores exhibit a local clustering pattern with moderate network strength.
+The analysis of platform-mediated consolidation indicates a significantly positive effect on network strength.
 This study provides valuable insights into the synergy between offline store expansion and online platform development, elucidating future trajectories in the evolving real estate brokerage market and analogous sectors.
+Moreover, the research confirms that clustering within a small segmented market allows the company to coexist with competitors, with the large company satisfying the majority of customers while other firms cater to heterogeneous customer needs.
   \end{abstract}
@@
 Chinese real estate listings market possesses distinct features characterized by the prominence of offline stores, setting it apart from the markets in other developed countries.
-Compared to the United States, where the Multiple Listing Service (MLS) provides comprehensive and reliable information online, facilitating transactions in a market where houses are typically situated far apart, the role of offline real estate stores is minimized.
-In contrast, Chinese real estate market is predominantly offline-based, with online listings serving mainly as references.
+Compared to the United States, where the Multiple Listing Service (MLS) provides comprehensive and reliable information online, facilitating transactions in a market where houses are typically situated far apart, the role of offline real estate stores is minimized.\footnote{\citet{hendel_relative_2009} documents that the MLS market experiences a significant growth in recent years.} In contrast, Chinese real estate market is predominantly offline-based, with online listings serving mainly as references.
 Face-to-face interactions remain crucial for transactions.
@@
 This regulatory environment allows real estate brokerages to sometimes post misleading prices to attract potential buyers, subsequently offering private information about other properties.
+Moreover, the Chinese real estate brokerage market operates under a bilateral agency model, resulting in lower transaction efficiency compared to the United States brokerage market.
 In Singapore, the real estate market is heavily influenced by government-coordinated prices and evaluation companies' suggested prices.
@@
 In this arrangement, agents have the flexibility to bring customers for house tours.} Furthermore, the platform-mediated consolidation significantly enhances the network effect, indicating that this consolidation strategy effectively strengthens the network effect of Lianjia's offline stores.
+Lastly, the result also confirms that the clustering within a small segmented market allows the company to coexist with competitors, with the large company satisfying the majority of customers while other firms cater to heterogeneous customer needs.
+Lianjia does not exclude other brokerages from the market, but rather coexists with them, thereby enhancing the overall market competitiveness.
+This finding is consistent with the study by \citep{gilbukh_goldsmith-pinkham_2019}, which indicates that inexperienced intermediaries hold a large market share, but their transaction efficiency is lower compared to experienced intermediaries.
 
@@
 For example, in the retail sector, online marketplaces such as Alibaba in China have significantly outpaced physical stores by consolidating various vendors into a single, accessible platform.
-Lastly, this study demonstrates that, under the platform's consolidation effect, offline stores can enhance revenue and improve transaction efficiency.
+Thirdly, this study demonstrates that, under the platform's consolidation effect, offline stores can enhance revenue and improve transaction efficiency.
 These findings can be extended to other similar fields, as discussed by \citep{10.1257/jep.28.2.3}.
+Lastly, this study also confirms that local network effect can not preclude other competitors from entering the market but the network effect can help the company to coexist with other competitors, and improve the overall market efficiency, consistent with the work by \citep{gilbukh_goldsmith-pinkham_2019}.
 
@@
 Genesove, D., and L. Han. 2012. Search and Matching in the Housing Market. \textit{Journal of Urban Economics}, 72(1), 31-45.
+
+\bibitem[Gilbukh and Goldsmith-Pinkham(2019)]{gilbukh_goldsmith-pinkham_2019}
+Gilbukh, S., and P. Goldsmith-Pinkham. 2019. Heterogeneous Real Estate Agents and the Housing Cycle. Yale University Working Paper.
 

### 2024-07-28 manuscript/main.tex
new file:   manuscript/July26.pdf 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	deleted:    manuscript/July26.pdf 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

@@
 The involvement of brokers reduces the information asymmetry and transactional frictions that are characteristic of the secondary housing market, thus enhancing market efficiency.
+
 With the improvement of China's legal system in the real estate market, the brokerage market is expanding and becoming more prosperous.
+Moreover, it is not merely a matter of legal improvement, as in the past, the intermediary market was quite chaotic, with individuals being able to set up a brokerage business without any qualifications.
+Nowadays, the government has taken steps to regulate the disorderly conduct of intermediaries through administrative and legal measures, leading to a more standardized and orderly market environment.
 Especially in the context of China's burgeoning real estate market, brokerage firms are assuming an increasingly important role in facilitating the communications between buyers and sellers \citep{glaeser_real_2017}.
@@
 
-Chinese real estate listings market possesses distinct features characterized by the prominence of offline stores, setting it apart from the markets in other developed countries.
-Compared to the United States, where the Multiple Listing Service (MLS) provides comprehensive and reliable information online, facilitating transactions in a market where houses are typically situated far apart, the role of offline real estate stores is minimized.\footnote{\citet{hendel_relative_2009} documents that the MLS market experiences a significant growth in recent years.} In contrast, Chinese real estate market is predominantly offline-based, with online listings serving mainly as references.
+The listing service of Chinese real estate market possesses distinct features characterized by the prominence of offline stores, setting it apart from the markets in other developed countries.
+Compared to the United States, where the Multiple Listing Service (MLS) provides comprehensive and reliable information online, facilitating transactions in a market where suits are typically situated far apart, the role of offline real estate stores is minimized.\footnote{\citet{hendel_relative_2009} documents that the MLS market experiences a significant growth in recent years.} In contrast, Chinese real estate market is predominantly offline-based, with online listings serving mainly as references.
 Face-to-face interactions remain crucial for transactions.
-Additionally, the Chinese government imposes stringent restrictions on the online listing prices, leading to a reluctance among sellers to list their properties online.
+Additionally, Chinese government imposes stringent restrictions on the upper and lower limits of online listing prices, leading to a reluctance among sellers to list their properties online.
 This regulatory environment allows real estate brokerages to sometimes post misleading prices to attract potential buyers, subsequently offering private information about other properties.
@@
 In Singapore, the real estate market is heavily influenced by government-coordinated prices and evaluation companies' suggested prices.
-Conversely, in China, sellers have more freedom to set arbitrary listing prices.
+Conversely, in China, sellers have more freedom to set arbitrary listing prices in the offline market.
 It is common practice for Chinese sellers to list their properties at higher prices, anticipating that buyers will negotiate and feel incentivized by securing a perceived better deal.
@@
 However, prior to 2018, the platform Beke primarily focused on facilitating listings from Lianjia's offline stores and aimed to attract buyers from the market.
-However, in 2014, Beke established a new strategy named Agent Cooperate Network (ACN), which integrates and shares the content across its multiple subsidiaries to realize multiple revenue models simultaneously.\footnote{The ACN model disaggregates the transaction process into specialized tasks handled by individual agents or stores.
+In 2014, Beke introduced a strategic initiative called the Agent Cooperation Network (ACN), which aims to integrate and share resources across its various subsidiaries.
+This strategy enables the realization of multiple revenue streams simultaneously, thereby optimizing operational efficiency and enhancing overall economic performance.\footnote{The ACN model disaggregates the transaction process into specialized tasks handled by individual agents or stores.
 These tasks include seller-side activities such as sourcing sellers, maintaining property listings, commission negotiations, and buyer-side activities like client acquisition, property-client matching, transaction facilitation, and financial services assistance.} Moreover, in 2018, Lianjia decided to enhance its Agent Cooperation Network (ACN) strategy by incorporating smaller brokerages into its network and launching franchise stores under the brand name Deyou, along with other smaller formats.
@@
 Additionally, Sansha city is featured in the bottom right corner of the graph.
+The base map is sourced from the AutoNavi Map.
 \end{figure}
@@
 Lastly, the result also confirms that the clustering within a small segmented market allows the company to coexist with competitors, with the large company satisfying the majority of customers while other firms cater to heterogeneous customer needs.
-Lianjia does not exclude other brokerages from the market, but rather coexists with them, thereby enhancing the overall market competitiveness.
-This finding is consistent with the study by \citep{gilbukh_goldsmith-pinkham_2019}, which indicates that inexperienced intermediaries hold a large market share, but their transaction efficiency is lower compared to experienced intermediaries.
+Lianjia does not exclude other brokerages from the market, but rather coexists with them, thereby enhancing the overall market competitiveness.\footnote{This finding is consistent with the study by \citep{gilbukh_goldsmith-pinkham_2019}, which indicates that inexperienced intermediaries hold a large market share, but their transaction efficiency is lower compared to experienced intermediaries.}
 
@@
 A fundamental study by \citep{Akerlof_1970} highlights the significant impact of asymmetric information on market dynamics, using the market for used cars as an example.
-Here, the prevalence of low-quality goods, known as 'lemons', often leads to market inefficiencies, a problem that is mirrored in the real estate sector.
+Here, the prevalence of low-quality goods, known as `lemons', often leads to market inefficiencies, a problem that is mirrored in the real estate sector.
 The challenge of asymmetric information in real markets was further emphasized by \citet{grossman_impossibility_1980}, who questioned the feasibility of the effective market assumption, particularly under conditions of information disparity.
@@
 \citet{ZUMPANO2003134} notes that while the duration of property searches has not changed markedly, the scope of searches has broadened to encompass more online listings.
-Moreover, \citet{ZHANG2021101104} associates the rise of online platforms with a reduction in existing home prices and an increase in sales volumes, a dynamic influenced by factors such as new home prices and household demographics.
+Moreover, \citet{ZHANG2021101104} associates the rise of online platforms with a reduction in existing house prices and an increase in sales volumes, a dynamic influenced by factors such as new house prices and household demographics.
 However, a detailed analysis of the impact of the presence of these platforms on market performance of offline stores remains scant.
@@
 
-To our knowledge, this paper represents the pioneering empirical investigation into the effects of offline store expansion and platform-mediated consolidation within the real estate brokerage market.
+Based on the study of existing literature, this paper represents the pioneering empirical investigation into the effects of offline store expansion and platform-mediated consolidation within the real estate brokerage market.
 Furthermore, it is the first to analyze the local network effects within the specific context of real estate transactions.
@@
 
-Each type of POI, excluding brokerages offline stores information, was matched to our data within a 500-meter radius, a distance typically covered by walking and consistent with urban planning standards for accessible urban design.
-This radius reflects the immediate urban environment influencing residential desirability and property values, as most of these POIs provide recreational services.
+Each type of POI, excluding brokerages offline stores information, was matched to our data within a 500-meter radius, a distance typically covered by walking and consistent with urban planning standards for accessible urban design.\footnote{We chose a 500-meter radius because the existing literature does not specifically document whether these types of points of interest (POIs) adhere strictly to the 5-minute walk policy.
+Furthermore, several studies have utilized a 500-meter radius to examine the influence of various types of POIs, including: \citep{LI2019165, doi:10.1287/mnsc.2019.3550}} This radius reflects the immediate urban environment influencing residential desirability and property values, as most of these POIs provide recreational services.
 Additionally, geo-informational data, including annual GDP data from \citet{zhao_forecasting_2017}, nighttime lights data from \citet{elvidge_annual_2021}, and air pollution data from \citet{doi:10.1021/acs.est.1c05309}, was integrated into our research.
@@
 
-From Figure \ref{fig:RD_design} we can see that there is indeed discontinuity in 410 meters of communities to the nearest Lianjia's store, which is pretty close to the lianjia's 5-minute walk distance policy (approximately 410 meters).
+From Figure \ref{fig:RD_design} we can see that there is indeed discontinuity in 410 meters of communities to the nearest Lianjia's store, which is pretty close to the Lianjia's 5-minute walk distance policy (approximately 410 meters).
 The observed decline in the Lianjia's influence is marked and suggests a pronounced reduction in its impact on the system overall within our study sample.
@@
 One another common concern in RDD is the potential for manipulation around the cutoff, which could invalidate the results.
-To address this, a "Donut Hole" robustness check can be implemented, where observations close to the cutoff are excluded to ensure that the results are not driven by manipulation or other local irregularities.
+To address this, a ``Donut Hole" robustness check can be implemented, where observations close to the cutoff are excluded to ensure that the results are not driven by manipulation or other local irregularities.
 In this study, we apply a Donut Hole robustness check to an RDD with a cutoff of 410 meters.
@@
 
-After constructing our optimal radius, we recalcualte the number of lianjia and other brokerages' stores within this radius.
-To check the robustness of the data, we divide our data to those with lianjia and those without lianjia and to check whether lianjia's offline stores have influential effect on the transaction effect in the neighborhoods.
-We can see that for transaction numbers, income, number of house tours and price concession are all significantly different in those neighborhoods with or without lianjia.
+After constructing our optimal radius, we recalcualte the number of Lianjia and other brokerages' stores within this radius.
+To check the robustness of the data, we divide our data to those with Lianjia and those without Lianjia and to check whether Lianjia's offline stores have influential effect on the transaction effect in the neighborhoods.
+We can see that for transaction numbers, income, number of house tours and price concession are all significantly different in those neighborhoods with or without Lianjia.
 In addition, we find that the other brokerages also have the same tendency that they typically open stores with the same strategy as Lianjia, which suggests that Lianjia does not have the market power to exclude competent companies from entering the market, and it also suggests that the market is not monopolized by Lianjia.
-We plot the relationship between the number of other brokerages's stores and the number of lianjia's stores and the figure is shown in Figure \ref{fig:same_distribution}.
+We plot the relationship between the number of other brokerages's stores and the number of Lianjia's stores and the figure is shown in Figure \ref{fig:same_distribution}.
 The figure shows that the the number of other brokerages' stores is positively correlated and the general trend tends to be linear, which further suggests that the market is not monopolized by Lianjia.
 
-From Table \ref{tab:statistical_district} we can see that the in our metro areas, the neighborhoods with lianjia within the influential radius tends to have higher number of sales, and the final transaction price is also \textyen 910,000 (approximately 35\%) higher than those neighborhoods without lianjia.
+From Table \ref{tab:statistical_district} we can see that the in our metro areas, the neighborhoods with Lianjia within the influential radius tends to have higher number of sales, and the final transaction price is also \textyen 910,000 (approximately 35\%) higher than those neighborhoods without Lianjia.
 Moreover, the number of other stores within the influential distance is also signnificantly more than 7.3, which also aligns with our previous intuition that the market is not monopolized by Lianjia.
 This significance difference suggests that if we treat our sample as a cross sectional data and estimate the result with static model without considering the individual fixed effect, we may get a biased result.
-Besides, our model may suffer from endogeneity issue, since the number of lianjia's stores may be endogenous to the transaction price and the number of stores.
+Besides, our model may suffer from endogeneity issue, since the number of Lianjia's stores may be endogenous to the transaction price and the number of stores.
 
@@
 
-    Note that the code book of the variables can be seen in the Appendix \ref{tab:codebook} and with or without lianjia represent whether there are Lianjia's offline stores within the influential radius.
+    Note that the code book of the variables can be seen in the Appendix \ref{tab:codebook} and with or without Lianjia represent whether there are Lianjia's offline stores within the influential radius.
     \end{tiny}
@@
 
-  Note that the code book of the variables can be seen in the Appendix \ref{tab:codebook} and with or without lianjia represent whether there are Lianjia's offline stores within the influential radius.
+  Note that the code book of the variables can be seen in the Appendix \ref{tab:codebook} and with or without Lianjia represent whether there are Lianjia's offline stores within the influential radius.
   \end{tiny}  
@@
     \label{fig:same_distribution}
-    Note: the x-axis is the number of lianjia's stores and the y-axis is the number of other brokerages' stores. The fit is a cubic polynomial fit.
+    Note: the x-axis is the number of Lianjia's stores and the y-axis is the number of other brokerages' stores. The fit is a cubic polynomial fit.
 \end{figure}
@@
 
-In our analysis, we focus on several dependent variables: \emph{the natural logarithm of lianjia's transaction number}, \emph{the natural logarithm of home tours}, \emph{the natural logarithm of transaction period} and \emph{the price concession}.
+In our analysis, we focus on several dependent variables: \emph{the natural logarithm of Lianjia's transaction number}, \emph{the natural logarithm of home tours}, \emph{the natural logarithm of transaction period} and \emph{the price concession}.
 To take the natural logarithm without lossing information, we decided to add one to the number of house tours because some transactions are purely online-based.
@@
 In column 1 and 2, we estimated the model using the neighborhood-level data and in column 3 and 4, we estiamted the model using the individual-level data, respectively.
+Standard Errors are clustered at the business area level.
     \label{tab:stylized_fact}
@@
     Note: we omit all the control variables in the regression model, and detailed descriptions can be seen from Table \ref{tab:statistical_district} and Table \ref{tab:statistical_individual}.
+Standard Errors are clustered at the business area level.
     \end{scriptsize}
@@
 From the market's performance, the Lianjia's offline's store's entry into the segmented market is an exogenous shock to the two-sided customers, where sellers are more likey to be attracted by the brokerage and buyers are also more likely to be attracted by the more listing information in the neighborhood.
-Although Lianjia's entry is not a randomized event, the DiD estimation method remains consistent in estimating the entry effect by comparing variations in outcome variables before and after Lianjia's entry in the segmented market.
+Although Lianjia's entry is not a randomized event, the DID estimation method remains consistent in estimating the entry effect by comparing variations in outcome variables before and after Lianjia's entry in the segmented market.
 
@@
 To visualize this network, we randomly selected 10 points and used a maximum search depth of 10 to plot the graph, as shown in Figure \ref{fig:network_formation_effect_graph}.
-WE constructed the measure indices as local clustering effect and global clustering effect.
+We constructed the measure indices as local clustering effect and global clustering effect.
 The local clustering effect refers to the degree to which nodes in a network tend to cluster together, forming tight-knit groups.
@@
     Note: we omit all the control variables in the regression model, and detailed descriptions can be seen from Table \ref{tab:statistical_district} and Table \ref{tab:statistical_individual}.
+Robsut Standard Errors are reported in parentheses.
     \end{scriptsize}
@@
 
+\bibitem[Chu et al.(2021)]{doi:10.1287/mnsc.2019.3550}
+Chu, J., Y. Duan, X. Yang, and L. Wang. 2021. The Last Mile Matters: Impact of Dockless Bike Sharing on Subway Housing Price Premium. \textit{Management Science}, 67(1), 297-316.
+
 \bibitem[d'Aspremont et al.(1979)]{daspremont_hotellings_1979}
@@
 Li, Z., and H. Qi. 2022. Platform Power: Monopolisation and Financialisation in the Era of Big Tech. \textit{Cambridge Journal of Economics}, 46(6), 1289-1314.
+
+\bibitem[Li et al.(2019)]{LI2019165}
+Li, H., Y. D. Wei, Y. Wu, and G. Tian. 2019. Analyzing Housing Prices in Shanghai with Open Data: Amenity, Accessibility, and Urban Structure. \textit{Cities}, 91, 165-179.
 
@@
 \bibitem[Piazzesi et al.(2020)]{10.1257/aer.20141772}
-Piazzesi, M., M. Schneider, and J. Stroebel. 2020. Segmented Housing Search. \textit{American Economic Review}, 110(3), 720-759.
-
-\bibitem[Piazzesi et al.(2020)]{piazzesi_segmented_2020}
 Piazzesi, M., M. Schneider, and J. Stroebel. 2020. Segmented Housing Search. \textit{American Economic Review}, 110(3), 720-759.
@@
 
-\bibitem[Zhang et al.(2021)]{zhang_online_2021}
-Zhang, X., Z.
-Lin, Y.
-Zhang, Y.
-Zheng, and J.
-Zhang.
-2021.
-Online Property Brokerage Platform and Prices of Second-Hand Houses: Evidence from Lianjia's Entry.
-\textit{Electronic Commerce Research and Applications}, 50, 101104.
-
 \bibitem[Zhao et al.(2017)]{zhao_forecasting_2017}

### 2024-07-28 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

@@
 In a perfectly competitive market, sellers would be indifferent in their choice of real estate agents.
-Nonetheless, as the market trends toward increased monopolization, sellers confront a dichotomous decision: engage a larger brokerage firm, which, despite higher fees, offers the potential for expedited transactions, or opt for a smaller brokerage with lower fees but potentially less efficient transaction facilitation.
+Nonetheless, as the market trends toward increased monopolistic competition, sellers confront a dichotomous decision: engage a larger brokerage firm, which, despite higher fees, offers the potential for expedited transactions, or opt for a smaller brokerage with lower fees but potentially less efficient transaction facilitation.
 
@@
 \end{table}
+
+\subsection{Mechanism Design} \label{subsec:mechanism_network_design}
+
+In the real estate market, real estate is not a homogeneous good, and the market is characterized by a large number of firms with no significant barriers to entry.
+Traditional economic theory suggests that such a market, characterized by substantial competition, numerous firms, and low market concentration, is consistent with real-world observations.
+For example, Lianjia's offline stores account for less than 5\% of the total, yet Lianjia handles about 20\% of the national transactions.
+In addition, many well-known agencies, such as Woaiwojia and Centaline Property Agency, operate in this market, indicating a monopolistic competitive environment.
+
+However, when looking at local segmented markets, the monopolistic competition model seems less applicable.
+In local markets, surrounding neighborhoods share similar community characteristics and public resources.
+Especially in China's real estate market, most properties are apartments, where the inherent differences between properties are minimal, making them relatively homogeneous goods.
+In addition, local real estate markets have no barriers to entry or exit, closely resembling perfect competition.
+From a cost perspective, the real estate market has undergone platform mediated reforms, where data resources have zero marginal cost characteristics and operating costs decrease as the user base expands, suggesting characteristics of a natural monopoly.
+Under these conditions, the operating position of firms differs significantly from that in a monopolistically competitive market.
+Due to network effects, an increase in the number of branches of a dominant real estate agency attracts more users, which in turn attracts more real estate listings.
+This positive feedback loop reinforces the dominant position of firms like Lianjia, leading to the formation of oligopolistic firms.
+These oligopolistic firms can further maintain their dominant market positions.
+Thus, even in the absence of barriers to entry and despite the presence of many competing firms, their operations can resemble those of a full monopoly.
+
+As our empirical results show, Lianjia's strategy has significantly enhanced its network strength within segmented markets.
+From this perspective, the enhancement of network effects further drives the market toward an oligopolistic competitive structure.
+Moreover, with the development of online platforms and new technologies, such as Lianjia's latest VR home viewing technology, these network effects are gradually shifting from local networks to a global network.
+As a result, this development is shaping the overall market into an oligopolistic competition model on a larger scale.
 

### 2024-07-29 manuscript/main.tex
new file:   manuscript/July29.pdf 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

@@
 
+In local segmented markets, oligopolistic firms are responsible for increasing network strength and have significant market power.
+In segmented markets where some oligopolistic firms do not have strong network effects, multiple other firms serve the diverse needs of consumers and expand their scale.
+The environment of free entry, rapid technological progress, and business model innovation leads to an inclusive competitive landscape in the real estate brokerage market.
+This environment allows oligopolistic firms to either enhance the strength of their network effects or have their dominant positions challenged.
+As a result, monopolistic structures emerge from and are subsequently disrupted by competition, allowing real estate intermediaries to continuously evolve and drive the industry's rapid growth.
+The practical implication is that a competitive oligopolistic structure does not inherently impede competitive efficiency.
+Instead, it can enhance firm efficiency, thereby facilitating better transactions for buyers and sellers and increasing overall market welfare.
+
 As our empirical results show, Lianjia's strategy has significantly enhanced its network strength within segmented markets.
-From this perspective, the enhancement of network effects further drives the market toward an oligopolistic competitive structure.
+From this perspective, the enhancement of network effects further drives the segmented market toward an oligopolistic competitive structure, which could increase the market welfare and facilitate the transactions between buyers and sellers.
 Moreover, with the development of online platforms and new technologies, such as Lianjia's latest VR home viewing technology, these network effects are gradually shifting from local networks to a global network.
 As a result, this development is shaping the overall market into an oligopolistic competition model on a larger scale.
+
+In the future, as the network effects intensify, the real estate market may witness a more pronounced consolidation of market power among a few dominant players.
+This consolidation can lead to increased efficiencies through economies of scale and scope, where firms leverage their vast data resources and technological advancements to optimize operations and enhance consumer experiences.
+However, this shift also raises important considerations for regulatory bodies to ensure that the market remains competitive and accessible.
+The dynamic interplay between technological innovation and market structure will be crucial.
+As firms like Lianjia continue to innovate, incorporating artificial intelligence, big data analytics, and blockchain for secure transactions, the real estate market could become more transparent and efficient.
+These advancements could lower transaction costs, reduce information asymmetry, and provide consumers with more personalized services.
+Furthermore, the global reach of network effects implies that real estate markets across different regions might become more interconnected.
+This interconnectivity can facilitate cross-border investments and diversify property portfolios for investors, contributing to a more resilient global real estate market.
+
+In conclusion, the evolution of the real estate market towards an oligopolistic competition model, driven by network effects and technological advancements, presents both opportunities and challenges.
+Policymakers and industry stakeholders must navigate this landscape carefully to harness the benefits of increased efficiency and innovation while safeguarding against potential market power abuses and ensuring equitable access for all participants.
+This balanced approach will be essential for sustaining long-term growth and enhancing overall market welfare in the real estate industry.
 

### 2024-07-29 manuscript/main.tex
deleted:    manuscript/July29.pdf 	renamed:    manuscript/main.pdf -> manuscript/Platform-Mediated Consolidation and Online Store Expansion.pdf 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

@@
 
-In the real estate market, real estate is not a homogeneous good, and the market is characterized by a large number of firms with no significant barriers to entry.
+In the real estate market, real estate is not a homogeneous good, and therefore, the brokerage market is characterized by a large number of firms with no significant barriers to entry.
 Traditional economic theory suggests that such a market, characterized by substantial competition, numerous firms, and low market concentration, is consistent with real-world observations.
@@
 These oligopolistic firms can further maintain their dominant market positions.
-Thus, even in the absence of barriers to entry and despite the presence of many competing firms, their operations can resemble those of a full monopoly.
 
@@
 The practical implication is that a competitive oligopolistic structure does not inherently impede competitive efficiency.
-Instead, it can enhance firm efficiency, thereby facilitating better transactions for buyers and sellers and increasing overall market welfare.
+Instead, as our empirical findings indicate, the enriched entry and transformations within the market lead to an increase in the number of transactions and house tours.
+This type of market structure can enhance firm efficiency, thereby facilitating more efficient transactions for buyers and sellers and improving overall market welfare, even though it may impede individual seller welfare.
 
@@
 
-In the future, as the network effects intensify, the real estate market may witness a more pronounced consolidation of market power among a few dominant players.
+In the future, as the network effects intensify, the real estate brokerage market may witness a more pronounced consolidation of market power among a few dominant players.
 This consolidation can lead to increased efficiencies through economies of scale and scope, where firms leverage their vast data resources and technological advancements to optimize operations and enhance consumer experiences.
@@
 These advancements could lower transaction costs, reduce information asymmetry, and provide consumers with more personalized services.
-Furthermore, the global reach of network effects implies that real estate markets across different regions might become more interconnected.
-This interconnectivity can facilitate cross-border investments and diversify property portfolios for investors, contributing to a more resilient global real estate market.
-
-In conclusion, the evolution of the real estate market towards an oligopolistic competition model, driven by network effects and technological advancements, presents both opportunities and challenges.
-Policymakers and industry stakeholders must navigate this landscape carefully to harness the benefits of increased efficiency and innovation while safeguarding against potential market power abuses and ensuring equitable access for all participants.
+Furthermore, the global reach of network effects implies that real estate brokerage markets across different regions might become more interconnected.
+This interconnectivity can facilitate cross-city or cross-province investments and diversify property portfolios for investors, contributing to a more resilient real estate market.
+
+In conclusion, the evolution of the real estate brokerage market towards an oligopolistic competition model, driven by network effects and technological advancements, presents both opportunities and challenges.
+From our empirical findings, this type of market structure can not impede the competitive efficiencies but policymakers and industry stakeholders must navigate this landscape carefully to harness the benefits of increased efficiency and innovation while safeguarding against potential market power abuses and ensuring equitable access for all participants.
 This balanced approach will be essential for sustaining long-term growth and enhancing overall market welfare in the real estate industry.

### 2024-07-31 manuscript/main.tex
renamed:    manuscript/Platform-Mediated Consolidation and Online Store Expansion.pdf -> manuscript/Platform-Mediated Consolidation and Offline Store Expansion.pdf 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	new file:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

@@
 We are grateful for the comments and suggestions made at the meeting.
-The code to replicate the paper can be accessed at \href{https://github.com/sergiozxy/RealEstateBrokerage}{https://github.com/sergiozxy/RealEstateBrokerage} The authors gratefully acknowledge financial support from the Fundamental Research Funds for the Central Universities of Sichuan University (2019hhf-08; SKSYL201812; 2018jj-01) and National Natural Science Foundation of China (71773081).
+The code to replicate the paper can be accessed at \href{https://github.com/sergiozxy/RealEstateBrokerage}{https://github.com/sergiozxy/RealEstateBrokerage} The authors gratefully acknowledge financial support from the Fundamental Research Funds for the Central Universities of Sichuan University (SKSYL2023-01) and National Natural Science Foundation of China (71773081).
 % We gratefully thank for Hanying Liu from Sichuan University and Chongyu Wang from Florida State University for insightful feedback.

### 2024-07-31 manuscript/main.tex
modified:   manuscript/Platform-Mediated Consolidation and Offline Store Expansion.pdf 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

@@
 We are grateful for the comments and suggestions made at the meeting.
-The code to replicate the paper can be accessed at \href{https://github.com/sergiozxy/RealEstateBrokerage}{https://github.com/sergiozxy/RealEstateBrokerage} The authors gratefully acknowledge financial support from the Fundamental Research Funds for the Central Universities of Sichuan University (SKSYL2023-01) and National Natural Science Foundation of China (71773081).
+The code to replicate the paper can be accessed at \href{https://github.com/sergiozxy/RealEstateBrokerage}{https://github.com/sergiozxy/RealEstateBrokerage} The authors gratefully acknowledge financial support from the Fundamental Research Funds for the Central Universities of Sichuan University (SKSYL2023-01)% and National Natural Science Foundation of China (71773081).
 % We gratefully thank for Hanying Liu from Sichuan University and Chongyu Wang from Florida State University for insightful feedback.

### 2024-08-01 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

@@
 By analyzing micro-level transactions of second-hand houses from Lianjia in ten major Chinese cities from 2016 to 2022, this research investigates how the transaction patterns of traditional brokerages, characterized by the strategic clustering of offline stores, transition towards platform-mediated consolidation, thereby facilitating the development of an extensive franchise network.
-Utilizing a regression discontinuity design (RDD), the study quantifies the optimal influence radius of offline stores (410 meters) on housing transactions.
-The study empirically estimates the effects of real estate brokerage's offline store expansion and platform-mediated consolidation on transaction properties.
+Utilizing a regression discontinuity design (RDD), this study quantifies the optimal influence radius of offline stores (410 meters) on housing transactions.
+this study empirically estimates the effects of real estate brokerage's offline store expansion and platform-mediated consolidation on transaction properties.
 The results indicate that this strategy significantly boosts revenues and attracts more people to housing tours.
 Additionally, the results suggest that neither the platform-mediated strategy nor offline expansion affects the transaction period, but offline store expansion can reduce the price gap between sellers and buyers.
-Furthermore, the study introduces a measure of network effect, revealing that Lianjia's offline stores exhibit a local clustering pattern with moderate network strength.
+Furthermore, this study introduces a measure of network effect, revealing that Lianjia's offline stores exhibit a local clustering pattern with moderate network strength.
 The analysis of platform-mediated consolidation indicates a significantly positive effect on network strength.
@@
 
-The listing service of Chinese real estate market possesses distinct features characterized by the prominence of offline stores, setting it apart from the markets in other developed countries.
-Compared to the United States, where the Multiple Listing Service (MLS) provides comprehensive and reliable information online, facilitating transactions in a market where suits are typically situated far apart, the role of offline real estate stores is minimized.\footnote{\citet{hendel_relative_2009} documents that the MLS market experiences a significant growth in recent years.} In contrast, Chinese real estate market is predominantly offline-based, with online listings serving mainly as references.
+The listing service of China's real estate market possesses distinct features characterized by the prominence of offline stores, setting it apart from the markets in other developed countries.
+Compared to the United States, where the Multiple Listing Service (MLS) provides comprehensive and reliable information online, facilitating transactions in a market where suits are typically situated far apart, the role of offline real estate stores is minimized.\footnote{\citet{hendel_relative_2009} documents that the MLS market experiences a significant growth in recent years.} In contrast, China's real estate market is predominantly offline-based, with online listings serving mainly as references.
 Face-to-face interactions remain crucial for transactions.
@@
 This regulatory environment allows real estate brokerages to sometimes post misleading prices to attract potential buyers, subsequently offering private information about other properties.
-Moreover, the Chinese real estate brokerage market operates under a bilateral agency model, resulting in lower transaction efficiency compared to the United States brokerage market.
+Moreover, the China's real estate brokerage market operates under a bilateral agency model, resulting in lower transaction efficiency compared to the United States brokerage market.
 In Singapore, the real estate market is heavily influenced by government-coordinated prices and evaluation companies' suggested prices.
@@
 
-Even though the Chinese real estate brokerage market has traditionally been characterized by intense competition among offline stores, the advent of online platforms has dramatically reshaped the dynamics of real estate transactions.
+Even though the China's real estate brokerage market has traditionally been characterized by intense competition among offline stores, the advent of online platforms has dramatically reshaped the dynamics of real estate transactions.
 Brokerage consolidation, a process where larger firms absorb smaller ones into a unified platform, is emerging as a transformative trend, redefining how properties are bought and sold across China.
@@
   \includegraphics[width=0.7\textwidth]{../figures/distribution_of_cities_share.pdf}
-  \caption{Distribution of Lianjia's stores' percentage across China}
+  \caption{Distribution of Lianjia's Stores' Percentage across China}
   \label{fig:precise_proportion_contraction}
@@
 
-Additionally, in the Chinese real estate market, brokerages still operate on a bilateral agency model, where sellers need to choose the agency that can help them sell their home in the fastest time and for the highest price possible for the transaction.
+Additionally, in the China's real estate market, brokerages still operate on a bilateral agency model, where sellers need to choose the agency that can help them sell their home in the fastest time and for the highest price possible for the transaction.
 However, due to the asymmetric information inherent in the real estate market, sellers face challenges in effectively informing and matching with potential buyers.
@@
 
-While sellers might consider a co-listing strategy—listing their property with multiple brokerages—this approach is suboptimal for several reasons within Chinese real estate market.
+While sellers might consider a co-listing strategy—listing their property with multiple brokerages—this approach is suboptimal for several reasons within China's real estate market.
 Despite previous literature, such as \citep{RePEc:kap:jrefec:v:67:y:2023:i:3:d:10.1007_s11146-021-09858-w}, indicating that the co-listing can be beneficial for clients under multiple-listing service.
-Specifically in Chinese real estate market, firstly, the exclusivity of contracts between sellers and agents often precludes the adoption of a co-listing strategy.
+Specifically in China's real estate market, firstly, the exclusivity of contracts between sellers and agents often precludes the adoption of a co-listing strategy.
 Secondly, although sellers can list their properties with multiple brokerages, smaller agencies frequently lack a sufficiently broad client base, limiting their effectiveness in selling homes.
@@
 This study focuses on the housing markets in ten major cities in China, namely Beijing, Shanghai, Chongqing, Tianjin, Shenzhen, Guangzhou, Chengdu, Hangzhou, Wuhan and Nanjing.
-These cities are not only pivotal to China's economic development, but also serve as exemplars of the broader trends and characteristics inherent in the Chinese real estate dynamics.
-Spanning from 2016 to 2022, the research period encapsulates a pivotal era in Chinese real estate sector.
+These cities are not only pivotal to China's economic development, but also serve as exemplars of the broader trends and characteristics inherent in the China's real estate dynamics.
+Spanning from 2016 to 2022, the research period encapsulates a pivotal era in China's real estate sector.
 During the first phase of the study, from 2016 to 2019, the housing markets in these cities experienced a remarkable boom.
@@
 We repeat the procedures described in the main analysis using this transformed dependent variable.
-The corresponding results are presented in Appendix Figure \ref{fig:RD_design_Robust} and Table \ref{tab:rd_bandwidth_kernel_results_robust}.
+The corresponding results are presented in Appendix Figure \ref{fig:RD_design_Robust} and Appendix Table \ref{tab:rd_bandwidth_kernel_results_robust}.
 Our findings indicate that the results remain consistent with those obtained using the original dependent variable.
@@
 We first check to identify any potential confounding variables that might be driving the results instead of the treatment effect.
-To achieve this, we conducted a placebo test by substituting the dependent variable with other control variables and the results are shown in Table \ref{tab:placebo_test_results}.
+To achieve this, we conducted a placebo test by substituting the dependent variable with other control variables and the results are shown in Appendix Table \ref{tab:placebo_test_results}.
 The results suggest that the discontinuity does not exist in the placebo test, which substantiates that the observed discontinuity is not due to any general discontinuity in the data at the cutoff but is specifically attributable to the treatment effect.
@@
     \includegraphics[width=0.7\textwidth]{../figures/scatter_plot_with_two_brokerages.pdf}
-    \caption{Tendency between two types of brokerages}
+    \caption{Tendency between Two Types of Brokerages}
     \label{fig:same_distribution}
@@
     \input{../result_tables/stylized_fact}
-    \caption{The DBI influence to the lianjia's transaction}
+    \caption{The DBI Influence to the Lianjia's Transaction}
 
@@
 To further check the robustness of our results, we conducted another three tests.
-In the Appendix, we conducted the same estimation but without additional control variables and the results are reported in Appendix Table \ref{tab:entry_effect_robustness_1} and Appendix Table \ref{tab:entry_effect_robustness_2}.
+In the Appendix, we conducted the same estimation but without additional control variables and the results are reported in Table \ref{tab:entry_effect_robustness_1} and Table \ref{tab:entry_effect_robustness_2}.
 The estiamted results are shown consistent without additional control variabels.
@@
 
-We also conducted a placebo test, as illustrated in Figure \ref{fig:placebo_concession_entry}.
+We also conducted a placebo test, as illustrated in Appendix Figure \ref{fig:placebo_concession_entry}.
 For this test, we employed a neighborhood sample with randomly generated treatment effects.
@@
 
-where our key independent variables are described above. Other settings are consistent with previous table \ref{tab:Dynamic} and the result is reported in Figure \ref{fig:dynamic_effect}.
+where our key independent variables are described above. Other settings are consistent with previous Table \ref{tab:Dynamic} and the result is reported in Figure \ref{fig:dynamic_effect}.
 
@@
 
-We conducted a placebo test, as illustrated in Figure \ref{fig:placebo_concession_plat} like our previous estimation of the offline store expansion.
+We conducted a placebo test, as illustrated in Appendix Figure \ref{fig:placebo_concession_plat} like our previous estimation of the offline store expansion.
 The test result also shows that there is no other confounding factors affecting our analysis.
@@
   \includegraphics[width=0.7\textwidth]{../figures/network_formation_effect.pdf}
-  \caption{The structure of network formation effect}
+  \caption{The Structure of Network Formation Effect}
   \label{fig:network_formation_effect_graph}
@@
 $***$ signifies a large network effect, ranging from 0.75 to 1.
+In the Appendix Section \ref{subsec:descriptions_clustering_indices}, we provide detailed descriptions of these indices.
+Moreover, Appendix Section \ref{subsec:other_indices_measures} describes other measures of network indices, including Appendix Table \ref{other:closeness_centrality}, Appendix Table \ref{other:degree_centrality} and Appendix Table \ref{other:page_rank}.
     \end{scriptsize}
@@
 The average effect of the network is 2.18 and the standard deviation is 2.55.
-We detailed describes these indices in Appendix Section \ref{subsec:descriptions_clustering_indices}.\footnote{We also Describes other measures of network indices in Appendix Section \ref{subsec:other_indices_measures}.} This connection is in line with the reality in several ways.
+We detailed describes these indices in Appendix Section \ref{subsec:descriptions_clustering_indices}.\footnote{We also Describes other measures of network indices in Appendix Section \ref{subsec:other_indices_measures}, including Appendix Table \ref{other:closeness_centrality}, Appendix Table \ref{other:degree_centrality} and Appendix Table \ref{other:page_rank}.} This connection is in line with the reality in several ways.
 Firstly, cooperation between stores to complete a transaction is very common, and having more stores within the segmented market can contribute significantly to the transaction process as more efforts can be jointly made by different agents.
@@
 
-Our study highlights the transformative impact of Lianjia's strategic expansion in Chinese real estate brokerage industry through the implementation of the online-mediated consolidation strategy and the massive expansion of offline branches.
+Our study highlights the transformative impact of Lianjia's strategic expansion in China's real estate brokerage industry through the implementation of the online-mediated consolidation strategy and the massive expansion of offline branches.
 Our empirical research demonstrates that Lianjia's approach, which seamlessly integrates online platforms with an extensive offline presence, significantly enhances revenue generation and influences consumer behavior through improved price concessions and increased number of house tours.
@@
 \bibitem[Hui and Chan(2014)]{hui_foreign_2014}
-Hui, E. C. M., and K. K. K. Chan. 2014. Foreign Direct Investment in Chinese real estate Market. \textit{Habitat International}, 43, 231-239.
+Hui, E. C. M., and K. K. K. Chan. 2014. Foreign Direct Investment in China's real estate market. \textit{Habitat International}, 43, 231-239.
 
@@
 The data reveals a significant clustering of stores around major residential buildings, demonstrating a high degree of localization within the real estate brokerage market.
-This pattern is indicative of the competitive dynamics and agglomeration economies prevalent in the Chinese real estate sector, where proximity to key infrastructure.
+This pattern is indicative of the competitive dynamics and agglomeration economies prevalent in the China's real estate sector, where proximity to key infrastructure.
 The data source is from AutoNavi Map.
@@
   \subfloat[RDD plot with third order polynomial]{\includegraphics[width=0.5\textwidth]{../figures/RD_Plot_3rd_Order_robust.pdf}\label{fig:RD_Plot_3rd_Order_Robust}}
-  \caption{RDD design Robustness Check using log(income)}
+  \caption{RDD Robustness Check using log(income)}
   \label{fig:RD_design_Robust}
@@
     \includegraphics[width=0.7\textwidth]{../figures/average_income_by_treatment_platform.pdf}
-    \caption{Treatment Effect of platform consolidation}
+    \caption{Treatment Effect of Platform Consolidation}
     \label{fig:treatment_consolidation}
@@
     \begin{scriptsize}
-      \caption{Robustness Check for Platform Consolidation Effect Using Nighttime Lights}
+      \caption{Robustness Check for Platform Consolidation Effect using Nighttime Lights}
       \label{tab:robustness_nighttime_light_consolidation}

### 2024-08-07 manuscript/main.tex
modified:   manuscript/Platform-Mediated Consolidation and Offline Store Expansion.pdf 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

@@
 One another common concern in RDD is the potential for manipulation around the cutoff, which could invalidate the results.
-To address this, a ``Donut Hole" robustness check can be implemented, where observations close to the cutoff are excluded to ensure that the results are not driven by manipulation or other local irregularities.
-In this study, we apply a Donut Hole robustness check to an RDD with a cutoff of 410 meters.
+To address this, a falsification testing based on ``Donut Hole'' specifications can be implemented, where observations close to the cutoff are excluded to ensure that the results are not driven by manipulation or other local irregularities.
+In this study, we conduct a robustness check using the Donut Hole method on a RDD with a cutoff at 410 meters.
 Specifically, we sequentially exclude observations within certain distances from the cutoff and re-estimate the treatment effect.

### 2024-08-07 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

@@
 
-From Table \ref{tab:statistical_district} we can see that the in our metro areas, the neighborhoods with Lianjia within the influential radius tends to have higher number of sales, and the final transaction price is also \textyen 910,000 (approximately 35\%) higher than those neighborhoods without Lianjia.
+From Table \ref{tab:statistical_district} we can see that in our metro areas, the neighborhoods with Lianjia within the influential radius tends to have higher number of sales, and the final transaction price is also \textyen 910,000 (approximately 35\%) higher than those neighborhoods without Lianjia.
 Moreover, the number of other stores within the influential distance is also signnificantly more than 7.3, which also aligns with our previous intuition that the market is not monopolized by Lianjia.
@@
 This could potentially will caused our estimation biased if we were to simply count the number of Lianjia's stores.
-To control for this issue, we employ a comparative metric: the ratio of Lianjia brokerages to the total number of real estate brokerages within the radius.
+To deal for this issue, we employ a comparative metric: the ratio of Lianjia brokerages to the total number of real estate brokerages within the radius.
 This ratio helps mitigate the bias that may arise from the strategic location choices of Lianjia, offering a clearer measure of its market influence relative to competitors.
@@
 
-where $Y_{it}$ is the three main dependent variables, including $\log(\text{number})$, price concession, and $\log(\text{lead times})$, $density_{it}$ is the DBI, $\bf{X}_{it}$ is a set of control variables, including brokerage\_control Lag(hedonic\_control), transaction\_control and region\_control, while $\eta_{t} \times \text{bs\_code}_i$ is the time dummy variable interacting with the fixed effect of the business area, $\mu_i$ is the neighborhood fixed effect and $\epsilon_{it}$ is the random error term.
+where $Y_{it}$ is the three main dependent variables, including $\log(\text{number})$, price concession, and $\log(\text{lead times})$, $density_{it}$ is the DBI, $\bf{X}_{it}$ are a set of control variables, including brokerage\_control Lag(hedonic\_control), transaction\_control and region\_control, while $\eta_{t} \times \text{bs\_code}_i$ is the time dummy variable interacting with the fixed effect of the business area, $\mu_i$ is the neighborhood fixed effect and $\epsilon_{it}$ is the random error term.
 The standard errors are clustered at the each business area level.\footnote{The business area is defined as a zone with combination of multiple neighborhoods, which Lianjia designates as the primary divisions of the entire region.
@@
 This strategic choice allows us to refine our proxy variable—the product of Lianjia's Dealership Balance Index (DBI) and annual dummies—as a better measure of Lianjia's local market power.
-Besides, to control for potential self correlation problem, we also included lagged one period dependent variables in the model.
+Besides, to control potential self correlation problem, we also included lagged one period dependent variables in the model.
 Other settings are the same with the previous model \eqref{eq:multi-way-fe} and the model is described as \eqref{eq:dynamic} and the results are reported in Table \ref{tab:Dynamic}:
@@
 
-Furthermore, in Table \ref{tab:entry_effect_robustness_2}, The entry of Lianjia's offline stores significantly shortens the transaction period for the moderate HHI group by about 5\%.
+Furthermore, in Table \ref{tab:entry_effect_robustness_2}, the entry of Lianjia's offline stores significantly shortens the transaction period for the moderate HHI group by about 5\%.
 Conversely, this effect is not significant in the lower HHI group and higher concentration group.
@@
 where $Q_y(\xi \mid X)$ represents the $\tau$-th quantile of the dependent variable $y$ given the predictors $X$, where $\tau \in \{5, 10, \ldots, 95\}$.
-$\beta_0$ is the intercept term, $\text{Pre\_Treatment}_{it}$ is a dummy variable indicating the pre-treatment period, $\text{Treatment}_{it}$ is a dummy variable indicating the treatment group in 2018 and $\text{Post\_j\_Treatment}$ is a set of dummy variables indicating the post treatment group interacting with that year.
+$\beta_0$ is the intercept term, $\text{Pre\_Treatment}_{it}$ is a dummy variable indicating the pre-treatment period, $\text{Treatment}_{it}$ is a dummy variable indicating the treatment group in 2018 and $\text{Post\_j\_Treatment}$ are a set of dummy variables indicating the post treatment group interacting with that year.
 $\mu_i$ represents individual fixed effects and $\eta_t$ is the year fixed effect and $\epsilon_{it}$ is the error term.

### 2024-08-07 manuscript/main.tex
modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

@@
 The average effect of the network is 2.18 and the standard deviation is 2.55.
-We detailed describes these indices in Appendix Section \ref{subsec:descriptions_clustering_indices}.\footnote{We also Describes other measures of network indices in Appendix Section \ref{subsec:other_indices_measures}, including Appendix Table \ref{other:closeness_centrality}, Appendix Table \ref{other:degree_centrality} and Appendix Table \ref{other:page_rank}.} This connection is in line with the reality in several ways.
+We describe these indices in detail in Appendix Section \ref{subsec:descriptions_clustering_indices}.\footnote{We also Describes other measures of network indices in Appendix Section \ref{subsec:other_indices_measures}, including Appendix Table \ref{other:closeness_centrality}, Appendix Table \ref{other:degree_centrality} and Appendix Table \ref{other:page_rank}.} This connection is in line with the reality in several ways.
 Firstly, cooperation between stores to complete a transaction is very common, and having more stores within the segmented market can contribute significantly to the transaction process as more efforts can be jointly made by different agents.
@@
 Secondly, Lianjia's platform-mediated consolidation can also increase its transaction revenue by 2.9\% to 6.2\% and boost the number of house tours by 2.9\% to 3.0\%.
-However, this effect does not significantly impact communication, thus not affecting the price concession and transaction period.
+However, this effect does not significantly influence communication, thereby not affecting price concessions or the transaction period.
 Lastly, we established the presence of localized network effects and found that Lianjia's network effects are primarily characterized by local clustering, with moderate network strength.

### 2024-08-08 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

@@
   \bibitem[Agarwal et al.(2019)]{AGARWAL2019715}
-Agarwal, S., J. He, T. F. Sing, and C. Song. 2019. Do Real Estate Agents Have Information Advantages in Housing Markets? \textit{Journal of Financial Economics}, 134(3), 715-735.
+Agarwal S, He J, Sing TF, Song C (2019) Do real estate agents have information advantages in housing markets? \textit{Journal of Financial Economics} 134(3):715-735.
 
 \bibitem[Agarwal et al.(2024)]{AGARWAL2024103668}
-Agarwal, S., Kuang, W., Wang, L., and Yang, Y. 2024. The role of agents in fraudulent activities: Evidence from the housing market in Beijing. \textit{Journal of Urban Economics}, 142, 103668.
+Agarwal S, Kuang W, Wang L, Yang Y (2024) The role of agents in fraudulent activities: Evidence from the housing market in Beijing. \textit{Journal of Urban Economics} 142:103668.
 
 \bibitem[Akerlof(1970)]{Akerlof_1970}
-Akerlof, G. A. 1970. The Market for "Lemons": Quality Uncertainty and the Market Mechanism. \textit{The Quarterly Journal of Economics}, 84(3), 488-500.
+Akerlof GA (1970) The Market for “Lemons”: Quality Uncertainty and the Market Mechanism. \textit{The Quarterly Journal of Economics} 84(3):488.
 
 \bibitem[Allen et al.(2023)]{RePEc:kap:jrefec:v:67:y:2023:i:3:d:10.1007_s11146-021-09858-w}
-Allen, M. T., J. D. Benefield, and R. C. Rutherford. 2023. Co-Listing Strategies: Better Transaction Outcomes? \textit{The Journal of Real Estate Finance and Economics}, 67(3), 517-544.
+Allen MT, Benefield JD, Rutherford RC (2023) Co-Listing Strategies: Better Transaction Outcomes? \textit{The Journal of Real Estate Finance and Economics} 67(3):517-544.
 
 \bibitem[Armstrong(2006)]{Armstrong2006}
-Armstrong, M. 2006. Competition in Two-Sided Markets. \textit{The RAND Journal of Economics}, 37(3), 668-691.
+Armstrong M (2006) Competition in two-sided markets. \textit{The RAND Journal of Economics} 37(3):668-691.
 
 \bibitem[Athey and Imbens(2006)]{https://doi.org/10.1111/j.1468-0262.2006.00668.x}
-Athey, S., and G.
-W.
-Imbens.
-2006.
-Identification and Inference in Nonlinear Difference-in-Differences Models.
-\textit{Econometrica}, 74(2), 431-497.% Available at \url{https://onlinelibrary.wiley.com/doi/abs/10.1111/j.1468-0262.2006.00668.x}.
+Athey S, Imbens GW (2006) Identification and Inference in Nonlinear Difference-in-Differences Models. \textit{Econometrica} 74(2):431-497.
 
 \bibitem[Athey and Imbens(2016)]{athey_recursive_2016}
-Athey, S., and G. Imbens. 2016. Recursive Partitioning for Heterogeneous Causal Effects. \textit{Proceedings of the National Academy of Sciences of the United States of America}, 113(27), 7353-7360.
+Athey S, Imbens GW (2016) Recursive partitioning for heterogeneous causal effects. \textit{Proceedings of the National Academy of Sciences} 113(27):7353-7360.
 
 \bibitem[Azmi et al.(2012)]{AZMI2012406}
-Azmi, D.
-I., H.
-A.
-Karim, and M.
-Z.
-M.
-Amin.
-2012.
-Comparing the Walking Behaviour between Urban and Rural Residents.
-\textit{Procedia - Social and Behavioral Sciences}, 68(7), 406-416.
-% Available at \url{https://www.sciencedirect.com/science/article/pii/S1877042812057205}.
+Azmi DI, Karim HA, Amin MZM (2012) Comparing the Walking Behaviour between Urban and Rural Residents. \textit{Procedia - Social and Behavioral Sciences} 68:406-416.
 
 \bibitem[Bailey et al.(2018)]{bailey_economic_2018}
-Bailey, M., R. Cao, T. Kuchler, and J. Stroebel. 2018. The Economic Effects of Social Networks: Evidence from the Housing Market. \textit{Journal of Political Economy}, 126(6), 2224-2276.
+Bailey M, Cao R, Kuchler T, Stroebel J (2018) The Economic Effects of Social Networks: Evidence from the Housing Market. \textit{Journal of Political Economy} 126(6):2224-2276.
 
 \bibitem[Barwick and Pathak(2015)]{https://doi.org/10.1111/1756-2171.12082}
-Barwick, P. J., and P. A. Pathak. 2015. The Costs of Free Entry: An Empirical Study of Real Estate Agents in Greater Boston. \textit{The RAND Journal of Economics}, 46(1), 103-145.
+Barwick PJ, Pathak PA (2015) The costs of free entry: an empirical study of real estate agents in Greater Boston. \textit{The RAND Journal of Economics} 46(1):103-145.
 
 \bibitem[Barwick et al.(2017)]{10.1257/app.20160214}
-Barwick, P. J., P. A. Pathak, and M. Wong. 2017. Conflicts of Interest and Steering in Residential Brokerage. \textit{American Economic Journal: Applied Economics}, 9(3), 191-222.
+Barwick PJ, Pathak PA, Wong M (2017) Conflicts of Interest and Steering in Residential Brokerage. \textit{American Economic Journal Applied Economics} 9(3):191-222.
 
 \bibitem[Beck et al.(2022)]{doi:10.1080/10527001.2021.2016340}
-Beck, J., F. Scott, and A. Yelowitz. 2022. The Impact of Real Estate Agent Specialization and Activity Level on Market Outcomes. \textit{Journal of Housing Research}, 31(2), 163-180.
+Beck J, Scott F, Yelowitz A (2022) The Impact of Real Estate Agent Specialization and Activity Level on Market Outcomes. \textit{Journal of Housing Research} 31(2):163-180.
 
 \bibitem[Chen and Wen(2017)]{chen_great_2017}
-Chen, K., and Y. Wen. 2017. The Great Housing Boom of China. \textit{American Economic Journal: Macroeconomics}, 9(2), 73-114.
+Chen K, Wen Y (2017) The Great Housing Boom of China. \textit{American Economic Journal Macroeconomics} 9(2):73-114.
 
 \bibitem[Christensen and Timmins(2022)]{RePEc:ucp:jpolec:doi:10.1086/720140}
-Christensen, P., and C. Timmins. 2022. Sorting or Steering: The Effects of Housing Discrimination on Neighborhood Choice. \textit{Journal of Political Economy}, 130(8), 2110-2163.
+Christensen P, Timmins C (2022) Sorting or Steering: The Effects of Housing Discrimination on Neighborhood Choice. \textit{Journal of Political Economy} 130(8):2110-2163.
 
 \bibitem[Chu et al.(2021)]{doi:10.1287/mnsc.2019.3550}
-Chu, J., Y. Duan, X. Yang, and L. Wang. 2021. The Last Mile Matters: Impact of Dockless Bike Sharing on Subway Housing Price Premium. \textit{Management Science}, 67(1), 297-316.
+Chu J, Duan Y, Yang X, Wang L (2021) The Last Mile Matters: Impact of Dockless Bike Sharing on Subway Housing Price Premium. \textit{Management Science} 67(1):297-316.
 
 \bibitem[d'Aspremont et al.(1979)]{daspremont_hotellings_1979}
-d'Aspremont, C., J. J. Gabszewicz, and J.-F. Thisse. 1979. On Hotelling’s "Stability in Competition". \textit{Econometrica}, 47(5), 1145-1150.
+D'Aspremont C, Gabszewicz JJ, Thisse J f. (1979) On Hotelling's “Stability in Competition.” \textit{Econometrica} 47(5):1145-1150.
 
 \bibitem[Elvidge et al.(2021)]{elvidge_annual_2021}
-Elvidge, C.
-D., M.
-Zhizhin, T.
-Ghosh, F.-C.
-Hsu, and J.
-Taneja.
-2021.
-Annual Time Series of Global VIIRS Nighttime Lights Derived from Monthly Averages: 2012 to 2019.
-\textit{Remote Sensing}, 13(5), 922.
+Elvidge CD, Zhizhin M, Ghosh T, Hsu FC, Taneja J (2021) Annual Time Series of Global VIIRS Nighttime Lights Derived from Monthly Averages: 2012 to 2019. \textit{Remote Sensing} 13(5):922.
 
 \bibitem[Farrell and Shapiro(1990)]{farrell_horizontal_1990}
-Farrell, J., and C. Shapiro. 1990. Horizontal Mergers: An Equilibrium Analysis. \textit{American Economic Review}, 80(1), 107-126.
+Farrell J, Shapiro C (1990) Horizontal Mergers: An Equilibrium Analysis. \textit{American Economic Review} 80(1):107-126.
 
 \bibitem[Genesove and Han(2012)]{GENESOVE201231}
-Genesove, D., and L. Han. 2012. Search and Matching in the Housing Market. \textit{Journal of Urban Economics}, 72(1), 31-45.
+Genesove D, Han L (2012) Search and matching in the housing market. \textit{Journal of Urban Economics} 72(1):31-45.
 
 \bibitem[Gilbukh and Goldsmith-Pinkham(2019)]{gilbukh_goldsmith-pinkham_2019}
-Gilbukh, S., and P. Goldsmith-Pinkham. 2019. Heterogeneous Real Estate Agents and the Housing Cycle. Yale University Working Paper.
+Gilbukh S, Goldsmith-Pinkham P (2019) Heterogeneous Real Estate Agents and the Housing Cycle. \textit{SSRN Electronic Journal}.
 
 \bibitem[Glaeser et al.(2017)]{glaeser_real_2017}
-Glaeser, E., W. Huang, Y. Ma, and A. Shleifer. 2017. A Real Estate Boom with Chinese Characteristics. \textit{Journal of Economic Perspectives}, 31(1), 93-116.
+Glaeser E, Huang W, Ma Y, Shleifer A (2017) A Real Estate Boom with Chinese Characteristics. \textit{The Journal of Economic Perspectives} 31(1):93-116.
 
 \bibitem[Grossman and Stiglitz(1980)]{grossman_impossibility_1980}
-Grossman, S. J., and J. E. Stiglitz. 1980. On the Impossibility of Informationally Efficient Markets. \textit{American Economic Review}, 70(3), 393-408.
+Grossman SJ, Stiglitz JE (1980) On the impossibility of informationally efficient markets. \textit{American Economic Review} 70(3):393-408.
 
 \bibitem[Han and Hong(2011)]{550a6ccf-cde2-3dd1-979f-1a8db2b8ceb9}
-Han, L., and S.-H. Hong. 2011. Testing Cost Inefficiency Under Free Entry in the Real Estate Brokerage Industry. \textit{Journal of Business \& Economic Statistics}, 29(4), 564-578.
+Han L, Hong SH (2011) Testing Cost Inefficiency Under Free Entry in the Real Estate Brokerage Industry. \textit{Journal of Business \& Economic Statistics} 29(4):564-578.
 
 \bibitem[Han and Strange(2015)]{HAN2015813}
-Han, L., and W. C. Strange. 2015. The Microstructure of Housing Markets: Search, Bargaining, and Brokerage. In \textit{Handbook of Regional and Urban Economics}, Vol. 5, pp. 813-886.
+Han L, Strange WC (2015) The Microstructure of Housing Markets. \textit{Handbook of Regional and Urban Economics}. 813-886.
 
 \bibitem[Handbury(2021)]{handbury_are_2021}
-Handbury, J. 2021. Are Poor Cities Cheap for Everyone? Non-Homotheticity and the Cost of Living Across U.S. Cities. \textit{Econometrica}, 89(6), 2679-2715.
+Handbury J (2021) Are Poor Cities Cheap for Everyone? Non-Homotheticity and the Cost of Living Across U.S. Cities. \textit{Econometrica} 89(6):2679-2715.
 
 \bibitem[Hendel et al.(2009)]{hendel_relative_2009} 
-Hendel, I., A. Nevo, and F. Ortalo-Magné. 2009. The Relative Performance of Real Estate Marketing Platforms: MLS versus FSBOMadison.com. \textit{American Economic Review}, 99(5), 1878-1898.
+Hendel I, Nevo A, Ortalo-Magné F (2009) The Relative Performance of Real Estate Marketing Platforms: MLS versus FSBOMadison.com. \textit{American Economic Review} 99(5):1878-1898.
 
 \bibitem[Hong(2022)]{https://doi.org/10.1002/jae.2891}
-Hong, S.-H. 2022. Real Estate Agents' Influence on Housing Search. \textit{Journal of Applied Econometrics}, 37(3), 563-582.
+Hong S-H (2022) Real estate agents' influence on housing search. \textit{Journal of Applied Econometrics} 37(3):563-582.
 
 \bibitem[Hotelling(1929)]{hotelling_stability_1929}
-Hotelling, H. 1929. The Stability in Competition. \textit{Economic Journal}, 39, 41-57.
+Hotelling H (1929) Stability in Competition. \textit{The Economic Journal} 39(153):41-57.
 
 \bibitem[Hsieh and Moretti(2003)]{hsieh_can_2003}
-Hsieh, C.-T., and E. Moretti. 2003. Can Free Entry Be Inefficient? Fixed Commissions and Social Waste in the Real Estate Industry. \textit{Journal of Political Economy}, 111(5), 1076-1122.
+Hsieh C-T, Moretti E (2003) Can Free Entry Be Inefficient? Fixed Commissions and Social Waste in the Real Estate Industry. \textit{Journal of Political Economy} 111(5):1076-1122.
 
 \bibitem[Hui and Chan(2014)]{hui_foreign_2014}
-Hui, E. C. M., and K. K. K. Chan. 2014. Foreign Direct Investment in China's real estate market. \textit{Habitat International}, 43, 231-239.
+Hui ECM, Chan KKK (2014) Foreign direct investment in China's real estate market. \textit{Habitat International} 43:231-239.
 
 \bibitem[Jud et al.(1996)]{doi:10.1080/10835547.1996.12090852}
-Jud, D., T. Seaks, and D. Winkler. 1996. Time on the Market: The Impact of Residential Brokerage. \textit{Journal of Real Estate Research}, 12(2), 447-458.
+Jud D, Seaks T, Winkler D (1996) Time on the Market: The Impact of Residential Brokerage. \textit{Journal of Real Estate Research} 12(2):447-458.
 
 \bibitem[Langley and Leyshon(2017)]{Langley_Leyshon_2017}
-Langley, P., and A. Leyshon. 2017. Platform Capitalism: The Intermediation and Capitalisation of Digital Economic Circulation. \textit{Finance and Society}, 3(1), 11-31.
+Langley P, Leyshon A (2017) Platform capitalism: The intermediation and capitalisation of digital economic circulation. \textit{Finance and Society} 3(1):11-31.
 
 \bibitem[Levitt and Syverson(2008)]{d082a2db-5cce-33f2-87c4-9cb020cc6666}
-Levitt, S.
-D., and C.
-Syverson.
-2008.
-Market Distortions When Agents Are Better Informed: The Value of Information in Real Estate Transactions.
-\textit{The Review of Economics and Statistics}, 90(4), 599-611.
+Levitt SD, Syverson C (2008) Market Distortions When Agents Are Better Informed: The Value of Information in Real Estate Transactions. \textit{The Review of Economics and Statistics} 90(4):599-611.
+
+\bibitem[Li et al.(2019)]{LI2019165}
+Li H, Wei YD, Wu Y, Tian G (2019) Analyzing housing prices in Shanghai with open data: Amenity, accessibility and urban structure. \textit{Cities} 91:165-179.
 
 \bibitem[Li and Qi(2022)]{10.1093/cje/beac054}
-Li, Z., and H. Qi. 2022. Platform Power: Monopolisation and Financialisation in the Era of Big Tech. \textit{Cambridge Journal of Economics}, 46(6), 1289-1314.
-
-\bibitem[Li et al.(2019)]{LI2019165}
-Li, H., Y. D. Wei, Y. Wu, and G. Tian. 2019. Analyzing Housing Prices in Shanghai with Open Data: Amenity, Accessibility, and Urban Structure. \textit{Cities}, 91, 165-179.
+Li Z, Qi H (2022) Platform power: monopolisation and financialisation in the era of big tech. \textit{Cambridge Journal of Economics} 46(6):1289-1314.
 
 \bibitem[Liu et al.(2023)]{liu2023chrono-urbanism}
-Liu, D., M.-P.
-Kwan, L.
-Wang, Z.
-Kan, J.
-Wang, and J.
-Huang.
-2023.
-Development of a Chrono-Urbanism Status Composite Index under the 5/10/15-Minute City Concept Using Social Media Big Data.
-\textit{Tijdschrift voor Economische en Sociale Geografie}, Early View.
-doi:10.1111/tesg.12613.
+Liu D, Kwan M-P, Wang L, Kan Z, Wang J, Huang J (2024) Development of a Chrono-Urbanism Status Composite Index under the 5/10/15-Minute City Concept Using Social Media Big Data.
+\textit{Tijdschrift Voor Economische En Sociale Geografie}.
 
 \bibitem[Machado and Santos Silva(2019)]{machado_quantiles_2019}
-Machado, J. A. F., and J. M. C. Santos Silva. 2019. Quantiles via Moments. \textit{Journal of Econometrics}, 213(1), 145-173.
+Machado JAF, Silva JMCS (2019) Quantiles via moments. \textit{Journal of Econometrics} 213(1):145-173.
 
 \bibitem[McCrary(2008)]{MCCRARY2008698}
-McCrary, J. 2008. Manipulation of the Running Variable in the Regression Discontinuity Design: A Density Test. \textit{Journal of Econometrics}, 142(2), 698-714.
+McCrary J (2008) Manipulation of the running variable in the regression discontinuity design: A density test. \textit{Journal of Econometrics} 142(2):698-714.
 
@@
 2018.
-\textit{Urban Residential Area Planning and Design Standard (GB50180-2018)}.
-Available from \url{http://www.moe.gov.cn/jyb_xwfb/xw_zt/moe_357/jyzt_2019n/2019_zt13/zcwj/201906/t20190606_384732.html}.
+Urban residential area planning and design standard (GB50180-2018).
+Available at: \url{http://www.moe.gov.cn/jyb_xwfb/xw_zt/moe_357/jyzt_2019n/2019_zt13/zcwj/201906/t20190606_384732.html} (accessed July 7, 2023).
 (in Chinese).
@@
 \bibitem[Peng(2023)]{peng_mortgage_2023}
-Peng, Y.
-2023.
-Mortgage Credit and Housing Markets.
-\textit{SSRN Electronic Journal}, Working Paper.
-Available at \url{https://ssrn.com/abstract=4537500} or \url{http://dx.doi.org/10.2139/ssrn.4537500}.
+Peng Y (2023) Mortgage Credit and Housing Markets. \textit{SSRN Electronic Journal}. % Available at \url{https://ssrn.com/abstract=4537500} or \url{http://dx.doi.org/10.2139/ssrn.4537500}.
 
 \bibitem[Piazzesi et al.(2020)]{10.1257/aer.20141772}
-Piazzesi, M., M. Schneider, and J. Stroebel. 2020. Segmented Housing Search. \textit{American Economic Review}, 110(3), 720-759.
+Piazzesi M, Schneider M, Stroebel J (2020) Segmented Housing Search. \textit{American Economic Review} 110(3):720-759.
 
 \bibitem[Pope et al.(2015)]{POPE201589}
-Pope, D. G., J. C. Pope, and J. R. Sydnor. 2015. Focal Points and Bargaining in Housing Markets. \textit{Games and Economic Behavior}, 93, 89-107.
+Pope DG, Pope JC, Sydnor JR (2015) Focal points and bargaining in housing markets. \textit{Games and Economic Behavior} 93:89-107.
 
 \bibitem[Qu et al.(2021)]{qu_identifying_2021}
-Qu, W., Y. Huang, and G. Deng. 2021. Identifying the Critical Factors Behind the Second-Hand Housing Price Concession: Empirical Evidence from China. \textit{Habitat International}, 117, 102442.
+Qu W, Huang Y, Deng G (2021) Identifying the critical factors behind the second-hand housing price concession: Empirical evidence from China. \textit{Habitat International} 117:102442.
 
 \bibitem[Rochet and Tirole(2003)]{10.1162/154247603322493212}
-Rochet, J.-C., and J. Tirole. 2003. Platform Competition in Two-Sided Markets. \textit{Journal of the European Economic Association}, 1(4), 990-1029.
+Rochet JC, Tirole J (2003) Platform Competition in Two-Sided Markets. \textit{Journal of the European Economic Association} 1(4):990-1029.
 
 \bibitem[Rochet and Tirole(2006)]{https://doi.org/10.1111/j.1756-2171.2006.tb00036.x}
-Rochet, J.-C., and J. Tirole. 2006. Two-Sided Markets: A Progress Report. \textit{The RAND Journal of Economics} 37(3): 645-667. % https://doi.org/10.1111/j.1756-2171.2006.tb00036.x.
+Rochet JC, Tirole J (2006) Two-sided markets: a progress report. \textit{The RAND Journal of Economics} 37(3):645-667.
 
 \bibitem[Rosen(1974)]{Rosen_hedonic}
-Rosen, S.
-1974.
-Hedonic Prices and Implicit Markets: Product Differentiation in Pure Competition.
-\textit{Journal of Political Economy}, 82(1), 34-55.% Available at \url{http://www.jstor.org/stable/1830899}.
+Rosen S (1974) Hedonic Prices and Implicit Markets: Product Differentiation in Pure Competition. \textit{Journal of Political Economy} 82(1):34-55.
 
 \bibitem[Rysman(2009)]{10.1257/jep.23.3.125}
-Rysman, M. 2009. The Economics of Two-Sided Markets. \textit{Journal of Economic Perspectives} 23(3): 125-143. % https://doi.org/10.1257/jep.23.3.125.
+Rysman M (2009) The Economics of Two-Sided Markets. \textit{Journal of Economic Perspectives} 23(3):125-143.
 
 \bibitem[Salz(2022)]{salz_intermediation_2022}
-Salz, T. 2022. Intermediation and Competition in Search Markets: An Empirical Case Study. \textit{Journal of Political Economy}, 130(2), 310-345.
+Salz T (2022) Intermediation and Competition in Search Markets: An Empirical Case Study. \textit{Journal of Political Economy} 130(2):310-345.
 
 \bibitem[Sirmans et al.(1991)]{SIRMANS1991207}
-Sirmans, C. F., G. K. Turnbull, and J. D. Benjamin. 1991. The Markets for Housing and Real Estate Broker Services. \textit{Journal of Housing Economics}, 1(3), 207-217.
+Sirmans CF, Turnbull GK, Benjamin JD (1991) The markets for housing and real estate broker services. \textit{Journal of Housing Economics} 1(3):207-217.
 
 \bibitem[Van Donkelaar et al.(2021)]{doi:10.1021/acs.est.1c05309}
-Van Donkelaar, A., M.
-S.
-Hammer, L.
-Bindle, M.
-Brauer, J.
-R.
-Brook, M.
-J.
-Garay, N.
-C.
-Hsu, O.
-V.
-Kalashnikova, R.
-A.
-Kahn, C.
-Lee, R.
-C.
-Levy, A.
-Lyapustin, A.
-M.
-Sayer, and R.
-V.
-Martin.
-2021.
-Monthly Global Estimates of Fine Particulate Matter and Their Uncertainty.
-\textit{Environmental Science \& Technology}, 55(22), 15287-15300.
+Van Donkelaar A, Hammer MS, Bindle L, Brauer M, Brook JR, Garay MJ, Hsu NC, et al.
+(2021) Monthly Global Estimates of Fine Particulate Matter and Their Uncertainty.
+\textit{Environmental Science \& Technology} 55(22):15287-15300.
 
 \bibitem[Van Nieuwerburgh and Veldkamp(2010)]{NIEUWERBURGH_information}
-Van Nieuwerburgh, S., and L. Veldkamp. 2010. Information Acquisition and Under-Diversification. \textit{The Review of Economic Studies}, 77(2), 779-805.
+Van Nieuwerburgh S, Veldkamp L (2010) Information Acquisition and Under-Diversification. \textit{The Review of Economic Studies} 77(2):779-805.
 
 \bibitem[Varian(2014)]{10.1257/jep.28.2.3}
-Varian, H. R. 2014. Big Data: New Tricks for Econometrics. \textit{Journal of Economic Perspectives}, 28(2), 3-28.
+Varian HR (2014) Big Data: New Tricks for Econometrics. \textit{Journal of Economic Perspectives} 28(2):3-28.
 
 \bibitem[Wei and Zhang(2011)]{wei_competitive_2011}
-Wei, S.-J., and X. Zhang. 2011. The Competitive Saving Motive: Evidence from Rising Sex Ratios and Savings Rates in China. \textit{Journal of Political Economy}, 119(3), 511-564.
+Wei SJ, Zhang X (2011) The Competitive Saving Motive: Evidence from Rising Sex Ratios and Savings Rates in China. \textit{Journal of Political Economy} 119(3):511-564.
 
 \bibitem[Weyl(2010)]{10.1257/aer.100.4.1642}
-Weyl, E. G. 2010. A Price Theory of Multi-Sided Platforms. \textit{American Economic Review} 100(4): 1642-1672. % https://doi.org/10.1257/aer.100.4.1642.
+Weyl EG (2010) A Price Theory of Multi-Sided Platforms. \textit{American Economic Review} 100(4):1642-1672.
 
 \bibitem[Williams(1998)]{williams_agency_1998}
-Williams, J. T. 1998. Agency and Brokerage of Real Assets in Competitive Equilibrium. \textit{Review of Financial Studies}, 11(2), 239-280.
+Williams JT (1998) Agency and Brokerage of Real Assets in Competitive Equilibrium. \textit{Review of Financial Studies} 11(2):239-280.
 
 \bibitem[Wong et al.(2012)]{wong_liquidity_2012}
-Wong, S. K., C. Y. Yiu, and K. W. Chau. 2012. Liquidity and Information Asymmetry in the Real Estate Market. \textit{The Journal of Real Estate Finance and Economics}, 45(1), 49-62.
+Wong SK, Yiu CY, Chau KW (2011) Liquidity and Information Asymmetry in the Real Estate Market. \textit{The Journal of Real Estate Finance and Economics} 45(1):49-62.
 
 \bibitem[Yang et al.(2021)]{YANG2021102359}
-Yang, L., K. W. Chau, and Y. Chen. 2021. Impacts of Information Asymmetry and Policy Shock on Rental and Vacancy Dynamics in Retail Property Markets. \textit{Habitat International}, 111, 102359.
+Yang L, Chau KW, Chen Y (2021) Impacts of information asymmetry and policy shock on rental and vacancy dynamics in retail property markets. \textit{Habitat International} 111:102359.
 
 \bibitem[Zhang et al.(2021)]{ZHANG2021101104}
-Zhang, X., Z.
-Lin, Y.
-Zhang, Y.
-Zheng, and J.
-Zhang.
-2021.
-Online Property Brokerage Platform and Prices of Second-Hand Houses: Evidence from Lianjia's Entry.
-\textit{Electronic Commerce Research and Applications}, 50, 101104.
+Zhang X, Lin Z, Zhang Y, Zheng Y, Zhang J (2021) Online property brokerage platform and prices of second-hand houses: Evidence from Lianjia's entry.
+\textit{Electronic Commerce Research and Applications} 50:101104.
+
+\bibitem[Zhao(2015)]{zhao_rational_2015}
+Zhao B (2015) Rational housing bubble. \textit{Economic Theory} 60(1):141-201.
 
 \bibitem[Zhao et al.(2017)]{zhao_forecasting_2017}
-Zhao, N., Y.
-Liu, G.
-Cao, E.
-L.
-Samson, and J.
-Zhang.
-2017.
-Forecasting China's GDP at the Pixel Level Using Nighttime Lights Time Series and Population Images.
-\textit{GIScience \& Remote Sensing}, 54(3), 407-425.
-
-\bibitem[Zhao(2015)]{zhao_rational_2015}
-Zhao, B. 2015. Rational Housing Bubble. \textit{Economic Theory}, 60(1), 141-201.
+Zhao N, Liu Y, Cao G, Samson EL, Zhang J (2017) Forecasting China's GDP at the pixel level using nighttime lights time series and population images. \textit{GIScience \& Remote Sensing} 54(3):407-425.
 
 \bibitem[Zhu and Iansiti(2019)]{WOS:000454186600016}
-Zhu, F., and M. Iansiti. 2019. Why Some Platforms Thrive and Others Don't. \textit{Harvard Business Review}, 97(1), 118-125.
+Zhu F, Iansiti M (2019) Why Some Platforms Thrive and Others Don't. \textit{Harvard Business Review} 97(1):118-125.
 
 \bibitem[Zumpano et al.(2003)]{ZUMPANO2003134}
-Zumpano, L. V., K. H. Johnson, and R. I. Anderson. 2003. Internet Use and Real Estate Brokerage Market Intermediation. \textit{Journal of Housing Economics}, 12(2), 134-150.
+Zumpano LV, Johnson KH, Anderson RI (2003) Internet use and real estate brokerage market intermediation. \textit{Journal of Housing Economics} 12(2):134-150.
 

### 2024-08-12 manuscript/main.tex
new file:   analysis/.Rhistory 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

@@
 
-\author[1]{Guoying Deng}
-\author[2]{Xuyuan Zhang \thanks{Email Address: \href{mailto:zxuyuan@umich.edu}{zxuyuan@umich.edu}}}
-\affil[1]{School of Economics, Sichuan University, China}
-\affil[2]{Department of Economics, University of Michigan, United States}
+\author[1]{Guoying Deng} % dengguoying@scu.edu.cn
+\author[2,3]{Li Gan} % ganli@tamu.edu 
+\author[4]{Xuyuan Zhang \thanks{Email Address: \href{mailto:zxuyuan@umich.edu}{zxuyuan@umich.edu}}}
+\affil[1]{School of Economics, Sichuan University, Chengdu, China}
+\affil[2]{Department of Economics, Texas A\&M University, College Station, TX, USA}
+\affil[3]{Survey and Research Center for China Household Finance, Southwestern University of Finance and Economics, Chengdu, China}
+\affil[4]{Department of Economics, University of Michigan, Ann Arbor, MI, USA}
 

### 2024-08-13 manuscript/main.tex
new file:   archived manuscript/main.tex 	new file:   archived manuscript/our-cites.bib 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

@@
 
+% bergemann_data_2024
+
 % https://www.zaobao.com.sg/realtime/china/story20231213-1455835#:~:text=%E6%8D%AE%E5%A4%AE%E8%A7%86%E6%96%B0%E9%97%BB%E6%8A%A5%E9%81%93%EF%BC%8C%E4%B8%AD%E5%9B%BD,%E6%96%B0%E5%BB%BA%E5%95%86%E5%93%81%E4%BD%8F%E5%AE%85%E4%BA%A4%E6%98%93%E9%87%8F%E3%80%82
@@
 
-While sellers might consider a co-listing strategy—listing their property with multiple brokerages—this approach is suboptimal for several reasons within China's real estate market.
-Despite previous literature, such as \citep{RePEc:kap:jrefec:v:67:y:2023:i:3:d:10.1007_s11146-021-09858-w}, indicating that the co-listing can be beneficial for clients under multiple-listing service.
-Specifically in China's real estate market, firstly, the exclusivity of contracts between sellers and agents often precludes the adoption of a co-listing strategy.
-Secondly, although sellers can list their properties with multiple brokerages, smaller agencies frequently lack a sufficiently broad client base, limiting their effectiveness in selling homes.
-Thirdly, engaging multiple brokers simultaneously can lead to reduced incentives among agents, as they perceive competition for the same property, diminishing their proactive efforts.
-Finally, while service cost variations between agencies are acknowledged, these costs are minor compared to the property's value and are more closely related to the risks associated with holding a financial asset.
-Consequently, risk-averse sellers are inclined to choose an agency that provides a guaranteed level of service.
+While the co-listing strategy—listing properties with multiple brokerages—has been suggested as beneficial in some markets, such as under a multiple-listing service \citep{RePEc:kap:jrefec:v:67:y:2023:i:3:d:10.1007_s11146-021-09858-w}, it is suboptimal within China's real estate context for several reasons.
+First, exclusive contracts between sellers and agents typically preclude co-listing, thereby limiting its feasibility.
+Second, although sellers can list with multiple brokerages, smaller agencies often lack a sufficient client base, reducing their effectiveness.
+Third, engaging multiple brokers can dilute agent incentives due to perceived competition, leading to less proactive efforts.
+Finally, while agency service cost differences exist, these costs are relatively minor compared to the property's value and are more closely related to the financial risks involved.
+Consequently, risk-averse sellers tend to prefer agencies offering a guaranteed service level.
+Moreover, \citet{bergemann_data_2024} finds that when platforms possess significant bargaining power, co-listing with multiple agents is no more efficient than listing with a single agent.
 
@@
 These findings can be extended to other similar fields, as discussed by \citep{10.1257/jep.28.2.3}.
-Lastly, this study also confirms that local network effect can not preclude other competitors from entering the market but the network effect can help the company to coexist with other competitors, and improve the overall market efficiency, consistent with the work by \citep{gilbukh_goldsmith-pinkham_2019}.
+Fourthly, this study also confirms that local network effect can not preclude other competitors from entering the market but the network effect can help the company to coexist with other competitors, and improve the overall market efficiency, consistent with the work by \citep{gilbukh_goldsmith-pinkham_2019}.
+Lastly, our paper use empirical data to shows the broad implication of the research \citep{bergemann_data_2024}, where the platform can benefits from increased bargaining power vis-\'a-vis sellers by exploiting its information advantage.
 
@@
 Beck J, Scott F, Yelowitz A (2022) The Impact of Real Estate Agent Specialization and Activity Level on Market Outcomes. \textit{Journal of Housing Research} 31(2):163-180.
+
+\bibitem[Bergemann and Bonatti(2024)]{bergemann_data_2024}
+Bergemann D, Bonatti A (2024) Data, Competition, and Digital Platforms. American Economic Review 114(8):2553-2595.
 

### 2024-08-16 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

@@
 
-According to the Ministry of Housing and Urban-Rural Development in China, the proportion of second-hand housing transactions rose to 37.1\% in 2023, with this trend showing continuous growth.
-Unlike the primary housing market, where transactions are straightforward, the secondary housing market necessitates sellers having access to buyers, thereby making transaction costs a critical factor for both parties.
-In this context, real estate brokers play a pivotal role in mitigating these costs.
-They provide essential market information, negotiation support, and legal assistance, thereby facilitating smoother and more efficient transactions in the real estate market.
-The involvement of brokers reduces the information asymmetry and transactional frictions that are characteristic of the secondary housing market, thus enhancing market efficiency.
-
-With the improvement of China's legal system in the real estate market, the brokerage market is expanding and becoming more prosperous.
-Moreover, it is not merely a matter of legal improvement, as in the past, the intermediary market was quite chaotic, with individuals being able to set up a brokerage business without any qualifications.
-Nowadays, the government has taken steps to regulate the disorderly conduct of intermediaries through administrative and legal measures, leading to a more standardized and orderly market environment.
-Especially in the context of China's burgeoning real estate market, brokerage firms are assuming an increasingly important role in facilitating the communications between buyers and sellers \citep{glaeser_real_2017}.
-Given the heterogeneous and "thin" nature of real estate goods \citep{HAN2015813}, the expertise and local market knowledge of real estate brokers have become indispensable in navigating the complex real estate landscape.
+In recent years, the secondary housing market in China has seen significant growth, with the proportion of second-hand housing transactions rising to 37.1\% in 2023, according to the Ministry of Housing and Urban-Rural Development.
+This growing market presents unique challenges compared to the primary housing market, primarily due to the necessity for sellers to connect with buyers, making transaction costs a critical factor.
+Real estate brokers play a pivotal role in mitigating these costs by providing essential market information, negotiation support, and legal assistance, thus facilitating smoother and more efficient transactions.
+The evolution of China's legal and regulatory framework has significantly impacted the real estate brokerage market, leading to increased standardization and a more orderly market environment.
+However, despite these improvements, the market remains characterized by offline-dominated transactions, where brokers' expertise and local market knowledge are indispensable due to the persistent information asymmetry.
+Given the heterogeneous and "thin" nature of real estate goods \citep{glaeser_real_2017, HAN2015813}, the expertise and local market knowledge of real estate brokers have become indispensable in navigating the complex real estate landscape.
 
@@
 
-Additionally, in the China's real estate market, brokerages still operate on a bilateral agency model, where sellers need to choose the agency that can help them sell their home in the fastest time and for the highest price possible for the transaction.
-However, due to the asymmetric information inherent in the real estate market, sellers face challenges in effectively informing and matching with potential buyers.
-In a perfectly competitive market, sellers would be indifferent in their choice of real estate agents.
-Nonetheless, as the market trends toward increased monopolistic competition, sellers confront a dichotomous decision: engage a larger brokerage firm, which, despite higher fees, offers the potential for expedited transactions, or opt for a smaller brokerage with lower fees but potentially less efficient transaction facilitation.
-
-While the co-listing strategy—listing properties with multiple brokerages—has been suggested as beneficial in some markets, such as under a multiple-listing service \citep{RePEc:kap:jrefec:v:67:y:2023:i:3:d:10.1007_s11146-021-09858-w}, it is suboptimal within China's real estate context for several reasons.
-First, exclusive contracts between sellers and agents typically preclude co-listing, thereby limiting its feasibility.
-Second, although sellers can list with multiple brokerages, smaller agencies often lack a sufficient client base, reducing their effectiveness.
-Third, engaging multiple brokers can dilute agent incentives due to perceived competition, leading to less proactive efforts.
-Finally, while agency service cost differences exist, these costs are relatively minor compared to the property's value and are more closely related to the financial risks involved.
-Consequently, risk-averse sellers tend to prefer agencies offering a guaranteed service level.
-Moreover, \citet{bergemann_data_2024} finds that when platforms possess significant bargaining power, co-listing with multiple agents is no more efficient than listing with a single agent.
-
-Given the dual nature of online promotion and offline transactions in the real estate brokerage industry, the quality of offline services is crucial for influencing client decisions.
-This principle underpins Lianjia's strategy of establishing numerous stores within targeted communities.
-By opening a wide range of stores in various neighborhoods and adopting a downstream consolidation model through platform design, the brokerage effectively attracts sellers to list their properties and buyers through its extensive platform resources.
-This strategy not only enhances transaction volume but also increases income derived from these transactions.
+In China's real estate market, brokerages predominantly operate under a bilateral agency model, where sellers are incentivized to select agencies that can maximize transaction speed and sale price.
+This agency selection process reflects the strategic behavior of sellers seeking to optimize outcomes within the competitive dynamics of the market.
+This decision is complicated by the inherent asymmetric information characteristic of real estate markets, which hinders sellers' ability to effectively communicate and connect with potential buyers.
+In a perfectly competitive market, sellers would theoretically be indifferent in their choice of real estate agents.
+However, as the market increasingly exhibits traits of monopolistic competition, sellers face a strategic choice: they can either engage a larger brokerage firm, which, despite commanding higher fees, offers the potential for quicker transactions due to superior market reach and resources, or they may opt for a smaller brokerage, which might charge lower fees but could be less efficient in facilitating transactions.
+
+This decision-making process is consistent with the theoretical framework proposed by \citep{bergemann_data_2024}, which examines the dynamics of platforms operating in markets characterized by product heterogeneity and significant market power.
+According to this framework, platforms can use their informational advantages and market power to attract higher quality sellers with lower listing prices by offering more favorable terms, such as more buyers.
+This ability to discriminate among sellers based on the quality of their offerings not only enhances the competitive position of the platform, but also contributes to more efficient market outcomes by aligning incentives between sellers and the platform.
+
+Nevertheless,  it is of the importance for the platform to meticulously evaluate the multihoming strategies that are utilized by the sellers.
+While the co-listing approach—where properties are listed with multiple brokerages—has been demonstrated to yield positive outcomes in certain markets, particularly those utilizing a multiple-listing service \citep{RePEc:kap:jrefec:v:67:y:2023:i:3:d:10.1007_s11146-021-09858-w}, it has been shown to be suboptimal in the context of China's real estate market for several reasons.
+Firstly, exclusive contracts between sellers and agents typically preclude co-listing, thereby limiting its feasibility.
+Secondly, although sellers are permitted to list with multiple brokerages, smaller agencies frequently lack an adequate client base, which consequently diminishes their efficacy.
+Thirdly, engaging multiple brokers can result in a dilution of agent incentives due to the perception of competition, which may lead to a reduction in proactive efforts.
+Finally, while there are differences in the costs of agency services, these costs are relatively minor in comparison to the value of the property and are more closely related to the financial risks involved.
+Consequently, risk-averse sellers tend to prefer agencies that offer a guaranteed level of service.
+Furthermore, \citet{bergemann_data_2024} finds that when platforms possess significant bargaining power, co-listing with multiple agents is no more efficient than listing with a single agent.\footnote{The original paper employs an off-platform transaction, yet the concept can be extended to encompass other brokerages in this context.}
+
+In the dual-natured environment of China's real estate brokerage industry, where online promotion and offline transactions are intertwined, the quality of offline services plays a pivotal role in influencing client decisions.
+This principle informs Lianjia's strategic approach, which entails the establishment of a dense network of storefronts within targeted neighborhoods.
+By proliferating stores across various neighborhoods and integrating a downstream consolidation model through platform design, Lianjia effectively capitalizes on its extensive resources to attract both sellers and buyers.
+This strategy not only boosts transaction volumes but also enhances the brokerage's revenue streams from these transactions, underscoring the importance of offline service quality in a market increasingly dominated by large, powerful platforms.
 
@@
 This exogenous effect captures the clustering impact of offline real estate brokerage stores.
-Our results indicate that Lianjia's offline stores significantly enhance transaction revenues, although this effect diminishes during and after the COVID-19 period.
-
-To evaluate the effects of platform-mediated consolidation, we consider the year Lianjia implemented its platform-mediated consolidation strategy as an exogenous shock to the market.
-This strategy primarily revolves around the ACN framework of Lianjia and the incorporation of various franchise stores into the network.
-Our empirical analysis indicates that this strategy significantly increases revenues and enhances the attraction of buyers and sellers, particularly in the number of house tours facilitated by the brokerage.
-However, our findings suggest that the platform-mediated consolidation does not effectively reduce the transaction period nor does it promote price concessions.
-This contrasts with the offline expansion strategy, which demonstrates a positive impact on promoting price concessions.
-While the economic impact of the online-based consolidation strategy is not as pronounced as that of the offline expansion strategy, it remains economically significant.
+The results demonstrate that Lianjia's offline stores markedly augment transaction revenues, although this impact wanes during and in the aftermath of the COVID-19 pandemic.
+Furthermore, the expansion of offline stores has been found to significantly increase the extent of price concessions, a result that is consistent with the findings of \citep{bergemann_data_2024}, where the bargaining power of the platform was found to be positively correlated with the pricing strategies employed by the seller.
+
+In order to evaluate the effects of platform-mediated consolidation, it is essential to consider the year in which Lianjia implemented its consolidation strategy, as this can be viewed as an exogenous shock to the market.
+This strategy, which was based on Lianjia's ACN framework, entailed the integration of a diverse range of franchise stores into its network.
+The empirical analysis demonstrates that this consolidation strategy led to a notable increase in revenues and enhanced the platform's appeal to both buyers and sellers, particularly by facilitating a greater number of house tours through the brokerage.
+Nevertheless, the analysis indicates that platform-mediated consolidation did not result in an immediate reduction in the transaction period or the promotion of price concessions in the short term.
+The notable impact on price concessions became evident after two periods following the consolidation, in alignment with Lianjia's offline expansion strategy, which exerted a positive influence on price concessions.
+This delayed impact can be attributed to the continued role of offline stores in the transaction process.
+In the initial stages, online advertisements may not be an effective means of attracting buyers.
+However, as the network expands and more buyers and sellers place their trust in the platform, the benefits become more pronounced.
+The integration of offline stores enhances the platform's bargaining power vis-à-vis sellers, as these physical locations are instrumental in converting buyer interest into completed transactions and consolidating the platform's market influence.
 
@@
 This effect can be attributed to the enhanced efficiency in matching buyers with suitable properties, thereby encouraging sellers to be more amenable to price negotiations.
+This also suggests that brokerages may be able to leverage improved bargaining power with sellers, potentially leading to enhanced transaction outcomes.
 Additionally, offline stores possess better control over neighborhood information, which aids in effectively marketing properties to potential buyers, thereby capturing additional surplus.
@@
 However, this effect diminishes for the moderately competitive group.
-The result indicates that the results indicate that when facing other competitors in the market, Lianjia is more likely to make greater efforts to attract more sellers.
-This analysis underscores the varying impacts of market concentration on Lianjia's market performance post-entry.
+The results suggest that Lianjia is more likely to intensify its efforts to attract a larger number of sellers when faced with increased market competition.
+As the number of sellers listing with Lianjia increases, the brokerage is able to attract a greater number of buyers and offer better services.
+By leveraging this expanded customer base, Lianjia is able to enhance its bargaining power over sellers, which in turn allows for greater price concessions in final transactions, ultimately benefiting the platform's overall competitive position in the market and increases total welfare.
 

### 2024-08-17 manuscript/main.tex
modified:   manuscript/main.aux 	new file:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

@@
 Compared to the United States, where the Multiple Listing Service (MLS) provides comprehensive and reliable information online, facilitating transactions in a market where suits are typically situated far apart, the role of offline real estate stores is minimized.\footnote{\citet{hendel_relative_2009} documents that the MLS market experiences a significant growth in recent years.} In contrast, China's real estate market is predominantly offline-based, with online listings serving mainly as references.
-Face-to-face interactions remain crucial for transactions.
-Additionally, Chinese government imposes stringent restrictions on the upper and lower limits of online listing prices, leading to a reluctance among sellers to list their properties online.
-This regulatory environment allows real estate brokerages to sometimes post misleading prices to attract potential buyers, subsequently offering private information about other properties.
-Moreover, the China's real estate brokerage market operates under a bilateral agency model, resulting in lower transaction efficiency compared to the United States brokerage market.
-In Singapore, the real estate market is heavily influenced by government-coordinated prices and evaluation companies' suggested prices.
-Conversely, in China, sellers have more freedom to set arbitrary listing prices in the offline market.
-It is common practice for Chinese sellers to list their properties at higher prices, anticipating that buyers will negotiate and feel incentivized by securing a perceived better deal.
+In-person interactions remain a vital aspect of the transaction process.
+Furthermore, the Chinese government imposes rigorous limitations on the upper and lower bounds of online listing prices, which has resulted in a reluctance among sellers to list their properties online.
+The regulatory environment permits real estate brokerages to occasionally post deceptive prices with the intention of attracting potential buyers, subsequently offering private information about other properties.
+Furthermore, the Chinese real estate brokerage market operates under a bilateral agency model, which results in a lower level of transaction efficiency when compared to the United States brokerage market.
+In Singapore, the real estate market is significantly influenced by government-coordinated prices and evaluation companies' suggested prices.
+Conversely, in China, sellers have greater autonomy to determine arbitrary listing prices in the offline market.
+It is a common practice for Chinese sellers to list their properties at higher prices, anticipating that buyers will negotiate and feel incentivized by securing a perceived better deal.
 
@@
 This strategy enables the realization of multiple revenue streams simultaneously, thereby optimizing operational efficiency and enhancing overall economic performance.\footnote{The ACN model disaggregates the transaction process into specialized tasks handled by individual agents or stores.
-These tasks include seller-side activities such as sourcing sellers, maintaining property listings, commission negotiations, and buyer-side activities like client acquisition, property-client matching, transaction facilitation, and financial services assistance.} Moreover, in 2018, Lianjia decided to enhance its Agent Cooperation Network (ACN) strategy by incorporating smaller brokerages into its network and launching franchise stores under the brand name Deyou, along with other smaller formats.
-This strategic move aimed to increase network effects and further consolidate the platform, thereby enhancing market power and operational efficiency.
+These tasks include seller-side activities such as sourcing sellers, maintaining property listings, commission negotiations, and buyer-side activities like client acquisition, property-client matching, transaction facilitation, and financial services assistance.} Furthermore, in 2018, Lianjia opted to augment its Agent Cooperation Network (ACN) strategy by integrating smaller brokerages into its network and inaugurating franchise stores under the Deyou brand, in addition to other smaller formats.
+This strategic maneuver was designed to augment network effects and further consolidate the platform, thereby enhancing market power and operational efficiency.
 
@@
 
-In the real estate market, real estate is not a homogeneous good, and therefore, the brokerage market is characterized by a large number of firms with no significant barriers to entry.
-Traditional economic theory suggests that such a market, characterized by substantial competition, numerous firms, and low market concentration, is consistent with real-world observations.
-For example, Lianjia's offline stores account for less than 5\% of the total, yet Lianjia handles about 20\% of the national transactions.
-In addition, many well-known agencies, such as Woaiwojia and Centaline Property Agency, operate in this market, indicating a monopolistic competitive environment.
-
-However, when looking at local segmented markets, the monopolistic competition model seems less applicable.
-In local markets, surrounding neighborhoods share similar community characteristics and public resources.
-Especially in China's real estate market, most properties are apartments, where the inherent differences between properties are minimal, making them relatively homogeneous goods.
-In addition, local real estate markets have no barriers to entry or exit, closely resembling perfect competition.
-From a cost perspective, the real estate market has undergone platform mediated reforms, where data resources have zero marginal cost characteristics and operating costs decrease as the user base expands, suggesting characteristics of a natural monopoly.
-Under these conditions, the operating position of firms differs significantly from that in a monopolistically competitive market.
-Due to network effects, an increase in the number of branches of a dominant real estate agency attracts more users, which in turn attracts more real estate listings.
-This positive feedback loop reinforces the dominant position of firms like Lianjia, leading to the formation of oligopolistic firms.
-These oligopolistic firms can further maintain their dominant market positions.
-
-In local segmented markets, oligopolistic firms are responsible for increasing network strength and have significant market power.
+In the context of the real estate market, it is evident that real estate is not a homogeneous good.
+Consequently, the brokerage market is distinguished by the presence of a considerable number of firms, exhibiting minimal barriers to entry.
+The prevailing economic theory posits that such a market, typified by robust competition, a multitude of firms, and a relatively low market concentration, is consistent with empirical observations.
+For instance, Lianjia's physical locations account for less than 5\% of the total, yet Lianjia handles approximately 20\% of the national transactions.
+Furthermore, numerous prominent agencies, such as Woaiwojia and Centaline Property Agency, operate within this market, indicating a monopolistic competitive environment.
+
+Nevertheless, when examining local segmented markets, the monopolistic competition model appears to be less pertinent.
+In local markets, the surrounding neighborhoods exhibit a high degree of homogeneity with respect to community characteristics and the availability of public resources.
+In particular, apartments are the most favored property type in the Chinese real estate market, characterized by minimal inherent differences, making them relatively homogeneous goods.
+Furthermore, local real estate markets exhibit no barriers to entry or exit, closely resembling perfect competition.
+From a cost perspective, the real estate market has undergone platform-mediated reforms, whereby data resources exhibit zero marginal cost characteristics and operating costs decrease in line with the expansion of the user base.
+This suggests the presence of characteristics associated with a natural monopoly.
+In light of these circumstances, the operational stance of firms diverges considerably from that observed in a monopolistically competitive market.
+The presence of network effects gives rise to a virtuous cycle wherein an expansion in the number of branches of a dominant real estate agency draws in a greater number of users, which in turn attracts a greater volume of real estate listings.
+This positive feedback loop serves to reinforce the dominant position of firms like Lianjia, ultimately leading to the formation of oligopolistic firms.
+These oligopolistic firms are then able to sustain and reinforce their dominant market positions.
+
+In local segmented markets, oligopolistic firms are responsible for increasing network strength and possess considerable market power.
 In segmented markets where some oligopolistic firms do not have strong network effects, multiple other firms serve the diverse needs of consumers and expand their scale.
-The environment of free entry, rapid technological progress, and business model innovation leads to an inclusive competitive landscape in the real estate brokerage market.
-This environment allows oligopolistic firms to either enhance the strength of their network effects or have their dominant positions challenged.
-As a result, monopolistic structures emerge from and are subsequently disrupted by competition, allowing real estate intermediaries to continuously evolve and drive the industry's rapid growth.
-The practical implication is that a competitive oligopolistic structure does not inherently impede competitive efficiency.
-Instead, as our empirical findings indicate, the enriched entry and transformations within the market lead to an increase in the number of transactions and house tours.
+The real estate brokerage market is characterised by an inclusive competitive landscape, which can be attributed to a number of factors, including free entry, rapid technological progress and business model innovation.
+This environment allows oligopolistic firms to either enhance the strength of their network effects or face challenges to their dominant positions.
+Consequently, monopolistic structures emerge from and are subsequently disrupted by competition, thereby enabling real estate intermediaries to continuously evolve and drive the industry's rapid growth.
+In practical terms, this suggests that a competitive oligopolistic structure does not inherently impede competitive efficiency.
+Rather, as our empirical findings indicate, the enriched entry and transformations within the market lead to an increase in the number of transactions and house tours.
 This type of market structure can enhance firm efficiency, thereby facilitating more efficient transactions for buyers and sellers and improving overall market welfare, even though it may impede individual seller welfare.
-
-As our empirical results show, Lianjia's strategy has significantly enhanced its network strength within segmented markets.
-From this perspective, the enhancement of network effects further drives the segmented market toward an oligopolistic competitive structure, which could increase the market welfare and facilitate the transactions between buyers and sellers.
-Moreover, with the development of online platforms and new technologies, such as Lianjia's latest VR home viewing technology, these network effects are gradually shifting from local networks to a global network.
-As a result, this development is shaping the overall market into an oligopolistic competition model on a larger scale.
-
-In the future, as the network effects intensify, the real estate brokerage market may witness a more pronounced consolidation of market power among a few dominant players.
-This consolidation can lead to increased efficiencies through economies of scale and scope, where firms leverage their vast data resources and technological advancements to optimize operations and enhance consumer experiences.
-However, this shift also raises important considerations for regulatory bodies to ensure that the market remains competitive and accessible.
-The dynamic interplay between technological innovation and market structure will be crucial.
-As firms like Lianjia continue to innovate, incorporating artificial intelligence, big data analytics, and blockchain for secure transactions, the real estate market could become more transparent and efficient.
-These advancements could lower transaction costs, reduce information asymmetry, and provide consumers with more personalized services.
-Furthermore, the global reach of network effects implies that real estate brokerage markets across different regions might become more interconnected.
-This interconnectivity can facilitate cross-city or cross-province investments and diversify property portfolios for investors, contributing to a more resilient real estate market.
+Moreover, this form of competition predominantly occurs among different brands within the larger platform, while the broader monopolistic or oligopolistic structure remains largely insulated from the competitive pressures posed by new entrants.
+
+As evidenced by our empirical findings, Lianjia's strategic approach has markedly augmented its network strength within the context of segmented markets.
+From this perspective, the enhancement of network effects further drives the segmented market toward an oligopolistic competitive structure, which could increase market welfare and facilitate transactions between buyers and sellers.
+Furthermore, with the advent of online platforms and novel technologies, such as Lianjia's cutting-edge virtual reality (VR) home viewing technology, these network effects are gradually shifting from local networks to a global network.
+Consequently, this development is transforming the overall market into an oligopolistic competition model on a larger scale.
+
+As network effects intensify in the future, the real estate brokerage market may witness a more pronounced consolidation of market power among a few dominant players.
+This consolidation may result in increased efficiencies through economies of scale and scope, whereby firms utilize their extensive data resources and technological advancements to optimize operations and enhance consumer experiences.
+Nevertheless, this transition gives rise to significant considerations for regulatory authorities, with a view to guaranteeing that the market remains competitive and accessible.
+The dynamic interplay between technological innovation and market structure will be of more crucial.
+As firms such as Lianjia persist in their efforts to innovate, incorporating artificial intelligence, big data analytics, and blockchain technology for secure transactions, the real estate market may become more transparent and efficient.
+Such developments could reduce transaction costs, diminish information asymmetry, and furnish consumers with more personalized services.
+Moreover, the global reach of network effects suggests that real estate brokerage markets across disparate regions may become more interconnected.
+This interconnectivity could facilitate cross-city or cross-province investments and diversify property portfolios for investors, thereby contributing to a more resilient real estate market.
 
 In conclusion, the evolution of the real estate brokerage market towards an oligopolistic competition model, driven by network effects and technological advancements, presents both opportunities and challenges.
-From our empirical findings, this type of market structure can not impede the competitive efficiencies but policymakers and industry stakeholders must navigate this landscape carefully to harness the benefits of increased efficiency and innovation while safeguarding against potential market power abuses and ensuring equitable access for all participants.
-This balanced approach will be essential for sustaining long-term growth and enhancing overall market welfare in the real estate industry.
+Our empirical findings indicate that this type of market structure does not impede competitive efficiencies.
+However, policymakers and industry stakeholders must navigate this landscape carefully to harness the benefits of increased efficiency and innovation while safeguarding against potential market power abuses and ensuring equitable access for all participants.
+A balanced approach to these issues will be essential for sustaining long-term growth and enhancing overall market welfare in the real estate industry.
 

### 2024-09-06 figures/distribution_of_hp_and_broker.tex
Update distribution_of_hp_and_broker.tex

@@
     \begin{minipage}{0.328\textwidth}
-        \includegraphics[width=\linewidth]{../figures/distribution_of_hp_and_broker/Beijing.pdf}
+        \includegraphics[width=\linewidth]{figures/distribution_of_hp_and_broker/Beijing.pdf}
     \end{minipage}
@@
     \begin{minipage}{0.328\textwidth}
-        \includegraphics[width=\linewidth]{../figures/distribution_of_hp_and_broker/Chengdu.pdf}
+        \includegraphics[width=\linewidth]{figures/distribution_of_hp_and_broker/Chengdu.pdf}
     \end{minipage}
     \begin{minipage}{0.328\textwidth}
-        \includegraphics[width=\linewidth]{../figures/distribution_of_hp_and_broker/Chongqing.pdf}
+        \includegraphics[width=\linewidth]{figures/distribution_of_hp_and_broker/Chongqing.pdf}
     \end{minipage}
@@
     \begin{minipage}{0.328\textwidth}
-        \includegraphics[width=\linewidth]{../figures/distribution_of_hp_and_broker/Guangzhou.pdf}
+        \includegraphics[width=\linewidth]{figures/distribution_of_hp_and_broker/Guangzhou.pdf}
     \end{minipage}
@@
     \begin{minipage}{0.328\textwidth}
-        \includegraphics[width=\linewidth]{../figures/distribution_of_hp_and_broker/Hangzhou.pdf}
+        \includegraphics[width=\linewidth]{figures/distribution_of_hp_and_broker/Hangzhou.pdf}
     \end{minipage}
     \begin{minipage}{0.328\textwidth}
-        \includegraphics[width=\linewidth]{../figures/distribution_of_hp_and_broker/Nanjing.pdf}
+        \includegraphics[width=\linewidth]{figures/distribution_of_hp_and_broker/Nanjing.pdf}
     \end{minipage}
@@
     \begin{minipage}{0.328\textwidth}
-        \includegraphics[width=\linewidth]{../figures/distribution_of_hp_and_broker/Shanghai.pdf}
+        \includegraphics[width=\linewidth]{figures/distribution_of_hp_and_broker/Shanghai.pdf}
     \end{minipage}
@@
     \begin{minipage}{0.328\textwidth}
-        \includegraphics[width=\linewidth]{../figures/distribution_of_hp_and_broker/Shenzhen.pdf}
+        \includegraphics[width=\linewidth]{figures/distribution_of_hp_and_broker/Shenzhen.pdf}
     \end{minipage}
     \begin{minipage}{0.328\textwidth}
-        \includegraphics[width=\linewidth]{../figures/distribution_of_hp_and_broker/Tianjin.pdf}
+        \includegraphics[width=\linewidth]{figures/distribution_of_hp_and_broker/Tianjin.pdf}
     \end{minipage}
@@
     \begin{minipage}{0.328\textwidth}
-        \includegraphics[width=\linewidth]{../figures/distribution_of_hp_and_broker/Wuhan.pdf}
+        \includegraphics[width=\linewidth]{figures/distribution_of_hp_and_broker/Wuhan.pdf}
     \end{minipage}
